### 2022-06-15 ms.tex
first

% \documentclass[linenumbers,preprint2,tighten,trackchanges]{aastex631}
\documentclass[nolinenumbers,preprint2,tighten]{aastex631}
\hypersetup{filecolor=cyan,urlcolor=magenta} %citecolor=green, linkcolor=red,
\newcommand{\vdag}{(v)^\dagger}
\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{mathrsfs}

\usepackage{bigints}
\usepackage{CJK}

\newcommand{\Msun}{\mathrm{M_\odot}}
\newcommand{\Mh}{M_\mathrm{h}}
\newcommand{\Mseed}{M_\mathrm{seed}}
\newcommand{\zseed}{z_\mathrm{seed}}
\newcommand{\hh}{\mathrm{H_2}}
\newcommand{\CII}{\mathrm{C_{II}}}
\newcommand{\vbsm}{v_\mathrm{bsm}}
\newcommand{\jlw}{J_{\rm LW}}
\newcommand{\Mdot}{\dot{M}}
\newcommand{\tlife}{t_\mathrm{life}}
\newcommand{\fseed}{f_\mathrm{seed}}
\newcommand{\fobsc}{f_\mathrm{obsc}}
\newcommand{\tEdd}{t_\mathrm{Edd}}
\newcommand{\Nt}{N_\mathrm{t}}
\newcommand{\Muv}{M_{1450}}
\newcommand{\Lbol}{L_\mathrm{bol}}
\newcommand{\fbol}{f_\mathrm{bol}}
\newcommand{\D}{\mathrm{d}}

\newcommand{\blue}[1]{\textcolor{blue}{ #1}}

%\received{March 1, 2021}
%\revised{April 1, 2021}
%\accepted{\today}

%% The following command can be used to set the latex table counters.  It
%% is needed in this document because it uses a mix of latex tabular and
%% AASTeX deluxetables.  In general it should not be needed.
\setcounter{table}{1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% The following section outlines numerous optional output that
%% can be displayed in the front matter or as running meta-data.

\shorttitle{BH growth toward $z=$ 6 BHMF \& QLF}
% \shortauthors{Li et al.}
%%
%% You can add a light gray and diagonal water-mark to the first page 
%% with this command:
% \watermark{DRAFT}
%% where "text", e.g. DRAFT, is the text to appear.  If the text is 
%% long you can control the water-mark size with:
%% \setwatermarkfontsize{dimension}
%% where dimension is any recognized LaTeX dimension, e.g. pt, in, etc.
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\graphicspath{{./}{../figs/}}
%% This is the end of the preamble.  Indicate the beginning of the
%% manuscript itself with \begin{document}.

\begin{document}
\begin{CJK*}{UTF8}{gbsn}

\title{Draft}

%% A significant change from earlier AASTEX versions is in the structure for 
%% calling author and affiliations. The change was necessary to implement 
%% auto-indexing of affiliations which prior was a manual process that could 
%% easily be tedious in large author manuscripts.
%%
%% Use \affiliation for affiliation information. The old \affil is now aliased
%% to \affiliation. AASTeX v6.31 will automatically index these in the header.
%% When a duplicate is found its index will be the same as its previous entry.
%%
%% Note that \altaffilmark and \altaffiltext have been removed and thus 
%% can not be used to document secondary affiliations. If they are used latex
%% will issue a specific error message and quit. Please use multiple 
%% \affiliation calls for to document more than one affiliation.
%%
%% The new \altaffiliation can be used to indicate some secondary information
%% such as fellowships. This command produces a non-numeric footnote that is
%% set away from the numeric \affiliation footnotes.  NOTE that if an
%% \altaffiliation command is used it must come BEFORE the \affiliation call,
%% right after the \author command, in order to place the footnotes in
%% the proper location.
%%
%% Use \email to set provide email addresses. Each \email will appear on its
%% own line so you can put multiple email address in one \email call. A new
%% \correspondingauthor command is available in V6.31 to identify the
%% corresponding author of the manuscript. It is the author's responsibility
%% to make sure this name is also in the author list.
%%
%% While authors can be grouped inside the same \author and \affiliation
%% commands it is better to have a single author for each. This allows for
%% one to exploit all the new benefits and should make book-keeping easier.
%%
%% If done correctly the peer review system will be able to
%% automatically put the author and affiliation information from the manuscript
%% and save the corresponding author the trouble of entering it by hand.

%\correspondingauthor{August Muench}
%\email{greg.schwarz@aas.org, gus.muench@aas.org}

% \author[0000-0002-1044-4081]{Wenxiu Li (李文秀)}

% \affiliation{American Astronomical Society \\
% 1667 K Street NW, Suite 800 \\
% Washington, DC 20006, USA}

%% Note that the \and command from previous versions of AASTeX is now
%% depreciated in this version as it is no longer necessary. AASTeX 
%% automatically takes care of all commas and "and"s between authors names.

%% AASTeX 6.31 has the new \collaboration and \nocollaboration commands to
%% provide the collaboration status of a group of authors. These commands 
%% can be used either before or after the list of corresponding authors. The
%% argument for \collaboration is the collaboration identifier. Authors are
%% encouraged to surround collaboration identifiers with ()s. The 
%% \nocollaboration command takes no argument and exists to indicate that
%% the nearby authors are not part of surrounding collaborations.

%% Mark off the abstract in the ``abstract'' environment. 
% \begin{abstract}

% \end{abstract}

%% Keywords should appear after the \end{abstract} command. 
%% The AAS Journals now uses Unified Astronomy Thesaurus concepts:
%% https://astrothesaurus.org
%% You will be asked to selected these concepts during the submission process
%% but this old "keyword" functionality is maintained in case authors want
%% to include these concepts in their preprints.
% \keywords{Classical Novae (251) --- Ultraviolet astronomy(1736) --- History of astronomy(1868) --- Interdisciplinary astronomy(804)}

%% We recommend that authors also use the natbib \citep
%% and \citet commands to identify citations.  The citations are
%% tied to the reference list via symbolic KEYs. The KEY corresponds
%% to the KEY in the \bibitem in the reference list below.

\vspace{5mm}
\section{Introduction} \label{sec:intro}
The growth of black holes (BHs) in galactic nuclei is elegantly related to their luminous accretion phases 
across the cosmic time \citep{1982MNRAS.200..115S,1992MNRAS.259..725S}. 
Comparing the local massive BH mass density and the integration of quasar luminosity function up to $z\sim$ 5, 
\citet{2002MNRAS.335..965Y} demonstrate the constraints on the BH accretion history and their radiative effeciency.
Extrapolation of such argument toward higher redshifts ($z\gtrsim$ 6) is unwarranted, 
due to the limitation of current capabilities of observing the high-$z$ quasar population \citep{2019BAAS...51c.121F}. 
Nevertheless, 
% while its essence is appropriate to BH evolution of all redshifts. 
in the era of the James Webb Space Telescope (JWST) and forthcoming facilities 
e.g., the Roman Space Telescope (RST) and Euclid, 
infrared imaging and spectroscopic observations will unveil a wealth of information on the
high-$z$ quasar properties and their environments 
\citep{2019BAAS...51c..45R, 2019arXiv190205569A, 2011arXiv1110.3193L}. 
Deep surveys of high-$z$ quasars and their host galaxies will shed light on the early BH evolution, 
also help answering the intriguing questions e.g., 
the existence of supermassive BHs in the early universe within one billion year, 
and the establishment of BH-galaxy coevolution \citep{2012Sci...337..544V,2013ASSL..396..293H,2020ARA&A..58...27I}.

Tracing back from $z\sim$ 6, BH seed formation is the starting point to shape the early evolution of the BH population.
From Pop III star remnants ($10-10^3 ~\Msun$) to direct collapse supermassive stars (10$^4-10^5 ~\Msun$), 
the properties of high-$z$ BH seeds are extensively modeled by simulations and semi-analytical works 
\citep[e.g.,][Toyouchi 2022]{2001ApJ...546..635O,2002Sci...295...93A,2006ApJ...652....6Y,2011MNRAS.416.2748I,
2012ApJ...756...93H,2013ApJ...778..178H,2014MNRAS.439.3798F,
2014MNRAS.445L.109I,2014MNRAS.445..544S,2014MNRAS.445..107V,2020MNRAS.499.5960S}. 
Environmental factors which modulate the Pop III star formation have been assessed, 
including (i) external ratiation in Lyman-Werner band which photo-dissociates the major coolant $\hh$ 
\citep{2002ApJ...569..558O,2003Natur.425..812B,2010MNRAS.402.1249S},
(ii) baryonic streaming motion which drives the gas against gravitational collapse 
\citep{2012MNRAS.424.1335F, 2014MNRAS.439.1092T, 2018ApJ...855...17H}
and 
(iii) violent mergers of the parent dark matter halo which dynamically excite the gas 
\citep{2003ApJ...592..645Y,2019Natur.566...85W}. 
These factors prevail in some environments at high redshifts and facilitate massive Pop III and even supermassive star formation, 
which contribute to the heavy seed scenario of supermassive BH formation at $z\gtrsim$ 6 
\citep[see a review by][]{2020ARA&A..58...27I}.

To construct the picture of BH evolution, the initial mass function (IMF) of BH seeds is required.
Studies have shown that Pop III stars (or the seed BH population) formed in mini-halos is top-heavy, while capped with $\sim 10^3~\Msun$ 
\citep{2014ApJ...781...60H,2015MNRAS.448..568H}.
Focusing on the progenitor halos of supermassive BHs at $z\sim$ 6, 
our recent semi-analytical work produces an IMF of BH seeds ranging from $10^2-10^5~\Msun$ \citep{2021ApJ...917...60L}. 
The IMF is consistent with the three-dimensional radiation hydrodynamical simulations 
constituting the stellar evolution with large scale mass inflow under realistic halo circumstances (Toyouchi et al. 2022).
In this work, we apply the seeding model to examine the BH growth in common regions in the early universe, 
constrained by the observable QLF and BHMF down to $z\sim$ 6, 
% our aim is to understand the growth patterns of early BHs.

This paper is organized as follows. Firstly, in \S \ref{sec:method} we describe the semi-analytical BH seeding procedure, 
the parameterized BH growth and how we reproduce the modeled BHMF and QLF dataset at $z\sim$ 6 using these ingredients. 
In \S \ref{sec:result} we present the fitting of model parameters constrained by quasar observations. 
We then summarize our findings in \S \ref{sec:discussion} and discuss the potential applications on exploring the high-$z$ universe.
Throughout this work, we apply the cosmological parameters from \cite{2016A&A...594A..13P},
i.e., $\Omega_{\mathrm{m}}=0.307,~\Omega_{\Lambda}=0.693,~
\Omega_{\mathrm{b}}=0.0486$, and $H_0=67.7 \mathrm{~km} \mathrm{~s}^{-1} \mathrm{Mpc}^{-1}$.

\vspace{5mm}
\section{METHODOLOGY}\label{sec:method}

\vspace{2mm}
\subsection{Seeds}\label{sec:seed}
The QLFs at high redshifts are determined by the original BH seeding and subsequent growth. 
Firstly we describe our model regarding the formation of BH seeds in progenitor DM halos 
that end up in high-$z$ quasar host galaxies with halo masses of $\Mh>10^{11}~\Msun$.
This is motivated by the observed masses of quasar hosts which are typically up to $\sim 10^{11-13}~\Msun$, 
probed by $\CII$ line width estimation \citep{2019ApJ...872L..29S}.
Therefore, we sample base halos with $\Mh = 10^{11}$, $10^{12}$, and $10^{13} ~\Msun$ at $z=$ 6. 
We then generate 10$^4$ merger trees with each base halo mass backward in time using the {\tt GALFORM} 
semi-analytic algorithm based on the extended Press-Schechter formalism 
\citep{1974ApJ...187..425P,2000MNRAS.319..168C,2008MNRAS.383..557P}.
The normalizations of the merger trees are estimated by the base halo number densities from Sheth-Tormen halo mass function \citep{2001MNRAS.323....1S}:
%%%%%%%
%    Eq. 1
%%%%%%%
\begin{equation}
n_{\Mh}= \int_{\Mh}^{10\Mh}  \frac{\D n_{\mathrm{ST}}} {\D \Mh} \D \Mh.
\label{eq:nST}
\end{equation}

BH seeding is also affected by the baryonic streaming motion of its natal cloud, 
where gas is streaming relative to the dark matter in the epoch of cosmic recombination at $z_\mathrm{rec}\approx$ 1100, 
originated from its decoupling with radiation.
The streaming velocity follows a Maxwell-Boltzmann distribution with a root-mean-square (\textit{rms}) speed of 
$\sigma(z) = 30~{\rm km~s}^{-1} (1+z)/(1+z_{\mathrm{rec}})$ which is decaying with time \citep{2010PhRvD..82h3520T}.
The impact of the super-sonic $\vbsm$ at high redshifts on the PopIII star (seed BH) formation 
is explored by various studies \citep{2012MNRAS.424.1335F,2014MNRAS.439.1092T,2017Sci...357.1375H,2019MNRAS.484.3510S,2021ApJ...917...60L}.
Their major findings are that the non-negligible $\vbsm$ injects kinetic support into pristine gas clouds, 
which increases their effective Jeans mass and delays star formation, 
yielding BH seeds heavier than typical PopIII stars. 
The volume fraction of the universe with streaming velocities higher than the \textit{rms} value
is estimated as $\simeq 0.4$. We then set $\vbsm=$ 0 and the \textit{rms} velocity as two representative cases, 
accounting for roughly $f_{\vbsm} = 60\%$ and $40\%$ of the seeding environments, respectively.

Next we introduce our seeding model where the gas dynamical and thermal evolution is regulated by the parent halo growth histories, 
and the environmental streaming velocities.
In \citet{2021ApJ...917...60L}, we propose an semi-analytical model which 
traces the gas evolution along its parent halo growth and yields the seed BH mass distribution. 
% The background UV radiation $$ is calculated by semi-analytical arguments of men
The merger heating and enhancement of background Lyman-Werner radiation intensity $\jlw$ 
due to halo clustering is taken into account to shape the gas thermal evolution. 
Besides, the baryonic streaming velocity $\vbsm$ together with the turbulent velocity $v_\mathrm{tur}$ 
through halo virialization is modeled by the effective sound speed of gas:
%%%%%%%
%    Eq. 2
%%%%%%%
\begin{equation}
  c_{\rm eff} = \sqrt{ c_{\rm s}^2+v_{\rm tur}^2/3+\left(\alpha_0 \vbsm \right)^2}, 
\end{equation}
where the coefficient $\alpha_0$ is suggested to be in order of unity by previous studies 
\citep{2017Sci...357.1375H,2019MNRAS.484.3510S} 
and we apply $\alpha_0 = 1$ in this work. 
Following this model we produce 10$^4$ BH seeds with their formation time and masses $M_\mathrm{seed}$, 
in each merger tree with a given $\vbsm$. 
Contributed by the number densities of the base halos and the fraction of environmental $\vbsm$, 
we construct the seed BH mass distribution shown in Fig.~\ref{fig:seedmf}.

%%%%%%%
%    Fig. 1
%%%%%%%
\begin{figure}
\centering
\includegraphics[width=85mm]{seedBHMF_z.pdf}
\caption{
Seed BH mass distribution formed in different redshift ranges . 
Each panel includes a redshift span of 10, 
with the newly formed BHs denoted by the hatched regions, 
and the cumulative BHs formed previously by the blue region.
The most vigorous seed formation epoches are in redshift ranges $z\sim$ $40-30$ and $30-20$.
Overall, the seed BH mass ranges from $\sim 10^2$ to $\gtrsim 10^5~\Msun$, 
imprinted with the various parent halo growth histories and environmental $\vbsm$. 
}
\label{fig:seedmf}
\end{figure}

%%%%%%%
%    Fig. 2
%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=170mm]{scheme.pdf}
\caption{
Schematical demonstration of the procedure to calculate the evolution of BH mass distribution 
from time $t$ to $t+\Delta t$. 
The probability of a BH with mass $M_\mathrm{i}$ grow to $M$ after $\Delta t$ is drew from the 
ERDF following Eq.~\ref{eq:Pl}. 
Thus the new BH mass distribution is reshaped iteratively by integrating with the $\lambda$ distribution. 
}
\label{fig:scheme}
\end{figure*}

% Figure 1 shows the BH seeds formed in progenitors of $\Mh = 10^{11}, 10^{12}$
\vspace{2mm}
\subsection{BH growth \& mass Function}\label{sec:MF}
% The BH accretion at high redshifts is probed only by snapshots, in their most luminous quasar phase. We have constraints on simulations and observations of lower redshift counterparts.
With seeds planted, we grow the BHs with a semi-analytical accretion rate model 
and study the BH mass distribution at redshift 6. 
The growth model is captured by a limited number of free parameters, 
% the quasar accretion is episodic with Eddington ratio variations,
describing the BH mass growth rate $\Mdot$ by: 
%%%%%%%
%    Eq. 3
%%%%%%%
\begin{equation}
  \label{eq:mdot}
  \Mdot = \frac{\lambda f\left(M\right) M}{\tEdd},
\end{equation}
where $\tEdd = \eta_0  M c^2/L_{\mathrm{Edd}} \approx 45$ Myr,
$\lambda = L/L_\mathrm{Edd}$ is the Eddington ratio that represents the strength of the accretion power.
Note here we adopt the radiative efficiency $\eta_0 \approx 0.1 $ according to the thin accretion disk model 
\citep{1973A&A....24..337S}, which is also consistent with 
the Soltan's argument  \citep{1982MNRAS.200..115S,2002MNRAS.335..965Y}.
% The high mass BH should be strangulated by as it grows, 
We introduce the mass dependency 
$f(M) = 0.5 \left[1+\left(M/10^8~\Msun\right)^\delta\right] ^ {-1}$, 
to suppress the high mass BH growth with a positive $\delta$. With decreasing $\delta$, 
the model is reduced to an exponential growth independent of BH mass.
% In \S~\ref{sec:fitting}, $\delta$ turns out to be close to 0, indicating an exponential grow manner independent of BH mass.

The quasar activity is episodic in nature, with bursts of accretion triggered by gas inflows 
% \citep[e.g., mergers or disk instabilities, see][]{2005Natur.433..604D,2005ApJ...630..705H}, 
\citep{2005Natur.433..604D,2005ApJ...630..705H}, 
and the accretion rate declines with self-regulating feedbacks \citep[e.g.,][]{2008ApJ...686..815Y,2011ApJ...737...26N} or 
self-similar disk evolution \citep{1991MNRAS.248..754P,2005ApJ...634..901Y,2007MNRAS.377L..25K}.
This ``flickering'' pattern of individual quasar luminosity evolution can be directly translated into the diversity in the Eddington ratios 
of a quasar sample, where the Eddington ratio distribution function (ERDF) $\D P/ \D\ln\lambda$ shares the same Schechter function shape 
with the differential time at different $\lambda$ \citep{2006ApJ...639..700H,2009ApJ...698.1550H}.
Observations also propose that the intrinsic ERDF in lower-$z$ quasars hosted by star forming galaxies follows a Schechter shape, 
\citep{2015MNRAS.447.2085S,2016ApJ...826...12J,2018MNRAS.474.1225A}, 
therefore we take 2 free parameters $\lambda_0$ and $\alpha$ to characterize the ERDF:
%%%%%%%
%    Eq. 4
%%%%%%%
\begin{equation}
  \label{eq:Pl}
  \frac{\D P}{ d\ln \lambda} \propto
  \left(\frac{\lambda} {\lambda_0} \right)^\alpha \exp{\left(-\frac{\lambda}{\lambda_0}\right)},
\end{equation}
normalized by the total probability above $\lambda_\mathrm{min}$ = 0.01.
The minimum Eddington ratio $\lambda_\mathrm{min}$ is motivated by the behavior of quasar luminosity evolution 
that decreases mildly toward $\lambda\sim 0.1-0.01$ with $\lesssim$ 100 Myr after activation \citep{2011ApJ...737...26N}, 
also suggested by a turnover at the lowest $\lambda\lesssim 0.01-0.001$ on the observational side \citep{2018MNRAS.474.1225A}.

To characterize the aforementioned ERDF in a BH population at any time snapshot, 
together with the episodic accretion pattern of individual BHs, 
we introduce a time duration $\tlife$, 
during which a single value of $\lambda$ following the ERDF of Eq.~(\ref{eq:Pl}) is assigned to a growing BH.
In this way we model a gear change taking place every $\tlife$, 
which avoids the unreality of a long-lasting super-Eddington accretion from seeding down to $z=$ 6. 
Note that the $\tlife$ is indispensable as a methodology in our modeling, 
albeit its direct comparison with observational luminous quasar lifetime is difficult, 
these timescales are correlated in realizing the SMBH growth. 
We leave a more detailed disucssion to \S~\ref{sec:discussion}.

Lastly, the seeding fraction $\fseed$ denotes the portion of halos where the central BH are initially seeded \citep{2009ApJ...696.1798T}.
Discussing on constraints from the origin of $\fseed$ is beyond our scope in this work. 
Instead we take different values $\fseed$ = 1, 0.1, and 0.01, 
and explore the dependency of the best-fit parameters on it.

Next, we explain our method to calculate the time evolution of BHMF, 
which is given by combining the BH mass distribution from the seeds growing independently in merger trees
with different base halo mass $\Mh$,
weighted by the environmental $\vbsm$ probability and seeding fraction: 
%%%%%%%
%    Eq. 5
%%%%%%%
\begin{align}
& \Phi_\mathrm{M} \equiv \frac{\D n}{\D \log M}  \nonumber \\
& =\sum_{\Mh}\sum_{\vbsm} n_{\Mh} f_{\vbsm} {\fseed} \left(\frac{\D P}{\D \log M}\right)_{\Mh, \vbsm}.
\end{align}

For a given combination of $\Mh$ and $\vbsm$, 
We then calculate the BH mass distribution $\D P/\D\log M$ iteratively 
at a series of checkpoints with an interval of $\tlife$, 
from the earliest seed formation time to $z=$ 6. 
% we set a total number of $\Nt$ checkpoints with an interval of $\tlife$,
% where $\Nt = \lfloor \left(t_\mathrm{H}(z=6) - t_\mathrm{H}(z_\mathrm{seed,max})\right)/ \tlife \rfloor$, 
At each checkpoint $t$, the BH mass distribution is developed from the growth of itself 
at the previous checkpoint, plus the seeds newly formed in between.
Considering the growth of a BH with mass $M_{\rm i}$ by a time interval $\Delta t$, 
from the accretion rate prescription in Eq.~(\ref{eq:mdot}), the final mass $M$ can be described in the relation 
%%%%%%%
%    Eq. 6
%%%%%%%
\begin{equation}
  \label{eq:mi2m}
  \ln \left(\frac{M} {M_{\rm i}}\right) + \frac{1}{\delta} 
  \left[ \left(\frac{M}{M_0}\right)^\delta - \left(\frac{M_{\rm i}}{M_0}\right)^\delta \right]
  = \frac{\lambda \Delta t}{\tEdd}.
\end{equation}

This yields the BH mass distribution 
%%%%%%%
%    Eq. 7
%%%%%%%
\begin{align}
  \label{eq:dpdm}
  & \frac{\D P}{\D \log M} = \int_{}^{} 
   \left(\frac{\D P}{\D \ln \lambda}\right)_{\lambda(M, M_\mathrm{i},\Delta t, \delta)} \nonumber \\
  & \left(\frac{\D \ln \lambda}{\D \log M} \right)_{M, M_\mathrm{i},\Delta t, \delta}
  \frac{\D P}{\D \log M_\mathrm{i}} \D\log M_\mathrm{i},
\end{align}
where ${\D P}/{\D \ln\lambda}$ is given by a set of parameters $\lambda_0$ and $\alpha$ in Eq.~(\ref{eq:Pl}), 
at the $\lambda$ value $\lambda\left(M, M_\mathrm{i},\Delta t, \delta\right)$ inferred from Eq.~(\ref{eq:mi2m}).
For the evolution of the BH mass distribution, we set $\Delta t=\tlife$.
On the other hand, for the growth of an individual seed, 
$\Delta t < \tlife$ is calculated from the seeding time to the current checkpoint,
and $ \D P/\D \log M_\mathrm{i}$ is a discrete function which is 10$^{-4}$ 
(normalized by the track numbers 10$^4$ in a merger tree) at $M_\mathrm{i} = M_\mathrm{seed}$, 
and 0 elsewhere.
This procedure is illustrated schematically in Fig.~\ref{fig:scheme}.

% wli
Setting discrete mass bins to resemble the integration in the calculation above, 
we ensure the convergence of the BHMF produced by increasing the number of mass bins to 800 log evenly across $10^2-10^{12}~\Msun$. 
Our results are consistent with that from directly generating random $\lambda$ 
following Eq.~(\ref{eq:Pl}) in each cycle of BH growth. 
Remarkably, we avoid the fluctuations in drawing random samples following the $\lambda$ distribution 
and extend to high mass (luminous) end in the BHMF (QLF) in a numerically efficient way.

% In the BHMF calculation, we set 100 mass bins ranging from  $10^2~\Msun$ to  $10^{12}~\Msun$, spacing evenly in logarithmic scale.
% This enables us to obtain the convergent BHMF at $z=$ 6 for any given parameters.

\vspace{2mm}
\subsection{QLF after obscuration}\label{sec:LF}
Furthermore, we can generate QLFs that is directly probed by high-$z$ observations.
%  compared with observations and in return constrain our model.
For a BH accreting with bolometric luminosity $\Lbol=\lambda L_\mathrm{Edd}$, 
its absolute magnitude $\Muv$ in the rest-frame ultraviolet (UV) band is given by:
%%%%%%%
%    Eq. 8
%%%%%%%
\begin{equation}
  \label{eq:M1450}
  \Muv= -21.0-2.5 \log  \left(\frac{\Lbol}{10^{45}~\mathrm{erg~s}^{-1}} \right).
\end{equation}
Here we adopt the bolometric correction factor $\fbol=4.4$ for the monochromatic UV band \citep{2006ApJS..166..470R}.
Under this conversion, an ERDF combined with the $z\sim$ 6 BH population is able to reproduce 
the quasar abundances with different luminosities. 
However, we note that a vital ingredient to construct the observed QLF, 
is the luminosity dependent obscuration fraction, 
which decreases the fraction of the detectable quasars toward the dimmer population 
\citep{2003ApJ...598..886U,2014ApJ...786..104U,2008A&A...490..905H,2014MNRAS.437.3550M}, 
thus differs the normalization and shape of the observed QLF from the intrinsic one.

% 讨论一下 obs fraction :
The current major regimes of quasar obscuration are from extinction by dusty torus and high density circumnuclear gas, 
hence intemately connected with the gas fueling and feedback process of accreting BHs \citep[see][for a review]{2018ARA&A..56..625H}.
However, from both theoretical and observational side, our current understanding of the quasar obscured fraction is inadequate, 
due to the sophisticated physical conditions which lead to obscuration and observational difficulties in probing it.
The high-$z$ qusars observed in their restframe UV-optical bands are profoundly obstructed by dust obscuration, 
while hard X-ray (2$-$10 keV) can penetrate the dust with gas dominating the absorption. 
Therefore, the dust obscuration is equavalently translated to gas absorption with column density $N_\mathrm{H}>10^{22}$ cm$^{-2}$ 
implied by the X-ray spectral fitting \citep[e.g.,][]{2003ApJ...598..886U,2007A&A...463...79G,2008A&A...490..905H}.
The redshift dependency of the obscured fraction is found to increase toward $z\sim 2$ and saturate at higher redshifts 
\citep{2008A&A...490..905H,2014ApJ...786..104U,2018MNRAS.473.2378V}.
We apply the obscuration fraction $\fobsc$ following the hard X-ray data analysis of \citet{2014ApJ...786..104U}, 
converting the hard X-ray to bolometric luminosity by the bolometric correction from \citet{2020A&A...636A..73D}.
The obscuration fraction is $\sim80\%$ (and 50\%, 30\%) with $\Muv$ = $-20$ (and $-24$, $-28$). 
Compared with another work by  \citet{2014MNRAS.437.3550M}, this shows a similar decreasing trend with luminosity, 
and the values are in agreement within a factor of 3.
In this work, we ignore the uncertain Comption thick ($N_\mathrm{H}>10^{24}$ cm$^{-2}$) quasar population, which is hidden even from hard X-ray observation 
and also has possible dependency on quasar properties.
% and it is currently not warranted to discuss the uncertainties of $\fobsc$.
Note that the obscured fraction at high-$z$ is still under investigated, 
with complex convertions between the probes in different observational bands,
% optical and X-ray observations, 
and we may refer to more solid prescriptions of $\fobsc$ in the future.

After taking obscuration into account, the observed luminosity function for a given BHMF and ERDF can be written as:
%%%%%%%
%    Eq. 9
%%%%%%%
\begin{align}
\label{eq:dn_dM1450}
& \Phi_\mathrm{\Muv} \equiv \frac{\D n}{\D \Muv} \nonumber \\
& = \left[1 -\fobsc\left(\Muv\right) \right] \times % \nonumber \\
\int_{}^{} \left(\frac{\D P}{\D \ln \lambda}\right)_{\lambda(\Muv, M)}  \nonumber \\
& \left(\frac{\D \ln \lambda}{\D \Muv} \right)_{\Muv, M} \Phi_\mathrm{M} \D \log M,
\end{align}
where $\lambda\left(\Muv,M\right)$ is the obtained from Eq.~(\ref{eq:M1450}).
%
Hence the observed QLF can be produced simultaneously with the BHMF from a set of model paramters, 
to be compared with the ones from observation.

\vspace{2mm}
\subsection{MCMC fitting}\label{sec:fitting}
In this section, we describe the Markov Chain Monte Carlo (MCMC) fitting procedure we adopt to optimize the parameters described in \S~\ref{sec:MF}. 
%%%%%%%
%    Fig. 2
%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=170mm]{contour.pdf}
\caption{
Posterior distributions of all the model parameters with 3 different $\fseed$ values, 
including the marginalized one dimensional projection and the two dimensional distribution between every two parameters. 
All the parameters converge to a single peak, 
and specially the $\log\delta$ is confined above the artificial $-3$ barrier, 
which is sufficiently low and can be neglected in the model.
}
\label{fig:contour}
\end{figure*}
%
% 1. data: observational MF LF; describe quadratic error in Willott 2010
Firstly the BHMF data is adopted from \citet{2010AJ....140..546W} (hereafter W10),
where they reconstruct the BHMF with the QLF and ERDF
extracted from the virial BH mass among $\sim$ 20 quasars at $z\approx$ 6. 
The BHMF spanning $10^7 < M <10^{10}~\Msun$ is best constrained around $10^9~\Msun$, 
and the error is pronounced toward the low mass and high mass end.
We take 10 mass bins spacing evenly in logscale and a quadratic form of the error, 
covering the same ranges as their bootstrap resamples (see Figure 8 of W10). 
On the observed QLF side, we adopt the binned data and error bars from \citet{2018ApJ...869..150M}, 
over a wide range of $-30 < \Muv <-22$ mag (see their Table 4 and Figure 13).

% 2. prior
The prior function, i.e. the probability distribution to draw parameter samples from, 
encodes the physically acceptable ranges and underlying distributions for all parameters. 
We assign uniform prior $\tlife$ within 10 to 200 Myr, 
motivated by the constraints on the quasar lifetime during an optically luminous phase \citep[e.g.,][]{2004cbhg.symp..169M}.
For the mass dependency of BH growth we constrain the value of $\log \delta$ from $-4$ to $-0.3$, 
slightly suppressing the growth in the high mass end. 
% After trials we find in the Markov chain, the value of $\tlife$ reduces to $\lesssim$ 100 Myr, 
% and the one for $\delta$ assembles to $\lesssim 0.1$. 
% Driven by these phenomena, we switch the uniform $\tlife$ prior to 10 to 200 Myr,
% and use $\log \delta$ instead of $\delta$ with a prior ranging from $-4$ to $-1$ in pursuit of better fitting performance. 
Specificaly, the prior is restricted by an exponential cutoff when $\log \delta < -3$,
since toward low $\log\delta$ the model is essentially mass-independent,
and remains uniform otherwise. 
For the characteristic value of Eddington ratio $\lambda_0$ in the Schechter shape, 
we impose a Gaussian prior with the mean value $\mu_{\lambda_0}=0.6$ and scatter $\sigma_{\lambda_0}=0.4$, 
% motivated by the various observations revealing a large sample of quasars with peak $\lambda\lesssim 1$,
motivated by the observations revealing $z=$ 6 quasars peak with $\lambda \sim 0.6$ 
% \citep[e.g.,][Onoue et al. in preparation]{2010AJ....140..546W}.
\citep[e.g.,][]{2010AJ....140..546W}.
Specially a complete sample of quasars from Onoue et al. in prep peak with $\log \lambda_0 \approx -0.24 \pm 0.31$ 
before correcting the selection bias. 
% It is worth noting that, observationally the high-$z$ ERDF is fitted by a log-normal function. 
% \blue{
% because of detection limit, there may be a large population of low $\lambda$ BHs unrevealed,
% so our model of Schechter distribution is purely from theoretical prediction 
% and extrapolation of the statistical properties of its low-$z$ counterparts. 
% Then the slope index alpha uncertain \dots
% }
% However, lower-$z$ quasar observations reveal that ERDF is better fitted by a Schechter function \citep{2015MNRAS.447.2085S}, 
% indicating a prominent population of low $\lambda$ quasars is hidden by the flux-limited incompleteness.
Finally to the slope index $\alpha$ which remains unconstrained by current probes,
% considering the more significant obscuration of lower $\lambda$ quasars 
we assign a Gaussian prior, with the mean value $\mu_{\alpha}=0.$ and scatter $\sigma_{\alpha}=0.3$.

%%%%%%%
%    Fig. 3
%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=170mm]{fits_MF.pdf}
\caption{
Fit of BHMF at $z=$ 6 by the best-fit parameters (orange line), with one sigma spread (shaded region) for the 3 different $\fseed$ values. 
The blue line shows the BHMF derived by \citet{2010AJ....140..546W}.
% error of observation
}
\label{fig:fitmf}
\end{figure*}

%%%%%%%
%    Fig. 4
%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=170mm]{fits_LF.pdf}
\caption{
Fit of QLF at $z=$ 6, by the best-fit parameters and one sigma spread as described in \ref{fig:fitmf}. 
The blue data points with error bars label the complete QLF sample from the observation by \citet{2018ApJ...869..150M}.
}
\label{fig:fitlf}
\end{figure*}

% 3. posterior
% Then evaluating the likelihood of the dataset reproducing the observed BHMF and QLF at $z=$ 6, 
% the Markov chain of samples converges to the best-fit (maximum likelihood) parameters.
Following the prior distribution, parameters are sampled to generate the synthetic BHMF and QLF dataset, 
which is then conjointly compared with the observational data. 
The offset between the model and data is evaluated as 
%%%%%%%
%    Eq. 10
%%%%%%%
\begin{align}
  \chi^2 = \sum_i
  \frac{\left(\log{\Phi_\mathrm{mod,i}} - \log{\Phi_\mathrm{obs,i}}\right)^2}{(\log{\Phi_\mathrm{err,i}})^2},
\end{align}
where $\Phi_\mathrm{mod,i}$ and $\Phi_\mathrm{obs,i}$ 
represent the modeled and observational values of $\Phi_\mathrm{M}$ ($\Phi_\mathrm{\Muv}$) in the \textit{i-}th BHMF (QLF) bin, and 
$\Phi_\mathrm{err,i}$ is the corresponding error.
Note that the equal constraints from the BHMF and QLF are realized by extracting
comparable numbers of data bins from $\Phi_\mathrm{M}$ and $\Phi_\mathrm{\Muv}$.
% the constraint is actually insensitive to the choice of bin numbers. 
The posterior distribution of the MCMC fitting is stabilized around the minimum value of $\chi^2$ (highest likelihood), 
with the models best reproducing the $z=$ 6 BHMF and QLF.

\vspace{5mm}
\section{Results}\label{sec:result}

\vspace{2mm}
\subsection{Fitting Results}\label{sec:fitting_result}
In Fig.~\ref{fig:contour}, we visualize the MCMC fitting results for each parameter: distribution with the peak and one sigma scatter, 
with panels (a), (b) and (c) for $\fseed=$ 1.0, 0.1 and 0.01, respectively. 
With different $\fseed$, the best-fit solutions consistently show that $\delta$ is a nuisance parameter, 
which is sufficiently small and should be marginalized out. This suggests that in our model assumption, 
a nearly exponential growth pattern is favored. 
% In other words, on average the BH growth can be described as exponential, 
% under the premise that the gas supply is episodical. 
The best-fit value of $\tlife$ is 20 $\sim$ 30 Myr for all the three cases, 
while $\alpha$ increases with decreasing $\fseed$, from $-0.15$ ($\fseed=1.0$) to 0.04 ($\fseed=0.1$) and 0.22 ($\fseed=0.01$).
indicating strong degeneracy between the $\fseed$ and $\alpha$ values. 
With lower $\fseed$, more fastly growing BHs are needed to reporduce the high mass end of the BHMF, hence the best-fit 
$\alpha$ increases and higher $\lambda$ is more commonly realized from the Schechter shape. 
% We expect more complete observations to better constrain the parameter priors in the model fitting.

In Fig.~\ref{fig:fitmf} and Fig.~\ref{fig:fitlf}, we show the BHMF and QLF at $z=$ 6 reproduced by the best-fit parameters, 
as well as the one sigma spread.
% Together with 100 bootstrap resamples, 
The parameters are inferred to be reasonable fits consistent with the observational data.

\vspace{2mm}
\subsection{Individual BH growth}\label{sec:evol}
The best-fit models from MCMC realizations enable us to generate a sample of BH evolutionary tracks starting from BH seeds.
Taking $\fseed=$ 0.01 as a fiducial case, in the following we demonstrate how the BH sample is constructed and its hints on observations.

We generate a 10$^7$ sample of BH at $z=$ 35, with seed mass $M_\star = 1.5\times 10^3~\Msun$, 
\blue{(10$^5$ sample size actually, but with $\fseed=0.01$, essentially 10$^7$)}
% \blue{(1e3 $\Msun$ in plot, with seed mass and redshift distribution can also be realized)}, 
motivated by the properties of typical BH seeds (with median formation redshift and median mass).
For individual BH growth history, every time interval $\tlife$ we assign an Eddington ratio 
$\lambda$ following the Schechter shape in Eq.~(\ref{eq:Pl}), 
until $z=$ 6 we take a snapshot of the BH mass and $\lambda$ distributions.
With the best-fit parameters, the BH growth tracks which finally end up with $>10^8~\Msun$ 
are shown in Fig.~\ref{fig:track}. 
We notice that in this sample there are 4 BHs with $M>10^9~\Msun$, 
among which 3 BHs are in sub-Eddington accretion mode, and 1 in super-Eddington. 
If we extrapolate the BH mass with the $z \sim$ 6 witnessed Eddington ratio back to $z\sim$ 30, 
the sub-Eddington accreting BHs trace back to exceedingly massive seeds which are hard to be explained by current seeding scenarios. 
Observations also raise strong challenges to the growth histories of these sub-Eddington accreting BHs
\citep[e.g.,][]{2019ApJ...880...77O}.
In contrast, the 1 super-Eddington accreting BH traces back to unrealistically low seed mass. 
On the other hand, we show the mass growth tracks assuming constant Eddington ratio $\lambda=1$ for comparison, 
and find all the BHs trace back to $\lesssim 10^2~\Msun$ in this constantly vigorous accretion case. 
Both two treatments lead to BH seed masses extrapolation which deviate from the initial seeds we plant. 
In \citet{2021ApJ...907L...1W}, they discover the currently known most distant quasar at $z=7.642$, 
tracing back with Eddington accretion, the central BH reaches the $10^{4-6}~\Msun$ seed mass range at $z=$ 30. 
However in our best-fit model, we observe that to trace back BH mass and understand their seeding scenarios, 
taking constant Eddington ratio derived from high-$z$ observation or assuming $\lambda=1$ are both unrealistic. 
Therefore we raise a caveat that under these assumptions the seed mass achieved may be unreliable. 
Instead we should take into account the episodical accretion nature of quasars, 
including both bursts of accretion and quiescent phases.
% This is supported strongly by our best model of a $\gtrsim 20$ Myr $\tlife$, which is intrinsically connected with 
% the observational active quasar episode.

%%%%%%%
%    Fig. 5
%%%%%%%
\begin{figure}
\centering
\includegraphics[width=85mm]{2022-05-05_14-27-43_Mevol.png}
\caption{
BH growth tracks from $z=$ 30 produced by the best-fit model in the $\fseed=0.01$ case, 
selected by the criterion $M>10^8~\Msun$ at $z=$ 6. 
Highlighted are 4 massive BHs with $M>10^9~\Msun$ (with colors), 
extrapolated back following exponential growth with constant Eddington ratio: 
constant $\lambda$ keeping the $z=$ 6 value with dashed lines and 
Eddington limit growth with $\lambda=1$ with dotted lines.
}
\label{fig:track}
\end{figure}

\vspace{2mm}
\subsection{Observed v.s. Intrinsic $\lambda$ Distribution}\label{sec:ldist}
Discussion on quasar \textit{intrinsic} properties is naturally difficult, 
in the sense that quasars are selected by \textit{observed} properties, 
e.g., a cut off of detection under some magnitude floor. 
The unavoidable bias of quasar surveys may be corrected by the selection function tested 
by experiments on the detectability of mock data.
In this section, we examine the effect of flux-limited quasar survey on the observed $\lambda$ distribution, 
taking advantage of our complete sample of model BHs in the whole luminosity range.

Based on the quasar sample from the best-fit model described in \S~\ref{sec:evol}, 
we select quasars above a bolometric luminosity cutoff at $\Lbol=10^{46}~\mathrm{erg~s^{-1}}$. 
In Fig.~\ref{fig:lhist}, we plot the intrinsic $\lambda$ distribution for the whole sample together with 
the selected sample (observed one). 
The intrinsic $\lambda$ follows the Schechter shape with a majority of inactive quasars, 
while the observed $\lambda$ is biased toward higher values, and the shape changes to 
more Gaussian-like distribution. 
The latter distribution is presented by various observational efforts 
\citep[e.g.,][]{2010AJ....140..546W,2019ApJ...873...35S}, 
while we predict a huge hidden population of low $\lambda$, 
based on the best-fit model connecting the BH growth history and high-$z$ BHMF and QLF. 
To demonstrate qualitatively the caveat for the detection limit on recovering the intrinsic quasar properties, 
we also plot the $\lambda$ distribution for a sample with $\Lbol>10^{45}~\mathrm{erg~s^{-1}}$. 
We find that lowering the detection limit unveils more quasars with low Eddington ratio. 
Therefore we emphasize that it is imperative to lower the detection limit in order to 
understand a more complete quasar sample at high-$z$, 
so that the numerous dimly accreting BHs can be shed light on.

%%%%%%%
%    Fig. 6
%%%%%%%
\begin{figure}
\centering
\includegraphics[width=85mm]{l_hist.png}
\caption{
Intrinsic $\lambda$ distribution (blue) and the observed ones after imposing selection effects by $\Lbol>10^{45}$ (orange) and 10$^{46}$ erg~s$^{-1}$ (green).
The observed histograms are elevated by arbitrary normalizations for comparison of the distribution shapes.
The intrinsic $\lambda$ distribution follows the dashed line which shows the analytical $\lambda$ distribution by the best-fit Schechter model. 
While with increasing $\Lbol$ limit, the observed $\lambda$ shows 
}
\label{fig:lhist}
\end{figure}

\vspace{5mm}
\section{Discussion}\label{sec:discussion}

% \begin{acknowledgments}
% % We thank all the people that have made this paper what it is today.  
% % This includes but not limited to Bob Hanisch, Chris Biemesderfer, Lee Brotzman,
% % Pierre Landau, Arthur Ogawa, Maxim Markevitch, Alexey Vikhlinin and Amy
% % Hendrickson. Also special thanks to David Hogg and Daniel Foreman-Mackey
% % for the new "modern" style design. Considerable help was provided via bug
% % reports and hacks from numerous people including Patriciddo Cubillos, Alex
% % Drlica-Wagner, Sean Lake, Michele Bannister, Peter Williams, and Jonathan
% % Gagne.
% \end{acknowledgments}

%% To help institutions obtain information on the effectiveness of their 
%% telescopes the AAS Journals has created a group of keywords for telescope 
%% facilities.
%
%% Following the acknowledgments section, use the following syntax and the
%% \facility{} or \facilities{} macros to list the keywords of facilities used 
%% in the research for the paper.  Each keyword is check against the master 
%% list during copy editing.  Individual instruments can be provided in 
%% parentheses, after the keyword, but they are not verified.

% \facilities{HST(STIS), Swift(XRT and UVOT), AAVSO, CTIO:1.3m, CTIO:1.5m,CXO}

%% Similar to \facility{}, there is the optional \software command to allow 
%% authors a place to specify which programs were used during the creation of 
%% the manuscript. Authors should list each code and include either a
%% citation or url to the code inside ()s when available.

% \software{astropy \citep{2013A&A...558A..33A,2018AJ....156..123A},  
%           Cloudy \citep{2013RMxAA..49..137F}, 
%           Source Extractor \citep{1996A&AS..117..393B}
%           }

%% Appendix material should be preceded with a single \appendix command.
%% There should be a \section command for each appendix. Mark appendix
%% subsections with the same markup you use in the main body of the paper.

%% Each Appendix (indicated with \section) will be lettered A, B, C, etc.
%% The equation counter will reset when it encounters the \appendix
%% command and will number appendix equations (A1), (A2), etc. The
%% Figure and Table counter will not reset.

%% For this sample we use BibTeX plus aasjournals.bst to generate the
%% the bibliography. The sample631.bib file was populated from ADS. To
%% get the citations to show in the compiled file do the following:
%%
%% pdflatex sample631.tex
%% bibtext sample631
%% pdflatex sample631.tex
%% pdflatex sample631.tex

\newpage
% \vspace{100mm}
\bibliography{ref}{}
\bibliographystyle{aasjournal}

%% This command is needed to show the entire author+affiliation list when
%% the collaboration and author truncation commands are used.  It has to
%% go at the end of the manuscript.
%\allauthors

%% Include this line if you are using the \added, \replaced, \deleted
%% commands to see a summary list of all changes at the end of the article.
%\listofchanges

\end{CJK*}
\end{document}

% End of file `sample631.tex'.

### 2022-06-17 ms.tex
Sec.2 revised, ref to be added

@@
 This is motivated by the observed masses of quasar hosts which are typically up to $\sim 10^{11-13}~\Msun$, 
-probed by $\CII$ line width estimation \citep{2019ApJ...872L..29S}.
+probed by \blue{$\CII$ line width estimation} \citep{2019ApJ...872L..29S}.
 Therefore, we sample base halos with $\Mh = 10^{11}$, $10^{12}$, and $10^{13} ~\Msun$ at $z=$ 6. 
@@
 semi-analytic algorithm based on the extended Press-Schechter formalism 
-\citep{1974ApJ...187..425P,2000MNRAS.319..168C,2008MNRAS.383..557P}.
-The normalizations of the merger trees are estimated by the base halo number densities from Sheth-Tormen halo mass function \citep{2001MNRAS.323....1S}:
-%%%%%%%
-%    Eq. 1
-%%%%%%%
-\begin{equation}
-n_{\Mh}= \int_{\Mh}^{10\Mh}  \frac{\D n_{\mathrm{ST}}} {\D \Mh} \D \Mh.
-\label{eq:nST}
-\end{equation}
+\citep{1974ApJ...187..425P,2000MNRAS.319..168C,2008MNRAS.383..557P}, and study the BH seeds formed therein.
 
@@
 Besides, the baryonic streaming velocity $\vbsm$ together with the turbulent velocity $v_\mathrm{tur}$ 
-through halo virialization is modeled by the effective sound speed of gas:
-%%%%%%%
-%    Eq. 2
-%%%%%%%
-\begin{equation}
-  c_{\rm eff} = \sqrt{ c_{\rm s}^2+v_{\rm tur}^2/3+\left(\alpha_0 \vbsm \right)^2}, 
-\end{equation}
-where the coefficient $\alpha_0$ is suggested to be in order of unity by previous studies 
-\citep{2017Sci...357.1375H,2019MNRAS.484.3510S} 
-and we apply $\alpha_0 = 1$ in this work. 
-Following this model we produce 10$^4$ BH seeds with their formation time and masses $M_\mathrm{seed}$, 
-in each merger tree with a given $\vbsm$. 
-Contributed by the number densities of the base halos and the fraction of environmental $\vbsm$, 
-we construct the seed BH mass distribution shown in Fig.~\ref{fig:seedmf}.
+through halo virialization is taken into account
+\footnote{
+We model the effective sound speed of gas as $c_{\rm eff} = \sqrt{ c_{\rm s}^2+v_{\rm tur}^2/3+\left(\alpha_0 \vbsm \right)^2}$,
+where the coefficient $\alpha_0 = 1$ is motivated by previous studies 
+\citep{2017Sci...357.1375H,2019MNRAS.484.3510S}.
+}.
+Following this model we produce 10$^4$ BH seeds with their formation time and masses, 
+in each merger tree with a given $\vbsm$, 
+the abundance of seeds is normalized with the base halo number density from the Sheth-Tormen \citep{2001MNRAS.323....1S} halo mass function:
+\begin{align*}
+  n_{\Mh}= \int_{\Mh}^{10\Mh}  \frac{\D n_{\mathrm{ST}}} {\D \Mh} \D \Mh, 
+\end{align*}
+weighted by the environmental $\vbsm$ fraction $f_{\vbsm}$. 
+We then construct the seed BH mass distribution shown in Fig.~\ref{fig:seedmf}.
 
@@
 and study the BH mass distribution at redshift 6. 
+\blue{(references + discussion)}
 The growth model is captured by a limited number of free parameters, 
@@
 %%%%%%%
-%    Eq. 3
+%    Eq. 1
 %%%%%%%
@@
 $f(M) = 0.5 \left[1+\left(M/10^8~\Msun\right)^\delta\right] ^ {-1}$, 
-to suppress the high mass BH growth with a positive $\delta$. With decreasing $\delta$, 
+to suppress the high mass BH growth with a positive $\delta$. 
+\blue{(references)}
+With decreasing $\delta$, 
 the model is reduced to an exponential growth independent of BH mass.
@@
 %%%%%%%
-%    Eq. 4
+%    Eq. 2
 %%%%%%%
@@
 %%%%%%%
-%    Eq. 5
+%    Eq. 3
 %%%%%%%
@@
 %%%%%%%
-%    Eq. 6
+%    Eq. 4
 %%%%%%%
@@
 %%%%%%%
-%    Eq. 7
+%    Eq. 5
 %%%%%%%
@@
 %%%%%%%
-%    Eq. 8
+%    Eq. 6
 %%%%%%%
@@
 %%%%%%%
-%    Eq. 9
+%    Eq. 7
 %%%%%%%
@@
 %%%%%%%
-%    Eq. 10
+%    Eq. 8
 %%%%%%%

### 2022-06-21 ms.tex
in Sec.2 revised partially as M, next would be Sec. 3 by K first round

@@
 that end up in high-$z$ quasar host galaxies with halo masses of $\Mh>10^{11}~\Msun$.
-This is motivated by the observed masses of quasar hosts which are typically up to $\sim 10^{11-13}~\Msun$, 
-probed by \blue{$\CII$ line width estimation} \citep{2019ApJ...872L..29S}.
+This is motivated by the estimated masses of quasar hosts which are typically up to $\sim 10^{11-13}~\Msun$, 
+probed by the $\left[\mathrm{C} \text{ II }\right]$ 158 $\micron$ fine structure line width \citep{2019ApJ...872L..29S}.
+\blue{references}
 Therefore, we sample base halos with $\Mh = 10^{11}$, $10^{12}$, and $10^{13} ~\Msun$ at $z=$ 6. 
@@
 %%%%%%%
+\begin{equation*}
+  \label{eq:mdot_1}
+  \Mdot = \frac{\lambda f\left(M\right) M}{\tEdd} ,
+\end{equation*}
 \begin{equation}
   \label{eq:mdot}
-  \Mdot = \frac{\lambda f\left(M\right) M}{\tEdd},
+  \Mdot = \lambda f\left(M\right) \Mdot_\mathrm{Edd} ,
 \end{equation}
-where $\tEdd = \eta_0  M c^2/L_{\mathrm{Edd}} \approx 45$ Myr,
-$\lambda = L/L_\mathrm{Edd}$ is the Eddington ratio that represents the strength of the accretion power.
-Note here we adopt the radiative efficiency $\eta_0 \approx 0.1 $ according to the thin accretion disk model 
-\citep{1973A&A....24..337S}, which is also consistent with 
-the Soltan's argument  \citep{1982MNRAS.200..115S,2002MNRAS.335..965Y}.
+% where $\tEdd = \eta_0  M c^2/L_{\mathrm{Edd}} \approx 45$ Myr,
+where $\lambda = L/L_\mathrm{Edd}$ is the Eddington ratio,
+and $\Mdot_\mathrm{Edd} = L_{\mathrm{Edd}}/\eta_0 c^2$ is the Eddington accretion rate with the radiative efficiency $\eta_0$.
+Note here we adopt the radiative efficiency $\eta_0 \approx 0.1 $,
+according to the thin accretion disk model \citep{1973A&A....24..337S}, 
+which is also consistent with the Soltan's argument \citep{1982MNRAS.200..115S,2002MNRAS.335..965Y}.
+Then $\tEdd =  M/\Mdot_{\mathrm{Edd}} \approx 45$ Myr is the Salpeter $e$-folding timescale \citep{1964ApJ...140..796S}.
 % The high mass BH should be strangulated by as it grows, 
@@
 For a BH accreting with bolometric luminosity $\Lbol=\lambda L_\mathrm{Edd}$, 
-its absolute magnitude $\Muv$ in the rest-frame ultraviolet (UV) band is given by:
+its rest-frame ultraviolot (UV) absolute magnitude $\Muv$ 
+at 1450 $\mathrm{\AA}$ is given by: 
 %%%%%%%
@@
 is the luminosity dependent obscuration fraction, 
-which decreases the fraction of the detectable quasars toward the dimmer population 
+which decreases the fraction of the detectable quasars preferentially in the dimmer population 
 \citep{2003ApJ...598..886U,2014ApJ...786..104U,2008A&A...490..905H,2014MNRAS.437.3550M}, 
@@
 \caption{
-Posterior distributions of all the model parameters with 3 different $\fseed$ values, 
+Posterior distributions of all the model parameters with $\fseed=0.1$ and 0.01, 
 including the marginalized one dimensional projection and the two dimensional distribution between every two parameters. 
@@
 Fit of QLF at $z=$ 6, by the best-fit parameters and one sigma spread as described in \ref{fig:fitmf}. 
-The blue data points with error bars label the complete QLF sample from the observation by \citet{2018ApJ...869..150M}.
+The blue data points with error bars label the QLF from the observation by \citet{2018ApJ...869..150M}.
 }
@@
 Note that the equal constraints from the BHMF and QLF are realized by extracting
-comparable numbers of data bins from $\Phi_\mathrm{M}$ and $\Phi_\mathrm{\Muv}$.
+comparable numbers of data points from $\Phi_\mathrm{M}$ and $\Phi_\mathrm{\Muv}$.
 % the constraint is actually insensitive to the choice of bin numbers. 

### 2022-06-24 ms.tex
ms0623

@@
 ERDF following Eq.~\ref{eq:Pl}. 
-Thus the new BH mass distribution is reshaped iteratively by integrating with the $\lambda$ distribution. 
+Thus the new BH mass distribution is reshaped iteratively by integrating with the ERDF. 
 }
@@
 %%%%%%%
-\begin{equation*}
-  \label{eq:mdot_1}
-  \Mdot = \frac{\lambda f\left(M\right) M}{\tEdd} ,
-\end{equation*}
+% \begin{equation*}
+%   \label{eq:mdot_1}
+%   \Mdot = \frac{\lambda f\left(M\right) M}{\tEdd} ,
+% \end{equation*}
 \begin{equation}
@@
 following Eq.~(\ref{eq:Pl}) in each cycle of BH growth. 
-Remarkably, we avoid the fluctuations in drawing random samples following the $\lambda$ distribution 
+Remarkably, we avoid the fluctuations in drawing random samples following the ERDF 
 and extend to high mass (luminous) end in the BHMF (QLF) in a numerically efficient way.
@@
 %%%%%%%
-%    Fig. 2
+%    Fig. 3
 %%%%%%%
@@
 %%%%%%%
-%    Fig. 3
+%    Fig. 4
 %%%%%%%
@@
 \centering
-\includegraphics[width=170mm]{fits_MF.pdf}
+\includegraphics[width=170mm]{fits_MF.png}
 \caption{
-Fit of BHMF at $z=$ 6 by the best-fit parameters (orange line), with one sigma spread (shaded region) for the 3 different $\fseed$ values. 
+Fit of BHMF at $z=$ 6 by the best-fit parameters (orange line), with one sigma spread (shaded region) for $\fseed=$ 0.1 and 0.01. 
 The blue line shows the BHMF derived by \citet{2010AJ....140..546W}.
@@
 %%%%%%%
-%    Fig. 4
+%    Fig. 5
 %%%%%%%
@@
 \centering
-\includegraphics[width=170mm]{fits_LF.pdf}
+\includegraphics[width=170mm]{fits_LF.png}
 \caption{
@@
 In Fig.~\ref{fig:contour}, we visualize the MCMC fitting results for each parameter: distribution with the peak and one sigma scatter, 
-with panels (a), (b) and (c) for $\fseed=$ 1.0, 0.1 and 0.01, respectively. 
-With different $\fseed$, the best-fit solutions consistently show that $\delta$ is a nuisance parameter, 
+with panels (a) and (b) for $\fseed=$ 0.1 and 0.01, respectively. 
+The results for the $\fseed=1$ case is complemented in the Appendix.
+With different $\fseed$, the best-fit solutions consistently show that $\delta \lesssim -1$ is a nuisance parameter, 
 which is sufficiently small and should be marginalized out. This suggests that in our model assumption, 
@@
 % under the premise that the gas supply is episodical. 
-The best-fit value of $\tlife$ is 20 $\sim$ 30 Myr for all the three cases, 
-while $\alpha$ increases with decreasing $\fseed$, from $-0.15$ ($\fseed=1.0$) to 0.04 ($\fseed=0.1$) and 0.22 ($\fseed=0.01$).
-indicating strong degeneracy between the $\fseed$ and $\alpha$ values. 
-With lower $\fseed$, more fastly growing BHs are needed to reporduce the high mass end of the BHMF, hence the best-fit 
-$\alpha$ increases and higher $\lambda$ is more commonly realized from the Schechter shape. 
+The best-fit value of $\tlife$ is 20 $\sim$ 30 Myr for both cases, 
+while that of $\alpha$ increases with decreasing $\fseed$, 
+from 0.12 ($\fseed=0.1$) to 0.20 ($\fseed=0.01$),
+indicating a strong degeneracy between the $\fseed$ and $\alpha$ values. 
+With lower seeding fraction, a larger number of BHs are required to grow rapidly to reporduce the observed massive population at $z\sim$ 6, 
+hence the best-fit $\alpha$ increases and higher accretion rate is realized from the Schechter shape with higher $\alpha$. 
 % We expect more complete observations to better constrain the parameter priors in the model fitting.
@@
 as well as the one sigma spread. 
-% Together with 100 bootstrap resamples, 
-The parameters are inferred to be reasonable fits consistent with the observational data.
+The observed BHMF in W10 and QLF in \citet{2018ApJ...869..150M} with errors are also plotted for comparison.
+Note that the BHMF in W10 is only sensitive to the $>10^8~\Msun$ regime and our results are consistent in this mass range.
+The QLF fitting results overproduce the abundance of faint quasars than observation, 
+% due to the lack of fine tuning by the model parameters in the low mass range, 
+with the tension slightly eased in the case of $\fseed=0.01$ than $\fseed=0.1$. 
+The cause of this difference is that in the $\fseed=0.01$ case, 
+the progenitor BHs of $10^{7-8}~\Msun$ is systematically lower than in the $\fseed=0.1$ case, 
+which is closer to the peak of the seed mass distribution (see Fig.~\ref{fig:seedmf}), 
+this naturally brings the slope of QLF (and BHMF) in the faint (low-mass) end shallower than in the luminous (high-mass) end.
+Overall, the parameters are inferred to be reasonable fits consistent with the observational data.
 
@@
 The best-fit models from MCMC realizations enable us to generate a sample of BH evolutionary tracks starting from BH seeds.
-Taking $\fseed=$ 0.01 as a fiducial case, in the following we demonstrate how the BH sample is constructed and its hints on observations.
+We take $\fseed=$ 0.01 as a fiducial case, where the best-fit parameters for BH growth are 
+$\tlife=18.76$ Myr, $\log\delta=-1.26$, $\lambda_0=0.87$, and $\alpha=0.20$.
+In the following we demonstrate how the BH sample is constructed and its hints on observations.
 
-We generate a 10$^7$ sample of BH at $z=$ 35, with seed mass $M_\star = 1.5\times 10^3~\Msun$, 
-\blue{(10$^5$ sample size actually, but with $\fseed=0.01$, essentially 10$^7$)}
+% We generate a 10$^7$ sample of BHs at $z=$ 35, with seed mass $M_\star = 1.5\times 10^3~\Msun$, 
+% \blue{(10$^5$ sample size actually, but with $\fseed=0.01$, essentially 10$^7$)}
 % \blue{(1e3 $\Msun$ in plot, with seed mass and redshift distribution can also be realized)}, 
-motivated by the properties of typical BH seeds (with median formation redshift and median mass).
+% motivated by the properties of typical BH seeds (with median formation redshift and median mass).
+We plant a sample of 10$^7$ BH seeds at high redshifts, 
+with their formation time and mass distribution according to the seeding model described in \S~\ref{sec:seed}. 
 For individual BH growth history, every time interval $\tlife$ we assign an Eddington ratio 
 $\lambda$ following the Schechter shape in Eq.~(\ref{eq:Pl}), 
-until $z=$ 6 we take a snapshot of the BH mass and $\lambda$ distributions.
+until $z=$ 6 we take a snapshot of the BH mass and ERDF.
 With the best-fit parameters, the BH growth tracks which finally end up with $>10^8~\Msun$ 
 are shown in Fig.~\ref{fig:track}. 
-We notice that in this sample there are 4 BHs with $M>10^9~\Msun$, 
-among which 3 BHs are in sub-Eddington accretion mode, and 1 in super-Eddington. 
+We notice that in this sample there are 7 BHs with $M>10^9~\Msun$, 
+among which 5 BHs are in sub-Eddington accretion mode, and 2 in super-Eddington. 
 If we extrapolate the BH mass with the $z \sim$ 6 witnessed Eddington ratio back to $z\sim$ 30, 
@@
 \citep[e.g.,][]{2019ApJ...880...77O}.
-In contrast, the 1 super-Eddington accreting BH traces back to unrealistically low seed mass. 
+In contrast, the super-Eddington accreting BHs trace back to unrealistically low seed mass. 
 On the other hand, we show the mass growth tracks assuming constant Eddington ratio $\lambda=1$ for comparison, 
-and find all the BHs trace back to $\lesssim 10^2~\Msun$ in this constantly vigorous accretion case. 
-Both two treatments lead to BH seed masses extrapolation which deviate from the initial seeds we plant. 
+and find all the BHs trace back to $\lesssim 10^2~\Msun$ with the constantly vigorous accretion. 
+Both treatments of the constant $\lambda$ lead to BH seed masses extrapolation that deviate from the initial seeds we plant. 
 In \citet{2021ApJ...907L...1W}, they discover the currently known most distant quasar at $z=7.642$, 
@@
 %%%%%%%
-%    Fig. 5
+%    Fig. 6
 %%%%%%%
@@
 \centering
-\includegraphics[width=85mm]{2022-05-05_14-27-43_Mevol.png}
+\includegraphics[width=85mm]{Mevol.png}
 \caption{
@@
 selected by the criterion $M>10^8~\Msun$ at $z=$ 6. 
-Highlighted are 4 massive BHs with $M>10^9~\Msun$ (with colors), 
+Highlighted are 7 massive BHs with $M>10^9~\Msun$ (with colors), 
 extrapolated back following exponential growth with constant Eddington ratio: 
-constant $\lambda$ keeping the $z=$ 6 value with dashed lines and 
-Eddington limit growth with $\lambda=1$ with dotted lines.
+constant $\lambda$ keeping the $z=$ 6 value with dotted lines and 
+Eddington limit growth with $\lambda=1$ with dashed lines.
 }
@@
 \vspace{2mm}
-\subsection{Observed v.s. Intrinsic $\lambda$ Distribution}\label{sec:ldist}
+\subsection{Observed v.s. Intrinsic ERDF}\label{sec:ldist}
 Discussion on quasar \textit{intrinsic} properties is naturally difficult, 
-in the sense that quasars are selected by \textit{observed} properties, 
+in the sense that quasars are selected by their \textit{observed} properties, 
 e.g., a cut off of detection under some magnitude floor. 
@@
 by experiments on the detectability of mock data.
-In this section, we examine the effect of flux-limited quasar survey on the observed $\lambda$ distribution, 
-taking advantage of our complete sample of model BHs in the whole luminosity range.
+In this section, we examine the effect of flux-limited quasar survey on the observed ERDF, 
+taking advantage of our complete sample of BH population in the whole luminosity range.
 
@@
 we select quasars above a bolometric luminosity cutoff at $\Lbol=10^{46}~\mathrm{erg~s^{-1}}$. 
-In Fig.~\ref{fig:lhist}, we plot the intrinsic $\lambda$ distribution for the whole sample together with 
+In Fig.~\ref{fig:lhist}, we plot the intrinsic ERDF for the whole sample together with 
 the selected sample (observed one). 
-The intrinsic $\lambda$ follows the Schechter shape with a majority of inactive quasars, 
-while the observed $\lambda$ is biased toward higher values, and the shape changes to 
-more Gaussian-like distribution. 
-The latter distribution is presented by various observational efforts 
+The intrinsic Eddington ratio follows the Schechter shape with a majority of inactive quasars, 
+while the observed Eddington ratio is biased toward higher values, and the shape changes to 
+more resembling log-normal distribution. 
+The latter distribution is presented by various observational efforts in $z\sim$ 6 quasar samples
 \citep[e.g.,][]{2010AJ....140..546W,2019ApJ...873...35S}, 
-while we predict a huge hidden population of low $\lambda$, 
-based on the best-fit model connecting the BH growth history and high-$z$ BHMF and QLF. 
+while we predict a huge hidden population with low Eddington ratio, 
+based on the best-fit growth model connecting the BH seeding and $z\sim$ 6 BHMF and QLF. 
 To demonstrate qualitatively the caveat for the detection limit on recovering the intrinsic quasar properties, 
-we also plot the $\lambda$ distribution for a sample with $\Lbol>10^{45}~\mathrm{erg~s^{-1}}$. 
+we also examine the observed ERDF by selecting quasars with $\Lbol>10^{45}~\mathrm{erg~s^{-1}}$. 
 We find that lowering the detection limit unveils more quasars with low Eddington ratio. 
@@
 %%%%%%%
-%    Fig. 6
+%    Fig. 7
 %%%%%%%
@@
 \centering
-\includegraphics[width=85mm]{l_hist.png}
+\includegraphics[width=85mm]{distf2N5_06231122_l_hist.png}
 \caption{
-Intrinsic $\lambda$ distribution (blue) and the observed ones after imposing selection effects by $\Lbol>10^{45}$ (orange) and 10$^{46}$ erg~s$^{-1}$ (green).
+Intrinsic ERDF (blue) and the observed ones after imposing selection effects by $\Lbol>L_\mathrm{lim}=10^{45}$ (orange) and 10$^{46}$ erg~s$^{-1}$ (green).
 The observed histograms are elevated by arbitrary normalizations for comparison of the distribution shapes.
-The intrinsic $\lambda$ distribution follows the dashed line which shows the analytical $\lambda$ distribution by the best-fit Schechter model. 
-While with increasing $\Lbol$ limit, the observed $\lambda$ shows 
+The intrinsic ERDF follows the dashed line which shows the analytical ERDF by the best-fit Schechter model. 
+While with the detection limit imposed, the observed ERDFs resemble log-normal shape. 
+With decreasing $L_\mathrm{lim}$, more low $\lambda$ population is unveiled.
 }

### 2022-06-27 ms.tex
ms0627

@@
+\documentclass[twocolumn, twocolappendix]{aastex63}
+
 % \documentclass[linenumbers,preprint2,tighten,trackchanges]{aastex631}
-\documentclass[nolinenumbers,preprint2,tighten]{aastex631}
+%\documentclass[nolinenumbers,preprint2,tighten]{aastex631}
 \hypersetup{filecolor=cyan,urlcolor=magenta} %citecolor=green, linkcolor=red,
@@
 \newcommand{\Msun}{\mathrm{M_\odot}}
+\newcommand{\Msunyr}{\mathrm{M_\odot~yr^{-1}}}
 \newcommand{\Mh}{M_\mathrm{h}}
@@
 
+\newcommand{\red}[1]{\textcolor{red}{ #1}}
 \newcommand{\blue}[1]{\textcolor{blue}{ #1}}
@@
 \shorttitle{BH growth toward $z=$ 6 BHMF \& QLF}
-% \shortauthors{Li et al.}
+\shortauthors{Li et al.}
 %%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\graphicspath{{./}{../figs/}}
+\graphicspath{{../figs/}}
+% \graphicspath{{./}{figures/}{figs/}}
 %% This is the end of the preamble.  Indicate the beginning of the
@@
 \title{Draft}
+
+\correspondingauthor{}
+\email{}
+
+\author[0000-0001-9840-4959]{Wenxiu Li}
+\affiliation{Department of Astronomy, School of Physics, Peking University, Beijing, 100871, China}
+\author[0000-0001-9840-4959]{Kohei Inayoshi}
+\affiliation{Kavli Institute for Astronomy and Astrophysics, Peking University, Beijing 100871, China}
+\author[0000-0001-9840-4959]{Masafusa Onoue}
+\altaffiliation{Kavli Astrophysics Fellow}
+\affiliation{Kavli Institute for Astronomy and Astrophysics, Peking University, Beijing 100871, China}
+\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (Kavli IPMU, WPI), The University of Tokyo, Chiba 277-8583, Japan}
 
@@
 %% Mark off the abstract in the ``abstract'' environment. 
-% \begin{abstract}
-
-% \end{abstract}
+\begin{abstract}
+W\\
+E\\
+N\\
+X\\
+I\\
+U\\
+L\\
+I\\
+1\\
+2\\
+3
+\end{abstract}
 
@@
 %% to include these concepts in their preprints.
-% \keywords{Classical Novae (251) --- Ultraviolet astronomy(1736) --- History of astronomy(1868) --- Interdisciplinary astronomy(804)}
+\keywords{Supermassive black holes (1663); Quasars (1319); High-redshift galaxies (734)}
 
@@
 \subsection{Seeds}\label{sec:seed}
-The QLFs at high redshifts are determined by the original BH seeding and subsequent growth. 
-Firstly we describe our model regarding the formation of BH seeds in progenitor DM halos 
-that end up in high-$z$ quasar host galaxies with halo masses of $\Mh>10^{11}~\Msun$.
-This is motivated by the estimated masses of quasar hosts which are typically up to $\sim 10^{11-13}~\Msun$, 
-probed by the $\left[\mathrm{C} \text{ II }\right]$ 158 $\micron$ fine structure line width \citep{2019ApJ...872L..29S}.
-\blue{references}
-Therefore, we sample base halos with $\Mh = 10^{11}$, $10^{12}$, and $10^{13} ~\Msun$ at $z=$ 6. 
-We then generate 10$^4$ merger trees with each base halo mass backward in time using the {\tt GALFORM} 
+The QLFs at high redshifts are determined by the BH seeding mechanism and subsequent growth. 
+We first describe our model regarding the formation of BH seeds in progenitor DM halos 
+that end up in high-$z$ quasar host galaxies with halo mass of $\Mh \gtrsim 10^{11}~\Msun$.
+The mass range of DM halos for $z\sim 6$ quasars is motivated by the halo mass measurement, 
+assuming that the rotation velocity based on [\ion{C}{2}] 158 $\micron$ line width is equal to the circular velocity of the halo.
+%is is motivated by the estimated masses of quasar hosts which are typically up to $\sim 10^{11-13}~\Msun$, 
+%probed by the [\ion{C}{2}] 158 $\micron$ fine structure line width 
+\citep{2002ApJ...578...90F,2013ApJ...773...44W,2019ApJ...872L..29S}.
+Therefore, we consider three parent halos with $\Mh = 10^{11}$, $10^{12}$, and $10^{13} ~\Msun$ at $z=$ 6
+and generate 10$^4$ merger trees for each parent halo mass backward in time using the {\tt GALFORM} 
 semi-analytic algorithm based on the extended Press-Schechter formalism 
-\citep{1974ApJ...187..425P,2000MNRAS.319..168C,2008MNRAS.383..557P}, and study the BH seeds formed therein.
+\citep{1974ApJ...187..425P,2000MNRAS.319..168C,2008MNRAS.383..557P}.
+%, and study the BH seeds formed therein.
+For each tree, we adopt a minimum DM halo mass of $M_{\rm h,min}=10^5~\Msun$, which is lower enough to capture 
+the earliest star formation episodes via H$_2$ line cooling at the high-$z$ universe \citep{1996ApJ...464..523H,1997ApJ...474....1T}.
 
-BH seeding is also affected by the baryonic streaming motion of its natal cloud, 
-where gas is streaming relative to the dark matter in the epoch of cosmic recombination at $z_\mathrm{rec}\approx$ 1100, 
-originated from its decoupling with radiation.
-The streaming velocity follows a Maxwell-Boltzmann distribution with a root-mean-square (\textit{rms}) speed of 
-$\sigma(z) = 30~{\rm km~s}^{-1} (1+z)/(1+z_{\mathrm{rec}})$ which is decaying with time \citep{2010PhRvD..82h3520T}.
-The impact of the super-sonic $\vbsm$ at high redshifts on the PopIII star (seed BH) formation 
-is explored by various studies \citep{2012MNRAS.424.1335F,2014MNRAS.439.1092T,2017Sci...357.1375H,2019MNRAS.484.3510S,2021ApJ...917...60L}.
-Their major findings are that the non-negligible $\vbsm$ injects kinetic support into pristine gas clouds, 
-which increases their effective Jeans mass and delays star formation, 
-yielding BH seeds heavier than typical PopIII stars. 
-The volume fraction of the universe with streaming velocities higher than the \textit{rms} value
-is estimated as $\simeq 0.4$. We then set $\vbsm=$ 0 and the \textit{rms} velocity as two representative cases, 
-accounting for roughly $f_{\vbsm} = 60\%$ and $40\%$ of the seeding environments, respectively.
+We consider seed BH formation in the main progenitors of quasar host galaxies, following a semi-analytical model established by \citet{2021ApJ...917...60L}.
+In the highly-biased, overdense regions of the universe, those progenitor halos are likely irradiated by intense H$_2$-photodissociating radiation 
+from nearby star-forming galaxies and heat the interior gas by successive mergers. 
+The two effects counteracting H$_2$ formation and cooling prevent gas collapse and delay prior star formation \citep[e.g.,][]{2014MNRAS.445..107V,2019Natur.566...85W}.
+Under such peculiar circumstances, massive clouds collapse to the halo centers at high accretion rates and leave massive stars (presumably seed BHs) behind.
+Our model takes into account various key physical processes on star formation such as halo merger heating, radiative cooling, and
+(photo-)chemical reaction networks.
+%, and gravitational instability of the central gaseous cores.
+The time evolution of the gas dynamics and thermal states is calculated in a self-consistent way with the halo assembly history.
+%the gas dynamical and thermal evolution is regulated by the parent halo growth histories, and the environmental streaming velocities.
+%
+%Next we introduce our seeding model where the gas dynamical and thermal evolution is regulated by the parent halo growth histories, 
+%and the environmental streaming velocities.
+%In \citet{2021ApJ...917...60L}, we propose an semi-analytical model which 
+%traces the gas evolution along its parent halo growth and yields the seed BH mass distribution. 
+% The background UV radiation $$ is calculated by semi-analytical arguments of men
+%The merger heating and enhancement of background Lyman-Werner radiation intensity $\jlw$ 
+%due to halo clustering is taken into account to shape the gas thermal evolution.
 
-Next we introduce our seeding model where the gas dynamical and thermal evolution is regulated by the parent halo growth histories, 
-and the environmental streaming velocities.
-In \citet{2021ApJ...917...60L}, we propose an semi-analytical model which 
-traces the gas evolution along its parent halo growth and yields the seed BH mass distribution. 
-% The background UV radiation $$ is calculated by semi-analytical arguments of men
-The merger heating and enhancement of background Lyman-Werner radiation intensity $\jlw$ 
-due to halo clustering is taken into account to shape the gas thermal evolution. 
-Besides, the baryonic streaming velocity $\vbsm$ together with the turbulent velocity $v_\mathrm{tur}$ 
-through halo virialization is taken into account
-\footnote{
-We model the effective sound speed of gas as $c_{\rm eff} = \sqrt{ c_{\rm s}^2+v_{\rm tur}^2/3+\left(\alpha_0 \vbsm \right)^2}$,
-where the coefficient $\alpha_0 = 1$ is motivated by previous studies 
-\citep{2017Sci...357.1375H,2019MNRAS.484.3510S}.
-}.
-Following this model we produce 10$^4$ BH seeds with their formation time and masses, 
-in each merger tree with a given $\vbsm$, 
-the abundance of seeds is normalized with the base halo number density from the Sheth-Tormen \citep{2001MNRAS.323....1S} halo mass function:
-\begin{align*}
-  n_{\Mh}= \int_{\Mh}^{10\Mh}  \frac{\D n_{\mathrm{ST}}} {\D \Mh} \D \Mh, 
-\end{align*}
-weighted by the environmental $\vbsm$ fraction $f_{\vbsm}$. 
-We then construct the seed BH mass distribution shown in Fig.~\ref{fig:seedmf}.
+In addition, we consider baryonic streaming motion relative to the DM produced in the epoch of cosmic recombination at $z_{\rm rec} \simeq 1100$.
+%originated from its decoupling with radiation.
+This effect also delays gas collapse and star formation in protogalaxies through injection of kinetic energy into gas
+\citep[e.g.,][]{2012MNRAS.424.1335F, 2014MNRAS.439.1092T, 2017Sci...357.1375H,2019MNRAS.484.3510S,2021ApJ...917...60L}.
+The amplitude of the streaming velocity is set to $\vbsm = 0$ and $\vbsm=1~\sigma_{\rm bsm}$, where $\sigma_{\rm bsm}=30~{\rm km~s}^{-1} (1+z)/(1+z_{\rm rec})$
+is the root-mean-square speed at a redshift of $z$ \citep{2010PhRvD..82h3520T}.
+We calculate the effective sound speed of gas as $c_{\rm eff} = \{c_{\rm s}^2+v_{\rm tur}^2/3+\left(\alpha_0 \vbsm \right)^2 \}^{1/2}$ at the center of each progenitor halo,
+where $c_{\rm s}$ is the thermal sound speed, $v_{\rm tur}$ is the turbulent velocity of gas (i.e., the specific kinetic energy accumulated through halo mergers), and
+the coefficient is set to $\alpha_0=1$\footnote{The value of $\alpha_0=1.0$ is motivated by cosmological simulations of massive primordial stars
+under fast streaming velocities \citep{2017Sci...357.1375H,2019MNRAS.484.3510S}.
+Note that our previous study in \citet{2021ApJ...917...60L} adopted $\alpha_0=4.7$ \citep{2018ApJ...855...17H}.}.
+%
+%Besides, the baryonic streaming velocity $\vbsm$ together with the turbulent velocity $v_\mathrm{tur}$ 
+%through halo virialization is taken into account
+%\footnote{
+%We model the effective sound speed of gas as $c_{\rm eff} = \sqrt{ c_{\rm s}^2+v_{\rm tur}^2/3+\left(\alpha_0 \vbsm \right)^2}$,
+%where the coefficient $\alpha_0 = 1$ is motivated by previous studies 
+%\citep{2017Sci...357.1375H,2019MNRAS.484.3510S}.
+%}.
+When the gas core becomes gravitationally unstable, the evolution of the gas density profile is well described by 
+the Penston-Larson self-similar solution \citep{1969MNRAS.144..425P,1969MNRAS.145..271L}. 
+The mass accretion rate from the envelope can be written as $\dot{M}=c_{\rm eff}^3/G$,
+where $G$ is the gravitational constant.
+
+%%%%%%%%%
+%	REVISE.   %
+%%%%%%%%%
+\red{KI: we need to explain how we calculate the final stellar mass from the accretion rate. pls add one new paragraph here. 
+also add an argument about translation from stellar mass to BH remnant mass.}
+
+Zooming in to the protostellar vicinity, an accretion disk forms due to the angular momentum of the inflowing material from large scale. 
+The episodic accretion through the clumpy disk decreases the time-averaged accretion rate onto the protostar by $\Mdot_{\star}=\eta \Mdot$, 
+where we take $\eta=0.3$ as the conversion efficiency from global accretion to that through the disk \citep[][Toyouchi 2022]{2016MNRAS.459.1137S}. 
+\blue{
+  (Toyouchi+ find 0.4 actually.)
+}
+We then exploit the accretion rate to estimate the protostellar mass and that of the subsequent seed BH formed.
+
+The growth pattern of an accreting protostar differs in the effect of radiative feedback,
+with the accretion rate $\Mdot_\star$ in different regimes compared with a critical value $\dot{M}_{\mathrm{crit}}=0.04~\Msunyr$ 
+\citep{2001ApJ...561L..55O,2013ApJ...778..178H,2013A&A...558A..59S,2015MNRAS.452..755S,2018MNRAS.474.2757H}.
+With average accretion rates exceeding $\Mdot_\mathrm{crit}$, the stellar envelope inflates, 
+with its surface temperature as low as $T_\mathrm{eff} \simeq 5000$ K, 
+resulting in trivial UV radiative feedback that hardly affect the accretion flow. 
+The stellar mass is then built up to $\sim 10^5~\Msun$ and limited by the internal GR instability 
+\citep{2016PhRvD..94b1501S,2017ApJ...842L...6W,2019PASA...36...27W}, which is fitted as 
+\begin{equation*}
+ M_{\star, \mathrm{GR}} \simeq\left[0.83 \log \left(\frac{\dot{M}_{\star}}{\Msunyr}\right)+2.48\right] \times 10^{5} ~\Msun,
+\end{equation*}
+in the range of $\dot{M}_\star\gtrsim 0.1~\Msunyr$.
+
+On the other hand, with accretion rates lower than $\Mdot_\mathrm{crit}$, 
+protostars can contract with the effective temperature rapidly increasing to $\sim 10^5$ K, 
+hence the strong UV photons photoevaporate the gaseous disk and hinder the mass accretion 
+\citep{2008ApJ...681..771M,2011Sci...334.1250H}. 
+In this case, the final stellar mass is capped by the balance of the mass loss rate via disk photoevaporation $\dot{M}_{\mathrm{pe}}$
+and the accretion rate $\dot{M}_{\star}$, and the former is expressed as 
+% \begin{equation*}
+  % \dot{M}_{\mathrm{pe}} \simeq 2.1 \times 10^{-2} \Msunyr \left(\frac{\Phi_{\mathrm{ion}}}{10^{52} \mathrm{~s}^{-1}}\right)^{1 / 2}\left(\frac{R_{\rm{disk}}}{0.1 \mathrm{pc}}\right)^{1/2}.
+% \end{equation*}
+$\dot{M}_{\mathrm{pe}} \simeq 2.1 \times 10^{-2} \Msunyr \left( \Phi_{\mathrm{ion}}/10^{52} \mathrm{~s}^{-1}\right)^{1 / 2}\left(R_{\rm{disk}}/0.1 \mathrm{pc}\right)^{1/2}$ 
+\citep{2013ApJ...773..155T}.
+Here we adopt the emissivity of UV photons $\Phi_{\mathrm{ion}} \simeq 1.6 \times 10^{52} \mathrm{~s}^{-1}\left(M_{\star} / 10^{4} \Msun \right)$ following \citet{2012ApJ...750...66J}, 
+and the disk size is estimated as the stellar gravitational influence radius for 2$\times 10^4$ K ionized gas 
+$R_{\mathrm{disk}} \simeq  G M_{\star}/c_{\mathrm{s}, \mathrm{ion}}^{2} \simeq 0.17 \mathrm{pc}\left( M_{\star}/ 10^{4} \Msun \right)$.
+The final stellar mass regulated by radiative feedback is thus 
+\begin{equation*}
+M_{\star, \mathrm{fb}} \simeq 2.9 \times 10^{3} \Msun\left(\frac{\dot{M}_{\star}}{0.01 M_{\odot} \mathrm{yr}^{-1}}\right), 
+\end{equation*}
+for $\Mdot_\star\lesssim \Mdot_\mathrm{crit}$.
+
+With the intermediate accretion rates between $\Mdot_\mathrm{crit}$ and $0.1~\Msunyr$, 
+we perform logarithmic interpolation in the $\Mdot_\star - M_\star$ plane to smoothly connect 
+$M_{\star, \mathrm{fb}}$ and $M_{\star, \mathrm{GR}}$ at the boundaries.
+In the death of these metal poor stars, most mass are expected to reserve to the collapse into BHs 
+\citep{2003ApJ...591..288H,2010ApJ...714.1217B,2015MNRAS.451.4086S}.
+Therefore, we take the seed BH masses as those of their progenitor stars.
+
+Based on the probability distribution function of the BH seed mass $\D P/ \D \log M_{\bullet, i}$, we construct the mass function of those seeds formed in one parent halo
+with a mass of $\Mh$ where gas has a coherent streaming velocity of $\vbsm$ as a function of time (and redshift).
+The absolute abundance of those seed BHs is calculated with the number density of the parent halo in a comoving volume at $z=6$ 
+from the Sheth-Tormen mass function \citep{2001MNRAS.323....1S},
+%
+\begin{align}
+  n_{\Mh}= \int_{\Mh}^{10\Mh}  \frac{\D n_{\mathrm{ST}}} {\D \Mh'} \D \Mh', 
+\end{align}
+%
+where we adopt $\Mh = 10^{11}$, $10^{12}$, and $10^{13}~\Msun$, 
+% (\red{KI: explicitly show those numbers?})
+with number densities $n_{\Mh} = 9.87\times 10^{-4}$, $6.15\times 10^{-6}$, 
+and $8.92\times 10^{-10}~ \text{Mpc}^{-3}$, respectively.
+Combining the PDF and number normalization, we obtain the seed BH mass function as
+%
+\begin{align}
+\Phi_\mathrm{M}^{\rm seed} \equiv \sum_{\Mh, \vbsm} n_{\Mh} f_{\vbsm} 
+\cdot \frac{\D P}{\D \log M_{\bullet, i}}\Big| _{\Mh, \vbsm},
+\end{align}
+%
+where $f_{\vbsm}$ is the volume fraction of the universe with a streaming velocity.
+The value is calculated as $f_{\vbsm} = 0.6$ and $0.4$ for $\vbsm = 0$ and $\vbsm=1~\sigma_{\rm bsm}$, respectively.
+
+%BH seeding is also affected by the baryonic streaming motion of its natal cloud, 
+%where gas is streaming relative to the dark matter in the epoch of cosmic recombination at $z_\mathrm{rec}\approx$ 1100, 
+%originated from its decoupling with radiation.
+%The streaming velocity follows a Maxwell-Boltzmann distribution with a root-mean-square (\textit{rms}) speed of 
+%$\sigma(z) = 30~{\rm km~s}^{-1} (1+z)/(1+z_{\mathrm{rec}})$ which is decaying with time \citep{2010PhRvD..82h3520T}.
+%The impact of the super-sonic $\vbsm$ at high redshifts on the PopIII star (seed BH) formation 
+%is explored by various studies \citep{2012MNRAS.424.1335F,2014MNRAS.439.1092T,2017Sci...357.1375H,2019MNRAS.484.3510S,2021ApJ...917...60L}.
+%Their major findings are that the non-negligible $\vbsm$ injects kinetic support into pristine gas clouds, 
+%which increases their effective Jeans mass and delays star formation, 
+%yielding BH seeds heavier than typical PopIII stars. 
+%The volume fraction of the universe with streaming velocities higher than the \textit{rms} value
+%is estimated as $\simeq 0.4$. We then set $\vbsm=$ 0 and the \textit{rms} velocity as two representative cases, 
+%accounting for roughly $f_{\vbsm} = 60\%$ and $40\%$ of the seeding environments, respectively.
 
@@
 \label{fig:scheme}
+\vspace{5mm}
 \end{figure*}
@@
 \vspace{2mm}
-\subsection{BH growth \& mass Function}\label{sec:MF}
-% The BH accretion at high redshifts is probed only by snapshots, in their most luminous quasar phase. We have constraints on simulations and observations of lower redshift counterparts.
-With seeds planted, we grow the BHs with a semi-analytical accretion rate model 
-and study the BH mass distribution at redshift 6. 
+\subsection{BH mass growth}
+% The BH accretion at high redshifts is probed only by snapshots, in their most luminous quasar phase. 
+% We have constraints on simulations and observations of lower redshift counterparts.
+With BH seeds planted, we grow the BHs with a semi-analytical accretion rate model and study the evolution of the BH mass distribution until $z=6$. 
 \blue{(references + discussion)}
-The growth model is captured by a limited number of free parameters, 
+The growth model is characterized by a minimal number of free parameters, 
 % the quasar accretion is episodic with Eddington ratio variations,
-describing the BH mass growth rate $\Mdot$ by: 
+describing the BH mass growth rate $\Mdot$ by
 %%%%%%%
@@
 %   \label{eq:mdot_1}
-%   \Mdot = \frac{\lambda f\left(M\right) M}{\tEdd} ,
+%   \Mdot_\bullet = \frac{\lambda f(M_\bullet) M_\bullet}{\tEdd} ,
 % \end{equation*}
@@
   \label{eq:mdot}
-  \Mdot = \lambda f\left(M\right) \Mdot_\mathrm{Edd} ,
+  \Mdot_\bullet = \lambda f(M_\bullet) \Mdot_\mathrm{Edd} ,
 \end{equation}
 % where $\tEdd = \eta_0  M c^2/L_{\mathrm{Edd}} \approx 45$ Myr,
-where $\lambda = L/L_\mathrm{Edd}$ is the Eddington ratio,
-and $\Mdot_\mathrm{Edd} = L_{\mathrm{Edd}}/\eta_0 c^2$ is the Eddington accretion rate with the radiative efficiency $\eta_0$.
-Note here we adopt the radiative efficiency $\eta_0 \approx 0.1 $,
-according to the thin accretion disk model \citep{1973A&A....24..337S}, 
-which is also consistent with the Soltan's argument \citep{1982MNRAS.200..115S,2002MNRAS.335..965Y}.
-Then $\tEdd =  M/\Mdot_{\mathrm{Edd}} \approx 45$ Myr is the Salpeter $e$-folding timescale \citep{1964ApJ...140..796S}.
+where $\lambda \equiv L/L_\mathrm{Edd}$ is the Eddington ratio,
+and $\Mdot_\mathrm{Edd} \equiv L_{\mathrm{Edd}}/\eta_0 c^2$ is the Eddington accretion rate with a 10\% radiative efficiency of $\eta_0=0.1$ \citep{1973A&A....24..337S},
+%Note here we adopt the radiative efficiency $\eta_0 \approx 0.1 $,
+%according to the thin accretion disk model \citep{1973A&A....24..337S}, 
+which is consistent with the value obtained from the Soltan's argument \citep{1982MNRAS.200..115S,2002MNRAS.335..965Y}.
 % The high mass BH should be strangulated by as it grows, 
-We introduce the mass dependency 
-$f(M) = 0.5 \left[1+\left(M/10^8~\Msun\right)^\delta\right] ^ {-1}$, 
-to suppress the high mass BH growth with a positive $\delta$. 
-\blue{(references)}
-With decreasing $\delta$, 
-the model is reduced to an exponential growth independent of BH mass.
+We define the mass dependent function of $f(M_\bullet)$ as 
+%
+\begin{equation}
+f(M_\bullet) = \frac{2}{1+\left(M_\bullet /M_{\bullet,c} \right)^\delta}, 
+\end{equation}
+%
+where we adopt $M_{\bullet,c}=10^8~\Msun$.
+With a positive value of $\delta$, the BH growth at the high mass end is suppressed. \blue{(references, Ueda+14?s)}.
+In the limit of $\delta \ll 1$, where $f(M_\bullet) \simeq 1$ is approximated independent of $M_{\bullet,c}$, the model reproduces an exponential growth with an $e$-folding timescale of
+$\tEdd =  M_\bullet/\Mdot_{\mathrm{Edd}} \approx 45$ Myr.
+%h independent of BH mass.
 % In \S~\ref{sec:fitting}, $\delta$ turns out to be close to 0, indicating an exponential grow manner independent of BH mass.
+%Then $\tEdd =  M/\Mdot_{\mathrm{Edd}} \approx 45$ Myr is the Salpeter $e$-folding timescale \citep{1964ApJ...140..796S}.
 
-The quasar activity is episodic in nature, with bursts of accretion triggered by gas inflows 
+The quasar activity is episodic in nature, with accretion bursts triggered by gas inflows to the galactic nuclei
 % \citep[e.g., mergers or disk instabilities, see][]{2005Natur.433..604D,2005ApJ...630..705H}, 
@@
 and the accretion rate declines with self-regulating feedbacks \citep[e.g.,][]{2008ApJ...686..815Y,2011ApJ...737...26N} or 
-self-similar disk evolution \citep{1991MNRAS.248..754P,2005ApJ...634..901Y,2007MNRAS.377L..25K}.
-This ``flickering'' pattern of individual quasar luminosity evolution can be directly translated into the diversity in the Eddington ratios 
-of a quasar sample, where the Eddington ratio distribution function (ERDF) $\D P/ \D\ln\lambda$ shares the same Schechter function shape 
-with the differential time at different $\lambda$ \citep{2006ApJ...639..700H,2009ApJ...698.1550H}.
-Observations also propose that the intrinsic ERDF in lower-$z$ quasars hosted by star forming galaxies follows a Schechter shape, 
-\citep{2015MNRAS.447.2085S,2016ApJ...826...12J,2018MNRAS.474.1225A}, 
-therefore we take 2 free parameters $\lambda_0$ and $\alpha$ to characterize the ERDF:
+self-similar disk evolution \citep{1991MNRAS.248..754P,2005ApJ...634..901Y,2007MNRAS.377L..25K}. \red{KI: what's this?}
+This ``flickering'' pattern of individual quasar luminosity evolution can be directly translated into the diversity in the Eddington ratios of a quasar sample, 
+\red{where the Eddington ratio distribution function (ERDF) $\D P/ \D\ln\lambda$ shares the same Schechter function shape 
+with the differential time at different $\lambda$ \citep{2006ApJ...639..700H,2009ApJ...698.1550H}.}
+\red{KI: don't follow this logic...}
+For type-I AGN populations at low redshifts, the ERDF is characterized with a Schechter function
+%Observations also propose that the intrinsic ERDF in lower-$z$ quasars hosted by star forming galaxies follows a Schechter shape, 
+\citep{2015MNRAS.447.2085S,2016ApJ...826...12J,2018MNRAS.474.1225A}.
+Motivated by those facts, we give the ERDF by a Schechter function with two free parameters $\lambda_0$ and $\alpha$ as
 %%%%%%%
@@
   \label{eq:Pl}
-  \frac{\D P}{ d\ln \lambda} \propto
-  \left(\frac{\lambda} {\lambda_0} \right)^\alpha \exp{\left(-\frac{\lambda}{\lambda_0}\right)},
+  \frac{\D P}{ \D \ln \lambda} \propto
+  \left(\frac{\lambda} {\lambda_0} \right)^\alpha \exp{\left(-\frac{\lambda}{\lambda_0}\right)}.
 \end{equation}
-normalized by the total probability above $\lambda_\mathrm{min}$ = 0.01.
-The minimum Eddington ratio $\lambda_\mathrm{min}$ is motivated by the behavior of quasar luminosity evolution 
-that decreases mildly toward $\lambda\sim 0.1-0.01$ with $\lesssim$ 100 Myr after activation \citep{2011ApJ...737...26N}, 
-also suggested by a turnover at the lowest $\lambda\lesssim 0.01-0.001$ on the observational side \citep{2018MNRAS.474.1225A}.
+The normalization is set so that the integrant of this function over $\lambda_\mathrm{min}(=0.01) \leq \lambda < \infty$ is unity.
+%normalized by the total probability above $\lambda_\mathrm{min}$ = 0.01.
+The minimum Eddington ratio $\lambda_\mathrm{min}$ is adopted from the simulated evolution of quasar luminosities 
+that decrease mildly toward $\lambda \sim 0.1-0.01$ with $\lesssim$ 100 Myr after the peak activity \citep{2011ApJ...737...26N}.
+Moreover, a turnover at the lowest value $\lambda\lesssim 0.01-0.001$ in the ERDF is suggested by observations \citep{2018MNRAS.474.1225A}.
 
-To characterize the aforementioned ERDF in a BH population at any time snapshot, 
-together with the episodic accretion pattern of individual BHs, 
-we introduce a time duration $\tlife$, 
-during which a single value of $\lambda$ following the ERDF of Eq.~(\ref{eq:Pl}) is assigned to a growing BH.
-In this way we model a gear change taking place every $\tlife$, 
-which avoids the unreality of a long-lasting super-Eddington accretion from seeding down to $z=$ 6. 
-Note that the $\tlife$ is indispensable as a methodology in our modeling, 
+To characterize the ERDF for a BH population at any time snapshot together with the episodic accretion pattern of individual BHs, 
+we introduce a time duration of $\tlife$, during which a single value of $\lambda$ that follows the ERDF of Eq.~(\ref{eq:Pl}) is assigned to an accreting BH.
+In this way, we give a different growth speed of a BH in every period with a duration of $\tlife$ until $z=6$ (the corresponding cosmic age is $t_{\rm H}\simeq 800$ Myr).
+This treatment enables us to capture the nature of accretion bursts and avoid an unrealistically long-lasting rapid growth phase of a BH.
+\red{We note that the value of $\tlife$ is indispensable as a methodology in our modeling, 
 albeit its direct comparison with observational luminous quasar lifetime is difficult, 
 these timescales are correlated in realizing the SMBH growth. 
-We leave a more detailed disucssion to \S~\ref{sec:discussion}.
+We leave a more detailed discussion to \S~\ref{sec:discussion}.}
+To be done later...
 
-Lastly, the seeding fraction $\fseed$ denotes the portion of halos where the central BH are initially seeded \citep{2009ApJ...696.1798T}.
-Discussing on constraints from the origin of $\fseed$ is beyond our scope in this work. 
-Instead we take different values $\fseed$ = 1, 0.1, and 0.01, 
-and explore the dependency of the best-fit parameters on it.
+Thus far, we assume that {\it all} the parent halos form seed BHs during their assembly and end up in quasar host galaxies by $z\simeq 6$.
+To relax this stringent assumption, we introduce the seeding fraction of $\fseed (\leq 1)$.
+As discussed in \citet{2009ApJ...696.1798T}, a small value of $\fseed <1$ is required to avoid overproduction of SMBHs at $z\sim 6$,
+depending on BH seeding and growth mechanisms in semi-analytical models.
+% that denotes the portion of DM halos where seed BHs are seeded \citep{2009ApJ...696.1798T}.
+Since the value has been poorly constrained both by theoretical and observational studies, we treat it as a free parameter.
+We take three different values of $\fseed = 1$, $0.1$, and $0.01$ and explore the dependence on the best-fit BHMF and QLF.
+Note that the seed mass function shown in Fig.~\ref{fig:seedmf} is given with $\fseed = 1$.
 
+\subsection{BH mass function}\label{sec:MF}
+
+We describe how to calculate the time evolution of the BH mass function, combining the semi-analytical growth model 
+and the ERDF (see Eqs.~\ref{eq:mdot} and \ref{eq:Pl}).
+For a given mass distribution function $\D P/\D  M_{\bullet, i}$ at $t=t_i$, we give the BHMF at $t=t_i+\Delta t$ as
+%%%%%%%
+%    Eq. 5
+%%%%%%%
+\begin{equation}
+  \label{eq:dpdm}
+  \frac{\D P}{\D M_\bullet} = \int
+   \frac{\D P}{\D \ln \lambda}\Big|_{\lambda_\ast} \cdot
+   \frac{\D \ln \lambda_\ast}{\D  M_\bullet}\Big|_{\Delta t, M_{\bullet,i}} \cdot
+   %_{M, M_\mathrm{i},\Delta t, \delta}
+  \frac{\D P}{\D M_{\bullet, i}}~\D M_{\bullet, i},
+\end{equation}
+%
+where $\lambda_\ast$ is the Eddington ratio required for a BH with $M_{\bullet,i}$ to grow up to $M_{\bullet}$ within $\Delta t$
+and is calculated analytically by
+%%%%%%%
+%    Eq. 4
+%%%%%%%
+\begin{equation}
+  \label{eq:mi2m}
+\frac{\lambda_\ast \Delta t}{\tEdd}=
+  \ln \left(\frac{M_\bullet} {M_{\bullet,i}}\right) + \frac{1}{\delta} 
+  \left[ \left(\frac{M_\bullet}{M_{\bullet,c}}\right)^\delta - \left(\frac{M_{\bullet, i}}{M_{\bullet,c}}\right)^\delta \right],
+\end{equation}
+%
+and the derivative of ($\D \ln \lambda_\ast / \D  M_\bullet )|_{\Delta t, M_{\bullet,i}}$ is given by Eq.~(\ref{eq:mi2m}).
+After the seed formation terminates (i.e., after the total number of BHs is fixed), we perform this integration in every timestep 
+by setting to $\Delta t = t_{\rm life}$ until $z=6$.
+
+\if0
 Next, we explain our method to calculate the time evolution of BHMF, 
@@
 \end{align}
-where ${\D P}/{\D \ln\lambda}$ is given by a set of parameters $\lambda_0$ and $\alpha$ in Eq.~(\ref{eq:Pl}), 
-at the $\lambda$ value $\lambda\left(M, M_\mathrm{i},\Delta t, \delta\right)$ inferred from Eq.~(\ref{eq:mi2m}).
-For the evolution of the BH mass distribution, we set $\Delta t=\tlife$.
+
+\fi
+
+%where ${\D P}/{\D \ln\lambda}$ is given by a set of parameters $\lambda_0$ and $\alpha$ in Eq.~(\ref{eq:Pl}), 
+%at the $\lambda$ value $\lambda\left(M, M_\mathrm{i},\Delta t, \delta\right)$ inferred from Eq.~(\ref{eq:mi2m}).
+%For the evolution of the BH mass distribution, we set $\Delta t=\tlife$.
 On the other hand, for the growth of an individual seed, 
@@
 
+\if0
+
 \vspace{5mm}
@@
 
+\fi
+
 \newpage

### 2022-06-30 ms.tex
ms0629

@@
 
-\newcommand{\Msun}{\mathrm{M_\odot}}
-\newcommand{\Msunyr}{\mathrm{M_\odot~yr^{-1}}}
+\newcommand{\Msun}{M_\odot}
+\newcommand{\Msunyr}{M_\odot~{\rm yr}^{-1}}
 \newcommand{\Mh}{M_\mathrm{h}}
@@
 \newcommand{\Mdot}{\dot{M}}
-\newcommand{\tlife}{t_\mathrm{life}}
+% \newcommand{\tlife}{t_\mathrm{life}}
+\newcommand{\tlife}{\tau}
 \newcommand{\fseed}{f_\mathrm{seed}}
@@
 \newcommand{\blue}[1]{\textcolor{blue}{ #1}}
+
+\defcitealias{2010AJ....140..546W}{W10}
+\defcitealias{2018ApJ...869..150M}{M18}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\graphicspath{{../figs/}}
+\graphicspath{{./}{../figs/}}
 % \graphicspath{{./}{figures/}{figs/}}
@@
 
-%%%%%%%%%
-%	REVISE.   %
-%%%%%%%%%
-\red{KI: we need to explain how we calculate the final stellar mass from the accretion rate. pls add one new paragraph here. 
-also add an argument about translation from stellar mass to BH remnant mass.}
-
-Zooming in to the protostellar vicinity, an accretion disk forms due to the angular momentum of the inflowing material from large scale. 
-The episodic accretion through the clumpy disk decreases the time-averaged accretion rate onto the protostar by $\Mdot_{\star}=\eta \Mdot$, 
-where we take $\eta=0.3$ as the conversion efficiency from global accretion to that through the disk \citep[][Toyouchi 2022]{2016MNRAS.459.1137S}. 
-\blue{
-  (Toyouchi+ find 0.4 actually.)
-}
-We then exploit the accretion rate to estimate the protostellar mass and that of the subsequent seed BH formed.
-
-The growth pattern of an accreting protostar differs in the effect of radiative feedback,
-with the accretion rate $\Mdot_\star$ in different regimes compared with a critical value $\dot{M}_{\mathrm{crit}}=0.04~\Msunyr$ 
+At the vicinity of an accreting protostar, an accretion disk forms due to angular momentum of the inflowing material from large scales. 
+The episodic nature of disk accretion decreases the time-averaged accretion rate onto the protostar as $\Mdot_{\star}=\eta \Mdot$, 
+where we adopt $\eta=0.3$ as the conversion efficiency \citep[][Toyouchi 2022]{2016MNRAS.459.1137S}. 
+%\blue{
+%  (Toyouchi+ find 0.4 actually.)
+%}
+%Thus, we estimate the accretion rate to estimate the protostellar mass and that of the subsequent seed BH formed. 
+The stellar radius evolution of an accreting protostar and the radiative feedback strength depend sensitively on whether
+the accretion rate becomes higher than a critical value of $\dot{M}_{\mathrm{crit}}=0.04~\Msunyr$ 
 \citep{2001ApJ...561L..55O,2013ApJ...778..178H,2013A&A...558A..59S,2015MNRAS.452..755S,2018MNRAS.474.2757H}.
-With average accretion rates exceeding $\Mdot_\mathrm{crit}$, the stellar envelope inflates, 
-with its surface temperature as low as $T_\mathrm{eff} \simeq 5000$ K, 
-resulting in trivial UV radiative feedback that hardly affect the accretion flow. 
-The stellar mass is then built up to $\sim 10^5~\Msun$ and limited by the internal GR instability 
-\citep{2016PhRvD..94b1501S,2017ApJ...842L...6W,2019PASA...36...27W}, which is fitted as 
-\begin{equation*}
- M_{\star, \mathrm{GR}} \simeq\left[0.83 \log \left(\frac{\dot{M}_{\star}}{\Msunyr}\right)+2.48\right] \times 10^{5} ~\Msun,
-\end{equation*}
-in the range of $\dot{M}_\star\gtrsim 0.1~\Msunyr$.
-
-On the other hand, with accretion rates lower than $\Mdot_\mathrm{crit}$, 
-protostars can contract with the effective temperature rapidly increasing to $\sim 10^5$ K, 
-hence the strong UV photons photoevaporate the gaseous disk and hinder the mass accretion 
+For $\dot{M}_\ast > \Mdot_\mathrm{crit}$, the stellar envelope inflates owing to rapid entropy injection through accreting matter,
+keeping its surface temperature as low as $T_\mathrm{eff} \simeq 5000$ K. 
+Since stellar UV radiation is hardly emitted from the cold surface, the accretion flow efficiently feeds the central star without being 
+impeded by radiative feedback.
+As a result, the stellar mass reaches $\sim 10^5~\Msun$ but is limited by the general-relativistic instability to
+%
+\begin{equation}
+ M_{\star, \mathrm{GR}} \simeq\left[0.83~\log \left(\frac{\dot{M}_{\star}}{\Msunyr}\right)+2.48\right] \times 10^{5} ~\Msun,
+\end{equation}
+%
+in the range of $\dot{M}_\star\gtrsim 0.1~\Msunyr$ \citep{2016PhRvD..94b1501S,2017ApJ...842L...6W,2019PASA...36...27W}.
+On the other hand, for $\dot{M}_\ast \leq \Mdot_\mathrm{crit}$, protostars can contract by loosing its thermal energy via radiative diffusion
+and increases its surface temperature to $T_\mathrm{eff} \sim 10^5$ K.
+Hence, intense stellar UV radiation heats the disk surface and launches mass outflows, preventing mass supply from the disk to the star
 \citep{2008ApJ...681..771M,2011Sci...334.1250H}. 
-In this case, the final stellar mass is capped by the balance of the mass loss rate via disk photoevaporation $\dot{M}_{\mathrm{pe}}$
-and the accretion rate $\dot{M}_{\star}$, and the former is expressed as 
+In this case, the stellar mass is determined by the balance between mass accretion and mass loss via photoevaporation \citep{2013ApJ...773..155T},
+and can be approximated as (see more details in \citealt{2021ApJ...917...60L})
+%the final stellar mass is capped by the balance of the mass loss rate via disk photoevaporation $\dot{M}_{\mathrm{pe}}$
+%and the accretion rate $\dot{M}_{\star}$, and the former is expressed as 
 % \begin{equation*}
@@
 % \end{equation*}
-$\dot{M}_{\mathrm{pe}} \simeq 2.1 \times 10^{-2} \Msunyr \left( \Phi_{\mathrm{ion}}/10^{52} \mathrm{~s}^{-1}\right)^{1 / 2}\left(R_{\rm{disk}}/0.1 \mathrm{pc}\right)^{1/2}$ 
-\citep{2013ApJ...773..155T}.
-Here we adopt the emissivity of UV photons $\Phi_{\mathrm{ion}} \simeq 1.6 \times 10^{52} \mathrm{~s}^{-1}\left(M_{\star} / 10^{4} \Msun \right)$ following \citet{2012ApJ...750...66J}, 
-and the disk size is estimated as the stellar gravitational influence radius for 2$\times 10^4$ K ionized gas 
-$R_{\mathrm{disk}} \simeq  G M_{\star}/c_{\mathrm{s}, \mathrm{ion}}^{2} \simeq 0.17 \mathrm{pc}\left( M_{\star}/ 10^{4} \Msun \right)$.
-The final stellar mass regulated by radiative feedback is thus 
-\begin{equation*}
-M_{\star, \mathrm{fb}} \simeq 2.9 \times 10^{3} \Msun\left(\frac{\dot{M}_{\star}}{0.01 M_{\odot} \mathrm{yr}^{-1}}\right), 
-\end{equation*}
-for $\Mdot_\star\lesssim \Mdot_\mathrm{crit}$.
-
-With the intermediate accretion rates between $\Mdot_\mathrm{crit}$ and $0.1~\Msunyr$, 
+%$\dot{M}_{\mathrm{pe}} \simeq 2.1 \times 10^{-2} \Msunyr \left( \Phi_{\mathrm{ion}}/10^{52} \mathrm{~s}^{-1}\right)^{1 / 2}\left(R_{\rm{disk}}/0.1 \mathrm{pc}\right)^{1/2}$ 
+%\citep{2013ApJ...773..155T}.
+%Here we adopt the emissivity of UV photons $\Phi_{\mathrm{ion}} \simeq 1.6 \times 10^{52} \mathrm{~s}^{-1}\left(M_{\star} / 10^{4} \Msun \right)$ following \citet{2012ApJ...750...66J}, 
+%and the disk size is estimated as the stellar gravitational influence radius for 2$\times 10^4$ K ionized gas 
+%$R_{\mathrm{disk}} \simeq  G M_{\star}/c_{\mathrm{s}, \mathrm{ion}}^{2} \simeq 0.17 \mathrm{pc}\left( M_{\star}/ 10^{4} \Msun \right)$.
+%The final stellar mass regulated by radiative feedback is thus 
+%
+\begin{equation}
+M_{\star, \mathrm{fb}} \simeq 2.9 \times 10^{3} \Msun\left(\frac{\dot{M}_{\star}}{0.01 M_{\odot} \mathrm{yr}^{-1}}\right).
+\end{equation}
+%
+%for $\Mdot_\star\lesssim \Mdot_\mathrm{crit}$. 
+For an intermediate accretion rate between $\Mdot_\mathrm{crit}$ and $0.1~\Msunyr$, 
 we perform logarithmic interpolation in the $\Mdot_\star - M_\star$ plane to smoothly connect 
 $M_{\star, \mathrm{fb}}$ and $M_{\star, \mathrm{GR}}$ at the boundaries.
-In the death of these metal poor stars, most mass are expected to reserve to the collapse into BHs 
+At the end of the stellar lifetime, those massive primordial stars result in BHs without significant mass loss via stellar winds.
 \citep{2003ApJ...591..288H,2010ApJ...714.1217B,2015MNRAS.451.4086S}.
-Therefore, we take the seed BH masses as those of their progenitor stars.
-
-Based on the probability distribution function of the BH seed mass $\D P/ \D \log M_{\bullet, i}$, we construct the mass function of those seeds formed in one parent halo
+Therefore, we consider the mass distribution of seed BHs as that of their stellar progenitors.
+
+\blue{
+  I think the $\Phi^{\rm seed}$ is accurate with the following descriptions, also used for Sec. 2.3
+}
+In the $itr$-th DM growth history where a seed BH is formed with mass $M_\text{itr}$ at the cosmic age $t_\text{itr}$, 
+it discretely contributes to the probability distribution function of seed mass at time $t$ as 
+\begin{equation}
+  p^{\rm seed}_{\rm itr} (M_\bullet,t)\equiv \frac{\D^2 P^{\rm seed}_{\rm itr}}{\D M_\bullet \D t}= 10^{-4} \delta(M_\bullet-M_\text{itr}) \delta(t-t_\text{itr}).
+\end{equation}
+Based on the cumulative seed mass probability distribution function $\D P^{\rm seed}_{\rm itr}/ \D M_{\bullet} \left(t\right)$ 
+which is the integral of $p^{\rm seed}_{\rm itr} (M_\bullet,t)$ over time, 
+we construct the mass function from all seeds ($itr$ from 1 to 10$^4$) formed in one parent halo
 with a mass of $\Mh$ where gas has a coherent streaming velocity of $\vbsm$ as a function of time (and redshift).
@@
 %
-where we adopt $\Mh = 10^{11}$, $10^{12}$, and $10^{13}~\Msun$, 
-% (\red{KI: explicitly show those numbers?})
-with number densities $n_{\Mh} = 9.87\times 10^{-4}$, $6.15\times 10^{-6}$, 
-and $8.92\times 10^{-10}~ \text{Mpc}^{-3}$, respectively.
-Combining the PDF and number normalization, we obtain the seed BH mass function as
+where we adopt $\Mh = 10^{11}$, $10^{12}$, and $10^{13}~\Msun$, with number densities of
+$n_{\Mh} = 9.9\times 10^{-4}$, $6.2\times 10^{-6}$, and $8.9\times 10^{-10}~ \text{Mpc}^{-3}$, respectively.
+Combining the PDF and number density normalization, we obtain the seed BH mass function cumulative at time $t$ as
 %
 \begin{align}
-\Phi_\mathrm{M}^{\rm seed} \equiv \sum_{\Mh, \vbsm} n_{\Mh} f_{\vbsm} 
-\cdot \frac{\D P}{\D \log M_{\bullet, i}}\Big| _{\Mh, \vbsm},
+\Phi_{M_\bullet}^{\rm seed}\left(t\right) \equiv \sum_{\Mh, \vbsm} n_{\Mh} f_{\vbsm} 
+\cdot \sum_{\rm itr} \frac{\D P_{\rm itr}^{\rm seed}}{\D \log M_{\bullet}}\left(t\right) \Big| _{\Mh, \vbsm},
 \end{align}
@@
 \centering
-\includegraphics[width=170mm]{scheme.pdf}
+\includegraphics[width=150mm]{scheme.png}
 \caption{
 Schematical demonstration of the procedure to calculate the evolution of BH mass distribution 
-from time $t$ to $t+\Delta t$. 
-The probability of a BH with mass $M_\mathrm{i}$ grow to $M$ after $\Delta t$ is drew from the 
+between checkpoints time $t_0$ to $t_0+\tau$. 
+The probability of a BH with mass $M_0$ grow to $M$ after $\Delta t=\tau$ is drew from the 
 ERDF following Eq.~\ref{eq:Pl}. 
-Thus the new BH mass distribution is reshaped iteratively by integrating with the ERDF. 
+For a newly formed seed BH $M_{\rm i}$, the probability distribution function of BH mass is a delta function, 
+and the growth time is $t_0+\tau-t_{\rm i}$.
+Thus the evolution of BH mass distribution is reshaped iteratively 
+plus taking account of the newly formed seeds if any.
 }
@@
 \vspace{2mm}
+
 \subsection{BH mass growth}
@@
 \citep{2005Natur.433..604D,2005ApJ...630..705H}, 
-and the accretion rate declines with self-regulating feedbacks \citep[e.g.,][]{2008ApJ...686..815Y,2011ApJ...737...26N} or 
-self-similar disk evolution \citep{1991MNRAS.248..754P,2005ApJ...634..901Y,2007MNRAS.377L..25K}. \red{KI: what's this?}
-This ``flickering'' pattern of individual quasar luminosity evolution can be directly translated into the diversity in the Eddington ratios of a quasar sample, 
-\red{where the Eddington ratio distribution function (ERDF) $\D P/ \D\ln\lambda$ shares the same Schechter function shape 
-with the differential time at different $\lambda$ \citep{2006ApJ...639..700H,2009ApJ...698.1550H}.}
-\red{KI: don't follow this logic...}
+and the accretion rate declines by self-regulating feedback processes \citep[e.g.,][]{2008ApJ...686..815Y,2011ApJ...737...26N} 
+or gas consumption \citep{1991MNRAS.248..754P,2005ApJ...634..901Y,2007MNRAS.377L..25K}. 
+This ``flickering'' pattern of individual quasar luminosity evolution can be directly translated into the diversity 
+in the Eddington ratios of quasar samples. 
+We here suppose that the Eddington ratio distribution function $\D P/ \D\ln\lambda$ (ERDF) is characterized
+with a Schechter function and the distribution function is independent of redshift 
+\citep{2006ApJ...639..700H,2009ApJ...698.1550H}. \red{KI: I slightly modified the previous sentence. Is that what you meant?}
+\blue{
+  not exactly, what I meant may not be necessary here, but we may discuss later.
+}
 For type-I AGN populations at low redshifts, the ERDF is characterized with a Schechter function
@@
 
-To characterize the ERDF for a BH population at any time snapshot together with the episodic accretion pattern of individual BHs, 
-we introduce a time duration of $\tlife$, during which a single value of $\lambda$ that follows the ERDF of Eq.~(\ref{eq:Pl}) is assigned to an accreting BH.
-In this way, we give a different growth speed of a BH in every period with a duration of $\tlife$ until $z=6$ (the corresponding cosmic age is $t_{\rm H}\simeq 800$ Myr).
-This treatment enables us to capture the nature of accretion bursts and avoid an unrealistically long-lasting rapid growth phase of a BH.
-\red{We note that the value of $\tlife$ is indispensable as a methodology in our modeling, 
-albeit its direct comparison with observational luminous quasar lifetime is difficult, 
-these timescales are correlated in realizing the SMBH growth. 
-We leave a more detailed discussion to \S~\ref{sec:discussion}.}
-To be done later...
+To characterize the ERDF for a BH population at any time snapshot together with the episodic 
+accretion pattern of individual BHs, 
+we introduce a time duration of $\tlife$, during which a single value of $\lambda$ that follows 
+the ERDF of Eq.~(\ref{eq:Pl}) is assigned to an accreting BH.
+In this way, we give a different growth speed of a BH in every period with a duration of $\tlife$ until $z=6$ 
+(the corresponding cosmic age is $t_{\rm H}\simeq 800$ Myr).
+This treatment enables us to capture the nature of accretion bursts and avoid an unrealistically 
+long-lasting rapid growth phase of a BH.
+This phenomenological method introducing a parameter of $\tlife(<t_{\rm H})$ allows us to avoid 
+numerous uncertainties in modeling of the galaxy assembly, gas feeding, and BH feedback processes in the quasar 
+progenitor halos.
+Instead of treating those ingredients implemented in previous semi-analytical models, we extract 
+an averaged but fundamental timescale that governs mutual correlation between the BHMF and QLF,
+based on direct comparison to those distribution functions for observed high-$z$ quasar population.
+%We leave a more detailed discussion to \S~\ref{sec:discussion}.}
 
@@
 
-We describe how to calculate the time evolution of the BH mass function, combining the semi-analytical growth model 
-and the ERDF (see Eqs.~\ref{eq:mdot} and \ref{eq:Pl}).
-For a given mass distribution function $\D P/\D  M_{\bullet, i}$ at $t=t_i$, we give the BHMF at $t=t_i+\Delta t$ as
+We describe how to calculate the time evolution of the BH mass function, 
+combining the semi-analytical growth model and the ERDF (see Eqs.~\ref{eq:mdot} and \ref{eq:Pl}).
+
+\blue{
+  modified afterwards; btw may I change $t_{\rm life}$ to $\tau$ in the newcommand line at the beginning?
+}
+We set a series of checkpoints with an interval of $\tlife$, 
+tracing back from $t_{\rm H}(z=6)$ to just prior than the first seed formation.
+% we set a total number of $\Nt$ checkpoints with an interval of $\tlife$,
+% where $\Nt = \lfloor \left(t_\mathrm{H}(z=6) - t_\mathrm{H}(z_\mathrm{seed,max})\right)/ \tlife \rfloor$, 
+Starting from the earliest checkpoint, the BH mass distribution evolves iteratively during each cycle,
+together with the seeds newly formed in between.
+For a given mass distribution function $\D P/\D  M_{\bullet, 0}$ at $t=t_0$, 
+we give its evolution at $t=t_0+\Delta t$ as
 %%%%%%%
@@
    \frac{\D P}{\D \ln \lambda}\Big|_{\lambda_\ast} \cdot
-   \frac{\D \ln \lambda_\ast}{\D  M_\bullet}\Big|_{\Delta t, M_{\bullet,i}} \cdot
+   \frac{\D \ln \lambda_\ast}{\D  M_\bullet}\Big|_{\Delta t, M_{\bullet,0}} \cdot
    %_{M, M_\mathrm{i},\Delta t, \delta}
-  \frac{\D P}{\D M_{\bullet, i}}~\D M_{\bullet, i},
+  \frac{\D P}{\D M_{\bullet, 0}}~\D M_{\bullet, 0},
 \end{equation}
 %
-where $\lambda_\ast$ is the Eddington ratio required for a BH with $M_{\bullet,i}$ to grow up to $M_{\bullet}$ within $\Delta t$
-and is calculated analytically by
+where $\lambda_\ast$ is the Eddington ratio required for a BH with $M_{\bullet,0}$ to grow up to $M_{\bullet}$ within $\Delta t$
+and is calculated analytically from Eq.~(\ref{eq:mi2m}) by
 %%%%%%%
@@
   \label{eq:mi2m}
-\frac{\lambda_\ast \Delta t}{\tEdd}=
+\frac{2 \lambda_\ast \Delta t}{\tEdd}=
   \ln \left(\frac{M_\bullet} {M_{\bullet,i}}\right) + \frac{1}{\delta} 
-  \left[ \left(\frac{M_\bullet}{M_{\bullet,c}}\right)^\delta - \left(\frac{M_{\bullet, i}}{M_{\bullet,c}}\right)^\delta \right],
+  \left[ \left(\frac{M_\bullet}{M_{\bullet,c}}\right)^\delta - \left(\frac{M_{\bullet, 0}}{M_{\bullet,c}}\right)^\delta \right],
 \end{equation}
 %
-and the derivative of ($\D \ln \lambda_\ast / \D  M_\bullet )|_{\Delta t, M_{\bullet,i}}$ is given by Eq.~(\ref{eq:mi2m}).
-After the seed formation terminates (i.e., after the total number of BHs is fixed), we perform this integration in every timestep 
-by setting to $\Delta t = t_{\rm life}$ until $z=6$.
-
-\if0
-Next, we explain our method to calculate the time evolution of BHMF, 
-which is given by combining the BH mass distribution from the seeds growing independently in merger trees
-with different base halo mass $\Mh$,
-weighted by the environmental $\vbsm$ probability and seeding fraction: 
+with the derivative of ($\D \ln \lambda_\ast / \D  M_\bullet )|_{\Delta t, M_{\bullet,0}}$ also determined.
+Specifically $\Delta t = \tlife$ is set for the BH mass distribution iteration from the latest checkpoint, 
+and for a seed $i$ formed at $t_{\rm i}$ during this cycle, 
+we adopt $\Delta t = t-t_{\rm i}$, and $\D P^{\rm seed}_{\rm i}/ \D M_{\bullet}$ as the initial mass distribution.
+This procedure is illustrated schematically in Fig.~\ref{fig:scheme}. 
+% After the seed formation terminates (i.e., after the total number of BHs is fixed), we perform this integration in every timestep 
+% by setting to $\Delta t = \tlife$ until $z=6$.
+Combining the number density contribution from all the parent halos weighted by environmental $\vbsm$ fraction, 
+the BHMF is thus written as
 %%%%%%%
@@
 %%%%%%%
-\begin{align}
-& \Phi_\mathrm{M} \equiv \frac{\D n}{\D \log M}  \nonumber \\
-& =\sum_{\Mh}\sum_{\vbsm} n_{\Mh} f_{\vbsm} {\fseed} \left(\frac{\D P}{\D \log M}\right)_{\Mh, \vbsm}.
-\end{align}
-
-For a given combination of $\Mh$ and $\vbsm$, 
-We then calculate the BH mass distribution $\D P/\D\log M$ iteratively 
-at a series of checkpoints with an interval of $\tlife$, 
-from the earliest seed formation time to $z=$ 6. 
-% we set a total number of $\Nt$ checkpoints with an interval of $\tlife$,
-% where $\Nt = \lfloor \left(t_\mathrm{H}(z=6) - t_\mathrm{H}(z_\mathrm{seed,max})\right)/ \tlife \rfloor$, 
-At each checkpoint $t$, the BH mass distribution is developed from the growth of itself 
-at the previous checkpoint, plus the seeds newly formed in between.
-Considering the growth of a BH with mass $M_{\rm i}$ by a time interval $\Delta t$, 
-from the accretion rate prescription in Eq.~(\ref{eq:mdot}), the final mass $M$ can be described in the relation 
-%%%%%%%
-%    Eq. 4
-%%%%%%%
 \begin{equation}
-  \label{eq:mi2m}
-  \ln \left(\frac{M} {M_{\rm i}}\right) + \frac{1}{\delta} 
-  \left[ \left(\frac{M}{M_0}\right)^\delta - \left(\frac{M_{\rm i}}{M_0}\right)^\delta \right]
-  = \frac{\lambda \Delta t}{\tEdd}.
+  \Phi_{M_\bullet} 
+  =\sum_{\Mh, \vbsm} n_{\Mh} f_{\vbsm} {\fseed} \cdot \frac{\D P}{\D \log M_\bullet}\Big|_{\Mh, \vbsm}.
  \end{equation}
 
-This yields the BH mass distribution 
-%%%%%%%
-%    Eq. 5
-%%%%%%%
-\begin{align}
-  \label{eq:dpdm}
-  & \frac{\D P}{\D \log M} = \int_{}^{} 
-   \left(\frac{\D P}{\D \ln \lambda}\right)_{\lambda(M, M_\mathrm{i},\Delta t, \delta)} \nonumber \\
-  & \left(\frac{\D \ln \lambda}{\D \log M} \right)_{M, M_\mathrm{i},\Delta t, \delta}
-  \frac{\D P}{\D \log M_\mathrm{i}} \D\log M_\mathrm{i},
-\end{align}
-
-\fi
-
-%where ${\D P}/{\D \ln\lambda}$ is given by a set of parameters $\lambda_0$ and $\alpha$ in Eq.~(\ref{eq:Pl}), 
-%at the $\lambda$ value $\lambda\left(M, M_\mathrm{i},\Delta t, \delta\right)$ inferred from Eq.~(\ref{eq:mi2m}).
-%For the evolution of the BH mass distribution, we set $\Delta t=\tlife$.
-On the other hand, for the growth of an individual seed, 
-$\Delta t < \tlife$ is calculated from the seeding time to the current checkpoint,
-and $ \D P/\D \log M_\mathrm{i}$ is a discrete function which is 10$^{-4}$ 
-(normalized by the track numbers 10$^4$ in a merger tree) at $M_\mathrm{i} = M_\mathrm{seed}$, 
-and 0 elsewhere.
-This procedure is illustrated schematically in Fig.~\ref{fig:scheme}.
-
-% wli
-Setting discrete mass bins to resemble the integration in the calculation above, 
+We note that setting discrete mass bins to resemble the integration in the calculation above, 
 we ensure the convergence of the BHMF produced by increasing the number of mass bins to 800 log evenly across $10^2-10^{12}~\Msun$. 
-Our results are consistent with that from directly generating random $\lambda$ 
+Our results of $\Phi_{M_\bullet}$ are consistent with that from directly generating random $\lambda$ 
 following Eq.~(\ref{eq:Pl}) in each cycle of BH growth. 
 Remarkably, we avoid the fluctuations in drawing random samples following the ERDF 
-and extend to high mass (luminous) end in the BHMF (QLF) in a numerically efficient way.
+and extend to massive (luminous) end in the BHMF (QLF) in a numerically efficient way.
 
@@
 \vspace{2mm}
-\subsection{QLF after obscuration}\label{sec:LF}
-Furthermore, we can generate QLFs that is directly probed by high-$z$ observations.
+\subsection{Quasar luminosity function with obscure correction}\label{sec:LF}
+
+Using the BHMF and its evolution, we construct the QLF, which can be directly probed by high-$z$ quasar observations.
 %  compared with observations and in return constrain our model.
-For a BH accreting with bolometric luminosity $\Lbol=\lambda L_\mathrm{Edd}$, 
-its rest-frame ultraviolot (UV) absolute magnitude $\Muv$ 
-at 1450 $\mathrm{\AA}$ is given by: 
+For an accreting BH with a bolometric luminosity of $\Lbol=\lambda L_\mathrm{Edd}$, 
+its rest-frame ultraviolot (UV) absolute magnitude of $\Muv$ at 1450 $\mathrm{\AA}$ is estimated by
 %%%%%%%
@@
   \label{eq:M1450}
-  \Muv= -21.0-2.5 \log  \left(\frac{\Lbol}{10^{45}~\mathrm{erg~s}^{-1}} \right).
+  \Muv= -21.0-2.5 \log  \left(\frac{\Lbol}{10^{45}~\mathrm{erg~s}^{-1}} \right),
 \end{equation}
-Here we adopt the bolometric correction factor $\fbol=4.4$ for the monochromatic UV band \citep{2006ApJS..166..470R}.
-Under this conversion, an ERDF combined with the $z\sim$ 6 BH population is able to reproduce 
-the quasar abundances with different luminosities. 
-However, we note that a vital ingredient to construct the observed QLF, 
-is the luminosity dependent obscuration fraction, 
-which decreases the fraction of the detectable quasars preferentially in the dimmer population 
-\citep{2003ApJ...598..886U,2014ApJ...786..104U,2008A&A...490..905H,2014MNRAS.437.3550M}, 
-thus differs the normalization and shape of the observed QLF from the intrinsic one.
-
-% 讨论一下 obs fraction :
-The current major regimes of quasar obscuration are from extinction by dusty torus and high density circumnuclear gas, 
-hence intemately connected with the gas fueling and feedback process of accreting BHs \citep[see][for a review]{2018ARA&A..56..625H}.
-However, from both theoretical and observational side, our current understanding of the quasar obscured fraction is inadequate, 
-due to the sophisticated physical conditions which lead to obscuration and observational difficulties in probing it.
-The high-$z$ qusars observed in their restframe UV-optical bands are profoundly obstructed by dust obscuration, 
-while hard X-ray (2$-$10 keV) can penetrate the dust with gas dominating the absorption. 
-Therefore, the dust obscuration is equavalently translated to gas absorption with column density $N_\mathrm{H}>10^{22}$ cm$^{-2}$ 
-implied by the X-ray spectral fitting \citep[e.g.,][]{2003ApJ...598..886U,2007A&A...463...79G,2008A&A...490..905H}.
-The redshift dependency of the obscured fraction is found to increase toward $z\sim 2$ and saturate at higher redshifts 
-\citep{2008A&A...490..905H,2014ApJ...786..104U,2018MNRAS.473.2378V}.
-We apply the obscuration fraction $\fobsc$ following the hard X-ray data analysis of \citet{2014ApJ...786..104U}, 
-converting the hard X-ray to bolometric luminosity by the bolometric correction from \citet{2020A&A...636A..73D}.
-The obscuration fraction is $\sim80\%$ (and 50\%, 30\%) with $\Muv$ = $-20$ (and $-24$, $-28$). 
-Compared with another work by  \citet{2014MNRAS.437.3550M}, this shows a similar decreasing trend with luminosity, 
-and the values are in agreement within a factor of 3.
-In this work, we ignore the uncertain Comption thick ($N_\mathrm{H}>10^{24}$ cm$^{-2}$) quasar population, which is hidden even from hard X-ray observation 
-and also has possible dependency on quasar properties.
+%
+where we adopt a bolometric correction factor of $f^{\rm bol}_{1450}=4.4$ for the monochromatic UV band 
+\citep{2006ApJS..166..470R}.
+Combining this conversion factor and the ERDF to govern the BH growth, the the quasar abundances with different luminosities 
+can be constructed straightforward.
+%Under this conversion, an ERDF combined with the $z\sim$ 6 BH population is able to reproduce 
+%the quasar abundances with different luminosities. 
+However, we note that the {\it intrinsic} QLF is not necessary identical to the {\it observed} QLF
+because a larger fraction of fainter quasars are missed in current observations owing to quasar obscuration.
+%it is crucial to obtain we note that a vital ingredient to construct the observed QLF, 
+Therefore, the number of fainter quasars observed as type-I AGNs is reduced by the obscuration effect
+%Therefore, is the luminosity dependent obscuration fraction, 
+%which decreases the fraction of the detectable quasars preferentially in the dimmer population 
+\citep{2003ApJ...598..886U,2014ApJ...786..104U,2008A&A...490..905H,2014MNRAS.437.3550M}. 
+%thus differs the normalization and shape of the observed QLF from the intrinsic one.
+
+% 讨论一下 obs fraction 
+A widely-accepted mechanism causing quasar obscuration is extinction by dusty tori and dense gas clouds 
+in the circumnuclear region, hence tightly related with gas fueling and feedback processes from accreting BHs 
+\citep[see][for a review]{2018ARA&A..56..625H}.
+However, the physical conditions for quasar obscuration have been poorly understood even with extensive studies both on theoretical and observational sides. 
+% our current understanding of the quasar obscured fraction is inadequate, 
+%due to the sophisticated physical conditions which lead to obscuration and observational difficulties in probing it.
+Observationally, the obscured fraction of AGNs with hydrogen column density of $N_{\rm H}>10^{22}~{\rm cm}^{-2}$
+can be estimated from spectral analyses of AGNs in the X-ray band
+%The high-$z$ quasars observed in the rest-frame UV-optical bands are profoundly obstructed by dust obscuration, 
+%\red{while hard X-rays in the 2$-$10 keV band can penetrate the dust with gas dominating the absorption.} \red{(KI: what does it mean?)} 
+%\red{Therefore, dust obscuration is equivalently translated to gas absorption with a hydrogen column density of $N_\mathrm{H}>10^{22}$ cm$^{-2}$ 
+%implied by the X-ray spectral fitting 
+\citep[e.g.,][]{2003ApJ...598..886U,2007A&A...463...79G,2008A&A...490..905H}. 
+The obscured fraction is nearly $\gtrsim 80\%$ at $L_{\rm X}<10^{43}~{\rm erg~s}^{-1}$ and 
+decreases with the X-ray luminosity \citep{2014ApJ...786..104U,2014MNRAS.437.3550M}.
+The exact function shape still remains under debate, but the overall dependence on the X-ray luminosity holds.
+Moreover, the obscured fraction is found to increase gradually toward higher redshifts and is saturated $z\sim 2$
+\citep{2008A&A...490..905H,2014ApJ...786..104U,2014MNRAS.437.3550M,2018MNRAS.473.2378V}.
+
+In this work, we adopt the obscuration fraction $\fobsc$ given by \citet{2014ApJ...786..104U}, 
+converting the hard X-ray luminosity to the 1450\AA magnitude with bolometric correction factors of
+$f^{\rm bol}_{\rm X}=???$ \citep{2020A&A...636A..73D} and $f^{\rm bol}_{1450}=4.4$ \citep{2006ApJS..166..470R}.
+The obscuration fraction is $\simeq 0.8$, $0.5$, $0.3$ at $\Muv$ = $-20$, $-24$, $-28$ mag. 
+%An alternative form proposed by \citet{2014MNRAS.437.3550M} shows a similar dependence of $\fobsc$ with the luminosity,
+%but the values somewhat differ from that given by \citet{2014ApJ...786..104U} \red{within a factor of $XXX$ KI: more quantitativelt}.
+%Compared with another work by  \citet{2014MNRAS.437.3550M}, this shows a similar decreasing trend with luminosity, 
+%and the values are in agreement within a factor of 3.
+Here, we neglect the contribution from Compton-thick AGNs with $N_\mathrm{H}>10^{24}$ cm$^{-2}$, 
+which are obscured even in the hard X-ray band and show possible dependence on quasar properties.
 % and it is currently not warranted to discuss the uncertainties of $\fobsc$.
-Note that the obscured fraction at high-$z$ is still under investigated, 
-with complex convertions between the probes in different observational bands,
+It is worth noting that the obscured fraction for high-$z$ quasar populations is still under investigation,
+and the uncertainties would affect our analyses for fainter quasars.
+%with complex convertions between the probes in different observational bands,
 % optical and X-ray observations, 
-and we may refer to more solid prescriptions of $\fobsc$ in the future.
-
-After taking obscuration into account, the observed luminosity function for a given BHMF and ERDF can be written as:
+%and is need to be 
+%and we may refer to more solid prescriptions of $\fobsc$ in the future.
+We leave more comprehensive arguments about the quasar obscuration effect for future work.
+
+After taking into account the obscuration effect, the observed QLF for a given BHMF and ERDF is calculated as
 %%%%%%%
@@
 %%%%%%%
-\begin{align}
+\begin{equation}
 \label{eq:dn_dM1450}
-& \Phi_\mathrm{\Muv} \equiv \frac{\D n}{\D \Muv} \nonumber \\
-& = \left[1 -\fobsc\left(\Muv\right) \right] \times % \nonumber \\
-\int_{}^{} \left(\frac{\D P}{\D \ln \lambda}\right)_{\lambda(\Muv, M)}  \nonumber \\
-& \left(\frac{\D \ln \lambda}{\D \Muv} \right)_{\Muv, M} \Phi_\mathrm{M} \D \log M,
-\end{align}
-where $\lambda\left(\Muv,M\right)$ is the obtained from Eq.~(\ref{eq:M1450}).
-%
-Hence the observed QLF can be produced simultaneously with the BHMF from a set of model paramters, 
+\Phi_{\Muv} 
+%\equiv \frac{\D n}{\D \Muv} \nonumber \\
+ = (1 -\fobsc)  % \nonumber \\
+\int \frac{\D P}{\D \ln \lambda}\Big|_{\tilde{\lambda}}  \cdot
+\frac{\D \ln \tilde{\lambda}}{\D \Muv} \cdot
+ \Phi_{M_\bullet} \D \log M_\bullet,
+\end{equation}
+%
+where the values of $\tilde{\lambda}=\lambda(\Muv, M_\bullet)$ and $\D \ln \tilde{\lambda}/\D \Muv$ are calculated analytically from Eq.~(\ref{eq:M1450}).
+%
+Hence, the observed QLF can be produced simultaneously with the BHMF from a set of model parameters, 
 to be compared with the ones from observation.
@@
 \subsection{MCMC fitting}\label{sec:fitting}
-In this section, we describe the Markov Chain Monte Carlo (MCMC) fitting procedure we adopt to optimize the parameters described in \S~\ref{sec:MF}. 
+
 %%%%%%%
@@
 \centering
-\includegraphics[width=170mm]{contour.pdf}
+\includegraphics[width=180mm]{contour.pdf}
 \caption{
@@
 \label{fig:contour}
+\vspace{5mm}
 \end{figure*}
 %
-% 1. data: observational MF LF; describe quadratic error in Willott 2010
-Firstly the BHMF data is adopted from \citet{2010AJ....140..546W} (hereafter W10),
-where they reconstruct the BHMF with the QLF and ERDF
-extracted from the virial BH mass among $\sim$ 20 quasars at $z\approx$ 6. 
-The BHMF spanning $10^7 < M <10^{10}~\Msun$ is best constrained around $10^9~\Msun$, 
-and the error is pronounced toward the low mass and high mass end.
-We take 10 mass bins spacing evenly in logscale and a quadratic form of the error, 
-covering the same ranges as their bootstrap resamples (see Figure 8 of W10). 
-On the observed QLF side, we adopt the binned data and error bars from \citet{2018ApJ...869..150M}, 
-over a wide range of $-30 < \Muv <-22$ mag (see their Table 4 and Figure 13).
-
-% 2. prior
-The prior function, i.e. the probability distribution to draw parameter samples from, 
-encodes the physically acceptable ranges and underlying distributions for all parameters. 
-We assign uniform prior $\tlife$ within 10 to 200 Myr, 
-motivated by the constraints on the quasar lifetime during an optically luminous phase \citep[e.g.,][]{2004cbhg.symp..169M}.
-For the mass dependency of BH growth we constrain the value of $\log \delta$ from $-4$ to $-0.3$, 
-slightly suppressing the growth in the high mass end. 
+
+In this section, we describe the Markov Chain Monte Carlo (MCMC) fitting procedure used to optimize 
+the BH growth parameters so that the observed BHMF and QLF are consistently reproduced. 
+As discussed in \S~\ref{sec:MF}, we consider five parameters of $\tlife$, $\delta$, $\alpha$, $\lambda_0$, and $\fseed$.
+The best-fit values of the first four parameters are calculated by the MCMC method, while $\fseed$ is fixed to a single value.
+In what follows, we describe the results for $\fseed = 0.1$ and $0.01$ (see Appendix for the case with $\fseed =1.0$).
+
+% prior
+In this analysis, we constrain those parameters to be within certain physically acceptable ranges, 
+assuming a prior function for each quantity.
+We use a uniform prior on $\tlife$ with a limit of $10~{\rm Myr} \leq \tlife \leq 200~{\rm Myr}$,
+motivated by the constraints on the quasar lifetime based on various observations
+\citep[e.g.,][]{2004cbhg.symp..169M}.
+The parameter of $\delta$ that characterizes a non-exponential BH growth 
+is constrained at $\log \delta$ from $-4$ to $-0.3$ \red{KI: add a footnote, explaining why not $\delta$ but $\log \delta$?}.
+%slightly suppressing the growth in the high mass end. 
 % After trials we find in the Markov chain, the value of $\tlife$ reduces to $\lesssim$ 100 Myr, 
@@
 % and use $\log \delta$ instead of $\delta$ with a prior ranging from $-4$ to $-1$ in pursuit of better fitting performance. 
-Specificaly, the prior is restricted by an exponential cutoff when $\log \delta < -3$,
-since toward low $\log\delta$ the model is essentially mass-independent,
-and remains uniform otherwise. 
-For the characteristic value of Eddington ratio $\lambda_0$ in the Schechter shape, 
-we impose a Gaussian prior with the mean value $\mu_{\lambda_0}=0.6$ and scatter $\sigma_{\lambda_0}=0.4$, 
+The prior function is uniform at $\log \delta \geq -3$ and is imposed to decay with an exponential cutoff at $\log \delta < -3$,
+which is small enough for the model to be approximately mass independent.
+%since toward low $\log\delta$ the model is essentially mass-independent,
+%and remains uniform otherwise. 
+For the characteristic Eddington ratio $\lambda_0$ in the Schechter-type ERDF, 
+we impose a Gaussian prior function with a mean value of $\mu_{\lambda_0}=0.6$ and a dispersion of $\sigma_{\lambda_0}=0.4$.
 % motivated by the various observations revealing a large sample of quasars with peak $\lambda\lesssim 1$,
-motivated by the observations revealing $z=$ 6 quasars peak with $\lambda \sim 0.6$ 
+The choice is motivated by the brightest quasar samples at $z=$ 6, whose ERDF function is peaked around $\lambda \sim 0.6$ 
 % \citep[e.g.,][Onoue et al. in preparation]{2010AJ....140..546W}.
 \citep[e.g.,][]{2010AJ....140..546W}.
-Specially a complete sample of quasars from Onoue et al. in prep peak with $\log \lambda_0 \approx -0.24 \pm 0.31$ 
-before correcting the selection bias. 
+\red{Specially a complete sample of quasars from Onoue et al. in prep peak with $\log \lambda_0 \approx -0.24 \pm 0.31$ 
+before correcting the selection bias. (to be revised by MO)}.
 % It is worth noting that, observationally the high-$z$ ERDF is fitted by a log-normal function. 
@@
 % indicating a prominent population of low $\lambda$ quasars is hidden by the flux-limited incompleteness.
-Finally to the slope index $\alpha$ which remains unconstrained by current probes,
+For the low-$\lambda$ slope of $\alpha$ in the ERDF, we assign a Gaussian prior function with a mean value 
+$\mu_{\alpha}=0$ and a dispersion of $\sigma_{\alpha}=0.3$.
+Note that the value of $\alpha$ remains poorly constrained by the current high-$z$ quasar observations,
+but the low-$z$ quasar samples support $-0.3 \lesssim \alpha \lesssim 0.3$ \citep[e.g., see Figure 21 in][]{2015MNRAS.447.2085S}.
 % considering the more significant obscuration of lower $\lambda$ quasars 
-we assign a Gaussian prior, with the mean value $\mu_{\alpha}=0.$ and scatter $\sigma_{\alpha}=0.3$.
+%we assign a Gaussian prior, with the mean value $\mu_{\alpha}=0.$ and scatter $\sigma_{\alpha}=0.3$.
+
+%
+% 1. data: observational MF LF; describe quadratic error in Willott 2010
+The observed BHMF data is taken from \citet{2010AJ....140..546W} (hereafter \citetalias{2010AJ....140..546W}), where 
+the virial BH mass measurements for $\sim 20$ bright quasars at $z\simeq $ 6 are used.
+%rom the virial BH mass among $\sim$ 20 quasars at $z\approx$ 6.
+%they reconstruct the BHMF with the QLF and ERDF
+%extracted from the virial BH mass among $\sim$ 20 quasars at $z\approx$ 6. 
+Although the BHMF spans over $10^7 < M_\bullet/\Msun <10^{10}$, the best constraint is given around 
+$M_\bullet \simeq 10^{8.5}~\Msun$
+and thus the statistical error size becomes larger both at the lower and higher mass range.
+We set up 10 logarithmically spaced mass bins and adopt errors with sizes increasing quadratically as 
+$\Phi_{M_\bullet}^{\rm err} = \pm \{0.2 +   [\log (M_\bullet/10^{8.5}~\Msun)]^2/3 \}~{\rm dex}$,
+covering the same mass range as in their bootstrap resamples (see Figure 8 of W10). 
+The observed QLF is taken from \citet{2018ApJ...869..150M} (hereafter \citetalias{2018ApJ...869..150M}) 
+over a wide range of $-30 < \Muv <-22$ mag (see their Table 4 and Figure 13). 
+The magnitude bins and the error sizes are given consistently with \citetalias{2018ApJ...869..150M}.
+
+% 3. posterior
+% Then evaluating the likelihood of the dataset reproducing the observed BHMF and QLF at $z=$ 6, 
+% the Markov chain of samples converges to the best-fit (maximum likelihood) parameters.
+Following the prior distribution functions, the four parameters are sampled to generate the synthetic 
+BHMF and QLF dataset, which are compared to the observational dataset. 
+The discrepancy between the model and observational data is evaluated with a $\chi^2$-value defined by
+%%%%%%%
+%    Eq. 8
+%%%%%%%
+\begin{align}
+  \chi^2 = \sum_{i,j}
+  \frac{\left(\log{\Phi^{\rm mod}_{i,j}} - \log{\Phi^{\rm obs}_{i,j}}\right)^2}{(\log{\Phi^{\rm err}_{i,j}})^2},
+\end{align}
+where $\Phi^{\rm mod}_{i,j}$ and $\Phi^{\rm obs}_{i,j}$ represent the modeled and observational value 
+on the \textit{i-}th BHMF ($j=M_\bullet$) and QLF ($j=\Muv$) bin, and $\Phi^{\rm err}_{i,j}$ is the corresponding error.
+Adopting 10 mass bins and 12 magnitude bins, we treat the errors from comparison both in the BHMF and QLF
+with a nearly equal weight.
+%te that the equal constraints from the BHMF and QLF are realized by extracting
+%comparable numbers of data points from $\Phi_\mathrm{M}$ and $\Phi_\mathrm{\Muv}$.
+% the constraint is actually insensitive to the choice of bin numbers. 
+The posterior distribution of the MCMC fitting is stabilized around the minimum value of $\chi^2$ (highest likelihood), 
+with the models best reproducing the $z=$ 6 BHMF and QLF.
+
+\vspace{5mm}
+\section{Results}\label{sec:result}
+
+\vspace{2mm}
+\subsection{Fitting Results}\label{sec:fitting_result}
+In Fig.~\ref{fig:contour}, we visualize the MCMC fitting results for each parameter in two-dimensional 
+posterior distribution for the case $\fseed= 0.1$ (left) and $0.01$ (right), respectively.
+The three vertical lines on each one-dimensional posterior distribution present the peak and the values
+with $1\sigma$ scatter.
+The result for the $\fseed=1$ case is discussed in the Appendix.
+
+For the two cases, the best-fit solutions consistently show a small values of $\delta < 0.01$.
+%, which is sufficiently small and should be marginalized out. 
+This suggests that in our model assumption, a nearly exponential BH growth pattern is favored. 
+% In other words, on average the BH growth can be described as exponential, 
+% under the premise that the gas supply is episodical. 
+The typical duration of quasar activity is required to be $\tlife \simeq 29$ Myr for both the cases, 
+which is $\sim 64\%$ of the $e$-folding time for an exponential growth.
+This suggests that accreting seed BHs vary their growth speeds (i.e., the Eddington ratio) 
+$\sim 30$ times on average, over the cosmic time of $t_{\rm H}\simeq 800$ Myr at $z\simeq 6$.
+The timescale of $\tlife$ also gives a lower bound of the quasar lifetimes of $t_{\rm Q}\sim 1-10$ Myr, 
+which are estimated by the measurement of the physical extents of hydrogen Ly$\alpha$ proximity zones 
+observed in the rest-frame UV spectra (e.g., Eilers+2018, Davies+ 2019).\red{KI: we need to figure out 
+if their $t_Q$ is the quasar age or lifetime, or something else?}
+More detailed comparison is discussed in \S\ref{sec:evol}.
+
+The two parameters characterizing the ERDF are given as
+$(\lambda_0,\alpha) = (0.89,0.12)$ and $(0.87,0.20)$ for $\fseed=0.01$ and $0.1$, respectively.
+With those values, the number fraction of BHs growing with Eddington ratios above $\lambda_0$ is
+estimated as $P(>\lambda_0)=***$.
+Thus, nearly ***\% of BHs are required to grow in mass rapidly to be SMBHs by $z\simeq 6$,
+consistent with a general picture for the early assembly of SMBHs (ref, Xiaohui? Willott? SDSS papers?)
+The characteristic Eddington ratio needs to be close to unity, otherwise the highest luminosity and BH mass
+in the model would differ from those in observations.
+On the other hand, the power-law index of $\alpha$ in the ERDF tends to increases as the seeding fraction decreases,
+indicating that the number of inactive BHs with $\lambda \ll \lambda_0$ is reduced.
+\red{KI: can you check if $\fseed \cdot P(>\lambda_0)$ is roughly constant?}
+Thus, with lower seeding fractions, a larger number of active BHs with $\lambda \sim \lambda_0$ 
+participate in the high-$z$ quasar assembly and reproduce the bulk properties of the BHMF and QLF.
+%hence the best-fit $\alpha$ increases and higher accretion rate is realized from the Schechter shape with higher $\alpha$. 
+% We expect more complete observations to better constrain the parameter priors in the model fitting.
+
+In Figs.~\ref{fig:fitmf} and \ref{fig:fitlf}, we show the BHMF and QLF at $z=$ 6 reproduced by the best-fit parameters
+as well as the $1\sigma$ spread, where the QLF model excludes a contribution from obscured quasars, 
+yielding the {\it observed} QLF for type-I AGN populations.
+The observed BHMF in \citetalias{2010AJ....140..546W} and QLF in \citetalias{2018ApJ...869..150M} 
+with statistical errors are also overlaid for comparison.
+We note that \citetalias{2010AJ....140..546W} constructed the BHMF using quasar samples with 
+$10^8~\Msun \lesssim M_\bullet \lesssim 3\times 10^9~\Msun$.
+In the high-mass regime, our fitting result nicely agrees to that in \citetalias{2010AJ....140..546W}.
+The QLF fitting results are also consistent with the observed one over $-29~{\rm mag} \lesssim \Muv \lesssim -25~{\rm mag}$,
+but seems to overproduce the abundance of fainter quasars at $\Muv>-24~{\rm mag}$.
+% due to the lack of fine tuning by the model parameters in the low mass range, 
+The difference at the fainter end tends to be alleviated with the seeding fraction lowered ($\fseed = 0.01$),
+because the progenitors of $z=6$ BHs with $10^{7-8}~\Msun$ (or similarly, 
+$-22~{\rm mag} \lesssim \Muv \lesssim -24~{\rm mag}$) were less massive seed BHs with $\sim ***~\Msun$,
+which is closer to the peak of the seed mass distribution (see Fig.~\ref{fig:seedmf}).
+Those BH population naturally produces a flatter slope of the QLF (and BHMF) at the faint (low-mass) end.
+Overall, the parameters are inferred to be reasonable fits consistent with the observational data.
 
@@
 \centering
-\includegraphics[width=170mm]{fits_MF.png}
+\includegraphics[width=160mm]{fits_MF.png}
 \caption{
@@
 \centering
-\includegraphics[width=170mm]{fits_LF.png}
+\includegraphics[width=160mm]{fits_LF.png}
 \caption{
@@
 
-% 3. posterior
-% Then evaluating the likelihood of the dataset reproducing the observed BHMF and QLF at $z=$ 6, 
-% the Markov chain of samples converges to the best-fit (maximum likelihood) parameters.
-Following the prior distribution, parameters are sampled to generate the synthetic BHMF and QLF dataset, 
-which is then conjointly compared with the observational data. 
-The offset between the model and data is evaluated as 
-%%%%%%%
-%    Eq. 8
-%%%%%%%
-\begin{align}
-  \chi^2 = \sum_i
-  \frac{\left(\log{\Phi_\mathrm{mod,i}} - \log{\Phi_\mathrm{obs,i}}\right)^2}{(\log{\Phi_\mathrm{err,i}})^2},
-\end{align}
-where $\Phi_\mathrm{mod,i}$ and $\Phi_\mathrm{obs,i}$ 
-represent the modeled and observational values of $\Phi_\mathrm{M}$ ($\Phi_\mathrm{\Muv}$) in the \textit{i-}th BHMF (QLF) bin, and 
-$\Phi_\mathrm{err,i}$ is the corresponding error.
-Note that the equal constraints from the BHMF and QLF are realized by extracting
-comparable numbers of data points from $\Phi_\mathrm{M}$ and $\Phi_\mathrm{\Muv}$.
-% the constraint is actually insensitive to the choice of bin numbers. 
-The posterior distribution of the MCMC fitting is stabilized around the minimum value of $\chi^2$ (highest likelihood), 
-with the models best reproducing the $z=$ 6 BHMF and QLF.
-
-\if0
-
-\vspace{5mm}
-\section{Results}\label{sec:result}
-
 \vspace{2mm}
-\subsection{Fitting Results}\label{sec:fitting_result}
-In Fig.~\ref{fig:contour}, we visualize the MCMC fitting results for each parameter: distribution with the peak and one sigma scatter, 
-with panels (a) and (b) for $\fseed=$ 0.1 and 0.01, respectively. 
-The results for the $\fseed=1$ case is complemented in the Appendix.
-With different $\fseed$, the best-fit solutions consistently show that $\delta \lesssim -1$ is a nuisance parameter, 
-which is sufficiently small and should be marginalized out. This suggests that in our model assumption, 
-a nearly exponential growth pattern is favored. 
-% In other words, on average the BH growth can be described as exponential, 
-% under the premise that the gas supply is episodical. 
-The best-fit value of $\tlife$ is 20 $\sim$ 30 Myr for both cases, 
-while that of $\alpha$ increases with decreasing $\fseed$, 
-from 0.12 ($\fseed=0.1$) to 0.20 ($\fseed=0.01$),
-indicating a strong degeneracy between the $\fseed$ and $\alpha$ values. 
-With lower seeding fraction, a larger number of BHs are required to grow rapidly to reporduce the observed massive population at $z\sim$ 6, 
-hence the best-fit $\alpha$ increases and higher accretion rate is realized from the Schechter shape with higher $\alpha$. 
-% We expect more complete observations to better constrain the parameter priors in the model fitting.
-
-In Fig.~\ref{fig:fitmf} and Fig.~\ref{fig:fitlf}, we show the BHMF and QLF at $z=$ 6 reproduced by the best-fit parameters, 
-as well as the one sigma spread. 
-The observed BHMF in W10 and QLF in \citet{2018ApJ...869..150M} with errors are also plotted for comparison.
-Note that the BHMF in W10 is only sensitive to the $>10^8~\Msun$ regime and our results are consistent in this mass range.
-The QLF fitting results overproduce the abundance of faint quasars than observation, 
-% due to the lack of fine tuning by the model parameters in the low mass range, 
-with the tension slightly eased in the case of $\fseed=0.01$ than $\fseed=0.1$. 
-The cause of this difference is that in the $\fseed=0.01$ case, 
-the progenitor BHs of $10^{7-8}~\Msun$ is systematically lower than in the $\fseed=0.1$ case, 
-which is closer to the peak of the seed mass distribution (see Fig.~\ref{fig:seedmf}), 
-this naturally brings the slope of QLF (and BHMF) in the faint (low-mass) end shallower than in the luminous (high-mass) end.
-Overall, the parameters are inferred to be reasonable fits consistent with the observational data.
-
+\subsection{Model dependence}\label{sec:modep}
+\red{KI: It'd be good to discuss the dependence of our results on key parameters such as $\tlife$.
+You repeat the MCMC fitting with a fixed value of $\tlife$? Saying like for a longer $\tlife$,
+the fitting results would never be improved.}
+
+\vspace{2mm}
+\subsection{Cosmological evolution of BHMF and QLF}\label{sec:cosm}
+\red{KI: shall we discuss the $z$-dependence of the BHMF and QLF?
+Don't need to repeat calculations. Just using the same parameters with 1sigma scatter?
+Showing $\rho_{\bullet}(z)$ in $\Msun ~ {\rm Mpc}^{-3}$, which is the integrant of BHMF, would be interesting}
+
+\section{Discussion}
 \vspace{2mm}
 \subsection{Individual BH growth}\label{sec:evol}
-The best-fit models from MCMC realizations enable us to generate a sample of BH evolutionary tracks starting from BH seeds.
+
+The best-fit model from the MCMC realizations enables us to generate a sample of BH evolutionary tracks starting from BH seeds.
 We take $\fseed=$ 0.01 as a fiducial case, where the best-fit parameters for BH growth are 
-$\tlife=18.76$ Myr, $\log\delta=-1.26$, $\lambda_0=0.87$, and $\alpha=0.20$.
-In the following we demonstrate how the BH sample is constructed and its hints on observations.
+$\tlife=18.76$ Myr, $\delta=0.055$, $\lambda_0=0.87$, and $\alpha=0.20$.
+We apply the result to construction individual evolutionary tracks of BHs and give some implications to high-$z$ quasar observations.
 
@@
 % motivated by the properties of typical BH seeds (with median formation redshift and median mass).
-We plant a sample of 10$^7$ BH seeds at high redshifts, 
-with their formation time and mass distribution according to the seeding model described in \S~\ref{sec:seed}. 
-For individual BH growth history, every time interval $\tlife$ we assign an Eddington ratio 
-$\lambda$ following the Schechter shape in Eq.~(\ref{eq:Pl}), 
-until $z=$ 6 we take a snapshot of the BH mass and ERDF.
-With the best-fit parameters, the BH growth tracks which finally end up with $>10^8~\Msun$ 
-are shown in Fig.~\ref{fig:track}. 
-We notice that in this sample there are 7 BHs with $M>10^9~\Msun$, 
-among which 5 BHs are in sub-Eddington accretion mode, and 2 in super-Eddington. 
-If we extrapolate the BH mass with the $z \sim$ 6 witnessed Eddington ratio back to $z\sim$ 30, 
-the sub-Eddington accreting BHs trace back to exceedingly massive seeds which are hard to be explained by current seeding scenarios. 
-Observations also raise strong challenges to the growth histories of these sub-Eddington accreting BHs
-\citep[e.g.,][]{2019ApJ...880...77O}.
-In contrast, the super-Eddington accreting BHs trace back to unrealistically low seed mass. 
-On the other hand, we show the mass growth tracks assuming constant Eddington ratio $\lambda=1$ for comparison, 
-and find all the BHs trace back to $\lesssim 10^2~\Msun$ with the constantly vigorous accretion. 
-Both treatments of the constant $\lambda$ lead to BH seed masses extrapolation that deviate from the initial seeds we plant. 
+We generate a sample of 10$^7$ BH seeds, whose formation time and mass distribution at birth follow the model described in \S~\ref{sec:seed}. 
+To growth the individual BHs, we assign an Eddington ratio $\lambda$ in every interval $\tlife$ until $z=6$,
+following the ERDF characterized by a Schechter function with $\lambda_0=0.87$ and $\alpha=0.20$.
+%until $z=$ 6 we take a snapshot of the BH mass and ERDF.
+With the best-fit parameters, the BH growth tracks that end up with $>10^8~\Msun$ by $z=6$ are shown in Fig.~\ref{fig:track}. 
+\red{KI: what is the frequency $N$ of BH accretion bursts with $\lambda>\lambda_0$ between $z=6$ and $10$? The duty cycle for the sub-sample
+is $f_{\rm duty}\simeq N\tlife/\Delta t_{\rm H}$.}
+
+In this sub-sample, we find seven BHs heavier than $M=10^9~\Msun$ (highlighted with solid curves), 
+among which five BHs show $\lambda<1$ in the snapshots at $z=6$.
+Tracing the BH growth curve back to $z=30$ with the Eddington ratio observed at $z=6$ (dotted curves),
+the extrapolated mass of those sub-Eddington BHs at $z=6$ is as massive as $M_\bullet \gg 10^5~\Msun$ and is 
+substantially higher than the mass range for seed BHs.
+%ting BHs trace back to exceedingly massive seeds which are hard to be explained by current seeding scenarios. 
+%
+%If we extrapolate the BH mass with the $z \sim$ 6 witnessed Eddington ratio back to $z\sim$ 30, 
+%the sub-Eddington accreting BHs trace back to exceedingly massive seeds which are hard to be explained by current seeding scenarios. 
+It has been pointed out by \cite{2019ApJ...880...77O} that such simple extrapolation of the growth history for low-$\lambda$ quasars 
+does not work properly (see their Figure 10).
+%it is challenging that observations of fait quasars strong challenges to the growth histories of these sub-Eddington accreting BHs
+%
+In contrast, the extrapolated mass of super-Eddington BHs yields unrealistically small values at the seeding epochs,
+indicating a short duration of super-Eddington accretion modes.
+For comparison, we show the mass growth tracks assuming a constant Eddington ratio of $\lambda=1$, 
+where the extrapolated seed mass is $M_\bullet \sim 10^2~\Msun$.
+%Both treatments of the constant $\lambda$ lead to BH seed masses extrapolation that deviate from the initial seeds we plant. 
+This argument clearly demonstrates that multiple accretion episodes with different values of $\lambda$ should be taken into account 
+to infer the seeding mass for the observed SMBHs as bright quasars at $z\gtrsim 6-7$, instead of assuming one single number 
+of the Eddington ratio.
+
+\red{KI: still not sure what we discuss below... among the 7 BHs, is anyone consistent with Feige's BH?}
 In \citet{2021ApJ...907L...1W}, they discover the currently known most distant quasar at $z=7.642$, 
@@
 
-\vspace{5mm}
-\section{Discussion}\label{sec:discussion}
-
 % \begin{acknowledgments}
@@
 
-\fi
-
 \newpage

### 2022-06-30 ms.tex
Sec. 2.4 intermediate

@@
 Combining this conversion factor and the ERDF to govern the BH growth, the the quasar abundances with different luminosities 
-can be constructed straightforward.
+can be constructed straightforwardly.
 %Under this conversion, an ERDF combined with the $z\sim$ 6 BH population is able to reproduce 
 %the quasar abundances with different luminosities. 
-However, we note that the {\it intrinsic} QLF is not necessary identical to the {\it observed} QLF
-because a larger fraction of fainter quasars are missed in current observations owing to quasar obscuration.
+However, we note that the shape and normalization of the {\it intrinsic} QLF is not necessary identical to the {\it observed} QLF
+because a larger fraction of fainter quasars are missed in current observations owing to quasar obscuration, 
 %it is crucial to obtain we note that a vital ingredient to construct the observed QLF, 
-Therefore, the number of fainter quasars observed as type-I AGNs is reduced by the obscuration effect
+i.e., the number of fainter quasars observed as type-I AGNs is largely reduced by the obscuration effect
 %Therefore, is the luminosity dependent obscuration fraction, 
@@
 In this work, we adopt the obscuration fraction $\fobsc$ given by \citet{2014ApJ...786..104U}, 
-converting the hard X-ray luminosity to the 1450\AA magnitude with bolometric correction factors of
-$f^{\rm bol}_{\rm X}=???$ \citep{2020A&A...636A..73D} and $f^{\rm bol}_{1450}=4.4$ \citep{2006ApJS..166..470R}.
-The obscuration fraction is $\simeq 0.8$, $0.5$, $0.3$ at $\Muv$ = $-20$, $-24$, $-28$ mag. 
+converting the hard X-ray luminosity to the 1450 $\mathrm{\AA}$ magnitude with bolometric correction factors of
+\begin{equation*}
+  f^{\rm bol}_{\rm X} =
+  a\left[1+\left(\frac{\log \left(\Lbol / L_\odot\right)}{b}\right)^{c}\right],
+\end{equation*}
+where $a=10.96$, $b = 11.93$, and $c = 17.79$ \citep[Eq. 2 in ][]{2020A&A...636A..73D}, 
+and $f^{\rm bol}_{1450}=4.4$ \citep{2006ApJS..166..470R}.
+The obscuration fraction reads 
+\begin{equation*}
+  \fobsc = \text{min}\lbrace  0.84 , 0.73-0.24\times[ (\log \Lbol/L_\odot) -43.75] \rbrace,
+\end{equation*}
+following \citet{2014ApJ...786..104U}.
+An alternative fitting of $\fobsc$ proposed by \citet{2014MNRAS.437.3550M} from *** (different sample?) is 
+\begin{equation*}
+  \fobsc = 0.56 + \frac{1}{\pi} \text{arctan} \frac{43.89 - (\log \Lbol/L_\odot)}{0.46},
+\end{equation*}
+we fit the parameters using this prescription and discuss the sensitivity of results to $\fobsc$.
+
+% The obscuration fraction is $\simeq 0.8$, $0.5$, $0.3$ at $\Muv$ = $-20$, $-24$, $-28$ mag. 
 %An alternative form proposed by \citet{2014MNRAS.437.3550M} shows a similar dependence of $\fobsc$ with the luminosity,
@@
 
-After taking into account the obscuration effect, the observed QLF for a given BHMF and ERDF is calculated as
+After taking into account the obscuration effect, 
+the observed QLF for a given BHMF and ERDF is calculated as
 %%%%%%%

### 2022-07-11 ms.tex
version 0710, Sec.3.3 (BHMF_rhoz, QLF_rhoz) added

@@
 \newcommand{\Mh}{M_\mathrm{h}}
+\newcommand{\Mbh}{M_\bullet}
 \newcommand{\Mseed}{M_\mathrm{seed}}
@@
 Therefore, we consider three parent halos with $\Mh = 10^{11}$, $10^{12}$, and $10^{13} ~\Msun$ at $z=$ 6
-and generate 10$^4$ merger trees for each parent halo mass backward in time using the {\tt GALFORM} 
+and generate $N_{\rm tot} (= 10^4)$ merger trees for each parent halo mass backward in time using the {\tt GALFORM} 
 semi-analytic algorithm based on the extended Press-Schechter formalism 
@@
 
-\blue{
-  I think the $\Phi^{\rm seed}$ is accurate with the following descriptions, also used for Sec. 2.3
+%%%%%%%
+%    Fig. 1
+%%%%%%%
+\begin{figure*}
+\centering
+\includegraphics[width=160mm]{seedBHMF_z.pdf}
+\caption{
+Seed BH mass distribution formed in different redshift ranges . 
+Each panel includes a redshift span of 10, 
+with the newly formed BHs denoted by the hatched regions, 
+and the cumulative BHs formed previously by the blue region.
+The most vigorous seed formation epoches are in redshift ranges $z\sim$ $40-30$ and $30-20$.
+Overall, the seed BH mass ranges from $\sim 10^2$ to $\gtrsim 10^5~\Msun$, 
+imprinted with the various parent halo growth histories and environmental $\vbsm$. 
 }
-In the $itr$-th DM growth history where a seed BH is formed with mass $M_\text{itr}$ at the cosmic age $t_\text{itr}$, 
-it discretely contributes to the probability distribution function of seed mass at time $t$ as 
+\label{fig:seedmf}
+\end{figure*}
+
+Let us consider that a seed BH with a mass of $M_{\bullet,i}$ formed in the $i$-th halo merger tree at the cosmic age $t_i$ ($1\leq i \leq N_{\rm tot}=10^4$),
+%In the $i$-th DM growth history where a seed BH is formed with mass $M_\text{itr}$ at the cosmic age $t_\text{itr}$, 
+and each of them contributes to the probability distribution function of seed mass at time $t$ as
+% 
 \begin{equation}
-  p^{\rm seed}_{\rm itr} (M_\bullet,t)\equiv \frac{\D^2 P^{\rm seed}_{\rm itr}}{\D M_\bullet \D t}= 10^{-4} \delta(M_\bullet-M_\text{itr}) \delta(t-t_\text{itr}).
+  p^{\rm seed}_i (\Mbh,t)\equiv \frac{\D^2 P^{\rm seed}_i}{\D \Mbh ~\D t}= \frac{ \delta(\Mbh-M_{\bullet,i})~ \delta(t-t_i)}{N_{\rm tot}}.
 \end{equation}
-Based on the cumulative seed mass probability distribution function $\D P^{\rm seed}_{\rm itr}/ \D M_{\bullet} \left(t\right)$ 
-which is the integral of $p^{\rm seed}_{\rm itr} (M_\bullet,t)$ over time, 
-we construct the mass function from all seeds ($itr$ from 1 to 10$^4$) formed in one parent halo
-with a mass of $\Mh$ where gas has a coherent streaming velocity of $\vbsm$ as a function of time (and redshift).
+%
+Based on the cumulative seed mass probability distribution function $\D P^{\rm seed}_i/ \D \Mbh$ 
+which is the integral of $p^{\rm seed}_i (\Mbh,t)$ over time, 
+we construct the mass function from all $N_{\rm tot}$ seeds formed in one parent halo
+with a mass of $\Mh$, where gas has a coherent streaming velocity of $\vbsm$ as a function of time (and redshift).
 The absolute abundance of those seed BHs is calculated with the number density of the parent halo in a comoving volume at $z=6$ 
@@
 \begin{align}
-\Phi_{M_\bullet}^{\rm seed}\left(t\right) \equiv \sum_{\Mh, \vbsm} n_{\Mh} f_{\vbsm} 
-\cdot \sum_{\rm itr} \frac{\D P_{\rm itr}^{\rm seed}}{\D \log M_{\bullet}}\left(t\right) \Big| _{\Mh, \vbsm},
+\Phi_{\Mbh}^{\rm seed}\left(t\right) \equiv \sum_{\Mh, \vbsm} n_{\Mh} f_{\vbsm} 
+\cdot \sum_{\rm itr} \frac{\D P^{\rm seed}_i}{\D \log \Mbh}\left(t\right) \Big| _{\Mh, \vbsm},
 \end{align}
@@
 %accounting for roughly $f_{\vbsm} = 60\%$ and $40\%$ of the seeding environments, respectively.
-
-%%%%%%%
-%    Fig. 1
-%%%%%%%
-\begin{figure}
-\centering
-\includegraphics[width=85mm]{seedBHMF_z.pdf}
-\caption{
-Seed BH mass distribution formed in different redshift ranges . 
-Each panel includes a redshift span of 10, 
-with the newly formed BHs denoted by the hatched regions, 
-and the cumulative BHs formed previously by the blue region.
-The most vigorous seed formation epoches are in redshift ranges $z\sim$ $40-30$ and $30-20$.
-Overall, the seed BH mass ranges from $\sim 10^2$ to $\gtrsim 10^5~\Msun$, 
-imprinted with the various parent halo growth histories and environmental $\vbsm$. 
-}
-\label{fig:seedmf}
-\end{figure}
 
@@
 %   \label{eq:mdot_1}
-%   \Mdot_\bullet = \frac{\lambda f(M_\bullet) M_\bullet}{\tEdd} ,
+%   \Mdot_\bullet = \frac{\lambda f(\Mbh) \Mbh}{\tEdd} ,
 % \end{equation*}
@@
   \label{eq:mdot}
-  \Mdot_\bullet = \lambda f(M_\bullet) \Mdot_\mathrm{Edd} ,
+  \Mdot_\bullet = \lambda f(\Mbh) \Mdot_\mathrm{Edd} ,
 \end{equation}
@@
 % The high mass BH should be strangulated by as it grows, 
-We define the mass dependent function of $f(M_\bullet)$ as 
+We define the mass dependent function of $f(\Mbh)$ as 
 %
 \begin{equation}
-f(M_\bullet) = \frac{2}{1+\left(M_\bullet /M_{\bullet,c} \right)^\delta}, 
+f(\Mbh) = \frac{2}{1+\left(\Mbh /M_{\bullet,c} \right)^\delta}, 
 \end{equation}
@@
 With a positive value of $\delta$, the BH growth at the high mass end is suppressed. \blue{(references, Ueda+14?s)}.
-In the limit of $\delta \ll 1$, where $f(M_\bullet) \simeq 1$ is approximated independent of $M_{\bullet,c}$, the model reproduces an exponential growth with an $e$-folding timescale of
-$\tEdd =  M_\bullet/\Mdot_{\mathrm{Edd}} \approx 45$ Myr.
+In the limit of $\delta \ll 1$, where $f(\Mbh) \simeq 1$ is approximated independent of $M_{\bullet,c}$, the model reproduces an exponential growth with an $e$-folding timescale of
+$\tEdd =  \Mbh/\Mdot_{\mathrm{Edd}} \approx 45$ Myr.
 %h independent of BH mass.
@@
 combining the semi-analytical growth model and the ERDF (see Eqs.~\ref{eq:mdot} and \ref{eq:Pl}).
-
-\blue{
-  modified afterwards; btw may I change $t_{\rm life}$ to $\tau$ in the newcommand line at the beginning?
-}
-We set a series of checkpoints with an interval of $\tlife$, 
-tracing back from $t_{\rm H}(z=6)$ to just prior than the first seed formation.
+We first set a series of checkpoints with an interval of $\tlife$, 
+tracing back from $t_{\rm H}(z=6)$ to just prior than the first seed formation time $t_1$, where $t_i$ is the $i$-th seed forming time
+as defined in \S\ref{sec:seed} ($1\leq i\leq N_{\rm tot}$).
+Note that the number of the checkpoints is given by $\lceil (t_{\rm H}-t_1)/\tau \rceil+1$, where $\lceil x\rceil \equiv {\rm min}\{n \in \mathbb{Z}~ |~x\leq n\}$.
 % we set a total number of $\Nt$ checkpoints with an interval of $\tlife$,
 % where $\Nt = \lfloor \left(t_\mathrm{H}(z=6) - t_\mathrm{H}(z_\mathrm{seed,max})\right)/ \tlife \rfloor$,
-Starting from the earliest checkpoint, the BH mass distribution evolves iteratively during each cycle,
-together with the seeds newly formed in between.
-For a given mass distribution function $\D P/\D  M_{\bullet, 0}$ at $t=t_0$, 
+
+The time evolution of the BH mass distribution is calculated from the first checkpoint to $t_{\rm H}(z=6)$ by adding newly-forming seed BHs
+and taking into account growth of existing BHs via mass accretion.
+%every by evolves iteratively during each cycle,together with the seeds newly formed in between.
+For a given mass distribution function $\D P/\D  M_{\bullet, 0}$ at a checkpoint of $t=t_0$, 
 we give its evolution at $t=t_0+\Delta t$ as
@@
   \label{eq:dpdm}
-  \frac{\D P}{\D M_\bullet} = \int
+  \frac{\D P}{\D \Mbh} = \int
    \frac{\D P}{\D \ln \lambda}\Big|_{\lambda_\ast} \cdot
-   \frac{\D \ln \lambda_\ast}{\D  M_\bullet}\Big|_{\Delta t, M_{\bullet,0}} \cdot
+   \frac{\D \ln \lambda_\ast}{\D  \Mbh}\Big|_{\Delta t, M_{\bullet,0}} \cdot
    %_{M, M_\mathrm{i},\Delta t, \delta}
@@
 %
-where $\lambda_\ast$ is the Eddington ratio required for a BH with $M_{\bullet,0}$ to grow up to $M_{\bullet}$ within $\Delta t$
+where $\lambda_\ast$ is the Eddington ratio required for a BH with $M_{\bullet,0}$ to grow up to $\Mbh$ within $\Delta t$
 and is calculated analytically from Eq.~(\ref{eq:mi2m}) by
@@
 \frac{2 \lambda_\ast \Delta t}{\tEdd}=
-  \ln \left(\frac{M_\bullet} {M_{\bullet,i}}\right) + \frac{1}{\delta} 
-  \left[ \left(\frac{M_\bullet}{M_{\bullet,c}}\right)^\delta - \left(\frac{M_{\bullet, 0}}{M_{\bullet,c}}\right)^\delta \right],
+  \ln \left(\frac{\Mbh} {M_{\bullet,i}}\right) + \frac{1}{\delta} 
+  \left[ \left(\frac{\Mbh}{M_{\bullet,c}}\right)^\delta - \left(\frac{M_{\bullet, 0}}{M_{\bullet,c}}\right)^\delta \right],
 \end{equation}
 %
-with the derivative of ($\D \ln \lambda_\ast / \D  M_\bullet )|_{\Delta t, M_{\bullet,0}}$ also determined.
-Specifically $\Delta t = \tlife$ is set for the BH mass distribution iteration from the latest checkpoint, 
-and for a seed $i$ formed at $t_{\rm i}$ during this cycle, 
-we adopt $\Delta t = t-t_{\rm i}$, and $\D P^{\rm seed}_{\rm i}/ \D M_{\bullet}$ as the initial mass distribution.
+with the derivative of ($\D \ln \lambda_\ast / \D  \Mbh )|_{\Delta t, M_{\bullet,0}}$ also determined.
+For existing BHs formed prior to this checkpoint, we calculate the evolution of the mass distribution by setting $\Delta t = \tlife$.
+% is set for the BH mass distribution iteration from the latest checkpoint, 
+For a seed BH formed during this cycle (i.e., $t_0\leq t_k < t_0+\tlife$), 
+we evolve $\D P^{\rm seed}_k/\D \Mbh$ by setting $\Delta t = t_0+\tlife -t_k$ and add it to the mass distribution 
+of the existing BHs at $t=t_0+\tlife$.
+%adopt $\Delta t = t-t_k$, and $\D P^{\rm seed}_{\rm i}/ \D \Mbh$ as the initial mass distribution.
 This procedure is illustrated schematically in Fig.~\ref{fig:scheme}. 
@@
 % by setting to $\Delta t = \tlife$ until $z=6$.
-Combining the number density contribution from all the parent halos weighted by environmental $\vbsm$ fraction, 
-the BHMF is thus written as
+Combining the PDF and number density normalization, the BHMF is given by
+%
 %%%%%%%
@@
 \begin{equation}
-  \Phi_{M_\bullet} 
-  =\sum_{\Mh, \vbsm} n_{\Mh} f_{\vbsm} {\fseed} \cdot \frac{\D P}{\D \log M_\bullet}\Big|_{\Mh, \vbsm}.
+  \Phi_{\Mbh} 
+  =\sum_{\Mh, \vbsm} n_{\Mh} f_{\vbsm} {\fseed} \cdot \frac{\D P}{\D \log \Mbh}\Big|_{\Mh, \vbsm}.
  \end{equation}
 
-We note that setting discrete mass bins to resemble the integration in the calculation above, 
-we ensure the convergence of the BHMF produced by increasing the number of mass bins to 800 log evenly across $10^2-10^{12}~\Msun$. 
-Our results of $\Phi_{M_\bullet}$ are consistent with that from directly generating random $\lambda$ 
-following Eq.~(\ref{eq:Pl}) in each cycle of BH growth. 
-Remarkably, we avoid the fluctuations in drawing random samples following the ERDF 
-and extend to massive (luminous) end in the BHMF (QLF) in a numerically efficient way.
+To perform the integration and follow the time evolution of the mass function, we set up 
+logarithmically spaced mass grids at $10^2 \leq \Mbh /\Msun \leq 10^{12}$.
+The number of the grid points is set to $N_{\rm bin}=800$, so that the convergence of the numerical result is ensured.
+%
+%We note that setting discrete mass bins to resemble the integration in the calculation above, 
+%we ensure the convergence of the BHMF produced by increasing the number of mass bins to 800 log evenly across $10^2-10^{12}~\Msun$. 
+Our result of $\Phi_{\Mbh}$ is consistent with that obtained from the direct sampling method, where 
+we generate $10^7$ BH samples whose initial mass and the Eddington ratio in each cycle are assigned
+and reconstruct the BHMF at $z=6$ by collecting the $10^7$ samples.
+%Our results of $\Phi_{\Mbh}$ are consistent with that from directly generating random $\lambda$ 
+%following Eq.~(\ref{eq:Pl}) in each cycle of BH growth. 
+%Remarkably, 
+Our method reduces the statistical errors seen in the direct sampling method 
+and thus allows us to extend the BHMF and QLF to the higher mass and brighter end
+in a reasonable computational time.
 
@@
 following \citet{2014ApJ...786..104U}.
-An alternative fitting of $\fobsc$ proposed by \citet{2014MNRAS.437.3550M} from *** (different sample?) is 
+An alternative fitting of $\fobsc$ proposed by \citet{2014MNRAS.437.3550M} from *** \blue{(different sample?)} is 
 \begin{equation*}
@@
 we fit the parameters using this prescription and discuss the sensitivity of results to $\fobsc$.
-
-% The obscuration fraction is $\simeq 0.8$, $0.5$, $0.3$ at $\Muv$ = $-20$, $-24$, $-28$ mag. 
+% wli: add more!
+
 %An alternative form proposed by \citet{2014MNRAS.437.3550M} shows a similar dependence of $\fobsc$ with the luminosity,
@@
 \frac{\D \ln \tilde{\lambda}}{\D \Muv} \cdot
- \Phi_{M_\bullet} \D \log M_\bullet,
+ \Phi_{\Mbh} \D \log \Mbh,
 \end{equation}
 %
-where the values of $\tilde{\lambda}=\lambda(\Muv, M_\bullet)$ and $\D \ln \tilde{\lambda}/\D \Muv$ are calculated analytically from Eq.~(\ref{eq:M1450}).
+where the values of $\tilde{\lambda}=\lambda(\Muv, \Mbh)$ and $\D \ln \tilde{\lambda}/\D \Muv$ are calculated analytically from Eq.~(\ref{eq:M1450}).
 %
@@
 The parameter of $\delta$ that characterizes a non-exponential BH growth 
-is constrained at $\log \delta$ from $-4$ to $-0.3$ \red{KI: add a footnote, explaining why not $\delta$ but $\log \delta$?}.
+is constrained at $\log \delta$ from $-4$ to $-0.3$ 
+\footnote[2]{ We first set uniform prior $0\leq \delta \leq 1$, 
+and find the posterior distribution assembles to $\delta \lesssim 0.1$.
+We then switch to impose the $\log \delta$ prior to improve the fitting performance at small $\delta$ values.
+}, 
+\red{KI: add a footnote, explaining why not $\delta$ but $\log \delta$?}.
 %slightly suppressing the growth in the high mass end. 
@@
 %extracted from the virial BH mass among $\sim$ 20 quasars at $z\approx$ 6. 
-Although the BHMF spans over $10^7 < M_\bullet/\Msun <10^{10}$, the best constraint is given around 
-$M_\bullet \simeq 10^{8.5}~\Msun$
+Although the BHMF spans over $10^7 < \Mbh/\Msun <10^{10}$, the best constraint is given around 
+$\Mbh \simeq 10^{8.5}~\Msun$
 and thus the statistical error size becomes larger both at the lower and higher mass range.
 We set up 10 logarithmically spaced mass bins and adopt errors with sizes increasing quadratically as 
-$\Phi_{M_\bullet}^{\rm err} = \pm \{0.2 +   [\log (M_\bullet/10^{8.5}~\Msun)]^2/3 \}~{\rm dex}$,
+$\Phi_{\Mbh}^{\rm err} = \pm \{0.2 +   [\log (\Mbh/10^{8.5}~\Msun)]^2/3 \}~{\rm dex}$,
 covering the same mass range as in their bootstrap resamples (see Figure 8 of W10). 
@@
 where $\Phi^{\rm mod}_{i,j}$ and $\Phi^{\rm obs}_{i,j}$ represent the modeled and observational value 
-on the \textit{i-}th BHMF ($j=M_\bullet$) and QLF ($j=\Muv$) bin, and $\Phi^{\rm err}_{i,j}$ is the corresponding error.
+on the \textit{i-}th BHMF ($j=\Mbh$) and QLF ($j=\Muv$) bin, and $\Phi^{\rm err}_{i,j}$ is the corresponding error.
 Adopting 10 mass bins and 12 magnitude bins, we treat the errors from comparison both in the BHMF and QLF
@@
 $(\lambda_0,\alpha) = (0.89,0.12)$ and $(0.87,0.20)$ for $\fseed=0.01$ and $0.1$, respectively.
-With those values, the number fraction of BHs growing with Eddington ratios above $\lambda_0$ is
-estimated as $P(>\lambda_0)=***$.
+With those values, the number fraction of BHs growing with Eddington ratios above unity is
+estimated as $P(>1)=***$.
 Thus, nearly ***\% of BHs are required to grow in mass rapidly to be SMBHs by $z\simeq 6$,
@@
 in the model would differ from those in observations.
-On the other hand, the power-law index of $\alpha$ in the ERDF tends to increases as the seeding fraction decreases,
+On the other hand, the power-law index of $\alpha$ in the ERDF tends to increase as the seeding fraction decreases,
 indicating that the number of inactive BHs with $\lambda \ll \lambda_0$ is reduced.
@@
 We note that \citetalias{2010AJ....140..546W} constructed the BHMF using quasar samples with 
-$10^8~\Msun \lesssim M_\bullet \lesssim 3\times 10^9~\Msun$.
+$10^8~\Msun \lesssim \Mbh \lesssim 3\times 10^9~\Msun$.
 In the high-mass regime, our fitting result nicely agrees to that in \citetalias{2010AJ....140..546W}.
@@
 
+%%%%%%%
+%    Fig. 
+%%%%%%%
+\begin{figure*}
+\centering
+\includegraphics[width=160mm]{BHMF_rhoz.png}
+\caption{
+Left panel: BHMF at $z$ from 6 to 10. The solid lines denote modeled BHMF produced by the best-fit parameters 
+and the shaded regions are the one sigma spread. 
+Right panel: the mass density of BHs with $\Mbh > 10^7~\Msun$, integrated from the BHMF in the left panel.
+}
+\label{fig:BHMF_rhoz}
+\end{figure*}
+
+%%%%%%%
+%    Fig. 
+%%%%%%%
+\begin{figure*}
+\centering
+\includegraphics[width=160mm]{QLF_rhoz.png}
+\caption{
+Left panel: QLF at $z$ from 6 to 10. The solid lines denote modeled QLF produced by the best-fit parameters 
+and the shaded regions are the one sigma spread. 
+Right panel: the cumulative number density of quasars with $\Muv <-26$, integrated from the QLF in the left panel.
+}
+\label{fig:QLF_rhoz}
+\end{figure*}
+
+Constrained by $z\sim 6$ observations, 
+the best-fit model from the MCMC realizations enables us to probe the statistical BH evolution at higher redshifts.
+As a fiducial case, we take the best-fit parameters of BH growth for $\fseed=$ 0.01, 
+where $\tlife=18.76$ Myr, $\delta=0.055$, $\lambda_0=0.87$, and $\alpha=0.20$.
+We apply the result to construct BHMF and QLF at higher redshifts 
+and produce implications to high-$z$ observations in the future.
+
+The best-fit modeled BHMFs with 1-$\sigma$ scatter at redshifts $z$ from 6 to 10 is shown in  Fig.~\ref{fig:BHMF_rhoz}.
+The number density of BHs with $\Mbh=10^7~\Msun$ emerging from high redshifts increase by a factor of $\sim 4$ per unit redshift.
+The mass density of BHs with $\Mbh \gtrsim 10^7~\Msun$ is integrated by the BHMF as
+\begin{equation}
+  \rho_\bullet(z)=\int_{10^7~\Msun}^{\infty} \Phi_{\Mbh} (z) \Mbh \D \log \Mbh, 
+\end{equation}
+as a function of redshift.
+Thus we predict the early assembly of BH mass in the galactic nuclei, 
+and the steep decline toward higher redshifts can be described by a fitting formula $\rho_\bullet(z)\propto 10^{k_{\rm M}(z-6)}$,
+with $k_{\rm M}\approx -0.8$. 
+The exponential dependency on redshift is reminiscent of the cosmic galaxy mass growth 
+$M_{\star} \propto e^{-B z}$, as a consequnce of the assumption of fixed galaxy to DM halo mass ratio, 
+and the growth rate of DM halos in the extended Press-Schechter formalism 
+$\D \left(\ln \Mh \right) / \D t \propto(1+z)^{5/2}$ \citep{2008MNRAS.383..615N}.
+Our results suggest that the cumulative massive BH mass density growing in galactic nuclei also follows 
+an exponential evolution with redshift, 
+which is statistically in agreement with the host halo and galaxy growth.
+
+On the other hand, the QLFs at $z$ from 6 to 10 are also deduced from the BH growth model (see Fig.~\ref{fig:QLF_rhoz}).
+The model QLFs we propose give interesting prediction and will be further constrained by higher redshift quasar observations.
+The luminous quasar ($\Muv <-26$) density evolution with redshift is shown in Fig.~\ref{fig:QLF_rhoz}, and fitted with 
+$n(z,\Muv<-26)\propto 10^{k_{\rm L}z}$, where $k_{\rm L}\approx -0.95$. 
+A rapid decline in luminous quasar population toward high redshift is firstly proposed by \citet{2001AJ....122.2833F}, 
+with $k_{\rm L}= -0.47$ in their analysis of $z$ from 3 to 6 quasar sample. 
+A steeper decline in higher redshifts is suggested in recent studies of $z\gtrsim 6$ quasars, 
+e.g. \citet{2019ApJ...884...30W} measure the spatial density of $z\sim 6.7$ quasars, 
+and fit the parameter $k_{\rm L}=-0.78$ by connecting the $z\sim 6$ result from \citet{2016ApJ...833..222J}.
+Studies with the assumption of the close correlation of DM halo mass with central BH mass, and a constant Eddington ratio 
+interprete this rapid decline by the rarity of massive halos toward higher redshifts \citep[e.g.,][]{2010ApJ...718..231S}, 
+while another entangling factor is the radiative efficiency in converting BH growth rate to luminosity. 
+In this work we argue that the episodical BH accretion with bursts and quiescent phases is 
+important in matching the $z\sim 6$ quasar observations, 
+and this calls consideration of the more realistic BH-galaxy coevolution in understanding the observable AGN properties.
+
 \section{Discussion}
@@
 
-The best-fit model from the MCMC realizations enables us to generate a sample of BH evolutionary tracks starting from BH seeds.
-We take $\fseed=$ 0.01 as a fiducial case, where the best-fit parameters for BH growth are 
-$\tlife=18.76$ Myr, $\delta=0.055$, $\lambda_0=0.87$, and $\alpha=0.20$.
-We apply the result to construction individual evolutionary tracks of BHs and give some implications to high-$z$ quasar observations.
-
+From the BH growth model described in \S~\ref{sec:MF}, we further explore individual BH evolutionary tracks starting from the BH seeds.
+% We take $\fseed=$ 0.01 as a fiducial case, where the best-fit parameters for BH growth are 
+% $\tlife=18.76$ Myr, $\delta=0.055$, $\lambda_0=0.87$, and $\alpha=0.20$.
+% We apply the result to construct individual evolutionary tracks of BHs and produce implications to high-$z$ quasar observations.
 % We generate a 10$^7$ sample of BHs at $z=$ 35, with seed mass $M_\star = 1.5\times 10^3~\Msun$, 
@@
 % motivated by the properties of typical BH seeds (with median formation redshift and median mass).
-We generate a sample of 10$^7$ BH seeds, whose formation time and mass distribution at birth follow the model described in \S~\ref{sec:seed}. 
+We generate a sample of 10$^7$ BHs, whose formation time and mass distribution at birth follow the model described in \S~\ref{sec:seed}. 
 To growth the individual BHs, we assign an Eddington ratio $\lambda$ in every interval $\tlife$ until $z=6$,
@@
 Tracing the BH growth curve back to $z=30$ with the Eddington ratio observed at $z=6$ (dotted curves),
-the extrapolated mass of those sub-Eddington BHs at $z=6$ is as massive as $M_\bullet \gg 10^5~\Msun$ and is 
+the extrapolated mass of those sub-Eddington BHs at $z=6$ is as massive as $\Mbh \gg 10^5~\Msun$ and is 
 substantially higher than the mass range for seed BHs.
@@
 For comparison, we show the mass growth tracks assuming a constant Eddington ratio of $\lambda=1$, 
-where the extrapolated seed mass is $M_\bullet \sim 10^2~\Msun$.
+where the extrapolated seed mass is $\Mbh \sim 10^2~\Msun$.
 %Both treatments of the constant $\lambda$ lead to BH seed masses extrapolation that deviate from the initial seeds we plant. 

### 2022-07-21 ms.tex
Sec. 3.2 & fig:tau added

@@
 \newcommand{\fobsc}{f_\mathrm{obsc}}
-\newcommand{\tEdd}{t_\mathrm{Edd}}
 \newcommand{\Nt}{N_\mathrm{t}}
@@
 where $c_{\rm s}$ is the thermal sound speed, $v_{\rm tur}$ is the turbulent velocity of gas (i.e., the specific kinetic energy accumulated through halo mergers), and
-the coefficient is set to $\alpha_0=1$\footnote{The value of $\alpha_0=1.0$ is motivated by cosmological simulations of massive primordial stars
+the coefficient is set to $\alpha_0=1$\footnote[1]{The value of $\alpha_0=1.0$ is motivated by cosmological simulations of massive primordial stars
 under fast streaming velocities \citep{2017Sci...357.1375H,2019MNRAS.484.3510S}.
@@
 The probability of a BH with mass $M_0$ grow to $M$ after $\Delta t=\tau$ is drew from the 
-ERDF following Eq.~\ref{eq:Pl}. 
+ERDF following Eq.~(\ref{eq:Pl}). 
 For a newly formed seed BH $M_{\rm i}$, the probability distribution function of BH mass is a delta function, 
@@
 \subsection{BH mass growth}
+\label{sec:model}
 % The BH accretion at high redshifts is probed only by snapshots, in their most luminous quasar phase. 
@@
 %   \label{eq:mdot_1}
-%   \Mdot_\bullet = \frac{\lambda f(\Mbh) \Mbh}{\tEdd} ,
+%   \Mdot_\bullet = \frac{\lambda f(\Mbh) \Mbh}{t_{\rm S}} ,
 % \end{equation*}
@@
 \end{equation}
-% where $\tEdd = \eta_0  M c^2/L_{\mathrm{Edd}} \approx 45$ Myr,
+% where $t_{\rm S} = \eta_0  M c^2/L_{\mathrm{Edd}} \approx 45$ Myr,
 where $\lambda \equiv L/L_\mathrm{Edd}$ is the Eddington ratio,
@@
 In the limit of $\delta \ll 1$, where $f(\Mbh) \simeq 1$ is approximated independent of $M_{\bullet,c}$, the model reproduces an exponential growth with an $e$-folding timescale of
-$\tEdd =  \Mbh/\Mdot_{\mathrm{Edd}} \approx 45$ Myr.
+$t_{\rm S} =  \Mbh/\Mdot_{\mathrm{Edd}} \approx 45$ Myr, well known as the Salpeter timescale \citep{1964ApJ...140..796S}.
 %h independent of BH mass.
 % In \S~\ref{sec:fitting}, $\delta$ turns out to be close to 0, indicating an exponential grow manner independent of BH mass.
-%Then $\tEdd =  M/\Mdot_{\mathrm{Edd}} \approx 45$ Myr is the Salpeter $e$-folding timescale \citep{1964ApJ...140..796S}.
+%Then $t_{\rm S} =  M/\Mdot_{\mathrm{Edd}} \approx 45$ Myr is the Salpeter $e$-folding timescale \citep{1964ApJ...140..796S}.
 
@@
   \label{eq:mi2m}
-\frac{2 \lambda_\ast \Delta t}{\tEdd}=
+\frac{2 \lambda_\ast \Delta t}{t_{\rm S}}=
   \ln \left(\frac{\Mbh} {M_{\bullet,i}}\right) + \frac{1}{\delta} 
@@
 and the uncertainties would affect our analyses for fainter quasars.
-%with complex convertions between the probes in different observational bands,
+%with complex conversions between the probes in different observational bands,
 % optical and X-ray observations, 
@@
 This suggests that accreting seed BHs vary their growth speeds (i.e., the Eddington ratio) 
-$\sim 30$ times on average, over the cosmic time of $t_{\rm H}\simeq 800$ Myr at $z\simeq 6$.
+$\sim 30$ times on average, toward the cosmic time of $t_{\rm H}\gtrsim 900$ Myr at $z\simeq 6$.
 The timescale of $\tlife$ also gives a lower bound of the quasar lifetimes of $t_{\rm Q}\sim 1-10$ Myr, 
@@
 $(\lambda_0,\alpha) = (0.89,0.12)$ and $(0.87,0.20)$ for $\fseed=0.01$ and $0.1$, respectively.
-With those values, the number fraction of BHs growing with Eddington ratios above unity is
-estimated as $P(>1)=***$.
-Thus, nearly ***\% of BHs are required to grow in mass rapidly to be SMBHs by $z\simeq 6$,
-consistent with a general picture for the early assembly of SMBHs (ref, Xiaohui? Willott? SDSS papers?)
+\blue{\\This paragraph is revised hereafter.}
+With those values, the number fraction of super-Eddington accreting BHs is
+estimated as $P(\lambda>1)=0.064$ and 0.075, respectively. 
+The small discrepancy is enlarged with the multiple cycles of assigning $\lambda$ to BH growth, 
+and increase the fraction of the super-Eddington phase for smaller $\fseed$. 
+Thus for different $\fseed$ values, a similar number density of BHs which rapidly grow to be SMBHs by $z\simeq 6$ is produced, 
+consistent with a general picture for the early assembly of SMBHs 
+\citep[e.g.,][]{2006NewAR..50..665F,2008AJ....135.1057J,2010AJ....139..906W}.
 The characteristic Eddington ratio needs to be close to unity, otherwise the highest luminosity and BH mass
@@
 On the other hand, the power-law index of $\alpha$ in the ERDF tends to increase as the seeding fraction decreases,
-indicating that the number of inactive BHs with $\lambda \ll \lambda_0$ is reduced.
-\red{KI: can you check if $\fseed \cdot P(>\lambda_0)$ is roughly constant?}
-Thus, with lower seeding fractions, a larger number of active BHs with $\lambda \sim \lambda_0$ 
-participate in the high-$z$ quasar assembly and reproduce the bulk properties of the BHMF and QLF.
-%hence the best-fit $\alpha$ increases and higher accretion rate is realized from the Schechter shape with higher $\alpha$. 
-% We expect more complete observations to better constrain the parameter priors in the model fitting.
+indicating that fraction of active BHs with $\lambda \gtrsim 1$ is elevated. 
+Thus, with lower seeding fractions, the high-$z$ quasar assembly spends a larger fraction of time in active phases 
+and reproduce the bulk properties of the BHMF and QLF.
 
@@
 because the progenitors of $z=6$ BHs with $10^{7-8}~\Msun$ (or similarly, 
-$-22~{\rm mag} \lesssim \Muv \lesssim -24~{\rm mag}$) were less massive seed BHs with $\sim ***~\Msun$,
+$-22~{\rm mag} \lesssim \Muv \lesssim -24~{\rm mag}$) were less massive seed BHs with $\sim 10^4~\Msun$,
 which is closer to the peak of the seed mass distribution (see Fig.~\ref{fig:seedmf}).
@@
 
+As described in \S~\ref{sec:model}, we introduce the parameter $\tau$ as a typical timescale 
+for individual duration of quasar accretion activities, i.e. in each cycle $\tlife$ 
+we assign Eddington ratio $\lambda$ following the parameterized ERDF for all BHs.
+The extraction of this timescale essentially modifys the ERDF in the whole BH growth history, 
+because the multiple sampling of $\lambda$ reduces the possibility of a BH accreting on average with $\lambda \gtrsim \lambda_0$ 
+than single sampling. 
+However at any time during growth, the ERDF of the BH population remains the same as at $z\sim$ 6, 
+therefore we ensure treating all cosmic time equally.
+
+% tau极端小，则非常小的lambda，不能解释 （且delta func？ 有必要说或是放在后面讨论？）
+
+Hereafter we demonstrate the role of $\tlife$ on shaping the BHMF evolution and the consequent QLF. 
+In the left panel of Fig.~\ref{fig:tau}, the BHMF at $z=6$ is calculated from setting $\tlife=$ 10, 18, and 50 Myr, 
+and keeping the other parameters as the best-fit values for the $\fseed=0.01$ case.
+While $\tlife \approx$ 18 Myr is the best-fit value, resulting in the BHMF which nicely matches the results in \citetalias{2010AJ....140..546W}, 
+the other two cases demonstrate the sensitivity of the $\tlife$ value in producing the bulk of massive BHs 
+and the slope in the high mass tail. 
+For $\tlife=$ 10 Myr, the number of Eddington ratio assignment cycles increases to $\sim$ 80 
+from $\sim$ 40 with the best-fit $\tlife$ value. 
+Thus the possibility of continuous high Eddington ratio accretion along the growth is lower, 
+suppressing the growth of massive BHs at $M_\bullet \gtrsim 10^8~\Msun$. 
+On the other hand, for $\tlife=$ 50 Myr, with $\sim$ 16 times of multiple Eddington ratio assignment,
+on average high values of $\lambda\gtrsim \lambda_0$ is non-negligibly realized in the BHMF evolution. 
+Therefore in the high mass end of BHMF at $z=$ 6, the BH population is significantly overproduced than the constraints from observation.
+
+The QLF at $z=6$ is shown in the right panel of Fig.~\ref{fig:tau}. 
+In the conversion from BHMF to QLF, the ERDF is the same for different $\tlife$ values, 
+following the $P(\lambda)$ in Eq.~(\ref{eq:Pl}) with $\lambda_0=0.87$ and a=0.20. 
+Thus the deviation from the observed QLF in \citetalias{2018ApJ...869..150M}  shows similar trends as in the BHMF. 
+i.e., $\tlife$ values lower (higher) than the best-fit one leads to the under(over)-production of the luminous quasar population.
+We notice that the best-fit value of $\tlife$ favors a moderate fraction of $t_{\rm S}$, 
+which regulates the BH growth and reproduces the quasar observation together with the other best-fit parameters in their reasonable ranges.
+
+%%%%%%%
+%    Fig. 
+%%%%%%%
+\begin{figure*}
+\centering
+\includegraphics[width=160mm]{tau.png}
+\caption{
+Left panel: BHMF at $z=$ 6 calculated with $\tlife= $. The solid lines denote modeled BHMF produced by the best-fit parameters 
+and the shaded regions are the one sigma spread. 
+Right panel: the mass density of BHs with $\Mbh > 10^7~\Msun$, integrated from the BHMF in the left panel.
+}
+\label{fig:tau}
+\end{figure*}
+
 \vspace{2mm}
 \subsection{Cosmological evolution of BHMF and QLF}\label{sec:cosm}
-\red{KI: shall we discuss the $z$-dependence of the BHMF and QLF?
-Don't need to repeat calculations. Just using the same parameters with 1sigma scatter?
-Showing $\rho_{\bullet}(z)$ in $\Msun ~ {\rm Mpc}^{-3}$, which is the integrant of BHMF, would be interesting}
+% \red{KI: shall we discuss the $z$-dependence of the BHMF and QLF?
+% Don't need to repeat calculations. Just using the same parameters with 1sigma scatter?
+% Showing $\rho_{\bullet}(z)$ in $\Msun ~ {\rm Mpc}^{-3}$, which is the integrant of BHMF, would be interesting}
 
@@
 
-Constrained by $z\sim 6$ observations, 
-the best-fit model from the MCMC realizations enables us to probe the statistical BH evolution at higher redshifts.
+\begin{table}
+\renewcommand\thetable{1} %! fix indexing
+\caption{$\rho_\bullet(z)$ Evolution Parameters}
+\begin{center}
+% \tablenum{1}
+\begin{tabular}{l c r}
+\hline
+$M_{\rm min}$ & $\log \rho_{\bullet,0}$ & $k_{\rm M}$ ~~~ \\ 
+\hline 
+\hline
+10$^7$  &  $-5.91\pm 0.28$  &  $-0.58 \pm 0.21$  \\
+10$^8$  &  $-6.93\pm 0.47$  &  $-0.78 \pm 0.31$  \\
+% 10$^9$  &  $-8.30_{-0.47}^{+0.47}$  & $-1.04_{-0.58}^{+0.54}$ \\
+10$^9$  &  $-8.30\pm 0.47$  &  $-1.04 \pm 0.58$ \\
+\hline 
+\end{tabular}
+\label{tab:MFz}
+\end{center}
+\end{table}
+
+Based on the constraint from $z\sim 6$ quasar observations, the best-fit model from the MCMC realizations enables
+us to probe the statistical BH evolution at higher redshifts.
 As a fiducial case, we take the best-fit parameters of BH growth for $\fseed=$ 0.01,
 where $\tlife=18.76$ Myr, $\delta=0.055$, $\lambda_0=0.87$, and $\alpha=0.20$.
-We apply the result to construct BHMF and QLF at higher redshifts 
-and produce implications to high-$z$ observations in the future.
-
-The best-fit modeled BHMFs with 1-$\sigma$ scatter at redshifts $z$ from 6 to 10 is shown in  Fig.~\ref{fig:BHMF_rhoz}.
-The number density of BHs with $\Mbh=10^7~\Msun$ emerging from high redshifts increase by a factor of $\sim 4$ per unit redshift.
-The mass density of BHs with $\Mbh \gtrsim 10^7~\Msun$ is integrated by the BHMF as
-\begin{equation}
-  \rho_\bullet(z)=\int_{10^7~\Msun}^{\infty} \Phi_{\Mbh} (z) \Mbh \D \log \Mbh, 
-\end{equation}
-as a function of redshift.
-Thus we predict the early assembly of BH mass in the galactic nuclei, 
-and the steep decline toward higher redshifts can be described by a fitting formula $\rho_\bullet(z)\propto 10^{k_{\rm M}(z-6)}$,
-with $k_{\rm M}\approx -0.8$. 
-The exponential dependency on redshift is reminiscent of the cosmic galaxy mass growth 
-$M_{\star} \propto e^{-B z}$, as a consequnce of the assumption of fixed galaxy to DM halo mass ratio, 
-and the growth rate of DM halos in the extended Press-Schechter formalism 
-$\D \left(\ln \Mh \right) / \D t \propto(1+z)^{5/2}$ \citep{2008MNRAS.383..615N}.
-Our results suggest that the cumulative massive BH mass density growing in galactic nuclei also follows 
-an exponential evolution with redshift, 
-which is statistically in agreement with the host halo and galaxy growth.
-
-On the other hand, the QLFs at $z$ from 6 to 10 are also deduced from the BH growth model (see Fig.~\ref{fig:QLF_rhoz}).
-The model QLFs we propose give interesting prediction and will be further constrained by higher redshift quasar observations.
-The luminous quasar ($\Muv <-26$) density evolution with redshift is shown in Fig.~\ref{fig:QLF_rhoz}, and fitted with 
-$n(z,\Muv<-26)\propto 10^{k_{\rm L}z}$, where $k_{\rm L}\approx -0.95$. 
-A rapid decline in luminous quasar population toward high redshift is firstly proposed by \citet{2001AJ....122.2833F}, 
-with $k_{\rm L}= -0.47$ in their analysis of $z$ from 3 to 6 quasar sample. 
-A steeper decline in higher redshifts is suggested in recent studies of $z\gtrsim 6$ quasars, 
-e.g. \citet{2019ApJ...884...30W} measure the spatial density of $z\sim 6.7$ quasars, 
-and fit the parameter $k_{\rm L}=-0.78$ by connecting the $z\sim 6$ result from \citet{2016ApJ...833..222J}.
-Studies with the assumption of the close correlation of DM halo mass with central BH mass, and a constant Eddington ratio 
-interprete this rapid decline by the rarity of massive halos toward higher redshifts \citep[e.g.,][]{2010ApJ...718..231S}, 
-while another entangling factor is the radiative efficiency in converting BH growth rate to luminosity. 
-In this work we argue that the episodical BH accretion with bursts and quiescent phases is 
-important in matching the $z\sim 6$ quasar observations, 
-and this calls consideration of the more realistic BH-galaxy coevolution in understanding the observable AGN properties.
+We apply the result to construction of BHMFs and QLFs at higher redshifts and give implications for
+the future explorations of high-$z$ quasars.
+In the left panel of Fig.~\ref{fig:BHMF_rhoz}, we show the BHMFs at five different redshifts of $z=6-10$.
+For all the redshifts, the BHMFs can be characterized with a double power-law function, similar to lower-$z$ quasar populations.
+From higher to lower redshifts, the number density of BHs heavier than $M_\bullet = 10^7~\Msun$ increases
+and the high-mass tail of the distribution is extended owing to efficient growth of the most massive BH population.
+%The number density of BHs with $\Mbh=10^7~\Msun$ emerging from high redshifts increase by a factor of $\sim 4$ per unit redshift.
+In the right panel of Fig.~\ref{fig:BHMF_rhoz}, we also present the cumulative mass density of BHs with $\Mbh \geq M_{\rm min}$ in a comoving volume,
+defined by the integration of the BHMF as
+%
+\begin{equation}
+ \rho_\bullet(z)=\int_{M_{\rm min}}^{\infty} \Phi_{\Mbh} (z) \Mbh \D \log \Mbh,
+\end{equation}
+%
+%as a function of redshift.
+where we set the minimum mass to $M_{\rm min}=10^7$, $10^8$, and $10^9~\Msun$.
+This result shows that the early BH assembly takes place rapidly and the redshift-dependence can be approximated by
+%
+\begin{equation}
+\rho_\bullet(z)
+%= \rho_{\bullet 0}\cdot e^{k_{\rm M}(z-6)}
+\simeq \rho_{\bullet,0}~ 10^{k_{\rm M}(z-6)},
+\end{equation}
+%
+where the fitted values of $\rho_{\bullet,0}$ and $k_{\rm M}$ are shown in Table.~\ref{tab:MFz}.
+On the other hand, the stellar mass density of the quasar progenitor halos is calculated as
+%
+\begin{equation}
+\rho_{\star}(z)
+\simeq f_\star n_{\Mh} M_h~ 10^{k_{\rm h}(z-6)},
+\end{equation}
+%
+where $f_\star(\equiv M_\star/\Mh)$ is the mass ratio of the galaxy stellar mass to the DM halo mass and
+$n_{\Mh}$ is the number density of quasar host halos with $\Mh$ in a comoving volume at $z=6$; namely,
+the value of $n_{\Mh}\Mh \simeq (6.2-99)\times 10^6~\Msun~{\rm Mpc}^{-3}$.
+We here express the mass growth of the DM halo with a functional form of $\propto 10^{k_{\rm h} z}$,
+which nicely reproduces the mass growth of DM halos
+\citep[e.g.,][]{2002ApJ...568...52W,2008MNRAS.383..615N,2008MNRAS.388.1792N,2010MNRAS.406.2267F}
+\footnote[3]{
+In fact, this redshift dependence leads to a halo-mass growth rate of $\D \left(\ln \Mh \right) / \D t \propto(1+z)^{5/2}$,
+which has been understood based on the extended Press-Schechter formalism and also derived by
+a fit to merger trees from cosmological N-body simulations \citep{2013MNRAS.435..999D}.}.
+% The redshift dependence yields the cosmic BH growth rate in the matter-dominated universe
+% as $\dot{\rho}_\bullet \propto \rho_\bullet (1+z)^{5/2}$ or
+
+% \begin{align}
+% \dot{\rho}_\bullet(z) & =\dot{\rho}_\bullet(z=6)\left(\frac{1+z}{7}\right)^{5/2} 10^{k_{\rm M}(z-6)}, \\
+% &\simeq *** ~\Msunyr~{\rm Mpc}^{-3} \left(\frac{1+z}{7}\right)^{5/2} e^{\bar{k}_{\rm M}(z-6)},\nonumber
+% \end{align}
+
+% where $\bar{k}_{\rm M} \equiv k_{\rm M} \ln 10 \simeq -1.84$.
+% \red{KI: I'm not sure what we discuss here... One thing is the cosmic SFR density (Madau's plot).
+% Is there something like Madau's plot but for DM halos?}
+% The exponential dependence on redshift is reminiscent of the cosmic galaxy mass growth
+% $M_{\star} \propto e^{-B z}$, as a consequnce of the assumption of fixed galaxy to DM halo mass ratio,
+% and the growth rate of DM halos in the extended Press-Schechter formalism
+% $\D \left(\ln \Mh \right) / \D t \propto(1+z)^{5/2}$ \citep{2008MNRAS.383..615N}.
+% Our results suggest that the cumulative massive BH mass density growing in galactic nuclei also follows
+% an exponential evolution with redshift,
+% which is statistically in agreement with the host halo and galaxy growth.
+The star-to-halo mass ratio is assumed to be $f_\star =0.01$ for those quasar progenitor halos at $z>6$
+% (UNIVERSEMACHINE; Behroozi et al. 2019).
+\citep[fits by code {\tt UNIVERSEMACHINE} in][]{2019MNRAS.488.3143B}.
+%https://ui.adsabs.harvard.edu/abs/2019MNRAS.488.3143B/abstract
+With those values, we estimate the cumulative stellar-to-BH mass ratio for high-$z$ quasars as
+%
+\begin{equation}
+\frac{\rho_{\star}(z)}{\rho_{\bullet}(z)}
+\simeq 2.5\times 10^{3} \left(\frac{f_\star}{0.01}\right)
+~ 10^{(k_{\rm h}-k_{\rm M})(z-6)},
+\end{equation}
+% wli now
+\red{KI: please check the value of $k_{\rm h}-k_{\rm M}$.}
+\blue{
+where $k_{\rm h} \approx -0.16 $ for the parent halo growth histories.
+}
+Therefore, at $z\sim 6$ the bulge-to-BH mass ratio $\sim O(10^3)$ for the entire BH population (i.e., low-mass BHs and low-luminosity quasars) 
+is broadly consistent with those seen in the local universe, although SMBHs observed as high-$z$ quasars
+appear to be overmassive compared to the local relation \citep{2013ApJ...773...44W,2020A&A...637A..84P} \dots.
+
+Next, we show the QLFs at different redshifts of $z=6-10$ taken from the BH growth model in the left panel of Fig.~\ref{fig:QLF_rhoz}.
+%The model QLFs we propose give interesting prediction and will be further constrained by higher redshift quasar observations.
+\red{KI: add more explanations about the QLFs. How about the detection limits of Euclid, Roman, and others?
+Also, you could compare your results with Aaron Yung's results.}
+In the right panel of Fig.~\ref{fig:QLF_rhoz}, we present the number density of luminous quasars with $\Muv <-26$ as a function of redshift.
+The evolutionary trend can be fitted as $\propto 10^{k_{\rm L}z}$, where $k_{\rm L}\approx -0.97$.
+A rapid decay of the quasar number density toward higher redshifts is found by previous studies \citep[e.g.,][]{2001AJ....122.2833F,2016ApJ...833..222J},
+which show $k_{\rm L}= -0.47$ and $-0.72$ from the analysis of quasar samples at $z\simeq 3-5$ and $z\simeq 5-6$, respectively.
+Recently, a steeper decline of luminous quasar number density toward higher redshifts is proposed by \citet{2019ApJ...884...30W},
+suggesting $k_{\rm L}=-0.78$ at $6\lesssim z \lesssim 7$.
+%a steeper decline ifts is suggested in recent studies of $z\gtrsim 6$ quasars,
+%e.g. \citet{2019ApJ...884...30W} measure the spatial density of $z\sim 6.7$ quasars,
+%and fit the parameter $k_{\rm L}=-0.78$ by connecting the $z\sim 6$ result from \citet{2016ApJ...833..222J}.
+The rapid decline toward higher redshifts is nicely characterized by the treatment of episodic natures of BH accretion with a finite value of
+$\tau ~(\simeq 20~{\rm Myr})$, in order to match the statistical properties of high-$z$ quasars.
+We also note that the tendency would be explained by the rarity of massive quasar-host halos at higher redshifts,
+non-constant radiative efficiencies that covert the BH growth rate into the luminosity, or some combination of these effects
+\citep[e.g.,][]{2010ApJ...718..231S}.
 

### 2022-07-21 ms.tex
version 0721; caption of fig:tau added

@@
 \caption{
-Left panel: BHMF at $z=$ 6 calculated with $\tlife= $. The solid lines denote modeled BHMF produced by the best-fit parameters 
-and the shaded regions are the one sigma spread. 
-Right panel: the mass density of BHs with $\Mbh > 10^7~\Msun$, integrated from the BHMF in the left panel.
+Left panel: BHMF at $z=$ 6 calculated in the $\fseed=0.01$ case, 
+with different $\tlife=$ 10, 18 (the best-fit value), and 50 Myr, respectively, 
+and other parameters are fixed to the best-fit values. 
+The blue curve denotes the BHMF constrained by the \citetalias{2010AJ....140..546W} result. 
+With lower(higher) $\tlife$ than the best-fit value, the BHMF is under(over)-produced in the high mass end.
+Right panel: QLF at $z=$ 6 calculated with the same parameters as in the left panel.
+The overlaid blue dots are from the \citetalias{2018ApJ...869..150M} $z\sim$ 6 quasar observation. 
+With $\tlife$ values different from the best-fit value, the consequent QLF show 
+similar trends of deviation from observation as in the BHMF curves.
 }

### 2022-07-22 ms.tex
intro, caption, discussion revised by k;

@@
 \section{Introduction} \label{sec:intro}
-The growth of black holes (BHs) in galactic nuclei is elegantly related to their luminous accretion phases 
+The growth of massive black holes (BHs) in galactic nuclei is elegantly related to their luminous accretion phases
 across the cosmic time \citep{1982MNRAS.200..115S,1992MNRAS.259..725S}.
-Comparing the local massive BH mass density and the integration of quasar luminosity function up to $z\sim$ 5, 
-\citet{2002MNRAS.335..965Y} demonstrate the constraints on the BH accretion history and their radiative effeciency.
-Extrapolation of such argument toward higher redshifts ($z\gtrsim$ 6) is unwarranted, 
-due to the limitation of current capabilities of observing the high-$z$ quasar population \citep{2019BAAS...51c.121F}. 
-Nevertheless, 
-% while its essence is appropriate to BH evolution of all redshifts. 
-in the era of the James Webb Space Telescope (JWST) and forthcoming facilities 
+Comparing the mass density of massive BHs in the local universe and the mass accreted onto BH inferred from
+the integration of the quasar luminosity function based on multi-wavelength observations,
+the cosmic BH accretion history and their radiative efficiency are nicely constrained \citet{2002MNRAS.335..965Y}
+\red{KI: add more references, Ueda+14, Delvecchio+14, Marconi?, and some Shankar's papers}.
+
+Extrapolation of this argument toward higher redshifts beyond $z\sim$ 6 is limited because of the current capability for
+high-$z$ quasar observations \citep{2019BAAS...51c.121F} \red{KI: you could find better reference in this Decadal Survey?}.
+Nevertheless,... \red{KI: you could say the current status of $z=6$ QLFs/BHMFs; citing Jiang+16, 18, Willott+10, HSC papers.}
+Moreover, in the era of the James Webb Space Telescope (JWST) and forthcoming facilities,
 e.g., the Roman Space Telescope (RST) and Euclid,
@@
 also help answering the intriguing questions e.g., 
-the existence of supermassive BHs in the early universe within one billion year, 
-and the establishment of BH-galaxy coevolution \citep{2012Sci...337..544V,2013ASSL..396..293H,2020ARA&A..58...27I}.
-
-Tracing back from $z\sim$ 6, BH seed formation is the starting point to shape the early evolution of the BH population.
-From Pop III star remnants ($10-10^3 ~\Msun$) to direct collapse supermassive stars (10$^4-10^5 ~\Msun$), 
-the properties of high-$z$ BH seeds are extensively modeled by simulations and semi-analytical works 
-\citep[e.g.,][Toyouchi 2022]{2001ApJ...546..635O,2002Sci...295...93A,2006ApJ...652....6Y,2011MNRAS.416.2748I,
-2012ApJ...756...93H,2013ApJ...778..178H,2014MNRAS.439.3798F,
-2014MNRAS.445L.109I,2014MNRAS.445..544S,2014MNRAS.445..107V,2020MNRAS.499.5960S}. 
-Environmental factors which modulate the Pop III star formation have been assessed, 
-including (i) external ratiation in Lyman-Werner band which photo-dissociates the major coolant $\hh$ 
-\citep{2002ApJ...569..558O,2003Natur.425..812B,2010MNRAS.402.1249S},
-(ii) baryonic streaming motion which drives the gas against gravitational collapse 
-\citep{2012MNRAS.424.1335F, 2014MNRAS.439.1092T, 2018ApJ...855...17H}
+the existence of supermassive BHs in the early universe within one billion year 
+\citep{2012Sci...337..544V,2013ASSL..396..293H,2020ARA&A..58...27I}, 
+and the establishment of BH-galaxy coevolution 
+\red{cite Wang+2013; Venemans+2017, Izumi et al. 2021, Inayoshi+2022 simulation, Habouzit+2022}.
+
+Formation of seed BHs is the starting point to characterize the early assembly of massive BH populations.
+Their formation pathway and expected mass range have been extensively investigated by numerical simulations and
+semi-analytical studies
+%From Pop III star remnants ($10-10^3 ~\Msun$) to direct collapse supermassive stars (10$^4-10^5 ~\Msun$),
+%the properties of high-$z$ BH seeds are extensively modeled by simulations and semi-analytical works
+%\citep[e.g.,][Toyouchi 2022]{2001ApJ...546..635O,2002Sci...295...93A,2006ApJ...652....6Y,2011MNRAS.416.2748I,
+%2012ApJ...756...93H,2013ApJ...778..178H,2014MNRAS.439.3798F,
+%2014MNRAS.445L.109I,2014MNRAS.445..544S,2014MNRAS.445..107V,2020MNRAS.499.5960S}.
+\red{KI: I think here we should cite more general citations: Begelman+2006; Tanaka \& Haiman 2009; Hirano+14, 15,
+Toyouchi+2022, one Natarajan+Volonteri's paper discussing the mass function, Valiante+2018, Sassano+21}
+Massive star formation episodes in the early universe is substantially modulated by external environmental effects such as
+%factors which modulate the Pop III star formation have been assessed,
+(i) H$_2$ photo-dissociating irradiation from nearby galaxies
+%irradiation in Lyman-Werner band which photo-dissociates the major coolant $\hh$
+\citep{2001ApJ...546..635O,2002ApJ...569..558O,2003Natur.425..812B,2010MNRAS.402.1249S,2014MNRAS.445..544S,2014MNRAS.445..107V}
+\red{KI: add Chon+16},
+(ii) supersonic baryonic streaming motion that delays gas collapse in halos
+\citep{2012MNRAS.424.1335F, 2014MNRAS.439.1092T, 2018ApJ...855...17H} \red{KI: add Inayoshi, Li \& Haiman 18, Schauer +17},
 and
-(iii) violent mergers of the parent dark matter halo which dynamically excite the gas 
-\citep{2003ApJ...592..645Y,2019Natur.566...85W}. 
-These factors prevail in some environments at high redshifts and facilitate massive Pop III and even supermassive star formation, 
-which contribute to the heavy seed scenario of supermassive BH formation at $z\gtrsim$ 6 
-\citep[see a review by][]{2020ARA&A..58...27I}.
+(iii) dynamical heating caused by frequent halo mergers and turbulence injection led by cold accretion flows
+\citep{2003ApJ...592..645Y, 2019Natur.566...85W} \red{KI: add Latif's Nature paper, Mayer+10 or 15}.
+Those effects keep isothermal collapse ($T\sim 8000~{\rm K}$) of massive gas at high accretion rates of $\gtrsim 0.1~\Msunyr$
+without vigorous fragmentation \citep{2014MNRAS.445L.109I} \red{KI: add Becerra+15, Latif+16}, and allow supermassive stars
+with $\sim 10^5~\Msun$ (presumably seed BHs) to form at the halo centers \red{cite Hosokawa+13, Woods+19?, Schleicher+13, Toyouchi+22}.
+Although the conditions required for heavy seed formation are thought to be too stringent to be realized in the typical regions of the early universe
+\red{cite Dijkstra+08, Ahn+09, Inayoshi \& Tanaka 15}, recent studies by Lupi+21 and Li+21 found that the heavy-seed formation
+can be accelerated in the rare, overdense regions of the universe, where non-linear galaxy clustering boosts the irradiation intensity
+and the frequency of halo mergers.
+%These factors prevail in some environments at high redshifts and facilitate massive Pop III and even supermassive star formation,
+%which contribute to the heavy seed scenario of supermassive BH formation at $z\gtrsim$ 6
+%\citep[see a review by][]{2020ARA&A..58...27I}.
+
+\red{Introduction of previous studies on QLFs for high-$z$ populations. mention Yung's paper, Ricarte \& Natarajan paper, recent Finkelstein's paper?
+Also, I remember one paper of our former postdoc, Kim.
+Also, recent Raffaella's student's paper and "highly-empirical paper" you introduced.
+Please add more (I might miss some relevant papers.)}
+\blue{
+High-z
+}
 
@@
 \caption{
-Seed BH mass distribution formed in different redshift ranges . 
-Each panel includes a redshift span of 10, 
-with the newly formed BHs denoted by the hatched regions, 
-and the cumulative BHs formed previously by the blue region.
-The most vigorous seed formation epoches are in redshift ranges $z\sim$ $40-30$ and $30-20$.
-Overall, the seed BH mass ranges from $\sim 10^2$ to $\gtrsim 10^5~\Msun$, 
-imprinted with the various parent halo growth histories and environmental $\vbsm$. 
+Mass distribution of seed BHs formed in quasar host galaxies at different redshifts ($50\lesssim z \lesssim 10$).
+%Each panel includes a redshift span of 10, 
+In each panel, the cumulative number distribution of BHs are shown and 
+the contribution from newly-born BHs at the redshift interval are denoted with the hatched region.
+%with the newly formed BHs denoted by the hatched regions, 
+%and the cumulative BHs formed previously by the blue region.
+The majority of seed BHs form in the epoch of $40\lesssim z \lesssim 20$.
+%The most vigorous seed formation epoches are in redshift ranges $z\sim$ $40-30$ and $30-20$.
+Overall, the seed BH mass distribution is extended to $M_\bullet \gtrsim 10^5~\Msun$, 
+imprinted with various pathways of parent halo assembly and environmental effects as discussed in \S\ref{sec:seed}.
 }
@@
 \caption{
-Posterior distributions of all the model parameters with $\fseed=0.1$ and 0.01, 
-including the marginalized one dimensional projection and the two dimensional distribution between every two parameters. 
-All the parameters converge to a single peak, 
-and specially the $\log\delta$ is confined above the artificial $-3$ barrier, 
-which is sufficiently low and can be neglected in the model.
+Two dimensional posterior distribution of all the model parameters with $\fseed=0.1$ and 0.01, 
+along with the marginalized one dimensional projection.
+% and the two dimensional distribution between every two parameters. 
+The distribution of three parameters ($\tau$, $\lambda_0$, and $\alpha$) show single peaks,
+meaning the convergence of those parameters.
+The distribution of $\log\delta$ is relatively broader but suggests that the value of $\delta$
+is sufficiently low and thus the mass-dependent growth model is excluded.
+% confined above the artificial $-3$ barrier, 
+%which is sufficiently low and can be neglected in the model.
 }
@@
 
+%%%%%%%
+%    Fig. 4
+%%%%%%%
+\begin{figure*}
+\centering
+\includegraphics[width=160mm]{fits_MF.png}
+\caption{
+The BH mass function at $z=6$ with the best-fit parameters (purple curve) and the $1\sigma$ spread for the cases with $\fseed=0.1$ (left) and $0.01$ (right). 
+For comparison, the BHMF inferred by \citetalias{2010AJ....140..546W} is overlaid (blue curve and shaded region).
+The data is used for the model parameter fitting.
+%.The blue line shows the BHMF derived by \citet{2010AJ....140..546W}.
+% error of observation
+}
+\label{fig:fitmf}
+\end{figure*}
+
+%%%%%%%
+%    Fig. 5
+%%%%%%%
+\begin{figure*}
+\centering
+\includegraphics[width=160mm]{fits_LF.png}
+\caption{
+The quasar luminosity function at $z=6$ with the best-fit parameters (purple curve) and the $1\sigma$ spread for the cases with $\fseed=0.1$ (left) and $0.01$ (right). 
+%as described in \ref{fig:fitmf}. 
+The observed data (blue symbols) with error bars are taken from \citetalias{2018ApJ...869..150M} and is used for the model parameter fitting.
+}
+\label{fig:fitlf}
+\end{figure*}
+
 \vspace{2mm}
@@
 This suggests that accreting seed BHs vary their growth speeds (i.e., the Eddington ratio) 
-$\sim 30$ times on average, toward the cosmic time of $t_{\rm H}\gtrsim 900$ Myr at $z\simeq 6$.
+$\sim 30$ times on average, over the cosmic time of $t_{\rm H}\simeq 800$ Myr at $z\simeq 6$.
 The timescale of $\tlife$ also gives a lower bound of the quasar lifetimes of $t_{\rm Q}\sim 1-10$ Myr, 
@@
 More detailed comparison is discussed in \S\ref{sec:evol}.
+
+%%%%%%%
+%    Fig. 
+%%%%%%%
+\begin{figure*}
+\centering
+\includegraphics[width=160mm]{tau.png}
+\caption{
+Left panel: BHMF at $z=$ 6 calculated in the $\fseed=0.01$ case, 
+with different $\tlife=$ 10, 18 (the best-fit value), and 50 Myr, respectively, 
+and other parameters are fixed to the best-fit values. 
+The blue curve denotes the BHMF constrained by the \citetalias{2010AJ....140..546W} result. 
+With lower(higher) $\tlife$ than the best-fit value, the BHMF is under(over)-produced in the high mass end.
+Right panel: QLF at $z=$ 6 calculated with the same parameters as in the left panel.
+The overlaid blue dots are from the \citetalias{2018ApJ...869..150M} $z\sim$ 6 quasar observation. 
+With $\tlife$ values different from the best-fit value, the consequent QLF show 
+similar trends of deviation from observation as in the BHMF curves.
+}
+\label{fig:tau}
+\end{figure*}
 
@@
 
-%%%%%%%
-%    Fig. 4
-%%%%%%%
-\begin{figure*}
-\centering
-\includegraphics[width=160mm]{fits_MF.png}
-\caption{
-Fit of BHMF at $z=$ 6 by the best-fit parameters (orange line), with one sigma spread (shaded region) for $\fseed=$ 0.1 and 0.01. 
-The blue line shows the BHMF derived by \citet{2010AJ....140..546W}.
-% error of observation
-}
-\label{fig:fitmf}
-\end{figure*}
-
-%%%%%%%
-%    Fig. 5
-%%%%%%%
-\begin{figure*}
-\centering
-\includegraphics[width=160mm]{fits_LF.png}
-\caption{
-Fit of QLF at $z=$ 6, by the best-fit parameters and one sigma spread as described in \ref{fig:fitmf}. 
-The blue data points with error bars label the QLF from the observation by \citet{2018ApJ...869..150M}.
-}
-\label{fig:fitlf}
-\end{figure*}
-
 \vspace{2mm}
@@
 
-%%%%%%%
-%    Fig. 
-%%%%%%%
-\begin{figure*}
-\centering
-\includegraphics[width=160mm]{tau.png}
-\caption{
-Left panel: BHMF at $z=$ 6 calculated in the $\fseed=0.01$ case, 
-with different $\tlife=$ 10, 18 (the best-fit value), and 50 Myr, respectively, 
-and other parameters are fixed to the best-fit values. 
-The blue curve denotes the BHMF constrained by the \citetalias{2010AJ....140..546W} result. 
-With lower(higher) $\tlife$ than the best-fit value, the BHMF is under(over)-produced in the high mass end.
-Right panel: QLF at $z=$ 6 calculated with the same parameters as in the left panel.
-The overlaid blue dots are from the \citetalias{2018ApJ...869..150M} $z\sim$ 6 quasar observation. 
-With $\tlife$ values different from the best-fit value, the consequent QLF show 
-similar trends of deviation from observation as in the BHMF curves.
-}
-\label{fig:tau}
-\end{figure*}
-
 \vspace{2mm}
-\subsection{Cosmological evolution of BHMF and QLF}\label{sec:cosm}
-% \red{KI: shall we discuss the $z$-dependence of the BHMF and QLF?
-% Don't need to repeat calculations. Just using the same parameters with 1sigma scatter?
-% Showing $\rho_{\bullet}(z)$ in $\Msun ~ {\rm Mpc}^{-3}$, which is the integrant of BHMF, would be interesting}
+\section{Cosmological evolution of BH mass and quasar luminosity function}\label{sec:cosm}
+%\red{KI: shall we discuss the $z$-dependence of the BHMF and QLF?
+%Don't need to repeat calculations. Just using the same parameters with 1sigma scatter?
+%Showing $\rho_{\bullet}(z)$ in $\Msun ~ {\rm Mpc}^{-3}$, which is the integrant of BHMF, would be interesting}
 
@@
 \caption{
-Left panel: BHMF at $z$ from 6 to 10. The solid lines denote modeled BHMF produced by the best-fit parameters 
-and the shaded regions are the one sigma spread. 
-Right panel: the mass density of BHs with $\Mbh > 10^7~\Msun$, integrated from the BHMF in the left panel.
+{\it Left panel}: BH mass functions at different redshifts of $6\leq z \leq 10$.
+The solid lines denote modeled BHMF produced by the best-fit parameters 
+and the shaded regions present the $1\sigma$ spread. 
+{\it Right panel}: the redshift evolution of the cumulative mass density of BHs with $\Mbh \geq 10^7~\Msun$ in a comoving volume, 
+evaluated by the integration of the BHMF shown in the left panel.
+The evolutionary trend can be approximated as $\rho_\bullet (z) \propto 10^{k_M z}$, where $k_M\simeq -0.8$.
 }
 \label{fig:BHMF_rhoz}
-\end{figure*}
-
-%%%%%%%
-%    Fig. 
-%%%%%%%
-\begin{figure*}
-\centering
-\includegraphics[width=160mm]{QLF_rhoz.png}
-\caption{
-Left panel: QLF at $z$ from 6 to 10. The solid lines denote modeled QLF produced by the best-fit parameters 
-and the shaded regions are the one sigma spread. 
-Right panel: the cumulative number density of quasars with $\Muv <-26$, integrated from the QLF in the left panel.
-}
-\label{fig:QLF_rhoz}
 \end{figure*}
@@
 the future explorations of high-$z$ quasars.
+
+\subsection{Black hole mass function}
+
 In the left panel of Fig.~\ref{fig:BHMF_rhoz}, we show the BHMFs at five different redshifts of $z=6-10$.
@@
 %https://ui.adsabs.harvard.edu/abs/2019MNRAS.488.3143B/abstract
-With those values, we estimate the cumulative stellar-to-BH mass ratio for high-$z$ quasars as
+With those values, we estimate the stellar-to-BH mass ratio for high-$z$ quasars as
 %
@@
 \end{equation}
-% wli now
+% 
 \red{KI: please check the value of $k_{\rm h}-k_{\rm M}$.}
@@
 is broadly consistent with those seen in the local universe, although SMBHs observed as high-$z$ quasars
-appear to be overmassive compared to the local relation \citep{2013ApJ...773...44W,2020A&A...637A..84P} \dots.
+appear to be overmassive compared to the local relation \citep[e.g.,][]{2013ApJ...773...44W,2020A&A...637A..84P}.
+
+\subsection{Quasar luminosity function}
 
@@
 \citep[e.g.,][]{2010ApJ...718..231S}.
+%Studies with the assumption of the close correlation of DM halo mass with central BH mass, and a constant Eddington ratio 
+%interprete this rapid decline by the rarity of massive halos toward higher redshifts \citep[e.g.,][]{2010ApJ...718..231S}, 
+%while another entangling factor is the radiative efficiency in converting BH growth rate to luminosity. 
+%In our work, we argue that the episodical BH accretion with bursts and quiescent phases is 
+%important in matching the $z\sim 6$ quasar observations, 
+%and this calls consideration of the more realistic BH-galaxy coevolution in understanding the observable AGN properties.
+
+%%%%%%%
+%    Fig. 
+%%%%%%%
+\begin{figure*}
+\centering
+\includegraphics[width=160mm]{QLF_rhoz.png}
+\caption{
+{\it Left panel}: quasar luminosity functions at different redshifts of $6\leq z \leq 10$. 
+The solid lines denote modeled QLF produced by the best-fit parameters and the shaded regions present the $1\sigma$ spread. 
+{\it Right panel}: the redshift evolution of the cumulative number density of quasars with $\Muv <-26~{\rm mag}$ in a comoving volume,
+evaluated by the integration of the QLF shown in the left panel.
+The evolutionary trend can be approximated as $n(\Muv<-26~{\rm mag})\propto 10^{k_{L} z}$, where $k_L \simeq -0.95$.
+This result indicates rapid decline of the number of bright quasars toward higher redshifts, consistent with previous observations
+\citep[red data points; see][]{2016ApJ...833..222J, 2019ApJ...884...30W}
+}
+\label{fig:QLF_rhoz}
+\end{figure*}
 
@@
 \caption{
-BH growth tracks from $z=$ 30 produced by the best-fit model in the $\fseed=0.01$ case, 
-selected by the criterion $M>10^8~\Msun$ at $z=$ 6. 
-Highlighted are 7 massive BHs with $M>10^9~\Msun$ (with colors), 
-extrapolated back following exponential growth with constant Eddington ratio: 
-constant $\lambda$ keeping the $z=$ 6 value with dotted lines and 
-Eddington limit growth with $\lambda=1$ with dashed lines.
+Evolutionary tracks of individual seed BHs with the the best-fit growth model parameters in the $\fseed=0.01$ case.
+Among all the samples, we select BHs that reach $M\geq 10^8~\Msun$ at $z=6$ (solid curves). 
+The heaviest 7 BHs with $M_\bullet \geq 10^9~\Msun$ at $z=6$ are highlighted with colors. 
+For the heaviest BHs, we draw the assembly history assuming an exponential growth with a constant Eddington ratio: 
+the $\lambda$-value found at $z=6$ for each BH (dotted curves; extrapolation with an observed value of $\lambda$) and 
+$\lambda =1$ (dashed curves; continuous Eddington growth).
+%constant $\lambda$ keeping the $z=$ 6 value with dotted lines and 
+%Eddington limit growth with $\lambda=1$ with dashed lines.
 }
@@
 \vspace{2mm}
-\subsection{Observed v.s. Intrinsic ERDF}\label{sec:ldist}
-Discussion on quasar \textit{intrinsic} properties is naturally difficult, 
-in the sense that quasars are selected by their \textit{observed} properties, 
-e.g., a cut off of detection under some magnitude floor. 
-The unavoidable bias of quasar surveys may be corrected by the selection function tested 
-by experiments on the detectability of mock data.
-In this section, we examine the effect of flux-limited quasar survey on the observed ERDF, 
-taking advantage of our complete sample of BH population in the whole luminosity range.
+\subsection{The distribution of the Eddington ratio: \\observed v.s. underlying populations}\label{sec:ldist}
+
+It is challenging to discuss the properties of the underlying quasar population
+%Discussion on quasar \textit{intrinsic} properties is naturally difficult, 
+because observed quasars are selected based on some criteria, e.g., the limiting magnitude.
+%a cut off of detection under some magnitude floor. 
+The unavoidable bias of quasar surveys could be corrected with the selection function calibrated
+by experiments on the detectability of mock data, but is not fully solved. 
+In this section, we examine the effect of flux-limited quasar surveys on the observed ERDF, 
+taking advantage of our complete sample of high-$z$ BH populations in the whole luminosity range.
 
 Based on the quasar sample from the best-fit model described in \S~\ref{sec:evol}, 
-we select quasars above a bolometric luminosity cutoff at $\Lbol=10^{46}~\mathrm{erg~s^{-1}}$. 
-In Fig.~\ref{fig:lhist}, we plot the intrinsic ERDF for the whole sample together with 
-the selected sample (observed one). 
-The intrinsic Eddington ratio follows the Schechter shape with a majority of inactive quasars, 
-while the observed Eddington ratio is biased toward higher values, and the shape changes to 
-more resembling log-normal distribution. 
-The latter distribution is presented by various observational efforts in $z\sim$ 6 quasar samples
-\citep[e.g.,][]{2010AJ....140..546W,2019ApJ...873...35S}, 
-while we predict a huge hidden population with low Eddington ratio, 
-based on the best-fit growth model connecting the BH seeding and $z\sim$ 6 BHMF and QLF. 
-To demonstrate qualitatively the caveat for the detection limit on recovering the intrinsic quasar properties, 
-we also examine the observed ERDF by selecting quasars with $\Lbol>10^{45}~\mathrm{erg~s^{-1}}$. 
-We find that lowering the detection limit unveils more quasars with low Eddington ratio. 
-Therefore we emphasize that it is imperative to lower the detection limit in order to 
-understand a more complete quasar sample at high-$z$, 
-so that the numerous dimly accreting BHs can be shed light on.
+we select quasars with a bolometric luminosity cut.
+%of $\Lbol \geq 10^{46}~\mathrm{erg~s^{-1}}$. 
+In Fig.~\ref{fig:lhist}, we present the intrinsic ERDFs for the whole BH sample (blue) and the selected sample with
+a luminosity cut of $\Lbol \geq 10^{46}~\mathrm{erg~s^{-1}}$ (green) and $\Lbol \geq 10^{45}~\mathrm{erg~s^{-1}}$ (orange).  
+The Eddington ratio for the whole sample follows a Schechter shape with a majority of inactive quasars, 
+while the observed Eddington ratio is biased toward higher values and the distribution results in a log-normal shape. 
+The latter distribution is presented by various observational efforts in the $z\sim$ 6 brightest quasar samples 
+\citep[e.g.,][]{2010AJ....140..546W,2019ApJ...873...35S}.
+However, our best-fit growth model reproducing both the BHMF and QLF at $z\sim$ 6 suggests the existence of
+a large number of underlying BH populations with low Eddington ratios. 
+%based on the best-fit growth model connecting the BH seeding and $z\sim$ 6 BHMF and QLF. 
+We find that the log-normal shape still holds with the lower luminosity cut, 
+%To demonstrate qualitatively the caveat for the detection limit on recovering the intrinsic quasar properties, 
+%we also examine the observed ERDF by selecting quasars with $\Lbol>10^{45}~\mathrm{erg~s^{-1}}$. 
+but a lower detection limit unveils more hidden quasars with low Eddington ratios. 
+This will be proved by the ongoing observations with the Subaru HSC providing low-luminosity and less-massive BH samples
+(Onoue et al. in prep).
+%Therefore, we emphasize that it is imperative to lower the detection limit in order to 
+%understand a more complete quasar sample at high-$z$, 
+%so that the numerous dimly accreting BHs can be shed light on.
 
@@
 \centering
-\includegraphics[width=85mm]{distf2N5_06231122_l_hist.png}
+\includegraphics[width=80mm]{distf2N5_06231122_l_hist.png}
 \caption{
-Intrinsic ERDF (blue) and the observed ones after imposing selection effects by $\Lbol>L_\mathrm{lim}=10^{45}$ (orange) and 10$^{46}$ erg~s$^{-1}$ (green).
+The intrinsic Eddington ratio distribution function for the whole BH sample (blue) and the selected sample with
+a luminosity cut of $\Lbol \geq 10^{46}~\mathrm{erg~s^{-1}}$ (green) and $\Lbol \geq 10^{45}~\mathrm{erg~s^{-1}}$ (orange).  
+%Intrinsic ERDF (blue) and the observed ones after imposing selection effects by $\Lbol>L_\mathrm{lim}=10^{45}$ (orange) and 10$^{46}$ erg~s$^{-1}$ (green).
 The observed histograms are elevated by arbitrary normalizations for comparison of the distribution shapes.
-The intrinsic ERDF follows the dashed line which shows the analytical ERDF by the best-fit Schechter model. 
-While with the detection limit imposed, the observed ERDFs resemble log-normal shape. 
-With decreasing $L_\mathrm{lim}$, more low $\lambda$ population is unveiled.
+The intrinsic ERDF follows the best-fitted Schechter function (dashed curve), 
+while the observed ERDF with a detection limit imposed results in a log-normal shape, 
+with a large low Eddington ratio quasars hidden from detection.
+The log-normal shape still holds with the lower luminosity cut, 
+but a lower detection limit alleviates the selection effect against the low Eddington ratio quasar populations.
+%With decreasing $L_\mathrm{lim}$, more low $\lambda$ population is unveiled.
 }
@@
 
+\clearpage
+
 \newpage

### 2022-07-22 ms.tex
written and revised by k 1st round, now without abstract & summary; version 0722

@@
 \blue{
-High-z
+% High-z
 }
@@
 \subsection{Model dependence}\label{sec:modep}
-\red{KI: It'd be good to discuss the dependence of our results on key parameters such as $\tlife$.
-You repeat the MCMC fitting with a fixed value of $\tlife$? Saying like for a longer $\tlife$,
-the fitting results would never be improved.}
-
 As described in \S~\ref{sec:model}, we introduce the parameter $\tau$ as a typical timescale
-for individual duration of quasar accretion activities, i.e. in each cycle $\tlife$ 
-we assign Eddington ratio $\lambda$ following the parameterized ERDF for all BHs.
-The extraction of this timescale essentially modifys the ERDF in the whole BH growth history, 
-because the multiple sampling of $\lambda$ reduces the possibility of a BH accreting on average with $\lambda \gtrsim \lambda_0$ 
-than single sampling. 
-However at any time during growth, the ERDF of the BH population remains the same as at $z\sim$ 6, 
-therefore we ensure treating all cosmic time equally.
-
+for individual durations of quasar accretion activity.
+Specifically, we assign an Eddington ratio $\lambda$ following the ERDF for all BHs in each cycle
+with a time duration of $\tau$.
+Variable accretion episodes in every cycle essentially modify the effective ERDF in the whole BH growth history,
+because multiple sampling of $\lambda$ reduces the possibility of a BH growing with $\lambda \gtrsim \lambda_0$
+compared to that with a single sampling of $\lambda$.
+%However at any time during growth, the ERDF of the BH population remains the same as at $z\sim$ 6,
+%therefore we ensure treating all cosmic time equally.
+In what follows, we demonstrate the role of $\tlife$ in shaping the BHMF evolution and the consequent QLF.
 % tau极端小，则非常小的lambda，不能解释 （且delta func？ 有必要说或是放在后面讨论？）
 
-Hereafter we demonstrate the role of $\tlife$ on shaping the BHMF evolution and the consequent QLF. 
-In the left panel of Fig.~\ref{fig:tau}, the BHMF at $z=6$ is calculated from setting $\tlife=$ 10, 18, and 50 Myr, 
-and keeping the other parameters as the best-fit values for the $\fseed=0.01$ case.
-While $\tlife \approx$ 18 Myr is the best-fit value, resulting in the BHMF which nicely matches the results in \citetalias{2010AJ....140..546W}, 
-the other two cases demonstrate the sensitivity of the $\tlife$ value in producing the bulk of massive BHs 
-and the slope in the high mass tail. 
-For $\tlife=$ 10 Myr, the number of Eddington ratio assignment cycles increases to $\sim$ 80 
-from $\sim$ 40 with the best-fit $\tlife$ value. 
-Thus the possibility of continuous high Eddington ratio accretion along the growth is lower, 
-suppressing the growth of massive BHs at $M_\bullet \gtrsim 10^8~\Msun$. 
-On the other hand, for $\tlife=$ 50 Myr, with $\sim$ 16 times of multiple Eddington ratio assignment,
-on average high values of $\lambda\gtrsim \lambda_0$ is non-negligibly realized in the BHMF evolution. 
-Therefore in the high mass end of BHMF at $z=$ 6, the BH population is significantly overproduced than the constraints from observation.
+In the left panel of Fig.~\ref{fig:tau}, we present the BHMF at $z=6$ for three different values of $\tlife=10$, $18$, and $50$ Myr,
+but keeping the other parameters as the best-fit values ($\lambda_0=0.87$ and $\alpha=0.20$) for the case with $\fseed=0.01$.
+We note that $\tlife \approx$ 18 Myr is the best-fit value reproducing the BHMF consistent with that of \citetalias{2010AJ....140..546W}.
+%the other two cases demonstrate the sensitivity of the $\tlife$ value in producing the bulk of massive BHs
+%and the slope in the high mass tail.
+For $\tlife=10$ Myr, the frequency of Eddington ratio assignment increases twice until $z=6$.
+%to $\sim$ 80 from $\sim$ 40 with the best-fit $\tlife$ value.
+Therefore, continuous and efficient growth of BHs with $\lambda \gtrsim \lambda_0$ is less likely to occur,
+%high Eddington ratio accretion along the growth is lower,
+suppressing the formation of BHs heavier than $M_\bullet \simeq 10^8~\Msun$.
+Moreover, if a high Eddington ratio is given with a certain but low probability, the BH mass hardly increases
+within $\tlife=10$ Myr, which is $\simeq 20\%$ of the $e$-folding timescale.
+On the other hand, for $\tlife=$ 50 Myr, there is a non-negligible probability that
+% $\sim$ 16 times of Eddington ratio assignment,
+more BHs experience high accretion rates with $\lambda\gtrsim \lambda_0$ through their assembly history.
+%high values of $\lambda\gtrsim \lambda_0$ is non-negligibly realized in the BHMF evolution.
+Therefore, the high mass end of the BHMF is further extended and those massive populations are substantially
+overproduced compared to the observed abundance.
+%in the high mass end of BHMF at $z=$ 6, the BH population is significantly overproduced than the constraints from observation.
 
 The QLF at $z=6$ is shown in the right panel of Fig.~\ref{fig:tau}.
-In the conversion from BHMF to QLF, the ERDF is the same for different $\tlife$ values, 
-following the $P(\lambda)$ in Eq.~(\ref{eq:Pl}) with $\lambda_0=0.87$ and a=0.20. 
-Thus the deviation from the observed QLF in \citetalias{2018ApJ...869..150M}  shows similar trends as in the BHMF. 
-i.e., $\tlife$ values lower (higher) than the best-fit one leads to the under(over)-production of the luminous quasar population.
-We notice that the best-fit value of $\tlife$ favors a moderate fraction of $t_{\rm S}$, 
-which regulates the BH growth and reproduces the quasar observation together with the other best-fit parameters in their reasonable ranges.
+%In the conversion from BHMF to QLF, the ERDF is the same for different $\tlife$ values,
+%following the $P(\lambda)$ in Eq.~(\ref{eq:Pl}) with $\lambda_0=0.87$ and $\alpha=0.20$.
+Overall, the dependence of the QLF on the choice of $\tau$ shows the same trend as in the BHMF,
+%the deviation from the observed QLF of \citetalias{2018ApJ...869..150M} shows similar trends as in the BHMF.
+i.e., higher (lower) $\tlife$ values lead to under(over)-production of the luminous quasar population.
+The best-fit value of $\tlife (\simeq 18$ Myr) favors a moderate fraction of $t_{\rm S}$.
+This suggests the importance of regulated growth of BHs to reproduce the shape of the observed BHMF and QLF.
+%reproduces the quasar observation together with the other best-fit parameters in their reasonable ranges.
+In \S\ref{sec:evol}, we apply this episodic accretion model to individual growth pathways of high-$z$ quasars
+and demonstrate that normal seeding mechanisms can explain the existence of massive BHs with low luminosity
+observed at $z\simeq 6-7$.
 
@@
 \section{Discussion}
+\label{sec:discussion}
 \vspace{2mm}

### 2022-07-26 ms.tex
version 0726; my abstract added; k comments: intro refs, f_duty added

@@
 \begin{abstract}
-W\\
-E\\
-N\\
-X\\
-I\\
-U\\
-L\\
-I\\
-1\\
-2\\
-3
+The early evolution of black hole mass function (BHMF) and the quasar luminosity function (QLF)
+plays an important role in the establishment of BH-galaxy coevolution at high redshifts ($z\gtrsim$ 6).
+However, the accretion and radiation properties of growing BHs in the high-$z$ environments 
+still remain a challenge to be explored.
+In this work, based on a semi-analytic BH seed formation model, 
+we relate the seeding time and BH masses at born with the growth tracks of their parent halos. 
+We then construct the mass and luminosity evolution of the BH population with a growth model 
+characterizing the episodical BH accretion and Eddington ratio distribution function (ERDF) motivated by observational constraints.
+The model parameters are fitted to reproduce the observed BHMF and QLF of the quasar population down to $z\sim$ 6.
+Our best-fit models suggest that BHs grow with episodical bursts and quescent phases, with time duration 
+typically in units of 20 $\sim$ 30 Myr. 
+In the sub-sample of massive BHs with $M\gtrsim 10^8~\Msun$, 
+the duty cycle of active accretion phase is $f_{\rm duty}\sim 0.15$, 
+boosted from that in the whole population by nearly a factor of two. 
+We find that the intrinsic ERDF of the whole quasar population is well presented by a Schechter shape, 
+indicating a large number of low Eddington ratio objects missed by the current flux-limited quasar selections.
+We give prediction of the early evolution of BHMF and QLF, as well as the growth patterns of individual BHs, 
+which will likely be unveied by deep and wide-field surveys with, e.g. 
+the James Webb Space Telescope (JWST) and the forthcoming Roman Space Telescope (RST) and Euclid.
 \end{abstract}
@@
 The growth of massive black holes (BHs) in galactic nuclei is elegantly related to their luminous accretion phases
-across the cosmic time \citep{1982MNRAS.200..115S,1992MNRAS.259..725S}.
+across the cosmic time \citep{1982MNRAS.200..115S}%,1992MNRAS.259..725S}.
 Comparing the mass density of massive BHs in the local universe and the mass accreted onto BH inferred from
 the integration of the quasar luminosity function based on multi-wavelength observations,
-the cosmic BH accretion history and their radiative efficiency are nicely constrained \citet{2002MNRAS.335..965Y}
-\red{KI: add more references, Ueda+14, Delvecchio+14, Marconi?, and some Shankar's papers}.
+the cosmic BH accretion history and their radiative efficiency are nicely constrained 
+\citep[e.g.][]{1971ApJ...170..223C,1992MNRAS.259..725S,2002MNRAS.335..965Y,2004MNRAS.351..169M,2008MNRAS.388.1011M,2004MNRAS.354.1020S,
+2009ApJ...690...20S,2014MNRAS.439.2736D,2014ApJ...786..104U,2017A&A...600A..64T}.
 
 Extrapolation of this argument toward higher redshifts beyond $z\sim$ 6 is limited because of the current capability for
-high-$z$ quasar observations \citep{2019BAAS...51c.121F} \red{KI: you could find better reference in this Decadal Survey?}.
-Nevertheless,... \red{KI: you could say the current status of $z=6$ QLFs/BHMFs; citing Jiang+16, 18, Willott+10, HSC papers.}
+high-$z$ quasar observations \citep{2013ApJ...768..105M,2016ApJ...829...33Y,2019ApJ...884...30W,2019BAAS...51c.121F}.
+% \red{KI: you could find better reference in this Decadal Survey?}.
+\red{KI: you could say the current status of $z=6$ QLFs/BHMFs; citing Jiang+16, 18, Willott+10, HSC papers.}
+\blue{
+Nevertheless, currently the $z\sim 6$ quasar population is well constrained by multiband surveys 
+\citep{2008AJ....135.1057J,2010AJ....139..906W,2016arXiv161205560C,2016ApJ...833..222J,2018PASJ...70S..35M,2019ApJ...883..183M,2019AJ....157..168D},
+with the quasar luminosity function constructed \citep[e.g.,][]{2018ApJ...869..150M}, 
+and the virial BH mass investigated from the Mg II 2798 $\rm{\AA}$ line width where deep spectroscopic measurements are carried out
+\citep{2007AJ....134.1150J,2007ApJ...669...32K,2010AJ....140..546W,2018Natur.553..473B,2019ApJ...880...77O,2019ApJ...873...35S}. 
+}
 Moreover, in the era of the James Webb Space Telescope (JWST) and forthcoming facilities,
@@
 and the establishment of BH-galaxy coevolution 
-\red{cite Wang+2013; Venemans+2017, Izumi et al. 2021, Inayoshi+2022 simulation, Habouzit+2022}.
+\citep[e.g.,][]{2013ApJ...773...44W,2017ApJ...851L...8V,2021ApJ...914...36I,2022ApJ...927..237I,2022MNRAS.511.3751H}.
+% \red{cite Wang+2013; Venemans+2017, Izumi et al. 2021, Inayoshi+2022 simulation, Habouzit+2022}.
 
@@
 %2014MNRAS.445L.109I,2014MNRAS.445..544S,2014MNRAS.445..107V,2020MNRAS.499.5960S}.
-\red{KI: I think here we should cite more general citations: Begelman+2006; Tanaka \& Haiman 2009; Hirano+14, 15,
-Toyouchi+2022, one Natarajan+Volonteri's paper discussing the mass function, Valiante+2018, Sassano+21}
+\citep{2006MNRAS.370..289B,2009ApJ...696.1798T,2012MNRAS.422.2051N,2014ApJ...781...60H,
+2015MNRAS.448..568H,2018MNRAS.474.3825V,2021MNRAS.506..613S,2022arXiv220614459T}.
+% \red{KI: I think here we should cite more general citations: Begelman+2006; Tanaka \& Haiman 2009; Hirano+14, 15,
+% Toyouchi+2022, one Natarajan+Volonteri's paper discussing the mass function, Valiante+2018, Sassano+21}
 Massive star formation episodes in the early universe is substantially modulated by external environmental effects such as
@@
 %irradiation in Lyman-Werner band which photo-dissociates the major coolant $\hh$
-\citep{2001ApJ...546..635O,2002ApJ...569..558O,2003Natur.425..812B,2010MNRAS.402.1249S,2014MNRAS.445..544S,2014MNRAS.445..107V}
-\red{KI: add Chon+16},
+\citep{2001ApJ...546..635O,2002ApJ...569..558O,2003Natur.425..812B,2010MNRAS.402.1249S,2014MNRAS.445..544S,2014MNRAS.445..107V,2016ApJ...832..134C},
+% \red{KI: add Chon+16},
 (ii) supersonic baryonic streaming motion that delays gas collapse in halos
-\citep{2012MNRAS.424.1335F, 2014MNRAS.439.1092T, 2018ApJ...855...17H} \red{KI: add Inayoshi, Li \& Haiman 18, Schauer +17},
+\citep{2012MNRAS.424.1335F, 2014MNRAS.439.1092T, 2018ApJ...855...17H,2017MNRAS.471.4878S,2018MNRAS.479.4017I},
+% \red{KI: add Inayoshi, Li \& Haiman 18, Schauer +17},
 and
 (iii) dynamical heating caused by frequent halo mergers and turbulence injection led by cold accretion flows
-\citep{2003ApJ...592..645Y, 2019Natur.566...85W} \red{KI: add Latif's Nature paper, Mayer+10 or 15}.
+\citep{2003ApJ...592..645Y,2010Natur.466.1082M,2015ApJ...810...51M,2019Natur.566...85W,2022Natur.607...48L}.
+% \red{KI: add Latif's Nature paper, Mayer+10 or 15}.
 Those effects keep isothermal collapse ($T\sim 8000~{\rm K}$) of massive gas at high accretion rates of $\gtrsim 0.1~\Msunyr$
-without vigorous fragmentation \citep{2014MNRAS.445L.109I} \red{KI: add Becerra+15, Latif+16}, and allow supermassive stars
-with $\sim 10^5~\Msun$ (presumably seed BHs) to form at the halo centers \red{cite Hosokawa+13, Woods+19?, Schleicher+13, Toyouchi+22}.
+without vigorous fragmentation \citep{2014MNRAS.445L.109I,2015MNRAS.446.2380B,2016PASA...33...51L},% \red{KI: add Becerra+15, Latif+16}, 
+and allow supermassive stars with $\sim 10^5~\Msun$ (presumably seed BHs) to form at the halo centers 
+\citep{2013ApJ...778..178H,2013A&A...558A..59S,2019PASA...36...27W,2022arXiv220614459T}.
+% \red{cite Hosokawa+13, Woods+19?, Schleicher+13, Toyouchi+22}.
 Although the conditions required for heavy seed formation are thought to be too stringent to be realized in the typical regions of the early universe
-\red{cite Dijkstra+08, Ahn+09, Inayoshi \& Tanaka 15}, recent studies by Lupi+21 and Li+21 found that the heavy-seed formation
+\citep{2008MNRAS.391.1961D,2009ApJ...695.1430A,2015MNRAS.450.4350I},
+% \red{cite Dijkstra+08, Ahn+09, Inayoshi \& Tanaka 15}, 
+recent studies by \citet{2021MNRAS.503.5046L} and \citet{2021ApJ...917...60L} found that the heavy-seed formation
 can be accelerated in the rare, overdense regions of the universe, where non-linear galaxy clustering boosts the irradiation intensity
@@
 \blue{
+% Haiman \& Loeb 1997.
 % High-z
@@
 where $\lambda \equiv L/L_\mathrm{Edd}$ is the Eddington ratio,
-and $\Mdot_\mathrm{Edd} \equiv L_{\mathrm{Edd}}/\eta_0 c^2$ is the Eddington accretion rate with a 10\% radiative efficiency of $\eta_0=0.1$ \citep{1973A&A....24..337S},
+and $\Mdot_\mathrm{Edd} \equiv L_{\mathrm{Edd}}/\eta_0 c^2$ is the Eddington accretion rate with a radiative efficiency of $\eta_0=0.1$ \citep{1973A&A....24..337S},
 %Note here we adopt the radiative efficiency $\eta_0 \approx 0.1 $,
 %according to the thin accretion disk model \citep{1973A&A....24..337S}, 
-which is consistent with the value obtained from the Soltan's argument \citep{1982MNRAS.200..115S,2002MNRAS.335..965Y}.
+which is consistent with the value obtained from the Soltan's argument \citep[e.g.,][]{2002MNRAS.335..965Y,2010ApJ...725..388C}.
 % The high mass BH should be strangulated by as it grows, 
-We define the mass dependent function of $f(\Mbh)$ as 
+\blue{
+On the basis of studies on the mass dependence of the radiative efficiency for AGNs at $z\lesssim$ 3 
+\citep{2008MNRAS.390..561C,2012ApJ...749..187L,2014ApJ...786..104U}, 
+we also introduce a similar functional form which defines the mass dependent function of $f(\Mbh)$ as 
 %
@@
 where we adopt $M_{\bullet,c}=10^8~\Msun$.
-With a positive value of $\delta$, the BH growth at the high mass end is suppressed. \blue{(references, Ueda+14?s)}.
+With a positive value of $\delta$, the BH growth at the high mass end is suppressed.
+%  \blue{(references, Ueda+14?s)}.
+}
 In the limit of $\delta \ll 1$, where $f(\Mbh) \simeq 1$ is approximated independent of $M_{\bullet,c}$, the model reproduces an exponential growth with an $e$-folding timescale of
@@
 with a Schechter function and the distribution function is independent of redshift 
-\citep{2006ApJ...639..700H,2009ApJ...698.1550H}. \red{KI: I slightly modified the previous sentence. Is that what you meant?}
-\blue{
-  not exactly, what I meant may not be necessary here, but we may discuss later.
-}
+\citep{2006ApJ...639..700H,2009ApJ...698.1550H}.
+%
 For type-I AGN populations at low redshifts, the ERDF is characterized with a Schechter function
@@
 In this way, we give a different growth speed of a BH in every period with a duration of $\tlife$ until $z=6$ 
-(the corresponding cosmic age is $t_{\rm H}\simeq 800$ Myr).
+(the corresponding cosmic age is $t_{\rm H}\gtrsim 900$ Myr).
 This treatment enables us to capture the nature of accretion bursts and avoid an unrealistically 
@@
 following \citet{2014ApJ...786..104U}.
-An alternative fitting of $\fobsc$ proposed by \citet{2014MNRAS.437.3550M} from *** \blue{(different sample?)} is 
+\blue{
+An alternative fitting of $\fobsc$ proposed by \citet{2014MNRAS.437.3550M} 
+for their X-ray AGN sample with additional optical obscuration classification gives 
 \begin{equation*}
-  \fobsc = 0.56 + \frac{1}{\pi} \text{arctan} \frac{43.89 - (\log \Lbol/L_\odot)}{0.46},
+  \fobsc = 0.56 + \frac{1}{\pi} \text{arctan} \frac{43.89 - (\log \Lbol/L_\odot)}{0.46}.
 \end{equation*}
-we fit the parameters using this prescription and discuss the sensitivity of results to $\fobsc$.
-% wli: add more!
-
-%An alternative form proposed by \citet{2014MNRAS.437.3550M} shows a similar dependence of $\fobsc$ with the luminosity,
-%but the values somewhat differ from that given by \citet{2014ApJ...786..104U} \red{within a factor of $XXX$ KI: more quantitativelt}.
-%Compared with another work by  \citet{2014MNRAS.437.3550M}, this shows a similar decreasing trend with luminosity, 
-%and the values are in agreement within a factor of 3.
+We also fit the parameters using this prescription and discuss the sensitivity of results to $\fobsc$ in the Appendix.
+}
+
 Here, we neglect the contribution from Compton-thick AGNs with $N_\mathrm{H}>10^{24}$ cm$^{-2}$, 
@@
 This suggests that accreting seed BHs vary their growth speeds (i.e., the Eddington ratio) 
-$\sim 30$ times on average, over the cosmic time of $t_{\rm H}\simeq 800$ Myr at $z\simeq 6$.
+$\sim 30$ times on average, toward the cosmic time of $t_{\rm H} \gtrsim 900$ Myr at $z\simeq 6$.
 The timescale of $\tlife$ also gives a lower bound of the quasar lifetimes of $t_{\rm Q}\sim 1-10$ Myr, 
@@
 $(\lambda_0,\alpha) = (0.89,0.12)$ and $(0.87,0.20)$ for $\fseed=0.01$ and $0.1$, respectively.
-\blue{\\This paragraph is revised hereafter.}
+\blue{
 With those values, the number fraction of super-Eddington accreting BHs is
@@
 and reproduce the bulk properties of the BHMF and QLF.
+}
 
@@
 We generate a sample of 10$^7$ BHs, whose formation time and mass distribution at birth follow the model described in \S~\ref{sec:seed}. 
-To growth the individual BHs, we assign an Eddington ratio $\lambda$ in every interval $\tlife$ until $z=6$,
-following the ERDF characterized by a Schechter function with $\lambda_0=0.87$ and $\alpha=0.20$.
-%until $z=$ 6 we take a snapshot of the BH mass and ERDF.
-With the best-fit parameters, the BH growth tracks that end up with $>10^8~\Msun$ by $z=6$ are shown in Fig.~\ref{fig:track}. 
+Following the best fit parameters in the case of $\fseed = 0.01$,
+we assign an Eddington ratio $\lambda$ in every interval $\tlife=18.76$ Myr to grow the individual BHs until $z=6$. 
+The value of $\lambda$ follows the ERDF characterized by a Schechter distribution with $\lambda_0=0.87$ and $\alpha=0.20$.
+With those parameters, we show the BH growth tracks that end up with $>10^8~\Msun$ by $z=6$ in Fig.~\ref{fig:track}. 
 \red{KI: what is the frequency $N$ of BH accretion bursts with $\lambda>\lambda_0$ between $z=6$ and $10$? The duty cycle for the sub-sample
 is $f_{\rm duty}\simeq N\tlife/\Delta t_{\rm H}$.}
+\blue{
+We take this sub-sample representing the observable massive BH population,
+which is easier to be probed by flux-limited quasar observations.
+During the growth histories of these BHs, it is interesting to examine the duty cycle of the active phase, 
+e.g., characterized as $f_{\rm duty}\simeq N\tlife/\Delta t_{\rm H}$,
+where $N$ is the frequency of a BH growing with super-Eddington accretion bursts,
+in a time duration $\Delta t_{\rm H}$.
+We estimate the duty cycle between the cosmic age of $z=$ 10 to $z=$ 6,
+and find $f_{\rm duty}\simeq 0.15$.
+On the other hand, the value of $f_{\rm duty}$ in the whole BH population 
+can be estimated as the probability of super-Eddington realization in one single epoch 
+$P(\lambda>1)=$ 0.075 (see \S~\ref{sec:fitting_result}), 
+which is about twice lower than the value of $f_{\rm duty}$.
+Therefore the massive sub-sample is biased toward the BHs undergoing more active accretion episodes.
+}
 

### 2022-07-27 ms.tex
first roll fixing k comments

@@
 
-\title{Draft}
+\title{Constraining Black Hole Growth with High-z Quasar Observations}
 
@@
 \affiliation{Kavli Institute for the Physics and Mathematics of the Universe (Kavli IPMU, WPI), The University of Tokyo, Chiba 277-8583, Japan}
+\author[0000-0003-3467-6079]{Daisuke Toyouchi}
+\affiliation{Research Center for the Early Universe (RESCEU), The University of Tokyo, Hongo, 7-3-1, Bunkyo-ku Tokyo, 113-0033, Japan}
 
@@
 plays an important role in the establishment of BH-galaxy coevolution at high redshifts ($z\gtrsim$ 6).
-However, the accretion and radiation properties of growing BHs in the high-$z$ environments 
-still remain a challenge to be explored.
+However, understanding the accretion and radiation properties of growing BHs in the high-$z$ environments 
+still remains challenging.
 In this work, based on a semi-analytic BH seed formation model, 
-we relate the seeding time and BH masses at born with the growth tracks of their parent halos. 
-We then construct the mass and luminosity evolution of the BH population with a growth model 
-characterizing the episodical BH accretion and Eddington ratio distribution function (ERDF) motivated by observational constraints.
-The model parameters are fitted to reproduce the observed BHMF and QLF of the quasar population down to $z\sim$ 6.
+we relate BH seeds with the growth tracks of their parent halos. 
+We then construct a model of BH mass and luminosity evolution 
+characterizing the episodical BH accretion and Eddington ratio distribution function (ERDF).
+The model parameters are fitted to reproduce the observed BHMF and QLF of the quasar population at $z\sim$ 6.
 Our best-fit models suggest that BHs grow with episodical bursts and quescent phases, with time duration 
 typically in units of 20 $\sim$ 30 Myr. 
-In the sub-sample of massive BHs with $M\gtrsim 10^8~\Msun$, 
-the duty cycle of active accretion phase is $f_{\rm duty}\sim 0.15$, 
+The duty cycle of active accretion is $f_{\rm duty}\sim 0.15$ for massive BHs with $M\gtrsim 10^8~\Msun$, 
 boosted from that in the whole population by nearly a factor of two. 
@@
 indicating a large number of low Eddington ratio objects missed by the current flux-limited quasar selections.
-We give prediction of the early evolution of BHMF and QLF, as well as the growth patterns of individual BHs, 
-which will likely be unveied by deep and wide-field surveys with, e.g. 
-the James Webb Space Telescope (JWST) and the forthcoming Roman Space Telescope (RST) and Euclid.
+We give prediction of the early evolution of BHMF and QLF,
+as well as the growth patterns of individual BHs, 
+which will likely be unveiled by the James Webb Space Telescope (JWST) and future deep and wide-field surveys.
+%  with, e.g. 
+% the , Roman Space Telescope (RST), and Euclid.
 \end{abstract}
@@
 \section{Introduction} \label{sec:intro}
-The growth of massive black holes (BHs) in galactic nuclei is elegantly related to their luminous accretion phases
-across the cosmic time \citep{1982MNRAS.200..115S}%,1992MNRAS.259..725S}.
+The growth of massive black holes (BHs) in active galactic nuclei (AGN) is elegantly related to their luminous accretion phases
+across the cosmic time \citep{1982MNRAS.200..115S}.
+%,1992MNRAS.259..725S}.
 Comparing the mass density of massive BHs in the local universe and the mass accreted onto BH inferred from
@@
 % \red{KI: you could find better reference in this Decadal Survey?}.
-\red{KI: you could say the current status of $z=6$ QLFs/BHMFs; citing Jiang+16, 18, Willott+10, HSC papers.}
-\blue{
 Nevertheless, currently the $z\sim 6$ quasar population is well constrained by multiband surveys
-\citep{2008AJ....135.1057J,2010AJ....139..906W,2016arXiv161205560C,2016ApJ...833..222J,2018PASJ...70S..35M,2019ApJ...883..183M,2019AJ....157..168D},
-with the quasar luminosity function constructed \citep[e.g.,][]{2018ApJ...869..150M}, 
-and the virial BH mass investigated from the Mg II 2798 $\rm{\AA}$ line width where deep spectroscopic measurements are carried out
+\citep{2008AJ....135.1057J,2010AJ....139..906W,2016arXiv161205560C,2016ApJ...833..222J,2018PASJ...70S..35M,2019ApJ...883..183M,2019AJ....157..168D}
+along with the quasar luminosity function \citep[e.g.,][]{2018ApJ...869..150M}.
+%and the virial BH mass estimates
+%from the \ion{Mg}{2} 2798 $\rm{\AA}$ line width 
+%where 
+Deep spectroscopic observations of high-$z$ quasars enable us to measure the virial BH mass 
+with the \ion{Mg}{2} single-epoch method and bring insights of the mass distribution
 \citep{2007AJ....134.1150J,2007ApJ...669...32K,2010AJ....140..546W,2018Natur.553..473B,2019ApJ...880...77O,2019ApJ...873...35S}. 
-}
 Moreover, in the era of the James Webb Space Telescope (JWST) and forthcoming facilities,
@@
 % The high mass BH should be strangulated by as it grows, 
-\blue{
 On the basis of studies on the mass dependence of the radiative efficiency for AGNs at $z\lesssim$ 3 
 \citep{2008MNRAS.390..561C,2012ApJ...749..187L,2014ApJ...786..104U}, 
-we also introduce a similar functional form which defines the mass dependent function of $f(\Mbh)$ as 
+we introduce a similar functional form that characterizes its mass dependence 
 %
@@
 %
-where we adopt $M_{\bullet,c}=10^8~\Msun$.
-With a positive value of $\delta$, the BH growth at the high mass end is suppressed.
+where $M_{\bullet,c}=10^8~\Msun$ is adopted.
+With a positive value of $\delta$, the BH growth at the high mass end is suppressed, 
+while for small BHs the growth rate is accelerated.
 %  \blue{(references, Ueda+14?s)}.
-}
 In the limit of $\delta \ll 1$, where $f(\Mbh) \simeq 1$ is approximated independent of $M_{\bullet,c}$, the model reproduces an exponential growth with an $e$-folding timescale of
@@
 \end{equation*}
-where $a=10.96$, $b = 11.93$, and $c = 17.79$ \citep[Eq. 2 in ][]{2020A&A...636A..73D}, 
+where $a=10.96$, $b = 11.93$, and $c = 17.79$ \citep[Eq.~2 in ][]{2020A&A...636A..73D}, 
 and $f^{\rm bol}_{1450}=4.4$ \citep{2006ApJS..166..470R}.
@@
 following \citet{2014ApJ...786..104U}.
-\blue{
-An alternative fitting of $\fobsc$ proposed by \citet{2014MNRAS.437.3550M} 
-for their X-ray AGN sample with additional optical obscuration classification gives 
+An alternative fitting form of $\fobsc$ based on their X-ray AGN sample with additional optical obscuration classification 
+is propose by \citet{2014MNRAS.437.3550M} as
+%
 \begin{equation*}
-  \fobsc = 0.56 + \frac{1}{\pi} \text{arctan} \frac{43.89 - (\log \Lbol/L_\odot)}{0.46}.
+  \fobsc = 0.56 + \frac{1}{\pi}~ \text{arctan} \left[ \frac{43.89 - (\log \Lbol/L_\odot)}{0.46}\right].
 \end{equation*}
-We also fit the parameters using this prescription and discuss the sensitivity of results to $\fobsc$ in the Appendix.
-}
+%
+We also conduct the parameter fitting with this prescription and discuss the sensitivity of our results to 
+the choice of $\fobsc$ in the Appendix.
 
@@
 and find the posterior distribution assembles to $\delta \lesssim 0.1$.
-We then switch to impose the $\log \delta$ prior to improve the fitting performance at small $\delta$ values.
-}, 
-\red{KI: add a footnote, explaining why not $\delta$ but $\log \delta$?}.
+We then switch to impose the $\log \delta$ prior to improve the fitting performance at small $\delta$ values.}.
+%\red{KI: add a footnote, explaining why not $\delta$ but $\log \delta$?}.
 %slightly suppressing the growth in the high mass end. 
@@
 The two parameters characterizing the ERDF are given as
-$(\lambda_0,\alpha) = (0.89,0.12)$ and $(0.87,0.20)$ for $\fseed=0.01$ and $0.1$, respectively.
-\blue{
-With those values, the number fraction of super-Eddington accreting BHs is
-estimated as $P(\lambda>1)=0.064$ and 0.075, respectively. 
-The small discrepancy is enlarged with the multiple cycles of assigning $\lambda$ to BH growth, 
-and increase the fraction of the super-Eddington phase for smaller $\fseed$. 
-Thus for different $\fseed$ values, a similar number density of BHs which rapidly grow to be SMBHs by $z\simeq 6$ is produced, 
-consistent with a general picture for the early assembly of SMBHs 
-\citep[e.g.,][]{2006NewAR..50..665F,2008AJ....135.1057J,2010AJ....139..906W}.
+$(\lambda_0,\alpha) = (0.89,0.12)$ and $(0.87,0.20)$ for $\fseed=0.1$ and $0.01$, respectively.
+With those values, the fraction of super-Eddington accreting BHs is estimated as $P(\lambda>1)=0.064$ and 0.075, respectively. 
+While the probability of rapid accretion in each cycle is similar, multiple accretion episodes enlarge the difference.
+Moreover, the best fit value of $\delta$ is $(0.001,0.055)$ for the two $\fseed$ cases,
+the higher $\delta$ value encourages the growth of small BHs with $M_\bullet <10^8~\Msun$,
+so that the ten-fold difference in $\fseed$ is nearly offset.
+%Thus for different $\fseed$ values, a similar number density of BHs which rapidly grow to be SMBHs by $z\simeq 6$ is produced, 
+%consistent with a general picture for the early assembly of SMBHs 
+%\citep[e.g.,][]{2006NewAR..50..665F,2008AJ....135.1057J,2010AJ....139..906W}.
 The characteristic Eddington ratio needs to be close to unity, otherwise the highest luminosity and BH mass
@@
 and reproduce the bulk properties of the BHMF and QLF.
-}
 
@@
 % 
-\red{KI: please check the value of $k_{\rm h}-k_{\rm M}$.}
-\blue{
 where $k_{\rm h} \approx -0.16 $ for the parent halo growth histories.
-}
 Therefore, at $z\sim 6$ the bulge-to-BH mass ratio $\sim O(10^3)$ for the entire BH population (i.e., low-mass BHs and low-luminosity quasars) 
@@
 With those parameters, we show the BH growth tracks that end up with $>10^8~\Msun$ by $z=6$ in Fig.~\ref{fig:track}. 
-\red{KI: what is the frequency $N$ of BH accretion bursts with $\lambda>\lambda_0$ between $z=6$ and $10$? The duty cycle for the sub-sample
-is $f_{\rm duty}\simeq N\tlife/\Delta t_{\rm H}$.}
-\blue{
-We take this sub-sample representing the observable massive BH population,
-which is easier to be probed by flux-limited quasar observations.
-During the growth histories of these BHs, it is interesting to examine the duty cycle of the active phase, 
-e.g., characterized as $f_{\rm duty}\simeq N\tlife/\Delta t_{\rm H}$,
-where $N$ is the frequency of a BH growing with super-Eddington accretion bursts,
-in a time duration $\Delta t_{\rm H}$.
-We estimate the duty cycle between the cosmic age of $z=$ 10 to $z=$ 6,
-and find $f_{\rm duty}\simeq 0.15$.
-On the other hand, the value of $f_{\rm duty}$ in the whole BH population 
-can be estimated as the probability of super-Eddington realization in one single epoch 
-$P(\lambda>1)=$ 0.075 (see \S~\ref{sec:fitting_result}), 
-which is about twice lower than the value of $f_{\rm duty}$.
-Therefore the massive sub-sample is biased toward the BHs undergoing more active accretion episodes.
-}
+%\red{KI: what is the frequency $N$ of BH accretion bursts with $\lambda>\lambda_0$ between $z=6$ and $10$? The duty cycle for the sub-sample
+%is $f_{\rm duty}\simeq N\tlife/\Delta t_{\rm H}$.}
+For those massive BHs, we estimate the duty cycle between $z=10$ and $6$ defined as $f_{\rm duty} \equiv \mathcal{N}\tlife/\Delta t_{\rm H}$, 
+where $\mathcal{N}$ is the frequency of super-Eddington accretion bursts with $\lambda>1$ and $\Delta t_{\rm H}\simeq 450$ Myr.
+The average duty cycle is found to be $\langle f_{\rm duty}\rangle \simeq 0.15$.
+%We take this sub-sample representing the observable massive BH population,
+%which is easier to be probed by flux-limited quasar observations.
+%During the growth histories of these BHs, it is interesting to examine the duty cycle of the active phase, 
+%e.g., characterized as $f_{\rm duty}\simeq N\tlife/\Delta t_{\rm H}$,
+%where $N$ is the frequency of a BH growing with super-Eddington accretion bursts,
+%in a time duration $\Delta t_{\rm H}$.
+%We estimate the duty cycle between the cosmic age of $z=$ 10 to $z=$ 6,
+%and find $f_{\rm duty}\simeq 0.15$.
+On the other hand, the average duty cycle for the entire BH population is given by $P(\lambda>1)= 0.075$ 
+(see \S~\ref{sec:fitting_result}), which is half of that for the sub-sample.
+Therefore, this clearly shows that the massive BH samples observed in $z\simeq 6$ quasars are biased toward a population that
+undergoes active accretion episodes at higher redshifts.
 

### 2022-07-28 ms.tex
version 0728 1. title and shortened abstract 2. QLF construction statements in introduction, and small modification in blue to make the logic more fluent.

@@
 indicating a large number of low Eddington ratio objects missed by the current flux-limited quasar selections.
-We give prediction of the early evolution of BHMF and QLF,
-as well as the growth patterns of individual BHs, 
+We predict the early evolution of BHMF and QLF, as well as the growth patterns of individual BHs, 
 which will likely be unveiled by the James Webb Space Telescope (JWST) and future deep and wide-field surveys.
@@
 \citep[e.g.][]{1971ApJ...170..223C,1992MNRAS.259..725S,2002MNRAS.335..965Y,2004MNRAS.351..169M,2008MNRAS.388.1011M,2004MNRAS.354.1020S,
-2009ApJ...690...20S,2014MNRAS.439.2736D,2014ApJ...786..104U,2017A&A...600A..64T}.
+2009ApJ...690...20S,2014MNRAS.439.2736D,2014ApJ...786..104U,2017A&A...600A..64T,2022arXiv220607357S}.
 
@@
 \citep[e.g.,][]{2013ApJ...773...44W,2017ApJ...851L...8V,2021ApJ...914...36I,2022ApJ...927..237I,2022MNRAS.511.3751H}.
-% \red{cite Wang+2013; Venemans+2017, Izumi et al. 2021, Inayoshi+2022 simulation, Habouzit+2022}.
-
-Formation of seed BHs is the starting point to characterize the early assembly of massive BH populations.
-Their formation pathway and expected mass range have been extensively investigated by numerical simulations and
+
+\blue{
+Nevertheless, starting from empirical BH seeding, combinded with growth chanels e.g., merger and accretion modes,
+models can in return give prediction of the QLF at high redshifts 
+\citep[e.g.,][]{2018MNRAS.474.1995R,2018MNRAS.481.3278R,2021MNRAS.508.2706Y,2022MNRAS.511..616T}. 
+The classical way of regulating BH growth is by keeping the tight relation between $M_\bullet$ 
+and the parent halo mass or the mass of the stellar bulge
+\citep{2007ApJ...669...45H,2013ARA&A..51..511K},
+then following the hierarchical DM halo growth
+\citep[e.g.,][]{1998ApJ...503..505H,2010ApJ...718..231S,2021ApJ...910L..11K}.
+The model parameters can thus be calibrated with low-$z$ BHMF and QLF,
+and subsequently predict the higher redshift and faint quassar observations.
+On the other hand, studies also conduct extrafpolation on the low-$z$ QLF evolution and forecast the high-$z$ QLF shapes,
+which could be investigated by furture surveys
+\citep[e.g.,][]{2020MNRAS.495.3252S,2022arXiv220702233F}.
+}
+
+\red{Introduction of previous studies on QLFs for high-$z$ populations. mention Yung's paper, Ricarte \& Natarajan paper, recent Finkelstein's paper?
+Also, I remember one paper of our former postdoc, Kim.
+Also, recent Raffaella's student's paper and "highly-empirical paper" you introduced.
+Please add more (I might miss some relevant papers.)}
+
+\blue{
+As a starting point to characterize the early assembly of massive BH populations,
+the seed BH formation has been extensively investigated by numerical simulations and
 semi-analytical studies
+}
+% Formation of seed BHs is the starting point to characterize the early assembly of massive BH populations.
+% Their formation pathway and expected mass range have been extensively investigated by numerical simulations and
+% semi-analytical studies
+%
 %From Pop III star remnants ($10-10^3 ~\Msun$) to direct collapse supermassive stars (10$^4-10^5 ~\Msun$),
@@
 
-\red{Introduction of previous studies on QLFs for high-$z$ populations. mention Yung's paper, Ricarte \& Natarajan paper, recent Finkelstein's paper?
-Also, I remember one paper of our former postdoc, Kim.
-Also, recent Raffaella's student's paper and "highly-empirical paper" you introduced.
-Please add more (I might miss some relevant papers.)}
 \blue{
-% Haiman \& Loeb 1997.
-% High-z
+More explicitly, the initial mass function (IMF) of BH seeds is required to construct the picture of BH evolution.
 }
-
-To construct the picture of BH evolution, the initial mass function (IMF) of BH seeds is required.
+% To construct the picture of BH evolution, the initial mass function (IMF) of BH seeds is required.
 Studies have shown that Pop III stars (or the seed BH population) formed in mini-halos is top-heavy, while capped with $\sim 10^3~\Msun$ 
@@
 While the probability of rapid accretion in each cycle is similar, multiple accretion episodes enlarge the difference.
-Moreover, the best fit value of $\delta$ is $(0.001,0.055)$ for the two $\fseed$ cases,
+Moreover, the best fit values of $\delta$ are $(0.001,0.055)$ for the two $\fseed$ cases,
 the higher $\delta$ value encourages the growth of small BHs with $M_\bullet <10^8~\Msun$,

### 2022-07-31 ms.tex
version 0731; intro revised by k; need add a SMBH track crossing Wang2021, QLF result and detection limit description

--- 2022-07-27 ms.tex
@@
 \begin{abstract}
-The early evolution of black hole mass function (BHMF) and the quasar luminosity function (QLF)
-plays an important role in the establishment of BH-galaxy coevolution at high redshifts ($z\gtrsim$ 6).
-However, understanding the accretion and radiation properties of growing BHs in the high-$z$ environments 
-still remains challenging.
-In this work, based on a semi-analytic BH seed formation model, 
-we relate BH seeds with the growth tracks of their parent halos. 
-We then construct a model of BH mass and luminosity evolution 
-characterizing the episodical BH accretion and Eddington ratio distribution function (ERDF).
-The model parameters are fitted to reproduce the observed BHMF and QLF of the quasar population at $z\sim$ 6.
-Our best-fit models suggest that BHs grow with episodical bursts and quescent phases, with time duration 
-typically in units of 20 $\sim$ 30 Myr. 
-The duty cycle of active accretion is $f_{\rm duty}\sim 0.15$ for massive BHs with $M\gtrsim 10^8~\Msun$, 
-boosted from that in the whole population by nearly a factor of two. 
-We find that the intrinsic ERDF of the whole quasar population is well presented by a Schechter shape, 
-indicating a large number of low Eddington ratio objects missed by the current flux-limited quasar selections.
-We give prediction of the early evolution of BHMF and QLF,
-as well as the growth patterns of individual BHs, 
-which will likely be unveiled by the James Webb Space Telescope (JWST) and future deep and wide-field surveys.
-%  with, e.g. 
+The early evolution of the quasar luminosity and black hole mass function (MF) encodes key information
+on the physics determining the radiative and accretion processes of supermassive black holes (SMBHs) in high-redshift quasars.
+Although the shape of the luminosity function (LF) has been constrained by recent wide and deep surveys,
+it still remains challenging to develop a theoretical model that explains the redshift evolution and BH growth self-consistently.
+In this study, based on a semi-analytical model for the formation and growth of seed BHs
+in quasar progenitor halos,
+we construct the LF and MF of the early BH population that experiences multiple accretion bursts,
+in each of which the Eddington ratio is assigned following a Schechter function.
+Our best-fit model to reproduce the observed LF and MF at $z\simeq 6$
+suggests that several episodes of modest super-Eddington accretion occur
+and each of them lasts $\tau \simeq 20-30$ Myr.
+The average duty cycle of BHs that reach $\gtrsim 10^8~\Msun$ by $z\simeq 6$ is as high as $\simeq 15~\%$,
+which is nearly twice that of the entire population.
+We also find that the observed Eddington-ratio distribution function is skewed to a log-normal shape from the intrinsic Shechter function
+owing to detection limits of quasar observations.
+The predicted redshift evolution of both LF and MF of earliest BHs suggests a rapid decay of their number and mass
+toward higher redshifts of $z>6$, compared to galaxy stellar mass.
+This will be unveiled by future deep and wide surveys with the James Webb Space Telescope, Roman Space Telescope, and Euclid.
 % the , Roman Space Telescope (RST), and Euclid.
@@
 \citep[e.g.,][]{2013ApJ...773...44W,2017ApJ...851L...8V,2021ApJ...914...36I,2022ApJ...927..237I,2022MNRAS.511.3751H}.
-% \red{cite Wang+2013; Venemans+2017, Izumi et al. 2021, Inayoshi+2022 simulation, Habouzit+2022}.
-
-Formation of seed BHs is the starting point to characterize the early assembly of massive BH populations.
-Their formation pathway and expected mass range have been extensively investigated by numerical simulations and
-semi-analytical studies
-%From Pop III star remnants ($10-10^3 ~\Msun$) to direct collapse supermassive stars (10$^4-10^5 ~\Msun$),
-%the properties of high-$z$ BH seeds are extensively modeled by simulations and semi-analytical works
-%\citep[e.g.,][Toyouchi 2022]{2001ApJ...546..635O,2002Sci...295...93A,2006ApJ...652....6Y,2011MNRAS.416.2748I,
-%2012ApJ...756...93H,2013ApJ...778..178H,2014MNRAS.439.3798F,
-%2014MNRAS.445L.109I,2014MNRAS.445..544S,2014MNRAS.445..107V,2020MNRAS.499.5960S}.
+
+The shapes of the QLF and BHMF contain key information on the physics characterizing the radiative 
+and accretion processes of high-z SMBHs, as well as seeding mechanisms in principle.
+Two approaches have been utilized to model those distribution functions.  
+The first is semi-analytical modeling, in which BH seed formation, gas accretion, and BH mergers associated 
+with the hierarchical growth of the parent dark-matter halos are taken into account in a simplified way. 
+This is an effective way of examining the statistical properties of BH populations and making predictions 
+that can be directly compared with the QLF and BHMF
+\citep[e.g.,][]{1998ApJ...503..505H,2010ApJ...718..231S,2018MNRAS.474.1995R,2018MNRAS.481.3278R,
+2021MNRAS.508.2706Y,2021ApJ...910L..11K,2022MNRAS.511..616T}. 
+However, due to the limitation of capturing detailed properties of the relevant physics, 
+a large number of model parameters need to be calibrated based on the observed distribution functions 
+of lower-$z$ quasar population \citep[e.g.,][]{2007ApJ...669...45H}
+and empirical correlations between the SMBH mass and their host galaxy properties seen
+in the local universe \citep{2013ARA&A..51..511K}.
+The second approach is more phenomenological, using extrapolation of the low-$z$ QLF evolution with 
+fitting function forms \citep[e.g.,][]{2020MNRAS.495.3252S,2022arXiv220702233F}.
+This method also allows us to forecast the higher-$z$ QLF and bring insights for future surveys.
+Nevertheless, those semi-analytical and phenomenological approaches introduce numerous physical parameters
+and make the key mechanisms reproducing the observed results obscure.
+Therefore, it is required to construct a theoretical model that is characterized by a minimum number of parameters
+but capable of dealing with essential physical processes.
+
+To determine the initial conditions of the early BH assembly,
+the formation pathway of seed BHs has been extensively investigated by numerical simulations and semi-analytical studies
+%Formation of seed BHs is the starting point to characterize the early assembly of massive BH populations.
+%Their formation pathway and expected mass range have been extensively investigated by numerical simulations and
+%semi-analytical studies
 \citep{2006MNRAS.370..289B,2009ApJ...696.1798T,2012MNRAS.422.2051N,2014ApJ...781...60H,
 2015MNRAS.448..568H,2018MNRAS.474.3825V,2021MNRAS.506..613S,2022arXiv220614459T}.
-% \red{KI: I think here we should cite more general citations: Begelman+2006; Tanaka \& Haiman 2009; Hirano+14, 15,
-% Toyouchi+2022, one Natarajan+Volonteri's paper discussing the mass function, Valiante+2018, Sassano+21}
 Massive star formation episodes in the early universe is substantially modulated by external environmental effects such as
-%factors which modulate the Pop III star formation have been assessed,
 (i) H$_2$ photo-dissociating irradiation from nearby galaxies
-%irradiation in Lyman-Werner band which photo-dissociates the major coolant $\hh$
 \citep{2001ApJ...546..635O,2002ApJ...569..558O,2003Natur.425..812B,2010MNRAS.402.1249S,2014MNRAS.445..544S,2014MNRAS.445..107V,2016ApJ...832..134C},
-% \red{KI: add Chon+16},
 (ii) supersonic baryonic streaming motion that delays gas collapse in halos
 \citep{2012MNRAS.424.1335F, 2014MNRAS.439.1092T, 2018ApJ...855...17H,2017MNRAS.471.4878S,2018MNRAS.479.4017I},
-% \red{KI: add Inayoshi, Li \& Haiman 18, Schauer +17},
-and
-(iii) dynamical heating caused by frequent halo mergers and turbulence injection led by cold accretion flows
+and (iii) dynamical heating caused by frequent halo mergers and turbulence injection led by cold accretion flows
 \citep{2003ApJ...592..645Y,2010Natur.466.1082M,2015ApJ...810...51M,2019Natur.566...85W,2022Natur.607...48L}.
-% \red{KI: add Latif's Nature paper, Mayer+10 or 15}.
 Those effects keep isothermal collapse ($T\sim 8000~{\rm K}$) of massive gas at high accretion rates of $\gtrsim 0.1~\Msunyr$
-without vigorous fragmentation \citep{2014MNRAS.445L.109I,2015MNRAS.446.2380B,2016PASA...33...51L},% \red{KI: add Becerra+15, Latif+16}, 
+without vigorous fragmentation \citep{2014MNRAS.445L.109I,2015MNRAS.446.2380B,2016PASA...33...51L},
 and allow supermassive stars with $\sim 10^5~\Msun$ (presumably seed BHs) to form at the halo centers 
 \citep{2013ApJ...778..178H,2013A&A...558A..59S,2019PASA...36...27W,2022arXiv220614459T}.
-% \red{cite Hosokawa+13, Woods+19?, Schleicher+13, Toyouchi+22}.
 Although the conditions required for heavy seed formation are thought to be too stringent to be realized in the typical regions of the early universe
 \citep{2008MNRAS.391.1961D,2009ApJ...695.1430A,2015MNRAS.450.4350I},
-% \red{cite Dijkstra+08, Ahn+09, Inayoshi \& Tanaka 15}, 
 recent studies by \citet{2021MNRAS.503.5046L} and \citet{2021ApJ...917...60L} found that the heavy-seed formation
@@
 and the frequency of halo mergers.
-%These factors prevail in some environments at high redshifts and facilitate massive Pop III and even supermassive star formation,
-%which contribute to the heavy seed scenario of supermassive BH formation at $z\gtrsim$ 6
-%\citep[see a review by][]{2020ARA&A..58...27I}.
-
-\red{Introduction of previous studies on QLFs for high-$z$ populations. mention Yung's paper, Ricarte \& Natarajan paper, recent Finkelstein's paper?
-Also, I remember one paper of our former postdoc, Kim.
-Also, recent Raffaella's student's paper and "highly-empirical paper" you introduced.
-Please add more (I might miss some relevant papers.)}
-\blue{
-% Haiman \& Loeb 1997.
-% High-z
-}
-
+As a result, \citet{2021ApJ...917...60L} predicted a top-heavy mass distribution of seed BHs ranging from $10^2-10^5~\Msun$.
+
+In this paper, we propose a theoretical model for the redshift-dependent QLF and BHMF at $z\gtrsim 6$,
+% applying the initial mass function (IMF) of seed BHs obtained from \cite{2021ApJ...917...60L}.
+applying the semi-analytic seed formation model from \cite{2021ApJ...917...60L} to study the BH growth in common regions in the early universe.
+We assume that the early BH population experiences multiple accretion bursts, in each of which the Eddington ratio is assigned 
+following a Schechter distribution function. 
+We conduct the Markov Chain Monte Carlo (MCMC) fitting procedure to optimize the BH growth parameters 
+so that the observed BHMF and QLF at $z\simeq 6$ are simultaneously reproduced. 
+Our best-fit model suggests several episodes of modest super-Eddington accretion and requires
+individual burst durations of $\simeq 20-30$ Myr to avoid over(under)-production of BHs at the high-mass end.
+Furthermore, we construct the redshift-dependent QLF and BHMF that imply a rapid decay of 
+their number and mass toward higher redshifts of $z>6$.
+We also find that the observed Eddington-ratio distribution function is skewed to a log-normal shape from the intrinsic Shechter function
+owing to detection limits of quasar observations.
+Those results will be unveiled by future deep and wide surveys with the James Webb Space Telescope, Roman Space Telescope, and Euclid.
+
+\if0
 To construct the picture of BH evolution, the initial mass function (IMF) of BH seeds is required.
@@
 % our aim is to understand the growth patterns of early BHs.
+\fi
 

### 2022-08-05 ms.tex
version 0805; N_detect added; GLF+QLF plot; summary from k

@@
 which are estimated by the measurement of the physical extents of hydrogen Ly$\alpha$ proximity zones 
-observed in the rest-frame UV spectra (e.g., Eilers+2018, Davies+ 2019).\red{KI: we need to figure out 
-if their $t_Q$ is the quasar age or lifetime, or something else?}
+observed in the rest-frame UV spectra \citep[e.g.,][]{2018ApJ...867...30E,2019ApJ...884L..19D}.
+% \red{KI: we need to figure out if their $t_Q$ is the quasar age or lifetime, or something else?}
 More detailed comparison is discussed in \S\ref{sec:evol}.
@@
 evaluated by the integration of the BHMF shown in the left panel.
-The evolutionary trend can be approximated as $\rho_\bullet (z) \propto 10^{k_M z}$, where $k_M\simeq -0.8$.
+The evolutionary trend can be approximated as $\rho_\bullet (z) \propto 10^{k_M z}$, where $k_M\simeq -0.68$.
 }
@@
 \hline
-10$^7$  &  $-5.91\pm 0.28$  &  $-0.58 \pm 0.21$  \\
-10$^8$  &  $-6.93\pm 0.47$  &  $-0.78 \pm 0.31$  \\
+10$^7$  &  $ 1.81\pm 0.28$  &  $-0.68 \pm 0.21$  \\
+10$^8$  &  $ 1.54\pm 0.47$  &  $-0.84 \pm 0.31$  \\
 % 10$^9$  &  $-8.30_{-0.47}^{+0.47}$  & $-1.04_{-0.58}^{+0.54}$ \\
-10$^9$  &  $-8.30\pm 0.47$  &  $-1.04 \pm 0.58$ \\
+10$^9$  &  $ 1.01\pm 0.47$  &  $-1.01 \pm 0.58$ \\
 \hline 
@@
 \end{table}
+
+\begin{table*}
+{ % group it, so that centering can work?
+\centering
+\renewcommand\thetable{2} %! fix indexing
+\caption{Detection number of quasars estimated for future surveys}
+% \tablenum{2}
+\begin{tabular}{lcccccccccccc}
+\hline Telescope & Survey area & Photo. depth & $N(z\sim 6)$ & $N(z\sim 7)$ & $N(z\sim 8)$ & $N(z\sim 9)$ & $N(z\sim10)$ \\
+& (\rm{deg}$^2$) & (AB~mag) \\
+\hline 
+% 6758..6598057248175, 1514.3392258726712, 349.27228533671644, 85.15836783444871, 25.
+Deep \it{LSST}   & 18000 & 27.5 & 73865 & 18470 &  4688 & 1237 & 389\\
+Wide \it{RST}    &  2000 & 27   & 6758 &  1514 &  349 & 85 & 25  \\
+Wide \it{Euclid} & 15000 & 24   & 6653  &  708 &   93 & 14 & 2  \\
+\hline
+\end{tabular}
+\label{tab:N_detect}
+}
+\end{table*}
 
@@
 For all the redshifts, the BHMFs can be characterized with a double power-law function, similar to lower-$z$ quasar populations.
-From higher to lower redshifts, the number density of BHs heavier than $M_\bullet = 10^7~\Msun$ increases
+From higher to lower redshifts, the number density of BHs heavier than $M_{\rm min} = 10^7~\Msun$ increases
 and the high-mass tail of the distribution is extended owing to efficient growth of the most massive BH population.
@@
 \begin{equation}
- \rho_\bullet(z)=\int_{M_{\rm min}}^{\infty} \Phi_{\Mbh} (z) \Mbh \D \log \Mbh,
+ \rho_\bullet(z)=\int_{M_{\rm min}}^{\infty} \Phi_{\Mbh} (z) \Mbh \D \log \Mbh.
 \end{equation}
@@
 %as a function of redshift.
-where we set the minimum mass to $M_{\rm min}=10^7$, $10^8$, and $10^9~\Msun$.
-This result shows that the early BH assembly takes place rapidly and the redshift-dependence can be approximated by
+Varying the minimum mass as $M_{\rm min}=10^7$, $10^8$, and $10^9~\Msun$,
+we find that the early BH assembly takes place rapidly and the redshift-dependence can be approximated by
 %
@@
 \subsection{Quasar luminosity function}
-
-Next, we show the QLFs at different redshifts of $z=6-10$ taken from the BH growth model in the left panel of Fig.~\ref{fig:QLF_rhoz}.
-%The model QLFs we propose give interesting prediction and will be further constrained by higher redshift quasar observations.
-\red{KI: add more explanations about the QLFs. How about the detection limits of Euclid, Roman, and others?
-Also, you could compare your results with Aaron Yung's results.}
-In the right panel of Fig.~\ref{fig:QLF_rhoz}, we present the number density of luminous quasars with $\Muv <-26$ as a function of redshift.
+On the other hand, the statistics of BH masses together with the ERDF in their growth history can rebuild quasar luminosity functions across cosmic time,
+which is interesting to be probed with future observations.
+In Fig.~\ref{fig:LFs}, we show the QLF prediction by the best-fit model with 1-$\sigma$ scatter at redshifts $z=$ 7 to 10.
+Considering the scarcity of faint quasars ($\Muv\gtrsim -20$) sampled in \citet{2014ApJ...786..104U},
+we emphasize that the observed (Type I) QLF after the current obscuration prescription can be highly uncertain in the faint end,
+which is to be improved by the future equipments.
+% More thorough studies on the high-$z$ quasar obscuration by upcoming equipments will improve the understanding on this aspect.
+We also produce the intrinsic (Type I and Type II) luminosity function without obscuration effects.
+The QLF emgerging from high redshifts quickly evolves toward brighter luminosity 
+with the number of quasars increases as BHs grow.
+
+Thanks to numerous efforts in the high-$z$ galaxy observation field,
+we overlay the galaxy UV luminosity function at each redshift,
+with both binned data points and the fitting functions in Schechter and double power law (DPL) shape
+\citep{2021AJ....162...47B,2022ApJS..259...20H,2020MNRAS.493.2059B,2022arXiv220712356D,2013MNRAS.432.2696M,2019ApJ...883...99S,
+2022ApJ...929....1H,2018ApJ...867..150M,2022arXiv220801612H,2016ApJ...819..129O,2022arXiv220709434N}.
+Compared to our QLF predictions, galaxies prevail in the faint end at all these redshifts,
+with their LFs quickly declines toward the luminous end.%, where quasars outshine.
+The large number of galaxies with $\Muv\gtrsim -23$ makes it prohibitive to probe rare quasars among the faint objects detected.
+While with increasing luminosity, the extrapolation of galaxy LF curve with the Schechter fitting function drops quickly,
+crossing the QLF at $\Muv$ at critical values of $\Muv\sim-23$, $-24$, and $-25$ at redshifts $z=7-8$, $9$, and $10-13$, respectively.
+While for the galaxy LF fitted by DPL function,
+the corresponding crossing point shifts to $\Muv\sim-26$, $-25$, and $\ll -30$.
+Therefore the galaxy contamination effect on quasar observations still remains model-dependent. 
+In the future, deep and wide-field surveys e.g.,
+Deep {\it{LSST}} \citep{2017arXiv170801617R}, Wide {\it{RST}} \citep{2019arXiv190205569A}, and Wide {\it{Euclid}} \citep{2011arXiv1110.3193L}
+will be crucial to construct the LF data for high-$z$ quasars and galaxies,
+categorizing them by spectroscopic diagnostics.
+We show the detection limit of these surveys at each redshift in Fig.~\ref{fig:LFs},
+demonstrating their capability of optimizing high-$z$ galaxy and quasar observations.
+The adopted survey parameters is shown in Table.~\ref{tab:N_detect}.
+The depths of detection will be pushed down to $\Muv\lesssim -20$,
+which is able to uncover the critical luminosities at which the numbers of galaxies and quasars are comparable.
+The number of high-$z$ quasars are also predicted at each redshift (Table.~\ref{tab:N_detect}),
+with the assumption of the survey volume with $\Delta z =1$ and 100\% completeness.
+The large sample of objects at those high redshifts will shed light on
+the early coevolution of galaxies and BHs in a statistically unbiased way.
+
+% Next, we show the QLFs at different redshifts of $z=6-10$ taken from the BH growth model in the left panel of Fig.~\ref{fig:QLF_rhoz}.
+% %The model QLFs we propose give interesting prediction and will be further constrained by higher redshift quasar observations.
+% \red{KI: add more explanations about the QLFs. How about the detection limits of Euclid, Roman, and others?
+% Also, you could compare your results with Aaron Yung's results.}
+In Fig.~\ref{fig:QLF_rhoz}, we present the number density of luminous quasars with $\Muv <-26$ as a function of redshift.
 The evolutionary trend can be fitted as $\propto 10^{k_{\rm L}z}$, where $k_{\rm L}\approx -0.97$.
@@
 %and this calls consideration of the more realistic BH-galaxy coevolution in understanding the observable AGN properties.
+
+\begin{figure*}
+\gridline{\fig{M0r8_f2linLF_spreadz7_KI.pdf}{0.45\textwidth}{}
+          \fig{M0r8_f2linLF_spreadz8_KI.pdf}{0.45\textwidth}{}}
+\gridline{\fig{M0r8_f2linLF_spreadz9_KI.pdf}{0.45\textwidth}{}
+          \fig{M0r8_f2linLF_spreadz10_KI.pdf}{0.45\textwidth}{}}
+\caption{QLF evolution at redshifts from $z=7$ to $z\gtrsim 10$.
+In all panels the solid lines denote modeled QLF produced by the best-fit parameters and the shaded regions present the $1\sigma$ spread. 
+The intrinsic QLF without obscuration effect is shown in the dashed lines,
+deviating from the observed QLF mostly in the faint end.
+The expected depths and volumes of future surveys with
+Deep {\it{LSST}}, Wide {\it{RST}}, and Wide {\it{Euclid}} are overlaid with the blue thin lines,
+indicating the detectability of quasars at these redshifts.
+High-$z$ galaxy LF data points (grey) and fitting functions in the Schechter (dotted  magenta line) and DPL (dash-dotted  magenta line) shapes are shown.
+With the extrapolated galaxy LFs in different shapes,
+the galaxy contamination effect on quasar selection can be estimated.
+\label{fig:LFs}}
+\end{figure*}
 
@@
 
-\red{KI: still not sure what we discuss below... among the 7 BHs, is anyone consistent with Feige's BH?}
+% \red{KI: still not sure what we discuss below... among the 7 BHs, is anyone consistent with Feige's BH?}
 In \citet{2021ApJ...907L...1W}, they discover the currently known most distant quasar at $z=7.642$, 
@@
 
+\section{Summary}
+In this paper, we propose a theoretical model for the redshift-dependent QLF and BHMF at $z\gtrsim 6$,
+applying the initial mass function of seed BHs.
+We assume that the early BH population experiences multiple accretion bursts, in each of which the Eddington ratio
+is assigned following a Schechter distribution function.
+We conduct the MCMC fitting procedure used to optimize the BH growth parameters
+so that the observed BHMF and QLF at $z\simeq 6$ are simultaneously reproduced.
+Our best-fit model to reproduce the QLF and BHMF at $z\simeq 6$ yields the ERDF characterized with the two parameters of
+$(\lambda_0, \alpha)=(0.89,0.12)$ and $(0.87,0.20)$ for the BH seeding fraction of $\fseed = 0.01$ and $0.1$, respectively.
+The models suggests that several episodes of modest super-Eddington accretion occur and each accretion phase lasts $\simeq 20-30$ Myr.
+For longer (and shorter) burst durations, the number of BHs at the high mass end is over(-under) produced.
+Therefore, multiple accretion bursts with variable Eddington ratios enable the early BH population to grow and shine,
+consistent with the observed distribution functions.
+Using the best-fit model parameters, we construct the redshift-dependent QLF and BHMF at $6\leq z \leq 10$.
+The two functions suggest a rapid decay of the number and mass density of massive BHs and luminous quasars in a cosmic volume
+toward higher redshifts as $\propto 10^{-k_i z}$, where $k_{\rm M}\simeq -0.68$ for the BH mass and $k_{\rm L}=$ for the quasar number.
+The predicted value of the decay slope $k_{\rm L}$ is consistent with that estimated by previous observations for $z\simeq 6-7$ quasars
+but tends to be slightly steeper at higher redshifts.
+\red{Add comparison to GLFs and expected detection numbers }\blue{
+Comparing to galaxy LFs at redshifts from $z=7$ to $z\gtrsim 10$, the QLFs we predict is burried in the faint end at $\Muv \gtrsim -23$ by the huge galaxy population,
+which raises the challenge of select quasars from the high-$z$ faint objects.
+While in the luminous end, quasars account for a significant fraction of high-$z$ UV luminosity function,
+we predict the critical luminosity at which galaxy and quasars make equal contribution,
+depending on the fitting function form of galaxy LFs.}
+We further explore individual BH evolutionary tracks starting from the BH seeds, applying the BH growth model
+with the best-fit parameters reproducing their statistical properties.
+For massive BHs that reach $\gtrsim 10^8~\Msun$ by $z\simeq 6$, the average duty cycle of accretion is as high as $\simeq 15~\%$.
+Since the duty cycle is nearly twice that of the entire population, the BH samples observed in $z\simeq 6$ quasars are
+biased toward a population that undergoes active accretion episodes.
+Multiple accretion-burst treatment nicely produces the mass assembly history of individual high$-z$ luminous quasars,
+unlike the case where one single value of the Eddington ratio is assigned.
+We also find that the observed Eddington-ratio distribution function is skewed to a log-normal shape from the intrinsic Shechter function
+owing to detection limits of quasar observations.
+Those results will be unveiled by future deep and wide surveys with the JWST, LSST, RST, and Euclid.
+
 % \begin{acknowledgments}

### 2022-08-07 ms.tex
version0806; complete before k send to collegues

--- 2022-07-31 ms.tex
@@
 \usepackage{CJK}
+\usepackage{lipsum}
 
@@
 \citep{2008AJ....135.1057J,2010AJ....139..906W,2016arXiv161205560C,2016ApJ...833..222J,2018PASJ...70S..35M,2019ApJ...883..183M,2019AJ....157..168D}
-along with the quasar luminosity function \citep[e.g.,][]{2018ApJ...869..150M}.
+along with the quasar luminosity function \citep[e.g.,][]{2015ApJ...798...28K,2018ApJ...869..150M}.
 %and the virial BH mass estimates
@@
 \citep{2006MNRAS.370..289B,2009ApJ...696.1798T,2012MNRAS.422.2051N,2014ApJ...781...60H,
-2015MNRAS.448..568H,2018MNRAS.474.3825V,2021MNRAS.506..613S,2022arXiv220614459T}.
+2015MNRAS.448..568H,2018MNRAS.474.3825V,2021MNRAS.506..613S,2022arXiv220614459T,2022arXiv220505717B}.
 Massive star formation episodes in the early universe is substantially modulated by external environmental effects such as
@@
 \centering
-\includegraphics[width=160mm]{seedBHMF_z.pdf}
+\includegraphics[width=160mm]{seedBHMF_z.png}
 \caption{
@@
 In each panel, the cumulative number distribution of BHs are shown and 
-the contribution from newly-born BHs at the redshift interval are denoted with the hatched region.
+the contribution from newly-born BHs at the redshift interval are highlighted in magenta.
 %with the newly formed BHs denoted by the hatched regions, 
@@
 With BH seeds planted, we grow the BHs with a semi-analytical accretion rate model and study the evolution of the BH mass distribution until $z=6$. 
-\blue{(references + discussion)}
+% \blue{(references + discussion)}
 The growth model is characterized by a minimal number of free parameters, 
@@
 \label{fig:tau}
+\vspace{4mm}
 \end{figure*}
@@
 evaluated by the integration of the BHMF shown in the left panel.
-The evolutionary trend can be approximated as $\rho_\bullet (z) \propto 10^{k_M z}$, where $k_M\simeq -0.8$.
+The evolutionary trend can be approximated as $\rho_\bullet (z) \propto 10^{k_M z}$, where $k_M\simeq -0.68$.
 }
 \label{fig:BHMF_rhoz}
+\vspace{4mm}
 \end{figure*}
-
-\begin{table}
-\renewcommand\thetable{1} %! fix indexing
-\caption{$\rho_\bullet(z)$ Evolution Parameters}
-\begin{center}
-% \tablenum{1}
-\begin{tabular}{l c r}
-\hline
-$M_{\rm min}$ & $\log \rho_{\bullet,0}$ & $k_{\rm M}$ ~~~ \\ 
-\hline 
-\hline
-10$^7$  &  $-5.91\pm 0.28$  &  $-0.58 \pm 0.21$  \\
-10$^8$  &  $-6.93\pm 0.47$  &  $-0.78 \pm 0.31$  \\
-% 10$^9$  &  $-8.30_{-0.47}^{+0.47}$  & $-1.04_{-0.58}^{+0.54}$ \\
-10$^9$  &  $-8.30\pm 0.47$  &  $-1.04 \pm 0.58$ \\
-\hline 
-\end{tabular}
-\label{tab:MFz}
-\end{center}
-\end{table}
 
@@
 
+%%%%%%%
+%    Table. 1 
+%%%%%%%
+\begin{table}
+\renewcommand\thetable{1} %! fix indexing
+\caption{$\rho_\bullet(z)$ Evolution Parameters}
+\begin{center}
+% \tablenum{1}
+\begin{tabular}{l c r}
+\hline
+\hline
+$M_{\rm min}$ & $\log \rho_{\bullet,0}$ & $k_{\rm M}$ ~~~ \\ 
+\hline 
+10$^7$  &  $ 1.81\pm 0.28$  &  $-0.68 \pm 0.21$  \\
+10$^8$  &  $ 1.54\pm 0.47$  &  $-0.84 \pm 0.31$  \\
+% 10$^9$  &  $-8.30_{-0.47}^{+0.47}$  & $-1.04_{-0.58}^{+0.54}$ \\
+10$^9$  &  $ 1.01\pm 0.47$  &  $-1.01 \pm 0.58$ \\
+\hline 
+\end{tabular}
+\label{tab:MFz}
+\end{center}
+\end{table}
+
+%%%%%%%
+%    Fig. 
+%%%%%%%
+\begin{figure*}
+\centering
+\includegraphics[width=160mm]{QLF_rhoz.png}
+\caption{
+{\it Left panel}: quasar luminosity functions at different redshifts of $6\leq z \leq 10$. 
+The solid lines denote modeled QLF produced by the best-fit parameters and the shaded regions present the $1\sigma$ spread. 
+{\it Right panel}: the redshift evolution of the cumulative number density of quasars with $\Muv <-26~{\rm mag}$ in a comoving volume,
+evaluated by the integration of the QLF shown in the left panel.
+The evolutionary trend can be approximated as $n(\Muv<-26~{\rm mag})\propto 10^{k_{L} z}$, where $k_L \simeq -0.96$.
+This result indicates rapid decline of the number of bright quasars toward higher redshifts, consistent with previous observations
+\citep[red data points; see][]{2016ApJ...833..222J, 2019ApJ...884...30W}
+}
+\label{fig:QLF_rhoz}
+\vspace{5mm}
+\end{figure*}
+
 \subsection{Quasar luminosity function}
@@
 Next, we show the QLFs at different redshifts of $z=6-10$ taken from the BH growth model in the left panel of Fig.~\ref{fig:QLF_rhoz}.
-%The model QLFs we propose give interesting prediction and will be further constrained by higher redshift quasar observations.
-\red{KI: add more explanations about the QLFs. How about the detection limits of Euclid, Roman, and others?
-Also, you could compare your results with Aaron Yung's results.}
-In the right panel of Fig.~\ref{fig:QLF_rhoz}, we present the number density of luminous quasars with $\Muv <-26$ as a function of redshift.
+Similar to the BHMF, for all the redshift range, the shape of the QLF is well approximated with a double power-law function.
+From higher to lower redshifts, the number density of luminous quasars increases and the bright-end of the distribution is extended.
+% %The model QLFs we propose give interesting prediction and will be further constrained by higher redshift quasar observations.
+% \red{KI: add more explanations about the QLFs. How about the detection limits of Euclid, Roman, and others?
+% Also, you could compare your results with Aaron Yung's results.}
+In the right panle of Fig.~\ref{fig:QLF_rhoz}, we present the number density of luminous quasars with $\Muv <-26~{\rm mag}$ as a function of redshift.
 The evolutionary trend can be fitted as $\propto 10^{k_{\rm L}z}$, where $k_{\rm L}\approx -0.97$.
@@
 
-%%%%%%%
-%    Fig. 
-%%%%%%%
-\begin{figure*}
+%On the other hand, the statistics of BH masses together with the ERDF in their growth history can rebuild quasar luminosity functions across cosmic time,
+%which is interesting to be probed with future observations.
+In Fig.~\ref{fig:LFs}, we divide the cosmological QLF into four different epochs; (a) $z\simeq 7$, (b) $z\simeq 8$, (c) $z\simeq 9$, and (d) $z\simeq 10-13$.
+The black solid and dashed curves present the QLF for the unobscured population (i.e., type-I AGNs, same as those in Fig.~\ref{fig:QLF_rhoz})
+and the whole population (i.e., type-I and type-II AGNs).
+We note that the AGN obscured fraction based on X-ray samples \citep{2014ApJ...786..104U} is applied to faint objects, 
+but the correction factor is highly uncertain at the faint end of $\Muv\gtrsim -20$ mag.
+% sampled in \citet{2014ApJ...786..104U},
+%we emphasize that the observed (Type I) QLF after the current obscuration prescription can be highly uncertain in the faint end,
+%ßwhich is to be improved by the future equipments.
+% More thorough studies on the high-$z$ quasar obscuration by upcoming equipments will improve the understanding on this aspect.
+%We also produce the intrinsic (Type I and Type II) luminosity function without obscuration effects.
+%The QLF emgerging from high redshifts quickly evolves toward brighter luminosity 
+%with the number of quasars increases as BHs grow.
+We also overlay the expected depths and volumes of upcoming survey programs (blue lines) with Wide Euclid \citep{2011arXiv1110.3193L}
+and Wide RST \citep{2019arXiv190205569A}.
+Table.~\ref{tab:N_detect} summarizes the expected number of detected quasars in each survey. 
+Euclid will identify quasars up to $z\sim 8$ and discover $O(100-1000)$ quasars at $z\simeq 7-8$.
+The RST will be able to explore the very faint ($\Muv>-22$ mag) but abundant quasar population even at $z>10$, in principle,
+after subtracting galaxy contaminants.
+
+%will be crucial to construct the LF data for high-$z$ quasars and galaxies,
+%categorizing them by spectroscopic diagnostics.
+%We show the detection limit of these surveys at each redshift in Fig.~\ref{fig:LFs},
+%demonstrating their capability of optimizing high-$z$ galaxy and quasar observations.
+%The adopted survey parameters is shown in Table.~\ref{tab:N_detect}.
+%The depths of detection will be pushed down to $\Muv\lesssim -20$,
+%which is able to uncover the critical luminosities at which the numbers of galaxies and quasars are comparable.
+%The number of high-$z$ quasars are also predicted at each redshift (Table.~\ref{tab:N_detect}),
+%with the assumption of the survey volume with $\Delta z =1$ and 100\% completeness.
+%The large sample of objects at those high redshifts will shed light on
+%the early coevolution of galaxies and BHs in a statistically unbiased way.
+
+We also show the galaxy UV luminosity function in each panel
+%Thanks to numerous efforts in the high-$z$ galaxy observation field,
+%we overlay the galaxy UV luminosity function at each redshift,
+along with the fitting functions in a Schechter (dotted curves) and double power law (dashed-dotted curves) shape extended to the brighter end
+\citep{2021AJ....162...47B,2022ApJS..259...20H,2020MNRAS.493.2059B,2022arXiv220712356D,2013MNRAS.432.2696M,2019ApJ...883...99S,
+Harikane_2022b,2018ApJ...867..150M,Harikane_2022c,2016ApJ...819..129O,2022arXiv220709434N}.
+Compared to our QLF predictions, those galaxies prevail in the faint end at all these redshifts and the number decreases toward the luminous end.
+The large number of galaxies with $\Muv\gtrsim -23$ mag makes it difficult to probe rare quasars among those faint objects.
+Since extrapolated galaxy LFs with a Schechter shape decline quickly with the luminosity increasing,
+the galaxy LFs cross the QLFs at $\Muv$ with critical values of $\Muv \sim -23$, $-24$, and $-25$ mag at redshifts $z=7-8$, $9$, and $10-13$, respectively.
+On the other hand, if the galaxy LFs are extended with a power law, the corresponding crossing magnitude shifts to $\Muv\sim-26$, $-25$, and $\ll -30$ mag.
+%Therefore the galaxy contamination effect on quasar observations still remains model-dependent. 
+Therefore, future deep and wide surveys will lead to significant progress understanding the relative 
+contribution of both populations to astrophysical phenomena in the cosmic dawn.
+
+%%%%%%%
+%    Fig. 9
+%%%%%%%
+\begin{figure*}[h!]
 \centering
-\includegraphics[width=160mm]{QLF_rhoz.png}
-\caption{
-{\it Left panel}: quasar luminosity functions at different redshifts of $6\leq z \leq 10$. 
-The solid lines denote modeled QLF produced by the best-fit parameters and the shaded regions present the $1\sigma$ spread. 
-{\it Right panel}: the redshift evolution of the cumulative number density of quasars with $\Muv <-26~{\rm mag}$ in a comoving volume,
-evaluated by the integration of the QLF shown in the left panel.
-The evolutionary trend can be approximated as $n(\Muv<-26~{\rm mag})\propto 10^{k_{L} z}$, where $k_L \simeq -0.95$.
-This result indicates rapid decline of the number of bright quasars toward higher redshifts, consistent with previous observations
-\citep[red data points; see][]{2016ApJ...833..222J, 2019ApJ...884...30W}
+\includegraphics[width=85mm]{M0r8_f2linLF_spreadz7_KI.pdf}\hspace{5mm}
+\includegraphics[width=85mm]{M0r8_f2linLF_spreadz8_KI.pdf}\\\vspace{5mm}
+\includegraphics[width=85mm]{M0r8_f2linLF_spreadz9_KI.pdf}\hspace{5mm}
+\includegraphics[width=85mm]{M0r8_f2linLF_spreadz10_KI.pdf}
+\caption{Predicted quasar luminosity functions and depths and volumes of upcoming surveys.
+The black solid and dashed curves present the QLF for the unobscured population (e.g., type-I AGNs) 
+and the whole population (i.e., type-I and type-II AGNs), and the shaded region presents the $1\sigma$ spread.
+The expected depths and volumes of future surveys with Wide RST and Wide Euclid are overlaid with the blue lines,
+indicating the detectability of quasars at these redshifts.
+Galaxy UV luminosity functions are plotted with the data points (grey) and fitting functions with a Schechter (dotted curve) and double power-law (dash-dotted curve) shape.
+The galaxy luminosity function data at $z\sim$ 7 are taken from \citet[triangles]{2022ApJS..259...20H} \&
+\citet[circles]{2021AJ....162...47B}, and the fitting functions are produced by \citet{2022ApJS..259...20H}. 
+At $z\sim$ 8, the data points are from \citet[triangles]{2021AJ....162...47B},
+\citet[circles]{2022arXiv220712356D}, \citet[pluses]{2013MNRAS.432.2696M}, \citet[diamond]{2020MNRAS.493.2059B}, and \citet[pentagons]{2019ApJ...883...99S},
+as well as the fitting results by  \citet[double power law]{2020MNRAS.493.2059B} \& \citet[Schechter]{2013MNRAS.432.2696M}.
+At  $z\sim$ 9, those data are from \citet[triangles]{Harikane_2022c}, \citet[circles]{2022arXiv220712356D}, \citet[pluses]{2020MNRAS.493.2059B}, \citet[diamonds]{2019ApJ...883...99S}, and \citet[pentagons]{2018ApJ...867..150M},
+with the fitting functions from  \citet{Harikane_2022c}.
+At $z\sim$ $10-13$, \citet[triangles]{Harikane_2022c},\citet[circles]{2022arXiv220712356D},\citet[pluses]{Harikane_2022b}, \citet[diamonds]{2022arXiv220709434N}, \citet[pentagons]{2018ApJ...867..150M}, and \citet[stars]{2016ApJ...819..129O},
+and the fitting functions are produced by \citet{Harikane_2022c}.
 }
-\label{fig:QLF_rhoz}
+\label{fig:LFs}
 \end{figure*}
+
+%%%%%%%
+%    Table. 2 
+%%%%%%%
+\startlongtable
+\begin{deluxetable*}{lccccccc}%[h!]
+\tablecolumns{2}
+\renewcommand\thetable{2} %! fix indexing
+\tablewidth{0pt} 
+\tablecaption{Detection Number of Quasars Estimated for Future Surveys}
+\tablehead{
+  \colhead{Telescope} & \colhead{ Survey area} & \colhead{Photo. depth} &  \colhead{$N(z\sim 6)$} & \colhead{$N(z\sim 7)$}& \colhead{$N(z\sim 8)$}&  \colhead{$N(z\sim 9)$}&  \colhead{$N(z\sim 10)$}\\
+  \colhead{} & \colhead{(\rm{deg}$^2$)} & \colhead{(AB mag)} & & & & & 
+}
+\startdata
+Wide RST    &  2000 & 27   & 6758 &  1514 &  349 & 85 & 25  \\
+Wide Euclid & 15000 & 24   & 6653  &  708 &   93 & -- & --  \\
+\enddata
+\label{tab:N_detect}
+\tablecomments{
+Based on the 5$\sigma$ point source detection limits, the number of quasars at each redshift are predicted
+with the assumption of the survey volume with $\Delta z =1$ and 100\% completeness.
+}
+\end{deluxetable*}
+
+%In the future, deep and wide-field surveys e.g.,
+%Wide {\it{RST}} \citep{2019arXiv190205569A} and Wide {\it{Euclid}} \citep{2011arXiv1110.3193L,2017MNRAS.470.5007M}
+%will be crucial to construct the LF data for high-$z$ quasars and galaxies,
+%categorizing them by spectroscopic diagnostics.
+%We show the detection limit of these surveys at each redshift in Fig.~\ref{fig:LFs},
+%demonstrating their capability of optimizing high-$z$ galaxy and quasar observations.
+%The adopted survey parameters is shown in Table.~\ref{tab:N_detect}.
+%The depths of detection will be pushed down to $\Muv\lesssim -20$,
+%which is able to uncover the critical luminosities at which the numbers of galaxies and quasars are comparable.
+%The number of high-$z$ quasars are also predicted at each redshift (Table.~\ref{tab:N_detect}),
+%with the assumption of the survey volume with $\Delta z =1$ and 100\% completeness.
+%The large sample of objects at those high redshifts will shed light on
+%the early coevolution of galaxies and BHs in a statistically unbiased way.
 
@@
 %%%%%%%
-%    Fig. 6
+%    Fig. 10
 %%%%%%%
@@
 %%%%%%%
-%    Fig. 7
+%    Fig. 11
 %%%%%%%
@@
 
+\section{Summary}
+In this paper, we propose a theoretical model for the redshift-dependent QLF and BHMF at $z\gtrsim 6$,
+applying the initial mass function of seed BHs.
+We assume that the early BH population experiences multiple accretion bursts, in each of which the Eddington ratio
+is assigned following a Schechter distribution function.
+We conduct the MCMC fitting procedure used to optimize the BH growth parameters
+so that the observed BHMF and QLF at $z\simeq 6$ are simultaneously reproduced.
+Our best-fit model to reproduce the QLF and BHMF at $z\simeq 6$ yields the ERDF characterized with the two parameters of
+$(\lambda_0, \alpha)=(0.89,0.12)$ and $(0.87,0.20)$ for the BH seeding fraction of $\fseed = 0.01$ and $0.1$, respectively.
+The models suggests that several episodes of modest super-Eddington accretion occur and each accretion phase lasts $\simeq 20-30$ Myr.
+For longer (and shorter) burst durations, the number of BHs at the high mass end is over(-under) produced.
+Therefore, multiple accretion bursts with variable Eddington ratios enable the early BH population to grow and shine,
+consistent with the observed distribution functions.
+Using the best-fit model parameters, we construct the redshift-dependent QLF and BHMF at $6\leq z \leq 10$.
+The two functions suggest a rapid decay of the number and mass density of massive BHs and luminous quasars in a cosmic volume
+toward higher redshifts as $\propto 10^{-k_i z}$, where $k_{\rm M}\simeq -0.68$ for the BH mass and $k_{\rm L}=-0.96$ for the quasar number.
+The predicted value of the decay slope $k_{\rm L}$ is consistent with that estimated by previous observations for $z\simeq 6-7$ quasars
+but tends to be slightly steeper at higher redshifts.
+% \red{Add comparison to GLFs and expected detection numbers }\blue{
+Compared to the galaxy luminosity functions at redshifts from $z=7$ to $z\gtrsim 10$, the QLFs we predict are burried in the faint end at $\Muv \gtrsim -23$ mag,
+which makes it more challenging to select such faint quasars.
+The number of quasars dominates over that of galaxies in the bright end of the UV luminosity function.
+We predict the critical magnitude at which galaxies and quasars equally contribute in number,
+depending on extrapolation of the galaxy luminosity functions.
+We further explore individual BH evolutionary tracks starting from the BH seeds, applying the BH growth model
+with the best-fit parameters reproducing their statistical properties.
+For massive BHs that reach $\gtrsim 10^8~\Msun$ by $z\simeq 6$, the average duty cycle of accretion is as high as $\simeq 15~\%$.
+Since the duty cycle is nearly twice that of the entire population, the BH samples observed in $z\simeq 6$ quasars are
+biased toward a population that undergoes active accretion episodes.
+Multiple accretion-burst treatment nicely produces the mass assembly history of individual high$-z$ luminous quasars,
+unlike the case where one single value of the Eddington ratio is assigned.
+We also find that the observed Eddington-ratio distribution function is skewed to a log-normal shape from the intrinsic Shechter function
+owing to detection limits of quasar observations.
+Those results will be unveiled by future deep and wide surveys with the JWST, RST, and Euclid.
+
 % \begin{acknowledgments}

### 2022-08-16 ms.tex
version0807; k revise and recieve comments from DT,MO...

@@
 %\documentclass[nolinenumbers,preprint2,tighten]{aastex631}
-\hypersetup{filecolor=cyan,urlcolor=magenta} %citecolor=green, linkcolor=red,
+\hypersetup{filecolor=cyan,urlcolor=blue} %citecolor=green, linkcolor=red,
 \newcommand{\vdag}{(v)^\dagger}
@@
 
-\correspondingauthor{}
-\email{}
+\correspondingauthor{Wenxiu Li; Kohei Inayoshi}
+\email{wenxiuli@pku.edu.cn; inayoshi@pku.edu.cn}
 
@@
 \begin{abstract}
-The early evolution of the quasar luminosity and black hole mass function (MF) encodes key information
-on the physics determining the radiative and accretion processes of supermassive black holes (SMBHs) in high-redshift quasars.
-Although the shape of the luminosity function (LF) has been constrained by recent wide and deep surveys,
-it still remains challenging to develop a theoretical model that explains the redshift evolution and BH growth self-consistently.
+The early evolution of the quasar luminosity function (QLF) and black hole mass function (BHMF) encodes 
+key information on the physics determining the radiative and accretion processes of supermassive 
+black holes (SMBHs) in high-redshift quasars.
+Although the shape of the QLF has been constrained by recent wide and deep surveys,
+it still remains challenging to develop a theoretical model that explains its redshift evolution with BH growth self-consistently.
 In this study, based on a semi-analytical model for the formation and growth of seed BHs
 in quasar progenitor halos,
-we construct the LF and MF of the early BH population that experiences multiple accretion bursts,
-in each of which the Eddington ratio is assigned following a Schechter function.
-Our best-fit model to reproduce the observed LF and MF at $z\simeq 6$
+we construct the QLF and BHMF of the early BH population that experiences multiple accretion bursts,
+in each of which constant Eddington ratio is assigned following a Schechter distribution function.
+Our best-fit model to reproduce the observed QLF and BHMF at $z\simeq 6$
 suggests that several episodes of modest super-Eddington accretion occur
@@
 owing to detection limits of quasar observations.
-The predicted redshift evolution of both LF and MF of earliest BHs suggests a rapid decay of their number and mass
+The predicted redshift evolution of both QLF and BHMF of earliest BHs suggests a rapid decay of their number and mass
 toward higher redshifts of $z>6$, compared to galaxy stellar mass.
@@
 \section{Introduction} \label{sec:intro}
-The growth of massive black holes (BHs) in active galactic nuclei (AGN) is elegantly related to their luminous accretion phases
+The growth of massive BHs in active galactic nuclei (AGN) is elegantly related to their luminous accretion phases
 across the cosmic time \citep{1982MNRAS.200..115S}.
@@
 Comparing the mass density of massive BHs in the local universe and the mass accreted onto BH inferred from
-the integration of the quasar luminosity function based on multi-wavelength observations,
+the integration of the QLF based on multi-wavelength observations,
 the cosmic BH accretion history and their radiative efficiency are nicely constrained 
@@
 \citep{2008AJ....135.1057J,2010AJ....139..906W,2016arXiv161205560C,2016ApJ...833..222J,2018PASJ...70S..35M,2019ApJ...883..183M,2019AJ....157..168D}
-along with the quasar luminosity function \citep[e.g.,][]{2015ApJ...798...28K,2018ApJ...869..150M}.
+along with the QLF \citep[e.g.,][]{2015ApJ...798...28K,2018ApJ...869..150M}.
 %and the virial BH mass estimates
@@
 
-\vspace{5mm}
+\vspace{2mm}
 \section{METHODOLOGY}\label{sec:method}
@@
 
-\vspace{5mm}
+\vspace{2mm}
 \section{Results}\label{sec:result}
@@
 \caption{
-Left panel: BHMF at $z=$ 6 calculated in the $\fseed=0.01$ case, 
-with different $\tlife=$ 10, 18 (the best-fit value), and 50 Myr, respectively, 
-and other parameters are fixed to the best-fit values. 
-The blue curve denotes the BHMF constrained by the \citetalias{2010AJ....140..546W} result. 
-With lower(higher) $\tlife$ than the best-fit value, the BHMF is under(over)-produced in the high mass end.
-Right panel: QLF at $z=$ 6 calculated with the same parameters as in the left panel.
-The overlaid blue dots are from the \citetalias{2018ApJ...869..150M} $z\sim$ 6 quasar observation. 
-With $\tlife$ values different from the best-fit value, the consequent QLF show 
-similar trends of deviation from observation as in the BHMF curves.
+The BH mass function (left) and quasar luminosity function (right) at $z=$ 6 in the case of $\fseed=0.01$, 
+with different values of $\tlife=$ 10, 18 (the best-fit value), and 50 Myr, respectively.
+Note that the other parameters are fixed to the best-fit values. 
+The $z=6$ BHMF (\citetalias{2010AJ....140..546W}) and QLF (\citetalias{2018ApJ...869..150M}) 
+are overlaid with the blue curve and data points.
+With shorter (longer) timescales of each accretion episode $\tlife$, the number of BHs at the high mass end and bright end is under(over)-produced.
+%Right panel: QLF at $z=$ 6 calculated with the same parameters as in the left panel.
+%The overlaid blue dots are from the \citetalias{2018ApJ...869..150M} $z\sim$ 6 quasar observation. 
+%With $\tlife$ values different from the best-fit value, the consequent QLF show 
+%similar trends of deviation from observation as in the BHMF curves.
+Multiple accretion bursts in each duration of $\tau \simeq 20$ Myr best produce the observations,
+which is nearly half of the $e$-folding time of the exponential BH mass growth.
 }
@@
 Galaxy UV luminosity functions are plotted with the data points (grey) and fitting functions with a Schechter (dotted curve) and double power-law (dash-dotted curve) shape.
-The galaxy luminosity function data at $z\sim$ 7 are taken from \citet[triangles]{2022ApJS..259...20H} \&
-\citet[circles]{2021AJ....162...47B}, and the fitting functions are produced by \citet{2022ApJS..259...20H}. 
-At $z\sim$ 8, the data points are from \citet[triangles]{2021AJ....162...47B},
-\citet[circles]{2022arXiv220712356D}, \citet[pluses]{2013MNRAS.432.2696M}, \citet[diamond]{2020MNRAS.493.2059B}, and \citet[pentagons]{2019ApJ...883...99S},
-as well as the fitting results by  \citet[double power law]{2020MNRAS.493.2059B} \& \citet[Schechter]{2013MNRAS.432.2696M}.
-At  $z\sim$ 9, those data are from \citet[triangles]{Harikane_2022c}, \citet[circles]{2022arXiv220712356D}, \citet[pluses]{2020MNRAS.493.2059B}, \citet[diamonds]{2019ApJ...883...99S}, and \citet[pentagons]{2018ApJ...867..150M},
-with the fitting functions from  \citet{Harikane_2022c}.
-At $z\sim$ $10-13$, \citet[triangles]{Harikane_2022c},\citet[circles]{2022arXiv220712356D},\citet[pluses]{Harikane_2022b}, \citet[diamonds]{2022arXiv220709434N}, \citet[pentagons]{2018ApJ...867..150M}, and \citet[stars]{2016ApJ...819..129O},
-and the fitting functions are produced by \citet{Harikane_2022c}.
+The galaxy luminosity function data at $z\sim$ 7 are taken from \citet{2022ApJS..259...20H} and \citet{2021AJ....162...47B}. 
+At $z\sim$ 8, the data points are from \citet{2021AJ....162...47B},
+\citet{2022arXiv220712356D}, \citet{2013MNRAS.432.2696M}, \citet{2020MNRAS.493.2059B}, and \citet{2019ApJ...883...99S}.
+At  $z\sim$ 9, those data are from \citet{Harikane_2022c}, \citet{2022arXiv220712356D}, \citet{2020MNRAS.493.2059B}, \citet{2019ApJ...883...99S}, 
+and \citet{2018ApJ...867..150M}.
+At $z\sim$ $10-13$, we take data from \citet{Harikane_2022c}, \citet{2022arXiv220712356D}, \citet{Harikane_2022b}, \citet{2022arXiv220709434N}, \citet{2018ApJ...867..150M}, 
+and \citet{2016ApJ...819..129O}.
+The fitting forms of the luminosity functions are given by \citet{2022ApJS..259...20H} at $z\simeq 7$, 
+\citet{2020MNRAS.493.2059B} and \citet{2013MNRAS.432.2696M} at $z\simeq 8$, and \citet{Harikane_2022c} at $9\lesssim z\lesssim 13$.
 }
@@
 
-In this sub-sample, we find seven BHs heavier than $M=10^9~\Msun$ (highlighted with solid curves), 
-among which five BHs show $\lambda<1$ in the snapshots at $z=6$.
-Tracing the BH growth curve back to $z=30$ with the Eddington ratio observed at $z=6$ (dotted curves),
-the extrapolated mass of those sub-Eddington BHs at $z=6$ is as massive as $\Mbh \gg 10^5~\Msun$ and is 
-substantially higher than the mass range for seed BHs.
-%ting BHs trace back to exceedingly massive seeds which are hard to be explained by current seeding scenarios. 
-%
-%If we extrapolate the BH mass with the $z \sim$ 6 witnessed Eddington ratio back to $z\sim$ 30, 
-%the sub-Eddington accreting BHs trace back to exceedingly massive seeds which are hard to be explained by current seeding scenarios. 
-It has been pointed out by \cite{2019ApJ...880...77O} that such simple extrapolation of the growth history for low-$\lambda$ quasars 
-does not work properly (see their Figure 10).
-%it is challenging that observations of fait quasars strong challenges to the growth histories of these sub-Eddington accreting BHs
-%
-In contrast, the extrapolated mass of super-Eddington BHs yields unrealistically small values at the seeding epochs,
-indicating a short duration of super-Eddington accretion modes.
-For comparison, we show the mass growth tracks assuming a constant Eddington ratio of $\lambda=1$, 
-where the extrapolated seed mass is $\Mbh \sim 10^2~\Msun$.
-%Both treatments of the constant $\lambda$ lead to BH seed masses extrapolation that deviate from the initial seeds we plant. 
-This argument clearly demonstrates that multiple accretion episodes with different values of $\lambda$ should be taken into account 
-to infer the seeding mass for the observed SMBHs as bright quasars at $z\gtrsim 6-7$, instead of assuming one single number 
-of the Eddington ratio.
-
-% \red{KI: still not sure what we discuss below... among the 7 BHs, is anyone consistent with Feige's BH?}
-In \citet{2021ApJ...907L...1W}, they discover the currently known most distant quasar at $z=7.642$, 
-tracing back with Eddington accretion, the central BH reaches the $10^{4-6}~\Msun$ seed mass range at $z=$ 30. 
-However in our best-fit model, we observe that to trace back BH mass and understand their seeding scenarios, 
-taking constant Eddington ratio derived from high-$z$ observation or assuming $\lambda=1$ are both unrealistic. 
-Therefore we raise a caveat that under these assumptions the seed mass achieved may be unreliable. 
-Instead we should take into account the episodical accretion nature of quasars, 
-including both bursts of accretion and quiescent phases.
-% This is supported strongly by our best model of a $\gtrsim 20$ Myr $\tlife$, which is intrinsically connected with 
-% the observational active quasar episode.
-
 %%%%%%%
@@
 \end{figure}
+
+In this sub-sample, we find seven BHs heavier than $M=10^9~\Msun$ (highlighted with solid curves), 
+among which five BHs show $\lambda<1$ in the snapshots at $z=6$.
+Tracing the BH growth curve back to $z=30$ with the Eddington ratio observed at $z=6$ (dotted curves),
+the extrapolated mass of those sub-Eddington BHs at $z=6$ is as massive as $\Mbh \gg 10^5~\Msun$ and is 
+substantially higher than the mass range for seed BHs.
+%ting BHs trace back to exceedingly massive seeds which are hard to be explained by current seeding scenarios. 
+%
+%If we extrapolate the BH mass with the $z \sim$ 6 witnessed Eddington ratio back to $z\sim$ 30, 
+%the sub-Eddington accreting BHs trace back to exceedingly massive seeds which are hard to be explained by current seeding scenarios. 
+It has been pointed out by \cite{2019ApJ...880...77O} that such simple extrapolation of the growth history for low-$\lambda$ quasars 
+does not work properly (see their Figure 10).
+%it is challenging that observations of fait quasars strong challenges to the growth histories of these sub-Eddington accreting BHs
+%
+In contrast, the extrapolated mass of super-Eddington BHs yields unrealistically small values at the seeding epochs,
+indicating a short duration of super-Eddington accretion modes.
+For comparison, we show the mass growth tracks assuming a constant Eddington ratio of $\lambda=1$, 
+where the extrapolated seed mass is $\Mbh \sim 10^2~\Msun$.
+%Both treatments of the constant $\lambda$ lead to BH seed masses extrapolation that deviate from the initial seeds we plant. 
+This argument clearly demonstrates that multiple accretion episodes with different values of $\lambda$ should be taken into account 
+to infer the seeding mass for the observed SMBHs as bright quasars at $z\gtrsim 6-7$, instead of assuming one single number 
+of the Eddington ratio.
+
+% \red{KI: still not sure what we discuss below... among the 7 BHs, is anyone consistent with Feige's BH?}
+In \citet{2021ApJ...907L...1W}, they discover the currently known most distant quasar at $z=7.642$, 
+tracing back with Eddington accretion, the central BH reaches the $10^{4-6}~\Msun$ seed mass range at $z=$ 30. 
+However in our best-fit model, we observe that to trace back BH mass and understand their seeding scenarios, 
+taking constant Eddington ratio derived from high-$z$ observation or assuming $\lambda=1$ are both unrealistic. 
+Therefore we raise a caveat that under these assumptions the seed mass achieved may be unreliable. 
+Instead we should take into account the episodical accretion nature of quasars, 
+including both bursts of accretion and quiescent phases.
+% This is supported strongly by our best model of a $\gtrsim 20$ Myr $\tlife$, which is intrinsically connected with 
+% the observational active quasar episode.
 
@@
 biased toward a population that undergoes active accretion episodes.
-Multiple accretion-burst treatment nicely produces the mass assembly history of individual high$-z$ luminous quasars,
+Multiple accretion-burst treatment nicely produces the mass assembly history of individual high-$z$ luminous quasars,
 unlike the case where one single value of the Eddington ratio is assigned.
@@
 
-% \begin{acknowledgments}
-% % We thank all the people that have made this paper what it is today.  
-% % This includes but not limited to Bob Hanisch, Chris Biemesderfer, Lee Brotzman,
-% % Pierre Landau, Arthur Ogawa, Maxim Markevitch, Alexey Vikhlinin and Amy
-% % Hendrickson. Also special thanks to David Hogg and Daniel Foreman-Mackey
-% % for the new "modern" style design. Considerable help was provided via bug
-% % reports and hacks from numerous people including Patriciddo Cubillos, Alex
-% % Drlica-Wagner, Sean Lake, Michele Bannister, Peter Williams, and Jonathan
-% % Gagne.
-% \end{acknowledgments}
-
+\acknowledgments
+We greatly thank Jin Wu, AAA, BBB, and CCC for constructive discussions. 
+We acknowledge support from the National Natural Science Foundation of China 
+(12073003, 12003003, 11721303, 11991052, 11950410493, and 1215041030), 
+and the China Manned Space Project Nos. CMS-CSST-2021-A04 and CMS-CSST-2021-A06. 
+The numerical simulations were performed with the Cray XC50 at the Center for Computational Astrophysics (CfCA) 
+of the National Astronomical Observatory of Japan and with the High-performance Computing Platform of Peking University.
 %% To help institutions obtain information on the effectiveness of their 
@@
 
-\clearpage
+% \clearpage
 

### 2022-08-18 ms.tex
version0818; 1st round revising according to MO&DT

@@
 We also find that the observed Eddington-ratio distribution function is skewed to a log-normal shape from the intrinsic Shechter function
-owing to detection limits of quasar observations.
-The predicted redshift evolution of both QLF and BHMF of earliest BHs suggests a rapid decay of their number and mass
+owing to detection limits of quasar surveys.
+The predicted redshift evolution of both QLF and BHMF of the earliest BHs suggests a rapid decay of their number and mass
 toward higher redshifts of $z>6$, compared to galaxy stellar mass.
@@
 %,1992MNRAS.259..725S}.
-Comparing the mass density of massive BHs in the local universe and the mass accreted onto BH inferred from
-the integration of the QLF based on multi-wavelength observations,
-the cosmic BH accretion history and their radiative efficiency are nicely constrained 
+The cosmic BH accretion history and their radiative efficiency are well constrained by 
+comparing the mass density of massive BHs in the local universe and the mass accreted onto BH inferred from
+the integration of the QLF based on multi-wavelength observations
 \citep[e.g.][]{1971ApJ...170..223C,1992MNRAS.259..725S,2002MNRAS.335..965Y,2004MNRAS.351..169M,2008MNRAS.388.1011M,2004MNRAS.354.1020S,
@@
 
-Extrapolation of this argument toward higher redshifts beyond $z\sim$ 6 is limited because of the current capability for
-high-$z$ quasar observations \citep{2013ApJ...768..105M,2016ApJ...829...33Y,2019ApJ...884...30W,2019BAAS...51c.121F}.
-% \red{KI: you could find better reference in this Decadal Survey?}.
-Nevertheless, currently the $z\sim 6$ quasar population is well constrained by multiband surveys
+Currently the $z\sim 6$ quasar population is well constrained by multiband surveys
 \citep{2008AJ....135.1057J,2010AJ....139..906W,2016arXiv161205560C,2016ApJ...833..222J,2018PASJ...70S..35M,2019ApJ...883..183M,2019AJ....157..168D}
-along with the QLF \citep[e.g.,][]{2015ApJ...798...28K,2018ApJ...869..150M}.
+along with the QLF \citep[e.g.,][]{2017ApJ...847L..15O,2015ApJ...798...28K,2018ApJ...869..150M}.
 %and the virial BH mass estimates
@@
 with the \ion{Mg}{2} single-epoch method and bring insights of the mass distribution
-\citep{2007AJ....134.1150J,2007ApJ...669...32K,2010AJ....140..546W,2018Natur.553..473B,2019ApJ...880...77O,2019ApJ...873...35S}. 
-Moreover, in the era of the James Webb Space Telescope (JWST) and forthcoming facilities,
+\citep[e.g.,][]{2007AJ....134.1150J,2007ApJ...669...32K,2010AJ....140..546W,2018Natur.553..473B,2019ApJ...880...77O,2019ApJ...873...35S}. 
+However, extrapolation of the Soltan argument toward higher redshifts beyond $z\sim$ 6 is limited because of the current difficulty of
+constructing high-$z$ QLFs \citep{2013ApJ...768..105M,2016ApJ...829...33Y,2019ApJ...884...30W,2019BAAS...51c.121F}.
+Nevertheless, in the era of the James Webb Space Telescope (JWST) and forthcoming facilities,
 e.g., the Roman Space Telescope (RST) and Euclid,
@@
 This is an effective way of examining the statistical properties of BH populations and making predictions 
-that can be directly compared with the QLF and BHMF
+that can be directly compared with the observed QLF and BHMF
 \citep[e.g.,][]{1998ApJ...503..505H,2010ApJ...718..231S,2018MNRAS.474.1995R,2018MNRAS.481.3278R,
@@
 The second approach is more phenomenological, using extrapolation of the low-$z$ QLF evolution with 
-fitting function forms \citep[e.g.,][]{2020MNRAS.495.3252S,2022arXiv220702233F}.
+fitting function forms \citep[e.g.,][]{2019MNRAS.488.1035K,2020MNRAS.495.3252S,2022arXiv220702233F}.
 This method also allows us to forecast the higher-$z$ QLF and bring insights for future surveys.
@@
 applying the semi-analytic seed formation model from \cite{2021ApJ...917...60L} to study the BH growth in common regions in the early universe.
-We assume that the early BH population experiences multiple accretion bursts, in each of which the Eddington ratio is assigned 
+We assume that the early BH population experiences multiple accretion bursts, in each of which constant Eddington ratio is assigned 
 following a Schechter distribution function. 
@@
 owing to detection limits of quasar observations.
-Those results will be unveiled by future deep and wide surveys with the James Webb Space Telescope, Roman Space Telescope, and Euclid.
+Those results will be tested by future deep and wide-field surveys with the Roman Space Telescope and Euclid.
 
@@
 $M_{\star, \mathrm{fb}}$ and $M_{\star, \mathrm{GR}}$ at the boundaries.
-At the end of the stellar lifetime, those massive primordial stars result in BHs without significant mass loss via stellar winds.
+At the end of the stellar lifetime, those massive primordial stars result in BHs without significant mass loss 
+($\sim 10\%$ to $50\%$) via stellar winds.
 \citep{2003ApJ...591..288H,2010ApJ...714.1217B,2015MNRAS.451.4086S}.
-Therefore, we consider the mass distribution of seed BHs as that of their stellar progenitors.
+Therefore, we consider the mass distribution of seed BHs represented by that of their stellar progenitors.
 
@@
 %Each panel includes a redshift span of 10, 
-In each panel, the cumulative number distribution of BHs are shown and 
-the contribution from newly-born BHs at the redshift interval are highlighted in magenta.
+In each panel, the cumulative number distribution of BHs formed prior than the redshift interval is shown with green bars,
+and the contribution from newly-born BHs during the interval are highlighted in magenta.
 %with the newly formed BHs denoted by the hatched regions, 
@@
 % where $t_{\rm S} = \eta_0  M c^2/L_{\mathrm{Edd}} \approx 45$ Myr,
-where $\lambda \equiv L/L_\mathrm{Edd}$ is the Eddington ratio,
+where $\lambda \equiv L/L_\mathrm{Edd}$ is the luminosity-based Eddington ratio,
 and $\Mdot_\mathrm{Edd} \equiv L_{\mathrm{Edd}}/\eta_0 c^2$ is the Eddington accretion rate with a radiative efficiency of $\eta_0=0.1$ \citep{1973A&A....24..337S},
@@
 \vspace{2mm}
-\subsection{Quasar luminosity function with obscure correction}\label{sec:LF}
+\subsection{Obscuration-corrected QLF}\label{sec:LF}
 
@@
 \citep{2006ApJS..166..470R}.
-Combining this conversion factor and the ERDF to govern the BH growth, the the quasar abundances with different luminosities 
+Combining this conversion factor and the ERDF to govern the BH growth, the quasar abundances with different luminosities 
 can be constructed straightforwardly.
@@
 However, we note that the shape and normalization of the {\it intrinsic} QLF is not necessary identical to the {\it observed} QLF
-because a larger fraction of fainter quasars are missed in current observations owing to quasar obscuration, 
+because quasar surveys with optical and near-infrared telescopes are not sensitive to the obscured quasar population at high redshifts,
+% a larger fraction of fainter quasars are missed in current observations owing to quasar obscuration, 
 %it is crucial to obtain we note that a vital ingredient to construct the observed QLF, 
@@
 %which decreases the fraction of the detectable quasars preferentially in the dimmer population 
-\citep{2003ApJ...598..886U,2014ApJ...786..104U,2008A&A...490..905H,2014MNRAS.437.3550M}. 
+\citep{2003ApJ...598..886U,2007A&A...463...79G,2008A&A...490..905H,2014ApJ...786..104U,2014MNRAS.437.3550M}. 
 %thus differs the normalization and shape of the observed QLF from the intrinsic one.
@@
 \citep[see][for a review]{2018ARA&A..56..625H}.
-However, the physical conditions for quasar obscuration have been poorly understood even with extensive studies both on theoretical and observational sides. 
+While at high redshifts, obscuration from much wider galactic scale may also be common \citep{2020MNRAS.495.2135N},
+and the denser gas may imply a growing obscured fraction with redshift \citep[]{2022arXiv220603508G}. 
+The physical conditions for high-$z$ quasar obscuration and their observational effects remains debated,
+and we refer to the observational constraints in this study.
+% even with extensive studies both on theoretical and observational sides
 % our current understanding of the quasar obscured fraction is inadequate, 
@@
 The exact function shape still remains under debate, but the overall dependence on the X-ray luminosity holds.
-Moreover, the obscured fraction is found to increase gradually toward higher redshifts and is saturated $z\sim 2$
+Moreover, the obscured fraction is found to increase gradually toward higher redshifts and is saturated at $z\gtrsim 2-3$
 \citep{2008A&A...490..905H,2014ApJ...786..104U,2014MNRAS.437.3550M,2018MNRAS.473.2378V}.
@@
 An alternative fitting form of $\fobsc$ based on their X-ray AGN sample with additional optical obscuration classification 
-is propose by \citet{2014MNRAS.437.3550M} as
+is proposed by \citet{2014MNRAS.437.3550M} as
 %
@@
 is sufficiently low and thus the mass-dependent growth model is excluded.
-% confined above the artificial $-3$ barrier, 
-%which is sufficiently low and can be neglected in the model.
 }
@@
 % \citep[e.g.,][Onoue et al. in preparation]{2010AJ....140..546W}.
-\citep[e.g.,][]{2010AJ....140..546W}.
-\red{Specially a complete sample of quasars from Onoue et al. in prep peak with $\log \lambda_0 \approx -0.24 \pm 0.31$ 
-before correcting the selection bias. (to be revised by MO)}.
+after luminosity bias correction \citep[e.g.,][]{2010AJ....140..546W}.
 % It is worth noting that, observationally the high-$z$ ERDF is fitted by a log-normal function. 
@@
 The observed BHMF data is taken from \citet{2010AJ....140..546W} (hereafter \citetalias{2010AJ....140..546W}), where 
-the virial BH mass measurements for $\sim 20$ bright quasars at $z\simeq $ 6 are used.
+the virial BH mass measurements for 17 bright quasars at $z\simeq $ 6 are used.
 %rom the virial BH mass among $\sim$ 20 quasars at $z\approx$ 6.
@@
 This suggests that accreting seed BHs vary their growth speeds (i.e., the Eddington ratio) 
-$\sim 30$ times on average, toward the cosmic time of $t_{\rm H} \gtrsim 900$ Myr at $z\simeq 6$.
+$\sim 30$ times on average, toward the cosmic time of $t_{\rm H} \sim 900$ Myr at $z\simeq 6$.
 The timescale of $\tlife$ also gives a lower bound of the quasar lifetimes of $t_{\rm Q}\sim 1-10$ Myr, 
@@
 
+\blue{
+The best-fit parameters for the two cases of $\fseed$ both reproduce the bulk properties of the BHMF and QLF at $z\sim 6$,
+despite in the $\fseed=0.01$ case the number of the whole BH population is ten times lower than that with $\fseed=0.1$.
 The two parameters characterizing the ERDF are given as
 $(\lambda_0,\alpha) = (0.89,0.12)$ and $(0.87,0.20)$ for $\fseed=0.1$ and $0.01$, respectively.
-With those values, the fraction of super-Eddington accreting BHs is estimated as $P(\lambda>1)=0.064$ and 0.075, respectively. 
-While the probability of rapid accretion in each cycle is similar, multiple accretion episodes enlarge the difference.
-Moreover, the best fit values of $\delta$ are $(0.001,0.055)$ for the two $\fseed$ cases,
-the higher $\delta$ value encourages the growth of small BHs with $M_\bullet <10^8~\Msun$,
-so that the ten-fold difference in $\fseed$ is nearly offset.
+With those values, the fraction of super-Eddington accreting BHs is estimated as $P(\lambda>1)=0.064$ and 0.075. 
+The probability of rapid accretion in each cycle in the $\fseed=0.01$ case is slightly higher than that with $\fseed=0.1$,
+while multiple accretion episodes enlarge the difference.
+Moreover, given the best fit values of $\delta=(0.001,0.055)$ for the two $\fseed$ cases,
+the higher $\delta$ value enhances the growth of small BHs with $M_\bullet <10^8~\Msun$ in the $\fseed=0.01$ case,
+so that massive BHs are produced with number densities similar to that in the $\fseed=0.1$ case,
+i.e., the ten-fold difference in $\fseed$ is nearly compensated.
 %Thus for different $\fseed$ values, a similar number density of BHs which rapidly grow to be SMBHs by $z\simeq 6$ is produced, 
@@
 in the model would differ from those in observations.
-On the other hand, the power-law index of $\alpha$ in the ERDF tends to increase as the seeding fraction decreases,
+On the other hand, the power-law index of $\alpha$ in the ERDF increases as the seeding fraction decreases,
 indicating that fraction of active BHs with $\lambda \gtrsim 1$ is elevated. 
-Thus, with lower seeding fractions, the high-$z$ quasar assembly spends a larger fraction of time in active phases 
-and reproduce the bulk properties of the BHMF and QLF.
-
-In Figs.~\ref{fig:fitmf} and \ref{fig:fitlf}, we show the BHMF and QLF at $z=$ 6 reproduced by the best-fit parameters
-as well as the $1\sigma$ spread, where the QLF model excludes a contribution from obscured quasars, 
-yielding the {\it observed} QLF for type-I AGN populations.
-The observed BHMF in \citetalias{2010AJ....140..546W} and QLF in \citetalias{2018ApJ...869..150M} 
+Thus, with lower seeding fractions, the high-$z$ quasar assembly ought to spend a larger fraction of time in active phases.
+}
+
+In Figs.~\ref{fig:fitmf} and \ref{fig:fitlf}, we show the total BHMF and unobscured (type-I) QLF at $z=$ 6 
+reproduced by the best-fit parameters as well as the $1\sigma$ spread.
+% where the QLF model excludes a contribution from obscured quasars, 
+% yielding the {\it observed} QLF for type-I AGN populations.
+The total BHMF indicated in \citetalias{2010AJ....140..546W} and QLF from \citetalias{2018ApJ...869..150M} 
 with statistical errors are also overlaid for comparison.
@@
 $10^8~\Msun \lesssim \Mbh \lesssim 3\times 10^9~\Msun$.
-In the high-mass regime, our fitting result nicely agrees to that in \citetalias{2010AJ....140..546W}.
+Our best-fit BHMF model well agrees with their observational constraints in this mass range.
 The QLF fitting results are also consistent with the observed one over $-29~{\rm mag} \lesssim \Muv \lesssim -25~{\rm mag}$,
@@
 In the left panel of Fig.~\ref{fig:tau}, we present the BHMF at $z=6$ for three different values of $\tlife=10$, $18$, and $50$ Myr,
-but keeping the other parameters as the best-fit values ($\lambda_0=0.87$ and $\alpha=0.20$) for the case with $\fseed=0.01$.
+but keeping the other parameters to the best-fit values ($\lambda_0=0.87$ and $\alpha=0.20$) for the case with $\fseed=0.01$.
 We note that $\tlife \approx$ 18 Myr is the best-fit value reproducing the BHMF consistent with that of \citetalias{2010AJ....140..546W}.
@@
 %and the slope in the high mass tail.
-For $\tlife=10$ Myr, the frequency of Eddington ratio assignment increases twice until $z=6$.
+For $\tlife=10$ Myr, the frequency of Eddington ratio assignment increases by a factor of two until $z=6$.
 %to $\sim$ 80 from $\sim$ 40 with the best-fit $\tlife$ value.
@@
 %high values of $\lambda\gtrsim \lambda_0$ is non-negligibly realized in the BHMF evolution.
-Therefore, the high mass end of the BHMF is further extended and those massive populations are substantially
+Therefore, the high mass end of the BHMF is further enhanced and those massive populations are substantially
 overproduced compared to the observed abundance.
@@
 The best-fit value of $\tlife (\simeq 18$ Myr) favors a moderate fraction of $t_{\rm S}$.
-This suggests the importance of regulated growth of BHs to reproduce the shape of the observed BHMF and QLF.
-%reproduces the quasar observation together with the other best-fit parameters in their reasonable ranges.
+This result demonstrates the importance of early BHs experiencing multiple accretion episodes to 
+reproduce the observed distributions of BH mass and luminosity of quasars at $z\sim$ 6.
 In \S\ref{sec:evol}, we apply this episodic accretion model to individual growth pathways of high-$z$ quasars
@@
 \caption{
-{\it Left panel}: BH mass functions at different redshifts of $6\leq z \leq 10$.
+{\it Left panel}: BH mass functions at $z=6-10$. 
 The solid lines denote modeled BHMF produced by the best-fit parameters 
@@
 Based on the constraint from $z\sim 6$ quasar observations, the best-fit model from the MCMC realizations enables
-us to probe the statistical BH evolution at higher redshifts.
-As a fiducial case, we take the best-fit parameters of BH growth for $\fseed=$ 0.01,
+us to probe the statistical aspect of BH evolution at higher redshifts.
+As a fiducial case, we take the best-fit parameters of BH growth for our $\fseed=$ 0.01 model,
 where $\tlife=18.76$ Myr, $\delta=0.055$, $\lambda_0=0.87$, and $\alpha=0.20$.
@@
 
-In the left panel of Fig.~\ref{fig:BHMF_rhoz}, we show the BHMFs at five different redshifts of $z=6-10$.
-For all the redshifts, the BHMFs can be characterized with a double power-law function, similar to lower-$z$ quasar populations.
+In the left panel of Fig.~\ref{fig:BHMF_rhoz}, we show our predictions of the BHMFs at five different redshifts of $z=6-10$.
+For all redshift bins, the BHMFs can be characterized with a double power-law function, similar to lower-$z$ quasar populations
+\citep[e.g.,][]{2013ApJ...764...45K,2015MNRAS.447.2085S}.
 From higher to lower redshifts, the number density of BHs heavier than $M_{\rm min} = 10^7~\Msun$ increases
@@
 where the fitted values of $\rho_{\bullet,0}$ and $k_{\rm M}$ are shown in Table.~\ref{tab:MFz}.
+
 On the other hand, the stellar mass density of the quasar progenitor halos is calculated as
@@
 We here express the mass growth of the DM halo with a functional form of $\propto 10^{k_{\rm h} z}$,
-which nicely reproduces the mass growth of DM halos
+which can describe the mass growth of DM halos
 \citep[e.g.,][]{2002ApJ...568...52W,2008MNRAS.383..615N,2008MNRAS.388.1792N,2010MNRAS.406.2267F}
@@
 Therefore, at $z\sim 6$ the bulge-to-BH mass ratio $\sim O(10^3)$ for the entire BH population (i.e., low-mass BHs and low-luminosity quasars) 
-is broadly consistent with those seen in the local universe, although SMBHs observed as high-$z$ quasars
-appear to be overmassive compared to the local relation \citep[e.g.,][]{2013ApJ...773...44W,2020A&A...637A..84P}.
+\blue{
+is roughly one order of magnitude lower than those seen in the local universe \citep[$\simeq$ 200 from][]{2013ARA&A..51..511K},
+although SMBHs observed as high-$z$ quasars appear to be $\sim 10$ times overmassive compared to the local relation 
+\citep[e.g.,][]{2013ApJ...773...44W,2020A&A...637A..84P,2021ApJ...911..141N}.
+Conclusion?
+}
 
@@
 \caption{
-{\it Left panel}: quasar luminosity functions at different redshifts of $6\leq z \leq 10$. 
+{\it Left panel}: quasar luminosity functions at $z=6-10$. 
 The solid lines denote modeled QLF produced by the best-fit parameters and the shaded regions present the $1\sigma$ spread. 
@@
 
-Next, we show the QLFs at different redshifts of $z=6-10$ taken from the BH growth model in the left panel of Fig.~\ref{fig:QLF_rhoz}.
+Next, we show our prediction of $z=6-10$ unobscured QLFs taken from the BH growth model in the left panel of Fig.~\ref{fig:QLF_rhoz}.
 Similar to the BHMF, for all the redshift range, the shape of the QLF is well approximated with a double power-law function.
-From higher to lower redshifts, the number density of luminous quasars increases and the bright-end of the distribution is extended.
+From higher to lower redshifts, the number density of luminous quasars increases and the bright-end of the distribution rises.
 % %The model QLFs we propose give interesting prediction and will be further constrained by higher redshift quasar observations.
@@
 %and fit the parameter $k_{\rm L}=-0.78$ by connecting the $z\sim 6$ result from \citet{2016ApJ...833..222J}.
-The rapid decline toward higher redshifts is nicely characterized by the treatment of episodic natures of BH accretion with a finite value of
+The rapid decline toward higher redshifts is characterized by the treatment of episodic natures of BH accretion with a finite value of
 $\tau ~(\simeq 20~{\rm Myr})$, in order to match the statistical properties of high-$z$ quasars.
@@
 and the whole population (i.e., type-I and type-II AGNs).
-We note that the AGN obscured fraction based on X-ray samples \citep{2014ApJ...786..104U} is applied to faint objects, 
+The AGN obscured fraction based on X-ray samples \citep{2014ApJ...786..104U} is applied to faint objects, 
 but the correction factor is highly uncertain at the faint end of $\Muv\gtrsim -20$ mag.
@@
 %with the number of quasars increases as BHs grow.
-We also overlay the expected depths and volumes of upcoming survey programs (blue lines) with Wide Euclid \citep{2011arXiv1110.3193L}
-and Wide RST \citep{2019arXiv190205569A}.
+We also overlay the expected depths and survey volumes of upcoming near-infrared surveys by
+Euclid \citep{2011arXiv1110.3193L} and RST \citep{2019arXiv190205569A}.
+Only their Wide survey layers are considered here.
 Table.~\ref{tab:N_detect} summarizes the expected number of detected quasars in each survey. 
@@
 Since extrapolated galaxy LFs with a Schechter shape decline quickly with the luminosity increasing,
-the galaxy LFs cross the QLFs at $\Muv$ with critical values of $\Muv \sim -23$, $-24$, and $-25$ mag at redshifts $z=7-8$, $9$, and $10-13$, respectively.
-On the other hand, if the galaxy LFs are extended with a power law, the corresponding crossing magnitude shifts to $\Muv\sim-26$, $-25$, and $\ll -30$ mag.
+the galaxy LFs intersect with the QLFs at $\Muv \sim -23$, $-24$, and $-25$ mag at redshifts $z=7-8$, $9$, and $10-13$, respectively.
+On the other hand, if the bright end of the galaxy LFs are extended with a power law, the corresponding crossing magnitude shifts to $\Muv\sim-26$, $-25$, and $\ll -30$ mag.
 %Therefore the galaxy contamination effect on quasar observations still remains model-dependent. 
 Therefore, future deep and wide surveys will lead to significant progress understanding the relative 
-contribution of both populations to astrophysical phenomena in the cosmic dawn.
+contribution of both populations to astrophysical phenomena e.g., the ionizing photon budget in the cosmic dawn.
 
@@
 Following the best fit parameters in the case of $\fseed = 0.01$,
-we assign an Eddington ratio $\lambda$ in every interval $\tlife=18.76$ Myr to grow the individual BHs until $z=6$. 
-The value of $\lambda$ follows the ERDF characterized by a Schechter distribution with $\lambda_0=0.87$ and $\alpha=0.20$.
+we assign an Eddington ratio $\lambda$ in every time interval $\tlife=18.76$ Myr to grow the individual BHs until $z=6$. 
+The value of $\lambda$ follows the ERDF characterized by a Schechter distribution with $\lambda_0=0.87$ and $\alpha=0.20$
+(see \S~\ref{sec:fitting_result}).
 With those parameters, we show the BH growth tracks that end up with $>10^8~\Msun$ by $z=6$ in Fig.~\ref{fig:track}. 
@@
 where $\mathcal{N}$ is the frequency of super-Eddington accretion bursts with $\lambda>1$ and $\Delta t_{\rm H}\simeq 450$ Myr.
-The average duty cycle is found to be $\langle f_{\rm duty}\rangle \simeq 0.15$.
+The average duty cycle is found to be $\langle f_{\rm duty}\rangle \simeq 0.15$ (i.e., $\Delta t_{\rm H} \times f_{\rm duty} \simeq 70$ Myr).
 %We take this sub-sample representing the observable massive BH population,
@@
 %and find $f_{\rm duty}\simeq 0.15$.
-On the other hand, the average duty cycle for the entire BH population is given by $P(\lambda>1)= 0.075$ 
+On the other hand, the average duty cycle for the entire BH population is given by $f_{\rm duty}= 0.075$ 
 (see \S~\ref{sec:fitting_result}), which is half of that for the sub-sample.
@@
 %
-In contrast, the extrapolated mass of super-Eddington BHs yields unrealistically small values at the seeding epochs,
-indicating a short duration of super-Eddington accretion modes.
+In contrast, the extrapolated growth curves of $z\sim$ 6 super-Eddington BHs are unrealistically steep,
+reaching $<100 ~\Msun$ within several hundred million years.
+This fact indicates short durations of the super-Eddington accretion mode.
 For comparison, we show the mass growth tracks assuming a constant Eddington ratio of $\lambda=1$, 
-where the extrapolated seed mass is $\Mbh \sim 10^2~\Msun$.
+where the extrapolated seed mass is $\Mbh \sim 10^2~\Msun$ at $z\sim 30$.
 %Both treatments of the constant $\lambda$ lead to BH seed masses extrapolation that deviate from the initial seeds we plant. 
@@
 %Discussion on quasar \textit{intrinsic} properties is naturally difficult, 
-because observed quasars are selected based on some criteria, e.g., the limiting magnitude.
-%a cut off of detection under some magnitude floor. 
-The unavoidable bias of quasar surveys could be corrected with the selection function calibrated
-by experiments on the detectability of mock data, but is not fully solved. 
+because observed quasars are limited by the depths of photometric surveys, not by the BH mass or Eddington ratio.
+This unavoidable bias of quasar surveys can be corrected by taking into account the survey completeness;
+however, it is still challenging to constrain the low-mass end of the BHMF and low $\lambda$ end of the ERDF
+that the surveys are not sensitive to.
 In this section, we examine the effect of flux-limited quasar surveys on the observed ERDF, 
@@
 The latter distribution is presented by various observational efforts in the $z\sim$ 6 brightest quasar samples 
-\citep[e.g.,][]{2010AJ....140..546W,2019ApJ...873...35S}.
+\citep[e.g.,][]{2010AJ....140..546W,2019ApJ...873...35S,2022arXiv220705113F}.
 However, our best-fit growth model reproducing both the BHMF and QLF at $z\sim$ 6 suggests the existence of
@@
 This will be proved by the ongoing observations with the Subaru HSC providing low-luminosity and less-massive BH samples
-(Onoue et al. in prep).
+(Onoue et al. in prep) and upcoming optical survey by the Vera C. Rubin Observatory.
 %Therefore, we emphasize that it is imperative to lower the detection limit in order to 
@@
 \centering
-\includegraphics[width=80mm]{distf2N5_06231122_l_hist.png}
+\includegraphics[width=70mm]{distf2N5_06231122_l_hist.png}
 \caption{
@@
 while the observed ERDF with a detection limit imposed results in a log-normal shape, 
-with a large low Eddington ratio quasars hidden from detection.
+with a large number of sub-Eddington quasars excluded.
 The log-normal shape still holds with the lower luminosity cut, 
@@
 \section{Summary}
-In this paper, we propose a theoretical model for the redshift-dependent QLF and BHMF at $z\gtrsim 6$,
-applying the initial mass function of seed BHs.
-We assume that the early BH population experiences multiple accretion bursts, in each of which the Eddington ratio
+In this paper, we propose a theoretical model for the redshift-dependent QLF and BHMF at $z\gtrsim 6$.
+We apply the seed BH mass function from PopIII remnants ranging in $10^{2-5}~\Msun$.
+We assume that the early BH population experiences multiple accretion bursts, in each of which constant Eddington ratio
 is assigned following a Schechter distribution function.
-We conduct the MCMC fitting procedure used to optimize the BH growth parameters
-so that the observed BHMF and QLF at $z\simeq 6$ are simultaneously reproduced.
-Our best-fit model to reproduce the QLF and BHMF at $z\simeq 6$ yields the ERDF characterized with the two parameters of
+Then we conduct the MCMC fitting to optimize the BH growth parameters
+so that the observed BHMF and QLF at $z\simeq 6$ are simultaneously reproduced. Our major findings are summarized as follows.
+\begin{itemize}
+\item
+Our model favors the BH Eddington ratio $\lambda$ following a Schechter distribution function to reproduce the QLF and BHMF at $z\simeq 6$.
+The distribution shape is motivated by low-$z$ AGN observations.
+The characteristic Eddington ratio $\lambda_0$ and the power law slope $\alpha$ at low Eddington ratio are best-fitted by
 $(\lambda_0, \alpha)=(0.89,0.12)$ and $(0.87,0.20)$ for the BH seeding fraction of $\fseed = 0.01$ and $0.1$, respectively.
-The models suggests that several episodes of modest super-Eddington accretion occur and each accretion phase lasts $\simeq 20-30$ Myr.
+The parameter $\tau$ characterizing the duration of each accretion burst is featured by our model,
+with typical values $\tau \simeq 20-30$ Myr.
 For longer (and shorter) burst durations, the number of BHs at the high mass end is over(-under) produced.
@@
 consistent with the observed distribution functions.
+\item
 Using the best-fit model parameters, we construct the redshift-dependent QLF and BHMF at $6\leq z \leq 10$.
@@
 but tends to be slightly steeper at higher redshifts.
-% \red{Add comparison to GLFs and expected detection numbers }\blue{
+\item
 Compared to the galaxy luminosity functions at redshifts from $z=7$ to $z\gtrsim 10$, the QLFs we predict are burried in the faint end at $\Muv \gtrsim -23$ mag,
-which makes it more challenging to select such faint quasars.
+which makes it challenging to select such faint quasars.
 The number of quasars dominates over that of galaxies in the bright end of the UV luminosity function.
@@
 We further explore individual BH evolutionary tracks starting from the BH seeds, applying the BH growth model
-with the best-fit parameters reproducing their statistical properties.
-For massive BHs that reach $\gtrsim 10^8~\Msun$ by $z\simeq 6$, the average duty cycle of accretion is as high as $\simeq 15~\%$.
+with the best-fit parameters to examine their statistical properties.
+\item
+For massive BHs that reach $\gtrsim 10^8~\Msun$ by $z\simeq 6$, the average duty cycle of super-Eddington accretion is as high as $\simeq 15~\%$.
 Since the duty cycle is nearly twice that of the entire population, the BH samples observed in $z\simeq 6$ quasars are
 biased toward a population that undergoes active accretion episodes.
-Multiple accretion-burst treatment nicely produces the mass assembly history of individual high-$z$ luminous quasars,
+Multiple accretion-burst treatment well produces the mass assembly history of individual high-$z$ luminous quasars,
 unlike the case where one single value of the Eddington ratio is assigned.
 We also find that the observed Eddington-ratio distribution function is skewed to a log-normal shape from the intrinsic Shechter function
-owing to detection limits of quasar observations.
-Those results will be unveiled by future deep and wide surveys with the JWST, RST, and Euclid.
+owing to detection limits of quasar surveys.
+Those results will be tested by future deep and wide surveys with the JWST, RST, and Euclid.
+\end{itemize}
 
 \acknowledgments
-We greatly thank Jin Wu, AAA, BBB, and CCC for constructive discussions. 
+We greatly thank Jin Wu, Zhiwei Pan, BBB, and CCC for constructive discussions. 
 We acknowledge support from the National Natural Science Foundation of China 
-(12073003, 12003003, 11721303, 11991052, 11950410493, and 1215041030), 
+(12073003, 12003003, 11721303, 11991052, 11950410493, 1215041030, and 12150410307), 
 and the China Manned Space Project Nos. CMS-CSST-2021-A04 and CMS-CSST-2021-A06. 
@@
 
-% \clearpage
+\clearpage
 

### 2022-08-21 ms.tex
version 0819, before giving k; next based on points he lists

@@
 \blue{
-is roughly one order of magnitude lower than those seen in the local universe \citep[$\simeq$ 200 from][]{2013ARA&A..51..511K},
+is broadly consistent with those seen in the local universe \citep[$\simeq 200-1000$ in e.g.,][]{2012ApJ...751L..25V,2013ARA&A..51..511K},
 although SMBHs observed as high-$z$ quasars appear to be $\sim 10$ times overmassive compared to the local relation 
 \citep[e.g.,][]{2013ApJ...773...44W,2020A&A...637A..84P,2021ApJ...911..141N}.
-Conclusion?
+Our result suggests that overall the build-up of stellar mass in galaxies is earlier than BHs,
+which will be tested by high-$z$ galaxy and quasar surveys.
 }
@@
 \centering
-\includegraphics[width=70mm]{distf2N5_06231122_l_hist.png}
+% \includegraphics[width=70mm]{distf2N5_06231122_l_hist.png}
+\includegraphics[width=80mm]{l_hist.png}
 \caption{

### 2022-08-21 ms.tex
Sec.5.1 updated

@@
 % motivated by the properties of typical BH seeds (with median formation redshift and median mass).
-We generate a sample of 10$^7$ BHs, whose formation time and mass distribution at birth follow the model described in \S~\ref{sec:seed}. 
+We generate a sample of 10$^6$ BHs, whose formation time and mass distribution at birth follow the model described in \S~\ref{sec:seed}. 
 Following the best fit parameters in the case of $\fseed = 0.01$,
-we assign an Eddington ratio $\lambda$ in every time interval $\tlife=18.76$ Myr to grow the individual BHs until $z=6$. 
-The value of $\lambda$ follows the ERDF characterized by a Schechter distribution with $\lambda_0=0.87$ and $\alpha=0.20$
-(see \S~\ref{sec:fitting_result}).
-With those parameters, we show the BH growth tracks that end up with $>10^8~\Msun$ by $z=6$ in Fig.~\ref{fig:track}. 
-%\red{KI: what is the frequency $N$ of BH accretion bursts with $\lambda>\lambda_0$ between $z=6$ and $10$? The duty cycle for the sub-sample
-%is $f_{\rm duty}\simeq N\tlife/\Delta t_{\rm H}$.}
-For those massive BHs, we estimate the duty cycle between $z=10$ and $6$ defined as $f_{\rm duty} \equiv \mathcal{N}\tlife/\Delta t_{\rm H}$, 
+for every time interval $\tlife=18.76$ Myr,
+we assign a constant Eddington ratio $\lambda$ generated randomly from the Schechter distribution function 
+characterized by $\lambda_0=0.87$ and $\alpha=0.20$ (see \S~\ref{sec:fitting_result}).
+With these parameters, we grow the individual BHs until $z=6$ and 
+study the statistical behavior in the growth of massive BHs.
+
+We estimate the duty cycle between $z=10$ and $6$ defined as $f_{\rm duty} \equiv \mathcal{N}\tlife/\Delta t_{\rm H}$, 
 where $\mathcal{N}$ is the frequency of super-Eddington accretion bursts with $\lambda>1$ and $\Delta t_{\rm H}\simeq 450$ Myr.
-The average duty cycle is found to be $\langle f_{\rm duty}\rangle \simeq 0.15$ (i.e., $\Delta t_{\rm H} \times f_{\rm duty} \simeq 70$ Myr).
-%We take this sub-sample representing the observable massive BH population,
-%which is easier to be probed by flux-limited quasar observations.
-%During the growth histories of these BHs, it is interesting to examine the duty cycle of the active phase, 
-%e.g., characterized as $f_{\rm duty}\simeq N\tlife/\Delta t_{\rm H}$,
-%where $N$ is the frequency of a BH growing with super-Eddington accretion bursts,
-%in a time duration $\Delta t_{\rm H}$.
-%We estimate the duty cycle between the cosmic age of $z=$ 10 to $z=$ 6,
-%and find $f_{\rm duty}\simeq 0.15$.
+For BH populations grown to $M_\bullet>10^7$, $10^8$ and $10^9~\Msun$ at $z=$ 6,
+the average duty cycle is found to be $\langle f_{\rm duty}\rangle \simeq 0.12$, 0.15, and 0.19
+(i.e., $\Delta t_{\rm H} \times f_{\rm duty} \simeq 55$, 69, and 85 Myr), respectively.
 On the other hand, the average duty cycle for the entire BH population is given by $f_{\rm duty}= 0.075$ 
-(see \S~\ref{sec:fitting_result}), which is half of that for the sub-sample.
-Therefore, this clearly shows that the massive BH samples observed in $z\simeq 6$ quasars are biased toward a population that
-undergoes active accretion episodes at higher redshifts.
-
+(see \S~\ref{sec:fitting_result}), which much lower than these massive sub-samples.
+Therefore, we suggest that the massive BHs observed in $z\simeq 6$ quasars are biased in a way that
+the more massive populations undergo longer active accretion episodes along their growth.
+
+In Fig.~\ref{fig:track}, we show the BH growth tracks that end up with $M_\bullet>10^8~\Msun$ by $z=6$.
+%
 %%%%%%%
@@
 \end{figure}
-
-In this sub-sample, we find seven BHs heavier than $M=10^9~\Msun$ (highlighted with solid curves), 
-among which five BHs show $\lambda<1$ in the snapshots at $z=6$.
-Tracing the BH growth curve back to $z=30$ with the Eddington ratio observed at $z=6$ (dotted curves),
-the extrapolated mass of those sub-Eddington BHs at $z=6$ is as massive as $\Mbh \gg 10^5~\Msun$ and is 
+%
+%
+In this sub-sample, we find five BHs heavier than $M=10^9~\Msun$ (highlighted with solid curves),
+among which all of them show $\lambda<1$ at the  $z=6$ snapshot.
+% among which five BHs show $\lambda<1$ in the snapshots at $z=6$.
+Tracing the BH growth curve back to $z=30$ with the Eddington ratio observed at $z=6$ (dashed curves),
+the extrapolated mass of those sub-Eddington BHs at $z=6$ is as massive as $\Mbh \gg 10^6~\Msun$ and is 
 substantially higher than the mass range for seed BHs.
@@
 does not work properly (see their Figure 10).
-%it is challenging that observations of fait quasars strong challenges to the growth histories of these sub-Eddington accreting BHs
-%
-In contrast, the extrapolated growth curves of $z\sim$ 6 super-Eddington BHs are unrealistically steep,
-reaching $<100 ~\Msun$ within several hundred million years.
-This fact indicates short durations of the super-Eddington accretion mode.
-For comparison, we show the mass growth tracks assuming a constant Eddington ratio of $\lambda=1$, 
-where the extrapolated seed mass is $\Mbh \sim 10^2~\Msun$ at $z\sim 30$.
+% In contrast, the extrapolated growth curves of $z\sim$ 6 super-Eddington BHs are unrealistically steep,
+% reaching $<100 ~\Msun$ within several hundred million years.
+% This fact indicates short durations of the super-Eddington accretion mode.
+For comparison, we show the mass growth tracks assuming constant Eddington accretion (i.e., $\lambda=1$),
+where the extrapolated seed mass is $\Mbh \lesssim 10^2~\Msun$ at $z\sim 30$.
 %Both treatments of the constant $\lambda$ lead to BH seed masses extrapolation that deviate from the initial seeds we plant. 
-This argument clearly demonstrates that multiple accretion episodes with different values of $\lambda$ should be taken into account 
-to infer the seeding mass for the observed SMBHs as bright quasars at $z\gtrsim 6-7$, instead of assuming one single number 
-of the Eddington ratio.
+Therefore, one may postulate that short durations of super-Eddington accretion lead to the exsitence of the massive BHs.
+Based on the BH seeds and growth model we develop,
+we reiterate that multiple accretion episodes with different values of $\lambda$ should be taken into account 
+to infer the seeding mass for the observed SMBHs as bright quasars at $z\gtrsim 6-7$,
+instead of assuming one single number of the Eddington ratio.
 
@@
 including both bursts of accretion and quiescent phases.
-% This is supported strongly by our best model of a $\gtrsim 20$ Myr $\tlife$, which is intrinsically connected with 
-% the observational active quasar episode.
+Among the five supermassive BH growth tracks,
+we find one matching this currently known most distant quasar, 
+with $M_\bullet \simeq 1.8\times 10^9~\Msun$ and $\lambda \simeq 0.5$ at $z=7.6$ (shown with red curve).
+Starting from $z\sim 29$ with $M_{\rm seed} \sim 10^5~\Msun$,
+this overmassive growth history is realized by the combination of rare halo environments initilizing a heavy seed, 
+and several super-Eddington accretion bursts.
 

### 2022-08-24 ms.tex
version0824; Sec5.1,5.2(fig only); Sec3.1 updated

@@
 This will be unveiled by future deep and wide surveys with the James Webb Space Telescope, Roman Space Telescope, and Euclid.
-% the , Roman Space Telescope (RST), and Euclid.
 \end{abstract}
@@
 Currently the $z\sim 6$ quasar population is well constrained by multiband surveys
-\citep{2008AJ....135.1057J,2010AJ....139..906W,2016arXiv161205560C,2016ApJ...833..222J,2018PASJ...70S..35M,2019ApJ...883..183M,2019AJ....157..168D}
-along with the QLF \citep[e.g.,][]{2017ApJ...847L..15O,2015ApJ...798...28K,2018ApJ...869..150M}.
+\citep{2008AJ....135.1057J,2010AJ....139..906W,2016arXiv161205560C,2018PASJ...70S..35M,2019ApJ...883..183M,2019AJ....157..168D}
+along with the QLF \citep[e.g.,][]{2015ApJ...798...28K,2016ApJ...833..222J,2017ApJ...847L..15O,2018ApJ...869..150M}.
 %and the virial BH mass estimates
@@
 owing to detection limits of quasar observations.
-Those results will be tested by future deep and wide-field surveys with the Roman Space Telescope and Euclid.
+Those results will be tested by future deep and wide-field surveys with JWST, RST, and Euclid,
+by conducting spectroscopic measurements of individual BH masses and constructing high-$z$ QLFs.
 
@@
   \label{eq:M1450}
-  \Muv= -21.0-2.5 \log  \left(\frac{\Lbol}{10^{45}~\mathrm{erg~s}^{-1}} \right),
+  \Muv= -21.0-2.5 \log  \left(\frac{\Lbol}{10^{45}~\mathrm{erg~s}^{-1}} \right) \rm{mag},
 \end{equation}
@@
 \caption{
-The quasar luminosity function at $z=6$ with the best-fit parameters (purple curve) and the $1\sigma$ spread for the cases with $\fseed=0.1$ (left) and $0.01$ (right). 
-%as described in \ref{fig:fitmf}. 
+The unobscured quasar luminosity function at $z=6$ with the best-fit parameters (black solid line) and the $1\sigma$ spread for the cases with $\fseed=0.1$ (left) and $0.01$ (right).
 The observed data (blue symbols) with error bars are taken from \citetalias{2018ApJ...869..150M} and is used for the model parameter fitting.
+The upper bound of faint quasar number density is derived from the cumulative QLF presented in \citet{2022NatAs...6..850J}.
+The X-ray QLF data in the faint end inferred from the $z\sim 5-6.1$ quasar sample in \citet{2019ApJ...884...19G} are denoted by orange symbols,
+note that we conduct an extrapolation with quasar number densities scaling with $10^{-0.72\Delta z}$ at $z$ in $5-6$ \citep{2016ApJ...833..222J}.
+For comparison, we show the intrinsic QLF predicted by our model in dashed lines.
 }
@@
 i.e., the ten-fold difference in $\fseed$ is nearly compensated.
-%Thus for different $\fseed$ values, a similar number density of BHs which rapidly grow to be SMBHs by $z\simeq 6$ is produced, 
-%consistent with a general picture for the early assembly of SMBHs 
-%\citep[e.g.,][]{2006NewAR..50..665F,2008AJ....135.1057J,2010AJ....139..906W}.
 The characteristic Eddington ratio needs to be close to unity, otherwise the highest luminosity and BH mass
@@
 indicating that fraction of active BHs with $\lambda \gtrsim 1$ is elevated. 
-Thus, with lower seeding fractions, the high-$z$ quasar assembly ought to spend a larger fraction of time in active phases.
+Thus, with lower seeding fractions, the high-$z$ quasar assembly ought to experience more active growth phases to reproduce the observations.
 }
 
-In Figs.~\ref{fig:fitmf} and \ref{fig:fitlf}, we show the total BHMF and unobscured (type-I) QLF at $z=$ 6 
-reproduced by the best-fit parameters as well as the $1\sigma$ spread.
-% where the QLF model excludes a contribution from obscured quasars, 
-% yielding the {\it observed} QLF for type-I AGN populations.
-The total BHMF indicated in \citetalias{2010AJ....140..546W} and QLF from \citetalias{2018ApJ...869..150M} 
-with statistical errors are also overlaid for comparison.
-We note that \citetalias{2010AJ....140..546W} constructed the BHMF using quasar samples with 
+Next, we demonstrate that overall, the parameters are inferred to be reasonable fits consistent with the observational data of both of the BHMF and QLF.
+In Fig.~\ref{fig:fitmf}, we show the total BHMF at $z=$ 6 reproduced by the best-fit parameters as well as the $1\sigma$ spread.
+We also present the total BHMF indicated by \citetalias{2010AJ....140..546W} with statistical errors for comparison.
+The BHMF data put more constraints in the fitting procedure, and help the fitting converge.
+However, a complete BHMF is necessary for better constraints, especially the low-mass end, 
+which inherit more of the seeding information during a short growth time.
+For current comparison,
+we note that \citetalias{2010AJ....140..546W} constructed the BHMF using quasar samples with 
 $10^8~\Msun \lesssim \Mbh \lesssim 3\times 10^9~\Msun$.
-Our best-fit BHMF model well agrees with their observational constraints in this mass range.
-The QLF fitting results are also consistent with the observed one over $-29~{\rm mag} \lesssim \Muv \lesssim -25~{\rm mag}$,
-but seems to overproduce the abundance of fainter quasars at $\Muv>-24~{\rm mag}$.
-% due to the lack of fine tuning by the model parameters in the low mass range, 
+Our best-fit BHMF model well agrees with their constraints in this mass range.
+
+The unobscured (type-I) QLF fitting results at $z=$ 6 are presented in Fig.~\ref{fig:fitlf},
+along with the observed data from \citetalias{2018ApJ...869..150M}, which we adopt to the fitting.
+The best-fit QLF results are consistent with observation over $-29~{\rm mag} \lesssim \Muv \lesssim -25~{\rm mag}$.
+However, they overproduce the abundance of fainter quasars at $\Muv\gtrsim -24~{\rm mag}$,
+reflecting both the less constraints from observational data in the faint end,
+and the difficulty of reproducing such a small population of low-luminosity quasars based on our seeding and growth model.
 The difference at the fainter end tends to be alleviated with the seeding fraction lowered ($\fseed = 0.01$),
@@
 Those BH population naturally produces a flatter slope of the QLF (and BHMF) at the faint (low-mass) end.
-Overall, the parameters are inferred to be reasonable fits consistent with the observational data.
+In \citet{2022NatAs...6..850J}, an upper limit of the faint end QLF is provided, % by non-detection of faint quasars
+by analyzing this population in the Hubble Space Telescope (HST) imaging fields.
+Our best-fit unobscured QLF results lie within their constraints.
+
+On the other hand, studies on X-ray selected faint quasars report number densities much higher than that
+extrapolated from rest-UV observations \citep{2015A&A...578A..83G,2019ApJ...884...19G}.
+In addition to the systematic difference in the quasar identification methods,
+the X-ray observation should suffer less dust obscuration (see \S~\ref{sec:LF}),
+thus detect more quasars in the faint end.
+We also show the intrinsic QLF predicted by our best-fit parameters,
+which is without imposing obscuration thus representing the upper bound of detectable quasar numbers.
+Our intrinsic QLF is broadly consistent with the faint-end QLF from X-ray observation,
+despite slightly lower than their data points at $\Muv\gtrsim -21$ mag.
+% outshining effect
+From another point of view, studies explain the decrepancy of the UV and X-ray QLF in the faint end
+by pointing out that only AGNs outshining their host galaxies can be identified by the point source criteria
+in the rest-UV selection \citep{2020MNRAS.495.2135N,2022arXiv220712282K}.
+Especially in the faint end at $\Muv\gtrsim -24$ mag, the galaxy population can potentially contribute to this contamination significantly 
+\citep{2022ApJS..259...20H}.
+We do not take into account of this effect in the QLF correction,
+but we notice this important caveat and provide the galaxy number density information 
+in the higher-$z$ QLF predictions (see \S~\ref{sec:qlfglf}).
+
+% In Figs.~\ref{fig:fitmf} and \ref{fig:fitlf}, we show the total BHMF and unobscured (type-I) QLF at $z=$ 6 
+% reproduced by the best-fit parameters as well as the $1\sigma$ spread.
+% % where the QLF model excludes a contribution from obscured quasars, 
+% % yielding the {\it observed} QLF for type-I AGN populations.
+% The total BHMF indicated in \citetalias{2010AJ....140..546W} and QLF from \citetalias{2018ApJ...869..150M} 
+% with statistical errors are also overlaid for comparison.
+% We note that \citetalias{2010AJ....140..546W} constructed the BHMF using quasar samples with 
+% $10^8~\Msun \lesssim \Mbh \lesssim 3\times 10^9~\Msun$.
+% Our best-fit BHMF model well agrees with their observational constraints in this mass range.
+% The QLF fitting results are also consistent with the observed one over $-29~{\rm mag} \lesssim \Muv \lesssim -25~{\rm mag}$,
+% but seems to overproduce the abundance of fainter quasars at $\Muv>-24~{\rm mag}$.
+% % due to the lack of fine tuning by the model parameters in the low mass range, 
+% The difference at the fainter end tends to be alleviated with the seeding fraction lowered ($\fseed = 0.01$),
+% because the progenitors of $z=6$ BHs with $10^{7-8}~\Msun$ (or similarly, 
+% $-22~{\rm mag} \lesssim \Muv \lesssim -24~{\rm mag}$) were less massive seed BHs with $\sim 10^4~\Msun$,
+% which is closer to the peak of the seed mass distribution (see Fig.~\ref{fig:seedmf}).
+% Those BH population naturally produces a flatter slope of the QLF (and BHMF) at the faint (low-mass) end.
+% Overall, the parameters are inferred to be reasonable fits consistent with the observational data.
 
@@
 \subsection{Quasar luminosity function}
-
+\label{sec:qlfglf}
 Next, we show our prediction of $z=6-10$ unobscured QLFs taken from the BH growth model in the left panel of Fig.~\ref{fig:QLF_rhoz}.
@@
 
-In Fig.~\ref{fig:track}, we show the BH growth tracks that end up with $M_\bullet>10^8~\Msun$ by $z=6$.
+In Fig.~\ref{fig:Mevol}, we show the BH growth tracks that end up with $M_\bullet>10^8~\Msun$ by $z=6$.
 %
@@
 }
-\label{fig:track}
+\label{fig:Mevol}
 \end{figure}
@@
 we find one matching this currently known most distant quasar, 
-with $M_\bullet \simeq 1.8\times 10^9~\Msun$ and $\lambda \simeq 0.5$ at $z=7.6$ (shown with red curve).
-Starting from $z\sim 29$ with $M_{\rm seed} \sim 10^5~\Msun$,
+with $M_\bullet \simeq 1.7\times 10^9~\Msun$ and $\lambda \simeq 0.6$ at $z=7.6$ (shown with red curve).
+Starting from $z\sim 33$ with $M_{\rm seed} \sim 2\times 10^5~\Msun$,
 this overmassive growth history is realized by the combination of rare halo environments initilizing a heavy seed, 
@@
 Based on the quasar sample from the best-fit model described in \S~\ref{sec:evol}, 
-we select quasars with a bolometric luminosity cut.
-%of $\Lbol \geq 10^{46}~\mathrm{erg~s^{-1}}$. 
-In Fig.~\ref{fig:lhist}, we present the intrinsic ERDFs for the whole BH sample (blue) and the selected sample with
-a luminosity cut of $\Lbol \geq 10^{46}~\mathrm{erg~s^{-1}}$ (green) and $\Lbol \geq 10^{45}~\mathrm{erg~s^{-1}}$ (orange).  
+we select quasars with bolometric luminosity limits $L_{45}=10^{45}~\mathrm{erg~s^{-1}}$ and $L_{46}=10^{46}~\mathrm{erg~s^{-1}}$.
+In Fig.~\ref{fig:lhist}, we present the intrinsic ERDFs for the whole BH sample (blue)
+and the selected sample with a luminosity cut of $\Lbol \geq L_{45}$ (orange),
+and $\Lbol \geq L_{46}$ (green).
+For visible comparison, we elevate the observed histograms by a factor of 5 and 30
+for the luminosity limits with $L_{45}$ and $L_{46}$, respectively.
 The Eddington ratio for the whole sample follows a Schechter shape with a majority of inactive quasars, 
@@
 The intrinsic Eddington ratio distribution function for the whole BH sample (blue) and the selected sample with
-a luminosity cut of $\Lbol \geq 10^{46}~\mathrm{erg~s^{-1}}$ (green) and $\Lbol \geq 10^{45}~\mathrm{erg~s^{-1}}$ (orange).  
+a luminosity cut of $\Lbol \geq 10^{45}~\mathrm{erg~s^{-1}}$ (orange) and $\Lbol \geq 10^{46}~\mathrm{erg~s^{-1}}$ (green).  
 %Intrinsic ERDF (blue) and the observed ones after imposing selection effects by $\Lbol>L_\mathrm{lim}=10^{45}$ (orange) and 10$^{46}$ erg~s$^{-1}$ (green).
-The observed histograms are elevated by arbitrary normalizations for comparison of the distribution shapes.
+The observed histograms are elevated by a factor of 5 and 30, for comparison of the distribution shapes.
 The intrinsic ERDF follows the best-fitted Schechter function (dashed curve), 

### 2022-08-25 ms.tex
version0825; before Euclid from me.

@@
 by pointing out that only AGNs outshining their host galaxies can be identified by the point source criteria
-in the rest-UV selection \citep{2020MNRAS.495.2135N,2022arXiv220712282K}.
+in the rest-UV selection \citep{2020MNRAS.495.2135N,2021MNRAS.502.2757O,2022arXiv220712282K}.
 Especially in the faint end at $\Muv\gtrsim -24$ mag, the galaxy population can potentially contribute to this contamination significantly 
@@
 The evolutionary trend can be fitted as $\propto 10^{k_{\rm L}z}$, where $k_{\rm L}\approx -0.97$.
-A rapid decay of the quasar number density toward higher redshifts is found by previous studies \citep[e.g.,][]{2001AJ....122.2833F,2016ApJ...833..222J},
+Observationally, a rapid decay of the quasar number density toward higher redshifts is found by previous studies
+\citep[e.g.,][]{2001AJ....122.2833F,2013ApJ...768..105M,2016ApJ...833..222J,2019ApJ...884...30W},
 which show $k_{\rm L}= -0.47$ and $-0.72$ from the analysis of quasar samples at $z\simeq 3-5$ and $z\simeq 5-6$, respectively.
-Recently, a steeper decline of luminous quasar number density toward higher redshifts is proposed by \citet{2019ApJ...884...30W},
-suggesting $k_{\rm L}=-0.78$ at $6\lesssim z \lesssim 7$.
-%a steeper decline ifts is suggested in recent studies of $z\gtrsim 6$ quasars,
-%e.g. \citet{2019ApJ...884...30W} measure the spatial density of $z\sim 6.7$ quasars,
-%and fit the parameter $k_{\rm L}=-0.78$ by connecting the $z\sim 6$ result from \citet{2016ApJ...833..222J}.
+% Recently, a steeper decline of luminous quasar number density toward higher redshifts is proposed by \citet{2019ApJ...884...30W},
+% suggesting $k_{\rm L}=-0.78$ at $6\lesssim z \lesssim 7$.
 The rapid decline toward higher redshifts is characterized by the treatment of episodic natures of BH accretion with a finite value of
@@
 Only their Wide survey layers are considered here.
-Table.~\ref{tab:N_detect} summarizes the expected number of detected quasars in each survey. 
+Table.~\ref{tab:N_detect} summarizes the coverage and limiting magnitudes in each survey,
+and list the expected number of quasar detection.
 Euclid will identify quasars up to $z\sim 8$ and discover $O(100-1000)$ quasars at $z\simeq 7-8$.

### 2022-08-30 ms.tex
version0830; Sec.4.1&Fig.7 done w/o k; next Sec.4.2&Fig.8

@@
 we construct the QLF and BHMF of the early BH population that experiences multiple accretion bursts,
-in each of which constant Eddington ratio is assigned following a Schechter distribution function.
+in each of which a constant Eddington ratio is assigned following a Schechter distribution function.
 Our best-fit model to reproduce the observed QLF and BHMF at $z\simeq 6$
@@
 which is nearly twice that of the entire population.
-We also find that the observed Eddington-ratio distribution function is skewed to a log-normal shape from the intrinsic Shechter function
+We also find that the observed Eddington-ratio distribution function is skewed to a log-normal shape from the intrinsic Shechter-like function
 owing to detection limits of quasar surveys.
@@
 Deep spectroscopic observations of high-$z$ quasars enable us to measure the virial BH mass 
-with the \ion{Mg}{2} single-epoch method and bring insights of the mass distribution
+with the Mg~{\sc ii} single-epoch method and bring insights of the mass distribution
 \citep[e.g.,][]{2007AJ....134.1150J,2007ApJ...669...32K,2010AJ....140..546W,2018Natur.553..473B,2019ApJ...880...77O,2019ApJ...873...35S}. 
-However, extrapolation of the Soltan argument toward higher redshifts beyond $z\sim$ 6 is limited because of the current difficulty of
+However, extrapolation of the Soltan-Paczy{\'n}ski argument toward higher redshifts beyond $z\sim$ 6 is limited because of the current difficulty of
 constructing high-$z$ QLFs \citep{2013ApJ...768..105M,2016ApJ...829...33Y,2019ApJ...884...30W,2019BAAS...51c.121F}.
@@
 \citep{2019BAAS...51c..45R, 2019arXiv190205569A, 2011arXiv1110.3193L}. 
-Deep surveys of high-$z$ quasars and their host galaxies will shed light on the early BH evolution, 
-also help answering the intriguing questions e.g., 
-the existence of supermassive BHs in the early universe within one billion year 
-\citep{2012Sci...337..544V,2013ASSL..396..293H,2020ARA&A..58...27I}, 
-and the establishment of BH-galaxy coevolution 
+Deep surveys of high-$z$ quasars and their host galaxies will shed light on the early BH evolution and help 
+answer questions regarding the existence of SMBHs in the early universe \citep{2012Sci...337..544V,2013ASSL..396..293H,2020ARA&A..58...27I}, 
+and early development of BH-galaxy coevolution 
 \citep[e.g.,][]{2013ApJ...773...44W,2017ApJ...851L...8V,2021ApJ...914...36I,2022ApJ...927..237I,2022MNRAS.511.3751H}.
@@
 The first is semi-analytical modeling, in which BH seed formation, gas accretion, and BH mergers associated 
-with the hierarchical growth of the parent dark-matter halos are taken into account in a simplified way. 
+with the hierarchical growth of the parent dark matter (DM) halos are taken into account in a simplified way. 
 This is an effective way of examining the statistical properties of BH populations and making predictions 
@@
 2021MNRAS.508.2706Y,2021ApJ...910L..11K,2022MNRAS.511..616T}. 
-However, due to the limitation of capturing detailed properties of the relevant physics, 
+However, due to the limitation of capturing the detailed properties of the relevant physics, 
 a large number of model parameters need to be calibrated based on the observed distribution functions 
-of lower-$z$ quasar population \citep[e.g.,][]{2007ApJ...669...45H}
+of lower-$z$ quasar populations \citep[e.g.,][]{2007ApJ...669...45H}
 and empirical correlations between the SMBH mass and their host galaxy properties seen
@@
 Therefore, it is required to construct a theoretical model that is characterized by a minimum number of parameters
-but capable of dealing with essential physical processes.
+but capable of dealing with the essential physical processes.
 
@@
 % applying the initial mass function (IMF) of seed BHs obtained from \cite{2021ApJ...917...60L}.
-applying the semi-analytic seed formation model from \cite{2021ApJ...917...60L} to study the BH growth in common regions in the early universe.
-We assume that the early BH population experiences multiple accretion bursts, in each of which constant Eddington ratio is assigned 
+applying the semi-analytic seed formation model from \cite{2021ApJ...917...60L} to study the BH growth in the early universe.
+We assume that the early BH population experiences multiple accretion bursts, in each of which a constant Eddington ratio is assigned 
 following a Schechter distribution function. 
 We conduct the Markov Chain Monte Carlo (MCMC) fitting procedure to optimize the BH growth parameters 
-so that the observed BHMF and QLF at $z\simeq 6$ are simultaneously reproduced. 
+so that the observed QLF and BHMF at $z\simeq 6$ are simultaneously reproduced. 
 Our best-fit model suggests several episodes of modest super-Eddington accretion and requires
 individual burst durations of $\simeq 20-30$ Myr to avoid over(under)-production of BHs at the high-mass end.
-Furthermore, we construct the redshift-dependent QLF and BHMF that imply a rapid decay of 
+Furthermore, we construct the redshift-dependent QLF and BHMF, implying a rapid decay of 
 their number and mass toward higher redshifts of $z>6$.
-We also find that the observed Eddington-ratio distribution function is skewed to a log-normal shape from the intrinsic Shechter function
+We also find that the observed Eddington-ratio distribution function is skewed to a log-normal shape from the intrinsic Schechter-like function
 owing to detection limits of quasar observations.
@@
 
+\red{(to be revised)
 This paper is organized as follows. Firstly, in \S \ref{sec:method} we describe the semi-analytical BH seeding procedure, 
-the parameterized BH growth and how we reproduce the modeled BHMF and QLF dataset at $z\sim$ 6 using these ingredients. 
+the parameterized BH growth and how we reproduce the modeled QLF and BHMF dataset at $z\sim$ 6 using these ingredients. 
 In \S \ref{sec:result} we present the fitting of model parameters constrained by quasar observations. 
 We then summarize our findings in \S \ref{sec:discussion} and discuss the potential applications on exploring the high-$z$ universe.
+}
 Throughout this work, we apply the cosmological parameters from \cite{2016A&A...594A..13P},
@@
 that end up in high-$z$ quasar host galaxies with halo mass of $\Mh \gtrsim 10^{11}~\Msun$.
-The mass range of DM halos for $z\sim 6$ quasars is motivated by the halo mass measurement, 
-assuming that the rotation velocity based on [\ion{C}{2}] 158 $\micron$ line width is equal to the circular velocity of the halo.
+The mass range of those DM halos for $z\sim 6$ quasars is motivated by the halo mass measurement, 
+where the rotation velocity of gas based on the [C~{\sc ii}] 158 $\micron$ line width is assumed to be the circular velocity of the halo
 %is is motivated by the estimated masses of quasar hosts which are typically up to $\sim 10^{11-13}~\Msun$, 
@@
 %, and study the BH seeds formed therein.
-For each tree, we adopt a minimum DM halo mass of $M_{\rm h,min}=10^5~\Msun$, which is lower enough to capture 
+For each tree, we adopt a minimum DM halo mass of $M_{\rm h,min}=10^5~\Msun$, which is small enough to capture 
 the earliest star formation episodes via H$_2$ line cooling at the high-$z$ universe \citep{1996ApJ...464..523H,1997ApJ...474....1T}.
@@
 
-In addition, we consider baryonic streaming motion relative to the DM produced in the epoch of cosmic recombination at $z_{\rm rec} \simeq 1100$.
+In addition, we consider baryonic streaming motion relative to DM produced in the epoch of cosmic recombination at $z_{\rm rec} \simeq 1100$.
 %originated from its decoupling with radiation.
@@
 The episodic nature of disk accretion decreases the time-averaged accretion rate onto the protostar as $\Mdot_{\star}=\eta \Mdot$, 
-where we adopt $\eta=0.3$ as the conversion efficiency \citep[][Toyouchi 2022]{2016MNRAS.459.1137S}. 
+where we adopt $\eta=0.3$ as the conversion efficiency \citep{2016MNRAS.459.1137S, 2022arXiv220614459T}. 
 %\blue{
@@
 %Thus, we estimate the accretion rate to estimate the protostellar mass and that of the subsequent seed BH formed. 
-The stellar radius evolution of an accreting protostar and the radiative feedback strength depend sensitively on whether
+The size evolution of an accreting protostar and the radiative feedback strength depend sensitively on whether
 the accretion rate becomes higher than a critical value of $\dot{M}_{\mathrm{crit}}=0.04~\Msunyr$ 
@@
 in the range of $\dot{M}_\star\gtrsim 0.1~\Msunyr$ \citep{2016PhRvD..94b1501S,2017ApJ...842L...6W,2019PASA...36...27W}.
-On the other hand, for $\dot{M}_\ast \leq \Mdot_\mathrm{crit}$, protostars can contract by loosing its thermal energy via radiative diffusion
+On the other hand, for $\dot{M}_\ast \leq \Mdot_\mathrm{crit}$, the protostar begins to contract by loosing its thermal energy via radiative diffusion
 and increases its surface temperature to $T_\mathrm{eff} \sim 10^5$ K.
@@
 At the end of the stellar lifetime, those massive primordial stars result in BHs without significant mass loss 
-($\sim 10\%$ to $50\%$) via stellar winds.
-\citep{2003ApJ...591..288H,2010ApJ...714.1217B,2015MNRAS.451.4086S}.
-Therefore, we consider the mass distribution of seed BHs represented by that of their stellar progenitors.
+% ($\sim 10\%$ to $50\%$) 
+% \red{How do you get this percentage of mass loss?}
+via stellar winds \citep{2003ApJ...591..288H,2010ApJ...714.1217B,2015MNRAS.451.4086S}.
+Therefore, we consider that the stellar mass with interest is equal to that of its remnant BH.
 
@@
 
-Let us consider that a seed BH with a mass of $M_{\bullet,i}$ formed in the $i$-th halo merger tree at the cosmic age $t_i$ ($1\leq i \leq N_{\rm tot}=10^4$),
+Let us consider that a seed BH with a mass of $M_{\bullet,i}$ formed in the $i$-th halo merger tree at the cosmic age 
+$t_i$ ($1\leq i \leq N_{\rm tot}=10^4$),
 %In the $i$-th DM growth history where a seed BH is formed with mass $M_\text{itr}$ at the cosmic age $t_\text{itr}$, 
-and each of them contributes to the probability distribution function of seed mass at time $t$ as
+and each of them contributes to the probability distribution function (PDF) of seed mass at a time $t$ as
 % 
@@
 %
-Based on the cumulative seed mass probability distribution function $\D P^{\rm seed}_i/ \D \Mbh$ 
-which is the integral of $p^{\rm seed}_i (\Mbh,t)$ over time, 
+Based on the cumulative seed-mass distribution of $\D P^{\rm seed}_i/ \D \Mbh$
+(i.e., the integral of $p^{\rm seed}_i$ over time),
 we construct the mass function from all $N_{\rm tot}$ seeds formed in one parent halo
@@
 % We have constraints on simulations and observations of lower redshift counterparts.
-With BH seeds planted, we grow the BHs with a semi-analytical accretion rate model and study the evolution of the BH mass distribution until $z=6$. 
+With BH seeds planted, we grow the BHs with a semi-analytical accretion model and study the evolution of the BH mass distribution until $z=6$. 
 % \blue{(references + discussion)}
@@
 %according to the thin accretion disk model \citep{1973A&A....24..337S}, 
-which is consistent with the value obtained from the Soltan's argument \citep[e.g.,][]{2002MNRAS.335..965Y,2010ApJ...725..388C}.
+which is consistent with the value obtained from the Soltan-Paczy{\'n}ski argument \citep[e.g.,][]{2002MNRAS.335..965Y,2010ApJ...725..388C}.
 % The high mass BH should be strangulated by as it grows, 
@@
 \citep{2008MNRAS.390..561C,2012ApJ...749..187L,2014ApJ...786..104U}, 
-we introduce a similar functional form that characterizes its mass dependence 
+we introduce a similar functional form that characterizes the mass dependence 
 %
@@
 
-To characterize the ERDF for a BH population at any time snapshot together with the episodic 
-accretion pattern of individual BHs, 
-we introduce a time duration of $\tlife$, during which a single value of $\lambda$ that follows 
-the ERDF of Eq.~(\ref{eq:Pl}) is assigned to an accreting BH.
+To characterize the ERDF for a BH population at any time snapshot together with episodic 
+accretion patterns of individual BHs, 
+we introduce a time duration of $\tlife$, during which a single value of $\lambda$ is assigned to an accreting BH
+following the ERDF of Eq.~(\ref{eq:Pl}).
 In this way, we give a different growth speed of a BH in every period with a duration of $\tlife$ until $z=6$ 
@@
 Instead of treating those ingredients implemented in previous semi-analytical models, we extract 
-an averaged but fundamental timescale that governs mutual correlation between the BHMF and QLF,
+an averaged but fundamental timescale that governs mutual correlation between the QLF and BHMF,
 based on direct comparison to those distribution functions for observed high-$z$ quasar population.
@@
 Since the value has been poorly constrained both by theoretical and observational studies, we treat it as a free parameter.
-We take three different values of $\fseed = 1$, $0.1$, and $0.01$ and explore the dependence on the best-fit BHMF and QLF.
+% wli avoid fseed=1
+We take three different values of $\fseed = 1$, $0.1$, and $0.01$ and explore the dependence on the best-fit QLF and BHMF.
 Note that the seed mass function shown in Fig.~\ref{fig:seedmf} is given with $\fseed = 1$.
@@
 where $\lambda_\ast$ is the Eddington ratio required for a BH with $M_{\bullet,0}$ to grow up to $\Mbh$ within $\Delta t$
-and is calculated analytically from Eq.~(\ref{eq:mi2m}) by
+and is calculated analytically from Eq.~(\ref{eq:mdot}) by
 %%%%%%%
@@
 %
-with the derivative of ($\D \ln \lambda_\ast / \D  \Mbh )|_{\Delta t, M_{\bullet,0}}$ also determined.
+and the derivative of ($\D \ln \lambda_\ast / \D  \Mbh )|_{\Delta t, M_{\bullet,0}}$ is also determined.
 For existing BHs formed prior to this checkpoint, we calculate the evolution of the mass distribution by setting $\Delta t = \tlife$.
@@
 This procedure is illustrated schematically in Fig.~\ref{fig:scheme}. 
+\red{KI: Fig.~2 also needs to show the configuration of the checkpoints, adding more info.}
 % After the seed formation terminates (i.e., after the total number of BHs is fixed), we perform this integration in every timestep 
@@
 Combining this conversion factor and the ERDF to govern the BH growth, the quasar abundances with different luminosities 
-can be constructed straightforwardly.
+can be constructed.
 %Under this conversion, an ERDF combined with the $z\sim$ 6 BH population is able to reproduce 
@@
 
-% 讨论一下 obs fraction 
+% obs fraction 
 A widely-accepted mechanism causing quasar obscuration is extinction by dusty tori and dense gas clouds 
@@
 \citep[see][for a review]{2018ARA&A..56..625H}.
-While at high redshifts, obscuration from much wider galactic scale may also be common \citep{2020MNRAS.495.2135N},
-and the denser gas may imply a growing obscured fraction with redshift \citep[]{2022arXiv220603508G}. 
-The physical conditions for high-$z$ quasar obscuration and their observational effects remains debated,
-and we refer to the observational constraints in this study.
+In addition, dense gas clouds at galactic larger scales may have a significant contribution to quasar obscuration at 
+higher redshifts \citep{2020MNRAS.495.2135N}, and the obscured fraction is expected to increase with redshift \citep[]{2022arXiv220603508G}. 
+In this study, however, we adopt the prescription of the obscured fraction constrained from quasar observations at $z\lesssim 5$ 
+since the physical origin and conditions for high-z quasar obscuration is poorly understood yet.
+%While at high redshifts, obscuration from much wider galactic scale may also be common \citep{2020MNRAS.495.2135N},
+%and the denser gas may imply a growing obscured fraction with redshift \citep[]{2022arXiv220603508G}. 
+%The physical conditions for high-$z$ quasar obscuration and their observational effects remains debated,
+%and we refer to the observational constraints in this study.
 % even with extensive studies both on theoretical and observational sides
@@
 Observationally, the obscured fraction of AGNs with hydrogen column density of $N_{\rm H}>10^{22}~{\rm cm}^{-2}$
-can be estimated from spectral analyses of AGNs in the X-ray band
+can be estimated from spectral analyses in the X-ray band
 %The high-$z$ quasars observed in the rest-frame UV-optical bands are profoundly obstructed by dust obscuration, 
@@
 In this work, we adopt the obscuration fraction $\fobsc$ given by \citet{2014ApJ...786..104U}, 
-converting the hard X-ray luminosity to the 1450 $\mathrm{\AA}$ magnitude with bolometric correction factors of
+converting the hard X-ray luminosity to the absolute magnitude at 1450 $\mathrm{\AA}$ with bolometric correction factors of
 \begin{equation*}
@@
 \begin{equation*}
-  \fobsc = \text{min}\lbrace  0.84 , 0.73-0.24\times[ (\log \Lbol/L_\odot) -43.75] \rbrace,
+  \fobsc = \text{min}\lbrace  0.84 , 0.73-0.24\times[ \log (\Lbol/L_\odot) -43.75] \rbrace,
 \end{equation*}
@@
 \begin{equation*}
-  \fobsc = 0.56 + \frac{1}{\pi}~ \text{arctan} \left[ \frac{43.89 - (\log \Lbol/L_\odot)}{0.46}\right].
+  \fobsc = 0.56 + \frac{1}{\pi}~ \text{arctan} \left[ \frac{43.89 - \log (\Lbol/L_\odot)}{0.46}\right].
 \end{equation*}
@@
 the choice of $\fobsc$ in the Appendix.
+\red{KI: add appendix}
 
@@
 
-In this section, we describe the Markov Chain Monte Carlo (MCMC) fitting procedure used to optimize 
+In this section, we describe the MCMC fitting procedure used to optimize 
 the BH growth parameters so that the observed BHMF and QLF are consistently reproduced. 
@@
 In what follows, we describe the results for $\fseed = 0.1$ and $0.01$ (see Appendix for the case with $\fseed =1.0$).
+\red{KI: add appendix}
 
@@
 \begin{align}
-  \chi^2 = \sum_{i,j}
-  \frac{\left(\log{\Phi^{\rm mod}_{i,j}} - \log{\Phi^{\rm obs}_{i,j}}\right)^2}{(\log{\Phi^{\rm err}_{i,j}})^2},
+  \chi^2 = \sum_{x,i}
+  \frac{\left(\log{\Phi^{\rm mod}_{x,i}} - \log{\Phi^{\rm obs}_{x,i}}\right)^2}{(\log{\Phi^{\rm err}_{x,i}})^2},
 \end{align}
-where $\Phi^{\rm mod}_{i,j}$ and $\Phi^{\rm obs}_{i,j}$ represent the modeled and observational value 
-on the \textit{i-}th BHMF ($j=\Mbh$) and QLF ($j=\Muv$) bin, and $\Phi^{\rm err}_{i,j}$ is the corresponding error.
+where $\Phi^{\rm mod}_{x,i}$ and $\Phi^{\rm obs}_{x,i}$ represent the modeled and observational value 
+on the \textit{i-}th bin of the BHMF ($x=\Mbh$) and QLF ($x=\Muv$), and $\Phi^{\rm err}_{x,i}$ is the corresponding error.
+% on the \textit{i-}th bin of the BHMF ($j=1$) and QLF ($j=2$), and $\Phi^{\rm err}_{i,j}$ is the corresponding error.
 Adopting 10 mass bins and 12 magnitude bins, we treat the errors from comparison both in the BHMF and QLF
@@
 \section{Results}\label{sec:result}
+
+\vspace{2mm}
+\subsection{Fitting Results}\label{sec:fitting_result}
+
+\red{KI: we need to explain why the peak of the 1D posterior distribution does not correspond to the best-fit case.
+I think the peak value is not necessarily the same as the best-fit value. 
+Also, we need to list the best-fit parameters somewhere in the text.}
+
+In Fig.~\ref{fig:contour}, we visualize the MCMC fitting results for each parameter in two-dimensional 
+posterior distribution for the case of $\fseed= 0.1$ (left) and $0.01$ (right), respectively.
+The three vertical lines on each one-dimensional posterior distribution present the peak and the values
+with $1\sigma$ scatter.
+The result for the $\fseed=1$ case is discussed in the Appendix.
+\red{KI: add appendix}
+
+For both cases, the best-fit solution consistently shows a small value of $\delta < 0.01$. \red{KI: but, $\delta=0.055$ is used later...}
+%, which is sufficiently small and should be marginalized out. 
+This suggests that a nearly exponential BH growth manner is favored in our model assumption. 
+% In other words, on average the BH growth can be described as exponential, 
+% under the premise that the gas supply is episodical. 
+The typical duration of quasar activity is required to be $\tlife \simeq 20-30$ Myr for both the cases.
+%which is $\sim 64\%$ of the $e$-folding time for an exponential growth.
+This suggests that accreting seed BHs vary their growth speeds and their Eddington ratios 
+$\simeq 30-40$ times on average toward the cosmic time at $z\simeq 6$.
+The timescale of $\tlife$ also gives a lower bound of the quasar lifetimes of $t_{\rm Q}\sim 1-10$ Myr, 
+which are estimated by the measurement of the physical extents of hydrogen Ly$\alpha$ proximity zones 
+observed in the rest-frame UV spectra \citep[e.g.,][]{2018ApJ...867...30E,2019ApJ...884L..19D}.
+% \red{KI: we need to figure out if their $t_Q$ is the quasar age or lifetime, or something else?}
+More detailed comparison is discussed in \S\ref{sec:evol}.
+\red{KI: where is the discussion?}
 
@@
 
-\vspace{2mm}
-\subsection{Fitting Results}\label{sec:fitting_result}
-In Fig.~\ref{fig:contour}, we visualize the MCMC fitting results for each parameter in two-dimensional 
-posterior distribution for the case $\fseed= 0.1$ (left) and $0.01$ (right), respectively.
-The three vertical lines on each one-dimensional posterior distribution present the peak and the values
-with $1\sigma$ scatter.
-The result for the $\fseed=1$ case is discussed in the Appendix.
-
-For the two cases, the best-fit solutions consistently show a small values of $\delta < 0.01$.
-%, which is sufficiently small and should be marginalized out. 
-This suggests that in our model assumption, a nearly exponential BH growth pattern is favored. 
-% In other words, on average the BH growth can be described as exponential, 
-% under the premise that the gas supply is episodical. 
-The typical duration of quasar activity is required to be $\tlife \simeq 29$ Myr for both the cases, 
-which is $\sim 64\%$ of the $e$-folding time for an exponential growth.
-This suggests that accreting seed BHs vary their growth speeds (i.e., the Eddington ratio) 
-$\sim 30$ times on average, toward the cosmic time of $t_{\rm H} \sim 900$ Myr at $z\simeq 6$.
-The timescale of $\tlife$ also gives a lower bound of the quasar lifetimes of $t_{\rm Q}\sim 1-10$ Myr, 
-which are estimated by the measurement of the physical extents of hydrogen Ly$\alpha$ proximity zones 
-observed in the rest-frame UV spectra \citep[e.g.,][]{2018ApJ...867...30E,2019ApJ...884L..19D}.
-% \red{KI: we need to figure out if their $t_Q$ is the quasar age or lifetime, or something else?}
-More detailed comparison is discussed in \S\ref{sec:evol}.
+%The best-fit parameters for the two cases of $\fseed$ reproduce the bulk properties of the BHMF and QLF at $z\sim 6$,
+%despite in the $\fseed=0.01$ case the number of the whole BH population is ten times lower than that with $\fseed=0.1$.
+The two parameters characterizing the ERDF are given as
+$(\lambda_0,\alpha) = (0.89,0.12)$ and $(0.87,0.20)$ for $\fseed=0.1$ and $0.01$, respectively.
+%We note that the total number of BHs differs by a factor of ten between the two cases.
+With those values, the fraction of super-Eddington accreting BHs is estimated as $P(\lambda>1)=0.064$ and 0.075.
+While the probability of rapid accretion in each cycle differs slightly between the two cases,
+multiple accretion episodes enlarge the difference and enable more efficient BH growth for the lower seeding fraction.
+Moreover, the lower seeding-fraction case requires a higher value of $\delta (\simeq 0.055)$, accelerating 
+the growth of less massive BHs with $M_\bullet <10^8~\Msun$.
+Therefore, a larger fraction of seed BHs are delivered into the SMBH regime,
+% given the best fit values of $\delta=(0.001,0.055)$ for the two $\fseed$ cases,
+% the higher $\delta$ value enhances the growth of small BHs with $M_\bullet <10^8~\Msun$ in the $\fseed=0.01$ case,
+% so that massive BHs are produced with number densities similar to that in the $\fseed=0.1$ case,
+and the ten-fold difference in $\fseed$ is nearly compensated.
+The characteristic Eddington ratio needs to be close to unity, otherwise the highest luminosity and BH mass
+in the model would differ from those in observations.
+On the other hand, the power-law index of $\alpha$ in the ERDF increases as the seeding fraction decreases,
+indicating that fraction of active BHs with $\lambda \gtrsim 1$ is elevated. 
+Thus, with lower seeding fractions, the high-$z$ quasar assembly ought to experience more active growth phases to reproduce the observations.
+
+% Next, we demonstrate that the parameters are inferred to be reasonable fits consistent with the observational data of both of the BHMF and QLF.
+In Fig.~\ref{fig:fitmf}, we show the total BHMF at $z=$ 6 reproduced by the best-fit parameters for 
+$\fseed = 0.1$ (left) and $0.01$ (right) as well as the $1\sigma$ spread.
+For comparison, we present the BHMF inferred by \citetalias{2010AJ....140..546W} along with the statistical errors.
+Note that \citetalias{2010AJ....140..546W} constructed the BHMF using quasar samples with 
+$10^8~\Msun \lesssim \Mbh \lesssim 3\times 10^9~\Msun$.
+Overall, our best-fit BHMF model agrees with their constraints in this mass range.
+The power-law index of the BHMF ($\alpha_{M_\bullet} \equiv \D \ln \Phi_{M_\bullet}/\D \ln M_\bullet$) is as steep as $\alpha_{M_\bullet}\lesssim -1$
+at $M_\bullet \gtrsim 10^7~(3\times 10^7)~\Msun$ for $\fseed = 0.1 ~(0.01)$.
+The discrepancy between the model and observational data becomes larger at the high- and low-mass end,
+reflecting poor constraints on the BHMF from the current observations.
+%Therefore, both wider-field and deep surveys are required to determine the shape of the BHMF
+%The BHMF data put more constraints in the fitting procedure, and help the fitting converge.
+%However, a complete BHMF is necessary for better constraints, especially the low-mass end, 
+%which inherit more of the seeding information during a short growth time.
+The differences at the two extreme ends become smaller with the lower seeding fraction of $\fseed = 0.01$.
+This is because the progenitors of $z=6$ BHs with $10^{7-8}~\Msun$ were the most abundant BH population 
+in the seeding epochs (i.e., a flatter slope of the BHMF; see Fig.~\ref{fig:seedmf}) and mass growth for BHs heavier than 
+$\sim 10^8~\Msun$ is suppressed owing to the high value of $\delta~(\simeq 0.055)$.
+
+Fig.~\ref{fig:fitlf} presents the QLFs at $z=6$ reproduced by the best-fit parameters as well as the $1\sigma$ spreads.
+The solid and dashed curve is the {\it unobscured} QLF %(excluding a contribution from obscured quasars)
+and the {\it intrinsic} QLF (including both obscured and unobscured quasars), respectively.
+For comparison, we overlay the observational data used for the fitting and the QLF parametrized with 
+a double power-law shape obtained by \citetalias{2018ApJ...869..150M} (dotted curve).
+The best-fit unobscured QLF is consistent with the observed one at $-29~{\rm mag} \lesssim \Muv \lesssim -25~{\rm mag}$,
+but overproduces fainter quasars at $\Muv\gtrsim -24~{\rm mag}$.
+%, reflecting both the less constraints from observational data in the faint end,
+%and the difficulty of reproducing such a small population of low-luminosity quasars based on our seeding and growth model.
+As seen in the BHMF, the difference between the model and observational data at the faint end becomes smaller with
+the lower seeding fraction.
+Since the progenitors of those faint quasars were seed BHs located around the peak of the mass distribution,
+those BHs naturally produces a flatter slope of the QLF at the faint end.
+In addition, we show upper bounds of the faint quasar abundance at $\Muv\gtrsim -22~{\rm mag}$ \citep[green symbols;][]{2022NatAs...6..850J}
+%, an upper limit of the faint end QLF is provided, % by non-detection of faint quasars
+based on a search for quasars in the Hubble Space Telescope (HST) imaging fields.
+Our unobscured QLF lies within the constraints.
+
+Quasar observations in X-rays also provide 
+useful constraints on the intrinsic population because of the different quasar selection criteria and less obscuration effects in X-rays.
+Based on the X-ray selected faint quasars, \cite{2015A&A...578A..83G,2019ApJ...884...19G} reported higher number densities of faint quasars
+compared to those extrapolated from the rest-UV observations (e.g., the dotted curve by \citetalias{2018ApJ...869..150M}) 
+down to the faint end of $\Muv\gtrsim -22~{\rm mag}$ (orange symbols).
+%In addition to the systematic difference in the quasar identification methods,
+%the X-ray observation should suffer less dust obscuration (see \S~\ref{sec:LF}),
+%thus detect more quasars in the faint end.
+%We also show the intrinsic QLF predicted by our best-fit parameters,
+%which is without imposing obscuration thus representing the upper bound of detectable quasar numbers.
+Our best-fitted intrinsic QLF (dashed curve) is broadly consistent with the faint-end QLF from the X-ray observations within the errors,
+though the model predicts slightly lower numbers at $\Muv\gtrsim -21$ mag.
+% outshining effect
+From another point of view, the discrepancy between the UV and X-ray QLFs at the faint end would be explained by the fact that 
+only bright quasars outshining their host galaxies can be identified as point-like sources in the rest-UV quasar selection 
+(\citetalias{2018ApJ...869..150M}; \citealt{2020MNRAS.495.2135N,2021MNRAS.502.2757O,2022arXiv220712282K}).
+However, at the faint end at $\Muv\gtrsim -24$ mag, extended sources such as the brightest galaxies at $z\sim 6$ 
+dominate over quasars in number at the same UV magnitude \citep{2022ApJS..259...20H}.
+Thus, the current observations might miss quasars embedded in extended galaxy populations. 
+% We do not take into account of this effect in the QLF correction,
+% but we notice this important caveat and provide the galaxy number density information 
+% in the higher-$z$ QLF predictions (see \S~\ref{sec:qlfglf}).
+We leave this issue as an important caveat in high-$z$ quasar observations.
+
+% In Figs.~\ref{fig:fitmf} and \ref{fig:fitlf}, we show the total BHMF and unobscured (type-I) QLF at $z=$ 6 
+% reproduced by the best-fit parameters as well as the $1\sigma$ spread.
+% % where the QLF model excludes a contribution from obscured quasars, 
+% % yielding the {\it observed} QLF for type-I AGN populations.
+% The total BHMF indicated in \citetalias{2010AJ....140..546W} and QLF from \citetalias{2018ApJ...869..150M} 
+% with statistical errors are also overlaid for comparison.
+% We note that \citetalias{2010AJ....140..546W} constructed the BHMF using quasar samples with 
+% $10^8~\Msun \lesssim \Mbh \lesssim 3\times 10^9~\Msun$.
+% Our best-fit BHMF model well agrees with their observational constraints in this mass range.
+% The QLF fitting results are also consistent with the observed one over $-29~{\rm mag} \lesssim \Muv \lesssim -25~{\rm mag}$,
+% but seems to overproduce the abundance of fainter quasars at $\Muv>-24~{\rm mag}$.
+% % due to the lack of fine tuning by the model parameters in the low mass range, 
+% The difference at the fainter end tends to be alleviated with the seeding fraction lowered ($\fseed = 0.01$),
+% because the progenitors of $z=6$ BHs with $10^{7-8}~\Msun$ (or similarly, 
+% $-22~{\rm mag} \lesssim \Muv \lesssim -24~{\rm mag}$) were less massive seed BHs with $\sim 10^4~\Msun$,
+% which is closer to the peak of the seed mass distribution (see Fig.~\ref{fig:seedmf}).
+% Those BH population naturally produces a flatter slope of the QLF (and BHMF) at the faint (low-mass) end.
+% Overall, the parameters are inferred to be reasonable fits consistent with the observational data.
 
@@
 \label{fig:tau}
-\vspace{4mm}
+%\vspace{4mm}
 \end{figure*}
-
-\blue{
-The best-fit parameters for the two cases of $\fseed$ both reproduce the bulk properties of the BHMF and QLF at $z\sim 6$,
-despite in the $\fseed=0.01$ case the number of the whole BH population is ten times lower than that with $\fseed=0.1$.
-The two parameters characterizing the ERDF are given as
-$(\lambda_0,\alpha) = (0.89,0.12)$ and $(0.87,0.20)$ for $\fseed=0.1$ and $0.01$, respectively.
-With those values, the fraction of super-Eddington accreting BHs is estimated as $P(\lambda>1)=0.064$ and 0.075. 
-The probability of rapid accretion in each cycle in the $\fseed=0.01$ case is slightly higher than that with $\fseed=0.1$,
-while multiple accretion episodes enlarge the difference.
-Moreover, given the best fit values of $\delta=(0.001,0.055)$ for the two $\fseed$ cases,
-the higher $\delta$ value enhances the growth of small BHs with $M_\bullet <10^8~\Msun$ in the $\fseed=0.01$ case,
-so that massive BHs are produced with number densities similar to that in the $\fseed=0.1$ case,
-i.e., the ten-fold difference in $\fseed$ is nearly compensated.
-The characteristic Eddington ratio needs to be close to unity, otherwise the highest luminosity and BH mass
-in the model would differ from those in observations.
-On the other hand, the power-law index of $\alpha$ in the ERDF increases as the seeding fraction decreases,
-indicating that fraction of active BHs with $\lambda \gtrsim 1$ is elevated. 
-Thus, with lower seeding fractions, the high-$z$ quasar assembly ought to experience more active growth phases to reproduce the observations.
-}
-
-Next, we demonstrate that overall, the parameters are inferred to be reasonable fits consistent with the observational data of both of the BHMF and QLF.
-In Fig.~\ref{fig:fitmf}, we show the total BHMF at $z=$ 6 reproduced by the best-fit parameters as well as the $1\sigma$ spread.
-We also present the total BHMF indicated by \citetalias{2010AJ....140..546W} with statistical errors for comparison.
-The BHMF data put more constraints in the fitting procedure, and help the fitting converge.
-However, a complete BHMF is necessary for better constraints, especially the low-mass end, 
-which inherit more of the seeding information during a short growth time.
-For current comparison,
-we note that \citetalias{2010AJ....140..546W} constructed the BHMF using quasar samples with 
-$10^8~\Msun \lesssim \Mbh \lesssim 3\times 10^9~\Msun$.
-Our best-fit BHMF model well agrees with their constraints in this mass range.
-
-The unobscured (type-I) QLF fitting results at $z=$ 6 are presented in Fig.~\ref{fig:fitlf},
-along with the observed data from \citetalias{2018ApJ...869..150M}, which we adopt to the fitting.
-The best-fit QLF results are consistent with observation over $-29~{\rm mag} \lesssim \Muv \lesssim -25~{\rm mag}$.
-However, they overproduce the abundance of fainter quasars at $\Muv\gtrsim -24~{\rm mag}$,
-reflecting both the less constraints from observational data in the faint end,
-and the difficulty of reproducing such a small population of low-luminosity quasars based on our seeding and growth model.
-The difference at the fainter end tends to be alleviated with the seeding fraction lowered ($\fseed = 0.01$),
-because the progenitors of $z=6$ BHs with $10^{7-8}~\Msun$ (or similarly, 
-$-22~{\rm mag} \lesssim \Muv \lesssim -24~{\rm mag}$) were less massive seed BHs with $\sim 10^4~\Msun$,
-which is closer to the peak of the seed mass distribution (see Fig.~\ref{fig:seedmf}).
-Those BH population naturally produces a flatter slope of the QLF (and BHMF) at the faint (low-mass) end.
-In \citet{2022NatAs...6..850J}, an upper limit of the faint end QLF is provided, % by non-detection of faint quasars
-by analyzing this population in the Hubble Space Telescope (HST) imaging fields.
-Our best-fit unobscured QLF results lie within their constraints.
-
-On the other hand, studies on X-ray selected faint quasars report number densities much higher than that
-extrapolated from rest-UV observations \citep{2015A&A...578A..83G,2019ApJ...884...19G}.
-In addition to the systematic difference in the quasar identification methods,
-the X-ray observation should suffer less dust obscuration (see \S~\ref{sec:LF}),
-thus detect more quasars in the faint end.
-We also show the intrinsic QLF predicted by our best-fit parameters,
-which is without imposing obscuration thus representing the upper bound of detectable quasar numbers.
-Our intrinsic QLF is broadly consistent with the faint-end QLF from X-ray observation,
-despite slightly lower than their data points at $\Muv\gtrsim -21$ mag.
-% outshining effect
-From another point of view, studies explain the decrepancy of the UV and X-ray QLF in the faint end
-by pointing out that only AGNs outshining their host galaxies can be identified by the point source criteria
-in the rest-UV selection \citep{2020MNRAS.495.2135N,2021MNRAS.502.2757O,2022arXiv220712282K}.
-Especially in the faint end at $\Muv\gtrsim -24$ mag, the galaxy population can potentially contribute to this contamination significantly 
-\citep{2022ApJS..259...20H}.
-We do not take into account of this effect in the QLF correction,
-but we notice this important caveat and provide the galaxy number density information 
-in the higher-$z$ QLF predictions (see \S~\ref{sec:qlfglf}).
-
-% In Figs.~\ref{fig:fitmf} and \ref{fig:fitlf}, we show the total BHMF and unobscured (type-I) QLF at $z=$ 6 
-% reproduced by the best-fit parameters as well as the $1\sigma$ spread.
-% % where the QLF model excludes a contribution from obscured quasars, 
-% % yielding the {\it observed} QLF for type-I AGN populations.
-% The total BHMF indicated in \citetalias{2010AJ....140..546W} and QLF from \citetalias{2018ApJ...869..150M} 
-% with statistical errors are also overlaid for comparison.
-% We note that \citetalias{2010AJ....140..546W} constructed the BHMF using quasar samples with 
-% $10^8~\Msun \lesssim \Mbh \lesssim 3\times 10^9~\Msun$.
-% Our best-fit BHMF model well agrees with their observational constraints in this mass range.
-% The QLF fitting results are also consistent with the observed one over $-29~{\rm mag} \lesssim \Muv \lesssim -25~{\rm mag}$,
-% but seems to overproduce the abundance of fainter quasars at $\Muv>-24~{\rm mag}$.
-% % due to the lack of fine tuning by the model parameters in the low mass range, 
-% The difference at the fainter end tends to be alleviated with the seeding fraction lowered ($\fseed = 0.01$),
-% because the progenitors of $z=6$ BHs with $10^{7-8}~\Msun$ (or similarly, 
-% $-22~{\rm mag} \lesssim \Muv \lesssim -24~{\rm mag}$) were less massive seed BHs with $\sim 10^4~\Msun$,
-% which is closer to the peak of the seed mass distribution (see Fig.~\ref{fig:seedmf}).
-% Those BH population naturally produces a flatter slope of the QLF (and BHMF) at the faint (low-mass) end.
-% Overall, the parameters are inferred to be reasonable fits consistent with the observational data.
 
@@
 \centering
-\includegraphics[width=160mm]{BHMF_rhoz.png}
+\includegraphics[width=160mm]{BHMF_rhoz1.png}
 \caption{
+\if0
 {\it Left panel}: BH mass functions at $z=6-10$. 
@@
 The evolutionary trend can be approximated as $\rho_\bullet (z) \propto 10^{k_M z}$, where $k_M\simeq -0.68$.
+\fi
 }
@@
 where $\tlife=18.76$ Myr, $\delta=0.055$, $\lambda_0=0.87$, and $\alpha=0.20$.
-We apply the result to construction of BHMFs and QLFs at higher redshifts and give implications for
+We apply the result to construct BHMFs and QLFs at higher redshifts and give implications for
 the future explorations of high-$z$ quasars.
@@
 
-In the left panel of Fig.~\ref{fig:BHMF_rhoz}, we show our predictions of the BHMFs at five different redshifts of $z=6-10$.
-For all redshift bins, the BHMFs can be characterized with a double power-law function, similar to lower-$z$ quasar populations
-\citep[e.g.,][]{2013ApJ...764...45K,2015MNRAS.447.2085S}.
-From higher to lower redshifts, the number density of BHs heavier than $M_{\rm min} = 10^7~\Msun$ increases
-and the high-mass tail of the distribution is extended owing to efficient growth of the most massive BH population.
-%The number density of BHs with $\Mbh=10^7~\Msun$ emerging from high redshifts increase by a factor of $\sim 4$ per unit redshift.
-In the right panel of Fig.~\ref{fig:BHMF_rhoz}, we also present the cumulative mass density of BHs with $\Mbh \geq M_{\rm min}$ in a comoving volume,
+In the left panel of Fig.~\ref{fig:BHMF_rhoz}, we show our predictions of the BHMFs at five different redshifts of $z=6-10$,
+with both cases of $\fseed=0.1$ and 0.01.
+The seed BH mass function is already established with $M_\bullet \lesssim 2\times10^5~\Msun$ earlier than $z\sim 17$,
+so the BHMF at mass ranges higher than the typical seed mass is grown from a portion of $\fseed$ of all seeds.
+Therefore, with $\fseed=0.1$, the number of growing seeds is 10 times higher than in the $\fseed =0.01$ case,
+which is partially reflected by the difference of BHMFs at $M_\bullet \sim 10^{5-6}~\Msun$ in their early growth.
+As for $M_\bullet \gtrsim 10^7~\Msun$, which is potentially accessible by quasar observations,
+in all redshift bins, the BHMFs can be characterized with a double power-law function,
+similar to lower-$z$ quasar populations \citep[e.g.,][]{2013ApJ...764...45K,2015MNRAS.447.2085S}.
+Toward lower redshifts, the number density of BHs in the high-mass tail increases
+and SMBHs with $M_\bullet \gtrsim 10^9~\Msun$ emerge owing to efficient growth of the massive BH population.
+Constrained by the \citetalias{2010AJ....140..546W} BHMF with $M_\bullet \sim 10^8-3\times 10^9~\Msun$ at $z=6$, 
+the two $\fseed$ cases produce similar BHMF at in this mass and redshift range (see \S~\ref{sec:fitting_result}),
+while in the low mass range ($M_\bullet \lesssim 10^7~\Msun$), the difference in the two BHMF shapes is profound.
+The difference is also shown by the mass ranges where the slope of BHMF is close to $\alpha_{M_\bullet}\simeq -1$,
+i.e., the typical masses which dominate the cumulative mass density
+(see \S~\ref{sec:fitting_result}). In the case of $\fseed=0.01$, this typical mass range is higher,
+despite the integrated mass density is lower than that with $\fseed=0.1$.
+
+In the right panel of Fig.~\ref{fig:BHMF_rhoz}, 
+we also present the evolution of BH cumulative mass density in a comoving volume,
 defined by the integration of the BHMF as
 %
+\begin{equation}
+ \rho_\bullet(z)=\int_{\mathcal{D}}^{} \Phi_{\Mbh} (z) \Mbh \D \log \Mbh,
+\end{equation}
+%
+where the mass ranges are $\mathcal{D} = M_{\bullet}<10^6$,
+$10^6<M_{\bullet}<10^8$, and $M_\bullet>10^8~\Msun$.
+% Varying the mass ranges as $\mathcal{D} = [,10^5]$, $[10^5,10^6]$, $[10^6,10^8]$, and $[10^8,]~\Msun$,
+% Varying the mass ranges as $\mathcal{D} = \{M_{\bullet}<10^5\}, \{M_{\bullet} \rm{in} 10^{5-6}\}, 
+% 10^{6-8}$, and $M_{\bullet}>10^8~\Msun$,
+The mass density predicted by the $\fseed=0.1$ case is overall higher than that with $\fseed=0.01$.
+However, with $\fseed=0.01$, BHs in the low mass range quickly evolve into higher masses, 
+leading to convergent results in the two cases at $z\sim 6$.
+For comparison, we overlay the results of BH mass density evolution with $10^6<M_{\bullet}<10^8$, and $M_\bullet>10^8~\Msun$
+from cosmological simulations in \citet{2022MNRAS.513..670N}, with the dashed-dotted line and square colored according to the mass ranges.
+At lower redshifts $z\lesssim 7$, our results are in overall good agreement with theirs.
+However, our models predict more $10^{6-8}~\Msun$ BHs emerging at $z\sim 10-8$,
+owing to the joint effect of our seeding scenario and growth model,
+the former produces BH seeds earlier than their stringent seeding criteria,
+and the latter allows super-Eddington episodes occur which lead to rapid BH growth.
+The upper limit from the integrated X-ray emission \citep{2013ApJ...778..130T} is denoted by red triangles.
+The total BH mass density should be dominated by abundant low mass BHs, which is not comprised in our quasar host halos.
+In this sense, our BHs which result in observable quasars at $z\sim 6$ are a biased population.
+
+%
+\if0
 \begin{equation}
@@
 \end{table}    
+\fi
 
@@
 %which is interesting to be probed with future observations.
-In Fig.~\ref{fig:LFs}, we divide the cosmological QLF into four different epochs; (a) $z\simeq 7$, (b) $z\simeq 8$, (c) $z\simeq 9$, and (d) $z\simeq 10-13$.
+In Fig.~\ref{fig:LFs}, we divide the cosmological QLF evolution into four different epochs; (a) $z\simeq 7$, (b) $z\simeq 8$, (c) $z\simeq 9$, and (d) $z\simeq 10-13$.
 The black solid and dashed curves present the QLF for the unobscured population (i.e., type-I AGNs, same as those in Fig.~\ref{fig:QLF_rhoz})

### 2022-09-01 ms.tex
version0901; me:all revised; next: check k revision

@@
 %%%%%%%
-\begin{figure*}
+\begin{figure}
 \centering
-\includegraphics[width=160mm]{QLF_rhoz.png}
+\includegraphics[width=85mm]{M0r8_f2QLF.png} % width=160 QLF_rhoz.png
 \caption{
-{\it Left panel}: quasar luminosity functions at $z=6-10$. 
-The solid lines denote modeled QLF produced by the best-fit parameters and the shaded regions present the $1\sigma$ spread. 
-{\it Right panel}: the redshift evolution of the cumulative number density of quasars with $\Muv <-26~{\rm mag}$ in a comoving volume,
-evaluated by the integration of the QLF shown in the left panel.
-The evolutionary trend can be approximated as $n(\Muv<-26~{\rm mag})\propto 10^{k_{L} z}$, where $k_L \simeq -0.96$.
-This result indicates rapid decline of the number of bright quasars toward higher redshifts, consistent with previous observations
-\citep[red data points; see][]{2016ApJ...833..222J, 2019ApJ...884...30W}
+% {\it Left panel}: quasar luminosity functions at $z=6-10$. 
+% The solid lines denote modeled QLF produced by the best-fit parameters and the shaded regions present the $1\sigma$ spread. 
+% {\it Right panel}: the redshift evolution of the cumulative number density of quasars with $\Muv <-26~{\rm mag}$ in a comoving volume,
+% evaluated by the integration of the QLF shown in the left panel.
+% The evolutionary trend can be approximated as $n(\Muv<-26~{\rm mag})\propto 10^{k_{L} z}$, where $k_L \simeq -0.96$.
+% This result indicates rapid decline of the number of bright quasars toward higher redshifts, consistent with previous observations
+% \citep[red data points; see][]{2016ApJ...833..222J, 2019ApJ...884...30W}
 }
@@
 \vspace{5mm}
-\end{figure*}
-
-\subsection{Quasar luminosity function}
+\end{figure}
+
+\subsection{Quasar number density evolution}
 \label{sec:qlfglf}
-Next, we show our prediction of $z=6-10$ unobscured QLFs taken from the BH growth model in the left panel of Fig.~\ref{fig:QLF_rhoz}.
+\blue{(my revision on Fig.~\ref{fig:QLF_rhoz} description)
+Next, in Fig.~\ref{fig:QLF_rhoz} we show unobscured quasar number densities at different magnitudes evolving with redshift.
+Based on our best-fit parameters in the BH growth model, 
+we predict the number densities evolution at $z\sim 6-10$, of quasars at $\Muv=-23$ to $-27$ mag.
+We also show the quasar number densities from previous observational studies, depicting the cosmic QLF evolution from $z\sim 0-6$
+\citep{2006AJ....131.2766R,2008ApJ...675...49S,2013ApJ...768..105M,2018PASJ...70S..34A,2018ApJ...869..150M,2020ApJ...904...89N}.
+Peaking at $z\sim 2-3$, the quasar number densities at all magnitudes decline exponentially toward high redshifts.
+A rapid decay of the quasar number density toward higher redshifts is found by previous studies
+\citep[e.g.,][]{2001AJ....122.2833F,2013ApJ...768..105M,2016ApJ...833..222J,2019ApJ...884...30W},
+which show $k_{\rm L}= -0.47$ and $-0.72$ from the analysis of quasar samples at $z\simeq 3-5$ and $z\simeq 5-6$, respectively.
+From our theoretical prediction, the evolutionary trend of luminous quasar number density of with $\Muv <-26~{\rm mag}$ can
+be fitted as $\propto 10^{k_{\rm L}z}$, where $k_{\rm L}\approx -0.97$.
+The rapid decline toward higher redshifts is characterized by the treatment of episodic natures of BH accretion with a finite value of
+$\tau ~(\simeq 20~{\rm Myr})$, in order to match the statistical properties of high-$z$ quasars.
+We also note that the tendency would be explained by the rarity of massive quasar-host halos at higher redshifts,
+non-constant radiative efficiencies that covert the BH growth rate into the luminosity, or some combination of these effects
+\citep[e.g.,][]{2010ApJ...718..231S}.
+}
+
 Similar to the BHMF, for all the redshift range, the shape of the QLF is well approximated with a double power-law function.

### 2022-09-03 ms.tex
version0903; revision 1st roll following k0901

--- 2022-08-30 ms.tex
@@
 \vspace{2mm}
-\section{Results}\label{sec:result}
-
-\vspace{2mm}
-\subsection{Fitting Results}\label{sec:fitting_result}
+%\section{Results}\label{sec:result}
+\section{Results}\label{sec:fitting_result}
+
+%\vspace{2mm}
+%\subsection{Fitting Results}\label{sec:fitting_result}
 
@@
 \centering
-\includegraphics[width=160mm]{fits_MF.png}
+\includegraphics[width=145mm]{fits_MF.png}
 \caption{
@@
 \centering
-\includegraphics[width=160mm]{fits_LF.png}
+\includegraphics[width=145mm]{fits_LF.png}
 \caption{
@@
 \label{fig:fitlf}
+\vspace{2mm}
 \end{figure*}
@@
 
-%%%%%%%
-%    Fig. 
-%%%%%%%
-\begin{figure*}
-\centering
-\includegraphics[width=160mm]{tau.png}
-\caption{
-The BH mass function (left) and quasar luminosity function (right) at $z=$ 6 in the case of $\fseed=0.01$, 
-with different values of $\tlife=$ 10, 18 (the best-fit value), and 50 Myr, respectively.
-Note that the other parameters are fixed to the best-fit values. 
-The $z=6$ BHMF (\citetalias{2010AJ....140..546W}) and QLF (\citetalias{2018ApJ...869..150M}) 
-are overlaid with the blue curve and data points.
-With shorter (longer) timescales of each accretion episode $\tlife$, the number of BHs at the high mass end and bright end is under(over)-produced.
-%Right panel: QLF at $z=$ 6 calculated with the same parameters as in the left panel.
-%The overlaid blue dots are from the \citetalias{2018ApJ...869..150M} $z\sim$ 6 quasar observation. 
-%With $\tlife$ values different from the best-fit value, the consequent QLF show 
-%similar trends of deviation from observation as in the BHMF curves.
-Multiple accretion bursts in each duration of $\tau \simeq 20$ Myr best produce the observations,
-which is nearly half of the $e$-folding time of the exponential BH mass growth.
-}
-\label{fig:tau}
-%\vspace{4mm}
-\end{figure*}
-
-\vspace{2mm}
-\subsection{Model dependence}\label{sec:modep}
-As described in \S~\ref{sec:model}, we introduce the parameter $\tau$ as a typical timescale
-for individual durations of quasar accretion activity.
-Specifically, we assign an Eddington ratio $\lambda$ following the ERDF for all BHs in each cycle
-with a time duration of $\tau$.
-Variable accretion episodes in every cycle essentially modify the effective ERDF in the whole BH growth history,
-because multiple sampling of $\lambda$ reduces the possibility of a BH growing with $\lambda \gtrsim \lambda_0$
-compared to that with a single sampling of $\lambda$.
-%However at any time during growth, the ERDF of the BH population remains the same as at $z\sim$ 6,
-%therefore we ensure treating all cosmic time equally.
-In what follows, we demonstrate the role of $\tlife$ in shaping the BHMF evolution and the consequent QLF.
-% tau极端小，则非常小的lambda，不能解释 （且delta func？ 有必要说或是放在后面讨论？）
-
-In the left panel of Fig.~\ref{fig:tau}, we present the BHMF at $z=6$ for three different values of $\tlife=10$, $18$, and $50$ Myr,
-but keeping the other parameters to the best-fit values ($\lambda_0=0.87$ and $\alpha=0.20$) for the case with $\fseed=0.01$.
-We note that $\tlife \approx$ 18 Myr is the best-fit value reproducing the BHMF consistent with that of \citetalias{2010AJ....140..546W}.
-%the other two cases demonstrate the sensitivity of the $\tlife$ value in producing the bulk of massive BHs
-%and the slope in the high mass tail.
-For $\tlife=10$ Myr, the frequency of Eddington ratio assignment increases by a factor of two until $z=6$.
-%to $\sim$ 80 from $\sim$ 40 with the best-fit $\tlife$ value.
-Therefore, continuous and efficient growth of BHs with $\lambda \gtrsim \lambda_0$ is less likely to occur,
-%high Eddington ratio accretion along the growth is lower,
-suppressing the formation of BHs heavier than $M_\bullet \simeq 10^8~\Msun$.
-Moreover, if a high Eddington ratio is given with a certain but low probability, the BH mass hardly increases
-within $\tlife=10$ Myr, which is $\simeq 20\%$ of the $e$-folding timescale.
-On the other hand, for $\tlife=$ 50 Myr, there is a non-negligible probability that
-% $\sim$ 16 times of Eddington ratio assignment,
-more BHs experience high accretion rates with $\lambda\gtrsim \lambda_0$ through their assembly history.
-%high values of $\lambda\gtrsim \lambda_0$ is non-negligibly realized in the BHMF evolution.
-Therefore, the high mass end of the BHMF is further enhanced and those massive populations are substantially
-overproduced compared to the observed abundance.
-%in the high mass end of BHMF at $z=$ 6, the BH population is significantly overproduced than the constraints from observation.
-
-The QLF at $z=6$ is shown in the right panel of Fig.~\ref{fig:tau}.
-%In the conversion from BHMF to QLF, the ERDF is the same for different $\tlife$ values,
-%following the $P(\lambda)$ in Eq.~(\ref{eq:Pl}) with $\lambda_0=0.87$ and $\alpha=0.20$.
-Overall, the dependence of the QLF on the choice of $\tau$ shows the same trend as in the BHMF,
-%the deviation from the observed QLF of \citetalias{2018ApJ...869..150M} shows similar trends as in the BHMF.
-i.e., higher (lower) $\tlife$ values lead to under(over)-production of the luminous quasar population.
-The best-fit value of $\tlife (\simeq 18$ Myr) favors a moderate fraction of $t_{\rm S}$.
-This result demonstrates the importance of early BHs experiencing multiple accretion episodes to 
-reproduce the observed distributions of BH mass and luminosity of quasars at $z\sim$ 6.
-In \S\ref{sec:evol}, we apply this episodic accretion model to individual growth pathways of high-$z$ quasars
-and demonstrate that normal seeding mechanisms can explain the existence of massive BHs with low luminosity
-observed at $z\simeq 6-7$.
-
-\vspace{2mm}
+%\vspace{2mm}
 \section{Cosmological evolution of BH mass and quasar luminosity function}\label{sec:cosm}
@@
 \centering
-\includegraphics[width=160mm]{BHMF_rhoz1.png}
+\includegraphics[width=175mm]{BHMF_rhoz1.png}
 \caption{
@@
 \label{fig:BHMF_rhoz}
-\vspace{4mm}
+\vspace{0mm}
 \end{figure*}
@@
 us to probe the statistical aspect of BH evolution at higher redshifts.
-As a fiducial case, we take the best-fit parameters of BH growth for our $\fseed=$ 0.01 model,
-where $\tlife=18.76$ Myr, $\delta=0.055$, $\lambda_0=0.87$, and $\alpha=0.20$.
-We apply the result to construct BHMFs and QLFs at higher redshifts and give implications for
+%As a fiducial case, we take the best-fit parameters of BH growth for our $\fseed=$ 0.01 model,
+%where $\tlife=18.76$ Myr, $\delta=0.055$, $\lambda_0=0.87$, and $\alpha=0.20$.
+We apply the result to construct BHMFs and QLFs at $z\geq 6$ and give implications for
 the future explorations of high-$z$ quasars.
 
-\subsection{Black hole mass function}
-
-In the left panel of Fig.~\ref{fig:BHMF_rhoz}, we show our predictions of the BHMFs at five different redshifts of $z=6-10$,
-with both cases of $\fseed=0.1$ and 0.01.
-The seed BH mass function is already established with $M_\bullet \lesssim 2\times10^5~\Msun$ earlier than $z\sim 17$,
-so the BHMF at mass ranges higher than the typical seed mass is grown from a portion of $\fseed$ of all seeds.
-Therefore, with $\fseed=0.1$, the number of growing seeds is 10 times higher than in the $\fseed =0.01$ case,
-which is partially reflected by the difference of BHMFs at $M_\bullet \sim 10^{5-6}~\Msun$ in their early growth.
-As for $M_\bullet \gtrsim 10^7~\Msun$, which is potentially accessible by quasar observations,
-in all redshift bins, the BHMFs can be characterized with a double power-law function,
+\subsection{Black Hole Mass Functions}
+
+In the left panel of Fig.~\ref{fig:BHMF_rhoz}, we show the predicted BHMFs at five different redshifts of $z=6-10$
+for $\fseed=0.1$ (solid) and $0.01$ (dashed).
+Since the mass distribution of seed BHs is already established at $M_\bullet \lesssim 2\times10^5~\Msun$ earlier on ($z\gtrsim 17$),
+the high-mass tail of the BHMF is built up owing to a fraction $\fseed$ of all the seeds.
+Therefore, the case with $\fseed=0.1$ yields the number of growing seeds ten times higher compared to the case with $\fseed =0.01$,
+making the difference of the abundance at $M_\bullet \sim 10^{5-6}~\Msun$\footnote{
+For each case, a fraction $(1-\fseed)$ of BHs are assumed to keep the original mass at birth without subsequent growth.}.
+For BHs with $M_\bullet \gtrsim 10^7~\Msun$, which is potentially accessible by quasar observations,
+the BHMFs can be characterized with a double power-law function,
 similar to lower-$z$ quasar populations \citep[e.g.,][]{2013ApJ...764...45K,2015MNRAS.447.2085S}.
@@
 and SMBHs with $M_\bullet \gtrsim 10^9~\Msun$ emerge owing to efficient growth of the massive BH population.
-Constrained by the \citetalias{2010AJ....140..546W} BHMF with $M_\bullet \sim 10^8-3\times 10^9~\Msun$ at $z=6$, 
-the two $\fseed$ cases produce similar BHMF at in this mass and redshift range (see \S~\ref{sec:fitting_result}),
-while in the low mass range ($M_\bullet \lesssim 10^7~\Msun$), the difference in the two BHMF shapes is profound.
-The difference is also shown by the mass ranges where the slope of BHMF is close to $\alpha_{M_\bullet}\simeq -1$,
-i.e., the typical masses which dominate the cumulative mass density
-(see \S~\ref{sec:fitting_result}). In the case of $\fseed=0.01$, this typical mass range is higher,
-despite the integrated mass density is lower than that with $\fseed=0.1$.
-
-In the right panel of Fig.~\ref{fig:BHMF_rhoz}, 
-we also present the evolution of BH cumulative mass density in a comoving volume,
+Constrained by the \citetalias{2010AJ....140..546W} BHMF with $M_\bullet \simeq 10^8-3\times 10^9~\Msun$ at $z=6$,
+the two cases produce similar shape of mass distribution in this mass and redshift range (see \S~\ref{sec:fitting_result}),
+while the difference in the two BHMF shapes is profound toward the low mass range of $M_\bullet \lesssim 10^7~\Msun$.
+%The BH abundance and shape of the mass distribution at $10^5 \lesssim M_\bullet/\Msun \lesssim 10^7$ depend on the seeding fraction,
+%while the distributions converge at $M_\bullet \gg 10^7~\Msun$ toward $z= 6$. 
+This result suggests that the information on the seeding process would still remain in the low mass regime of $M_\bullet \lesssim 10^7~\Msun$.
+%
+%The different seeding fraction varies the characteristic BH mass where the BHMF slope is close to $\alpha_{M_\bullet}\simeq -1$,
+%i.e., the typical masses which dominate the cumulative mass density (see \S~\ref{sec:fitting_result}). 
+% the difference is also shown by the mass ranges where the slope of BHMF is close to $\alpha_{M_\bullet}\simeq -1$,
+%i.e., the typical masses which dominate the cumulative mass density (see \S~\ref{sec:fitting_result}). 
+%In the case of $\fseed=0.01$, this typical mass range is higher, despite the integrated mass density is lower than that with $\fseed=0.1$.
+
+In the right panel of Fig.~\ref{fig:BHMF_rhoz}, we present the cumulative mass density of BHs in a comoving volume
+for $\fseed=0.1$ (solid) and $0.01$ (dashed),
 defined by the integration of the BHMF as
@@
 \begin{equation}
- \rho_\bullet(z)=\int_{\mathcal{D}}^{} \Phi_{\Mbh} (z) \Mbh \D \log \Mbh,
+ \rho_\bullet(z)=\int_{\mathcal{I}} \Phi_{\Mbh} (z) \Mbh ~\D \log \Mbh.
 \end{equation}
 %
-where the mass ranges are $\mathcal{D} = M_{\bullet}<10^6$,
-$10^6<M_{\bullet}<10^8$, and $M_\bullet>10^8~\Msun$.
-% Varying the mass ranges as $\mathcal{D} = [,10^5]$, $[10^5,10^6]$, $[10^6,10^8]$, and $[10^8,]~\Msun$,
-% Varying the mass ranges as $\mathcal{D} = \{M_{\bullet}<10^5\}, \{M_{\bullet} \rm{in} 10^{5-6}\}, 
-% 10^{6-8}$, and $M_{\bullet}>10^8~\Msun$,
-The mass density predicted by the $\fseed=0.1$ case is overall higher than that with $\fseed=0.01$.
-However, with $\fseed=0.01$, BHs in the low mass range quickly evolve into higher masses, 
-leading to convergent results in the two cases at $z\sim 6$.
-For comparison, we overlay the results of BH mass density evolution with $10^6<M_{\bullet}<10^8$, and $M_\bullet>10^8~\Msun$
-from cosmological simulations in \citet{2022MNRAS.513..670N}, with the dashed-dotted line and square colored according to the mass ranges.
-At lower redshifts $z\lesssim 7$, our results are in overall good agreement with theirs.
+Here, we consider three mass ranges: $M_\bullet \leq 10^6~\Msun$ (blue), $10^6~\Msun < M_\bullet < 10^8~\Msun$ (orange),
+and $M_\bullet \geq 10^8~\Msun$ (green).
+Overall, the mass density of the heaviest BHs quickly grows toward lower redshifts,
+while the mass density barely evolves for the lightest BHs.
+At $z\lesssim 7-8$, more massive BHs with $\gg 10^6~\Msun$ begin to dominate the total mass budget of the entire BH population,
+promoting the so-called downsizing or anti-hierarchical evolution of massive BHs 
+in terms of mass occupation \citep[e.g.,][]{2014ApJ...786..104U}.
+Moreover, as shown in the left panel, the mass-density evolution is affected by the choice of the seeding fraction more substantially
+for less massive BHs that keep the information on their initial conditions at birth.
+
+%%%%%%%
+%    Table. 2 
+%%%%%%%
+%\startlongtable
+\begin{deluxetable*}{lccccccc}%[t!]
+\tablecolumns{1}
+\renewcommand\thetable{1} %! fix indexing
+\tablewidth{0pt} 
+\tablecaption{Detection Number of Quasars Estimated for Future Surveys}
+\tablehead{
+  \colhead{Telescope} & \colhead{ Survey area} & \colhead{Photo. depth} &  \colhead{$N(z\sim 6)$} & \colhead{$N(z\sim 7)$}& \colhead{$N(z\sim 8)$}&  \colhead{$N(z\sim 9)$}&  \colhead{$N(z\sim 10)$}\\
+  \colhead{} & \colhead{(\rm{deg}$^2$)} & \colhead{(AB mag)} & & & & & 
+}
+\startdata
+Wide RST    &  2000 & 27   & 6758 &  1514 &  349 & 85 & 25  \\
+Wide Euclid & 15000 & 24   & 6653  &  708 &   93 & -- & --  \\
+\enddata
+\label{tab:N_detect}
+\tablecomments{
+Based on the 5$\sigma$ point source detection limits, the number of quasars at each redshift are predicted
+with the assumption of the survey volume with $\Delta z =1$ and 100\% completeness.
+}
+\end{deluxetable*}
+
+%The mass density predicted by the $\fseed=0.1$ case is overall higher than that with $\fseed=0.01$.
+%However, with $\fseed=0.01$, BHs in the low mass range quickly evolve into higher masses,
+%leading to convergent results in the two cases at $z\sim 6$.
+For comparison, we overlay the BH mass density evolution with $10^6<M_{\bullet}<10^8$, and $M_\bullet>10^8~\Msun$
+obtained from the cosmological simulations in \citet{2022MNRAS.513..670N} (open square symbols).
+At $z\lesssim 7$, our results are in overall good agreement with those simulation results.
 However, our models predict more $10^{6-8}~\Msun$ BHs emerging at $z\sim 10-8$,
-owing to the joint effect of our seeding scenario and growth model,
-the former produces BH seeds earlier than their stringent seeding criteria,
-and the latter allows super-Eddington episodes occur which lead to rapid BH growth.
-The upper limit from the integrated X-ray emission \citep{2013ApJ...778..130T} is denoted by red triangles.
-The total BH mass density should be dominated by abundant low mass BHs, which is not comprised in our quasar host halos.
-In this sense, our BHs which result in observable quasars at $z\sim 6$ are a biased population.
-
-%
+owing to the joint effect of our seeding and growth prescription that allows seed formation earlier on 
+and (modest) super-Eddington episodes.
+%the former produces BH seeds earlier than their stringent seeding criteria,
+%and the latter allows super-Eddington episodes occur which lead to rapid BH growth.
+Furthermore, the measured unresolved fraction of the cosmic X-ray background constrains
+the global accretion history of massive BHs at $z>5$ \citep{2012A&A...545L...6S,2013ApJ...778..130T}.
+Upper bounds on the accreted-mass density onto massive BHs (red triangles) prohibits overproduction of low mass BHs at cosmic dawn.
+Our quasar sample in the biased, overdense region of the universe (haboring DM halos with $\Mh\gtrsim 10^{11}~\Msun$) 
+are consistent with the constraint, unlike models that require a large number of stellar-mass BH remnants.
+
 \if0
-\begin{equation}
- \rho_\bullet(z)=\int_{M_{\rm min}}^{\infty} \Phi_{\Mbh} (z) \Mbh \D \log \Mbh.
-\end{equation}
-%
-%as a function of redshift.
 Varying the minimum mass as $M_{\rm min}=10^7$, $10^8$, and $10^9~\Msun$,
@@
 
-%%%%%%%
-%    Fig. 
-%%%%%%%
-\begin{figure*}
+\subsection{Quasar Luminosity Functions}
+\label{sec:qlfglf}
+
+%%%%%%%
+%    Fig. 9
+%%%%%%%
+\begin{figure*}[h!]
 \centering
-\includegraphics[width=160mm]{QLF_rhoz.png}
-\caption{
-{\it Left panel}: quasar luminosity functions at $z=6-10$. 
-The solid lines denote modeled QLF produced by the best-fit parameters and the shaded regions present the $1\sigma$ spread. 
-{\it Right panel}: the redshift evolution of the cumulative number density of quasars with $\Muv <-26~{\rm mag}$ in a comoving volume,
-evaluated by the integration of the QLF shown in the left panel.
-The evolutionary trend can be approximated as $n(\Muv<-26~{\rm mag})\propto 10^{k_{L} z}$, where $k_L \simeq -0.96$.
-This result indicates rapid decline of the number of bright quasars toward higher redshifts, consistent with previous observations
-\citep[red data points; see][]{2016ApJ...833..222J, 2019ApJ...884...30W}
+\includegraphics[width=85mm]{M0r8_f2linLF_spreadz7_KI.pdf}\hspace{5mm}
+\includegraphics[width=85mm]{M0r8_f2linLF_spreadz8_KI.pdf}\\\vspace{5mm}
+\includegraphics[width=85mm]{M0r8_f2linLF_spreadz9_KI.pdf}\hspace{5mm}
+\includegraphics[width=85mm]{M0r8_f2linLF_spreadz10_KI.pdf}
+\caption{Predicted quasar luminosity functions and depths and volumes of upcoming surveys.
+The black solid and dashed curves present the QLF for the unobscured population (e.g., type-I AGNs) 
+and the whole population (i.e., type-I and type-II AGNs), and the shaded region presents the $1\sigma$ spread.
+The expected depths and volumes of future surveys with Wide RST and Wide Euclid are overlaid with the blue lines,
+indicating the detectability of quasars at these redshifts.
+Galaxy UV luminosity functions are plotted with the data points (grey) and fitting functions with a Schechter (dotted curve) and double power-law (dash-dotted curve) shape.
+The galaxy luminosity function data at $z\sim$ 7 are taken from \citet{2022ApJS..259...20H} and \citet{2021AJ....162...47B}. 
+At $z\sim$ 8, the data points are from \citet{2021AJ....162...47B},
+\citet{2022arXiv220712356D}, \citet{2013MNRAS.432.2696M}, \citet{2020MNRAS.493.2059B}, and \citet{2019ApJ...883...99S}.
+At  $z\sim$ 9, those data are from \citet{Harikane_2022c}, \citet{2022arXiv220712356D}, \citet{2020MNRAS.493.2059B}, \citet{2019ApJ...883...99S}, 
+and \citet{2018ApJ...867..150M}.
+At $z\sim$ $10-13$, we take data from \citet{Harikane_2022c}, \citet{2022arXiv220712356D}, \citet{Harikane_2022b}, \citet{2022arXiv220709434N}, \citet{2018ApJ...867..150M}, 
+and \citet{2016ApJ...819..129O}.
+The fitting forms of the luminosity functions are given by \citet{2022ApJS..259...20H} at $z\simeq 7$, 
+\citet{2020MNRAS.493.2059B} and \citet{2013MNRAS.432.2696M} at $z\simeq 8$, and \citet{Harikane_2022c} at $9\lesssim z\lesssim 13$.
 }
-\label{fig:QLF_rhoz}
-\vspace{5mm}
+\label{fig:LFs}
 \end{figure*}
 
-\subsection{Quasar luminosity function}
-\label{sec:qlfglf}
+\if0
 Next, we show our prediction of $z=6-10$ unobscured QLFs taken from the BH growth model in the left panel of Fig.~\ref{fig:QLF_rhoz}.
@@
 %and this calls consideration of the more realistic BH-galaxy coevolution in understanding the observable AGN properties.
-
+\fi
+
+Next, we show our prediction of $z=6-10$ unobscured QLFs taken from the BH growth model.
 %On the other hand, the statistics of BH masses together with the ERDF in their growth history can rebuild quasar luminosity functions across cosmic time,
@@
 but the correction factor is highly uncertain at the faint end of $\Muv\gtrsim -20$ mag.
+Similar to the BHMF, for all the redshift range, the shape of the QLF is well approximated with a double power-law function.
+From higher to lower redshifts, the number density of luminous quasars increases and the bright-end of the distribution rises.
 % sampled in \citet{2014ApJ...786..104U},
@@
 %%%%%%%
-%    Fig. 9
-%%%%%%%
-\begin{figure*}[h!]
+%    Fig. 
+%%%%%%%
+\begin{figure}
 \centering
-\includegraphics[width=85mm]{M0r8_f2linLF_spreadz7_KI.pdf}\hspace{5mm}
-\includegraphics[width=85mm]{M0r8_f2linLF_spreadz8_KI.pdf}\\\vspace{5mm}
-\includegraphics[width=85mm]{M0r8_f2linLF_spreadz9_KI.pdf}\hspace{5mm}
-\includegraphics[width=85mm]{M0r8_f2linLF_spreadz10_KI.pdf}
-\caption{Predicted quasar luminosity functions and depths and volumes of upcoming surveys.
-The black solid and dashed curves present the QLF for the unobscured population (e.g., type-I AGNs) 
-and the whole population (i.e., type-I and type-II AGNs), and the shaded region presents the $1\sigma$ spread.
-The expected depths and volumes of future surveys with Wide RST and Wide Euclid are overlaid with the blue lines,
-indicating the detectability of quasars at these redshifts.
-Galaxy UV luminosity functions are plotted with the data points (grey) and fitting functions with a Schechter (dotted curve) and double power-law (dash-dotted curve) shape.
-The galaxy luminosity function data at $z\sim$ 7 are taken from \citet{2022ApJS..259...20H} and \citet{2021AJ....162...47B}. 
-At $z\sim$ 8, the data points are from \citet{2021AJ....162...47B},
-\citet{2022arXiv220712356D}, \citet{2013MNRAS.432.2696M}, \citet{2020MNRAS.493.2059B}, and \citet{2019ApJ...883...99S}.
-At  $z\sim$ 9, those data are from \citet{Harikane_2022c}, \citet{2022arXiv220712356D}, \citet{2020MNRAS.493.2059B}, \citet{2019ApJ...883...99S}, 
-and \citet{2018ApJ...867..150M}.
-At $z\sim$ $10-13$, we take data from \citet{Harikane_2022c}, \citet{2022arXiv220712356D}, \citet{Harikane_2022b}, \citet{2022arXiv220709434N}, \citet{2018ApJ...867..150M}, 
-and \citet{2016ApJ...819..129O}.
-The fitting forms of the luminosity functions are given by \citet{2022ApJS..259...20H} at $z\simeq 7$, 
-\citet{2020MNRAS.493.2059B} and \citet{2013MNRAS.432.2696M} at $z\simeq 8$, and \citet{Harikane_2022c} at $9\lesssim z\lesssim 13$.
+%\includegraphics[width=160mm]{QLF_rhoz.png}
+\includegraphics[width=80mm]{M0r8_f2QLF.png}
+\caption{
+{\it Left panel}: quasar luminosity functions at $z=6-10$. 
+The solid lines denote modeled QLF produced by the best-fit parameters and the shaded regions present the $1\sigma$ spread. 
+{\it Right panel}: the redshift evolution of the cumulative number density of quasars with $\Muv <-26~{\rm mag}$ in a comoving volume,
+evaluated by the integration of the QLF shown in the left panel.
+The evolutionary trend can be approximated as $n(\Muv<-26~{\rm mag})\propto 10^{k_{L} z}$, where $k_L \simeq -0.96$.
+This result indicates rapid decline of the number of bright quasars toward higher redshifts, consistent with previous observations
+\citep[red data points; see][]{2016ApJ...833..222J, 2019ApJ...884...30W}
 }
-\label{fig:LFs}
-\end{figure*}
-
-%%%%%%%
-%    Table. 2 
-%%%%%%%
-\startlongtable
-\begin{deluxetable*}{lccccccc}%[h!]
-\tablecolumns{2}
-\renewcommand\thetable{2} %! fix indexing
-\tablewidth{0pt} 
-\tablecaption{Detection Number of Quasars Estimated for Future Surveys}
-\tablehead{
-  \colhead{Telescope} & \colhead{ Survey area} & \colhead{Photo. depth} &  \colhead{$N(z\sim 6)$} & \colhead{$N(z\sim 7)$}& \colhead{$N(z\sim 8)$}&  \colhead{$N(z\sim 9)$}&  \colhead{$N(z\sim 10)$}\\
-  \colhead{} & \colhead{(\rm{deg}$^2$)} & \colhead{(AB mag)} & & & & & 
+\label{fig:QLF_rhoz}
+\vspace{5mm}
+\end{figure}
+
+In Fig.~\ref{fig:QLF_rhoz}, we present the quasar number density as a function of redshift for 
+the case of $\fseed =0.1$ (solid) and $0.01$ (dashed).
+Each curve corresponds to the value at each UV magnitude from $\Muv=-27$ mag to $-23$ mag.
+Our theoretical predictions are shown at $z\geq 6$ (thick curves), while observational results are compiled at lower redshifts (thin curves).
+The evolutionary trend can be fitted as $\propto 10^{k_{\rm L}z}$,
+\red{
+where $k_{\rm L}\approx ***$ and $***$ for the brightest and faintest population
+at $z\gtrsim 6$, respectively.
 }
-\startdata
-Wide RST    &  2000 & 27   & 6758 &  1514 &  349 & 85 & 25  \\
-Wide Euclid & 15000 & 24   & 6653  &  708 &   93 & -- & --  \\
-\enddata
-\label{tab:N_detect}
-\tablecomments{
-Based on the 5$\sigma$ point source detection limits, the number of quasars at each redshift are predicted
-with the assumption of the survey volume with $\Delta z =1$ and 100\% completeness.
-}
-\end{deluxetable*}
+Observationally, a rapid decay of the quasar number density toward higher redshifts is found by previous studies
+\citep[e.g.,][]{2001AJ....122.2833F,2013ApJ...768..105M,2016ApJ...833..222J,2019ApJ...884...30W},
+which show $k_{\rm L}= -0.47$ and $-0.72$ from the analysis of quasar samples at $z\simeq 3-5$ and $z\simeq 5-6$, respectively.
+% Recently, a steeper decline of luminous quasar number density toward higher redshifts is proposed by \citet{2019ApJ...884...30W},
+% suggesting $k_{\rm L}=-0.78$ at $6\lesssim z \lesssim 7$.
+The rapid decline toward higher redshifts is characterized by the treatment of episodic natures of BH accretion with a finite value of
+$\tau ~(\simeq 20~{\rm Myr})$, in order to match the statistical properties of high-$z$ quasars.
+We also note that the tendency would be explained by the rarity of massive quasar-host halos at higher redshifts,
+non-constant radiative efficiencies that covert the BH growth rate into the luminosity, or some combination of these effects
+\citep[e.g.,][]{2010ApJ...718..231S}.
+
+%Studies with the assumption of the close correlation of DM halo mass with central BH mass, and a constant Eddington ratio 
+%interprete this rapid decline by the rarity of massive halos toward higher redshifts \citep[e.g.,][]{2010ApJ...718..231S}, 
+%while another entangling factor is the radiative efficiency in converting BH growth rate to luminosity. 
+%In our work, we argue that the episodical BH accretion with bursts and quiescent phases is 
+%important in matching the $z\sim 6$ quasar observations, 
+%and this calls consideration of the more realistic BH-galaxy coevolution in understanding the observable AGN properties.
 
@@
 
-From the BH growth model described in \S~\ref{sec:MF}, we further explore individual BH evolutionary tracks starting from the BH seeds.
+From the BH growth model described in \S~\ref{sec:MF}, we further explore individual BH evolutionary tracks starting from the BH seeding phases.
 % We take $\fseed=$ 0.01 as a fiducial case, where the best-fit parameters for BH growth are 
@@
 We generate a sample of 10$^6$ BHs, whose formation time and mass distribution at birth follow the model described in \S~\ref{sec:seed}. 
-Following the best fit parameters in the case of $\fseed = 0.01$,
+Adopting the best fit parameters in the case of $\fseed = 0.01$,
 for every time interval $\tlife=18.76$ Myr,
@@
 
-We estimate the duty cycle between $z=10$ and $6$ defined as $f_{\rm duty} \equiv \mathcal{N}\tlife/\Delta t_{\rm H}$, 
+First, we estimate the duty cycle between $z=10$ and $6$ defined as $f_{\rm duty} \equiv \mathcal{N}\tlife/\Delta t_{\rm H}$, 
 where $\mathcal{N}$ is the frequency of super-Eddington accretion bursts with $\lambda>1$ and $\Delta t_{\rm H}\simeq 450$ Myr.
@@
 (i.e., $\Delta t_{\rm H} \times f_{\rm duty} \simeq 55$, 69, and 85 Myr), respectively.
-On the other hand, the average duty cycle for the entire BH population is given by $f_{\rm duty}= 0.075$ 
-(see \S~\ref{sec:fitting_result}), which much lower than these massive sub-samples.
+On the other hand, the average duty cycle for the entire BH population is calculated as $f_{\rm duty}= 0.075$,
+adopting this ERDF (see \S~\ref{sec:fitting_result}), and is significantly lower than those massive BH sub-samples.
 Therefore, we suggest that the massive BHs observed in $z\simeq 6$ quasars are biased in a way that
@@
 
-In Fig.~\ref{fig:Mevol}, we show the BH growth tracks that end up with $M_\bullet>10^8~\Msun$ by $z=6$.
-%
 %%%%%%%
@@
 %
-In this sub-sample, we find five BHs heavier than $M=10^9~\Msun$ (highlighted with solid curves),
-among which all of them show $\lambda<1$ at the  $z=6$ snapshot.
+
+In Fig.~\ref{fig:Mevol}, we show the BH growth tracks that end up with $M_\bullet>10^8~\Msun$ by $z=6$ (grey thin curves).
+In this sub-sample, we find five BHs heavier than $M=10^9~\Msun$ (highlighted with colored thick curves),
+all of which indicate $\lambda \lesssim 1$ at the  $z=6$ snapshot.
 % among which five BHs show $\lambda<1$ in the snapshots at $z=6$.
@@
 % This fact indicates short durations of the super-Eddington accretion mode.
-For comparison, we show the mass growth tracks assuming constant Eddington accretion (i.e., $\lambda=1$),
+For comparison, we show the mass growth tracks assuming continuous Eddington accretion (i.e., $\lambda=1$),
 where the extrapolated seed mass is $\Mbh \lesssim 10^2~\Msun$ at $z\sim 30$.
 %Both treatments of the constant $\lambda$ lead to BH seed masses extrapolation that deviate from the initial seeds we plant. 
-Therefore, one may postulate that short durations of super-Eddington accretion lead to the exsitence of the massive BHs.
-Based on the BH seeds and growth model we develop,
+\red{Therefore, one may postulate that short durations of super-Eddington accretion lead to the existence of the massive BHs. KI: what do you mean?}
+\blue{It clearly indicates that super-Eddington accretion episodes are required to the existence of the massive BHs}
+Based on the BH seeding and growth model we develop,
 we reiterate that multiple accretion episodes with different values of $\lambda$ should be taken into account 
@@
 % \red{KI: still not sure what we discuss below... among the 7 BHs, is anyone consistent with Feige's BH?}
-In \citet{2021ApJ...907L...1W}, they discover the currently known most distant quasar at $z=7.642$, 
-tracing back with Eddington accretion, the central BH reaches the $10^{4-6}~\Msun$ seed mass range at $z=$ 30. 
-However in our best-fit model, we observe that to trace back BH mass and understand their seeding scenarios, 
-taking constant Eddington ratio derived from high-$z$ observation or assuming $\lambda=1$ are both unrealistic. 
-Therefore we raise a caveat that under these assumptions the seed mass achieved may be unreliable. 
-Instead we should take into account the episodical accretion nature of quasars, 
-including both bursts of accretion and quiescent phases.
-Among the five supermassive BH growth tracks,
-we find one matching this currently known most distant quasar, 
-with $M_\bullet \simeq 1.7\times 10^9~\Msun$ and $\lambda \simeq 0.6$ at $z=7.6$ (shown with red curve).
-Starting from $z\sim 33$ with $M_{\rm seed} \sim 2\times 10^5~\Msun$,
-this overmassive growth history is realized by the combination of rare halo environments initilizing a heavy seed, 
-and several super-Eddington accretion bursts.
+\citet{2021ApJ...907L...1W} discovered the currently known most distant quasar at $z=7.642$ (red diamond in Fig.~\ref{fig:Mevol}).
+Assuming continuous Eddington accretion, the extrapolated BH is as massive as $10^{4-6}~\Msun$ at $z= 30$. 
+%However in our best-fit model, we observe that to trace back BH mass and understand their seeding scenarios, 
+%taking constant Eddington ratio derived from high-$z$ observation or assuming $\lambda=1$ are both unrealistic. 
+%Therefore we raise a caveat that under these assumptions the seed mass achieved may be unreliable. 
+Our best-fit model naturally explains the existence of the most extreme BH,
+taking into account the episodical accretion nature of quasars,
+%(note extrapolation with the observed $\lambda$ requires an unrealistically high seed mass). 
+%including both bursts of accretion and quiescent phases.
+%Among the five supermassive BH growth tracks,
+%we find one matching this currently known most distant quasar, 
+and the consistent growth track among the sub-sample is indicated with the red solid curve 
+(with $M_\bullet \simeq 1.7\times 10^9~\Msun$ and $\lambda \simeq 0.6$ at $z=7.6$).
+This overmassive growth history is realized by the combination of rare halo environments planting a seed BH 
+with $\sim 2\times 10^5~\Msun$ at $z\sim 30$ and several (modest) super-Eddington accretion bursts.
 
@@
 This unavoidable bias of quasar surveys can be corrected by taking into account the survey completeness;
-however, it is still challenging to constrain the low-mass end of the BHMF and low $\lambda$ end of the ERDF
-that the surveys are not sensitive to.
+however, it is still challenging to constrain the low-mass end of the BHMF and low-$\lambda$ end of the ERDF.
+%that the surveys are not sensitive to.
 In this section, we examine the effect of flux-limited quasar surveys on the observed ERDF, 
@@
 and $\Lbol \geq L_{46}$ (green).
-For visible comparison, we elevate the observed histograms by a factor of 5 and 30
+For visual comparison, we elevate the observed histograms by a factor of 5 and 30
 for the luminosity limits with $L_{45}$ and $L_{46}$, respectively.
@@
 \section{Summary}
-In this paper, we propose a theoretical model for the redshift-dependent QLF and BHMF at $z\gtrsim 6$.
-We apply the seed BH mass function from PopIII remnants ranging in $10^{2-5}~\Msun$.
-We assume that the early BH population experiences multiple accretion bursts, in each of which constant Eddington ratio
+In this paper, we propose a theoretical model for the redshift-dependent QLF and BHMF at $z\gtrsim 6$,
+applying the mass distribution function of seed BHs over $10^2 \lesssim M_\bullet/\Msun \lesssim 10^{5}$
+that originate from massive primordial stars formed in the overdense region of the universe.
+In our accretion model, those early BH populations are assumed to experience multiple accretion bursts, in each of which a constant Eddington ratio
 is assigned following a Schechter distribution function.
-Then we conduct the MCMC fitting to optimize the BH growth parameters
-so that the observed BHMF and QLF at $z\simeq 6$ are simultaneously reproduced. Our major findings are summarized as follows.
+We further conduct the MCMC fitting to optimize the BH growth parameters
+so that the observed QLF and BHMF at $z\simeq 6$ are simultaneously reproduced. 
+Our major findings are summarized as follows.
+
 \begin{itemize}
 \item
-Our model favors the BH Eddington ratio $\lambda$ following a Schechter distribution function to reproduce the QLF and BHMF at $z\simeq 6$.
-The distribution shape is motivated by low-$z$ AGN observations.
-The characteristic Eddington ratio $\lambda_0$ and the power law slope $\alpha$ at low Eddington ratio are best-fitted by
+Our best-fit model to reproduce the QLF and BHMF at $z\simeq 6$ suggests that each accretion burst
+lasts $\tau \simeq 20-30$ Myr, which is a fraction of the $e$-folding time for the exponential BH mass growth.
+%Our model favors the BH Eddington ratio $\lambda$ following a Schechter distribution function to reproduce the QLF and BHMF at $z\simeq 6$.
+%The distribution shape is motivated by low-$z$ AGN observations.
+The Schechter shape of the ERDF is characterized with two parameters of 
+%The characteristic Eddington ratio $\lambda_0$ and the power law slope $\alpha$ at low Eddington ratio are best-fitted by
 $(\lambda_0, \alpha)=(0.89,0.12)$ and $(0.87,0.20)$ for the BH seeding fraction of $\fseed = 0.01$ and $0.1$, respectively.
-The parameter $\tau$ characterizing the duration of each accretion burst is featured by our model,
-with typical values $\tau \simeq 20-30$ Myr.
-For longer (and shorter) burst durations, the number of BHs at the high mass end is over(-under) produced.
-Therefore, multiple accretion bursts with variable Eddington ratios enable the early BH population to grow and shine,
-consistent with the observed distribution functions.
+%The parameter $\tau$ characterizing the duration of each accretion burst is featured by our model,
+%with typical values $\tau \simeq 20-30$ Myr.
+%For longer (and shorter) burst durations, the number of BHs at the high mass end is over(-under) produced.
+Multiple accretion bursts with variable Eddington ratios enable the early BH population to grow and shine,
+in a consistent way with the observed QLF and BHMF.
+
 \item
 Using the best-fit model parameters, we construct the redshift-dependent QLF and BHMF at $6\leq z \leq 10$.
-The two functions suggest a rapid decay of the number and mass density of massive BHs and luminous quasars in a cosmic volume
+\red{(to be revised) The two functions suggest a rapid decay of the number and mass density of massive BHs and luminous quasars in a cosmic volume
 toward higher redshifts as $\propto 10^{-k_i z}$, where $k_{\rm M}\simeq -0.68$ for the BH mass and $k_{\rm L}=-0.96$ for the quasar number.
 The predicted value of the decay slope $k_{\rm L}$ is consistent with that estimated by previous observations for $z\simeq 6-7$ quasars
-but tends to be slightly steeper at higher redshifts.
+but tends to be slightly steeper at higher redshifts. }
+
 \item
@@
 
+\appendix
+%%%%%%%
+%    Fig. 
+%%%%%%%
+\begin{figure*}
+\centering
+\includegraphics[width=160mm]{tau.png}
+\caption{
+The BH mass function (left) and quasar luminosity function (right) at $z=$ 6 in the case of $\fseed=0.01$, 
+with different values of $\tlife=$ 10, 18 (the best-fit value), and 50 Myr, respectively.
+Note that the other parameters are fixed to the best-fit values. 
+The $z=6$ BHMF (\citetalias{2010AJ....140..546W}) and QLF (\citetalias{2018ApJ...869..150M}) 
+are overlaid with the blue curve and data points.
+With shorter (longer) timescales of each accretion episode $\tlife$, the number of BHs at the high mass end and bright end is under(over)-produced.
+%Right panel: QLF at $z=$ 6 calculated with the same parameters as in the left panel.
+%The overlaid blue dots are from the \citetalias{2018ApJ...869..150M} $z\sim$ 6 quasar observation. 
+%With $\tlife$ values different from the best-fit value, the consequent QLF show 
+%similar trends of deviation from observation as in the BHMF curves.
+Multiple accretion bursts in each duration of $\tau \simeq 20$ Myr best produce the observations,
+which is nearly half of the $e$-folding time of the exponential BH mass growth.
+}
+\label{fig:tau}
+%\vspace{4mm}
+\end{figure*}
+
+\vspace{2mm}
+\section{Model dependence}\label{sec:modep}
+As described in \S~\ref{sec:model}, we introduce the parameter $\tau$ as a typical timescale
+for individual durations of quasar accretion activity.
+Specifically, we assign an Eddington ratio $\lambda$ following the ERDF for all BHs in each cycle
+with a time duration of $\tau$.
+Variable accretion episodes in every cycle essentially modify the effective ERDF in the whole BH growth history,
+because multiple sampling of $\lambda$ reduces the possibility of a BH growing with $\lambda \gtrsim \lambda_0$
+compared to that with a single sampling of $\lambda$.
+%However at any time during growth, the ERDF of the BH population remains the same as at $z\sim$ 6,
+%therefore we ensure treating all cosmic time equally.
+In what follows, we demonstrate the role of $\tlife$ in shaping the BHMF evolution and the consequent QLF.
+% tau极端小，则非常小的lambda，不能解释 （且delta func？ 有必要说或是放在后面讨论？）
+
+In the left panel of Fig.~\ref{fig:tau}, we present the BHMF at $z=6$ for three different values of $\tlife=10$, $18$, and $50$ Myr,
+but keeping the other parameters to the best-fit values ($\lambda_0=0.87$ and $\alpha=0.20$) for the case with $\fseed=0.01$.
+We note that $\tlife \approx$ 18 Myr is the best-fit value reproducing the BHMF consistent with that of \citetalias{2010AJ....140..546W}.
+%the other two cases demonstrate the sensitivity of the $\tlife$ value in producing the bulk of massive BHs
+%and the slope in the high mass tail.
+For $\tlife=10$ Myr, the frequency of Eddington ratio assignment increases by a factor of two until $z=6$.
+%to $\sim$ 80 from $\sim$ 40 with the best-fit $\tlife$ value.
+Therefore, continuous and efficient growth of BHs with $\lambda \gtrsim \lambda_0$ is less likely to occur,
+%high Eddington ratio accretion along the growth is lower,
+suppressing the formation of BHs heavier than $M_\bullet \simeq 10^8~\Msun$.
+Moreover, if a high Eddington ratio is given with a certain but low probability, the BH mass hardly increases
+within $\tlife=10$ Myr, which is $\simeq 20\%$ of the $e$-folding timescale.
+On the other hand, for $\tlife=$ 50 Myr, there is a non-negligible probability that
+% $\sim$ 16 times of Eddington ratio assignment,
+more BHs experience high accretion rates with $\lambda\gtrsim \lambda_0$ through their assembly history.
+%high values of $\lambda\gtrsim \lambda_0$ is non-negligibly realized in the BHMF evolution.
+Therefore, the high mass end of the BHMF is further enhanced and those massive populations are substantially
+overproduced compared to the observed abundance.
+%in the high mass end of BHMF at $z=$ 6, the BH population is significantly overproduced than the constraints from observation.
+
+The QLF at $z=6$ is shown in the right panel of Fig.~\ref{fig:tau}.
+%In the conversion from BHMF to QLF, the ERDF is the same for different $\tlife$ values,
+%following the $P(\lambda)$ in Eq.~(\ref{eq:Pl}) with $\lambda_0=0.87$ and $\alpha=0.20$.
+Overall, the dependence of the QLF on the choice of $\tau$ shows the same trend as in the BHMF,
+%the deviation from the observed QLF of \citetalias{2018ApJ...869..150M} shows similar trends as in the BHMF.
+i.e., higher (lower) $\tlife$ values lead to under(over)-production of the luminous quasar population.
+The best-fit value of $\tlife (\simeq 18$ Myr) favors a moderate fraction of $t_{\rm S}$.
+This result demonstrates the importance of early BHs experiencing multiple accretion episodes to 
+reproduce the observed distributions of BH mass and luminosity of quasars at $z\sim$ 6.
+In \S\ref{sec:evol}, we apply this episodic accretion model to individual growth pathways of high-$z$ quasars
+and demonstrate that normal seeding mechanisms can explain the existence of massive BHs with low luminosity
+observed at $z\simeq 6-7$.
+
 \clearpage

### 2022-09-14 ms.tex
version0914; my revised version

@@
 with the Mg~{\sc ii} single-epoch method and bring insights of the mass distribution
-\citep[e.g.,][]{2007AJ....134.1150J,2007ApJ...669...32K,2010AJ....140..546W,2018Natur.553..473B,2019ApJ...880...77O,2019ApJ...873...35S}. 
+(e.g., \citealt{2007AJ....134.1150J,2007ApJ...669...32K};
+\citealt{2010AJ....140..546W}, hereafter \citetalias{2010AJ....140..546W};
+\citealt{2018Natur.553..473B,2019ApJ...880...77O,2019ApJ...873...35S}). 
 However, extrapolation of the Soltan-Paczy{\'n}ski argument toward higher redshifts beyond $z\sim$ 6 is limited because of the current difficulty of
@@
 
-\red{(to be revised)
-This paper is organized as follows. Firstly, in \S \ref{sec:method} we describe the semi-analytical BH seeding procedure, 
-the parameterized BH growth and how we reproduce the modeled QLF and BHMF dataset at $z\sim$ 6 using these ingredients. 
-In \S \ref{sec:result} we present the fitting of model parameters constrained by quasar observations. 
-We then summarize our findings in \S \ref{sec:discussion} and discuss the potential applications on exploring the high-$z$ universe.
+\blue{
+This paper is organized as follows. Firstly, in \S~\ref{sec:method} we describe the semi-analytical BH seeding procedure, 
+the parameterized BH growth model and how we reproduce the QLF and BHMF dataset at $z\sim$ 6 using these ingredients. 
+In \S~\ref{sec:fitting_result} we present the fitting of model parameters constrained by quasar observations.
+In \S~\ref{sec:cosm} we discuss the cosmological evolution of BH mass and quasar luminosity functions 
+indicated by our best-fit models, as well as the potential detection of these BHs in their early growth.
+In \S~\ref{sec:discussion} we present the BH growth tracks and statistical properties along the $z\sim 6$ SMBH growth histories.
+We then summarize our findings in \S~\ref{sec:sum} and discuss the potential applications of quasar observations on exploring the high-$z$ universe.
 }
@@
 \centering
-\includegraphics[width=150mm]{scheme.png}
+\includegraphics[width=150mm]{scheme1.png}
 \caption{
 Schematical demonstration of the procedure to calculate the evolution of BH mass distribution 
-between checkpoints time $t_0$ to $t_0+\tau$. 
+between checkpoints time $T_0$ to $T_0+\tau$. 
 The probability of a BH with mass $M_0$ grow to $M$ after $\Delta t=\tau$ is drew from the 
@@
 For a newly formed seed BH $M_{\rm i}$, the probability distribution function of BH mass is a delta function, 
-and the growth time is $t_0+\tau-t_{\rm i}$.
+and the growth time is $T_0+\tau-t_{\rm i}$.
 Thus the evolution of BH mass distribution is reshaped iteratively 
-plus taking account of the newly formed seeds if any.
+plus taking account of the newly formed seeds if there are any.
 }
@@
 \begin{equation}
+\label{eq:f_M}
 f(\Mbh) = \frac{2}{1+\left(\Mbh /M_{\bullet,c} \right)^\delta}, 
@@
 Since the value has been poorly constrained both by theoretical and observational studies, we treat it as a free parameter.
-% wli avoid fseed=1
-We take three different values of $\fseed = 1$, $0.1$, and $0.01$ and explore the dependence on the best-fit QLF and BHMF.
-Note that the seed mass function shown in Fig.~\ref{fig:seedmf} is given with $\fseed = 1$.
+We take three different values of $\fseed = 1$, $0.1$, and $0.01$, and explore its effect on producing the QLF and BHMF.
+\blue{
+With analysis on the fitting results for $\fseed = 1$ and $\fseed = 0.1$,
+we find that the best-fit parameters in the two cases are overall similar (see Table.~\ref{tab:best_fits}). 
+For simplicity, we neglect presenting the discussion on the $\fseed=1$ case hereafter.
+}
+Note that for demonstration purposes, the seed mass function shown in Fig.~\ref{fig:seedmf} is given with $\fseed = 1$.
 
@@
 %every by evolves iteratively during each cycle,together with the seeds newly formed in between.
-For a given mass distribution function $\D P/\D  M_{\bullet, 0}$ at a checkpoint of $t=t_0$, 
-we give its evolution at $t=t_0+\Delta t$ as
+For a given mass distribution function $\D P/\D  M_{\bullet, 0}$ at a checkpoint of $t=T_0$, 
+we give its evolution at $t=T_0+\Delta t$ as
 %%%%%%%
@@
 % is set for the BH mass distribution iteration from the latest checkpoint, 
-For a seed BH formed during this cycle (i.e., $t_0\leq t_k < t_0+\tlife$), 
-we evolve $\D P^{\rm seed}_k/\D \Mbh$ by setting $\Delta t = t_0+\tlife -t_k$ and add it to the mass distribution 
-of the existing BHs at $t=t_0+\tlife$.
+For a seed BH formed during this cycle (i.e., $T_0\leq t_k < T_0+\tlife$), 
+we evolve $\D P^{\rm seed}_k/\D \Mbh$ by setting $\Delta t = T_0+\tlife -t_k$ and add it to the mass distribution 
+of the existing BHs at $t=T_0+\tlife$.
 %adopt $\Delta t = t-t_k$, and $\D P^{\rm seed}_{\rm i}/ \D \Mbh$ as the initial mass distribution.
@@
 following \citet{2014ApJ...786..104U}.
-An alternative fitting form of $\fobsc$ based on their X-ray AGN sample with additional optical obscuration classification 
-is proposed by \citet{2014MNRAS.437.3550M} as
-%
-\begin{equation*}
-  \fobsc = 0.56 + \frac{1}{\pi}~ \text{arctan} \left[ \frac{43.89 - \log (\Lbol/L_\odot)}{0.46}\right].
-\end{equation*}
-%
-We also conduct the parameter fitting with this prescription and discuss the sensitivity of our results to 
-the choice of $\fobsc$ in the Appendix.
-\red{KI: add appendix}
+% An alternative fitting form of $\fobsc$ based on their X-ray AGN sample with additional optical obscuration classification 
+% is proposed by \citet{2014MNRAS.437.3550M} as
+% %
+% \begin{equation*}
+%   \fobsc = 0.56 + \frac{1}{\pi}~ \text{arctan} \left[ \frac{43.89 - \log (\Lbol/L_\odot)}{0.46}\right].
+% \end{equation*}
+% %
+% We also conduct the parameter fitting with this prescription and discuss the sensitivity of our results to 
+% the choice of $\fobsc$ in the Appendix.
+% \red{KI: add appendix}
 
@@
 \centering
-\includegraphics[width=180mm]{contour.pdf}
+\includegraphics[width=180mm]{contour.png} % contour.pdf
 \caption{
@@
 The distribution of three parameters ($\tau$, $\lambda_0$, and $\alpha$) show single peaks,
-meaning the convergence of those parameters.
+displaying the convergence of those parameters.
 The distribution of $\log\delta$ is relatively broader but suggests that the value of $\delta$
@@
 The best-fit values of the first four parameters are calculated by the MCMC method, while $\fseed$ is fixed to a single value.
-In what follows, we describe the results for $\fseed = 0.1$ and $0.01$ (see Appendix for the case with $\fseed =1.0$).
-\red{KI: add appendix}
+% In what follows, we describe the results for $\fseed = 0.1$ and $0.01$ (see Appendix for the case with $\fseed =1.0$).
 
@@
 % \citep[e.g.,][Onoue et al. in preparation]{2010AJ....140..546W}.
-after luminosity bias correction \citep[e.g.,][]{2010AJ....140..546W}.
+after luminosity bias correction (e.g., \citetalias{2010AJ....140..546W}).
 % It is worth noting that, observationally the high-$z$ ERDF is fitted by a log-normal function. 
@@
 % 1. data: observational MF LF; describe quadratic error in Willott 2010
-The observed BHMF data is taken from \citet{2010AJ....140..546W} (hereafter \citetalias{2010AJ....140..546W}), where 
+The observed BHMF data is taken from \citetalias{2010AJ....140..546W}, where 
 the virial BH mass measurements for 17 bright quasars at $z\simeq $ 6 are used.
@@
 
-\red{KI: we need to explain why the peak of the 1D posterior distribution does not correspond to the best-fit case.
-I think the peak value is not necessarily the same as the best-fit value. 
-Also, we need to list the best-fit parameters somewhere in the text.}
-
-In Fig.~\ref{fig:contour}, we visualize the MCMC fitting results for each parameter in two-dimensional 
+% \red{KI: we need to explain why the peak of the 1D posterior distribution does not correspond to the best-fit case.
+% I think the peak value is not necessarily the same as the best-fit value. 
+% Also, we need to list the best-fit parameters somewhere in the text.}
+
+%%%%%%%
+%    Table. 1
+%%%%%%%
+\begin{deluxetable}{l|ccccccc}%[t!]
+\tablecolumns{1}
+\renewcommand\thetable{1} %! fix indexing
+\tablewidth{0pt} 
+\tablecaption{Best-fit Parameters \label{tab:best_fits}} %!!!!
+\tablehead{
+  \colhead{$\fseed$}  & \colhead{1} & \colhead{0.1} &  \colhead{0.01}
+}
+\startdata
+% $\fseed$    &      1 &      0.1  &  0.01  \\
+% \hline \hline
+$\tau$      &  23.13 &   20.07   & 18.76  \\
+$\delta$    &  0.001 &   0.001   & 0.055  \\
+$\lambda_0$ &  0.96  &   0.89    &  0.87  \\    
+$\alpha$    & -0.06  & 0.12   &  0.20  \\
+\enddata
+% \tablecomments{
+% The best-fit parameters optimized by MCMC sampling for the cases of $\fseed=1$, 0.1, and 0.01.
+% }
+\end{deluxetable}
+
+\blue{
+In the following, we discuss the MCMC fitting results and compare the reproduced BHMF and QLF with observations.
+In Fig.~\ref{fig:contour}, we visualize the fitting results for each parameter in two-dimensional 
 posterior distribution for the case of $\fseed= 0.1$ (left) and $0.01$ (right), respectively.
-The three vertical lines on each one-dimensional posterior distribution present the peak and the values
-with $1\sigma$ scatter.
-The result for the $\fseed=1$ case is discussed in the Appendix.
-\red{KI: add appendix}
-
-For both cases, the best-fit solution consistently shows a small value of $\delta < 0.01$. \red{KI: but, $\delta=0.055$ is used later...}
+The three vertical dashed lines in the one-dimensional distribution of each parameter
+correspond to 16, 50, and 84 percentiles, respectively.
+The best-fit values shown in red thick lines are tabulated in Table.~\ref{tab:best_fits}.
+Note that the 50 percentile does not overlap the peak of an asymmetric distribution.
+% wli : 1\sigma definition here?
+We define the $1\sigma$ scatter of a value (e.g., $\Phi_{M_\bullet}$) as the standard deviation of it calculated
+from randomly selected parameters from the sampling.
+% instead of the 16 and 84 percentiles here.
+}
+
+For both cases, the best-fit solution consistently shows a small value of $\delta < 0.1$.
 %, which is sufficiently small and should be marginalized out. 
-This suggests that a nearly exponential BH growth manner is favored in our model assumption. 
+This result favors the nearly exponential BH growth model with minor mass dependence (Eq.~\ref{eq:mdot},~\ref{eq:f_M}).
 % In other words, on average the BH growth can be described as exponential, 
@@
 \caption{
-The BH mass function at $z=6$ with the best-fit parameters (purple curve) and the $1\sigma$ spread for the cases with $\fseed=0.1$ (left) and $0.01$ (right). 
+The BH mass function at $z=6$ with the best-fit parameters (black curve) and the $1\sigma$ spread (shaded region) for the cases with $\fseed=0.1$ (left) and $0.01$ (right). 
 For comparison, the BHMF inferred by \citetalias{2010AJ....140..546W} is overlaid (blue curve and shaded region).
@@
 %%%%%%%
-%    Fig. 
+%    Fig. 6
 %%%%%%%
@@
 \caption{
-\if0
-{\it Left panel}: BH mass functions at $z=6-10$. 
-The solid lines denote modeled BHMF produced by the best-fit parameters 
-and the shaded regions present the $1\sigma$ spread. 
-{\it Right panel}: the redshift evolution of the cumulative mass density of BHs with $\Mbh \geq 10^7~\Msun$ in a comoving volume, 
+{\it Left panel}: BH mass functions predicted by the best-fit models at $z=6-10$,
+including a fraction of $\fseed$ seeds evolving by our model assumption and the remaining ($1-\fseed$) fraction with no subsequent growth.
+The solid (dashed) lines denote the cases with $\fseed=0.1$ (0.01).
+{\it Right panel}: the cumulative mass density evolution for BHs in different mass ranges in a comoving volume, 
 evaluated by the integration of the BHMF shown in the left panel.
-The evolutionary trend can be approximated as $\rho_\bullet (z) \propto 10^{k_M z}$, where $k_M\simeq -0.68$.
-\fi
+The dashed-dotted line and open square symbol show the results from \citet{2022MNRAS.513..670N}.
+The upper bound of accreted BH mass density from \citet{2013ApJ...778..130T} is denoted by red triangles.
+% The evolutionary trend can be approximated as $\rho_\bullet (z) \propto 10^{k_M z}$, where $k_M\simeq -0.68$.
 }
@@
 %%%%%%%
-%\startlongtable
 \begin{deluxetable*}{lccccccc}%[t!]
 \tablecolumns{1}
-\renewcommand\thetable{1} %! fix indexing
+\renewcommand\thetable{2} %! fix indexing
 \tablewidth{0pt} 
@@
 \startdata
-Wide RST    &  2000 & 27   & 6758 &  1514 &  349 & 85 & 25  \\
-Wide Euclid & 15000 & 24   & 6653  &  708 &   93 & -- & --  \\
+Wide RST    &  2000  & $YJH$ 27   & $6759_{-3185}^{+15} $ &  $1514_{-558}^{+169}$ &  $349_{-131}^{53}$ & $85_{-48}^{+23}$ & $25^{+12}_{-15}$  \\
+Wide Euclid & 15000  & $YJH$ 24   & $6654^{+95}_{-2282}$  &  $708^{+213}_{-237}$ &   $93^{+66}_{-56}$ & $14^{+32}_{-27}$ & --  \\
 \enddata
@@
 \tablecomments{
-Based on the 5$\sigma$ point source detection limits, the number of quasars at each redshift are predicted
+Based on the 5$\sigma$ point source detection limits of the $YJH$ bands in the two surveys,
+the number of quasars at each redshift are predicted
 with the assumption of the survey volume with $\Delta z =1$ and 100\% completeness.
@@
 For comparison, we overlay the BH mass density evolution with $10^6<M_{\bullet}<10^8$, and $M_\bullet>10^8~\Msun$
-obtained from the cosmological simulations in \citet{2022MNRAS.513..670N} (open square symbols).
+obtained from the cosmological simulations in \citet{2022MNRAS.513..670N} (dashed-dotted line and open square symbols).
 At $z\lesssim 7$, our results are in overall good agreement with those simulation results.
@@
 %%%%%%%
-%    Fig. 9
+%    Fig. 7
 %%%%%%%
@@
 \centering
-\includegraphics[width=85mm]{M0r8_f2linLF_spreadz7_KI.pdf}\hspace{5mm}
-\includegraphics[width=85mm]{M0r8_f2linLF_spreadz8_KI.pdf}\\\vspace{5mm}
-\includegraphics[width=85mm]{M0r8_f2linLF_spreadz9_KI.pdf}\hspace{5mm}
-\includegraphics[width=85mm]{M0r8_f2linLF_spreadz10_KI.pdf}
+\includegraphics[width=85mm]{LF_spreadz7.pdf}%\hspace{5mm}
+\includegraphics[width=85mm]{LF_spreadz8.pdf}\\%\vspace{5mm}
+\includegraphics[width=85mm]{LF_spreadz9.pdf}%\hspace{5mm}
+\includegraphics[width=85mm]{LF_spreadz10.pdf}
 \caption{Predicted quasar luminosity functions and depths and volumes of upcoming surveys.
@@
 \if0
-Next, we show our prediction of $z=6-10$ unobscured QLFs taken from the BH growth model in the left panel of Fig.~\ref{fig:QLF_rhoz}.
+Next, we show our prediction of $z=6-10$ unobscured QLFs taken from the BH growth model in the left panel of Fig.~\ref{fig:QLFmag_z}.
 Similar to the BHMF, for all the redshift range, the shape of the QLF is well approximated with a double power-law function.
@@
 % Also, you could compare your results with Aaron Yung's results.}
-In the right panle of Fig.~\ref{fig:QLF_rhoz}, we present the number density of luminous quasars with $\Muv <-26~{\rm mag}$ as a function of redshift.
+In the right panle of Fig.~\ref{fig:QLFmag_z}, we present the number density of luminous quasars with $\Muv <-26~{\rm mag}$ as a function of redshift.
 The evolutionary trend can be fitted as $\propto 10^{k_{\rm L}z}$, where $k_{\rm L}\approx -0.97$.
@@
 In Fig.~\ref{fig:LFs}, we divide the cosmological QLF evolution into four different epochs; (a) $z\simeq 7$, (b) $z\simeq 8$, (c) $z\simeq 9$, and (d) $z\simeq 10-13$.
-The black solid and dashed curves present the QLF for the unobscured population (i.e., type-I AGNs, same as those in Fig.~\ref{fig:QLF_rhoz})
+The black solid and dashed curves present the QLF for the unobscured population (i.e., type-I AGNs, same as those in Fig.~\ref{fig:QLFmag_z})
 and the whole population (i.e., type-I and type-II AGNs).
@@
 after subtracting galaxy contaminants.
+\blue{
+Studies that take into account contamination from MLT dwarfs and compact early-type galaxies and quasar selction method
+have confirmed the capability of these surveys in searching high-$z$ quasars \citep{2019A&A...631A..85E,2019BAAS...51c.121F}.
+With the simplified assumption of $100\%$ selection function against contaminants,
+our predicted yield of high-$z$ quasars for the Euclid wide survey is a few times higher than that by \citet{2019A&A...631A..85E}.
+Therefore, our estimation should represent an upper bound of the potentially detectable quasar population.
+}
 
@@
 %%%%%%%
-%    Fig. 
+%    Fig. 8
 %%%%%%%
@@
 %\includegraphics[width=160mm]{QLF_rhoz.png}
-\includegraphics[width=80mm]{M0r8_f2QLF.png}
+\includegraphics[width=80mm]{QLFmag_z.pdf}
 \caption{
-{\it Left panel}: quasar luminosity functions at $z=6-10$. 
-The solid lines denote modeled QLF produced by the best-fit parameters and the shaded regions present the $1\sigma$ spread. 
-{\it Right panel}: the redshift evolution of the cumulative number density of quasars with $\Muv <-26~{\rm mag}$ in a comoving volume,
-evaluated by the integration of the QLF shown in the left panel.
-The evolutionary trend can be approximated as $n(\Muv<-26~{\rm mag})\propto 10^{k_{L} z}$, where $k_L \simeq -0.96$.
-This result indicates rapid decline of the number of bright quasars toward higher redshifts, consistent with previous observations
-\citep[red data points; see][]{2016ApJ...833..222J, 2019ApJ...884...30W}
-}
-\label{fig:QLF_rhoz}
+Evolution of quasar luminosity functions at different UV magnitudes.
+The theoretical prediction from $z=6$ to $10$ for the cases of $\fseed=0.1$ and 0.01 are denoted by solid and dashed lines, respectively.
+From theoretical models, the slope is estimated as $k_\mathrm{L} \simeq -0.91$ and $-0.62$ for quasars at $\Muv=-27$ and $-23$ mag, respectively.
+The observational data at lower redshifts $z\sim 0-6$ are from the Subaru HSC results \citep{2018PASJ...70S..34A,2018ApJ...869..150M,2020ApJ...904...89N},
+SDSS \citep{2006AJ....131.2766R,2013ApJ...768..105M},
+the 2dFSDSS LRG and Quasar Survey (2SLAQ; \citealt{2009MNRAS.399.1755C}),
+and the Spitzer Wide-area Infrared Extragalactic Legacy Survey (SWIRE; \citealt{2008ApJ...675...49S}).
+}
+\label{fig:QLFmag_z}
 \vspace{5mm}
@@
 
-In Fig.~\ref{fig:QLF_rhoz}, we present the quasar number density as a function of redshift for 
+In Fig.~\ref{fig:QLFmag_z}, we present the quasar number density as a function of redshift for 
 the case of $\fseed =0.1$ (solid) and $0.01$ (dashed).
-Each curve corresponds to the value at each UV magnitude from $\Muv=-27$ mag to $-23$ mag.
-Our theoretical predictions are shown at $z\geq 6$ (thick curves), while observational results are compiled at lower redshifts (thin curves).
+Each curve corresponds to the value at a UV magnitude from $\Muv=-27$ mag to $-23$ mag.
+Our theoretical predictions are shown at $z\geq 6$ (thick curves),
+while observational results summarized in \cite{2020ApJ...904...89N} are compiled at lower redshifts (thin curves).
 The evolutionary trend can be fitted as $\propto 10^{k_{\rm L}z}$,
-\red{
-where $k_{\rm L}\approx ***$ and $***$ for the brightest and faintest population
+\blue{
+where $k_{\rm L}\approx -0.91$ and $-0.62$ for the brightest and faintest population
 at $z\gtrsim 6$, respectively.
-}
-Observationally, a rapid decay of the quasar number density toward higher redshifts is found by previous studies
+Specially for $\Muv=-26$ mag, our models predict $k_\mathrm{L} \simeq -0.84$.
+}
+Observationally, a rapid decay of luminous quasar (with $\Muv<-26$ mag) number density toward higher redshifts is found by previous studies
 \citep[e.g.,][]{2001AJ....122.2833F,2013ApJ...768..105M,2016ApJ...833..222J,2019ApJ...884...30W},
@@
 % suggesting $k_{\rm L}=-0.78$ at $6\lesssim z \lesssim 7$.
-The rapid decline toward higher redshifts is characterized by the treatment of episodic natures of BH accretion with a finite value of
+The rapid decline toward higher redshifts shows overall agreement with our model results.
+Our model is characterized by the episodic natures of BH accretion with a finite value of
 $\tau ~(\simeq 20~{\rm Myr})$, in order to match the statistical properties of high-$z$ quasars.
@@
 %%%%%%%
-%    Fig. 10
+%    Fig. 9
 %%%%%%%
@@
 %Both treatments of the constant $\lambda$ lead to BH seed masses extrapolation that deviate from the initial seeds we plant. 
-\red{Therefore, one may postulate that short durations of super-Eddington accretion lead to the existence of the massive BHs. KI: what do you mean?}
-\blue{It clearly indicates that super-Eddington accretion episodes are required to the existence of the massive BHs}
+% \red{Therefore, one may postulate that short durations of super-Eddington accretion lead to the existence of the massive BHs. KI: what do you mean?}
+% \blue{It indicates that super-Eddington accretion episodes are required to explain the existence of the massive BHs.}
 Based on the BH seeding and growth model we develop,
@@
 instead of assuming one single number of the Eddington ratio.
+
+\blue{
+Moreover, some individual quasar observations give exceptionally small proximity zone sizes,
+indicating short lifetime of their luminous phase $t_{\rm Q} \lesssim 10^4$ yr.
+The short quasar lifetime may be due to the young age of quasars ionizing the surrounding IGM \citep[e.g.,][]{2020ApJ...903...60I,2021ApJ...917...38E}.
+Our episodic quasar growth model agrees with this argument,
+besides alleviates the growth tension of SMBHs by episodic accretion bursts.
+In other words, the lifetime of luminous quasar phase is the cumulative time of accreting activity in the current episode.
+}
 
@@
 %%%%%%%
-%    Fig. 11
+%    Fig. 10
 %%%%%%%
@@
 \section{Summary}
+\label{sec:sum}
 In this paper, we propose a theoretical model for the redshift-dependent QLF and BHMF at $z\gtrsim 6$,
@@
 Using the best-fit model parameters, we construct the redshift-dependent QLF and BHMF at $6\leq z \leq 10$.
-\red{(to be revised) The two functions suggest a rapid decay of the number and mass density of massive BHs and luminous quasars in a cosmic volume
-toward higher redshifts as $\propto 10^{-k_i z}$, where $k_{\rm M}\simeq -0.68$ for the BH mass and $k_{\rm L}=-0.96$ for the quasar number.
-The predicted value of the decay slope $k_{\rm L}$ is consistent with that estimated by previous observations for $z\simeq 6-7$ quasars
-but tends to be slightly steeper at higher redshifts. }
+% \red{(to be revised)
+\blue{The two functions suggest a rapid decay of the number and mass density of massive BHs and luminous quasars
+in a cosmic volume toward higher redshifts,
+showing similar trend with predictions from previous observations and theoretical work.
+The predicted QLF at all redshifts of $z\gtrsim 6$ can be estimated as $\propto 10^{k_{\rm L} z}$,
+with the more luminous quasars decreasing more rapidly toward higher $z$.
+}
 
 \item
-Compared to the galaxy luminosity functions at redshifts from $z=7$ to $z\gtrsim 10$, the QLFs we predict are burried in the faint end at $\Muv \gtrsim -23$ mag,
+Compared to the galaxy luminosity functions at redshifts from $z=7$ to $z\gtrsim 10$,
+the QLFs we predict are burried in the faint end at $\Muv \gtrsim -23$ mag,
 which makes it challenging to select such faint quasars.
@@
 depending on extrapolation of the galaxy luminosity functions.
+
+\item
 We further explore individual BH evolutionary tracks starting from the BH seeds, applying the BH growth model
 with the best-fit parameters to examine their statistical properties.
-\item
 For massive BHs that reach $\gtrsim 10^8~\Msun$ by $z\simeq 6$, the average duty cycle of super-Eddington accretion is as high as $\simeq 15~\%$.
@@
 \appendix
-%%%%%%%
-%    Fig. 
+
+%%%%%%%
+%    Fig. 11
 %%%%%%%
@@
 \centering
-\includegraphics[width=160mm]{tau.png}
+\includegraphics[width=80mm]{f2MFtau.pdf}
+\includegraphics[width=80mm]{f2LFtau.pdf}
 \caption{
@@
 
-In the left panel of Fig.~\ref{fig:tau}, we present the BHMF at $z=6$ for three different values of $\tlife=10$, $18$, and $50$ Myr,
+In the left panel of Fig.~\ref{fig:tau}, we present the BHMF at $z=6$ for three different values of $\tlife=14$, $18$, and $37$ Myr,
 but keeping the other parameters to the best-fit values ($\lambda_0=0.87$ and $\alpha=0.20$) for the case with $\fseed=0.01$.
-We note that $\tlife \approx$ 18 Myr is the best-fit value reproducing the BHMF consistent with that of \citetalias{2010AJ....140..546W}.
+We note that $\tlife \approx$ 18 Myr is the best-fit value reproducing the BHMF consistent with that of \citetalias{2010AJ....140..546W},
+and the other two values represent the $16$ and $84$ percentiles of the one-dimensional distribution of $\tau$, respectively (see Fig.~\ref{fig:contour}).
 %the other two cases demonstrate the sensitivity of the $\tlife$ value in producing the bulk of massive BHs
 %and the slope in the high mass tail.
-For $\tlife=10$ Myr, the frequency of Eddington ratio assignment increases by a factor of two until $z=6$.
+For $\tlife=14$ Myr, the frequency of Eddington ratio assignment increases by a factor of 1.3 until $z=6$.
 %to $\sim$ 80 from $\sim$ 40 with the best-fit $\tlife$ value.
@@
 Moreover, if a high Eddington ratio is given with a certain but low probability, the BH mass hardly increases
-within $\tlife=10$ Myr, which is $\simeq 20\%$ of the $e$-folding timescale.
-On the other hand, for $\tlife=$ 50 Myr, there is a non-negligible probability that
+within $\tlife=14$ Myr, which is $\simeq 30\%$ of the $e$-folding timescale.
+On the other hand, for $\tlife=$ 37 Myr, there is a non-negligible probability that
 % $\sim$ 16 times of Eddington ratio assignment,
@@
 reproduce the observed distributions of BH mass and luminosity of quasars at $z\sim$ 6.
-In \S\ref{sec:evol}, we apply this episodic accretion model to individual growth pathways of high-$z$ quasars
-and demonstrate that normal seeding mechanisms can explain the existence of massive BHs with low luminosity
-observed at $z\simeq 6-7$.
-
-\clearpage
-
-\newpage
-% \vspace{100mm}
+% In \S\ref{sec:evol}, we apply this episodic accretion model to individual growth pathways of high-$z$ quasars
+% and demonstrate that normal seeding mechanisms can explain the existence of massive BHs with low luminosity
+% observed at $z\simeq 6-7$.
+
+% \clearpage
+
+% \newpage
+
+\vspace{100mm}
 \bibliography{ref}{}

### 2022-09-18 ms.tex
version0918; add PopII seed, M0=1e8 argument, before k revision.

@@
 \newcommand{\blue}[1]{\textcolor{blue}{ #1}}
+\newcommand{\orange}[1]{\textcolor{orange}{ #1}}
 
@@
 
-We consider seed BH formation in the main progenitors of quasar host galaxies, following a semi-analytical model established by \citet{2021ApJ...917...60L}.
+\orange{
+We consider seed BH formation as PopIII stellar remnants in the main progenitors of quasar host galaxies.
+We note that the more abundant but less massive PopII stellar remnants are likely to dominate
+the low mass end of the BHMF at $z\sim 6$,
+thus not significantly contribute to the observable QLF and BHMF \citep{2022MNRAS.511..616T}.
+}
+The BH seeding time and mass are determined adpoting a semi-analytical model established by \citet{2021ApJ...917...60L}.
 In the highly-biased, overdense regions of the universe, those progenitor halos are likely irradiated by intense H$_2$-photodissociating radiation 
@@
 \includegraphics[width=150mm]{scheme1.png}
-\caption{
-Schematical demonstration of the procedure to calculate the evolution of BH mass distribution 
-between checkpoints time $T_0$ to $T_0+\tau$. 
-The probability of a BH with mass $M_0$ grow to $M$ after $\Delta t=\tau$ is drew from the 
+\caption{\blue{
+Schematical demonstration of the procedure to calculate the evolution of BH mass distribution from the earliest BH seed to $z=6$.
+The checkpoints are spaced evenly with time interval $\tau$.
+From time $T_0$ to $T_0+\tau$, 
+the BH mass distribution evolves with $\Delta t=\tau$.
+For a newly formed seed BH $M_{\rm i}$, the probability distribution function of BH mass is a delta function, 
+and the growth time is $\Delta t = T_0+\tau-t_{\rm i}$.
+The probability of a BH with mass $M_0$ (or $M_{\rm i}$) to grow to $M$ after $\Delta t$ is drew from the 
 ERDF following Eq.~(\ref{eq:Pl}). 
-For a newly formed seed BH $M_{\rm i}$, the probability distribution function of BH mass is a delta function, 
-and the growth time is $T_0+\tau-t_{\rm i}$.
 Thus the evolution of BH mass distribution is reshaped iteratively 
-plus taking account of the newly formed seeds if there are any.
+plus taking account of the newly formed seeds if there are any.}
 }
@@
 where $M_{\bullet,c}=10^8~\Msun$ is adopted.
-With a positive value of $\delta$, the BH growth at the high mass end is suppressed, 
-while for small BHs the growth rate is accelerated.
-%  \blue{(references, Ueda+14?s)}.
-In the limit of $\delta \ll 1$, where $f(\Mbh) \simeq 1$ is approximated independent of $M_{\bullet,c}$, the model reproduces an exponential growth with an $e$-folding timescale of
+\orange{
+From the viewpoint of galactic-scale gas supply,
+this characteristic mass is in good agreement with the critical BH mass in \citet{2021ApJ...907...74T},
+above which super-Eddington mass growth of the central BHs no longer happens as
+galactic scale mass supply rates into the nuclear regions cannot be as large as the Eddington rates.
+With a positive value of $\delta$, we capture the suppression of BH growth at the high mass end, 
+while accelerate the growth rate of small BHs.
+}
+In the limit of $\delta \ll 1$, where $f(\Mbh) \simeq 1$ is approximated independent of $M_{\bullet,c}$,
+the model reduces to an exponential growth with an $e$-folding timescale of
 $t_{\rm S} =  \Mbh/\Mdot_{\mathrm{Edd}} \approx 45$ Myr, well known as the Salpeter timescale \citep{1964ApJ...140..796S}.
@@
 The three vertical dashed lines in the one-dimensional distribution of each parameter
-correspond to 16, 50, and 84 percentiles, respectively.
-The best-fit values shown in red thick lines are tabulated in Table.~\ref{tab:best_fits}.
-Note that the 50 percentile does not overlap the peak of an asymmetric distribution.
+correspond to 16\%, 50\%, and 84\% quantiles in the cumulative distribution, respectively.
+The best-fit values shown in red thick lines are tabulated in Table.~\ref{tab:best_fits},
+displaying consistency with the peaks in the one-dimensional distributions.
+Note that the best-fit values may not overlap the 50\% quantile lines,
+and the deviation are significant in asymmetric one-dimensional distributions.
+The two-dimensional distributions show that the parameter pairs
+($\tau$, $\lambda_0$) and ($\lambda_0$ and $\alpha$) are negatively correlated.
 % wli : 1\sigma definition here?
-We define the $1\sigma$ scatter of a value (e.g., $\Phi_{M_\bullet}$) as the standard deviation of it calculated
+We later refer the $1\sigma$ scatter of a value (e.g., $\Phi_{M_\bullet}$) to the standard deviation of it calculated
 from randomly selected parameters from the sampling.

### 2022-09-23 ms.tex
.
version0923; from me; revised all of Masa's 2nd round comments (w/o proximity zone); next: integrate w/ k's revision

@@
 Our best-fit model to reproduce the observed QLF and BHMF at $z\simeq 6$
-suggests that several episodes of modest super-Eddington accretion occur
+suggests that several episodes of super-Eddington accretion occur
 and each of them lasts $\tau \simeq 20-30$ Myr.
-The average duty cycle of BHs that reach $\gtrsim 10^8~\Msun$ by $z\simeq 6$ is as high as $\simeq 15~\%$,
+The average duty cycle in super-Eddington phases of BHs that reach $\gtrsim 10^8~\Msun$ by $z\simeq 6$ is as high as $\simeq 15~\%$,
 which is nearly twice that of the entire population.
@@
 
-\orange{
-We consider seed BH formation as PopIII stellar remnants in the main progenitors of quasar host galaxies.
-We note that the more abundant but less massive PopII stellar remnants are likely to dominate
-the low mass end of the BHMF at $z\sim 6$,
-thus not significantly contribute to the observable QLF and BHMF \citep{2022MNRAS.511..616T}.
-}
-The BH seeding time and mass are determined adpoting a semi-analytical model established by \citet{2021ApJ...917...60L}.
+We consider seed BH formation in the main progenitors of quasar host galaxies, following a semi-analytical model established by \citet{2021ApJ...917...60L}.
 In the highly-biased, overdense regions of the universe, those progenitor halos are likely irradiated by intense H$_2$-photodissociating radiation 
@@
 
+\orange{
+Lastly, we note that in each parent halo, we consider purely the PopIII stellar remnants in the seed BH mass function construction,
+neglecting the BHs formed by the second-generation PopII stars.
+Formed in metal-enriched environments, PopII stellar remnants are more abundant but typically less massive.
+They are likely to dominate the low mass end of the BHMF at $z\sim 6$,
+thus not significantly contribute to the observable QLF and BHMF \citep{2022MNRAS.511..616T}.
+}
+
 %BH seeding is also affected by the baryonic streaming motion of its natal cloud, 
@@
 \centering
-\includegraphics[width=150mm]{scheme1.png}
-\caption{\blue{
+\includegraphics[width=150mm]{scheme1.pdf}
+\caption{\orange{
 Schematical demonstration of the procedure to calculate the evolution of BH mass distribution from the earliest BH seed to $z=6$.
@@
 \centering
-\includegraphics[width=180mm]{contour.png} % contour.pdf
+\includegraphics[width=85mm]{f1_corner.pdf}
+\includegraphics[width=85mm]{f2_corner.pdf}
+% \includegraphics[width=180mm]{contour.png}
 \caption{
@@
 \begin{align}
+  \label{eq:chi2}
   \chi^2 = \sum_{x,i}
@@
 %%%%%%%
-\begin{deluxetable}{l|ccccccc}%[t!]
+\begin{deluxetable}{lcccccc}%[t!]
 \tablecolumns{1}
@@
 \tablehead{
-  \colhead{$\fseed$}  & \colhead{1} & \colhead{0.1} &  \colhead{0.01}
+  \colhead{$\fseed$}  & \colhead{$\tau$ (Myr)} & \colhead{$\delta$} &  \colhead{$\lambda_0$}  & \colhead{$\alpha$}  & \colhead{$\chi^2$}
 }
 \startdata
-% $\fseed$    &      1 &      0.1  &  0.01  \\
-% \hline \hline
-$\tau$      &  23.13 &   20.07   & 18.76  \\
-$\delta$    &  0.001 &   0.001   & 0.055  \\
-$\lambda_0$ &  0.96  &   0.89    &  0.87  \\    
-$\alpha$    & -0.06  & 0.12   &  0.20  \\
+1.0    &  23.13 &    0.001    &   0.96    &   -0.06    &    15.77   \\
+0.1    &  20.07 &    0.001    &   0.89    &    0.12    &    8.27    \\
+0.01   &  18.76 &    0.055    &   0.87    &    0.20    &    6.21    \\
 \enddata
-% \tablecomments{
-% The best-fit parameters optimized by MCMC sampling for the cases of $\fseed=1$, 0.1, and 0.01.
-% }
+\tablecomments{
+The best-fit parameters optimized by MCMC sampling for different cases of $\fseed$.
+The fitting performance is characterized by the relative magnitudes of the $\chi^2$ value.% (see Eq.~\ref{eq:chi2}).
+}
 \end{deluxetable}
@@
 \centering
-\includegraphics[width=145mm]{fits_MF.png}
+% \includegraphics[width=145mm]{fits_MF.png}
+\includegraphics[width=85mm]{f1ndraw60MF_spread.pdf}
+\includegraphics[width=85mm]{f2ndraw60MF_spread.pdf}
 \caption{
@@
 \centering
-\includegraphics[width=145mm]{fits_LF.png}
+% \includegraphics[width=145mm]{fits_LF.png}
+\includegraphics[width=85mm]{f1ndraw60LF_spread.pdf}
+\includegraphics[width=85mm]{f2ndraw60LF_spread.pdf}
 \caption{
@@
 %, an upper limit of the faint end QLF is provided, % by non-detection of faint quasars
-based on a search for quasars in the Hubble Space Telescope (HST) imaging fields.
+based on a search for point sources in the survey fields of the Hubble Space Telescope (HST).
 Our unobscured QLF lies within the constraints.
@@
 only bright quasars outshining their host galaxies can be identified as point-like sources in the rest-UV quasar selection 
-(\citetalias{2018ApJ...869..150M}; \citealt{2020MNRAS.495.2135N,2021MNRAS.502.2757O,2022arXiv220712282K}).
+(\citetalias{2018ApJ...869..150M}; \citealt{2020MNRAS.495.2135N,2020MNRAS.494.1771A,2021MNRAS.502.2757O,2021MNRAS.502..662B,2022arXiv220712282K}).
 However, at the faint end at $\Muv\gtrsim -24$ mag, extended sources such as the brightest galaxies at $z\sim 6$ 
@@
 \centering
-\includegraphics[width=175mm]{BHMF_rhoz1.png}
+% \includegraphics[width=175mm]{BHMF_rhoz1.png}
+\includegraphics[width=85mm]{MF.pdf}
+\includegraphics[width=85mm]{rhoM_comb.pdf}
 \caption{
@@
 evaluated by the integration of the BHMF shown in the left panel.
-The dashed-dotted line and open square symbol show the results from \citet{2022MNRAS.513..670N}.
-The upper bound of accreted BH mass density from \citet{2013ApJ...778..130T} is denoted by red triangles.
+The dashed-dotted line and open square symbols show the results from \citet{2022MNRAS.513..670N}.
+The upper bound of accreted BH mass density from \citet{2013ApJ...778..130T} is denoted by black circles.
 % The evolutionary trend can be approximated as $\rho_\bullet (z) \propto 10^{k_M z}$, where $k_M\simeq -0.68$.
@@
 \tablewidth{0pt} 
-\tablecaption{Detection Number of Quasars Estimated for Future Surveys}
+\tablecaption{Detection Number of Quasars Estimated for Future Surveys \label{tab:N_detect}} %! reference indexing
 \tablehead{
@@
 Wide RST    &  2000  & $YJH$  27   & $6759_{-3185}^{+15} $ &  $1514_{-558}^{+169}$ &  $349_{-131}^{53}$ & $85_{-48}^{+23}$ & $25^{+12}_{-15}$  \\
+Wide RST    &  2000  & $\Muv=-26$ & $21_{-5}^{+13} $      &  $2_{-7}^{+8}$        &  --  & -- & --  \\
 Wide Euclid & 15000  & $YJH$  24   & $6654^{+95}_{-2282}$  &  $708^{+213}_{-237}$ &   $93^{+66}_{-56}$ & $14^{+32}_{-27}$ & --  \\
+Wide Euclid & 15000  & $YJH$  23   & $2480^{+188}_{-614}$  &  $207^{+144}_{-114}$ &   $23^{+27}_{-19}$ & $3^{+12}_{-10}$ & --  \\
+Wide Euclid & 15000  & $\Muv=-26$ & $154^{+100}_{-38}$  &  $12^{+59}_{-50}$ &   $1^{+4}_{-3}$ & -- & --  \\
 \enddata
-\label{tab:N_detect}
 \tablecomments{
-Based on the 5$\sigma$ point source detection limits of the $YJH$ bands in the two surveys,
-the number of quasars at each redshift are predicted
-with the assumption of the survey volume with $\Delta z =1$ and 100\% completeness.
+Predicted number of quasars at each redshift in the two surveys, with the assumption of the survey volume with $\Delta z =1$ and 100\% completeness.
+The integration of QLF starts from the 5$\sigma$ point source detection limits of the $YJH$ bands in each survey, 
+and the bright magnitude with $\Muv=-26$ mag.
+In addition, detection limit with 22 mag in the $YJH$ bands is examined for Euclid,
+mimicking the effect of quasar selection function.% following \citet{2019A&A...631A..85E}.
 }
@@
 indicating short lifetime of their luminous phase $t_{\rm Q} \lesssim 10^4$ yr.
-The short quasar lifetime may be due to the young age of quasars ionizing the surrounding IGM \citep[e.g.,][]{2020ApJ...903...60I,2021ApJ...917...38E}.
+The short quasar lifetime may be due to the young age of quasars ionizing the surrounding IGM \citep[e.g.,][]{2017ApJ...840...24E,2020ApJ...903...60I,2021ApJ...917...38E}.
 Our episodic quasar growth model agrees with this argument,
@@
 The latter distribution is presented by various observational efforts in the $z\sim$ 6 brightest quasar samples 
-\citep[e.g.,][]{2010AJ....140..546W,2019ApJ...873...35S,2022arXiv220705113F}.
+\citep[e.g.,][]{2010AJ....140..546W,2019ApJ...873...35S,2021ApJ...923..262Y,2022arXiv220705113F}.
 However, our best-fit growth model reproducing both the BHMF and QLF at $z\sim$ 6 suggests the existence of
@@
 but a lower detection limit unveils more hidden quasars with low Eddington ratios. 
-This will be proved by the ongoing observations with the Subaru HSC providing low-luminosity and less-massive BH samples
-(Onoue et al. in prep) and upcoming optical survey by the Vera C. Rubin Observatory.
+Such sub-Eddington BH population at $z>6$ is being probed by the ongoing survey of the Subaru HSC and JWST
+\citep{2019ApJ...880...77O,2021jwst.prop.1967O},
+and will also be explored by upcoming wide-field surveys such as the Vera C. Rubin Observatory, Euclid, and RST.
+% This will be proved by the ongoing observations with the Subaru HSC providing low-luminosity and less-massive BH samples
+% (Onoue et al. in prep) and upcoming optical survey by the Vera C. Rubin Observatory.
 %Therefore, we emphasize that it is imperative to lower the detection limit in order to 

### 2022-09-25 ms.tex
version0925; me integrating all k's revision; except Table2 caption and main text; proximity zone including Masa; and k's 0924 file

@@
 key information on the physics determining the radiative and accretion processes of supermassive 
-black holes (SMBHs) in high-redshift quasars.
+black holes (BHs) in high-redshift quasars.
 Although the shape of the QLF has been constrained by recent wide and deep surveys,
@@
 In this study, based on a semi-analytical model for the formation and growth of seed BHs
-in quasar progenitor halos,
+in quasar progenitor dark matter halos,
 we construct the QLF and BHMF of the early BH population that experiences multiple accretion bursts,
@@
 which is nearly twice that of the entire population.
-We also find that the observed Eddington-ratio distribution function is skewed to a log-normal shape from the intrinsic Shechter-like function
+We also find that the observed Eddington-ratio distribution function is skewed to a log-normal shape from the intrinsic Schechter-like function
 owing to detection limits of quasar surveys.
-The predicted redshift evolution of both QLF and BHMF of the earliest BHs suggests a rapid decay of their number and mass
-toward higher redshifts of $z>6$, compared to galaxy stellar mass.
+The predicted redshift evolution of both QLF and BHMF of the earliest BHs suggests a rapid decay of their number and mass density 
+in a cosmic volume toward higher redshifts of $z>6$.
 This will be unveiled by future deep and wide surveys with the James Webb Space Telescope, Roman Space Telescope, and Euclid.
@@
 across the cosmic time \citep{1982MNRAS.200..115S}.
-%,1992MNRAS.259..725S}.
 The cosmic BH accretion history and their radiative efficiency are well constrained by 
-comparing the mass density of massive BHs in the local universe and the mass accreted onto BH inferred from
+comparing the mass density of supermassive BHs (SMBHs) in the local universe and the mass accreted onto BHs inferred from
 the integration of the QLF based on multi-wavelength observations
@@
 along with the QLF \citep[e.g.,][]{2015ApJ...798...28K,2016ApJ...833..222J,2017ApJ...847L..15O,2018ApJ...869..150M}.
-%and the virial BH mass estimates
-%from the \ion{Mg}{2} 2798 $\rm{\AA}$ line width 
-%where 
 Deep spectroscopic observations of high-$z$ quasars enable us to measure the virial BH mass 
 with the Mg~{\sc ii} single-epoch method and bring insights of the mass distribution
-(e.g., \citealt{2007AJ....134.1150J,2007ApJ...669...32K};
-\citealt{2010AJ....140..546W}, hereafter \citetalias{2010AJ....140..546W};
+(e.g., \citealt{2007AJ....134.1150J,2007ApJ...669...32K,2010AJ....140..546W};
+% \citealt{2010AJ....140..546W}, hereafter \citetalias{2010AJ....140..546W};
 \citealt{2018Natur.553..473B,2019ApJ...880...77O,2019ApJ...873...35S}). 
-However, extrapolation of the Soltan-Paczy{\'n}ski argument toward higher redshifts beyond $z\sim$ 6 is limited because of the current difficulty of
-constructing high-$z$ QLFs \citep{2013ApJ...768..105M,2016ApJ...829...33Y,2019ApJ...884...30W,2019BAAS...51c.121F}.
+However, extrapolation of the Soltan-Paczy{\'n}ski argument toward higher redshifts of $z\gtrsim$ 6 is still limited 
+because of the current capability of high-$z$ quasar observations 
+\citep{2013ApJ...768..105M,2016ApJ...829...33Y,2019ApJ...884...30W,2019BAAS...51c.121F}.
 Nevertheless, in the era of the James Webb Space Telescope (JWST) and forthcoming facilities,
@@
 \citep{2019BAAS...51c..45R, 2019arXiv190205569A, 2011arXiv1110.3193L}. 
-Deep surveys of high-$z$ quasars and their host galaxies will shed light on the early BH evolution and help 
+Deep observations of high-$z$ quasars and their host galaxies will shed light on the early BH evolution and help 
 answer questions regarding the existence of SMBHs in the early universe \citep{2012Sci...337..544V,2013ASSL..396..293H,2020ARA&A..58...27I}, 
@@
 with the hierarchical growth of the parent dark matter (DM) halos are taken into account in a simplified way. 
-This is an effective way of examining the statistical properties of BH populations and making predictions 
+This is an effective way of examining the statistical properties of the early BH population and making predictions 
 that can be directly compared with the observed QLF and BHMF
@@
 the formation pathway of seed BHs has been extensively investigated by numerical simulations and semi-analytical studies
-%Formation of seed BHs is the starting point to characterize the early assembly of massive BH populations.
-%Their formation pathway and expected mass range have been extensively investigated by numerical simulations and
-%semi-analytical studies
 \citep{2006MNRAS.370..289B,2009ApJ...696.1798T,2012MNRAS.422.2051N,2014ApJ...781...60H,
@@
 recent studies by \citet{2021MNRAS.503.5046L} and \citet{2021ApJ...917...60L} found that the heavy-seed formation
-can be accelerated in the rare, overdense regions of the universe, where non-linear galaxy clustering boosts the irradiation intensity
-and the frequency of halo mergers.
-As a result, \citet{2021ApJ...917...60L} predicted a top-heavy mass distribution of seed BHs ranging from $10^2-10^5~\Msun$.
+can be accelerated in rare, overdense regions of the universe, where non-linear galaxy clustering boosts the irradiation intensity
+and frequency of halo mergers.
+The mass distribution of seed BHs is expected to be substantially top-heavy, extending the upper mass to $\gtrsim 10^{4-5}~\Msun$
+\citep{2021ApJ...917...60L, 2022arXiv220614459T}.
+%As a result, \citet{2021ApJ...917...60L} predicted a top-heavy mass distribution of seed BHs ranging from $10^2-10^5~\Msun$.
 
 In this paper, we propose a theoretical model for the redshift-dependent QLF and BHMF at $z\gtrsim 6$,
-% applying the initial mass function (IMF) of seed BHs obtained from \cite{2021ApJ...917...60L}.
 applying the semi-analytic seed formation model from \cite{2021ApJ...917...60L} to study the BH growth in the early universe.
@@
 individual burst durations of $\simeq 20-30$ Myr to avoid over(under)-production of BHs at the high-mass end.
-Furthermore, we construct the redshift-dependent QLF and BHMF, implying a rapid decay of 
-their number and mass toward higher redshifts of $z>6$.
 We also find that the observed Eddington-ratio distribution function is skewed to a log-normal shape from the intrinsic Schechter-like function
 owing to detection limits of quasar observations.
+Furthermore, the evolution of the QLF and BHMF implies a rapid decay of 
+their number and mass density toward higher redshifts of $z>6$.
 Those results will be tested by future deep and wide-field surveys with JWST, RST, and Euclid,
@@
 
-\if0
-To construct the picture of BH evolution, the initial mass function (IMF) of BH seeds is required.
-Studies have shown that Pop III stars (or the seed BH population) formed in mini-halos is top-heavy, while capped with $\sim 10^3~\Msun$ 
-\citep{2014ApJ...781...60H,2015MNRAS.448..568H}.
-Focusing on the progenitor halos of supermassive BHs at $z\sim$ 6, 
-our recent semi-analytical work produces an IMF of BH seeds ranging from $10^2-10^5~\Msun$ \citep{2021ApJ...917...60L}. 
-The IMF is consistent with the three-dimensional radiation hydrodynamical simulations 
-constituting the stellar evolution with large scale mass inflow under realistic halo circumstances (Toyouchi et al. 2022).
-In this work, we apply the seeding model to examine the BH growth in common regions in the early universe, 
-constrained by the observable QLF and BHMF down to $z\sim$ 6, 
-% our aim is to understand the growth patterns of early BHs.
-\fi
-
-\blue{
-This paper is organized as follows. Firstly, in \S~\ref{sec:method} we describe the semi-analytical BH seeding procedure, 
-the parameterized BH growth model and how we reproduce the QLF and BHMF dataset at $z\sim$ 6 using these ingredients. 
-In \S~\ref{sec:fitting_result} we present the fitting of model parameters constrained by quasar observations.
-In \S~\ref{sec:cosm} we discuss the cosmological evolution of BH mass and quasar luminosity functions 
-indicated by our best-fit models, as well as the potential detection of these BHs in their early growth.
-In \S~\ref{sec:discussion} we present the BH growth tracks and statistical properties along the $z\sim 6$ SMBH growth histories.
-We then summarize our findings in \S~\ref{sec:sum} and discuss the potential applications of quasar observations on exploring the high-$z$ universe.
-}
+This paper is organized as follows. 
+In Section~\ref{sec:method}, we describe the semi-analytical model for BH seeding and subsequent growth via accretion,
+and explain the MCMC fitting procedure to constrain the theoretical models by the observations.
+%The physical parameters to characterize the QLF and BHMF in the model are optimized with the MCMC fitting to reproduce 
+%the observed distribution functions at $z=6$.
+In Section~\ref{sec:fitting_result}, we present the fitting results for the model parameters reproducing the observational results,
+and discuss the key physics to determining the BH growth.
+In Section~\ref{sec:cosm}, we discuss the cosmological evolution of the BHMF and QLF suggested by our best-fit models, 
+as well as the detection number of those BHs at $z\sim 6-10$ with Euclid and RST.
+In Section~\ref{sec:discussion}, we present the evolutionary tracks of individual BHs and their statistical properties at $z\gtrsim 6$,
+based on the growth model calibrated above.
+We finally summarize our findings in Section~\ref{sec:sum} and discuss the potential applications of quasar observations on 
+exploring the high-$z$ universe.
 Throughout this work, we apply the cosmological parameters from \cite{2016A&A...594A..13P},
@@
 \vspace{2mm}
-\subsection{Seeds}\label{sec:seed}
+\subsection{Seed BH formation}\label{sec:seed}
 The QLFs at high redshifts are determined by the BH seeding mechanism and subsequent growth. 
@@
 where the rotation velocity of gas based on the [C~{\sc ii}] 158 $\micron$ line width is assumed to be the circular velocity of the halo
-%is is motivated by the estimated masses of quasar hosts which are typically up to $\sim 10^{11-13}~\Msun$, 
-%probed by the [\ion{C}{2}] 158 $\micron$ fine structure line width 
 \citep{2002ApJ...578...90F,2013ApJ...773...44W,2019ApJ...872L..29S}.
@@
 \citep{1974ApJ...187..425P,2000MNRAS.319..168C,2008MNRAS.383..557P}.
-%, and study the BH seeds formed therein.
 For each tree, we adopt a minimum DM halo mass of $M_{\rm h,min}=10^5~\Msun$, which is small enough to capture 
@@
 (photo-)chemical reaction networks.
-%, and gravitational instability of the central gaseous cores.
 The time evolution of the gas dynamics and thermal states is calculated in a self-consistent way with the halo assembly history.
-%the gas dynamical and thermal evolution is regulated by the parent halo growth histories, and the environmental streaming velocities.
-%
-%Next we introduce our seeding model where the gas dynamical and thermal evolution is regulated by the parent halo growth histories, 
-%and the environmental streaming velocities.
-%In \citet{2021ApJ...917...60L}, we propose an semi-analytical model which 
-%traces the gas evolution along its parent halo growth and yields the seed BH mass distribution. 
-% The background UV radiation $$ is calculated by semi-analytical arguments of men
-%The merger heating and enhancement of background Lyman-Werner radiation intensity $\jlw$ 
-%due to halo clustering is taken into account to shape the gas thermal evolution.
 
 In addition, we consider baryonic streaming motion relative to DM produced in the epoch of cosmic recombination at $z_{\rm rec} \simeq 1100$.
-%originated from its decoupling with radiation.
 This effect also delays gas collapse and star formation in protogalaxies through injection of kinetic energy into gas
@@
 where $c_{\rm s}$ is the thermal sound speed, $v_{\rm tur}$ is the turbulent velocity of gas (i.e., the specific kinetic energy accumulated through halo mergers), and
-the coefficient is set to $\alpha_0=1$\footnote[1]{The value of $\alpha_0=1.0$ is motivated by cosmological simulations of massive primordial stars
+the coefficient is set to $\alpha_0=1$ \footnote[1]{The value of $\alpha_0=1.0$ is motivated by cosmological simulations of massive primordial stars
 under fast streaming velocities \citep{2017Sci...357.1375H,2019MNRAS.484.3510S}.
 Note that our previous study in \citet{2021ApJ...917...60L} adopted $\alpha_0=4.7$ \citep{2018ApJ...855...17H}.}.
-%
-%Besides, the baryonic streaming velocity $\vbsm$ together with the turbulent velocity $v_\mathrm{tur}$ 
-%through halo virialization is taken into account
-%\footnote{
-%We model the effective sound speed of gas as $c_{\rm eff} = \sqrt{ c_{\rm s}^2+v_{\rm tur}^2/3+\left(\alpha_0 \vbsm \right)^2}$,
-%where the coefficient $\alpha_0 = 1$ is motivated by previous studies 
-%\citep{2017Sci...357.1375H,2019MNRAS.484.3510S}.
-%}.
 When the gas core becomes gravitationally unstable, the evolution of the gas density profile is well described by 
@@
 %}
-%Thus, we estimate the accretion rate to estimate the protostellar mass and that of the subsequent seed BH formed. 
 The size evolution of an accreting protostar and the radiative feedback strength depend sensitively on whether
@@
 \citep{2008ApJ...681..771M,2011Sci...334.1250H}. 
-In this case, the stellar mass is determined by the balance between mass accretion and mass loss via photoevaporation \citep{2013ApJ...773..155T},
-and can be approximated as (see more details in \citealt{2021ApJ...917...60L})
-%the final stellar mass is capped by the balance of the mass loss rate via disk photoevaporation $\dot{M}_{\mathrm{pe}}$
-%and the accretion rate $\dot{M}_{\star}$, and the former is expressed as 
-% \begin{equation*}
-  % \dot{M}_{\mathrm{pe}} \simeq 2.1 \times 10^{-2} \Msunyr \left(\frac{\Phi_{\mathrm{ion}}}{10^{52} \mathrm{~s}^{-1}}\right)^{1 / 2}\left(\frac{R_{\rm{disk}}}{0.1 \mathrm{pc}}\right)^{1/2}.
-% \end{equation*}
-%$\dot{M}_{\mathrm{pe}} \simeq 2.1 \times 10^{-2} \Msunyr \left( \Phi_{\mathrm{ion}}/10^{52} \mathrm{~s}^{-1}\right)^{1 / 2}\left(R_{\rm{disk}}/0.1 \mathrm{pc}\right)^{1/2}$ 
-%\citep{2013ApJ...773..155T}.
-%Here we adopt the emissivity of UV photons $\Phi_{\mathrm{ion}} \simeq 1.6 \times 10^{52} \mathrm{~s}^{-1}\left(M_{\star} / 10^{4} \Msun \right)$ following \citet{2012ApJ...750...66J}, 
-%and the disk size is estimated as the stellar gravitational influence radius for 2$\times 10^4$ K ionized gas 
-%$R_{\mathrm{disk}} \simeq  G M_{\star}/c_{\mathrm{s}, \mathrm{ion}}^{2} \simeq 0.17 \mathrm{pc}\left( M_{\star}/ 10^{4} \Msun \right)$.
-%The final stellar mass regulated by radiative feedback is thus 
+In this case, the stellar mass is determined by the balance between mass accretion and mass loss via photoevaporation \citep{2013ApJ...773..155T}.
+The feedback-regulated mass can be approximated as
+\footnote[2]{A recent study by \citet{2022arXiv220614459T} provides a more sophisticated prescription of the feedback-regulated stellar mass based on their radiation hydrodynamical simulations.}
 %
 \begin{equation}
-M_{\star, \mathrm{fb}} \simeq 2.9 \times 10^{3} \Msun\left(\frac{\dot{M}_{\star}}{0.01 M_{\odot} \mathrm{yr}^{-1}}\right).
+M_{\star, \mathrm{fb}} \simeq 2.9 \times 10^{3} \Msun\left(\frac{\dot{M}_{\star}}{0.01 M_{\odot} \mathrm{yr}^{-1}}\right),
 \end{equation}
 %
-%for $\Mdot_\star\lesssim \Mdot_\mathrm{crit}$. 
+see more details in \cite{2021ApJ...917...60L}.
 For an intermediate accretion rate between $\Mdot_\mathrm{crit}$ and $0.1~\Msunyr$, 
@@
 At the end of the stellar lifetime, those massive primordial stars result in BHs without significant mass loss 
-% ($\sim 10\%$ to $50\%$) 
-% \red{How do you get this percentage of mass loss?}
 via stellar winds \citep{2003ApJ...591..288H,2010ApJ...714.1217B,2015MNRAS.451.4086S}.
@@
 %and the cumulative BHs formed previously by the blue region.
-The majority of seed BHs form in the epoch of $40\lesssim z \lesssim 20$.
+The majority of seed BHs form in the epoch of $20\lesssim z \lesssim 40$.
 %The most vigorous seed formation epoches are in redshift ranges $z\sim$ $40-30$ and $30-20$.
@@
 $t_i$ ($1\leq i \leq N_{\rm tot}=10^4$),
-%In the $i$-th DM growth history where a seed BH is formed with mass $M_\text{itr}$ at the cosmic age $t_\text{itr}$, 
 and each of them contributes to the probability distribution function (PDF) of seed mass at a time $t$ as
@@
 
+Fig.~\ref{fig:seedmf} presents how the seed mass function is developed in each redshift interval.
+The majority of seed BHs forms in the epoch of $20\lesssim z \lesssim 40$, and the distribution function is 
+extended to $M_\bullet \gtrsim 10^5~\Msun$, imprinted with the halo assembly and environmental effects.
+
 \orange{
@@
 
-%BH seeding is also affected by the baryonic streaming motion of its natal cloud, 
-%where gas is streaming relative to the dark matter in the epoch of cosmic recombination at $z_\mathrm{rec}\approx$ 1100, 
-%originated from its decoupling with radiation.
-%The streaming velocity follows a Maxwell-Boltzmann distribution with a root-mean-square (\textit{rms}) speed of 
-%$\sigma(z) = 30~{\rm km~s}^{-1} (1+z)/(1+z_{\mathrm{rec}})$ which is decaying with time \citep{2010PhRvD..82h3520T}.
-%The impact of the super-sonic $\vbsm$ at high redshifts on the PopIII star (seed BH) formation 
-%is explored by various studies \citep{2012MNRAS.424.1335F,2014MNRAS.439.1092T,2017Sci...357.1375H,2019MNRAS.484.3510S,2021ApJ...917...60L}.
-%Their major findings are that the non-negligible $\vbsm$ injects kinetic support into pristine gas clouds, 
-%which increases their effective Jeans mass and delays star formation, 
-%yielding BH seeds heavier than typical PopIII stars. 
-%The volume fraction of the universe with streaming velocities higher than the \textit{rms} value
-%is estimated as $\simeq 0.4$. We then set $\vbsm=$ 0 and the \textit{rms} velocity as two representative cases, 
-%accounting for roughly $f_{\vbsm} = 60\%$ and $40\%$ of the seeding environments, respectively.
-
 %%%%%%%
@@
 \centering
-\includegraphics[width=150mm]{scheme1.pdf}
+\includegraphics[width=170mm]{scheme1.pdf}
 \caption{\orange{
@@
 \label{sec:model}
-% The BH accretion at high redshifts is probed only by snapshots, in their most luminous quasar phase. 
-% We have constraints on simulations and observations of lower redshift counterparts.
-With BH seeds planted, we grow the BHs with a semi-analytical accretion model and study the evolution of the BH mass distribution until $z=6$. 
-% \blue{(references + discussion)}
-The growth model is characterized by a minimal number of free parameters, 
-% the quasar accretion is episodic with Eddington ratio variations,
-describing the BH mass growth rate $\Mdot$ by
-%%%%%%%
-%    Eq. 1
-%%%%%%%
-% \begin{equation*}
-%   \label{eq:mdot_1}
-%   \Mdot_\bullet = \frac{\lambda f(\Mbh) \Mbh}{t_{\rm S}} ,
-% \end{equation*}
+With BH seeds planted, we study the evolution of the BH mass distribution until $z=6$. 
+The growth model of each BH is characterized by a minimal number of free parameters, 
+giving the accretion rate by
+%
 \begin{equation}
@@
 \end{equation}
-% where $t_{\rm S} = \eta_0  M c^2/L_{\mathrm{Edd}} \approx 45$ Myr,
 where $\lambda \equiv L/L_\mathrm{Edd}$ is the luminosity-based Eddington ratio,
 and $\Mdot_\mathrm{Edd} \equiv L_{\mathrm{Edd}}/\eta_0 c^2$ is the Eddington accretion rate with a radiative efficiency of $\eta_0=0.1$ \citep{1973A&A....24..337S},
-%Note here we adopt the radiative efficiency $\eta_0 \approx 0.1 $,
-%according to the thin accretion disk model \citep{1973A&A....24..337S}, 
 which is consistent with the value obtained from the Soltan-Paczy{\'n}ski argument \citep[e.g.,][]{2002MNRAS.335..965Y,2010ApJ...725..388C}.
-% The high mass BH should be strangulated by as it grows, 
 On the basis of studies on the mass dependence of the radiative efficiency for AGNs at $z\lesssim$ 3 
 \citep{2008MNRAS.390..561C,2012ApJ...749..187L,2014ApJ...786..104U}, 
-we introduce a similar functional form that characterizes the mass dependence 
+we introduce a similar functional form of
 %
@@
 galactic scale mass supply rates into the nuclear regions cannot be as large as the Eddington rates.
-With a positive value of $\delta$, we capture the suppression of BH growth at the high mass end, 
-while accelerate the growth rate of small BHs.
-}
-In the limit of $\delta \ll 1$, where $f(\Mbh) \simeq 1$ is approximated independent of $M_{\bullet,c}$,
-the model reduces to an exponential growth with an $e$-folding timescale of
-$t_{\rm S} =  \Mbh/\Mdot_{\mathrm{Edd}} \approx 45$ Myr, well known as the Salpeter timescale \citep{1964ApJ...140..796S}.
-%h independent of BH mass.
-% In \S~\ref{sec:fitting}, $\delta$ turns out to be close to 0, indicating an exponential grow manner independent of BH mass.
-%Then $t_{\rm S} =  M/\Mdot_{\mathrm{Edd}} \approx 45$ Myr is the Salpeter $e$-folding timescale \citep{1964ApJ...140..796S}.
-
-The quasar activity is episodic in nature, with accretion bursts triggered by gas inflows to the galactic nuclei
-% \citep[e.g., mergers or disk instabilities, see][]{2005Natur.433..604D,2005ApJ...630..705H}, 
+}
+With a positive value of $\delta$, the BH growth at the high mass end is suppressed,
+while the growth speed for less masssive BHs is accelerated.
+In the limit of $\delta \ll 1$, where $f(\Mbh) \simeq 1$ is nearly independent of $M_{\bullet,c}$,
+the model in Eq.~(\ref{eq:f_M}) reproduces an exponential growth with an $e$-folding timescale of
+$t_{\rm S} =  \Mbh/\Mdot_{\mathrm{Edd}} \approx 45$ Myr (the so-called Salpeter timescale; \citealt{1964ApJ...140..796S}).
+
+Quasar activity is thought to take place episodically with accretion bursts triggered by gas inflows to the galactic nuclei
 \citep{2005Natur.433..604D,2005ApJ...630..705H}, 
@@
 \citep{2006ApJ...639..700H,2009ApJ...698.1550H}.
-%
-For type-I AGN populations at low redshifts, the ERDF is characterized with a Schechter function
-%Observations also propose that the intrinsic ERDF in lower-$z$ quasars hosted by star forming galaxies follows a Schechter shape, 
+For type-I AGNs at low redshifts, the ERDF is characterized with a Schechter function
 \citep{2015MNRAS.447.2085S,2016ApJ...826...12J,2018MNRAS.474.1225A}.
 Motivated by those facts, we give the ERDF by a Schechter function with two free parameters $\lambda_0$ and $\alpha$ as
-%%%%%%%
-%    Eq. 2
-%%%%%%%
+%
 \begin{equation}
@@
 \end{equation}
+%
 The normalization is set so that the integrant of this function over $\lambda_\mathrm{min}(=0.01) \leq \lambda < \infty$ is unity.
-%normalized by the total probability above $\lambda_\mathrm{min}$ = 0.01.
 The minimum Eddington ratio $\lambda_\mathrm{min}$ is adopted from the simulated evolution of quasar luminosities 
 that decrease mildly toward $\lambda \sim 0.1-0.01$ with $\lesssim$ 100 Myr after the peak activity \citep{2011ApJ...737...26N}.
-Moreover, a turnover at the lowest value $\lambda\lesssim 0.01-0.001$ in the ERDF is suggested by observations \citep{2018MNRAS.474.1225A}.
+Moreover, a turnover in the ERDF at the lowest value of $\lambda\lesssim 0.01-0.001$ is suggested by observations \citep{2018MNRAS.474.1225A}.
 
@@
 (the corresponding cosmic age is $t_{\rm H}\gtrsim 900$ Myr).
-This treatment enables us to capture the nature of accretion bursts and avoid an unrealistically 
+This treatment enables us to capture the nature of accretion bursts and prohibit an unrealistically 
 long-lasting rapid growth phase of a BH.
-This phenomenological method introducing a parameter of $\tlife(<t_{\rm H})$ allows us to avoid 
-numerous uncertainties in modeling of the galaxy assembly, gas feeding, and BH feedback processes in the quasar 
-progenitor halos.
+This phenomenological method also avoids numerous uncertainties in modeling of the galaxy assembly, 
+gas feeding, and BH feedback processes in the quasar progenitor halos.
 Instead of treating those ingredients implemented in previous semi-analytical models, we extract 
@@
 based on direct comparison to those distribution functions for observed high-$z$ quasar population.
-%We leave a more detailed discussion to \S~\ref{sec:discussion}.}
-
-Thus far, we assume that {\it all} the parent halos form seed BHs during their assembly and end up in quasar host galaxies by $z\simeq 6$.
+
+Thus far, we assume that {\it all} the seed BHs formed in parent halos participate in the assembly of SMBHs and 
+end up in quasar host galaxies by $z\simeq 6$.
 To relax this stringent assumption, we introduce the seeding fraction of $\fseed (\leq 1)$.
@@
 depending on BH seeding and growth mechanisms in semi-analytical models.
-% that denotes the portion of DM halos where seed BHs are seeded \citep{2009ApJ...696.1798T}.
 Since the value has been poorly constrained both by theoretical and observational studies, we treat it as a free parameter.
 We take three different values of $\fseed = 1$, $0.1$, and $0.01$, and explore its effect on producing the QLF and BHMF.
-\blue{
-With analysis on the fitting results for $\fseed = 1$ and $\fseed = 0.1$,
-we find that the best-fit parameters in the two cases are overall similar (see Table.~\ref{tab:best_fits}). 
-For simplicity, we neglect presenting the discussion on the $\fseed=1$ case hereafter.
-}
-Note that for demonstration purposes, the seed mass function shown in Fig.~\ref{fig:seedmf} is given with $\fseed = 1$.
+Since we find that the results in the cases of $\fseed = 1$ and $0.1$ are overall similar,
+we thus show only the cases with $\fseed=0.1$ and $0.01$ in the following discussion.
+Note that the seed mass function shown in Fig.~\ref{fig:seedmf} is given with $\fseed = 1$.
 
@@
 We describe how to calculate the time evolution of the BH mass function, 
-combining the semi-analytical growth model and the ERDF (see Eqs.~\ref{eq:mdot} and \ref{eq:Pl}).
+combining the semi-analytical growth model and ERDF (see Eqs.~\ref{eq:mdot} and \ref{eq:Pl}).
+The schematic illustration of our numerical procedure is shown in Fig.~\ref{fig:scheme}. 
 We first set a series of checkpoints with an interval of $\tlife$, 
@@
 Note that the number of the checkpoints is given by $\lceil (t_{\rm H}-t_1)/\tau \rceil+1$, where $\lceil x\rceil \equiv {\rm min}\{n \in \mathbb{Z}~ |~x\leq n\}$.
-% we set a total number of $\Nt$ checkpoints with an interval of $\tlife$,
-% where $\Nt = \lfloor \left(t_\mathrm{H}(z=6) - t_\mathrm{H}(z_\mathrm{seed,max})\right)/ \tlife \rfloor$,
 
@@
 and taking into account growth of existing BHs via mass accretion.
-%every by evolves iteratively during each cycle,together with the seeds newly formed in between.
 For a given mass distribution function $\D P/\D  M_{\bullet, 0}$ at a checkpoint of $t=T_0$, 
 we give its evolution at $t=T_0+\Delta t$ as
-%%%%%%%
-%    Eq. 5
-%%%%%%%
+%
 \begin{equation}
@@
    \frac{\D \ln \lambda_\ast}{\D  \Mbh}\Big|_{\Delta t, M_{\bullet,0}} \cdot
-   %_{M, M_\mathrm{i},\Delta t, \delta}
   \frac{\D P}{\D M_{\bullet, 0}}~\D M_{\bullet, 0},
@@
 and is calculated analytically from Eq.~(\ref{eq:mdot}) by
-%%%%%%%
-%    Eq. 4
-%%%%%%%
+%
 \begin{equation}
@@
 For existing BHs formed prior to this checkpoint, we calculate the evolution of the mass distribution by setting $\Delta t = \tlife$.
-% is set for the BH mass distribution iteration from the latest checkpoint, 
 For a seed BH formed during this cycle (i.e., $T_0\leq t_k < T_0+\tlife$), 
@@
 of the existing BHs at $t=T_0+\tlife$.
-%adopt $\Delta t = t-t_k$, and $\D P^{\rm seed}_{\rm i}/ \D \Mbh$ as the initial mass distribution.
-This procedure is illustrated schematically in Fig.~\ref{fig:scheme}. 
-\red{KI: Fig.~2 also needs to show the configuration of the checkpoints, adding more info.}
-% After the seed formation terminates (i.e., after the total number of BHs is fixed), we perform this integration in every timestep 
-% by setting to $\Delta t = \tlife$ until $z=6$.
 Combining the PDF and number density normalization, the BHMF is given by
 %
-%%%%%%%
-%    Eq. 3
-%%%%%%%
 \begin{equation}
@@
 
-To perform the integration and follow the time evolution of the mass function, we set up 
+To follow the time evolution of the mass function, we set up 
 logarithmically spaced mass grids at $10^2 \leq \Mbh /\Msun \leq 10^{12}$.
 The number of the grid points is set to $N_{\rm bin}=800$, so that the convergence of the numerical result is ensured.
-%
-%We note that setting discrete mass bins to resemble the integration in the calculation above, 
-%we ensure the convergence of the BHMF produced by increasing the number of mass bins to 800 log evenly across $10^2-10^{12}~\Msun$. 
 Our result of $\Phi_{\Mbh}$ is consistent with that obtained from the direct sampling method, where 
-we generate $10^7$ BH samples whose initial mass and the Eddington ratio in each cycle are assigned
-and reconstruct the BHMF at $z=6$ by collecting the $10^7$ samples.
-%Our results of $\Phi_{\Mbh}$ are consistent with that from directly generating random $\lambda$ 
-%following Eq.~(\ref{eq:Pl}) in each cycle of BH growth. 
-%Remarkably, 
+we consider the growth of $10^7$ individual BHs rather than the evolution of smooth analytical mass distribution functions.
 Our method reduces the statistical errors seen in the direct sampling method 
@@
 
-% In the BHMF calculation, we set 100 mass bins ranging from  $10^2~\Msun$ to  $10^{12}~\Msun$, spacing evenly in logarithmic scale.
-% This enables us to obtain the convergent BHMF at $z=$ 6 for any given parameters.
-
 \vspace{2mm}
@@
 Using the BHMF and its evolution, we construct the QLF, which can be directly probed by high-$z$ quasar observations.
-%  compared with observations and in return constrain our model.
 For an accreting BH with a bolometric luminosity of $\Lbol=\lambda L_\mathrm{Edd}$, 
 its rest-frame ultraviolot (UV) absolute magnitude of $\Muv$ at 1450 $\mathrm{\AA}$ is estimated by
-%%%%%%%
-%    Eq. 6
-%%%%%%%
+%
 \begin{equation}
   \label{eq:M1450}
-  \Muv= -21.0-2.5 \log  \left(\frac{\Lbol}{10^{45}~\mathrm{erg~s}^{-1}} \right) \rm{mag},
+  \Muv= -21.0-2.5 \log  \left(\frac{\Lbol}{10^{45}~\mathrm{erg~s}^{-1}} \right) ~[\rm{mag}],
 \end{equation}
 %
-where we adopt a bolometric correction factor of $f^{\rm bol}_{1450}=4.4$ for the monochromatic UV band 
+where a bolometric correction factor of $f^{\rm bol}_{1450}=4.4$ for the monochromatic UV band is adopted
 \citep{2006ApJS..166..470R}.
-Combining this conversion factor and the ERDF to govern the BH growth, the quasar abundances with different luminosities 
-can be constructed.
-%Under this conversion, an ERDF combined with the $z\sim$ 6 BH population is able to reproduce 
-%the quasar abundances with different luminosities. 
+We construct the QLF from the BHMF, combining this conversion factor and ERDF.
 However, we note that the shape and normalization of the {\it intrinsic} QLF is not necessary identical to the {\it observed} QLF
 because quasar surveys with optical and near-infrared telescopes are not sensitive to the obscured quasar population at high redshifts,
-% a larger fraction of fainter quasars are missed in current observations owing to quasar obscuration, 
-%it is crucial to obtain we note that a vital ingredient to construct the observed QLF, 
 i.e., the number of fainter quasars observed as type-I AGNs is largely reduced by the obscuration effect
-%Therefore, is the luminosity dependent obscuration fraction, 
-%which decreases the fraction of the detectable quasars preferentially in the dimmer population 
 \citep{2003ApJ...598..886U,2007A&A...463...79G,2008A&A...490..905H,2014ApJ...786..104U,2014MNRAS.437.3550M}.
-%thus differs the normalization and shape of the observed QLF from the intrinsic one.
 
@@
 In addition, dense gas clouds at galactic larger scales may have a significant contribution to quasar obscuration at 
-higher redshifts \citep{2020MNRAS.495.2135N}, and the obscured fraction is expected to increase with redshift \citep[]{2022arXiv220603508G}. 
-In this study, however, we adopt the prescription of the obscured fraction constrained from quasar observations at $z\lesssim 5$ 
-since the physical origin and conditions for high-z quasar obscuration is poorly understood yet.
-%While at high redshifts, obscuration from much wider galactic scale may also be common \citep{2020MNRAS.495.2135N},
-%and the denser gas may imply a growing obscured fraction with redshift \citep[]{2022arXiv220603508G}. 
-%The physical conditions for high-$z$ quasar obscuration and their observational effects remains debated,
-%and we refer to the observational constraints in this study.
-% even with extensive studies both on theoretical and observational sides
-% our current understanding of the quasar obscured fraction is inadequate, 
-%due to the sophisticated physical conditions which lead to obscuration and observational difficulties in probing it.
+higher redshifts \citep{2020MNRAS.495.2135N}.
+%and the obscured fraction is expected to increase with redshift \citep[]{2022arXiv220603508G}. 
+%However, we adopt the prescription of the obscured fraction constrained from quasar observations at $z\lesssim 5$ 
+However, the physical origin and conditions for high-z quasar obscuration has been poorly understood yet.
 Observationally, the obscured fraction of AGNs with hydrogen column density of $N_{\rm H}>10^{22}~{\rm cm}^{-2}$
 can be estimated from spectral analyses in the X-ray band
-%The high-$z$ quasars observed in the rest-frame UV-optical bands are profoundly obstructed by dust obscuration, 
-%\red{while hard X-rays in the 2$-$10 keV band can penetrate the dust with gas dominating the absorption.} \red{(KI: what does it mean?)} 
-%\red{Therefore, dust obscuration is equivalently translated to gas absorption with a hydrogen column density of $N_\mathrm{H}>10^{22}$ cm$^{-2}$ 
-%implied by the X-ray spectral fitting 
 \citep[e.g.,][]{2003ApJ...598..886U,2007A&A...463...79G,2008A&A...490..905H}. 
@@
 Moreover, the obscured fraction is found to increase gradually toward higher redshifts and is saturated at $z\gtrsim 2-3$
-\citep{2008A&A...490..905H,2014ApJ...786..104U,2014MNRAS.437.3550M,2018MNRAS.473.2378V}.
-
-In this work, we adopt the obscuration fraction $\fobsc$ given by \citet{2014ApJ...786..104U}, 
-converting the hard X-ray luminosity to the absolute magnitude at 1450 $\mathrm{\AA}$ with bolometric correction factors of
-\begin{equation*}
+\citep{2008A&A...490..905H,2014ApJ...786..104U,2014MNRAS.437.3550M,2018MNRAS.473.2378V,2022arXiv220603508G}.
+
+In this study, we adopt the obscuration fraction $\fobsc$ given by \cite{2014ApJ...786..104U} as
+%
+\begin{equation}
+\fobsc = \text{min}\left\{0.84 , 11.23-0.24 \log \left(\frac{\Lbol}{L_\odot}\right) \right \}.
+%  \fobsc = \text{min}\lbrace  0.84 , 0.73-0.24\times[ \log (\Lbol/L_\odot) -43.75] \rbrace,
+\end{equation}
+%
+Here, we use the bolometric correction factor from the hard X-ray band 
+%
+\begin{equation}
   f^{\rm bol}_{\rm X} =
   a\left[1+\left(\frac{\log \left(\Lbol / L_\odot\right)}{b}\right)^{c}\right],
-\end{equation*}
-where $a=10.96$, $b = 11.93$, and $c = 17.79$ \citep[Eq.~2 in ][]{2020A&A...636A..73D}, 
-and $f^{\rm bol}_{1450}=4.4$ \citep{2006ApJS..166..470R}.
-The obscuration fraction reads 
-\begin{equation*}
-  \fobsc = \text{min}\lbrace  0.84 , 0.73-0.24\times[ \log (\Lbol/L_\odot) -43.75] \rbrace,
-\end{equation*}
-following \citet{2014ApJ...786..104U}.
-% An alternative fitting form of $\fobsc$ based on their X-ray AGN sample with additional optical obscuration classification 
-% is proposed by \citet{2014MNRAS.437.3550M} as
-% %
-% \begin{equation*}
-%   \fobsc = 0.56 + \frac{1}{\pi}~ \text{arctan} \left[ \frac{43.89 - \log (\Lbol/L_\odot)}{0.46}\right].
-% \end{equation*}
-% %
-% We also conduct the parameter fitting with this prescription and discuss the sensitivity of our results to 
-% the choice of $\fobsc$ in the Appendix.
-% \red{KI: add appendix}
-
-Here, we neglect the contribution from Compton-thick AGNs with $N_\mathrm{H}>10^{24}$ cm$^{-2}$, 
+\end{equation}
+%
+where $a=10.96$, $b = 11.93$, and $c = 17.79$ are given in Eq.~(2) of \citet{2020A&A...636A..73D}. 
+In our analysis, we neglect the contribution from Compton-thick AGNs with $N_\mathrm{H}>10^{24}$ cm$^{-2}$, 
 which are obscured even in the hard X-ray band and show possible dependence on quasar properties.
-% and it is currently not warranted to discuss the uncertainties of $\fobsc$.
-It is worth noting that the obscured fraction for high-$z$ quasar populations is still under investigation,
-and the uncertainties would affect our analyses for fainter quasars.
-%with complex conversions between the probes in different observational bands,
-% optical and X-ray observations, 
-%and is need to be 
-%and we may refer to more solid prescriptions of $\fobsc$ in the future.
+It is worth noting that the obscured fraction for high-$z$ quasar populations is still under investigation.
+%and the uncertainties would affect our analyses for fainter quasars.
 We leave more comprehensive arguments about the quasar obscuration effect for future work.
@@
 the observed QLF for a given BHMF and ERDF is calculated as
-%%%%%%%
-%    Eq. 7
-%%%%%%%
+%
 \begin{equation}
@@
 
-%%%%%%%
-%    Fig. 3
-%%%%%%%
-\begin{figure*}
-\centering
-\includegraphics[width=85mm]{f1_corner.pdf}
-\includegraphics[width=85mm]{f2_corner.pdf}
-% \includegraphics[width=180mm]{contour.png}
-\caption{
-Two dimensional posterior distribution of all the model parameters with $\fseed=0.1$ and 0.01, 
-along with the marginalized one dimensional projection.
-% and the two dimensional distribution between every two parameters. 
-The distribution of three parameters ($\tau$, $\lambda_0$, and $\alpha$) show single peaks,
-displaying the convergence of those parameters.
-The distribution of $\log\delta$ is relatively broader but suggests that the value of $\delta$
-is sufficiently low and thus the mass-dependent growth model is excluded.
-}
-\label{fig:contour}
-\vspace{5mm}
-\end{figure*}
-%
-
 In this section, we describe the MCMC fitting procedure used to optimize 
 the BH growth parameters so that the observed BHMF and QLF are consistently reproduced. 
-As discussed in \S~\ref{sec:MF}, we consider five parameters of $\tlife$, $\delta$, $\alpha$, $\lambda_0$, and $\fseed$.
+As discussed in Section~\ref{sec:MF}, we consider five parameters of $\tlife$, $\delta$, $\alpha$, $\lambda_0$, and $\fseed$.
 The best-fit values of the first four parameters are calculated by the MCMC method, while $\fseed$ is fixed to a single value.
@@
 is constrained at $\log \delta$ from $-4$ to $-0.3$
-\footnote[2]{ We first set uniform prior $0\leq \delta \leq 1$, 
+\footnote[3]{ We first set a uniform prior at $0\leq \delta \leq 1$, 
 and find the posterior distribution assembles to $\delta \lesssim 0.1$.
 We then switch to impose the $\log \delta$ prior to improve the fitting performance at small $\delta$ values.}.
-%\red{KI: add a footnote, explaining why not $\delta$ but $\log \delta$?}.
-%slightly suppressing the growth in the high mass end. 
-% After trials we find in the Markov chain, the value of $\tlife$ reduces to $\lesssim$ 100 Myr, 
-% and the one for $\delta$ assembles to $\lesssim 0.1$. 
-% Driven by these phenomena, we switch the uniform $\tlife$ prior to 10 to 200 Myr,
-% and use $\log \delta$ instead of $\delta$ with a prior ranging from $-4$ to $-1$ in pursuit of better fitting performance. 
 The prior function is uniform at $\log \delta \geq -3$ and is imposed to decay with an exponential cutoff at $\log \delta < -3$,
-which is small enough for the model to be approximately mass independent.
-%since toward low $\log\delta$ the model is essentially mass-independent,
-%and remains uniform otherwise. 
+which is small enough for the model to be approximately mass independent, i.e., $f(M_\bullet)\simeq1$.
 For the characteristic Eddington ratio $\lambda_0$ in the Schechter-type ERDF, 
 we impose a Gaussian prior function with a mean value of $\mu_{\lambda_0}=0.6$ and a dispersion of $\sigma_{\lambda_0}=0.4$.
-% motivated by the various observations revealing a large sample of quasars with peak $\lambda\lesssim 1$,
-The choice is motivated by the brightest quasar samples at $z=$ 6, whose ERDF function is peaked around $\lambda \sim 0.6$ 
+The choice is motivated by the brightest quasar samples at $z=$ 6, whose ERDF is peaked around $\lambda \sim 0.6$ 
 % \citep[e.g.,][Onoue et al. in preparation]{2010AJ....140..546W}.
-after luminosity bias correction (e.g., \citetalias{2010AJ....140..546W}).
-% It is worth noting that, observationally the high-$z$ ERDF is fitted by a log-normal function. 
-% \blue{
-% because of detection limit, there may be a large population of low $\lambda$ BHs unrevealed,
-% so our model of Schechter distribution is purely from theoretical prediction 
-% and extrapolation of the statistical properties of its low-$z$ counterparts. 
-% Then the slope index alpha uncertain \dots
-% }
-% However, lower-$z$ quasar observations reveal that ERDF is better fitted by a Schechter function \citep{2015MNRAS.447.2085S}, 
-% indicating a prominent population of low $\lambda$ quasars is hidden by the flux-limited incompleteness.
+after luminosity bias correction \citep[e.g.,][]{2010AJ....140..546W}.
 For the low-$\lambda$ slope of $\alpha$ in the ERDF, we assign a Gaussian prior function with a mean value 
@@
 but the low-$z$ quasar samples support $-0.3 \lesssim \alpha \lesssim 0.3$ \citep[e.g., see Figure 21 in][]{2015MNRAS.447.2085S}.
-% considering the more significant obscuration of lower $\lambda$ quasars 
-%we assign a Gaussian prior, with the mean value $\mu_{\alpha}=0.$ and scatter $\sigma_{\alpha}=0.3$.
-
-%
-% 1. data: observational MF LF; describe quadratic error in Willott 2010
-The observed BHMF data is taken from \citetalias{2010AJ....140..546W}, where 
+
+The observed BHMF data is taken from \citet{2010AJ....140..546W} (hereafter, \citetalias{2010AJ....140..546W}), where 
 the virial BH mass measurements for 17 bright quasars at $z\simeq $ 6 are used.
-%rom the virial BH mass among $\sim$ 20 quasars at $z\approx$ 6.
-%they reconstruct the BHMF with the QLF and ERDF
-%extracted from the virial BH mass among $\sim$ 20 quasars at $z\approx$ 6. 
 Although the BHMF spans over $10^7 < \Mbh/\Msun <10^{10}$, the best constraint is given around 
@@
 
-% 3. posterior
-% Then evaluating the likelihood of the dataset reproducing the observed BHMF and QLF at $z=$ 6, 
-% the Markov chain of samples converges to the best-fit (maximum likelihood) parameters.
+% posterior
 Following the prior distribution functions, the four parameters are sampled to generate the synthetic 
@@
 The discrepancy between the model and observational data is evaluated with a $\chi^2$-value defined by
-%%%%%%%
-%    Eq. 8
-%%%%%%%
+%
 \begin{align}
-  \label{eq:chi2}
   \chi^2 = \sum_{x,i}
@@
 \end{align}
+%
 where $\Phi^{\rm mod}_{x,i}$ and $\Phi^{\rm obs}_{x,i}$ represent the modeled and observational value 
 on the \textit{i-}th bin of the BHMF ($x=\Mbh$) and QLF ($x=\Muv$), and $\Phi^{\rm err}_{x,i}$ is the corresponding error.
-% on the \textit{i-}th bin of the BHMF ($j=1$) and QLF ($j=2$), and $\Phi^{\rm err}_{i,j}$ is the corresponding error.
 Adopting 10 mass bins and 12 magnitude bins, we treat the errors from comparison both in the BHMF and QLF
 with a nearly equal weight.
-%te that the equal constraints from the BHMF and QLF are realized by extracting
-%comparable numbers of data points from $\Phi_\mathrm{M}$ and $\Phi_\mathrm{\Muv}$.
-% the constraint is actually insensitive to the choice of bin numbers. 
 The posterior distribution of the MCMC fitting is stabilized around the minimum value of $\chi^2$ (highest likelihood), 
@@
 
-% \red{KI: we need to explain why the peak of the 1D posterior distribution does not correspond to the best-fit case.
-% I think the peak value is not necessarily the same as the best-fit value. 
-% Also, we need to list the best-fit parameters somewhere in the text.}
+%%%%%%%
+%    Fig. 3
+%%%%%%%
+\begin{figure*}
+\centering
+\includegraphics[width=85mm]{f1_corner.pdf}
+\includegraphics[width=85mm]{f2_corner.pdf}
+\caption{
+Two dimensional posterior distribution of all the model parameters with $\fseed=0.1$ and 0.01, 
+along with the marginalized one dimensional projection.
+% and the two dimensional distribution between every two parameters. 
+The distribution of three parameters ($\tau$, $\lambda_0$, and $\alpha$) show single peaks,
+displaying the convergence of those parameters.
+The distribution of $\log\delta$ is relatively broader but suggests that the value of $\delta$
+is sufficiently low and thus the mass-dependent growth model is excluded.
+}
+\label{fig:contour}
+\vspace{5mm}
+\end{figure*}
+%
+
+We discuss the MCMC fitting results and compare the BHMF and QLF with those observed distribution functions.
+In Fig.~\ref{fig:contour}, we visualize the fitting results for each parameter in two-dimensional 
+posterior distribution for the case of $\fseed= 0.1$ (left) and $0.01$ (right), respectively.
+The three vertical dashed lines in the one-dimensional posterior distribution of each parameter
+correspond to 16\%, 50\%, and 84\% quantiles in the cumulative distribution, respectively.
+The best-fit values shown with the red lines are listed in Table~\ref{tab:best_fits},
+displaying consistency with the peaks in the one-dimensional distribution.
+%Note that the best-fit values may not overlap the 50\% quantile lines,
+%and the deviation are significant in asymmetric one-dimensional distribution.
+
+For the two cases, the best-fit solution consistently shows a small value of $\delta < 0.1$.
+This result favors the nearly exponential BH growth model with minor mass dependence (Eqs.~\ref{eq:mdot} and \ref{eq:f_M}).
+The typical duration of quasar activity is required to be $\tlife \simeq 20-30$ Myr for both the cases.
+This suggests that accreting seed BHs vary their growth speeds and their Eddington ratios 
+$\simeq 30-40$ times on average toward the cosmic time at $z\simeq 6$.
+The timescale of $\tlife$ is also related to the quasar lifetimes of $t_{\rm Q}\sim 1-10$ Myr, 
+which are estimated by the measurement of the physical extents of hydrogen Ly$\alpha$ proximity zones 
+observed in the rest-frame UV spectra \citep[e.g.,][]{2018ApJ...867...30E,2019ApJ...884L..19D}.
+More detailed comparison is discussed in \S\ref{sec:evol}.
 
@@
 
-\blue{
-In the following, we discuss the MCMC fitting results and compare the reproduced BHMF and QLF with observations.
-In Fig.~\ref{fig:contour}, we visualize the fitting results for each parameter in two-dimensional 
-posterior distribution for the case of $\fseed= 0.1$ (left) and $0.01$ (right), respectively.
-The three vertical dashed lines in the one-dimensional distribution of each parameter
-correspond to 16\%, 50\%, and 84\% quantiles in the cumulative distribution, respectively.
-The best-fit values shown in red thick lines are tabulated in Table.~\ref{tab:best_fits},
-displaying consistency with the peaks in the one-dimensional distributions.
-Note that the best-fit values may not overlap the 50\% quantile lines,
-and the deviation are significant in asymmetric one-dimensional distributions.
-The two-dimensional distributions show that the parameter pairs
-($\tau$, $\lambda_0$) and ($\lambda_0$ and $\alpha$) are negatively correlated.
-% wli : 1\sigma definition here?
-We later refer the $1\sigma$ scatter of a value (e.g., $\Phi_{M_\bullet}$) to the standard deviation of it calculated
-from randomly selected parameters from the sampling.
-% instead of the 16 and 84 percentiles here.
-}
-
-For both cases, the best-fit solution consistently shows a small value of $\delta < 0.1$.
-%, which is sufficiently small and should be marginalized out. 
-This result favors the nearly exponential BH growth model with minor mass dependence (Eq.~\ref{eq:mdot},~\ref{eq:f_M}).
-% In other words, on average the BH growth can be described as exponential, 
-% under the premise that the gas supply is episodical. 
-The typical duration of quasar activity is required to be $\tlife \simeq 20-30$ Myr for both the cases.
-%which is $\sim 64\%$ of the $e$-folding time for an exponential growth.
-This suggests that accreting seed BHs vary their growth speeds and their Eddington ratios 
-$\simeq 30-40$ times on average toward the cosmic time at $z\simeq 6$.
-The timescale of $\tlife$ also gives a lower bound of the quasar lifetimes of $t_{\rm Q}\sim 1-10$ Myr, 
-which are estimated by the measurement of the physical extents of hydrogen Ly$\alpha$ proximity zones 
-observed in the rest-frame UV spectra \citep[e.g.,][]{2018ApJ...867...30E,2019ApJ...884L..19D}.
-% \red{KI: we need to figure out if their $t_Q$ is the quasar age or lifetime, or something else?}
-More detailed comparison is discussed in \S\ref{sec:evol}.
-\red{KI: where is the discussion?}
+The best-fit parameters for the two cases of $\fseed$ reproduce the bulk properties of the BHMF and QLF at $z\sim 6$,
+despite the ten-fold difference in the seeding fraction.
+%The two parameters characterizing the ERDF are given as
+%$(\lambda_0,\alpha) = (0.89,0.12)$ and $(0.87,0.20)$ for $\fseed=0.1$ and $0.01$, respectively.
+With the fitted values for the ERDF, the fraction of super-Eddington accreting BHs is estimated as 
+$P(\lambda \geq 1)=0.064$ and $0.075$ for $\fseed=0.1$ and $0.01$, respectively.
+While the probability of rapid accretion in each cycle differs slightly between the two cases,
+multiple accretion episodes enlarge the difference and accelerate BH growth for the lower seeding fraction.
+Moreover, the case with $\fseed=0.01$ requires a higher value of $\delta (\simeq 0.055)$,
+promoting the growth of less massive BHs with $M_\bullet <10^8~\Msun$.
+Therefore, a larger fraction of seed BHs are delivered into the SMBH regime,
+and the ten-fold difference in $\fseed$ is nearly compensated.
+The characteristic Eddington ratio needs to be close to unity, otherwise the highest luminosity and BH mass
+in the model would differ from those in observations.
+On the other hand, the power-law index of $\alpha$ in the ERDF increases as the seeding fraction decreases,
+indicating that the fraction of active BHs with $\lambda \gtrsim 1$ is elevated. 
+Thus, with lower seeding fractions, the high-$z$ quasar assembly ought to experience more active growth phases to reproduce the observations.
 
@@
 \centering
-% \includegraphics[width=145mm]{fits_MF.png}
-\includegraphics[width=85mm]{f1ndraw60MF_spread.pdf}
+%\includegraphics[width=170mm]{fits_MF.png}
+\includegraphics[width=85mm]{f1ndraw60MF_spread.pdf}\hspace{3mm}
 \includegraphics[width=85mm]{f2ndraw60MF_spread.pdf}
@@
 \centering
-% \includegraphics[width=145mm]{fits_LF.png}
-\includegraphics[width=85mm]{f1ndraw60LF_spread.pdf}
+%\includegraphics[width=170mm]{fits_LF.png}
+\includegraphics[width=85mm]{f1ndraw60LF_spread.pdf}\hspace{3mm}
 \includegraphics[width=85mm]{f2ndraw60LF_spread.pdf}
@@
 
-%The best-fit parameters for the two cases of $\fseed$ reproduce the bulk properties of the BHMF and QLF at $z\sim 6$,
-%despite in the $\fseed=0.01$ case the number of the whole BH population is ten times lower than that with $\fseed=0.1$.
-The two parameters characterizing the ERDF are given as
-$(\lambda_0,\alpha) = (0.89,0.12)$ and $(0.87,0.20)$ for $\fseed=0.1$ and $0.01$, respectively.
-%We note that the total number of BHs differs by a factor of ten between the two cases.
-With those values, the fraction of super-Eddington accreting BHs is estimated as $P(\lambda>1)=0.064$ and 0.075.
-While the probability of rapid accretion in each cycle differs slightly between the two cases,
-multiple accretion episodes enlarge the difference and enable more efficient BH growth for the lower seeding fraction.
-Moreover, the lower seeding-fraction case requires a higher value of $\delta (\simeq 0.055)$, accelerating 
-the growth of less massive BHs with $M_\bullet <10^8~\Msun$.
-Therefore, a larger fraction of seed BHs are delivered into the SMBH regime,
-% given the best fit values of $\delta=(0.001,0.055)$ for the two $\fseed$ cases,
-% the higher $\delta$ value enhances the growth of small BHs with $M_\bullet <10^8~\Msun$ in the $\fseed=0.01$ case,
-% so that massive BHs are produced with number densities similar to that in the $\fseed=0.1$ case,
-and the ten-fold difference in $\fseed$ is nearly compensated.
-The characteristic Eddington ratio needs to be close to unity, otherwise the highest luminosity and BH mass
-in the model would differ from those in observations.
-On the other hand, the power-law index of $\alpha$ in the ERDF increases as the seeding fraction decreases,
-indicating that fraction of active BHs with $\lambda \gtrsim 1$ is elevated. 
-Thus, with lower seeding fractions, the high-$z$ quasar assembly ought to experience more active growth phases to reproduce the observations.
-
-% Next, we demonstrate that the parameters are inferred to be reasonable fits consistent with the observational data of both of the BHMF and QLF.
 In Fig.~\ref{fig:fitmf}, we show the total BHMF at $z=$ 6 reproduced by the best-fit parameters for 
-$\fseed = 0.1$ (left) and $0.01$ (right) as well as the $1\sigma$ spread.
+$\fseed = 0.1$ (left) and $0.01$ (right) as well as the statistical error, 
+which is defined as the $1\sigma$ standard deviation calculated from randomly selected parameters from the sampling.
 For comparison, we present the BHMF inferred by \citetalias{2010AJ....140..546W} along with the statistical errors.
@@
 at $M_\bullet \gtrsim 10^7~(3\times 10^7)~\Msun$ for $\fseed = 0.1 ~(0.01)$.
+The total mass budget of the entire BH population is dominated by BHs with the characteristic mass (see also Section~\ref{sec:cosm}). 
 The discrepancy between the model and observational data becomes larger at the high- and low-mass end,
 reflecting poor constraints on the BHMF from the current observations.
-%Therefore, both wider-field and deep surveys are required to determine the shape of the BHMF
-%The BHMF data put more constraints in the fitting procedure, and help the fitting converge.
-%However, a complete BHMF is necessary for better constraints, especially the low-mass end, 
-%which inherit more of the seeding information during a short growth time.
-The differences at the two extreme ends become smaller with the lower seeding fraction of $\fseed = 0.01$.
-This is because the progenitors of $z=6$ BHs with $10^{7-8}~\Msun$ were the most abundant BH population 
-in the seeding epochs (i.e., a flatter slope of the BHMF; see Fig.~\ref{fig:seedmf}) and mass growth for BHs heavier than 
-$\sim 10^8~\Msun$ is suppressed owing to the high value of $\delta~(\simeq 0.055)$.
-
-Fig.~\ref{fig:fitlf} presents the QLFs at $z=6$ reproduced by the best-fit parameters as well as the $1\sigma$ spreads.
-The solid and dashed curve is the {\it unobscured} QLF %(excluding a contribution from obscured quasars)
-and the {\it intrinsic} QLF (including both obscured and unobscured quasars), respectively.
-For comparison, we overlay the observational data used for the fitting and the QLF parametrized with 
-a double power-law shape obtained by \citetalias{2018ApJ...869..150M} (dotted curve).
-The best-fit unobscured QLF is consistent with the observed one at $-29~{\rm mag} \lesssim \Muv \lesssim -25~{\rm mag}$,
-but overproduces fainter quasars at $\Muv\gtrsim -24~{\rm mag}$.
-%, reflecting both the less constraints from observational data in the faint end,
-%and the difficulty of reproducing such a small population of low-luminosity quasars based on our seeding and growth model.
-As seen in the BHMF, the difference between the model and observational data at the faint end becomes smaller with
-the lower seeding fraction.
-Since the progenitors of those faint quasars were seed BHs located around the peak of the mass distribution,
-those BHs naturally produces a flatter slope of the QLF at the faint end.
-In addition, we show upper bounds of the faint quasar abundance at $\Muv\gtrsim -22~{\rm mag}$ \citep[green symbols;][]{2022NatAs...6..850J}
-%, an upper limit of the faint end QLF is provided, % by non-detection of faint quasars
-based on a search for point sources in the survey fields of the Hubble Space Telescope (HST).
-Our unobscured QLF lies within the constraints.
-
-Quasar observations in X-rays also provide 
-useful constraints on the intrinsic population because of the different quasar selection criteria and less obscuration effects in X-rays.
-Based on the X-ray selected faint quasars, \cite{2015A&A...578A..83G,2019ApJ...884...19G} reported higher number densities of faint quasars
-compared to those extrapolated from the rest-UV observations (e.g., the dotted curve by \citetalias{2018ApJ...869..150M}) 
-down to the faint end of $\Muv\gtrsim -22~{\rm mag}$ (orange symbols).
-%In addition to the systematic difference in the quasar identification methods,
-%the X-ray observation should suffer less dust obscuration (see \S~\ref{sec:LF}),
-%thus detect more quasars in the faint end.
-%We also show the intrinsic QLF predicted by our best-fit parameters,
-%which is without imposing obscuration thus representing the upper bound of detectable quasar numbers.
-Our best-fitted intrinsic QLF (dashed curve) is broadly consistent with the faint-end QLF from the X-ray observations within the errors,
-though the model predicts slightly lower numbers at $\Muv\gtrsim -21$ mag.
-% outshining effect
-From another point of view, the discrepancy between the UV and X-ray QLFs at the faint end would be explained by the fact that 
-only bright quasars outshining their host galaxies can be identified as point-like sources in the rest-UV quasar selection 
-(\citetalias{2018ApJ...869..150M}; \citealt{2020MNRAS.495.2135N,2020MNRAS.494.1771A,2021MNRAS.502.2757O,2021MNRAS.502..662B,2022arXiv220712282K}).
-However, at the faint end at $\Muv\gtrsim -24$ mag, extended sources such as the brightest galaxies at $z\sim 6$ 
-dominate over quasars in number at the same UV magnitude \citep{2022ApJS..259...20H}.
-Thus, the current observations might miss quasars embedded in extended galaxy populations. 
-% We do not take into account of this effect in the QLF correction,
-% but we notice this important caveat and provide the galaxy number density information 
-% in the higher-$z$ QLF predictions (see \S~\ref{sec:qlfglf}).
-We leave this issue as an important caveat in high-$z$ quasar observations.
-
-% In Figs.~\ref{fig:fitmf} and \ref{fig:fitlf}, we show the total BHMF and unobscured (type-I) QLF at $z=$ 6 
-% reproduced by the best-fit parameters as well as the $1\sigma$ spread.
-% % where the QLF model excludes a contribution from obscured quasars, 
-% % yielding the {\it observed} QLF for type-I AGN populations.
-% The total BHMF indicated in \citetalias{2010AJ....140..546W} and QLF from \citetalias{2018ApJ...869..150M} 
-% with statistical errors are also overlaid for comparison.
-% We note that \citetalias{2010AJ....140..546W} constructed the BHMF using quasar samples with 
-% $10^8~\Msun \lesssim \Mbh \lesssim 3\times 10^9~\Msun$.
-% Our best-fit BHMF model well agrees with their observational constraints in this mass range.
-% The QLF fitting results are also consistent with the observed one over $-29~{\rm mag} \lesssim \Muv \lesssim -25~{\rm mag}$,
-% but seems to overproduce the abundance of fainter quasars at $\Muv>-24~{\rm mag}$.
-% % due to the lack of fine tuning by the model parameters in the low mass range, 
-% The difference at the fainter end tends to be alleviated with the seeding fraction lowered ($\fseed = 0.01$),
-% because the progenitors of $z=6$ BHs with $10^{7-8}~\Msun$ (or similarly, 
-% $-22~{\rm mag} \lesssim \Muv \lesssim -24~{\rm mag}$) were less massive seed BHs with $\sim 10^4~\Msun$,
-% which is closer to the peak of the seed mass distribution (see Fig.~\ref{fig:seedmf}).
-% Those BH population naturally produces a flatter slope of the QLF (and BHMF) at the faint (low-mass) end.
-% Overall, the parameters are inferred to be reasonable fits consistent with the observational data.
-
-%\vspace{2mm}
-\section{Cosmological evolution of BH mass and quasar luminosity function}\label{sec:cosm}
-%\red{KI: shall we discuss the $z$-dependence of the BHMF and QLF?
-%Don't need to repeat calculations. Just using the same parameters with 1sigma scatter?
-%Showing $\rho_{\bullet}(z)$ in $\Msun ~ {\rm Mpc}^{-3}$, which is the integrant of BHMF, would be interesting}
+%The differences at the two extreme ends become smaller with the lower seeding fraction of $\fseed = 0.01$.
+%This is because the progenitors of $z=6$ BHs with $10^{7-8}~\Msun$ were the most abundant BH population 
+%in the seeding epochs (i.e., a flatter slope of the BHMF; see Fig.~\ref{fig:seedmf}) and mass growth for BHs heavier than 
+%$\sim 10^8~\Msun$ is suppressed owing to the high value of $\delta~(\simeq 0.055)$.
 
@@
 \centering
-% \includegraphics[width=175mm]{BHMF_rhoz1.png}
-\includegraphics[width=85mm]{MF.pdf}
-\includegraphics[width=85mm]{rhoM_comb.pdf}
+%\includegraphics[width=175mm]{BHMF_rhoz1.png}
+\includegraphics[width=85mm]{MF.pdf}\hspace{5mm}
+\includegraphics[width=81mm]{rhoM_comb.pdf}
 \caption{
@@
 The dashed-dotted line and open square symbols show the results from \citet{2022MNRAS.513..670N}.
-The upper bound of accreted BH mass density from \citet{2013ApJ...778..130T} is denoted by black circles.
+The upper bound of accreted BH mass density from \citet{2013ApJ...778..130T} is denoted by black arrows.
 % The evolutionary trend can be approximated as $\rho_\bullet (z) \propto 10^{k_M z}$, where $k_M\simeq -0.68$.
@@
 \label{fig:BHMF_rhoz}
-\vspace{0mm}
+\vspace{5mm}
 \end{figure*}
 
-Based on the constraint from $z\sim 6$ quasar observations, the best-fit model from the MCMC realizations enables
-us to probe the statistical aspect of BH evolution at higher redshifts.
-%As a fiducial case, we take the best-fit parameters of BH growth for our $\fseed=$ 0.01 model,
-%where $\tlife=18.76$ Myr, $\delta=0.055$, $\lambda_0=0.87$, and $\alpha=0.20$.
-We apply the result to construct BHMFs and QLFs at $z\geq 6$ and give implications for
-the future explorations of high-$z$ quasars.
-
-\subsection{Black Hole Mass Functions}
-
-In the left panel of Fig.~\ref{fig:BHMF_rhoz}, we show the predicted BHMFs at five different redshifts of $z=6-10$
-for $\fseed=0.1$ (solid) and $0.01$ (dashed).
-Since the mass distribution of seed BHs is already established at $M_\bullet \lesssim 2\times10^5~\Msun$ earlier on ($z\gtrsim 17$),
-the high-mass tail of the BHMF is built up owing to a fraction $\fseed$ of all the seeds.
-Therefore, the case with $\fseed=0.1$ yields the number of growing seeds ten times higher compared to the case with $\fseed =0.01$,
-making the difference of the abundance at $M_\bullet \sim 10^{5-6}~\Msun$\footnote{
-For each case, a fraction $(1-\fseed)$ of BHs are assumed to keep the original mass at birth without subsequent growth.}.
-For BHs with $M_\bullet \gtrsim 10^7~\Msun$, which is potentially accessible by quasar observations,
-the BHMFs can be characterized with a double power-law function,
-similar to lower-$z$ quasar populations \citep[e.g.,][]{2013ApJ...764...45K,2015MNRAS.447.2085S}.
-Toward lower redshifts, the number density of BHs in the high-mass tail increases
-and SMBHs with $M_\bullet \gtrsim 10^9~\Msun$ emerge owing to efficient growth of the massive BH population.
-Constrained by the \citetalias{2010AJ....140..546W} BHMF with $M_\bullet \simeq 10^8-3\times 10^9~\Msun$ at $z=6$,
-the two cases produce similar shape of mass distribution in this mass and redshift range (see \S~\ref{sec:fitting_result}),
-while the difference in the two BHMF shapes is profound toward the low mass range of $M_\bullet \lesssim 10^7~\Msun$.
-%The BH abundance and shape of the mass distribution at $10^5 \lesssim M_\bullet/\Msun \lesssim 10^7$ depend on the seeding fraction,
-%while the distributions converge at $M_\bullet \gg 10^7~\Msun$ toward $z= 6$. 
-This result suggests that the information on the seeding process would still remain in the low mass regime of $M_\bullet \lesssim 10^7~\Msun$.
-%
-%The different seeding fraction varies the characteristic BH mass where the BHMF slope is close to $\alpha_{M_\bullet}\simeq -1$,
-%i.e., the typical masses which dominate the cumulative mass density (see \S~\ref{sec:fitting_result}). 
-% the difference is also shown by the mass ranges where the slope of BHMF is close to $\alpha_{M_\bullet}\simeq -1$,
-%i.e., the typical masses which dominate the cumulative mass density (see \S~\ref{sec:fitting_result}). 
-%In the case of $\fseed=0.01$, this typical mass range is higher, despite the integrated mass density is lower than that with $\fseed=0.1$.
-
-In the right panel of Fig.~\ref{fig:BHMF_rhoz}, we present the cumulative mass density of BHs in a comoving volume
-for $\fseed=0.1$ (solid) and $0.01$ (dashed),
-defined by the integration of the BHMF as
-%
-\begin{equation}
- \rho_\bullet(z)=\int_{\mathcal{I}} \Phi_{\Mbh} (z) \Mbh ~\D \log \Mbh.
-\end{equation}
-%
-Here, we consider three mass ranges: $M_\bullet \leq 10^6~\Msun$ (blue), $10^6~\Msun < M_\bullet < 10^8~\Msun$ (orange),
-and $M_\bullet \geq 10^8~\Msun$ (green).
-Overall, the mass density of the heaviest BHs quickly grows toward lower redshifts,
-while the mass density barely evolves for the lightest BHs.
-At $z\lesssim 7-8$, more massive BHs with $\gg 10^6~\Msun$ begin to dominate the total mass budget of the entire BH population,
-promoting the so-called downsizing or anti-hierarchical evolution of massive BHs 
-in terms of mass occupation \citep[e.g.,][]{2014ApJ...786..104U}.
-Moreover, as shown in the left panel, the mass-density evolution is affected by the choice of the seeding fraction more substantially
-for less massive BHs that keep the information on their initial conditions at birth.
+Fig.~\ref{fig:fitlf} presents the QLFs at $z=6$ reproduced by the best-fit parameters as well as the $1\sigma$ spreads
+for $\fseed = 0.1$ (left) and $0.01$ (right).
+The solid and dashed curve is the {\it unobscured} and {\it intrinsic} QLF, respectively.
+The latter one includes both obscured and unobscured quasars.
+For comparison, we overlay the observational data taken from \citetalias{2018ApJ...869..150M} in blue
+and their parametric QLF with a double power-law function (dotted curve).
+Our best-fit unobscured QLF is consistent with the observed one at $-29~{\rm mag} \lesssim \Muv \lesssim -25~{\rm mag}$,
+but overproduces fainter quasars at $\Muv\gtrsim -24~{\rm mag}$.
+As seen in the BHMF, the difference between the model and observational data at the faint end becomes smaller with
+the lower seeding fraction.
+Since the progenitors of those faint quasars were seed BHs located around the peak of the mass distribution,
+those BHs naturally produces a flatter slope of the QLF at the faint end.
+In addition, we show upper bounds of the faint quasar abundance at $\Muv\gtrsim -22~{\rm mag}$ \citep[green;][]{2022NatAs...6..850J}
+based on a search for point sources in the survey fields of the Hubble Space Telescope (HST).
+Our unobscured QLF lies within the constraints.
+
+Quasar observations in X-rays also provide 
+useful constraints on the intrinsic population because of less obscuration in X-rays.
+Based on the X-ray selected faint quasars, \cite{2019ApJ...884...19G} reported a number density of 
+faint quasars in orange, which is substantially higher than that expected from extrapolation of the rest-UV based QLF by 
+\citetalias{2018ApJ...869..150M} (dotted curve) down to the faint end of $\Muv\gtrsim -22~{\rm mag}$.
+In Fig.~\ref{fig:fitlf}, we take their $z=5.55$ luminosity function correcting for redshift evolution 
+with a scale factor of $10^{-0.72\Delta z}$ \citep{2016ApJ...833..222J}, where $\Delta z=0.45$.
+Our best-fitted intrinsic QLF (dashed curve) is broadly consistent with the faint-end of the X-ray based QLF within the errors.
+From another point of view, the discrepancy between the UV and X-ray QLFs at the faint end would be explained by the fact that 
+only bright quasars outshining their host galaxies can be identified as point-like sources in the rest-UV quasar selection 
+(\citetalias{2018ApJ...869..150M}; \citealt{2020MNRAS.495.2135N,2020MNRAS.494.1771A,2021MNRAS.502.2757O,2021MNRAS.502..662B,2022arXiv220712282K}).
+However, at the faint end at $\Muv\gtrsim -24$ mag, extended sources such as the brightest galaxies at $z\sim 6$ 
+dominate over quasars in number at the same UV magnitude \citep{2022ApJS..259...20H}.
+Thus, the current observations might miss quasars embedded in extended galaxy populations. 
+We leave this issue as an important caveat in high-$z$ quasar observations.
+
+\vspace{2mm}
+\section{Cosmological evolution of BH mass and quasar luminosity function}\label{sec:cosm}
 
@@
 \tablewidth{0pt} 
-\tablecaption{Detection Number of Quasars Estimated for Future Surveys \label{tab:N_detect}} %! reference indexing
+\tablecaption{\blue{Detection Number of Quasars Estimated for Future Surveys} \label{tab:N_detect}} %! reference indexing
 \tablehead{
@@
 
-%The mass density predicted by the $\fseed=0.1$ case is overall higher than that with $\fseed=0.01$.
-%However, with $\fseed=0.01$, BHs in the low mass range quickly evolve into higher masses,
-%leading to convergent results in the two cases at $z\sim 6$.
-For comparison, we overlay the BH mass density evolution with $10^6<M_{\bullet}<10^8$, and $M_\bullet>10^8~\Msun$
-obtained from the cosmological simulations in \citet{2022MNRAS.513..670N} (dashed-dotted line and open square symbols).
+Based on the constraint from $z\sim 6$ quasar observations, the best-fit model from the MCMC realizations enables
+us to probe the statistical aspect of BH evolution at higher redshifts.
+We apply the result to construction of BHMFs and QLFs at $z\geq 6$ and give implications for
+the future explorations of high-$z$ quasars.
+
+\subsection{Black Hole Mass Functions}
+
+In the left panel of Fig.~\ref{fig:BHMF_rhoz}, we show the predicted BHMFs at five different redshifts of $z=6-10$
+for $\fseed=0.1$ (solid) and $0.01$ (dashed).
+As shown in Fig.~\ref{fig:seedmf}, the mass distribution of seed BHs develops up to $M_\bullet \lesssim 2\times10^5~\Msun$ by $z\gtrsim 17$.
+Thus, the high-mass tail of the BHMF is produced owing to subsequent growth of seed BHs (i.e., the fraction $\fseed$ of all the seeds).
+In fact, the case with $\fseed=0.1$ yields the number density of those growing seeds ten times higher than that with $\fseed =0.01$,
+making the difference in the BH abundance at $M_\bullet \sim 10^{5-6}~\Msun$.
+%\footnote{For each case, a fraction $(1-\fseed)$ of BHs are assumed to keep the original mass at birth without subsequent growth.}.
+This result suggests that the information on the seeding process still remains in the low mass regime.
+Toward lower redshifts, heavier BHs with $\gtrsim 10^7~\Msun$ emerge owing to efficient growth
+and thus the number density of such massive BHs in the high-mass tail increases.
+Since the BHMF shape at $z=6$ is constrained by \citetalias{2010AJ....140..546W},
+% BHMF with $M_\bullet \simeq 10^8-3\times 10^9~\Msun$ at $z=6$,
+the two cases reproduce similar shape of mass distribution at $M_\bullet \simeq 10^8-3\times 10^9~\Msun$ (see Fig.~\ref{fig:fitmf}).
+As a result, the BHMF at $M_\bullet \gtrsim 10^7~\Msun$, which is potentially accessible by quasar observations,
+can be characterized with a double power-law function, similar to lower-$z$ quasar populations \citep[e.g.,][]{2013ApJ...764...45K,2015MNRAS.447.2085S}.
+%while the difference in the two BHMF shapes is profound toward the low mass range of $M_\bullet \lesssim 10^7~\Msun$.
+%The BH abundance and shape of the mass distribution at $10^5 \lesssim M_\bullet/\Msun \lesssim 10^7$ depend on the seeding fraction,
+%while the distributions converge at $M_\bullet \gg 10^7~\Msun$ toward $z= 6$. 
+%This result suggests that the information on the seeding process would still remain in the low mass regime of $M_\bullet \lesssim 10^7~\Msun$.
+%
+%The different seeding fraction varies the characteristic BH mass where the BHMF slope is close to $\alpha_{M_\bullet}\simeq -1$,
+%i.e., the typical masses which dominate the cumulative mass density (see Section~\ref{sec:fitting_result}). 
+% the difference is also shown by the mass ranges where the slope of BHMF is close to $\alpha_{M_\bullet}\simeq -1$,
+%i.e., the typical masses which dominate the cumulative mass density (see Section~\ref{sec:fitting_result}). 
+%In the case of $\fseed=0.01$, this typical mass range is higher, despite the integrated mass density is lower than that with $\fseed=0.1$.
+
+In the right panel of Fig.~\ref{fig:BHMF_rhoz}, we present the cumulative mass density of BHs in a comoving volume
+for $\fseed=0.1$ (solid) and $0.01$ (dashed),
+defined by the integration of the BHMF as
+%
+\begin{equation}
+ \rho_\bullet(z)=\int_{\mathcal{I}} \Phi_{\Mbh} (z) \Mbh ~\D \log \Mbh.
+\end{equation}
+%
+Here, we consider three mass ranges: $M_\bullet \leq 10^6~\Msun$ (blue), $10^6~\Msun < M_\bullet < 10^8~\Msun$ (orange),
+and $M_\bullet \geq 10^8~\Msun$ (green).
+Overall, the mass density of the heaviest BHs quickly grows toward lower redshifts,
+while the mass density barely evolves for the lightest BHs.
+At $z\lesssim 7-8$, more massive BHs with $\gg 10^6~\Msun$ begin to dominate the total mass budget of the entire BH population,
+promoting the so-called downsizing or anti-hierarchical evolution of massive BHs 
+in terms of mass occupation \citep[e.g.,][]{2014ApJ...786..104U}.
+Note that the characteristic mass in the BHMF (i.e., $\alpha_{M_\bullet}=-1$) is $M_\bullet \simeq 10^7~(3\times 10^7)~\Msun$ for 
+$\fseed=0.1~(0.01)$.
+Moreover, as shown in the left panel, the mass-density evolution is affected by the choice of the seeding fraction more substantially
+for less massive BHs that keep the information on their initial conditions at birth.
+
+For comparison, we overlay the BH mass density evolution with $10^6<M_{\bullet}/\Msun<10^8$
+%, and $M_\bullet>10^8~\Msun$
+obtained from the cosmological simulations in \citet{2022MNRAS.513..670N} (dashed-dotted curve).
 At $z\lesssim 7$, our results are in overall good agreement with those simulation results.
-However, our models predict more $10^{6-8}~\Msun$ BHs emerging at $z\sim 10-8$,
-owing to the joint effect of our seeding and growth prescription that allows seed formation earlier on 
-and (modest) super-Eddington episodes.
-%the former produces BH seeds earlier than their stringent seeding criteria,
-%and the latter allows super-Eddington episodes occur which lead to rapid BH growth.
+However, our models predict a larger number of $10^{6-8}~\Msun$ BHs emerging at $z\sim 10-8$,
+owing to our model prescription that allows BH seed formation earlier on and (modest) super-Eddington episodes.
 Furthermore, the measured unresolved fraction of the cosmic X-ray background constrains
 the global accretion history of massive BHs at $z>5$ \citep{2012A&A...545L...6S,2013ApJ...778..130T}.
-Upper bounds on the accreted-mass density onto massive BHs (red triangles) prohibits overproduction of low mass BHs at cosmic dawn.
+Upper bounds on the accreted-mass density onto massive BHs (black arrows) prohibits overproduction of low mass BHs at cosmic dawn.
 Our quasar sample in the biased, overdense region of the universe (haboring DM halos with $\Mh\gtrsim 10^{11}~\Msun$) 
@@
 \citep[e.g.,][]{2002ApJ...568...52W,2008MNRAS.383..615N,2008MNRAS.388.1792N,2010MNRAS.406.2267F}
-\footnote[3]{
+\footnote[4]{
 In fact, this redshift dependence leads to a halo-mass growth rate of $\D \left(\ln \Mh \right) / \D t \propto(1+z)^{5/2}$,
@@
 \centering
-\includegraphics[width=85mm]{LF_spreadz7.pdf}%\hspace{5mm}
-\includegraphics[width=85mm]{LF_spreadz8.pdf}\\%\vspace{5mm}
-\includegraphics[width=85mm]{LF_spreadz9.pdf}%\hspace{5mm}
+\includegraphics[width=85mm]{LF_spreadz7.pdf}\hspace{2mm}
+\includegraphics[width=85mm]{LF_spreadz8.pdf}\\\vspace{5mm}
+\includegraphics[width=85mm]{LF_spreadz9.pdf}\hspace{2mm}
 \includegraphics[width=85mm]{LF_spreadz10.pdf}
@@
 
-Next, we show our prediction of $z=6-10$ unobscured QLFs taken from the BH growth model.
-%On the other hand, the statistics of BH masses together with the ERDF in their growth history can rebuild quasar luminosity functions across cosmic time,
-%which is interesting to be probed with future observations.
-In Fig.~\ref{fig:LFs}, we divide the cosmological QLF evolution into four different epochs; (a) $z\simeq 7$, (b) $z\simeq 8$, (c) $z\simeq 9$, and (d) $z\simeq 10-13$.
-The black solid and dashed curves present the QLF for the unobscured population (i.e., type-I AGNs, same as those in Fig.~\ref{fig:QLFmag_z})
-and the whole population (i.e., type-I and type-II AGNs).
-The AGN obscured fraction based on X-ray samples \citep{2014ApJ...786..104U} is applied to faint objects, 
+Fig.~\ref{fig:LFs} presents our prediction of QLFs at $z>6$ taken from the BH growth model.
+We divide the cosmological QLF evolution into four different epochs; (a) $z\simeq 7$, (b) $z\simeq 8$, (c) $z\simeq 9$, and (d) $z\simeq 10-13$.
+The black solid and dashed curve presents the QLF for the unobscured population 
+and entire population (including unobscured and obscured quasars), respectively.
+The obscured fraction based on X-ray samples \citep{2014ApJ...786..104U} is applied to faint objects, 
 but the correction factor is highly uncertain at the faint end of $\Muv\gtrsim -20$ mag.
@@
 From higher to lower redshifts, the number density of luminous quasars increases and the bright-end of the distribution rises.
-% sampled in \citet{2014ApJ...786..104U},
-%we emphasize that the observed (Type I) QLF after the current obscuration prescription can be highly uncertain in the faint end,
-%ßwhich is to be improved by the future equipments.
-% More thorough studies on the high-$z$ quasar obscuration by upcoming equipments will improve the understanding on this aspect.
-%We also produce the intrinsic (Type I and Type II) luminosity function without obscuration effects.
-%The QLF emgerging from high redshifts quickly evolves toward brighter luminosity 
-%with the number of quasars increases as BHs grow.
-We also overlay the expected depths and survey volumes of upcoming near-infrared surveys by
+
+\blue{
+We overlay the expected depths and survey volumes of upcoming near-infrared surveys by
 Euclid \citep{2011arXiv1110.3193L} and RST \citep{2019arXiv190205569A}.
-Only their Wide survey layers are considered here.
-Table.~\ref{tab:N_detect} summarizes the coverage and limiting magnitudes in each survey,
-and list the expected number of quasar detection.
-Euclid will identify quasars up to $z\sim 8$ and discover $O(100-1000)$ quasars at $z\simeq 7-8$.
-The RST will be able to explore the very faint ($\Muv>-22$ mag) but abundant quasar population even at $z>10$, in principle,
-after subtracting galaxy contaminants.
-\blue{
-Studies that take into account contamination from MLT dwarfs and compact early-type galaxies and quasar selction method
-have confirmed the capability of these surveys in searching high-$z$ quasars \citep{2019A&A...631A..85E,2019BAAS...51c.121F}.
-With the simplified assumption of $100\%$ selection function against contaminants,
-our predicted yield of high-$z$ quasars for the Euclid wide survey is a few times higher than that by \citet{2019A&A...631A..85E}.
-Therefore, our estimation should represent an upper bound of the potentially detectable quasar population.
-}
-
-%will be crucial to construct the LF data for high-$z$ quasars and galaxies,
-%categorizing them by spectroscopic diagnostics.
-%We show the detection limit of these surveys at each redshift in Fig.~\ref{fig:LFs},
-%demonstrating their capability of optimizing high-$z$ galaxy and quasar observations.
-%The adopted survey parameters is shown in Table.~\ref{tab:N_detect}.
-%The depths of detection will be pushed down to $\Muv\lesssim -20$,
-%which is able to uncover the critical luminosities at which the numbers of galaxies and quasars are comparable.
-%The number of high-$z$ quasars are also predicted at each redshift (Table.~\ref{tab:N_detect}),
-%with the assumption of the survey volume with $\Delta z =1$ and 100\% completeness.
-%The large sample of objects at those high redshifts will shed light on
-%the early coevolution of galaxies and BHs in a statistically unbiased way.
+Here we consider only their wide-area survey layers because other survey programs are not suitable for quasars at $z\gtrsim 7$.
+Table~\ref{tab:N_detect} summarizes the coverage and limiting magnitudes in each survey
+and lists the expected detection number of quasars.
+In priniciple, Euclid will identify quasars up to $z\sim 8$ and discover $O(100-1000)$ quasars at $z\simeq 7-8$.
+The RST will potentially be able to explore the very faint ($\Muv>-22$ mag) but abundant quasar population even at $z\gtrsim 10$. 
+%in principle, after subtracting galaxy contaminants.
+Note that we do not take into account selection criteria to differentiate quasars from other astrophysical sources such
+as Galactic brown dwarfs, strong Balmer-break galaxies, and extremely dusty star-forming galaxies at intermediate redshifts.
+Therefore, our estimate in Table~\ref{tab:N_detect} gives an upper bound of the number of detectable high-$z$ quasars.
+Nevertheless, this simplified assumption yields $\approx 3-7$ times higher values than those predicted by \citet{2019A&A...631A..85E}.
+%Studies that take into account contamination from MLT dwarfs and compact early-type galaxies and quasar selction method
+%have confirmed the capability of these surveys in searching high-$z$ quasars \citep{2019A&A...631A..85E,2019BAAS...51c.121F}.
+%With the simplified assumption of $100\%$ selection function against contaminants,
+%our predicted yield of high-$z$ quasars for the Euclid wide survey is a few times higher than that by \citet{2019A&A...631A..85E}.
+%Therefore, our estimation should represent an upper bound of the potentially detectable quasar population.
+}
+% me:On the other hand, we the selection effect to miss some quasars, especially the faint ones. Our prediction is
 
 We also show the galaxy UV luminosity function in each panel
-%Thanks to numerous efforts in the high-$z$ galaxy observation field,
-%we overlay the galaxy UV luminosity function at each redshift,
-along with the fitting functions in a Schechter (dotted curves) and double power law (dashed-dotted curves) shape extended to the brighter end
-\citep{2021AJ....162...47B,2022ApJS..259...20H,2020MNRAS.493.2059B,2022arXiv220712356D,2013MNRAS.432.2696M,2019ApJ...883...99S,
-Harikane_2022b,2018ApJ...867..150M,Harikane_2022c,2016ApJ...819..129O,2022arXiv220709434N}.
-Compared to our QLF predictions, those galaxies prevail in the faint end at all these redshifts and the number decreases toward the luminous end.
-The large number of galaxies with $\Muv\gtrsim -23$ mag makes it difficult to probe rare quasars among those faint objects.
+along with the fitting functions in a Schechter (dotted) and double power law (dashed-dotted) shape extended to the brighter end
+\citep{2013MNRAS.432.2696M, 2016ApJ...819..129O, 2018ApJ...867..150M, 2019ApJ...883...99S, 2020MNRAS.493.2059B,
+2021AJ....162...47B, 2022arXiv220712356D,
+2022ApJS..259...20H, Harikane_2022b, Harikane_2022c, 2022arXiv220709434N}.
+Galaxies at $\Muv\gtrsim -23$ mag dominate quasars in number at all the redshifts and make it 
+difficult to identify rare quasars among those faint objects.
 Since extrapolated galaxy LFs with a Schechter shape decline quickly with the luminosity increasing,
-the galaxy LFs intersect with the QLFs at $\Muv \sim -23$, $-24$, and $-25$ mag at redshifts $z=7-8$, $9$, and $10-13$, respectively.
-On the other hand, if the bright end of the galaxy LFs are extended with a power law, the corresponding crossing magnitude shifts to $\Muv\sim-26$, $-25$, and $\ll -30$ mag.
-%Therefore the galaxy contamination effect on quasar observations still remains model-dependent. 
-Therefore, future deep and wide surveys will lead to significant progress understanding the relative 
-contribution of both populations to astrophysical phenomena e.g., the ionizing photon budget in the cosmic dawn.
+the abundance of galaxies and quasars becomes comparable around $\Muv \sim -23$ mag ($z=7-8$), $-24$ mag ($z=9$), and $-25$ mag ($z=10-13$).
+On the other hand, if the bright end of the galaxy LFs are extended with a power law, those critical UV magnitudes shift to 
+$\Muv\sim-26$, $-25$, and $\ll -30$ mag for each redshift range.
+Future deep and wide surveys will unveil the relative contribution of the two populations and impacts on cosmic reionization.
 
@@
 In Fig.~\ref{fig:QLFmag_z}, we present the quasar number density as a function of redshift for 
-the case of $\fseed =0.1$ (solid) and $0.01$ (dashed).
+$\fseed =0.1$ (solid) and $0.01$ (dashed).
 Each curve corresponds to the value at a UV magnitude from $\Muv=-27$ mag to $-23$ mag.
@@
 The evolutionary trend can be fitted as $\propto 10^{k_{\rm L}z}$,
-\blue{
-where $k_{\rm L}\approx -0.91$ and $-0.62$ for the brightest and faintest population
+where $k_{\rm L}\simeq -0.91$ and $-0.62$ for the brightest and faintest population
 at $z\gtrsim 6$, respectively.
-Specially for $\Muv=-26$ mag, our models predict $k_\mathrm{L} \simeq -0.84$.
-}
-Observationally, a rapid decay of luminous quasar (with $\Muv<-26$ mag) number density toward higher redshifts is found by previous studies
-\citep[e.g.,][]{2001AJ....122.2833F,2013ApJ...768..105M,2016ApJ...833..222J,2019ApJ...884...30W},
-which show $k_{\rm L}= -0.47$ and $-0.72$ from the analysis of quasar samples at $z\simeq 3-5$ and $z\simeq 5-6$, respectively.
-% Recently, a steeper decline of luminous quasar number density toward higher redshifts is proposed by \citet{2019ApJ...884...30W},
-% suggesting $k_{\rm L}=-0.78$ at $6\lesssim z \lesssim 7$.
-The rapid decline toward higher redshifts shows overall agreement with our model results.
-Our model is characterized by the episodic natures of BH accretion with a finite value of
-$\tau ~(\simeq 20~{\rm Myr})$, in order to match the statistical properties of high-$z$ quasars.
-We also note that the tendency would be explained by the rarity of massive quasar-host halos at higher redshifts,
-non-constant radiative efficiencies that covert the BH growth rate into the luminosity, or some combination of these effects
-\citep[e.g.,][]{2010ApJ...718..231S}.
-
-%Studies with the assumption of the close correlation of DM halo mass with central BH mass, and a constant Eddington ratio 
-%interprete this rapid decline by the rarity of massive halos toward higher redshifts \citep[e.g.,][]{2010ApJ...718..231S}, 
-%while another entangling factor is the radiative efficiency in converting BH growth rate to luminosity. 
-%In our work, we argue that the episodical BH accretion with bursts and quiescent phases is 
-%important in matching the $z\sim 6$ quasar observations, 
-%and this calls consideration of the more realistic BH-galaxy coevolution in understanding the observable AGN properties.
-
-%In the future, deep and wide-field surveys e.g.,
-%Wide {\it{RST}} \citep{2019arXiv190205569A} and Wide {\it{Euclid}} \citep{2011arXiv1110.3193L,2017MNRAS.470.5007M}
-%will be crucial to construct the LF data for high-$z$ quasars and galaxies,
-%categorizing them by spectroscopic diagnostics.
-%We show the detection limit of these surveys at each redshift in Fig.~\ref{fig:LFs},
-%demonstrating their capability of optimizing high-$z$ galaxy and quasar observations.
-%The adopted survey parameters is shown in Table.~\ref{tab:N_detect}.
-%The depths of detection will be pushed down to $\Muv\lesssim -20$,
-%which is able to uncover the critical luminosities at which the numbers of galaxies and quasars are comparable.
-%The number of high-$z$ quasars are also predicted at each redshift (Table.~\ref{tab:N_detect}),
-%with the assumption of the survey volume with $\Delta z =1$ and 100\% completeness.
-%The large sample of objects at those high redshifts will shed light on
-%the early coevolution of galaxies and BHs in a statistically unbiased way.
-
-\section{Discussion}
-\label{sec:discussion}
+A rapid decay of the luminous quasar abundance at $\Muv<-26$ mag toward higher redshifts is found by 
+previous observational studies \citep[e.g.,][]{2001AJ....122.2833F,2013ApJ...768..105M,2016ApJ...833..222J,2019ApJ...884...30W}.
+For instance, \citet{2019ApJ...884...30W} proposed a decay index of $k_{\rm L}=-0.78\pm{0.18}$ at $6\lesssim z \lesssim 7$,
+consistent with our model prediction where $k_\mathrm{L} \simeq -0.84$.
+
+\vspace{2mm}
+\section{Discussion}\label{sec:discussion}
 \vspace{2mm}
@@
 
-From the BH growth model described in \S~\ref{sec:MF}, we further explore individual BH evolutionary tracks starting from the BH seeding phases.
-% We take $\fseed=$ 0.01 as a fiducial case, where the best-fit parameters for BH growth are 
-% $\tlife=18.76$ Myr, $\delta=0.055$, $\lambda_0=0.87$, and $\alpha=0.20$.
-% We apply the result to construct individual evolutionary tracks of BHs and produce implications to high-$z$ quasar observations.
-% We generate a 10$^7$ sample of BHs at $z=$ 35, with seed mass $M_\star = 1.5\times 10^3~\Msun$, 
-% \blue{(10$^5$ sample size actually, but with $\fseed=0.01$, essentially 10$^7$)}
-% \blue{(1e3 $\Msun$ in plot, with seed mass and redshift distribution can also be realized)}, 
-% motivated by the properties of typical BH seeds (with median formation redshift and median mass).
-We generate a sample of 10$^6$ BHs, whose formation time and mass distribution at birth follow the model described in \S~\ref{sec:seed}. 
-Adopting the best fit parameters in the case of $\fseed = 0.01$,
-for every time interval $\tlife=18.76$ Myr,
-we assign a constant Eddington ratio $\lambda$ generated randomly from the Schechter distribution function 
-characterized by $\lambda_0=0.87$ and $\alpha=0.20$ (see \S~\ref{sec:fitting_result}).
-With these parameters, we grow the individual BHs until $z=6$ and 
-study the statistical behavior in the growth of massive BHs.
-
-First, we estimate the duty cycle between $z=10$ and $6$ defined as $f_{\rm duty} \equiv \mathcal{N}\tlife/\Delta t_{\rm H}$, 
-where $\mathcal{N}$ is the frequency of super-Eddington accretion bursts with $\lambda>1$ and $\Delta t_{\rm H}\simeq 450$ Myr.
+From the BH growth model described in Section~\ref{sec:MF}, we further explore individual BH evolutionary tracks starting from the BH seeding phases.
+We generate a sample of 10$^6$ BHs, whose formation time and mass distribution at birth follow the model described in Section~\ref{sec:seed}. 
+Adopting the best fit parameters in the case of $\fseed = 0.01$, in every time interval $\tlife=18.76$ Myr,
+we assign a constant Eddington ratio generated from the Schechter-type ERDF characterized by $\lambda_0=0.87$ and $\alpha=0.20$ 
+(see Section~\ref{sec:fitting_result}).
+With these parameters, we grow the individual BHs until $z=6$ and study their statistical properties in producing massive BHs.
+
+First, we estimate the duty cycle between at $6\leq z\leq 10$ defined as $f_{\rm duty} \equiv \mathcal{N}\tlife/\Delta t_{\rm H}$, 
+where $\mathcal{N}$ is the frequency of super-Eddington accretion bursts with $\lambda \geq 1$ and $\Delta t_{\rm H}\simeq 450$ Myr.
 For BH populations grown to $M_\bullet>10^7$, $10^8$ and $10^9~\Msun$ at $z=$ 6,
@@
 On the other hand, the average duty cycle for the entire BH population is calculated as $f_{\rm duty}= 0.075$,
-adopting this ERDF (see \S~\ref{sec:fitting_result}), and is significantly lower than those massive BH sub-samples.
-Therefore, we suggest that the massive BHs observed in $z\simeq 6$ quasars are biased in a way that
+adopting this ERDF (see Section~\ref{sec:fitting_result}), which is significantly lower than those for massive BH sub-samples.
+Therefore, we suggest that SMBHs observed in $z\simeq 6$ quasars are biased in a way that
 the more massive populations undergo longer active accretion episodes along their growth.
@@
 %%%%%%%
-\begin{figure}
+\begin{figure*}
 \centering
-\includegraphics[width=85mm]{Mevol.png}
+\includegraphics[width=125mm]{Mevol.png}
 \caption{
@@
 \label{fig:Mevol}
-\end{figure}
+\end{figure*}
 %
@@
 all of which indicate $\lambda \lesssim 1$ at the  $z=6$ snapshot.
-% among which five BHs show $\lambda<1$ in the snapshots at $z=6$.
 Tracing the BH growth curve back to $z=30$ with the Eddington ratio observed at $z=6$ (dashed curves),
@@
 
-\blue{
-Moreover, some individual quasar observations give exceptionally small proximity zone sizes,
-indicating short lifetime of their luminous phase $t_{\rm Q} \lesssim 10^4$ yr.
-The short quasar lifetime may be due to the young age of quasars ionizing the surrounding IGM \citep[e.g.,][]{2017ApJ...840...24E,2020ApJ...903...60I,2021ApJ...917...38E}.
-Our episodic quasar growth model agrees with this argument,
-besides alleviates the growth tension of SMBHs by episodic accretion bursts.
-In other words, the lifetime of luminous quasar phase is the cumulative time of accreting activity in the current episode.
-}
-
 % \red{KI: still not sure what we discuss below... among the 7 BHs, is anyone consistent with Feige's BH?}
@@
 
+\blue{
+Moreover, some individual quasar observations give exceptionally small proximity zone sizes,
+indicating short lifetime of their luminous phase $t_{\rm Q} \lesssim 10^4$ yr.
+The short quasar lifetime may be due to the young age of quasars ionizing the surrounding IGM \citep[e.g.,][]{2020ApJ...903...60I,2021ApJ...917...38E}.
+Our episodic quasar growth model agrees with this argument,
+besides alleviates the growth tension of SMBHs by episodic accretion bursts.
+In other words, the lifetime of luminous quasar phase is the cumulative time of accreting activity in the current episode.
+}
+
 \vspace{2mm}
@@
 
-Based on the quasar sample from the best-fit model described in \S~\ref{sec:evol}, 
+Based on the quasar sample from the best-fit model described in Section~\ref{sec:evol}, 
 we select quasars with bolometric luminosity limits $L_{45}=10^{45}~\mathrm{erg~s^{-1}}$ and $L_{46}=10^{46}~\mathrm{erg~s^{-1}}$.
@@
 Using the best-fit model parameters, we construct the redshift-dependent QLF and BHMF at $6\leq z \leq 10$.
-% \red{(to be revised)
-\blue{The two functions suggest a rapid decay of the number and mass density of massive BHs and luminous quasars
-in a cosmic volume toward higher redshifts,
-showing similar trend with predictions from previous observations and theoretical work.
-The predicted QLF at all redshifts of $z\gtrsim 6$ can be estimated as $\propto 10^{k_{\rm L} z}$,
-with the more luminous quasars decreasing more rapidly toward higher $z$.
-}
+%\blue{
+The two distribution functions suggest a rapid decay of the number and mass density of massive BHs 
+and luminous quasars toward higher redshifts, as discussed in previous observations and theoretical studies.
+We quantify the decay speed of quasar numbers characterized with a functional form of $\propto 10^{k_{\rm L} z}$,
+and find $k_{\rm L}\simeq -0.91$ and $-0.62s$ for the brightest and faintest population at $z>6$.
+%with the more luminous quasars decreasing more rapidly toward higher $z$.
+%}
 
@@
 unlike the case where one single value of the Eddington ratio is assigned.
-We also find that the observed Eddington-ratio distribution function is skewed to a log-normal shape from the intrinsic Shechter function
+We also find that the observed Eddington-ratio distribution function is skewed to a log-normal shape from the intrinsic Schechter function
 owing to detection limits of quasar surveys.
@@
 \section{Model dependence}\label{sec:modep}
-As described in \S~\ref{sec:model}, we introduce the parameter $\tau$ as a typical timescale
+As described in Section~\ref{sec:model}, we introduce the parameter $\tau$ as a typical timescale
 for individual durations of quasar accretion activity.

### 2022-09-26 ms.tex
version0926; me integrating k's 0924 file

@@
 %%%%%%%
+\begin{deluxetable*}{ccccccccccc}%[t!]
+\tablecolumns{1}
+\renewcommand\thetable{2} %! fix indexing
+\tablewidth{0pt}
+\tablecaption{Parametric Quasar Luminosity Function}
+\tablehead{
+  & & \multicolumn{4}{c}{Unobscured QLF} && \multicolumn{4}{c}{Intrinsic QLF}  \\
+  \cline{3-6} \cline{8-11}
+  \colhead{Redshift} && \colhead{$\Phi^\ast$} & \colhead{$\Muv^\ast$} & \colhead{$\tilde \alpha$} & \colhead{$ \tilde \beta$}& &
+  \colhead{$\Phi^\ast$} & \colhead{$\Muv^\ast$} & \colhead{$\tilde \alpha$} & \colhead{$\tilde \beta$}\\
+  & & \colhead{(Gpc$^{-3}$ mag$^{-1}$)} & \colhead{(mag)} & & & &
+  \colhead{(Gpc$^{-3}$ mag$^{-1}$)} & \colhead{(mag)} & &
+}
+\startdata
+$z\sim 6$  && 46.5 & -23.62 & -1.33 & -2.57    && 89.2 & -23.73 & -1.59 & -2.67 \\
+$z\sim 7$  && 6.98 & -23.70 & -1.61 & -2.82   && 12.4 & -23.85 & -1.87 & -2.92 \\
+$z\sim 8$  && 1.18 & -23.80 & -1.83 & -3.02   && 1.91 & -23.98 & -2.08 & -3.12 \\
+$z\sim 9$  && 0.268 & -23.80 & -1.98 & -3.18  && 0.429& -23.96 & -2.23 & -3.28 \\
+$z\sim 10$ && 0.0841 & -23.68 & -2.01 & -3.30 && 0.144 & -23.82 & -2.35 & -3.40 \\
+\enddata
+\label{tab:QLF_fit}
+\tablecomments{Parametric fitting function of both unobscured and intrinsic QLFs at $z=6-10$, produced by the best-fit model with $\fseed=0.01$.
+}
+\end{deluxetable*}
+
+%%%%%%%
+%    Table. 3
+%%%%%%%
 \begin{deluxetable*}{lccccccc}%[t!]
 \tablecolumns{1}
-\renewcommand\thetable{2} %! fix indexing
+\renewcommand\thetable{3} %! fix indexing
 \tablewidth{0pt} 
@@
 % BHMF with $M_\bullet \simeq 10^8-3\times 10^9~\Msun$ at $z=6$,
-the two cases reproduce similar shape of mass distribution at $M_\bullet \simeq 10^8-3\times 10^9~\Msun$ (see Fig.~\ref{fig:fitmf}).
-As a result, the BHMF at $M_\bullet \gtrsim 10^7~\Msun$, which is potentially accessible by quasar observations,
+the two cases reproduce similar shapes of mass distribution at $M_\bullet \simeq 10^8-3\times 10^9~\Msun$ (see Fig.~\ref{fig:fitmf}).
+\blue{As a result, the BHMF at $M_\bullet \gtrsim 10^7~\Msun$, which is potentially accessible by quasar observations,
 can be characterized with a double power-law function, similar to lower-$z$ quasar populations \citep[e.g.,][]{2013ApJ...764...45K,2015MNRAS.447.2085S}.
-%while the difference in the two BHMF shapes is profound toward the low mass range of $M_\bullet \lesssim 10^7~\Msun$.
+}%while the difference in the two BHMF shapes is profound toward the low mass range of $M_\bullet \lesssim 10^7~\Msun$.
 %The BH abundance and shape of the mass distribution at $10^5 \lesssim M_\bullet/\Msun \lesssim 10^7$ depend on the seeding fraction,
@@
 while the mass density barely evolves for the lightest BHs.
-At $z\lesssim 7-8$, more massive BHs with $\gg 10^6~\Msun$ begin to dominate the total mass budget of the entire BH population,
+At $z\lesssim 7-8$, heavier BHs with $\gg 10^6~\Msun$ begin to dominate the total mass budget of the entire BH population,
 promoting the so-called downsizing or anti-hierarchical evolution of massive BHs 
 in terms of mass occupation \citep[e.g.,][]{2014ApJ...786..104U}.
-Note that the characteristic mass in the BHMF (i.e., $\alpha_{M_\bullet}=-1$) is $M_\bullet \simeq 10^7~(3\times 10^7)~\Msun$ for 
+Namely, the characteristic mass at $z\simeq 6$ in the BHMF (i.e., $\alpha_{M_\bullet}=-1$) is $M_\bullet \simeq 10^7~(3\times 10^7)~\Msun$ for 
 $\fseed=0.1~(0.01)$.
-Moreover, as shown in the left panel, the mass-density evolution is affected by the choice of the seeding fraction more substantially
-for less massive BHs that keep the information on their initial conditions at birth.
-
-For comparison, we overlay the BH mass density evolution with $10^6<M_{\bullet}/\Msun<10^8$
+Moreover, the seeding process affects the evolution of the mass density more substantially for less massive BHs,
+which keep the information on their initial conditions at birth.
+
+For comparison, we overlay the BH mass density evolution with $10^6~\Msun<M_{\bullet}<10^8~\Msun$
 %, and $M_\bullet>10^8~\Msun$
@@
 At $z\lesssim 7$, our results are in overall good agreement with those simulation results.
-However, our models predict a larger number of $10^{6-8}~\Msun$ BHs emerging at $z\sim 10-8$,
+However, our models predict a larger number of $10^{6-8}~\Msun$ BHs emerging at $z\sim 8-10$,
 owing to our model prescription that allows BH seed formation earlier on and (modest) super-Eddington episodes.
@@
 Our quasar sample in the biased, overdense region of the universe (haboring DM halos with $\Mh\gtrsim 10^{11}~\Msun$) 
-are consistent with the constraint, unlike models that require a large number of stellar-mass BH remnants.
+are consistent with the constraint, unlike models that require a large number of stellar-mass BH remnants \citep[see also][]{2009ApJ...696.1798T}.
 
@@
 Fig.~\ref{fig:LFs} presents our prediction of QLFs at $z>6$ taken from the BH growth model.
-We divide the cosmological QLF evolution into four different epochs; (a) $z\simeq 7$, (b) $z\simeq 8$, (c) $z\simeq 9$, and (d) $z\simeq 10-13$.
-The black solid and dashed curve presents the QLF for the unobscured population 
+We divide the cosmological QLF evolution results into four different epochs; (a) $z\simeq 7$, (b) $z\simeq 8$, (c) $z\simeq 9$, and (d) $z\simeq 10-13$.
+The black solid and dashed curves show the QLF for the unobscured population 
 and entire population (including unobscured and obscured quasars), respectively.
@@
 but the correction factor is highly uncertain at the faint end of $\Muv\gtrsim -20$ mag.
-Similar to the BHMF, for all the redshift range, the shape of the QLF is well approximated with a double power-law function.
+Similar to the BHMF, for all the redshift range, the shape of the QLF is well approximated with a double power-law function,
+%
+\begin{equation}
+\Phi(\Muv) = \frac{\Phi^\ast}
+{10^{0.4(\tilde \alpha+1)\Delta \Muv} + 10^{0.4(\tilde \beta+1)\Delta \Muv}},
+\end{equation}
+%
+where $\Phi^\ast$ (in units of Gpc$^{-3}$ mag$^{-1}$) is the overall normalization, $\Muv^\ast$ is the characteristic magnitude,
+$\Delta \Muv \equiv \Muv - \Muv^\ast$, and $\tilde \alpha$ is $\tilde \beta$ are the faint and bright-end power-law slopes, respectively.
+In Table~\ref{tab:QLF_fit}, we summarize those parameters of the parametric QLFs at $z=6-10$ for the best-fit models.
 From higher to lower redshifts, the number density of luminous quasars increases and the bright-end of the distribution rises.
@@
 difficult to identify rare quasars among those faint objects.
-Since extrapolated galaxy LFs with a Schechter shape decline quickly with the luminosity increasing,
-the abundance of galaxies and quasars becomes comparable around $\Muv \sim -23$ mag ($z=7-8$), $-24$ mag ($z=9$), and $-25$ mag ($z=10-13$).
-On the other hand, if the bright end of the galaxy LFs are extended with a power law, those critical UV magnitudes shift to 
+Since the extrapolated galaxy luminosity function with a Schechter shape declines quickly with the luminosity increasing,
+the galaxy abundance becomes comparable to that of quasars at $\Muv \sim -23$ mag ($z=7-8$), $-24$ mag ($z=9$), and $-25$ mag ($z=10-13$).
+On the other hand, if the bright end of the galaxy luminosity function is extended, the critical UV magnitude shifts to
 $\Muv\sim-26$, $-25$, and $\ll -30$ mag for each redshift range.
-Future deep and wide surveys will unveil the relative contribution of the two populations and impacts on cosmic reionization.
+Future deep and wide surveys will unveil the relative contribution of the two populations and impacts on cosmic reionization
+(see also \citetalias{2018ApJ...869..150M}, \citealt{2022NatAs...6..850J}).
 
@@
 Our theoretical predictions are shown at $z\geq 6$ (thick curves),
-while observational results summarized in \cite{2020ApJ...904...89N} are compiled at lower redshifts (thin curves).
+while observational results compiled in \cite{2020ApJ...904...89N} are shown at lower redshifts (thin curves).
 The evolutionary trend can be fitted as $\propto 10^{k_{\rm L}z}$,
@@
 previous observational studies \citep[e.g.,][]{2001AJ....122.2833F,2013ApJ...768..105M,2016ApJ...833..222J,2019ApJ...884...30W}.
-For instance, \citet{2019ApJ...884...30W} proposed a decay index of $k_{\rm L}=-0.78\pm{0.18}$ at $6\lesssim z \lesssim 7$,
-consistent with our model prediction where $k_\mathrm{L} \simeq -0.84$.
+For instance, \citet{2019ApJ...884...30W} proposed a decay index of $k_{\rm L}=-0.78\pm{0.18}$ for those bright quasars at $6\lesssim z \lesssim 7$,
+consistent with our model prediction \blue{where $k_\mathrm{L} \simeq -0.84$.}
 
@@
 We generate a sample of 10$^6$ BHs, whose formation time and mass distribution at birth follow the model described in Section~\ref{sec:seed}. 
-Adopting the best fit parameters in the case of $\fseed = 0.01$, in every time interval $\tlife=18.76$ Myr,
+Adopting the best-fit parameters in the case of $\fseed = 0.01$, in every time interval $\tlife=18.76$ Myr,
 we assign a constant Eddington ratio generated from the Schechter-type ERDF characterized by $\lambda_0=0.87$ and $\alpha=0.20$ 
 (see Section~\ref{sec:fitting_result}).
-With these parameters, we grow the individual BHs until $z=6$ and study their statistical properties in producing massive BHs.
+With those parameters, we grow the individual BHs until $z=6$ and study their statistical properties in producing massive BHs.
 
@@
 
-In Fig.~\ref{fig:Mevol}, we show the BH growth tracks that end up with $M_\bullet>10^8~\Msun$ by $z=6$ (grey thin curves).
-In this sub-sample, we find five BHs heavier than $M=10^9~\Msun$ (highlighted with colored thick curves),
+In Fig.~\ref{fig:Mevol}, we show the BH growth tracks that end up with $M_\bullet>10^8~\Msun$ by $z=6$ (grey curves).
+In this sub-sample, we find five BHs heavier than $M=10^9~\Msun$ (highlighted with colored solid curves),
 all of which indicate $\lambda \lesssim 1$ at the  $z=6$ snapshot.
-Tracing the BH growth curve back to $z=30$ with the Eddington ratio observed at $z=6$ (dashed curves),
-the extrapolated mass of those sub-Eddington BHs at $z=6$ is as massive as $\Mbh \gg 10^6~\Msun$ and is 
-substantially higher than the mass range for seed BHs.
+Tracing the BH growth curves back with the Eddington ratio observed at $z=6$ (dashed curves),
+the extrapolated masses of those massive, sub-Eddington BHs at $z=6$ are as heavy as $\Mbh \gg 10^6~\Msun$ at $z\sim 30$,
+which is substantially higher than the mass range for seed BHs.
 %ting BHs trace back to exceedingly massive seeds which are hard to be explained by current seeding scenarios. 
@@
 % This fact indicates short durations of the super-Eddington accretion mode.
-For comparison, we show the mass growth tracks assuming continuous Eddington accretion (i.e., $\lambda=1$),
+For comparison, we show the mass growth tracks assuming continuous Eddington accretion ($\lambda=1$; dashed-dotted curves),
 where the extrapolated seed mass is $\Mbh \lesssim 10^2~\Msun$ at $z\sim 30$.
@@
 % \blue{It indicates that super-Eddington accretion episodes are required to explain the existence of the massive BHs.}
-Based on the BH seeding and growth model we develop,
-we reiterate that multiple accretion episodes with different values of $\lambda$ should be taken into account 
+In conclusion, therefore, multiple accretion episodes with different values of $\lambda$ should be taken into account 
 to infer the seeding mass for the observed SMBHs as bright quasars at $z\gtrsim 6-7$,
@@
 (with $M_\bullet \simeq 1.7\times 10^9~\Msun$ and $\lambda \simeq 0.6$ at $z=7.6$).
-This overmassive growth history is realized by the combination of rare halo environments planting a seed BH 
+The result demonstrates that the formation of the massive BHs is achieved by the combination of rare halo environments planting a seed BH 
 with $\sim 2\times 10^5~\Msun$ at $z\sim 30$ and several (modest) super-Eddington accretion bursts.

### 2022-09-27 ms.tex
version0926; -- real one; w/ figs folder

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\graphicspath{{./}{../figs/}}
-% \graphicspath{{./}{figures/}{figs/}}
+% \graphicspath{{./}{../figs/}}
+\graphicspath{{./}{./figs/}}
 %% This is the end of the preamble.  Indicate the beginning of the
@@
 Overall, the seed BH mass distribution is extended to $M_\bullet \gtrsim 10^5~\Msun$, 
-imprinted with various pathways of parent halo assembly and environmental effects as discussed in \S\ref{sec:seed}.
+imprinted with various pathways of parent halo assembly and environmental effects as discussed in Section~\ref{sec:seed}.
 }
@@
 tracing back from $t_{\rm H}(z=6)$ to just prior than the first seed formation time $t_1$, where $t_i$ is the $i$-th seed forming time
-as defined in \S\ref{sec:seed} ($1\leq i\leq N_{\rm tot}$).
+as defined in Section~\ref{sec:seed} ($1\leq i\leq N_{\rm tot}$).
 Note that the number of the checkpoints is given by $\lceil (t_{\rm H}-t_1)/\tau \rceil+1$, where $\lceil x\rceil \equiv {\rm min}\{n \in \mathbb{Z}~ |~x\leq n\}$.
@@
 observed in the rest-frame UV spectra \citep[e.g.,][]{2018ApJ...867...30E,2019ApJ...884L..19D}.
-More detailed comparison is discussed in \S\ref{sec:evol}.
+More detailed comparison is discussed in Section~\ref{sec:evol}.
 
@@
 \tablewidth{0pt}
-\tablecaption{Parametric Quasar Luminosity Function}
+\tablecaption{Parametric Quasar Luminosity Function \label{tab:QLF_fit}}
 \tablehead{
@@
 \enddata
-\label{tab:QLF_fit}
-\tablecomments{Parametric fitting function of both unobscured and intrinsic QLFs at $z=6-10$, produced by the best-fit model with $\fseed=0.01$.
+\tablecomments{Parameters characterizing the double power-law fitting functions
+of both the unobscured and intrinsic QLFs.
+At $z=6-10$, the QLF evolution is produced by the best-fit BH growth model with $\fseed=0.01$.
 }
@@
 \tablewidth{0pt} 
-\tablecaption{\blue{Detection Number of Quasars Estimated for Future Surveys} \label{tab:N_detect}} %! reference indexing
+\tablecaption{Detection Number of Quasars Estimated for Future Surveys \label{tab:N_detect}} %! reference indexing
 \tablehead{
@@
 Wide RST    &  2000  & $\Muv=-26$ & $21_{-5}^{+13} $      &  $2_{-7}^{+8}$        &  --  & -- & --  \\
+\hline
 Wide Euclid & 15000  & $YJH$  24   & $6654^{+95}_{-2282}$  &  $708^{+213}_{-237}$ &   $93^{+66}_{-56}$ & $14^{+32}_{-27}$ & --  \\
@@
 \enddata
-\tablecomments{
-Predicted number of quasars at each redshift in the two surveys, with the assumption of the survey volume with $\Delta z =1$ and 100\% completeness.
-The integration of QLF starts from the 5$\sigma$ point source detection limits of the $YJH$ bands in each survey, 
-and the bright magnitude with $\Muv=-26$ mag.
-In addition, detection limit with 22 mag in the $YJH$ bands is examined for Euclid,
-mimicking the effect of quasar selection function.% following \citet{2019A&A...631A..85E}.
+\tablecomments{\blue{
+Predicted number of quasars by the BH growth model with $\fseed=0.01$ at each redshift in the two surveys, with the assumption of the survey volume with $\Delta z =1$ and 100\% completeness.
+The integration of QLF starts from the 5$\sigma$ point source detection limits of the $YJH$ bands in each survey (27 mag for the RST; 24 mag for Euclid), 
+and from the bright absolute magnitude with $\Muv<=-26$ mag.
+In addition, with more realistic quasar identification capability down to 23 mag in the $YJH$ bands,
+\citet{2019Barnett} predicts the yields of quasar numbers as 117 at $7<z<7.5$, 25 at $7.5<z<8.5$, and 2 at $8.5<z<9$.
+We set the same detection limit and find our result in good agreement with theirs.}
 }
@@
 \includegraphics[width=85mm]{LF_spreadz10.pdf}
-\caption{Predicted quasar luminosity functions and depths and volumes of upcoming surveys.
+\caption{Predicted quasar luminosity functions \blue{based on the BH growth model with $\fseed=0.01$},
+as well as depths and volumes of upcoming surveys.
 The black solid and dashed curves present the QLF for the unobscured population (e.g., type-I AGNs) 
@@
 
-Fig.~\ref{fig:LFs} presents our prediction of QLFs at $z>6$ taken from the BH growth model.
+Fig.~\ref{fig:LFs} presents our prediction of QLFs at $z>6$ taken from the BH growth model \blue{with $\fseed=0.01$.}
 We divide the cosmological QLF evolution results into four different epochs; (a) $z\simeq 7$, (b) $z\simeq 8$, (c) $z\simeq 9$, and (d) $z\simeq 10-13$.
@@
 We overlay the expected depths and survey volumes of upcoming near-infrared surveys by
-Euclid \citep{2011arXiv1110.3193L} and RST \citep{2019arXiv190205569A}.
+Euclid (\citealt{2011arXiv1110.3193L}; with realistic depth updated in \citealt{2019Barnett}) and RST \citep{2019arXiv190205569A}.
 Here we consider only their wide-area survey layers because other survey programs are not suitable for quasars at $z\gtrsim 7$.
-Table~\ref{tab:N_detect} summarizes the coverage and limiting magnitudes in each survey
-and lists the expected detection number of quasars.
+Table~\ref{tab:N_detect} summarizes the survey coverage and lists the expected detection number of quasars with varying limiting magnitudes.
+We first integrate the QLFs starting from the 5$\sigma$ point source detection limits (27 mag for the RST and 24 mag for Euclid).
 In priniciple, Euclid will identify quasars up to $z\sim 8$ and discover $O(100-1000)$ quasars at $z\simeq 7-8$.
 The RST will potentially be able to explore the very faint ($\Muv>-22$ mag) but abundant quasar population even at $z\gtrsim 10$. 
-%in principle, after subtracting galaxy contaminants.
-Note that we do not take into account selection criteria to differentiate quasars from other astrophysical sources such
+Note that here we do not take into account selection criteria to differentiate quasars from other astrophysical sources such
 as Galactic brown dwarfs, strong Balmer-break galaxies, and extremely dusty star-forming galaxies at intermediate redshifts.
-Therefore, our estimate in Table~\ref{tab:N_detect} gives an upper bound of the number of detectable high-$z$ quasars.
-Nevertheless, this simplified assumption yields $\approx 3-7$ times higher values than those predicted by \citet{2019A&A...631A..85E}.
+Therefore, this estimate gives an upper bound of the number of detectable high-$z$ quasars.
+Considering 23 mag as the effective depth based on analysis of quasar selection methods for Euclid \citep{2019Barnett},
+we find our estimate of the quasars yields in good agreement with their results.
+Besides, luminous quasars with $\Muv<=-26$ are predicted to be marginally detected by the RST and Euclid up to $z\sim 7$ and 8, respectively.
+However, \citet{2019BAAS...51c.121F} propose that quasar detection can reach $z\sim 9$ by the two surveys,
+where they extrapolate the number density of those bright quasars with a milder decay up to higher redshifts. (wli: they used $-0.78$, but we discuss it later with Fig.8.)
+The difference of predictions is to be tested by upcoming high-$z$ quasar observations.
 %Studies that take into account contamination from MLT dwarfs and compact early-type galaxies and quasar selction method
@@
 We also show the galaxy UV luminosity function in each panel
-along with the fitting functions in a Schechter (dotted) and double power law (dashed-dotted) shape extended to the brighter end
+along with the fitting functions in a Schechter (dotted) and double powe-law (dashed-dotted) shape extended to the brighter end
 \citep{2013MNRAS.432.2696M, 2016ApJ...819..129O, 2018ApJ...867..150M, 2019ApJ...883...99S, 2020MNRAS.493.2059B,
@@
 reproduce the observed distributions of BH mass and luminosity of quasars at $z\sim$ 6.
-% In \S\ref{sec:evol}, we apply this episodic accretion model to individual growth pathways of high-$z$ quasars
+% In Section~\ref{sec:evol}, we apply this episodic accretion model to individual growth pathways of high-$z$ quasars
 % and demonstrate that normal seeding mechanisms can explain the existence of massive BHs with low luminosity

### 2022-09-28 ms.tex
version0928_1; integrated w/ ms0927_k

@@
 %\documentclass[nolinenumbers,preprint2,tighten]{aastex631}
-\hypersetup{filecolor=cyan,urlcolor=blue} %citecolor=green, linkcolor=red,
+%\hypersetup{filecolor=cyan,urlcolor=blue} %citecolor=green, linkcolor=red,
 \newcommand{\vdag}{(v)^\dagger}
@@
 
-\title{Constraining Black Hole Growth with High-z Quasar Observations}
+\title{The Assembly of Black Hole Mass ad Luminosity Functions of High-redshift Quasars\\via Multiple Accretion Episodes}
 
@@
 \centering
-\includegraphics[width=160mm]{seedBHMF_z.png}
+\includegraphics[width=140mm]{seedBHMF_z.png}
 \caption{
-Mass distribution of seed BHs formed in quasar host galaxies at different redshifts ($50\lesssim z \lesssim 10$).
-%Each panel includes a redshift span of 10, 
-In each panel, the cumulative number distribution of BHs formed prior than the redshift interval is shown with green bars,
-and the contribution from newly-born BHs during the interval are highlighted in magenta.
-%with the newly formed BHs denoted by the hatched regions, 
-%and the cumulative BHs formed previously by the blue region.
+Mass distribution of seed BHs formed in quasar host galaxies at different redshifts ($10\leq z \leq 50$).
+In each panel, the contribution from newly-born BHs in the redshift interval is highlighted in magenta,
+and the cumulative number distribution of BHs formed by prior episodes is shown in green.
 The majority of seed BHs form in the epoch of $20\lesssim z \lesssim 40$.
-%The most vigorous seed formation epoches are in redshift ranges $z\sim$ $40-30$ and $30-20$.
-Overall, the seed BH mass distribution is extended to $M_\bullet \gtrsim 10^5~\Msun$, 
-imprinted with various pathways of parent halo assembly and environmental effects as discussed in Section~\ref{sec:seed}.
+Overall, the distribution is extended to $M_\bullet \gtrsim 10^5~\Msun$, 
+imprinted with the halo assembly and environmental effects discussed in Section~\ref{sec:seed}.
 }
 \label{fig:seedmf}
+\vspace{5mm}
 \end{figure*}
@@
 extended to $M_\bullet \gtrsim 10^5~\Msun$, imprinted with the halo assembly and environmental effects.
-
-\orange{
-Lastly, we note that in each parent halo, we consider purely the PopIII stellar remnants in the seed BH mass function construction,
-neglecting the BHs formed by the second-generation PopII stars.
-Formed in metal-enriched environments, PopII stellar remnants are more abundant but typically less massive.
-They are likely to dominate the low mass end of the BHMF at $z\sim 6$,
-thus not significantly contribute to the observable QLF and BHMF \citep{2022MNRAS.511..616T}.
-}
-
-%%%%%%%
-%    Fig. 2
-%%%%%%%
-\begin{figure*}
-\centering
-\includegraphics[width=170mm]{scheme1.pdf}
-\caption{\orange{
-Schematical demonstration of the procedure to calculate the evolution of BH mass distribution from the earliest BH seed to $z=6$.
-The checkpoints are spaced evenly with time interval $\tau$.
-From time $T_0$ to $T_0+\tau$, 
-the BH mass distribution evolves with $\Delta t=\tau$.
-For a newly formed seed BH $M_{\rm i}$, the probability distribution function of BH mass is a delta function, 
-and the growth time is $\Delta t = T_0+\tau-t_{\rm i}$.
-The probability of a BH with mass $M_0$ (or $M_{\rm i}$) to grow to $M$ after $\Delta t$ is drew from the 
-ERDF following Eq.~(\ref{eq:Pl}). 
-Thus the evolution of BH mass distribution is reshaped iteratively 
-plus taking account of the newly formed seeds if there are any.}
-}
-\label{fig:scheme}
-\vspace{5mm}
-\end{figure*}
-
-% Figure 1 shows the BH seeds formed in progenitors of $\Mh = 10^{11}, 10^{12}$
+Note that we consider massive seed BHs formed from low-metallicity environments,
+but neglect a potential contribution from BHs left behind the second-generation star formation
+that takes place in metal-enriched environments.
+%Finally, we note that in each parent halo, we consider purely the PopIII stellar remnants in the seed BH mass function construction,
+%neglecting the BHs formed by the second-generation PopII stars.
+%Formed in metal-enriched environments, PopII stellar remnants are more abundant but typically less massive.
+The latter ones would dominate in number at the low-mass end of the BHMF at $z\sim 6$,
+but have little impacts on the bulk properties of the observed QLF and BHMF \citep[see][]{2022MNRAS.511..616T}.
+
 \vspace{2mm}
-
 \subsection{BH mass growth}
@@
 %
-where $M_{\bullet,c}=10^8~\Msun$ is adopted.
-\orange{
-From the viewpoint of galactic-scale gas supply,
-this characteristic mass is in good agreement with the critical BH mass in \citet{2021ApJ...907...74T},
-above which super-Eddington mass growth of the central BHs no longer happens as
-galactic scale mass supply rates into the nuclear regions cannot be as large as the Eddington rates.
-}
+where $M_{\bullet,c}=10^8~\Msun$ is adopted
+\footnote[3]{
+A series of radiation hydrodynamical simulations for BH accretion
+suggest that the gas supplying from galactic scales into the nuclear scale does not sustain 
+super-Eddington accretion when the BH mass is higher than the characteristic value \citep{2021ApJ...907...74T}.}.
 With a positive value of $\delta$, the BH growth at the high mass end is suppressed,
@@
 $t_{\rm S} =  \Mbh/\Mdot_{\mathrm{Edd}} \approx 45$ Myr (the so-called Salpeter timescale; \citealt{1964ApJ...140..796S}).
+
+%%%%%%%
+%    Fig. 2
+%%%%%%%
+\begin{figure*}
+\centering
+\includegraphics[width=170mm]{scheme1.pdf}
+\caption{
+Schematic illustration of the numerical procedure for calculating the BH mass function
+between intervals with a duration of $\tau$.
+The time evolution of the distribution is calculated by adding newly-forming seed BHs and 
+taking into account growth of existing BHs via mass accretion.
+For a given BH population at a checkpoint at $t=T_0$, their growth is calculated with Eqs.~(\ref{eq:dpdm}) and (\ref{eq:mi2m}),
+where the ERDF is assumed to follow Eq.~(\ref{eq:Pl}).
+For a newly formed seed BH with $M_{\rm k}$ during the interval (i.e., $T_0 \leq t_k < T_0+\tau$), 
+we evolve the BH mass in $\Delta t = T_0+\tau -t_k$ and add it to the mass distribution of the existing BH.
+}
+\label{fig:scheme}
+\vspace{8mm}
+\end{figure*}
 
@@
 
+\vspace{2mm}
 \subsection{BH mass function}\label{sec:MF}
@@
 \vspace{2mm}
-%\section{Results}\label{sec:result}
 \section{Results}\label{sec:fitting_result}
-
-%\vspace{2mm}
-%\subsection{Fitting Results}\label{sec:fitting_result}
 
@@
 \centering
-\includegraphics[width=85mm]{f1_corner.pdf}
-\includegraphics[width=85mm]{f2_corner.pdf}
+\includegraphics[width=80mm]{f1_corner.pdf}\hspace{3mm}
+\includegraphics[width=80mm]{f2_corner.pdf}
 \caption{
-Two dimensional posterior distribution of all the model parameters with $\fseed=0.1$ and 0.01, 
+Two dimensional posterior distribution of all the model parameters with $\fseed=0.1$ (left) and 0.01 (right), 
 along with the marginalized one dimensional projection.
-% and the two dimensional distribution between every two parameters. 
-The distribution of three parameters ($\tau$, $\lambda_0$, and $\alpha$) show single peaks,
-displaying the convergence of those parameters.
-The distribution of $\log\delta$ is relatively broader but suggests that the value of $\delta$
-is sufficiently low and thus the mass-dependent growth model is excluded.
+The three vertical dashed lines in the one-dimensional posterior distribution of each parameter correspond to 
+16\%, 50\%, and 84\% quantiles in the cumulative distribution, respectively. 
+The best-fit values shown with the red lines are listed in Table~\ref{tab:best_fits}.
 }
@@
 %%%%%%%
-\begin{deluxetable}{lcccccc}%[t!]
+\begin{deluxetable}{cccccccc}%[t!]
 \tablecolumns{1}
@@
 \tablewidth{0pt}
-\tablecaption{Best-fit Parameters \label{tab:best_fits}} %!!!!
+\tablecaption{Best-fit parameters for BH growth\label{tab:best_fits}} %!!!!
 \tablehead{
-  \colhead{$\fseed$}  & \colhead{$\tau$ (Myr)} & \colhead{$\delta$} &  \colhead{$\lambda_0$}  & \colhead{$\alpha$}  & \colhead{$\chi^2$}
+  \colhead{$\fseed$}  && \colhead{$\tau$ (Myr)} & \colhead{$\delta$} &  \colhead{$\lambda_0$}  & \colhead{$\alpha$}  & \colhead{$\chi^2$}
 }
 \startdata
-1.0    &  23.13 &    0.001    &   0.96    &   -0.06    &    15.77   \\
-0.1    &  20.07 &    0.001    &   0.89    &    0.12    &    8.27    \\
-0.01   &  18.76 &    0.055    &   0.87    &    0.20    &    6.21    \\
+1.0    &&  23.13 &    0.001    &   0.96    &   -0.06    &    15.77   \\
+0.1    &&  20.07 &    0.001    &   0.89    &    0.12    &    8.27    \\
+0.01   &&  18.76 &    0.055    &   0.87    &    0.20    &    6.21    \\
 \enddata
 \tablecomments{
-The best-fit parameters optimized by MCMC sampling for different cases of $\fseed$.
-The fitting performance is characterized by the relative magnitudes of the $\chi^2$ value.% (see Eq.~\ref{eq:chi2}).
-}
+The best-fit parameters optimized by MCMC sampling for the three different cases of $\fseed$.
+The fitting performance is characterized by the relative magnitudes of the $\chi^2$ value.}
 \end{deluxetable}
@@
 \caption{
-The BH mass function at $z=6$ with the best-fit parameters (black curve) and the $1\sigma$ spread (shaded region) for the cases with $\fseed=0.1$ (left) and $0.01$ (right). 
-For comparison, the BHMF inferred by \citetalias{2010AJ....140..546W} is overlaid (blue curve and shaded region).
-The data is used for the model parameter fitting.
-%.The blue line shows the BHMF derived by \citet{2010AJ....140..546W}.
-% error of observation
+The BH mass function at $z=6$ with the best-fit parameters (black curve) and the $1\sigma$ statistical error (grey shaded region) 
+for the cases with $\fseed=0.1$ (left) and $0.01$ (right). 
+For comparison, the BHMF constructed by \citetalias{2010AJ....140..546W} and their statistical errors (see text) are shown with the cyan curve and shaded region.
 }
 \label{fig:fitmf}
+\vspace{2mm}
 \end{figure*}
@@
 \caption{
-The unobscured quasar luminosity function at $z=6$ with the best-fit parameters (black solid line) and the $1\sigma$ spread for the cases with $\fseed=0.1$ (left) and $0.01$ (right).
-The observed data (blue symbols) with error bars are taken from \citetalias{2018ApJ...869..150M} and is used for the model parameter fitting.
-The upper bound of faint quasar number density is derived from the cumulative QLF presented in \citet{2022NatAs...6..850J}.
-The X-ray QLF data in the faint end inferred from the $z\sim 5-6.1$ quasar sample in \citet{2019ApJ...884...19G} are denoted by orange symbols,
-note that we conduct an extrapolation with quasar number densities scaling with $10^{-0.72\Delta z}$ at $z$ in $5-6$ \citep{2016ApJ...833..222J}.
-For comparison, we show the intrinsic QLF predicted by our model in dashed lines.
+The quasar luminosity function at $z=6$ with the best-fit parameters (black curve) and the $1\sigma$ statistical error (grey shaded region) 
+for the cases with $\fseed=0.1$ (left) and $0.01$ (right).
+The solid and dashed curves are the unobscured and intrinsic QLF, respectively.
+We overlay the observational data for the unobscured QLF taken from \citetalias{2018ApJ...869..150M} in blue and their parametric function with a double power-law function (dotted curve).
+Upper bounds of the number density of faint quasars are given by \citet{2022NatAs...6..850J}, based on the Hubble Space Telescope imaging observations (green).
+The QLF data based on X-ray selected quasars at $z\sim 5.55$ are overlaid in orange \citep{2019ApJ...884...19G}, for which the normalization is scaled to $z=6$
+by a factor of $10^{-0.72\Delta z}$ \citep{2016ApJ...833..222J}, where $\Delta z=0.45$.
 }
 \label{fig:fitlf}
-\vspace{2mm}
+\vspace{5mm}
 \end{figure*}
@@
 \caption{
-{\it Left panel}: BH mass functions predicted by the best-fit models at $z=6-10$,
-including a fraction of $\fseed$ seeds evolving by our model assumption and the remaining ($1-\fseed$) fraction with no subsequent growth.
-The solid (dashed) lines denote the cases with $\fseed=0.1$ (0.01).
-{\it Right panel}: the cumulative mass density evolution for BHs in different mass ranges in a comoving volume, 
-evaluated by the integration of the BHMF shown in the left panel.
-The dashed-dotted line and open square symbols show the results from \citet{2022MNRAS.513..670N}.
-The upper bound of accreted BH mass density from \citet{2013ApJ...778..130T} is denoted by black arrows.
-% The evolutionary trend can be approximated as $\rho_\bullet (z) \propto 10^{k_M z}$, where $k_M\simeq -0.68$.
+{\it Left}: The predicted BH mass functions at $z=6-10$ for the case with $\fseed=0.1$ (solid) and $0.01$ (dashed), including the seed population.
+%including a fraction of $\fseed$ seeds evolving by our model assumption and the remaining ($1-\fseed$) fraction with no subsequent growth.
+%The solid (dashed) lines denote the cases with $\fseed=0.1$ (0.01).
+{\it Right}: the cumulative mass density for BHs in three different mass ranges: $M_\bullet \leq 10^6~\Msun$ (blue), $10^6~\Msun < M_\bullet < 10^8~\Msun$ (orange),
+and $M_\bullet \geq 10^8~\Msun$ (green).
+The dashed-dotted curve shows the results from the cosmological simulations by \citet{2022MNRAS.513..670N}.
+The black arrows present upper bounds of the mass accreted onto BHs obtained from measurements of unresolved cosmic X-ray background radiation \citep{2013ApJ...778..130T}.
 }
@@
 
-%%%%%%%
-%  Table. 2
-%%%%%%%
-\begin{deluxetable*}{ccccccccccc}%[t!]
-\tablecolumns{1}
-\renewcommand\thetable{2} %! fix indexing
-\tablewidth{0pt}
-\tablecaption{Parametric Quasar Luminosity Function \label{tab:QLF_fit}}
-\tablehead{
-  & & \multicolumn{4}{c}{Unobscured QLF} && \multicolumn{4}{c}{Intrinsic QLF}  \\
-  \cline{3-6} \cline{8-11}
-  \colhead{Redshift} && \colhead{$\Phi^\ast$} & \colhead{$\Muv^\ast$} & \colhead{$\tilde \alpha$} & \colhead{$ \tilde \beta$}& &
-  \colhead{$\Phi^\ast$} & \colhead{$\Muv^\ast$} & \colhead{$\tilde \alpha$} & \colhead{$\tilde \beta$}\\
-  & & \colhead{(Gpc$^{-3}$ mag$^{-1}$)} & \colhead{(mag)} & & & &
-  \colhead{(Gpc$^{-3}$ mag$^{-1}$)} & \colhead{(mag)} & &
-}
-\startdata
-$z\sim 6$  && 46.5 & -23.62 & -1.33 & -2.57    && 89.2 & -23.73 & -1.59 & -2.67 \\
-$z\sim 7$  && 6.98 & -23.70 & -1.61 & -2.82   && 12.4 & -23.85 & -1.87 & -2.92 \\
-$z\sim 8$  && 1.18 & -23.80 & -1.83 & -3.02   && 1.91 & -23.98 & -2.08 & -3.12 \\
-$z\sim 9$  && 0.268 & -23.80 & -1.98 & -3.18  && 0.429& -23.96 & -2.23 & -3.28 \\
-$z\sim 10$ && 0.0841 & -23.68 & -2.01 & -3.30 && 0.144 & -23.82 & -2.35 & -3.40 \\
-\enddata
-\tablecomments{Parameters characterizing the double power-law fitting functions
-of both the unobscured and intrinsic QLFs.
-At $z=6-10$, the QLF evolution is produced by the best-fit BH growth model with $\fseed=0.01$.
-}
-\end{deluxetable*}
-
-%%%%%%%
-%    Table. 3
-%%%%%%%
-\begin{deluxetable*}{lccccccc}%[t!]
-\tablecolumns{1}
-\renewcommand\thetable{3} %! fix indexing
-\tablewidth{0pt} 
-\tablecaption{Detection Number of Quasars Estimated for Future Surveys \label{tab:N_detect}} %! reference indexing
-\tablehead{
-  \colhead{Telescope} & \colhead{ Survey area} & \colhead{Photo. depth} &  \colhead{$N(z\sim 6)$} & \colhead{$N(z\sim 7)$}& \colhead{$N(z\sim 8)$}&  \colhead{$N(z\sim 9)$}&  \colhead{$N(z\sim 10)$}\\
-  \colhead{} & \colhead{(\rm{deg}$^2$)} & \colhead{(AB mag)} & & & & & 
-}
-\startdata
-Wide RST    &  2000  & $YJH$  27   & $6759_{-3185}^{+15} $ &  $1514_{-558}^{+169}$ &  $349_{-131}^{53}$ & $85_{-48}^{+23}$ & $25^{+12}_{-15}$  \\
-Wide RST    &  2000  & $\Muv=-26$ & $21_{-5}^{+13} $      &  $2_{-7}^{+8}$        &  --  & -- & --  \\
-\hline
-Wide Euclid & 15000  & $YJH$  24   & $6654^{+95}_{-2282}$  &  $708^{+213}_{-237}$ &   $93^{+66}_{-56}$ & $14^{+32}_{-27}$ & --  \\
-Wide Euclid & 15000  & $YJH$  23   & $2480^{+188}_{-614}$  &  $207^{+144}_{-114}$ &   $23^{+27}_{-19}$ & $3^{+12}_{-10}$ & --  \\
-Wide Euclid & 15000  & $\Muv=-26$  & $154^{+100}_{-38}$    &  $12^{+59}_{-50}$    &   $1^{+4}_{-3}$    & -- & --  \\
-\enddata
-\tablecomments{\blue{
-Predicted number of quasars by the BH growth model with $\fseed=0.01$ at each redshift in the two surveys, with the assumption of the survey volume with $\Delta z =1$ and 100\% completeness.
-The integration of QLF starts from the 5$\sigma$ point source detection limits of the $YJH$ bands in each survey (27 mag for the RST; 24 mag for Euclid), 
-and from the bright absolute magnitude with $\Muv<=-26$ mag.
-In addition, with more realistic quasar identification capability down to 23 mag in the $YJH$ bands,
-\citet{2019Barnett} predicts the yields of quasar numbers as 117 at $7<z<7.5$, 25 at $7.5<z<8.5$, and 2 at $8.5<z<9$.
-We set the same detection limit and find our result in good agreement with theirs.}
-}
-\end{deluxetable*}
-
 Based on the constraint from $z\sim 6$ quasar observations, the best-fit model from the MCMC realizations enables
@@
 Since the BHMF shape at $z=6$ is constrained by \citetalias{2010AJ....140..546W},
-% BHMF with $M_\bullet \simeq 10^8-3\times 10^9~\Msun$ at $z=6$,
 the two cases reproduce similar shapes of mass distribution at $M_\bullet \simeq 10^8-3\times 10^9~\Msun$ (see Fig.~\ref{fig:fitmf}).
-\blue{As a result, the BHMF at $M_\bullet \gtrsim 10^7~\Msun$, which is potentially accessible by quasar observations,
-can be characterized with a double power-law function, similar to lower-$z$ quasar populations \citep[e.g.,][]{2013ApJ...764...45K,2015MNRAS.447.2085S}.
-}%while the difference in the two BHMF shapes is profound toward the low mass range of $M_\bullet \lesssim 10^7~\Msun$.
+As a result, the BHMF at $M_\bullet \gtrsim 10^7~\Msun$, which is potentially accessible by quasar observations,
+can be characterized with a double power-law function, 
+%
+\begin{equation}
+\Phi_{M_\bullet}=\frac{\Phi_{M_\bullet}^\ast}{(M_\bullet/M_{\bullet}^\ast)^{-(\hat \alpha+1)} + (M_\bullet/M_{\bullet}^\ast)^{-(\hat \beta+1)}},
+\end{equation}
+%
+similar to lower-$z$ quasar populations \citep[e.g.,][]{2013ApJ...764...45K,2015MNRAS.447.2085S}.
+Here, $\Phi_{M_\bullet}^\ast$ (in units of Gpc$^{-3}$ dex$^{-1}$) is the overall normalization, $M_\bullet^\ast$ is the characteristic BH mass,
+and $\hat \alpha$ and $\hat \beta$ are the low and high-mass end power-law slopes, respectively.
+In Table~\ref{tab:BHMF_fit}, we summarize those parameters of the parametric BHMF at $z=6-10$ for the best-fit models.
+%while the difference in the two BHMF shapes is profound toward the low mass range of $M_\bullet \lesssim 10^7~\Msun$.
 %The BH abundance and shape of the mass distribution at $10^5 \lesssim M_\bullet/\Msun \lesssim 10^7$ depend on the seeding fraction,
@@
 %In the case of $\fseed=0.01$, this typical mass range is higher, despite the integrated mass density is lower than that with $\fseed=0.1$.
+
+%%%%%%%
+%  Table. 2
+%%%%%%%
+\begin{deluxetable}{ccccccc}%[t!]
+\tablecolumns{1}
+\renewcommand\thetable{2} %! fix indexing
+\tablewidth{0pt}
+\tablecaption{Parametric Black Hole Mass Function \label{tab:BHMF_fit}}
+\tablehead{
+%  & & \multicolumn{4}{c}{Unobscured QLF} && \multicolumn{4}{c}{Intrinsic QLF}  \\
+%  \cline{3-6} \cline{8-11}
+  \colhead{Redshift} & \colhead{$\Phi_{M_\bullet}^\ast$} & \colhead{$M_\bullet^\ast$} & \colhead{$\hat \alpha$} & \colhead{$ \hat \beta$}& \\
+   & \colhead{(Gpc$^{-3}$ dex$^{-1}$)} & \colhead{($10^7~\Msun$)} & & &
+}
+\startdata
+$z\sim 6$  & $1310$ & $6.13$ & -1.41 & -2.58    & \\
+$z\sim 7$  & $166$   & $8.12$ & -1.81 & -2.88    & \\
+$z\sim 8$  & $23.2$  & $9.98$ & -2.07 & -3.12    & \\
+$z\sim 9$  & $5.61$  & $9.44$ & -2.24 & -3.29    & \\
+$z\sim10$  & $2.13$ & $7.68$  & -2.35 & -3.41    & \\
+\enddata
+\tablecomments{The fitting parameters of the BHMF with 
+a double power-law function for the case with $\fseed=0.01$.
+The fitted mass range is $10^6~\Msun \leq M_\bullet \leq 10^{10}~\Msun$.
+}
+\end{deluxetable}
+
+%%%%%%%
+%    Fig. 7
+%%%%%%%
+\begin{figure*}
+\centering
+\includegraphics[width=85mm]{LF_spreadz7.pdf}\hspace{2mm}
+\includegraphics[width=85mm]{LF_spreadz8.pdf}\\\vspace{5mm}
+\includegraphics[width=85mm]{LF_spreadz9.pdf}\hspace{2mm}
+\includegraphics[width=85mm]{LF_spreadz10.pdf}
+\caption{
+The predicted quasar luminosity functions at (a) $z\sim 7$, (b) $z\sim 8$, (c) $z\sim 9$, (d) $z\sim 10-13$.
+The black solid and dashed curves are the unobscured and intrinsic QLF, respectively, and the shaded region presents the $1\sigma$ statistical error.
+The expected depths and volumes of future surveys with Wide RST (blue) and Wide Euclid (red) are overlaid in each panel (see Table~\ref{tab:N_detect}).
+For comparison, the galaxy UV luminosity functions are plotted with the data points (grey) and the fitting functions in purple with a Schechter (dotted) and double power-law (dash-dotted) shape.
+The luminosity function data are taken from \citet{2013MNRAS.432.2696M}, \citet{2016ApJ...819..129O}, \citet{2018ApJ...867..150M},
+\citet{2019ApJ...883...99S}, \citet{2020MNRAS.493.2059B}, \citet{2021AJ....162...47B},
+\citet{2022ApJS..259...20H,Harikane_2022b,Harikane_2022c}, \citet{2022arXiv220712356D}, \citet{2022arXiv220709434N}.
+The fitting forms of the galaxy luminosity functions are given by \citet{2022ApJS..259...20H} at $z\simeq 7$, 
+\citet{2020MNRAS.493.2059B} and \citet{2013MNRAS.432.2696M} at $z\simeq 8$, and \citet{Harikane_2022c} at $9\lesssim z\lesssim 13$.}
+\label{fig:LFs}
+\vspace{5mm}
+\end{figure*}
 
@@
 
-\if0
-Varying the minimum mass as $M_{\rm min}=10^7$, $10^8$, and $10^9~\Msun$,
-we find that the early BH assembly takes place rapidly and the redshift-dependence can be approximated by
-%
-\begin{equation}
-\rho_\bullet(z)
-%= \rho_{\bullet 0}\cdot e^{k_{\rm M}(z-6)}
-\simeq \rho_{\bullet,0}~ 10^{k_{\rm M}(z-6)},
-\end{equation}
-%
-where the fitted values of $\rho_{\bullet,0}$ and $k_{\rm M}$ are shown in Table.~\ref{tab:MFz}.
-
-On the other hand, the stellar mass density of the quasar progenitor halos is calculated as
-%
-\begin{equation}
-\rho_{\star}(z)
-\simeq f_\star n_{\Mh} M_h~ 10^{k_{\rm h}(z-6)},
-\end{equation}
-%
-where $f_\star(\equiv M_\star/\Mh)$ is the mass ratio of the galaxy stellar mass to the DM halo mass and
-$n_{\Mh}$ is the number density of quasar host halos with $\Mh$ in a comoving volume at $z=6$; namely,
-the value of $n_{\Mh}\Mh \simeq (6.2-99)\times 10^6~\Msun~{\rm Mpc}^{-3}$.
-We here express the mass growth of the DM halo with a functional form of $\propto 10^{k_{\rm h} z}$,
-which can describe the mass growth of DM halos
-\citep[e.g.,][]{2002ApJ...568...52W,2008MNRAS.383..615N,2008MNRAS.388.1792N,2010MNRAS.406.2267F}
-\footnote[4]{
-In fact, this redshift dependence leads to a halo-mass growth rate of $\D \left(\ln \Mh \right) / \D t \propto(1+z)^{5/2}$,
-which has been understood based on the extended Press-Schechter formalism and also derived by
-a fit to merger trees from cosmological N-body simulations \citep{2013MNRAS.435..999D}.}.
-% The redshift dependence yields the cosmic BH growth rate in the matter-dominated universe
-% as $\dot{\rho}_\bullet \propto \rho_\bullet (1+z)^{5/2}$ or
-
-% \begin{align}
-% \dot{\rho}_\bullet(z) & =\dot{\rho}_\bullet(z=6)\left(\frac{1+z}{7}\right)^{5/2} 10^{k_{\rm M}(z-6)}, \\
-% &\simeq *** ~\Msunyr~{\rm Mpc}^{-3} \left(\frac{1+z}{7}\right)^{5/2} e^{\bar{k}_{\rm M}(z-6)},\nonumber
-% \end{align}
-
-% where $\bar{k}_{\rm M} \equiv k_{\rm M} \ln 10 \simeq -1.84$.
-% \red{KI: I'm not sure what we discuss here... One thing is the cosmic SFR density (Madau's plot).
-% Is there something like Madau's plot but for DM halos?}
-% The exponential dependence on redshift is reminiscent of the cosmic galaxy mass growth
-% $M_{\star} \propto e^{-B z}$, as a consequnce of the assumption of fixed galaxy to DM halo mass ratio,
-% and the growth rate of DM halos in the extended Press-Schechter formalism
-% $\D \left(\ln \Mh \right) / \D t \propto(1+z)^{5/2}$ \citep{2008MNRAS.383..615N}.
-% Our results suggest that the cumulative massive BH mass density growing in galactic nuclei also follows
-% an exponential evolution with redshift,
-% which is statistically in agreement with the host halo and galaxy growth.
-The star-to-halo mass ratio is assumed to be $f_\star =0.01$ for those quasar progenitor halos at $z>6$
-% (UNIVERSEMACHINE; Behroozi et al. 2019).
-\citep[fits by code {\tt UNIVERSEMACHINE} in][]{2019MNRAS.488.3143B}.
-%https://ui.adsabs.harvard.edu/abs/2019MNRAS.488.3143B/abstract
-With those values, we estimate the stellar-to-BH mass ratio for high-$z$ quasars as
-%
-\begin{equation}
-\frac{\rho_{\star}(z)}{\rho_{\bullet}(z)}
-\simeq 2.5\times 10^{3} \left(\frac{f_\star}{0.01}\right)
-~ 10^{(k_{\rm h}-k_{\rm M})(z-6)},
-\end{equation}
-% 
-where $k_{\rm h} \approx -0.16 $ for the parent halo growth histories.
-Therefore, at $z\sim 6$ the bulge-to-BH mass ratio $\sim O(10^3)$ for the entire BH population (i.e., low-mass BHs and low-luminosity quasars) 
-\blue{
-is broadly consistent with those seen in the local universe \citep[$\simeq 200-1000$ in e.g.,][]{2012ApJ...751L..25V,2013ARA&A..51..511K},
-although SMBHs observed as high-$z$ quasars appear to be $\sim 10$ times overmassive compared to the local relation 
-\citep[e.g.,][]{2013ApJ...773...44W,2020A&A...637A..84P,2021ApJ...911..141N}.
-Our result suggests that overall the build-up of stellar mass in galaxies is earlier than BHs,
-which will be tested by high-$z$ galaxy and quasar surveys.
-}
-
-%%%%%%%
-%    Table. 1 
-%%%%%%%
-\begin{table}
-\renewcommand\thetable{1} %! fix indexing
-\caption{$\rho_\bullet(z)$ Evolution Parameters}
-\begin{center}
-% \tablenum{1}
-\begin{tabular}{l c r}
+%%%%%%%
+%  Table. 3
+%%%%%%%
+\begin{deluxetable*}{ccccccccccc}%[t!]
+\tablecolumns{1}
+\renewcommand\thetable{3} %! fix indexing
+\tablewidth{0pt}
+\tablecaption{Parametric Quasar Luminosity Function \label{tab:QLF_fit}}
+\tablehead{
+  & & \multicolumn{4}{c}{Unobscured QLF} && \multicolumn{4}{c}{Intrinsic QLF}  \\
+  \cline{3-6} \cline{8-11}
+  \colhead{Redshift} && \colhead{$\Phi_{\Muv}^\ast$} & \colhead{$\Muv^\ast$} & \colhead{$\tilde \alpha$} & \colhead{$ \tilde \beta$}& &
+  \colhead{$\Phi_{\Muv}^\ast$} & \colhead{$\Muv^\ast$} & \colhead{$\tilde \alpha$} & \colhead{$\tilde \beta$}\\
+  & & \colhead{(Gpc$^{-3}$ mag$^{-1}$)} & \colhead{(mag)} & & & &
+  \colhead{(Gpc$^{-3}$ mag$^{-1}$)} & \colhead{(mag)} & &
+}
+\startdata
+$z\sim 6$  && 46.5 & -23.62 & -1.33 & -2.57    && 89.2 & -23.73 & -1.59 & -2.67 \\
+$z\sim 7$  && 6.98 & -23.70 & -1.61 & -2.82   && 12.4 & -23.85 & -1.87 & -2.92 \\
+$z\sim 8$  && 1.18 & -23.80 & -1.83 & -3.02   && 1.91 & -23.98 & -2.08 & -3.12 \\
+$z\sim 9$  && 0.268 & -23.80 & -1.98 & -3.18  && 0.429& -23.96 & -2.23 & -3.28 \\
+$z\sim 10$ && 0.0841 & -23.68 & -2.01 & -3.30 && 0.144 & -23.82 & -2.35 & -3.40 \\
+\enddata
+\tablecomments{The fitting parameters of the unobscured and intrinsic QLFs with 
+a double power-law function for the case with $\fseed=0.01$.
+The fitted magnitude range is $-30~{\rm mag}  \leq \Muv \leq -18~{\rm mag}$.
+}
+\end{deluxetable*}
+
+%%%%%%%
+%    Table. 4
+%%%%%%%
+\begin{deluxetable*}{lccccccc}%[t!]
+\tablecolumns{1}
+\renewcommand\thetable{4} %! fix indexing
+\tablewidth{0pt} 
+\tablecaption{Detection Number of Quasars Estimated for Future Surveys \label{tab:N_detect}} %! reference indexing
+\tablehead{
+  \colhead{Telescope} & \colhead{ Survey area} & \colhead{Photo. depth} &  \colhead{$N(z\sim 6)$} & \colhead{$N(z\sim 7)$}& \colhead{$N(z\sim 8)$}&  \colhead{$N(z\sim 9)$}&  \colhead{$N(z\sim 10)$}\\
+  \colhead{} & \colhead{(\rm{deg}$^2$)} & \colhead{(AB mag)} & & & & & 
+}
+\startdata
+Wide Euclid & 15000  & $YJH$  24   & $6654^{+95}_{-2282}$  &  $708^{+213}_{-237}$ &   $93^{+66}_{-56}$ & $14^{+32}_{-27}$ & --  \\
+Wide Euclid & 15000  & $YJH$  23   & $2480^{+188}_{-614}$  &  $207^{+144}_{-114}$ &   $23^{+27}_{-19}$ & $3^{+12}_{-10}$ & --  \\
+Wide Euclid\dag & 15000  & selection func.  & --                             &  $204 (117)$                &   $16 (6)$             & $7 (2)$ & --  \\
+Wide Euclid & 15000  & $\Muv=-26$  & $154^{+100}_{-38}$    &  $12^{+59}_{-50}$    &   $1^{+4}_{-3}$    & -- & --  \\
 \hline
-\hline
-$M_{\rm min}$ & $\log \rho_{\bullet,0}$ & $k_{\rm M}$ ~~~ \\ 
-\hline 
-10$^7$  &  $ 1.81\pm 0.28$  &  $-0.68 \pm 0.21$  \\
-10$^8$  &  $ 1.54\pm 0.47$  &  $-0.84 \pm 0.31$  \\
-% 10$^9$  &  $-8.30_{-0.47}^{+0.47}$  & $-1.04_{-0.58}^{+0.54}$ \\
-10$^9$  &  $ 1.01\pm 0.47$  &  $-1.01 \pm 0.58$ \\
-\hline 
-\end{tabular}
-\label{tab:MFz}
-\end{center}
-\end{table}    
-\fi
+Wide RST    &  2000  & $YJH$  27   & $6759_{-3185}^{+15} $ &  $1514_{-558}^{+169}$ &  $349_{-131}^{53}$ & $85_{-48}^{+23}$ & $25^{+12}_{-15}$  \\
+Wide RST    &  2000  & $\Muv=-26$ & $21_{-5}^{+13} $      &  $2_{-7}^{+8}$        &  --  & -- & --  \\
+\enddata
+\tablecomments{
+The detection number of high-$z$ quasars predicted by the BH growth model with $\fseed=0.01$ at each redshift with the Euclid ad RST wide-area surveys, 
+assuming the survey volume with $\Delta z =1$ and 100\% completeness.
+The integration of the QLF is conducted for brighter populations than the 5$\sigma$ point source detection limits of 
+the $YJH$ bands in each survey (24 mag for Euclid and 27 mag for the RST), and the absolute magnitude with $\Muv \leq-26$ mag.\\
+\dag: To mimic realistic quasar identification capability, we show the detection numbers with $YJK=23$ mag in comparison with
+\citet{2019Barnett}. The values are taken from the fourth column of their Table~3 for the three redshift range: $7.0<z<7.5$, $8.0<z<8.5$, and $8.5<z<9.0$.
+The values correspond to different extrapolation of the quasar number density at higher redshifts ($\propto 10^{k_{\rm L}z}$); $k_{\rm L}=-0.72$ and $-0.92$.
+}
+\end{deluxetable*}
 
@@
 
-%%%%%%%
-%    Fig. 7
-%%%%%%%
-\begin{figure*}[h!]
-\centering
-\includegraphics[width=85mm]{LF_spreadz7.pdf}\hspace{2mm}
-\includegraphics[width=85mm]{LF_spreadz8.pdf}\\\vspace{5mm}
-\includegraphics[width=85mm]{LF_spreadz9.pdf}\hspace{2mm}
-\includegraphics[width=85mm]{LF_spreadz10.pdf}
-\caption{Predicted quasar luminosity functions \blue{based on the BH growth model with $\fseed=0.01$},
-as well as depths and volumes of upcoming surveys.
-The black solid and dashed curves present the QLF for the unobscured population (e.g., type-I AGNs) 
-and the whole population (i.e., type-I and type-II AGNs), and the shaded region presents the $1\sigma$ spread.
-The expected depths and volumes of future surveys with Wide RST and Wide Euclid are overlaid with the blue lines,
-indicating the detectability of quasars at these redshifts.
-Galaxy UV luminosity functions are plotted with the data points (grey) and fitting functions with a Schechter (dotted curve) and double power-law (dash-dotted curve) shape.
-The galaxy luminosity function data at $z\sim$ 7 are taken from \citet{2022ApJS..259...20H} and \citet{2021AJ....162...47B}. 
-At $z\sim$ 8, the data points are from \citet{2021AJ....162...47B},
-\citet{2022arXiv220712356D}, \citet{2013MNRAS.432.2696M}, \citet{2020MNRAS.493.2059B}, and \citet{2019ApJ...883...99S}.
-At  $z\sim$ 9, those data are from \citet{Harikane_2022c}, \citet{2022arXiv220712356D}, \citet{2020MNRAS.493.2059B}, \citet{2019ApJ...883...99S}, 
-and \citet{2018ApJ...867..150M}.
-At $z\sim$ $10-13$, we take data from \citet{Harikane_2022c}, \citet{2022arXiv220712356D}, \citet{Harikane_2022b}, \citet{2022arXiv220709434N}, \citet{2018ApJ...867..150M}, 
-and \citet{2016ApJ...819..129O}.
-The fitting forms of the luminosity functions are given by \citet{2022ApJS..259...20H} at $z\simeq 7$, 
-\citet{2020MNRAS.493.2059B} and \citet{2013MNRAS.432.2696M} at $z\simeq 8$, and \citet{Harikane_2022c} at $9\lesssim z\lesssim 13$.
-}
-\label{fig:LFs}
-\end{figure*}
-
-\if0
-Next, we show our prediction of $z=6-10$ unobscured QLFs taken from the BH growth model in the left panel of Fig.~\ref{fig:QLFmag_z}.
-Similar to the BHMF, for all the redshift range, the shape of the QLF is well approximated with a double power-law function.
-From higher to lower redshifts, the number density of luminous quasars increases and the bright-end of the distribution rises.
-% %The model QLFs we propose give interesting prediction and will be further constrained by higher redshift quasar observations.
-% \red{KI: add more explanations about the QLFs. How about the detection limits of Euclid, Roman, and others?
-% Also, you could compare your results with Aaron Yung's results.}
-In the right panle of Fig.~\ref{fig:QLFmag_z}, we present the number density of luminous quasars with $\Muv <-26~{\rm mag}$ as a function of redshift.
-The evolutionary trend can be fitted as $\propto 10^{k_{\rm L}z}$, where $k_{\rm L}\approx -0.97$.
-Observationally, a rapid decay of the quasar number density toward higher redshifts is found by previous studies
-\citep[e.g.,][]{2001AJ....122.2833F,2013ApJ...768..105M,2016ApJ...833..222J,2019ApJ...884...30W},
-which show $k_{\rm L}= -0.47$ and $-0.72$ from the analysis of quasar samples at $z\simeq 3-5$ and $z\simeq 5-6$, respectively.
-% Recently, a steeper decline of luminous quasar number density toward higher redshifts is proposed by \citet{2019ApJ...884...30W},
-% suggesting $k_{\rm L}=-0.78$ at $6\lesssim z \lesssim 7$.
-The rapid decline toward higher redshifts is characterized by the treatment of episodic natures of BH accretion with a finite value of
-$\tau ~(\simeq 20~{\rm Myr})$, in order to match the statistical properties of high-$z$ quasars.
-We also note that the tendency would be explained by the rarity of massive quasar-host halos at higher redshifts,
-non-constant radiative efficiencies that covert the BH growth rate into the luminosity, or some combination of these effects
-\citep[e.g.,][]{2010ApJ...718..231S}.
-%Studies with the assumption of the close correlation of DM halo mass with central BH mass, and a constant Eddington ratio 
-%interprete this rapid decline by the rarity of massive halos toward higher redshifts \citep[e.g.,][]{2010ApJ...718..231S}, 
-%while another entangling factor is the radiative efficiency in converting BH growth rate to luminosity. 
-%In our work, we argue that the episodical BH accretion with bursts and quiescent phases is 
-%important in matching the $z\sim 6$ quasar observations, 
-%and this calls consideration of the more realistic BH-galaxy coevolution in understanding the observable AGN properties.
-\fi
-
-Fig.~\ref{fig:LFs} presents our prediction of QLFs at $z>6$ taken from the BH growth model \blue{with $\fseed=0.01$.}
+Fig.~\ref{fig:LFs} presents our prediction of QLFs at $z>6$ taken from the BH growth model with $\fseed=0.01$.
 We divide the cosmological QLF evolution results into four different epochs; (a) $z\simeq 7$, (b) $z\simeq 8$, (c) $z\simeq 9$, and (d) $z\simeq 10-13$.
@@
 \begin{equation}
-\Phi(\Muv) = \frac{\Phi^\ast}
+\Phi_{\Muv} = \frac{\Phi_{\Muv}^\ast}
 {10^{0.4(\tilde \alpha+1)\Delta \Muv} + 10^{0.4(\tilde \beta+1)\Delta \Muv}},
@@
 %
-where $\Phi^\ast$ (in units of Gpc$^{-3}$ mag$^{-1}$) is the overall normalization, $\Muv^\ast$ is the characteristic magnitude,
-$\Delta \Muv \equiv \Muv - \Muv^\ast$, and $\tilde \alpha$ is $\tilde \beta$ are the faint and bright-end power-law slopes, respectively.
+where $\Phi_{\Muv}^\ast$ (in units of Gpc$^{-3}$ mag$^{-1}$) is the overall normalization, $\Muv^\ast$ is the characteristic magnitude,
+$\Delta \Muv \equiv \Muv - \Muv^\ast$, and $\tilde \alpha$ and $\tilde \beta$ are the faint and bright-end power-law slopes, respectively.
 In Table~\ref{tab:QLF_fit}, we summarize those parameters of the parametric QLFs at $z=6-10$ for the best-fit models.
@@
 
-\blue{
 We overlay the expected depths and survey volumes of upcoming near-infrared surveys by
 Euclid (\citealt{2011arXiv1110.3193L}; with realistic depth updated in \citealt{2019Barnett}) and RST \citep{2019arXiv190205569A}.
-Here we consider only their wide-area survey layers because other survey programs are not suitable for quasars at $z\gtrsim 7$.
+We here consider only their wide-area survey layers because other survey programs are not suitable for quasars at $z\gtrsim 7$.
 Table~\ref{tab:N_detect} summarizes the survey coverage and lists the expected detection number of quasars with varying limiting magnitudes.
-We first integrate the QLFs starting from the 5$\sigma$ point source detection limits (27 mag for the RST and 24 mag for Euclid).
-In priniciple, Euclid will identify quasars up to $z\sim 8$ and discover $O(100-1000)$ quasars at $z\simeq 7-8$.
-The RST will potentially be able to explore the very faint ($\Muv>-22$ mag) but abundant quasar population even at $z\gtrsim 10$. 
-Note that here we do not take into account selection criteria to differentiate quasars from other astrophysical sources such
-as Galactic brown dwarfs, strong Balmer-break galaxies, and extremely dusty star-forming galaxies at intermediate redshifts.
-Therefore, this estimate gives an upper bound of the number of detectable high-$z$ quasars.
-Considering 23 mag as the effective depth based on analysis of quasar selection methods for Euclid \citep{2019Barnett},
-we find our estimate of the quasars yields in good agreement with their results.
-Besides, luminous quasars with $\Muv<=-26$ are predicted to be marginally detected by the RST and Euclid up to $z\sim 7$ and 8, respectively.
-However, \citet{2019BAAS...51c.121F} propose that quasar detection can reach $z\sim 9$ by the two surveys,
-where they extrapolate the number density of those bright quasars with a milder decay up to higher redshifts. (wli: they used $-0.78$, but we discuss it later with Fig.8.)
-The difference of predictions is to be tested by upcoming high-$z$ quasar observations.
+We first integrate the QLFs starting from the 5$\sigma$ point source detection limits (24 mag for Euclid and 27 mag for RST, respectively).
+With the limiting magnitude, Euclid will identify quasars up to $z\lesssim 9$ and discover $\simeq 100-700$ quasars at $z\simeq 7-8$.
+The RST will be able to explore fainter ($\Muv>-22$ mag) but more abundant quasar populations up to $z\sim 10$,
+and increase the detection number by a factor of $\sim 2-6$ depending on the redshift range.
+However, realistic detection numbers are reduced from those ideal ones when we take into account selection criteria to differentiate 
+high-$z$ quasars from other astrophysical sources such as Galactic brown dwarfs and low-$z$ galaxy interlopers.
+Therefore, the estimated values above give upper bounds of the number of detectable high-$z$ quasars.
+Adopting $YJH=23$ mag as the effective depth based on the quasar selection methods for Euclid \citep{2019Barnett},
+our predicted detection numbers are in good agreement with their results but shows a better match for the case with extrapolation of $10^{-0.72z}$
+toward higher redshifts (see the fourth column in their Table~3).
+
+Luminous quasars with $\Muv \lesssim -26$ mag are expected to be marginally detected by the RST and Euclid up to $z\sim 7$ and 8, respectively.
+However, \citet{2019BAAS...51c.121F} proposed that quasar detection can reach $z\sim 9$ by the two surveys
+because a moderate decline of the quasar number density ($\propto 10^{-0.78z}$) is assumed.
+The difference of predictions is to be tested by upcoming high-$z$ quasar observations (see the discussion below).
 %Studies that take into account contamination from MLT dwarfs and compact early-type galaxies and quasar selction method
@@
 %Therefore, our estimation should represent an upper bound of the potentially detectable quasar population.
-}
 % me:On the other hand, we the selection effect to miss some quasars, especially the faint ones. Our prediction is
@@
 \caption{
-Evolution of quasar luminosity functions at different UV magnitudes.
-The theoretical prediction from $z=6$ to $10$ for the cases of $\fseed=0.1$ and 0.01 are denoted by solid and dashed lines, respectively.
-From theoretical models, the slope is estimated as $k_\mathrm{L} \simeq -0.91$ and $-0.62$ for quasars at $\Muv=-27$ and $-23$ mag, respectively.
+Redshift evolution of the quasar number density at different UV magnitudes.
+The theoretical prediction from $z=6$ to $10$ are shown for the cases of $\fseed=0.1$ (solid) and 0.01 (dashed), respectively.
+From the models at $z\geq 6$, the quasar number is characterized with $\propto 10^{k_{\rm L}z}$,
+where the index is $k_\mathrm{L} \simeq -0.91$ 
+and $-0.62$ for quasars at $\Muv=-27$ and $-23$ mag, respectively.
 The observational data at lower redshifts $z\sim 0-6$ are from the Subaru HSC results \citep{2018PASJ...70S..34A,2018ApJ...869..150M,2020ApJ...904...89N},
@@
 For instance, \citet{2019ApJ...884...30W} proposed a decay index of $k_{\rm L}=-0.78\pm{0.18}$ for those bright quasars at $6\lesssim z \lesssim 7$,
-consistent with our model prediction \blue{where $k_\mathrm{L} \simeq -0.84$.}
+consistent with our model prediction with $k_\mathrm{L} \simeq -0.84$.
 
@@
 Evolutionary tracks of individual seed BHs with the the best-fit growth model parameters in the $\fseed=0.01$ case.
-Among all the samples, we select BHs that reach $M\geq 10^8~\Msun$ at $z=6$ (solid curves). 
-The heaviest 7 BHs with $M_\bullet \geq 10^9~\Msun$ at $z=6$ are highlighted with colors. 
-For the heaviest BHs, we draw the assembly history assuming an exponential growth with a constant Eddington ratio: 
-the $\lambda$-value found at $z=6$ for each BH (dotted curves; extrapolation with an observed value of $\lambda$) and 
-$\lambda =1$ (dashed curves; continuous Eddington growth).
-%constant $\lambda$ keeping the $z=$ 6 value with dotted lines and 
-%Eddington limit growth with $\lambda=1$ with dashed lines.
+Among all the samples, we select BHs that reach $M\geq 10^8~\Msun$ at $z=6$ (grey thin curves). 
+The six heaviest SMBHs ($M_\bullet \geq 10^9~\Msun$ at $z=6$) are highlighted with colored curves. 
+For those BHs, we draw the assembly history assuming an exponential growth with a constant Eddington ratio: 
+the $\lambda$-value seen at $z=6$ for each BH (dotted) and $\lambda =1$ (dashed).
+Our best-fit model explains the existence of the most massive BHs via multiple accretion episodes with different values of $\lambda$,
+and reproduces the mass and Eddington ratio for the highest-$z$ quasar (\citealt{2021ApJ...907L...1W}; red diamond).
 }
 \label{fig:Mevol}
+\vspace{5mm}
 \end{figure*}
@@
 because observed quasars are limited by the depths of photometric surveys, not by the BH mass or Eddington ratio.
-This unavoidable bias of quasar surveys can be corrected by taking into account the survey completeness;
-however, it is still challenging to constrain the low-mass end of the BHMF and low-$\lambda$ end of the ERDF.
+This unavoidable bias of quasar surveys can be corrected by taking into account the survey completeness.
+%however, it is still challenging to constrain the low-mass end of the BHMF and low-$\lambda$ end of the ERDF.
 %that the surveys are not sensitive to.

### 2022-09-29 ms.tex
version0929; me added t_Q paragraph; before k's memos

@@
 \blue{
-Moreover, some individual quasar observations give exceptionally small proximity zone sizes,
-indicating short lifetime of their luminous phase $t_{\rm Q} \lesssim 10^4$ yr.
-The short quasar lifetime may be due to the young age of quasars ionizing the surrounding IGM \citep[e.g.,][]{2020ApJ...903...60I,2021ApJ...917...38E}.
-Our episodic quasar growth model agrees with this argument,
-besides alleviates the growth tension of SMBHs by episodic accretion bursts.
-In other words, the lifetime of luminous quasar phase is the cumulative time of accreting activity in the current episode.
+Moreover, observations on the quasar proximity zone size which traces the ionized IGM bubbles
+produce important constraints on the time $t_{\rm Q}$ elapsed with luminous quasar phase
+\citep{2007MNRAS.374..493B,2016ApJ...824..133K,2017ApJ...840...24E,2019ApJ...884L..19D}.
+Measurements with this method typically point toward a luminous quasar lifetime of $t_{\rm Q} \sim 1$ Myr,
+while some individual quasars which are inferred to have exceptionally small proximity zone sizes
+with $t_{\rm Q} \lesssim 10^4$ yr,
+may be due to the young age of quasars ionizing the surrounding IGM \citep[e.g.,][]{2020ApJ...903...60I,2021ApJ...917...38E}.
+Viewed from our episodic BH growth model, the timescale $t_{\rm Q}$ corresponds to the current duration of quasar activity,
+thus not necessary the entire quasar lifetime with accretion.
+Therefore, our model implies that the difference of the small v.s. normal proximity zone sizes just originates from the different stages they are observed.
+% Our episodic quasar growth model agrees with this argument,
+% besides alleviates the growth tension of SMBHs by episodic accretion bursts.
+% In other words, the lifetime of luminous quasar phase is the cumulative time of accreting activity in the current episode.
+On the other hand, transverse proximity effect probes a longer timescale ($\sim 10-100$ Myr) light curve from quasars through the ionizing light-echo in the IGM
+\citep{2004ApJ...612..706A,2008ApJ...674..660V,2019ApJ...882..165S,2022MNRAS.516..582K}.
+In our episodic BH accretion model, the time duration of accretion activity typically lasts for $\tau\sim 20$ Myr,
+and we predict uniform distributions of luminous quasars with lifetimes within this timescale.
+Besides, there is a non-negligible fraction $f_{2 \tau}$ of actively accreting quasars to have another super-Eddington in the previous episode,
+bearing light-echoes with timescales longer than $\tau$ but sensitive to the transverse proximity effect measurements \citep[see][]{2022MNRAS.516..582K}.
+We estimate it to be $f_{2 \tau}\simeq$ 0.09, 0.12, and 0.17,
+for massive BH sub-samples with $M_\bullet>10^7$, $10^8$ and $10^9~\Msun$ at $z=$ 6, respectively.
+Investigations on the quasar light curves can set strong constraints on the model prescription and improve our understanding on the BH growth histories through luminous quasar phases.
 }

### 2022-09-30 ms.tex
version0930; before M revision

--- 2022-09-28 ms.tex
@@
 key information on the physics determining the radiative and accretion processes of supermassive 
-black holes (BHs) in high-redshift quasars.
+black holes (BHs) in high-$z$ quasars.
 Although the shape of the QLF has been constrained by recent wide and deep surveys,
-it still remains challenging to develop a theoretical model that explains its redshift evolution with BH growth self-consistently.
+it still remains challenging to develop a theoretical model that explains its redshift evolution associated with BH growth self-consistently.
 In this study, based on a semi-analytical model for the formation and growth of seed BHs
@@
 Our best-fit model to reproduce the observed QLF and BHMF at $z\simeq 6$
-suggests that several episodes of super-Eddington accretion occur
+suggests that several episodes of moderate super-Eddington accretion occur
 and each of them lasts $\tau \simeq 20-30$ Myr.
@@
 owing to detection limits of quasar surveys.
-The predicted redshift evolution of both QLF and BHMF of the earliest BHs suggests a rapid decay of their number and mass density 
+The predicted redshift evolution of the QLF and BHMF of the earliest BHs suggests a rapid decay of their number and mass density 
 in a cosmic volume toward higher redshifts of $z>6$.
@@
 The cosmic BH accretion history and their radiative efficiency are well constrained by 
-comparing the mass density of supermassive BHs (SMBHs) in the local universe and the mass accreted onto BHs inferred from
+comparing the mass density of supermassive black holes (SMBHs) in the local universe and the mass accreted onto BHs inferred from
 the integration of the QLF based on multi-wavelength observations
@@
 The shapes of the QLF and BHMF contain key information on the physics characterizing the radiative 
-and accretion processes of high-z SMBHs, as well as seeding mechanisms in principle.
+and accretion processes of high-$z$ SMBHs, as well as their seeding mechanisms in principle.
 Two approaches have been utilized to model those distribution functions.  
@@
 the formation pathway of seed BHs has been extensively investigated by numerical simulations and semi-analytical studies
-\citep{2006MNRAS.370..289B,2009ApJ...696.1798T,2012MNRAS.422.2051N,2014ApJ...781...60H,
+\citep{2006MNRAS.370..289B,2009MNRAS.396..343R,2009ApJ...696.1798T,2012MNRAS.422.2051N,2014ApJ...781...60H,
 2015MNRAS.448..568H,2018MNRAS.474.3825V,2021MNRAS.506..613S,2022arXiv220614459T,2022arXiv220505717B}.
@@
 \citep{2008MNRAS.391.1961D,2009ApJ...695.1430A,2015MNRAS.450.4350I},
-recent studies by \citet{2021MNRAS.503.5046L} and \citet{2021ApJ...917...60L} found that the heavy-seed formation
+recent studies by \citet{2021MNRAS.503.5046L} and \citet{2021ApJ...917...60L} found that the formation of heavy seeds
 can be accelerated in rare, overdense regions of the universe, where non-linear galaxy clustering boosts the irradiation intensity
@@
 owing to detection limits of quasar observations.
-Furthermore, the evolution of the QLF and BHMF implies a rapid decay of 
-their number and mass density toward higher redshifts of $z>6$.
+We further discuss the redshift evolution of the QLF and BHMF at $z\gtrsim 6$,
+and give implications for future observations.
 Those results will be tested by future deep and wide-field surveys with JWST, RST, and Euclid,
@@
 In Section~\ref{sec:method}, we describe the semi-analytical model for BH seeding and subsequent growth via accretion,
-and explain the MCMC fitting procedure to constrain the theoretical models by the observations.
+and explain the MCMC fitting procedure to constrain the theoretical model by the high-$z$ quasar observations.
 %The physical parameters to characterize the QLF and BHMF in the model are optimized with the MCMC fitting to reproduce 
@@
 and discuss the key physics to determining the BH growth.
-In Section~\ref{sec:cosm}, we discuss the cosmological evolution of the BHMF and QLF suggested by our best-fit models, 
+In Section~\ref{sec:cosm}, we discuss the cosmological evolution of the BHMF and QLF suggested by our best-fit model,
 as well as the detection number of those BHs at $z\sim 6-10$ with Euclid and RST.
@@
 \citep{2001ApJ...561L..55O,2013ApJ...778..178H,2013A&A...558A..59S,2015MNRAS.452..755S,2018MNRAS.474.2757H}.
-For $\dot{M}_\ast > \Mdot_\mathrm{crit}$, the stellar envelope inflates owing to rapid entropy injection through accreting matter,
+For $\dot{M}_\star > \Mdot_\mathrm{crit}$, the stellar envelope inflates owing to rapid entropy injection through accreting matter,
 keeping its surface temperature as low as $T_\mathrm{eff} \simeq 5000$ K. 
@@
 in the range of $\dot{M}_\star\gtrsim 0.1~\Msunyr$ \citep{2016PhRvD..94b1501S,2017ApJ...842L...6W,2019PASA...36...27W}.
-On the other hand, for $\dot{M}_\ast \leq \Mdot_\mathrm{crit}$, the protostar begins to contract by loosing its thermal energy via radiative diffusion
+On the other hand, for $\dot{M}_\star \leq \Mdot_\mathrm{crit}$, the protostar begins to contract by loosing its thermal energy via radiative diffusion
 and increases its surface temperature to $T_\mathrm{eff} \sim 10^5$ K.
@@
 via stellar winds \citep{2003ApJ...591..288H,2010ApJ...714.1217B,2015MNRAS.451.4086S}.
-Therefore, we consider that the stellar mass with interest is equal to that of its remnant BH.
+Therefore, we consider that the stellar mass of interest is equal to that of its remnant BH.
 
@@
 and the cumulative number distribution of BHs formed by prior episodes is shown in green.
-The majority of seed BHs form in the epoch of $20\lesssim z \lesssim 40$.
-Overall, the distribution is extended to $M_\bullet \gtrsim 10^5~\Msun$, 
-imprinted with the halo assembly and environmental effects discussed in Section~\ref{sec:seed}.
+The majority of seed BHs form in the epoch of $20\lesssim z \lesssim 40$,
+and the distribution is extended to $M_\bullet \gtrsim 10^5~\Msun$, 
+reflecting the halo assembly and environmental effects discussed in Section~\ref{sec:seed}.
 }
@@
 Fig.~\ref{fig:seedmf} presents how the seed mass function is developed in each redshift interval.
-The majority of seed BHs forms in the epoch of $20\lesssim z \lesssim 40$, and the distribution function is 
-extended to $M_\bullet \gtrsim 10^5~\Msun$, imprinted with the halo assembly and environmental effects.
-Note that we consider massive seed BHs formed from low-metallicity environments,
+The majority of seed BHs form in the epoch of $20\lesssim z \lesssim 40$, and the distribution function is 
+extended to $M_\bullet \gtrsim 10^5~\Msun$, reflecting the halo assembly and environmental effects.
+Note that in this study, we consider massive seed BHs formed from low-metallicity environments,
 but neglect a potential contribution from BHs left behind the second-generation star formation
@@
 \end{equation}
-where $\lambda \equiv L/L_\mathrm{Edd}$ is the luminosity-based Eddington ratio,
+where $\lambda$ is the luminosity-based Eddington ratio,
+% $\lambda \equiv L/L_\mathrm{Edd}$ 
 and $\Mdot_\mathrm{Edd} \equiv L_{\mathrm{Edd}}/\eta_0 c^2$ is the Eddington accretion rate with a radiative efficiency of $\eta_0=0.1$ \citep{1973A&A....24..337S},
@@
 A series of radiation hydrodynamical simulations for BH accretion
-suggest that the gas supplying from galactic scales into the nuclear scale does not sustain 
+suggest that the gas supplying from galactic scales into the nuclear scale is not high enough to sustain 
 super-Eddington accretion when the BH mass is higher than the characteristic value \citep{2021ApJ...907...74T}.}.
@@
 Schematic illustration of the numerical procedure for calculating the BH mass function
-between intervals with a duration of $\tau$.
+between a time interval with a duration of $\tau$.
 The time evolution of the distribution is calculated by adding newly-forming seed BHs and 
@@
 For a newly formed seed BH with $M_{\rm k}$ during the interval (i.e., $T_0 \leq t_k < T_0+\tau$), 
-we evolve the BH mass in $\Delta t = T_0+\tau -t_k$ and add it to the mass distribution of the existing BH.
+we evolve the BH mass in $\Delta t = T_0+\tau -t_k$ and add it to the mass distribution of the existing BHs.
 }
@@
 \citep{2006ApJ...639..700H,2009ApJ...698.1550H}.
-For type-I AGNs at low redshifts, the ERDF is characterized with a Schechter function
+For unobscured AGNs at low redshifts, the ERDF is characterized with a Schechter function
 \citep{2015MNRAS.447.2085S,2016ApJ...826...12J,2018MNRAS.474.1225A}.
@@
 that decrease mildly toward $\lambda \sim 0.1-0.01$ with $\lesssim$ 100 Myr after the peak activity \citep{2011ApJ...737...26N}.
-Moreover, a turnover in the ERDF at the lowest value of $\lambda\lesssim 0.01-0.001$ is suggested by observations \citep{2018MNRAS.474.1225A}.
+Moreover, a turnover in the ERDF at the lowest value of $\lambda\lesssim 0.01-0.001$ is suggested by observations of X-ray selected AGNs \citep{2018MNRAS.474.1225A}.
 
@@
 In this way, we give a different growth speed of a BH in every period with a duration of $\tlife$ until $z=6$ 
-(the corresponding cosmic age is $t_{\rm H}\gtrsim 900$ Myr).
+(the corresponding cosmic age is $t_{\rm H}\simeq 913$ Myr).
 This treatment enables us to capture the nature of accretion bursts and prohibit an unrealistically 
@@
 We take three different values of $\fseed = 1$, $0.1$, and $0.01$, and explore its effect on producing the QLF and BHMF.
-Since we find that the results in the cases of $\fseed = 1$ and $0.1$ are overall similar,
+Since we find that the results in the cases of $\fseed = 1$ and $0.1$ are quantitatively similar,
 we thus show only the cases with $\fseed=0.1$ and $0.01$ in the following discussion.
@@
 We first set a series of checkpoints with an interval of $\tlife$, 
-tracing back from $t_{\rm H}(z=6)$ to just prior than the first seed formation time $t_1$, where $t_i$ is the $i$-th seed forming time
+tracing back from $t_{\rm H}(z=6)$ to just prior to the first seed formation time $t_1$, where $t_i$ is the $i$-th seed forming time
 as defined in Section~\ref{sec:seed} ($1\leq i\leq N_{\rm tot}$).
@@
 %
-where $\lambda_\ast$ is the Eddington ratio required for a BH with $M_{\bullet,0}$ to grow up to $\Mbh$ within $\Delta t$
+where $\lambda_\ast$ is the Eddington ratio required for a BH with $M_{\bullet,0}$ to grow up to $\Mbh$ in $\Delta t$,
 and is calculated analytically from Eq.~(\ref{eq:mdot}) by
@@
 and the derivative of ($\D \ln \lambda_\ast / \D  \Mbh )|_{\Delta t, M_{\bullet,0}}$ is also determined.
-For existing BHs formed prior to this checkpoint, we calculate the evolution of the mass distribution by setting $\Delta t = \tlife$.
+For existing BHs formed before this checkpoint, we calculate the evolution of the mass distribution by setting $\Delta t = \tlife$.
 For a seed BH formed during this cycle (i.e., $T_0\leq t_k < T_0+\tlife$), 
@@
 because quasar surveys with optical and near-infrared telescopes are not sensitive to the obscured quasar population at high redshifts,
-i.e., the number of fainter quasars observed as type-I AGNs is largely reduced by the obscuration effect
+i.e., the observed number of fainter quasars is largely reduced by the obscuration effect
 \citep{2003ApJ...598..886U,2007A&A...463...79G,2008A&A...490..905H,2014ApJ...786..104U,2014MNRAS.437.3550M}.
@@
 \citep[see][for a review]{2018ARA&A..56..625H}.
-In addition, dense gas clouds at galactic larger scales may have a significant contribution to quasar obscuration at 
+In addition, dense gas clouds at larger galactic scales may have a significant contribution to quasar obscuration at 
 higher redshifts \citep{2020MNRAS.495.2135N}.
@@
 %However, we adopt the prescription of the obscured fraction constrained from quasar observations at $z\lesssim 5$ 
-However, the physical origin and conditions for high-z quasar obscuration has been poorly understood yet.
+However, the physical origin and conditions for high-$z$ quasar obscuration have been poorly understood yet.
 Observationally, the obscured fraction of AGNs with hydrogen column density of $N_{\rm H}>10^{22}~{\rm cm}^{-2}$
@@
 
-In this study, we adopt the obscuration fraction $\fobsc$ given by \cite{2014ApJ...786..104U} as
+In this study, we adopt the obscuration fraction $\fobsc$ based on X-ray observations \citep{2014ApJ...786..104U}
+and rewrite it with bolometric luminosity as
 %
@@
 %
-Here, we use the bolometric correction factor from the hard X-ray band 
+Here, we use the bolometric correction factor from the hard X-ray band:
 %
@@
 %
-where $a=10.96$, $b = 11.93$, and $c = 17.79$ are given in Eq.~(2) of \citet{2020A&A...636A..73D}. 
+where $a=10.96$, $b = 11.93$, and $c = 17.79$ \citep[see Eq.~(2) in][]{2020A&A...636A..73D}. 
 In our analysis, we neglect the contribution from Compton-thick AGNs with $N_\mathrm{H}>10^{24}$ cm$^{-2}$, 
@@
 %and the uncertainties would affect our analyses for fainter quasars.
-We leave more comprehensive arguments about the quasar obscuration effect for future work.
+We leave more comprehensive arguments about this effect for future work.
 
@@
 %
-Hence, the observed QLF can be produced simultaneously with the BHMF from a set of model parameters, 
-to be compared with the ones from observation.
+Hence, the observed QLF can be produced simultaneously with the BHMF from a set of model parameters.
 
@@
 % prior
-In this analysis, we constrain those parameters to be within certain physically acceptable ranges, 
+In this analysis, we constrain those four parameters to be within certain physically acceptable ranges, 
 assuming a prior function for each quantity.
@@
 The parameter of $\delta$ that characterizes a non-exponential BH growth 
-is constrained at $\log \delta$ from $-4$ to $-0.3$
-\footnote[3]{ We first set a uniform prior at $0\leq \delta \leq 1$, 
+is constrained at $-4 \leq \log \delta \leq -0.3$
+\footnote[4]{ We first set a uniform prior at $0\leq \delta \leq 1$, 
 and find the posterior distribution assembles to $\delta \lesssim 0.1$.
@@
 $\Phi_{\Mbh}^{\rm err} = \pm \{0.2 +   [\log (\Mbh/10^{8.5}~\Msun)]^2/3 \}~{\rm dex}$,
-covering the same mass range as in their bootstrap resamples (see Figure 8 of W10). 
+covering the same mass range as in their bootstrap resamples (see Figure 8 of \citetalias{2010AJ....140..546W}). 
 The observed QLF is taken from \citet{2018ApJ...869..150M} (hereafter \citetalias{2018ApJ...869..150M}) 
-over a wide range of $-30 < \Muv <-22$ mag (see their Table 4 and Figure 13). 
+over a wide range of UV magnitude at $-30 < \Muv <-22$ mag (see their Table 4 and Figure 13). 
 The magnitude bins and the error sizes are given consistently with \citetalias{2018ApJ...869..150M}.
@@
 \centering
-\includegraphics[width=80mm]{f1_corner.pdf}\hspace{3mm}
-\includegraphics[width=80mm]{f2_corner.pdf}
+\includegraphics[width=85mm]{f1_corner.pdf}\hspace{3mm}
+\includegraphics[width=85mm]{f2_corner.pdf}
 \caption{
-Two dimensional posterior distribution of all the model parameters with $\fseed=0.1$ (left) and 0.01 (right), 
+Two dimensional posterior distribution of the four model parameters with $\fseed=0.1$ (left) and 0.01 (right), 
 along with the marginalized one dimensional projection.
@@
 
-For the two cases, the best-fit solution consistently shows a small value of $\delta < 0.1$.
-This result favors the nearly exponential BH growth model with minor mass dependence (Eqs.~\ref{eq:mdot} and \ref{eq:f_M}).
+For the two cases, the best-fit solution consistently yields a small value of $\delta < 0.1$.
+This result favors the nearly exponential BH growth model (Eqs.~\ref{eq:mdot} and \ref{eq:f_M}).
 The typical duration of quasar activity is required to be $\tlife \simeq 20-30$ Myr for both the cases.
@@
 observed in the rest-frame UV spectra \citep[e.g.,][]{2018ApJ...867...30E,2019ApJ...884L..19D}.
-More detailed comparison is discussed in Section~\ref{sec:evol}.
+The characteristic Eddington ratio needs to be close to unity, otherwise the highest luminosity and BH mass
+in the model would differ from those in observations.
+The power-law index of $\alpha$ in the ERDF increases as the seeding fraction decreases.
+Thus, a more significant fraction of BHs actively grow with $\lambda \gtrsim 1$ and contribute to developing of the QLF and BHMF.
 
@@
 The best-fit parameters optimized by MCMC sampling for the three different cases of $\fseed$.
-The fitting performance is characterized by the relative magnitudes of the $\chi^2$ value.}
+The fitting performance is quantified with the relative magnitudes of the $\chi^2$ value.}
 \end{deluxetable}
@@
 and the ten-fold difference in $\fseed$ is nearly compensated.
-The characteristic Eddington ratio needs to be close to unity, otherwise the highest luminosity and BH mass
-in the model would differ from those in observations.
-On the other hand, the power-law index of $\alpha$ in the ERDF increases as the seeding fraction decreases,
-indicating that the fraction of active BHs with $\lambda \gtrsim 1$ is elevated. 
-Thus, with lower seeding fractions, the high-$z$ quasar assembly ought to experience more active growth phases to reproduce the observations.
 
@@
 
-In Fig.~\ref{fig:fitmf}, we show the total BHMF at $z=$ 6 reproduced by the best-fit parameters for 
+In Fig.~\ref{fig:fitmf}, we show the BHMFs at $z=$ 6 reproduced by the best-fit parameters for 
 $\fseed = 0.1$ (left) and $0.01$ (right) as well as the statistical error, 
@@
 Overall, our best-fit BHMF model agrees with their constraints in this mass range.
-The power-law index of the BHMF ($\alpha_{M_\bullet} \equiv \D \ln \Phi_{M_\bullet}/\D \ln M_\bullet$) is as steep as $\alpha_{M_\bullet}\lesssim -1$
+The power-law index of the BHMF ($\gamma{M_\bullet} \equiv \D \ln \Phi_{M_\bullet}/\D \ln M_\bullet$) is as steep as $\gamma_{M_\bullet}\lesssim -1$
 at $M_\bullet \gtrsim 10^7~(3\times 10^7)~\Msun$ for $\fseed = 0.1 ~(0.01)$.
@@
 %The solid (dashed) lines denote the cases with $\fseed=0.1$ (0.01).
-{\it Right}: the cumulative mass density for BHs in three different mass ranges: $M_\bullet \leq 10^6~\Msun$ (blue), $10^6~\Msun < M_\bullet < 10^8~\Msun$ (orange),
+{\it Right}: the cumulative mass density for BHs in a comoving volume at three different mass ranges: $M_\bullet \leq 10^6~\Msun$ (blue), $10^6~\Msun < M_\bullet < 10^8~\Msun$ (orange),
 and $M_\bullet \geq 10^8~\Msun$ (green).
@@
 for $\fseed = 0.1$ (left) and $0.01$ (right).
-The solid and dashed curve is the {\it unobscured} and {\it intrinsic} QLF, respectively.
+The solid and dashed curve is the unobscured and intrinsic QLF, respectively.
 The latter one includes both obscured and unobscured quasars.
@@
 In addition, we show upper bounds of the faint quasar abundance at $\Muv\gtrsim -22~{\rm mag}$ \citep[green;][]{2022NatAs...6..850J}
-based on a search for point sources in the survey fields of the Hubble Space Telescope (HST).
+based on a search for point sources in the survey fields of the Hubble Space Telescope.
 Our unobscured QLF lies within the constraints.
@@
 Based on the X-ray selected faint quasars, \cite{2019ApJ...884...19G} reported a number density of 
-faint quasars in orange, which is substantially higher than that expected from extrapolation of the rest-UV based QLF by 
-\citetalias{2018ApJ...869..150M} (dotted curve) down to the faint end of $\Muv\gtrsim -22~{\rm mag}$.
-In Fig.~\ref{fig:fitlf}, we take their $z=5.55$ luminosity function correcting for redshift evolution 
-with a scale factor of $10^{-0.72\Delta z}$ \citep{2016ApJ...833..222J}, where $\Delta z=0.45$.
-Our best-fitted intrinsic QLF (dashed curve) is broadly consistent with the faint-end of the X-ray based QLF within the errors.
+faint quasars at $\Muv \gtrsim -22$.
+Here we take their $z=5.55$ luminosity function correcting for redshift evolution 
+with a scale factor of $10^{-0.72\Delta z}$ \citep{2016ApJ...833..222J}, where $\Delta z=0.45$,
+shown in orange in Fig.~\ref{fig:fitlf}.
+These values are substantially higher than that expected from extrapolation of the rest-UV based QLF by 
+\citetalias{2018ApJ...869..150M} (dotted curve) down to the faint end.
+In contrast, our best-fitted intrinsic QLF (dashed curve) is broadly consistent with the faint-end of the X-ray based QLF within the errors.
+
 From another point of view, the discrepancy between the UV and X-ray QLFs at the faint end would be explained by the fact that 
@@
 The black solid and dashed curves are the unobscured and intrinsic QLF, respectively, and the shaded region presents the $1\sigma$ statistical error.
-The expected depths and volumes of future surveys with Wide RST (blue) and Wide Euclid (red) are overlaid in each panel (see Table~\ref{tab:N_detect}).
+The expected depths and volumes of future surveys with Wide Euclid (blue; $YJH=23$ mag) and Wide RST (red; $YJH=27$ mag) are overlaid in each panel (see Table~\ref{tab:N_detect}).
 For comparison, the galaxy UV luminosity functions are plotted with the data points (grey) and the fitting functions in purple with a Schechter (dotted) and double power-law (dash-dotted) shape.
@@
 in terms of mass occupation \citep[e.g.,][]{2014ApJ...786..104U}.
-Namely, the characteristic mass at $z\simeq 6$ in the BHMF (i.e., $\alpha_{M_\bullet}=-1$) is $M_\bullet \simeq 10^7~(3\times 10^7)~\Msun$ for 
-$\fseed=0.1~(0.01)$.
+% Namely, the characteristic mass at $z\simeq 6$ in the BHMF (i.e., $\alpha_{M_\bullet}=-1$) is $M_\bullet \simeq 10^7~(3\times 10^7)~\Msun$ for 
+% $\fseed=0.1~(0.01)$.
 Moreover, the seeding process affects the evolution of the mass density more substantially for less massive BHs,
@@
 Upper bounds on the accreted-mass density onto massive BHs (black arrows) prohibits overproduction of low mass BHs at cosmic dawn.
-Our quasar sample in the biased, overdense region of the universe (haboring DM halos with $\Mh\gtrsim 10^{11}~\Msun$) 
-are consistent with the constraint, unlike models that require a large number of stellar-mass BH remnants \citep[see also][]{2009ApJ...696.1798T}.
+The mass density of BHs formed in the biased, overdense region of the universe %(haboring DM halos with $\Mh\gtrsim 10^{11}~\Msun$) 
+is consistent with the constraint, unlike models that require a large number of stellar-mass BH remnants \citep[see also][]{2009ApJ...696.1798T}.
 
@@
 \tablewidth{0pt} 
-\tablecaption{Detection Number of Quasars Estimated for Future Surveys \label{tab:N_detect}} %! reference indexing
+\tablecaption{Detection Number of Quasars in Future Surveys \label{tab:N_detect}} %! reference indexing
 \tablehead{
@@
 Wide Euclid\dag & 15000  & selection func.  & --                             &  $204 (117)$                &   $16 (6)$             & $7 (2)$ & --  \\
-Wide Euclid & 15000  & $\Muv=-26$  & $154^{+100}_{-38}$    &  $12^{+59}_{-50}$    &   $1^{+4}_{-3}$    & -- & --  \\
+% Wide Euclid & 15000  & $\Muv=-26$  & $154^{+100}_{-38}$    &  $12^{+59}_{-50}$    &   $1^{+4}_{-3}$    & -- & --  \\
 \hline
 Wide RST    &  2000  & $YJH$  27   & $6759_{-3185}^{+15} $ &  $1514_{-558}^{+169}$ &  $349_{-131}^{53}$ & $85_{-48}^{+23}$ & $25^{+12}_{-15}$  \\
-Wide RST    &  2000  & $\Muv=-26$ & $21_{-5}^{+13} $      &  $2_{-7}^{+8}$        &  --  & -- & --  \\
+% Wide RST    &  2000  & $\Muv=-26$ & $21_{-5}^{+13} $      &  $2_{-7}^{+8}$        &  --  & -- & --  \\
 \enddata
@@
 The integration of the QLF is conducted for brighter populations than the 5$\sigma$ point source detection limits of 
-the $YJH$ bands in each survey (24 mag for Euclid and 27 mag for the RST), and the absolute magnitude with $\Muv \leq-26$ mag.\\
+the $YJH$ bands in each survey (24 mag for Euclid and 27 mag for the RST).%, and the absolute magnitude with $\Muv \leq-26$ mag.\\
 \dag: To mimic realistic quasar identification capability, we show the detection numbers with $YJK=23$ mag in comparison with
@@
 Fig.~\ref{fig:LFs} presents our prediction of QLFs at $z>6$ taken from the BH growth model with $\fseed=0.01$.
-We divide the cosmological QLF evolution results into four different epochs; (a) $z\simeq 7$, (b) $z\simeq 8$, (c) $z\simeq 9$, and (d) $z\simeq 10-13$.
+We divide the cosmological QLF evolution results into four different epochs; (a) $z\sim 7$, (b) $z\sim 8$, (c) $z\sim 9$, and (d) $z\sim 10-13$.
 The black solid and dashed curves show the QLF for the unobscured population 
@@
 Table~\ref{tab:N_detect} summarizes the survey coverage and lists the expected detection number of quasars with varying limiting magnitudes.
-We first integrate the QLFs starting from the 5$\sigma$ point source detection limits (24 mag for Euclid and 27 mag for RST, respectively).
+We first integrate the QLFs starting from the 5$\sigma$ point source detection limits (\blue{$YJH$=} 24 mag for Euclid and 27 mag for RST, respectively).
 With the limiting magnitude, Euclid will identify quasars up to $z\lesssim 9$ and discover $\simeq 100-700$ quasars at $z\simeq 7-8$.
@@
 Therefore, the estimated values above give upper bounds of the number of detectable high-$z$ quasars.
-Adopting $YJH=23$ mag as the effective depth based on the quasar selection methods for Euclid \citep{2019Barnett},
+Indeed, \citet{2019Barnett} investigated the efficiency of quasar selection and
+found that combined with ground-based optical observations,
+high-$z$ quasars can be identified down to $YJH \sim$ 23 mag.
+Adopting $YJH=23$ mag as the effective depth, %based on the quasar selection methods for Euclid \citep{2019Barnett},
 our predicted detection numbers are in good agreement with their results but shows a better match for the case with extrapolation of $10^{-0.72z}$
@@
 
-Luminous quasars with $\Muv \lesssim -26$ mag are expected to be marginally detected by the RST and Euclid up to $z\sim 7$ and 8, respectively.
+Luminous quasars with $\Muv \lesssim -26$ mag are expected to be marginally detected by the RST and Euclid up to $z\sim 7$ and 8, respectively,
+with $\sim 1$ detection number predicted by the integration over model QLFs.
 However, \citet{2019BAAS...51c.121F} proposed that quasar detection can reach $z\sim 9$ by the two surveys
 because a moderate decline of the quasar number density ($\propto 10^{-0.78z}$) is assumed.
-The difference of predictions is to be tested by upcoming high-$z$ quasar observations (see the discussion below).
+The differences in those predictions will be tested by upcoming high-$z$ quasar observations (see more discussion below).
 %Studies that take into account contamination from MLT dwarfs and compact early-type galaxies and quasar selction method
@@
 We also show the galaxy UV luminosity function in each panel
-along with the fitting functions in a Schechter (dotted) and double powe-law (dashed-dotted) shape extended to the brighter end
+along with the fitting function in a Schechter (dotted) and double powe-law (dashed-dotted) shape extended to the brighter end
 \citep{2013MNRAS.432.2696M, 2016ApJ...819..129O, 2018ApJ...867..150M, 2019ApJ...883...99S, 2020MNRAS.493.2059B,
@@
 %%%%%%%
-\begin{figure}
+\begin{figure*}
 \centering
 %\includegraphics[width=160mm]{QLF_rhoz.png}
-\includegraphics[width=80mm]{QLFmag_z.pdf}
+\includegraphics[width=130mm]{QLFmag_z.pdf}
 \caption{
@@
 \vspace{5mm}
-\end{figure}
+\end{figure*}
 
@@
 previous observational studies \citep[e.g.,][]{2001AJ....122.2833F,2013ApJ...768..105M,2016ApJ...833..222J,2019ApJ...884...30W}.
-For instance, \citet{2019ApJ...884...30W} proposed a decay index of $k_{\rm L}=-0.78\pm{0.18}$ for those bright quasars at $6\lesssim z \lesssim 7$,
-consistent with our model prediction with $k_\mathrm{L} \simeq -0.84$.
+For instance, \citet{2019ApJ...884...30W} proposed a decay index of $k_{\rm L}=-0.78\pm{0.18}$ for those bright quasars at $6\lesssim z \lesssim 7$.
+The slopes in our model prediction of $\Muv <=-26$ are slightly steeper ($k_\mathrm{L} \simeq -0.84$ at $\Muv=-26$),
+but consistent with their result within the error range.
 
@@
 where $\mathcal{N}$ is the frequency of super-Eddington accretion bursts with $\lambda \geq 1$ and $\Delta t_{\rm H}\simeq 450$ Myr.
-For BH populations grown to $M_\bullet>10^7$, $10^8$ and $10^9~\Msun$ at $z=$ 6,
-the average duty cycle is found to be $\langle f_{\rm duty}\rangle \simeq 0.12$, 0.15, and 0.19
-(i.e., $\Delta t_{\rm H} \times f_{\rm duty} \simeq 55$, 69, and 85 Myr), respectively.
-On the other hand, the average duty cycle for the entire BH population is calculated as $f_{\rm duty}= 0.075$,
-adopting this ERDF (see Section~\ref{sec:fitting_result}), which is significantly lower than those for massive BH sub-samples.
-Therefore, we suggest that SMBHs observed in $z\simeq 6$ quasars are biased in a way that
-the more massive populations undergo longer active accretion episodes along their growth.
+For BH populations grown to $M_\bullet \geq10^7$, $10^8$ and $10^9~\Msun$ at $z=$ 6,
+the average duty cycle is found to be $\langle f_{\rm duty}\rangle \simeq 0.12$, 0.15, and 0.19, respectively.
+% (i.e., $\Delta t_{\rm H} \times f_{\rm duty} \simeq 55$, 69, and 85 Myr), respectively.
+On the other hand, the average duty cycle for the entire BH population is calculated as $f_{\rm duty}= \langle 0.075\rangle $
+adopting this ERDF (see Section~\ref{sec:fitting_result}), and is significantly lower than those for massive BH sub-samples.
+Therefore, we suggest that SMBHs observed in $z\sim 6$ quasars are a biased population
+that undergoes longer active accretion episodes along its growth.
 
@@
 In Fig.~\ref{fig:Mevol}, we show the BH growth tracks that end up with $M_\bullet>10^8~\Msun$ by $z=6$ (grey curves).
-In this sub-sample, we find five BHs heavier than $M=10^9~\Msun$ (highlighted with colored solid curves),
+In this sub-sample, we find six BHs heavier than $M=10^9~\Msun$ (highlighted with colored solid curves),
 all of which indicate $\lambda \lesssim 1$ at the  $z=6$ snapshot.
@@
 
-\blue{
-Moreover, some individual quasar observations give exceptionally small proximity zone sizes,
-indicating short lifetime of their luminous phase $t_{\rm Q} \lesssim 10^4$ yr.
-The short quasar lifetime may be due to the young age of quasars ionizing the surrounding IGM \citep[e.g.,][]{2020ApJ...903...60I,2021ApJ...917...38E}.
-Our episodic quasar growth model agrees with this argument,
-besides alleviates the growth tension of SMBHs by episodic accretion bursts.
-In other words, the lifetime of luminous quasar phase is the cumulative time of accreting activity in the current episode.
-}
+The measurement of the ionization state of the intergalactic medium (IGM) surrounding a quasar is
+a powerful tool to constrain the timescale of $t_{\rm Q}$ in a luminous quasar phase
+\citep{2007MNRAS.374..493B,2016ApJ...824..133K,2017ApJ...840...24E,2019ApJ...884L..19D}.
+Recent observations of the line-of-sight hydrogen Ly$\alpha$ proximity zone sizes indicate
+a short quasar age of $t_{\rm Q} \sim 1$ Myr on average, while the ages of some individual quasars are
+inferred to be even shorter than $t_{\rm Q} \sim 0.1$ Myr \citep[e.g.,][]{2020ApJ...903...60I,2021ApJ...917...38E}.
+However, we note that the line-of-sight proximity effect is only sensitive to the most recent activity of quasars.
+Alternatively, the transverse proximity effect is useful to probe a longer quasar activity comparable to the Salpeter timescale \citep{2004ApJ...612..706A,2008ApJ...674..660V,2019ApJ...882..165S}.
+Recently, \citet{2022MNRAS.516..582K} proposed a new technique to photometrically map the quasar light echoes using Ly$\alpha$ forest tomography
+and discussed an efficient observational strategy.
+With our MCMC fitting result reproducing the observed QLF and BHMF, each quasar activity is required to last for $\tau \simeq 20$ Myr on average.
+Moreover, a significant fraction ($\sim 10-20\%$) of the massive BHs with $M_\bullet \gtrsim 10^8~\Msun$ in our sample experience
+two successive active phases with a total active duration of $\sim 30-40$ Myr at $z\simeq 6$.
+Therefore, direct measurements of the distribution of $\tau$ in future observations will test our prediction on quasar activity and
+improve our understanding on the BH growth histories through luminous quasar phases.
 
@@
 
-It is challenging to discuss the properties of the underlying quasar population
-%Discussion on quasar \textit{intrinsic} properties is naturally difficult, 
-because observed quasars are limited by the depths of photometric surveys, not by the BH mass or Eddington ratio.
-This unavoidable bias of quasar surveys can be corrected by taking into account the survey completeness.
-%however, it is still challenging to constrain the low-mass end of the BHMF and low-$\lambda$ end of the ERDF.
-%that the surveys are not sensitive to.
-In this section, we examine the effect of flux-limited quasar surveys on the observed ERDF, 
-taking advantage of our complete sample of high-$z$ BH populations in the whole luminosity range.
+In general, it is challenging to unveil the properties of the underlying quasar population
+because of the limitation of the photometric depths of quasar surveys.
+In this section, we examine how the unavoidable bias affects the properties of the ERDF for observed quasars,
+taking our complete sample of high-$z$ BH populations in the whole luminosity range.
 
 Based on the quasar sample from the best-fit model described in Section~\ref{sec:evol},
-we select quasars with bolometric luminosity limits $L_{45}=10^{45}~\mathrm{erg~s^{-1}}$ and $L_{46}=10^{46}~\mathrm{erg~s^{-1}}$.
-In Fig.~\ref{fig:lhist}, we present the intrinsic ERDFs for the whole BH sample (blue)
-and the selected sample with a luminosity cut of $\Lbol \geq L_{45}$ (orange),
-and $\Lbol \geq L_{46}$ (green).
-For visual comparison, we elevate the observed histograms by a factor of 5 and 30
-for the luminosity limits with $L_{45}$ and $L_{46}$, respectively.
+we select quasars with bolometric luminosity limits of $L_{45}=10^{45}~\mathrm{erg~s^{-1}}$ and $L_{46}=10^{46}~\mathrm{erg~s^{-1}}$.
+In Fig.~\ref{fig:lhist}, we present the intrinsic ERDF for the whole BH sample (blue)
+and the apparent ERDFs for selected samples with a luminosity cut of $\Lbol \geq L_{45}$ (orange),
+and $\Lbol \geq L_{46}$ (green), respectively.
+For illustration purposes, we scale the normalization of the ERDFs with the luminosity cuts, multiplied by a factor of 5 and 30, respectively.
 The Eddington ratio for the whole sample follows a Schechter shape with a majority of inactive quasars,
-while the observed Eddington ratio is biased toward higher values and the distribution results in a log-normal shape. 
-The latter distribution is presented by various observational efforts in the $z\sim$ 6 brightest quasar samples 
-\citep[e.g.,][]{2010AJ....140..546W,2019ApJ...873...35S,2021ApJ...923..262Y,2022arXiv220705113F}.
-However, our best-fit growth model reproducing both the BHMF and QLF at $z\sim$ 6 suggests the existence of
-a large number of underlying BH populations with low Eddington ratios. 
-%based on the best-fit growth model connecting the BH seeding and $z\sim$ 6 BHMF and QLF. 
-We find that the log-normal shape still holds with the lower luminosity cut, 
-%To demonstrate qualitatively the caveat for the detection limit on recovering the intrinsic quasar properties, 
-%we also examine the observed ERDF by selecting quasars with $\Lbol>10^{45}~\mathrm{erg~s^{-1}}$. 
-but a lower detection limit unveils more hidden quasars with low Eddington ratios. 
-Such sub-Eddington BH population at $z>6$ is being probed by the ongoing survey of the Subaru HSC and JWST
-\citep{2019ApJ...880...77O,2021jwst.prop.1967O},
-and will also be explored by upcoming wide-field surveys such as the Vera C. Rubin Observatory, Euclid, and RST.
-% This will be proved by the ongoing observations with the Subaru HSC providing low-luminosity and less-massive BH samples
-% (Onoue et al. in prep) and upcoming optical survey by the Vera C. Rubin Observatory.
-%Therefore, we emphasize that it is imperative to lower the detection limit in order to 
-%understand a more complete quasar sample at high-$z$, 
-%so that the numerous dimly accreting BHs can be shed light on.
+while the observed Eddington ratio is biased toward higher values and the distribution results in a log-normal shape,
+consistent with that of the brightest quasars at $z\sim 6$ \citep[e.g.,][]{2010AJ....140..546W,2019ApJ...873...35S,2021ApJ...923..262Y,2022arXiv220705113F}.
+The log-normal shape still holds with the lower luminosity cut, but a lower luminosity threshold allows us to unveil more hidden quasars with low Eddington ratios.
+The existence of those sub-Eddington BHs at $z>6$ will be probed by the ongoing survey of the Subaru HSC and JWST
+\citep{2019ApJ...880...77O,2021jwst.prop.1967O}, as well as upcoming wide-field surveys such as the Vera C. Rubin Observatory, Euclid, and RST.
 
@@
 \caption{
-The intrinsic Eddington ratio distribution function for the whole BH sample (blue) and the selected sample with
-a luminosity cut of $\Lbol \geq 10^{45}~\mathrm{erg~s^{-1}}$ (orange) and $\Lbol \geq 10^{46}~\mathrm{erg~s^{-1}}$ (green).  
-%Intrinsic ERDF (blue) and the observed ones after imposing selection effects by $\Lbol>L_\mathrm{lim}=10^{45}$ (orange) and 10$^{46}$ erg~s$^{-1}$ (green).
-The observed histograms are elevated by a factor of 5 and 30, for comparison of the distribution shapes.
+The intrinsic Eddington ratio distribution function for the whole BH sample (blue) and the apparent distribution function for selected samples with
+a luminosity cut of $\Lbol \geq 10^{45}~\mathrm{erg~s^{-1}}$ (orange) and $\Lbol \geq 10^{46}~\mathrm{erg~s^{-1}}$ (green), respectively.
+The normalization of the ERDFs with the luminosity cuts is scaled by a factor of 5 and 30, respectively, for illustration purposes.
 The intrinsic ERDF follows the best-fitted Schechter function (dashed curve),
-while the observed ERDF with a detection limit imposed results in a log-normal shape, 
-with a large number of sub-Eddington quasars excluded.
-The log-normal shape still holds with the lower luminosity cut, 
-but a lower detection limit alleviates the selection effect against the low Eddington ratio quasar populations.
-%With decreasing $L_\mathrm{lim}$, more low $\lambda$ population is unveiled.
+while the observed ERDF with a detection limit results in a log-normal shape where most sub-Eddington quasars are excluded.
+The log-normal shape still holds with the lower luminosity cut, but a lower detection limit alleviates the selection effect against quasar populations with low Eddington ratios.
 }
@@
 In this paper, we propose a theoretical model for the redshift-dependent QLF and BHMF at $z\gtrsim 6$,
-applying the mass distribution function of seed BHs over $10^2 \lesssim M_\bullet/\Msun \lesssim 10^{5}$
-that originate from massive primordial stars formed in the overdense region of the universe.
-In our accretion model, those early BH populations are assumed to experience multiple accretion bursts, in each of which a constant Eddington ratio
-is assigned following a Schechter distribution function.
+applying the mass distribution function of seed BHs over $10^2~\Msun \lesssim M_\bullet \lesssim 10^5~\Msun$
+that originate from massive primordial stars formed in massive DM progenitor halos of quasar host galaxies.
+In our accretion model, those early BH populations are assumed to experience multiple accretion bursts with a time duration,
+in each of which a constant Eddington ratio is assigned following a Schechter distribution function.
 We further conduct the MCMC fitting to optimize the BH growth parameters
@@
 \item
-Our best-fit model to reproduce the QLF and BHMF at $z\simeq 6$ suggests that each accretion burst
-lasts $\tau \simeq 20-30$ Myr, which is a fraction of the $e$-folding time for the exponential BH mass growth.
-%Our model favors the BH Eddington ratio $\lambda$ following a Schechter distribution function to reproduce the QLF and BHMF at $z\simeq 6$.
-%The distribution shape is motivated by low-$z$ AGN observations.
-The Schechter shape of the ERDF is characterized with two parameters of 
-%The characteristic Eddington ratio $\lambda_0$ and the power law slope $\alpha$ at low Eddington ratio are best-fitted by
-$(\lambda_0, \alpha)=(0.89,0.12)$ and $(0.87,0.20)$ for the BH seeding fraction of $\fseed = 0.01$ and $0.1$, respectively.
-%The parameter $\tau$ characterizing the duration of each accretion burst is featured by our model,
-%with typical values $\tau \simeq 20-30$ Myr.
-%For longer (and shorter) burst durations, the number of BHs at the high mass end is over(-under) produced.
-Multiple accretion bursts with variable Eddington ratios enable the early BH population to grow and shine,
-in a consistent way with the observed QLF and BHMF.
+The best-fitted model requires the duration of accretion bursts to be $\tau \simeq 20-30$ Myr,
+which is a good fraction of the $e$-folding time for the exponential BH mass growth.
+The Schechter-like shape of the ERDF is constrained to produce the observed BHMF and QLF at $z\simeq 6$; namely,
+the characteristic Eddington ratio and power-law slope are $\lambda_0 \simeq 0.88$ and $\alpha \simeq 0.12-0.2$,
+depending the fraction of seed BHs that participate in the assembly of SMBHs (see Fig.~\ref{fig:contour}).
+%Multiple accretion bursts with variable Eddington ratios enable the early BH population to grow and shine,
+%in a consistent way with the observed QLF and BHMF.
 
 \item
-Using the best-fit model parameters, we construct the redshift-dependent QLF and BHMF at $6\leq z \leq 10$.
-%\blue{
-The two distribution functions suggest a rapid decay of the number and mass density of massive BHs 
-and luminous quasars toward higher redshifts, as discussed in previous observations and theoretical studies.
-We quantify the decay speed of quasar numbers characterized with a functional form of $\propto 10^{k_{\rm L} z}$,
-and find $k_{\rm L}\simeq -0.91$ and $-0.62s$ for the brightest and faintest population at $z>6$.
-%with the more luminous quasars decreasing more rapidly toward higher $z$.
-%}
+The cosmological evolution of the BHMF and QLF at $6\leq z \leq 10$ is predicted based on the model parameters
+calibrated with the observational data (see Figs.~\ref{fig:BHMF_rhoz}, \ref{fig:LFs}, and \ref{fig:QLFmag_z}).
+The fitting parameters of the BHMF and QLF with a double power-law function are summarized in Tables~\ref{tab:BHMF_fit} and \ref{tab:QLF_fit}.
+We find that the number density of luminous quasars decays toward higher redshifts as $\propto 10^{k_{\rm L} z}$,
+where $k_{\rm L}\simeq -0.91$ and $-0.62$ for the brightest and faintest population at $6<z<10$.
+We also show the detection number of high-$z$ quasars expected in Euclid and RST observations (see Table~\ref{tab:N_detect}).
+Those results will be tested with upcoming deep and wide-field surveys.
+
+% \item
+% Compared to the galaxy luminosity functions at redshifts from $z=7$ to $z\gtrsim 10$,
+% the QLFs we predict are burried in the faint end at $\Muv \gtrsim -23$ mag,
+% which makes it challenging to select such faint quasars.
+% The number of quasars dominates over that of galaxies in the bright end of the UV luminosity function.
+% We predict the critical magnitude at which galaxies and quasars equally contribute in number,
+% depending on extrapolation of the galaxy luminosity functions.
 
 \item
-Compared to the galaxy luminosity functions at redshifts from $z=7$ to $z\gtrsim 10$,
-the QLFs we predict are burried in the faint end at $\Muv \gtrsim -23$ mag,
-which makes it challenging to select such faint quasars.
-The number of quasars dominates over that of galaxies in the bright end of the UV luminosity function.
-We predict the critical magnitude at which galaxies and quasars equally contribute in number,
-depending on extrapolation of the galaxy luminosity functions.
-
-\item
-We further explore individual BH evolutionary tracks starting from the BH seeds, applying the BH growth model
-with the best-fit parameters to examine their statistical properties.
-For massive BHs that reach $\gtrsim 10^8~\Msun$ by $z\simeq 6$, the average duty cycle of super-Eddington accretion is as high as $\simeq 15~\%$.
-Since the duty cycle is nearly twice that of the entire population, the BH samples observed in $z\simeq 6$ quasars are
-biased toward a population that undergoes active accretion episodes.
-Multiple accretion-burst treatment well produces the mass assembly history of individual high-$z$ luminous quasars,
-unlike the case where one single value of the Eddington ratio is assigned.
+We apply the best-fit model for BH growth to evolution of individual BHs and examine their statistical properties.
+We find that the existence of SMBHs hosted in $z\gtrsim 6$ quasars can be explained by
+multiple accretion episodes, instead of assuming continuous Eddington-limited growth (see Fig.~\ref{fig:Mevol}).
+In fact, the average duty cycle of active accretion phases with $\lambda \geq 1$ is as high as $\simeq 15~\%$
+for massive BHs that reach $\gtrsim 10^8~\Msun$ by $z\simeq 6$.
+This indicates that those biased BH populations undergo longer active accretion episodes to be observed as quasars.
 We also find that the observed Eddington-ratio distribution function is skewed to a log-normal shape from the intrinsic Schechter function
-owing to detection limits of quasar surveys.
-Those results will be tested by future deep and wide surveys with the JWST, RST, and Euclid.
+owing to detection limits of quasar surveys (see Fig.~\ref{fig:lhist}).
+The log-normal shape still holds with a lower luminosity cut of $L_{\rm bol}\gtrsim 10^{45}~{\rm erg~s}^{-1}$.
+The existence of those underlying sub-Eddington BHs at $z>6$ will be probed by the ongoing survey of the Subaru HSC and JWST,
+as well as upcoming wide-field surveys such as the Vera C. Rubin Observatory, Euclid, and RST.
 \end{itemize}
@@
 \acknowledgments
-We greatly thank Jin Wu, Zhiwei Pan, BBB, and CCC for constructive discussions. 
+We greatly thank Yuichi Harikane, Nobunari Kashikawa, Yuanqi Liu, Yoshiki Matsuoka, Tohru Nagao, Zhiwei Pan, and Jin Wu for constructive discussions. 
 We acknowledge support from the National Natural Science Foundation of China 
@@
 The BH mass function (left) and quasar luminosity function (right) at $z=$ 6 in the case of $\fseed=0.01$,
-with different values of $\tlife=$ 10, 18 (the best-fit value), and 50 Myr, respectively.
-Note that the other parameters are fixed to the best-fit values. 
-The $z=6$ BHMF (\citetalias{2010AJ....140..546W}) and QLF (\citetalias{2018ApJ...869..150M}) 
-are overlaid with the blue curve and data points.
-With shorter (longer) timescales of each accretion episode $\tlife$, the number of BHs at the high mass end and bright end is under(over)-produced.
-%Right panel: QLF at $z=$ 6 calculated with the same parameters as in the left panel.
-%The overlaid blue dots are from the \citetalias{2018ApJ...869..150M} $z\sim$ 6 quasar observation. 
-%With $\tlife$ values different from the best-fit value, the consequent QLF show 
-%similar trends of deviation from observation as in the BHMF curves.
-Multiple accretion bursts in each duration of $\tau \simeq 20$ Myr best produce the observations,
-which is nearly half of the $e$-folding time of the exponential BH mass growth.
+with different values of $\tlife=$ 14, 18 (the best-fit value), and 37 Myr, respectively.
+Note that the other parameters are fixed to the best-fit values ($\delta=0.055$, $\lambda_0=0.87$, and $\alpha=0.20$).
+For comparison, we overlay the BHMF (\citetalias{2010AJ....140..546W}) and QLF (\citetalias{2018ApJ...869..150M}) at $z\simeq 6$ in blue.
+With the shorter (longer) timescales of each accretion episode $\tlife$, the number of BHs at the high mass end and bright end is under(over)-produced.
+Multiple accretion bursts with each duration of $\tau \simeq 18$ Myr, which is nearly half of the $e$-folding time of the exponential BH mass growth,
+reproduce the observed BHMF and QLF at $z\simeq 6$.
 }
 \label{fig:tau}
-%\vspace{4mm}
+\vspace{4mm}
 \end{figure*}
 
-\vspace{2mm}
-\section{Model dependence}\label{sec:modep}
-As described in Section~\ref{sec:model}, we introduce the parameter $\tau$ as a typical timescale
-for individual durations of quasar accretion activity.
-Specifically, we assign an Eddington ratio $\lambda$ following the ERDF for all BHs in each cycle
-with a time duration of $\tau$.
-Variable accretion episodes in every cycle essentially modify the effective ERDF in the whole BH growth history,
-because multiple sampling of $\lambda$ reduces the possibility of a BH growing with $\lambda \gtrsim \lambda_0$
-compared to that with a single sampling of $\lambda$.
-%However at any time during growth, the ERDF of the BH population remains the same as at $z\sim$ 6,
-%therefore we ensure treating all cosmic time equally.
-In what follows, we demonstrate the role of $\tlife$ in shaping the BHMF evolution and the consequent QLF.
-% tau极端小，则非常小的lambda，不能解释 （且delta func？ 有必要说或是放在后面讨论？）
+In our modeling for BH growth, we introduce a time duration $\tau$ of individual quasar activity,
+where a single value of the Eddington ratio $\lambda$ generated from the ERDF is assigned to all the BHs (see Section~\ref{sec:model}).
+Multiple sampling of $\lambda$ between the seeding epoch and $z=6$ reduces the probability that one BH
+keeps a fast growth speed at $\lambda \gtrsim \lambda_0$ all the way to $z=6$, compared to the case with a single sampling of $\lambda$.
+In what follows, we demonstrate the role of $\tlife$ in shaping the BHMF and QLF.
 
 In the left panel of Fig.~\ref{fig:tau}, we present the BHMF at $z=6$ for three different values of $\tlife=14$, $18$, and $37$ Myr,
-but keeping the other parameters to the best-fit values ($\lambda_0=0.87$ and $\alpha=0.20$) for the case with $\fseed=0.01$.
-We note that $\tlife \approx$ 18 Myr is the best-fit value reproducing the BHMF consistent with that of \citetalias{2010AJ....140..546W},
-and the other two values represent the $16$ and $84$ percentiles of the one-dimensional distribution of $\tau$, respectively (see Fig.~\ref{fig:contour}).
-%the other two cases demonstrate the sensitivity of the $\tlife$ value in producing the bulk of massive BHs
-%and the slope in the high mass tail.
-For $\tlife=14$ Myr, the frequency of Eddington ratio assignment increases by a factor of 1.3 until $z=6$.
-%to $\sim$ 80 from $\sim$ 40 with the best-fit $\tlife$ value.
-Therefore, continuous and efficient growth of BHs with $\lambda \gtrsim \lambda_0$ is less likely to occur,
-%high Eddington ratio accretion along the growth is lower,
-suppressing the formation of BHs heavier than $M_\bullet \simeq 10^8~\Msun$.
-Moreover, if a high Eddington ratio is given with a certain but low probability, the BH mass hardly increases
-within $\tlife=14$ Myr, which is $\simeq 30\%$ of the $e$-folding timescale.
-On the other hand, for $\tlife=$ 37 Myr, there is a non-negligible probability that
-% $\sim$ 16 times of Eddington ratio assignment,
-more BHs experience high accretion rates with $\lambda\gtrsim \lambda_0$ through their assembly history.
-%high values of $\lambda\gtrsim \lambda_0$ is non-negligibly realized in the BHMF evolution.
-Therefore, the high mass end of the BHMF is further enhanced and those massive populations are substantially
-overproduced compared to the observed abundance.
-%in the high mass end of BHMF at $z=$ 6, the BH population is significantly overproduced than the constraints from observation.
-
-The QLF at $z=6$ is shown in the right panel of Fig.~\ref{fig:tau}.
-%In the conversion from BHMF to QLF, the ERDF is the same for different $\tlife$ values,
-%following the $P(\lambda)$ in Eq.~(\ref{eq:Pl}) with $\lambda_0=0.87$ and $\alpha=0.20$.
+but keeping the other parameters to the best-fit values ($\delta=0.055$, $\lambda_0=0.87$, and $\alpha=0.20$) for the case with $\fseed=0.01$.
+We note that $\tlife \simeq$ 18 Myr is the best-fit value reproducing the observed BHMF and QLF at $z=6$,
+and the other two choices correspond to the $16\%$ and $84\%$ quantiles in the cumulative one-dimensional posterior distribution of $\tau$, respectively (see Fig.~\ref{fig:contour}).
+With the shorter quasar activity of $\tlife=14$ Myr, the frequency of Eddington ratio assignment increases by a factor of 1.3 until $z=6$, compared to the best-fit case.
+Therefore, continuous rapid growth of BHs with $\lambda \gtrsim \lambda_0$ is less likely to take place,
+preventing heavy BHs from forming.
+Moreover, even if a high Eddington ratio is given with a certain but low probability, the BH hardly grows in mass within such a short time $\tlife=14$ Myr,
+which is $\simeq 30\%$ of the $e$-folding timescale.
+On the other hand, with the longer quasar activity of $\tlife=$ 37 Myr, a substantial fraction of BHs experience high accretion rates with $\lambda\gtrsim \lambda_0$
+through their assembly history.
+Therefore, the high mass end of the BHMF is extended and massive BH populations with $\gg 10^8~\Msun$ are overproduced compared to the observed abundance.
+
+In the right panel of Fig.~\ref{fig:tau}, we show the QLF at $z=6$ with the three different values of $\tau$.
 Overall, the dependence of the QLF on the choice of $\tau$ shows the same trend as in the BHMF,
-%the deviation from the observed QLF of \citetalias{2018ApJ...869..150M} shows similar trends as in the BHMF.
-i.e., higher (lower) $\tlife$ values lead to under(over)-production of the luminous quasar population.
-The best-fit value of $\tlife (\simeq 18$ Myr) favors a moderate fraction of $t_{\rm S}$.
-This result demonstrates the importance of early BHs experiencing multiple accretion episodes to 
-reproduce the observed distributions of BH mass and luminosity of quasars at $z\sim$ 6.
-% In Section~\ref{sec:evol}, we apply this episodic accretion model to individual growth pathways of high-$z$ quasars
-% and demonstrate that normal seeding mechanisms can explain the existence of massive BHs with low luminosity
-% observed at $z\simeq 6-7$.
+i.e., a longer (shorter) $\tlife$ leads to under(over)-production of the luminous quasar population.
+%The best-fit value of $\tlife (\simeq 18$ Myr) favors a moderate fraction of $t_{\rm S}$.
+This result demonstrates the importance of multiple accretion episodes for the earliest BHs to
+reproduce the observed BHMF and QLF at $z\sim$ 6.
 

### 2022-09-30 ms.tex
version1001_0; for my check on Sec.4 etc. ms1 for table

@@
 \Omega_{\mathrm{b}}=0.0486$, and $H_0=67.7 \mathrm{~km} \mathrm{~s}^{-1} \mathrm{Mpc}^{-1}$.
+\blue{All magnitudes quoted in this paper are in the AB system.}
 
@@
 
-Based on the constraint from $z\sim 6$ quasar observations, the best-fit model from the MCMC realizations enables
-us to probe the statistical aspect of BH evolution at higher redshifts.
-We apply the result to construction of BHMFs and QLFs at $z\geq 6$ and give implications for
-the future explorations of high-$z$ quasars.
+% Based on the constraint from $z\sim 6$ quasar observations, the best-fit model from the MCMC realizations enables
+% us to probe the statistical aspect of BH evolution at higher redshifts.
+% We apply the result to construction of BHMFs and QLFs at $z\geq 6$ and give implications for
+% the future explorations of high-$z$ quasars.
+
+In previous sections, we calibrated the models for early SMBH evolution based on the observational constraints of BHMF and QLF at $z\sim6$.
+Next, we apply our model to predict the statistical properties of SMBHs at higher redshifts ($z\gtrsim$ 6)
+and provide prediction for future explorations of high-$z$ quasars.
 
@@
 As shown in Fig.~\ref{fig:seedmf}, the mass distribution of seed BHs develops up to $M_\bullet \lesssim 2\times10^5~\Msun$ by $z\gtrsim 17$.
-Thus, the high-mass tail of the BHMF is produced owing to subsequent growth of seed BHs (i.e., the fraction $\fseed$ of all the seeds).
+Thus, the high-mass tail of the BHMF is produced owing to subsequent growth of seed BHs with a fraction of $\fseed$.
+The information on the seeding process still remains in the low mass regime.
 In fact, the case with $\fseed=0.1$ yields the number density of those growing seeds ten times higher than that with $\fseed =0.01$,
 making the difference in the BH abundance at $M_\bullet \sim 10^{5-6}~\Msun$.
-%\footnote{For each case, a fraction $(1-\fseed)$ of BHs are assumed to keep the original mass at birth without subsequent growth.}.
-This result suggests that the information on the seeding process still remains in the low mass regime.
 Toward lower redshifts, heavier BHs with $\gtrsim 10^7~\Msun$ emerge owing to efficient growth
 and thus the number density of such massive BHs in the high-mass tail increases.
-Since the BHMF shape at $z=6$ is constrained by \citetalias{2010AJ....140..546W},
-the two cases reproduce similar shapes of mass distribution at $M_\bullet \simeq 10^8-3\times 10^9~\Msun$ (see Fig.~\ref{fig:fitmf}).
-As a result, the BHMF at $M_\bullet \gtrsim 10^7~\Msun$, which is potentially accessible by quasar observations,
+Since our model is calibrated against the $z=6$ BHMF of \citetalias{2010AJ....140..546W},
+the two cases with different seeding fractions yield similar shapes of mass distribution at $M_\bullet \simeq 10^8-3\times 10^9~\Msun$ (see Fig.~\ref{fig:fitmf}).
+The BHMF at $M_\bullet \gtrsim 10^7~\Msun$, which is potentially accessible by high-$z$ quasar observations,
 can be characterized with a double power-law function, 
@@
 \begin{equation}
-\Phi_{M_\bullet}=\frac{\Phi_{M_\bullet}^\ast}{(M_\bullet/M_{\bullet}^\ast)^{-(\hat \alpha+1)} + (M_\bullet/M_{\bullet}^\ast)^{-(\hat \beta+1)}},
+\Phi_{M_\bullet}=\frac{\Phi_{M_\bullet}^\ast}{(M_\bullet/M_{\bullet}^\ast)^{-(\hat \alpha+1)} + (M_\bullet/M_{\bullet}^\ast)^{-(\hat \beta+1)}}.
 \end{equation}
 %
-similar to lower-$z$ quasar populations \citep[e.g.,][]{2013ApJ...764...45K,2015MNRAS.447.2085S}.
+This function shape is also used to characterize the BHMF at lower-$z$ quasar populations
+\citep[e.g.,][]{2013ApJ...764...45K,2015MNRAS.447.2085S}.
 Here, $\Phi_{M_\bullet}^\ast$ (in units of Gpc$^{-3}$ dex$^{-1}$) is the overall normalization, $M_\bullet^\ast$ is the characteristic BH mass,
-and $\hat \alpha$ and $\hat \beta$ are the low and high-mass end power-law slopes, respectively.
-In Table~\ref{tab:BHMF_fit}, we summarize those parameters of the parametric BHMF at $z=6-10$ for the best-fit models.
+and $\hat \alpha$ and $\hat \beta$ are the low and high-mass end slopes, respectively.
+In Table~\ref{tab:BHMF_fit}, we summarize those parameters of the parametric BHMF at $z=6-10$ for the best-fit model in the case of $\fseed=0.01$.
 %while the difference in the two BHMF shapes is profound toward the low mass range of $M_\bullet \lesssim 10^7~\Msun$.
@@
 a double power-law function for the case with $\fseed=0.01$.
-The fitted mass range is $10^6~\Msun \leq M_\bullet \leq 10^{10}~\Msun$.
+The mass range we use for fitting is $10^6~\Msun \leq M_\bullet \leq 10^{10}~\Msun$.
 }
@@
 
-In the right panel of Fig.~\ref{fig:BHMF_rhoz}, we present the cumulative mass density of BHs in a comoving volume
+In the right panel of Fig.~\ref{fig:BHMF_rhoz}, we present the cumulative mass density of BHs $\rho_\bullet(z)$ in a comoving volume
 for $\fseed=0.1$ (solid) and $0.01$ (dashed),
-defined by the integration of the BHMF as
+which is equivalent to by the integration of the BHMF:
 %
@@
 Moreover, the seeding process affects the evolution of the mass density more substantially for less massive BHs,
-which keep the information on their initial conditions at birth.
-
-For comparison, we overlay the BH mass density evolution with $10^6~\Msun<M_{\bullet}<10^8~\Msun$
+which keeps the information on their initial conditions at birth.
+
+For comparison, we overlay in the right panel of Fig.~\ref{fig:BHMF_rhoz} the BH mass density evolution at $10^6~\Msun<M_{\bullet}<10^8~\Msun$
 %, and $M_\bullet>10^8~\Msun$
@@
 %%%%%%%
-\begin{deluxetable*}{lccccccc}%[t!]
+\begin{deluxetable*}{cccccccc}%[t!]
 \tablecolumns{1}
@@
 \tablewidth{0pt} 
-\tablecaption{Detection Number of Quasars in Future Surveys \label{tab:N_detect}} %! reference indexing
+\tablecaption{Expected Number of Quasars Discovered in Future NIR Surveys \label{tab:N_detect}} %! reference indexing
 \tablehead{
-  \colhead{Telescope} & \colhead{ Survey area} & \colhead{Photo. depth} &  \colhead{$N(z\sim 6)$} & \colhead{$N(z\sim 7)$}& \colhead{$N(z\sim 8)$}&  \colhead{$N(z\sim 9)$}&  \colhead{$N(z\sim 10)$}\\
-  \colhead{} & \colhead{(\rm{deg}$^2$)} & \colhead{(AB mag)} & & & & & 
+  \colhead{Survey} & \colhead{ Area} & \colhead{Selection} &  \colhead{$N(z\sim 6)$} & \colhead{$N(z\sim 7)$}& \colhead{$N(z\sim 8)$}&  \colhead{$N(z\sim 9)$}&  \colhead{$N(z\sim 10)$}\\
+  \colhead{} & \colhead{(\rm{deg}$^2$)} & \colhead{(mag)} & & & & & 
 }
 \startdata
-Wide Euclid & 15000  & $YJH$  24   & $6654^{+95}_{-2282}$  &  $708^{+213}_{-237}$ &   $93^{+66}_{-56}$ & $14^{+32}_{-27}$ & --  \\
-Wide Euclid & 15000  & $YJH$  23   & $2480^{+188}_{-614}$  &  $207^{+144}_{-114}$ &   $23^{+27}_{-19}$ & $3^{+12}_{-10}$ & --  \\
-Wide Euclid\dag & 15000  & selection func.  & --                             &  $204 (117)$                &   $16 (6)$             & $7 (2)$ & --  \\
+Euclid      & 15000           & $m_{1450}\leq 24$   & $6654^{+95}_{-2282}$  &  $708^{+213}_{-237}$ &   $93^{+66}_{-56}$ & $14^{+32}_{-14}$ & --  \\
+Euclid      & 15000           & $m_{1450}\leq 23$   & $2480^{+188}_{-614}$  &  $207^{+144}_{-114}$ &   $23^{+27}_{-19}$ & $3^{+12}_{-3}$ & --  \\
+Euclid Collab. (2019) & 15000   & selection func.  & --                             &  $204 (117)$                &   $16 (6)$             & $7 (2)$ & --  \\
 % Wide Euclid & 15000  & $\Muv=-26$  & $154^{+100}_{-38}$    &  $12^{+59}_{-50}$    &   $1^{+4}_{-3}$    & -- & --  \\
 \hline
-Wide RST    &  2000  & $YJH$  27   & $6759_{-3185}^{+15} $ &  $1514_{-558}^{+169}$ &  $349_{-131}^{53}$ & $85_{-48}^{+23}$ & $25^{+12}_{-15}$  \\
+RST    &  2000  & $m_{1450}\leq 27$  & $6759_{-3185}^{+15} $ &  $1514_{-558}^{+169}$ &  $349_{-131}^{53}$ & $85_{-48}^{+23}$ & $25^{+12}_{-15}$  \\
 % Wide RST    &  2000  & $\Muv=-26$ & $21_{-5}^{+13} $      &  $2_{-7}^{+8}$        &  --  & -- & --  \\
@@
 \tablecomments{
-The detection number of high-$z$ quasars predicted by the BH growth model with $\fseed=0.01$ at each redshift with the Euclid ad RST wide-area surveys, 
-assuming the survey volume with $\Delta z =1$ and 100\% completeness.
-The integration of the QLF is conducted for brighter populations than the 5$\sigma$ point source detection limits of 
-the $YJH$ bands in each survey (24 mag for Euclid and 27 mag for the RST).%, and the absolute magnitude with $\Muv \leq-26$ mag.\\
-\dag: To mimic realistic quasar identification capability, we show the detection numbers with $YJK=23$ mag in comparison with
+The detection number of high-$z$ quasars predicted by the BH growth model with $\fseed=0.01$ at each redshift with the Euclid ad RST wide-area surveys.
+The number density of quasars is shown from $z=6$ to $10$ with a step of 1.
+\blue{Selection completeness is assumed to be 100\% below the magnitude limits considered.
+The integration of the QLF is conducted for quasar populations brighter than the photometric depth $m_{1450}$,
+inferred from the 5$\sigma$ point source detection limits of the $YJH$ bands in each survey.
+To mimic realistic quasar identification capability, we show the detection numbers with $m_{1450}\leq 23$ mag in comparison with}
 \citet{2019Barnett}. The values are taken from the fourth column of their Table~3 for the three redshift range: $7.0<z<7.5$, $8.0<z<8.5$, and $8.5<z<9.0$.
 The values correspond to different extrapolation of the quasar number density at higher redshifts ($\propto 10^{k_{\rm L}z}$); $k_{\rm L}=-0.72$ and $-0.92$.
+\blue{We show the prediction of no detection or no prediction in the literature with the symbol ``--''.}
 }
@@
 Fig.~\ref{fig:LFs} presents our prediction of QLFs at $z>6$ taken from the BH growth model with $\fseed=0.01$.
-We divide the cosmological QLF evolution results into four different epochs; (a) $z\sim 7$, (b) $z\sim 8$, (c) $z\sim 9$, and (d) $z\sim 10-13$.
-The black solid and dashed curves show the QLF for the unobscured population 
+We show QLFs at different epochs; (a) $z\sim 7$, (b) $z\sim 8$, (c) $z\sim 9$, and (d) $z\sim 10-13$.
+The black solid and dashed curves of each panel show the QLF for the unobscured population 
 and entire population (including unobscured and obscured quasars), respectively.
-The obscured fraction based on X-ray samples \citep{2014ApJ...786..104U} is applied to faint objects, 
-but the correction factor is highly uncertain at the faint end of $\Muv\gtrsim -20$ mag.
+% The obscured fraction based on X-ray samples \citep{2014ApJ...786..104U} is applied to faint objects, 
+% but the correction factor is highly uncertain at the faint end of $\Muv\gtrsim -20$ mag.
+The $z\sim 5$ obscured fraction derived in an X-ray study by \citet{2014ApJ...786..104U} is used to convert the intrinsic QLF to the unobscured one,
+while we note that their obscuration fraction is highly uncertain at $\Muv \gtrsim-20$ mag.
 Similar to the BHMF, for all the redshift range, the shape of the QLF is well approximated with a double power-law function,
@@
 where $\Phi_{\Muv}^\ast$ (in units of Gpc$^{-3}$ mag$^{-1}$) is the overall normalization, $\Muv^\ast$ is the characteristic magnitude,
-$\Delta \Muv \equiv \Muv - \Muv^\ast$, and $\tilde \alpha$ and $\tilde \beta$ are the faint and bright-end power-law slopes, respectively.
+$\Delta \Muv \equiv \Muv - \Muv^\ast$, and $\tilde \alpha$ and $\tilde \beta$ are the faint and bright-end slopes, respectively.
 In Table~\ref{tab:QLF_fit}, we summarize those parameters of the parametric QLFs at $z=6-10$ for the best-fit models.
-From higher to lower redshifts, the number density of luminous quasars increases and the bright-end of the distribution rises.
+From higher to lower redshifts, the number density of luminous quasars increases and the bright-end slope gets flatter.
 
 We overlay the expected depths and survey volumes of upcoming near-infrared surveys by
-Euclid (\citealt{2011arXiv1110.3193L}; with realistic depth updated in \citealt{2019Barnett}) and RST \citep{2019arXiv190205569A}.
-We here consider only their wide-area survey layers because other survey programs are not suitable for quasars at $z\gtrsim 7$.
-Table~\ref{tab:N_detect} summarizes the survey coverage and lists the expected detection number of quasars with varying limiting magnitudes.
-We first integrate the QLFs starting from the 5$\sigma$ point source detection limits (\blue{$YJH$=} 24 mag for Euclid and 27 mag for RST, respectively).
-With the limiting magnitude, Euclid will identify quasars up to $z\lesssim 9$ and discover $\simeq 100-700$ quasars at $z\simeq 7-8$.
-The RST will be able to explore fainter ($\Muv>-22$ mag) but more abundant quasar populations up to $z\sim 10$,
-and increase the detection number by a factor of $\sim 2-6$ depending on the redshift range.
-However, realistic detection numbers are reduced from those ideal ones when we take into account selection criteria to differentiate 
-high-$z$ quasars from other astrophysical sources such as Galactic brown dwarfs and low-$z$ galaxy interlopers.
-Therefore, the estimated values above give upper bounds of the number of detectable high-$z$ quasars.
-Indeed, \citet{2019Barnett} investigated the efficiency of quasar selection and
-found that combined with ground-based optical observations,
-high-$z$ quasars can be identified down to $YJH \sim$ 23 mag.
+Euclid (\citealt{2011arXiv1110.3193L}; \citealt{2019Barnett}) and RST \citep{2019arXiv190205569A}.
+We here consider only their wide-area survey layers because narrow-field deep surveys are not suitable for high-$z$ quasars \citep[but see][]{2022arXiv220907325O}.
+\blue{
+Table~\ref{tab:N_detect} summarizes the expected number of quasars from those surveys.
+We first integrate the QLFs at the apparent magnitude $m_{1450}\leq$ 24 mag and 27 mag for Euclid and RST, respectively.
+These depths are the 5$\sigma$ point source detection limits in the $YJH$ bands of the two facilities.
+}
+Euclid will cover $\simeq 100-700$ quasars at $z\sim7-8$ down to the limiting magnitude, and can reach up to $z\sim 9$.
+The RST will explore fainter ($\Muv>-22$ mag) and more abundant quasar populations up to $z\sim 10$.
+% and increase the detection number by a factor of $\sim 2-6$ depending on the redshift range.
+% However, realistic detection numbers are reduced from those ideal ones when we take into account selection criteria to differentiate 
+% high-$z$ quasars from other astrophysical sources such as Galactic brown dwarfs and low-$z$ galaxy interlopers.
+However, the estimated values above give upper bounds of the number of detectable high-$z$ quasars,
+because selection completeness is not unity in the selection of high-$z$ quasars.
+\citet{2019Barnett} investigated the efficiency of quasar selection with Euclid images and
+\blue{found that combined with ground-based optical observations,
+$z\sim 7-9$ quasars can be identified down to $J \sim$ 23 mag}
+due to photometric noise and contaminants in the color selection such as Galactic brown dwarfs and low-$z$ early-type galaxies.
 Adopting $YJH=23$ mag as the effective depth, %based on the quasar selection methods for Euclid \citep{2019Barnett},
-our predicted detection numbers are in good agreement with their results but shows a better match for the case with extrapolation of $10^{-0.72z}$
-toward higher redshifts (see the fourth column in their Table~3).
+our predicted detection numbers are in good agreement with their results but shows a better match for the case
+where the QLFs are extrapolated with $10^{-0.72z}$ toward higher redshfits
+(see the fourth column in their Table~3).
 
@@
 
-We also show the galaxy UV luminosity function in each panel
+We also show the galaxy UV luminosity function in each panel of Fig.~\ref{fig:LFs}
 along with the fitting function in a Schechter (dotted) and double powe-law (dashed-dotted) shape extended to the brighter end
@@
 $\Muv\sim-26$, $-25$, and $\ll -30$ mag for each redshift range.
-Future deep and wide surveys will unveil the relative contribution of the two populations and impacts on cosmic reionization
+Future deep and wide surveys will unveil the relative contribution of the two populations and the relative roles in cosmic reionization
 (see also \citetalias{2018ApJ...869..150M}, \citealt{2022NatAs...6..850J}).
@@
 
-In Fig.~\ref{fig:QLFmag_z}, we present the quasar number density as a function of redshift for 
-$\fseed =0.1$ (solid) and $0.01$ (dashed).
+In Fig.~\ref{fig:QLFmag_z}, we present the quasar number density at different UV magnitudes from $\Muv=-27$ to $-23$ mag as a function of redshift.
+The solid curves show the cases for $\fseed = 0.1$ and the dashed curves show the cases for $\fseed = 0.01$ at each magnitude bin.
 Each curve corresponds to the value at a UV magnitude from $\Muv=-27$ mag to $-23$ mag.
@@
 A rapid decay of the luminous quasar abundance at $\Muv<-26$ mag toward higher redshifts is found by 
-previous observational studies \citep[e.g.,][]{2001AJ....122.2833F,2013ApJ...768..105M,2016ApJ...833..222J,2019ApJ...884...30W}.
+observational studies \citep[e.g.,][]{2001AJ....122.2833F,2013ApJ...768..105M,2016ApJ...833..222J,2019ApJ...884...30W}.
 For instance, \citet{2019ApJ...884...30W} proposed a decay index of $k_{\rm L}=-0.78\pm{0.18}$ for those bright quasars at $6\lesssim z \lesssim 7$.
 The slopes in our model prediction of $\Muv <=-26$ are slightly steeper ($k_\mathrm{L} \simeq -0.84$ at $\Muv=-26$),
-but consistent with their result within the error range.
+but consistent with their result within the $1\sigma$ error range.
 

### 2022-09-30 ms.tex
.

@@
 The black solid and dashed curves are the unobscured and intrinsic QLF, respectively, and the shaded region presents the $1\sigma$ statistical error.
-The expected depths and volumes of future surveys with Wide Euclid (blue; $YJH=23$ mag) and Wide RST (red; $YJH=27$ mag) are overlaid in each panel (see Table~\ref{tab:N_detect}).
+The expected depths and volumes of future surveys with Wide Euclid (blue; $m_{1450}= 23$ mag) and Wide RST (red; $m_{1450}= 27$ mag) are overlaid in each panel (see Table~\ref{tab:N_detect}).
 For comparison, the galaxy UV luminosity functions are plotted with the data points (grey) and the fitting functions in purple with a Schechter (dotted) and double power-law (dash-dotted) shape.
@@
 due to photometric noise and contaminants in the color selection such as Galactic brown dwarfs and low-$z$ early-type galaxies.
-Adopting $YJH=23$ mag as the effective depth, %based on the quasar selection methods for Euclid \citep{2019Barnett},
+Adopting $m_{1450}=23$ mag as the effective depth, %based on the quasar selection methods for Euclid \citep{2019Barnett},
 our predicted detection numbers are in good agreement with their results but shows a better match for the case

### 2022-10-04 ms.tex
version1005; arxiv (abstract 251 words)

@@
 
-\author[0000-0001-9840-4959]{Wenxiu Li}
+\author[0000-0002-1044-4081]{Wenxiu Li}
 \affiliation{Department of Astronomy, School of Physics, Peking University, Beijing, 100871, China}
@@
 \affiliation{Kavli Institute for Astronomy and Astrophysics, Peking University, Beijing 100871, China}
-\author[0000-0001-9840-4959]{Masafusa Onoue}
+\author[0000-0003-2984-6803]{Masafusa Onoue}
 \altaffiliation{Kavli Astrophysics Fellow}
@@
 black holes (BHs) in high-$z$ quasars.
-Although the shape of the QLF has been constrained by recent wide and deep surveys,
-it still remains challenging to develop a theoretical model that explains its redshift evolution associated with BH growth self-consistently.
-In this study, based on a semi-analytical model for the formation and growth of seed BHs
-in quasar progenitor dark matter halos,
+Although the QLF shape has been constrained by recent observations,
+it remains challenging to develop a theoretical model that explains its redshift evolution associated with BH growth self-consistently.
+In this study, based on a semi-analytical model for
+the BH formation and growth,
 we construct the QLF and BHMF of the early BH population that experiences multiple accretion bursts,
@@
 suggests that several episodes of moderate super-Eddington accretion occur
-and each of them lasts $\tau \simeq 20-30$ Myr.
-The average duty cycle in super-Eddington phases of BHs that reach $\gtrsim 10^8~\Msun$ by $z\simeq 6$ is as high as $\simeq 15~\%$,
+and each of them lasts for $\tau \simeq 20-30$ Myr.
+The average duty cycle in super-Eddington phases is $\simeq 15\%$ for massive BHs that reach $\gtrsim 10^8~\Msun$ by $z\simeq 6$,
 which is nearly twice that of the entire population.
-We also find that the observed Eddington-ratio distribution function is skewed to a log-normal shape from the intrinsic Schechter-like function
+We also find that the observed Eddington-ratio distribution function is skewed to a log-normal shape 
 owing to detection limits of quasar surveys.
-The predicted redshift evolution of the QLF and BHMF of the earliest BHs suggests a rapid decay of their number and mass density 
-in a cosmic volume toward higher redshifts of $z>6$.
-This will be unveiled by future deep and wide surveys with the James Webb Space Telescope, Roman Space Telescope, and Euclid.
+The predicted redshift evolution of the QLF and BHMF suggests a rapid decay of their number and mass density 
+in a cosmic volume toward $z\gtrsim 6$.
+These results will be unveiled by future deep and wide surveys with the James Webb Space Telescope, Roman Space Telescope, and Euclid.
 \end{abstract}
@@
 \citep[e.g.,][]{1998ApJ...503..505H,2010ApJ...718..231S,2018MNRAS.474.1995R,2018MNRAS.481.3278R,
-2021MNRAS.508.2706Y,2021ApJ...910L..11K,2022MNRAS.511..616T}. 
+2021MNRAS.508.2706Y,2021ApJ...910L..11K,2022MNRAS.511..616T,2022arXiv220714689O}. 
 However, due to the limitation of capturing the detailed properties of the relevant physics, 
@@
 Nevertheless, those semi-analytical and phenomenological approaches introduce numerous physical parameters
-and make the key mechanisms reproducing the observed results obscure.
-Therefore, it is required to construct a theoretical model that is characterized by a minimum number of parameters
+and make the essential mechanisms reproducing the observed results elusive.
+Therefore, it is required to construct a theoretical model characterized by a minimum number of parameters
 but capable of dealing with the essential physical processes.
@@
 recent studies by \citet{2021MNRAS.503.5046L} and \citet{2021ApJ...917...60L} found that the formation of heavy seeds
-can be accelerated in rare, overdense regions of the universe, where non-linear galaxy clustering boosts the irradiation intensity
+accelerates in rare, overdense regions of the universe, where non-linear galaxy clustering boosts the irradiation intensity
 and frequency of halo mergers.
@@
 %the observed distribution functions at $z=6$.
-In Section~\ref{sec:fitting_result}, we present the fitting results for the model parameters reproducing the observational results,
-and discuss the key physics to determining the BH growth.
+In Section~\ref{sec:fitting_result}, we present the fitting result for the model parameters reproducing the observational data,
+and discuss the physics determining the BH growth.
 In Section~\ref{sec:cosm}, we discuss the cosmological evolution of the BHMF and QLF suggested by our best-fit model,
-as well as the detection number of those BHs at $z\sim 6-10$ with Euclid and RST.
+as well as the detection number of those BHs at $z\sim 6$--$10$ with Euclid and RST.
 In Section~\ref{sec:discussion}, we present the evolutionary tracks of individual BHs and their statistical properties at $z\gtrsim 6$,
 based on the growth model calibrated above.
-We finally summarize our findings in Section~\ref{sec:sum} and discuss the potential applications of quasar observations on 
-exploring the high-$z$ universe.
+We finally summarize our findings in Section~\ref{sec:sum}.
+% and discuss the potential applications of quasar observations on exploring the high-$z$ universe.
 Throughout this work, we apply the cosmological parameters from \cite{2016A&A...594A..13P},
@@
 \Omega_{\mathrm{b}}=0.0486$, and $H_0=67.7 \mathrm{~km} \mathrm{~s}^{-1} \mathrm{Mpc}^{-1}$.
-\blue{All magnitudes quoted in this paper are in the AB system.}
+All magnitudes quoted in this paper are in the AB system.
 
@@
 \citep{2002ApJ...578...90F,2013ApJ...773...44W,2019ApJ...872L..29S}.
-Therefore, we consider three parent halos with $\Mh = 10^{11}$, $10^{12}$, and $10^{13} ~\Msun$ at $z=$ 6
+In our model, we consider three parent halos with $\Mh = 10^{11}$, $10^{12}$, and $10^{13} ~\Msun$ at $z=$ 6
 and generate $N_{\rm tot} (= 10^4)$ merger trees for each parent halo mass backward in time using the {\tt GALFORM} 
@@
 At the end of the stellar lifetime, those massive primordial stars result in BHs without significant mass loss 
-via stellar winds \citep{2003ApJ...591..288H,2010ApJ...714.1217B,2015MNRAS.451.4086S}.
-Therefore, we consider that the stellar mass of interest is equal to that of its remnant BH.
+via stellar winds \citep{2003ApJ...591..288H,2015MNRAS.451.4086S}.
+Therefore, we assume that the mass of a remant BH is equal to that of its stellar progenitor.
 
@@
 \centering
-\includegraphics[width=140mm]{seedBHMF_z.png}
+\includegraphics[width=140mm]{seedBHMF_z.pdf}
 \caption{
@@
 \Phi_{\Mbh}^{\rm seed}\left(t\right) \equiv \sum_{\Mh, \vbsm} n_{\Mh} f_{\vbsm} 
-\cdot \sum_{\rm itr} \frac{\D P^{\rm seed}_i}{\D \log \Mbh}\left(t\right) \Big| _{\Mh, \vbsm},
+\cdot \sum_{i}^{N_{\rm tot}} \frac{\D P^{\rm seed}_i}{\D \log \Mbh}\left(t\right) \Big| _{\Mh, \vbsm},
 \end{align}
@@
 extended to $M_\bullet \gtrsim 10^5~\Msun$, reflecting the halo assembly and environmental effects.
-Note that in this study, we consider massive seed BHs formed from low-metallicity environments,
-but neglect a potential contribution from BHs left behind the second-generation star formation
-that takes place in metal-enriched environments.
+Note that in this study, we consider massive seed BHs formed in low-metallicity environments,
+but neglect a potential contribution from BHs left behind the second-generation star formation in metal-enriched environments.
 %Finally, we note that in each parent halo, we consider purely the PopIII stellar remnants in the seed BH mass function construction,
@@
 The latter ones would dominate in number at the low-mass end of the BHMF at $z\sim 6$,
-but have little impacts on the bulk properties of the observed QLF and BHMF \citep[see][]{2022MNRAS.511..616T}.
+but have little impact on the bulk properties of the observed QLF and BHMF \citep[see][]{2022MNRAS.511..616T}.
 
@@
 \end{equation}
-where $\lambda$ is the luminosity-based Eddington ratio,
+where $\lambda$ is the ratio of the quasar bolometric luminosity to its Eddington luminosity $L_{\rm Edd}$,
 % $\lambda \equiv L/L_\mathrm{Edd}$ 
@@
 which is consistent with the value obtained from the Soltan-Paczy{\'n}ski argument \citep[e.g.,][]{2002MNRAS.335..965Y,2010ApJ...725..388C}.
-On the basis of studies on the mass dependence of the radiative efficiency for AGNs at $z\lesssim$ 3 
+Based on studies on the mass dependence of the radiative efficiency for AGNs at $z\lesssim$ 3 
 \citep{2008MNRAS.390..561C,2012ApJ...749..187L,2014ApJ...786..104U}, 
@@
 A series of radiation hydrodynamical simulations for BH accretion
-suggest that the gas supplying from galactic scales into the nuclear scale is not high enough to sustain 
+suggest that the gas supplying rate from galactic scales into the nuclear scale is not high enough to sustain 
 super-Eddington accretion when the BH mass is higher than the characteristic value \citep{2021ApJ...907...74T}.}.
@@
 \citep{2005Natur.433..604D,2005ApJ...630..705H}, 
-and the accretion rate declines by self-regulating feedback processes \citep[e.g.,][]{2008ApJ...686..815Y,2011ApJ...737...26N} 
+and the BH feeding rate declines by self-regulating feedback processes \citep[e.g.,][]{2008ApJ...686..815Y,2011ApJ...737...26N} 
 or gas consumption \citep{1991MNRAS.248..754P,2005ApJ...634..901Y,2007MNRAS.377L..25K}. 
@@
 
-To characterize the ERDF for a BH population at any time snapshot together with episodic 
-accretion patterns of individual BHs, 
+To characterize the % ERDF for a BH population at any time snapshot together with 
+episodic accretion patterns of individual BHs, 
 we introduce a time duration of $\tlife$, during which a single value of $\lambda$ is assigned to an accreting BH
@@
 an averaged but fundamental timescale that governs mutual correlation between the QLF and BHMF,
-based on direct comparison to those distribution functions for observed high-$z$ quasar population.
+based on direct comparison to those distribution functions for the observed high-$z$ quasar population.
 
@@
 Since the value has been poorly constrained both by theoretical and observational studies, we treat it as a free parameter.
-We take three different values of $\fseed = 1$, $0.1$, and $0.01$, and explore its effect on producing the QLF and BHMF.
+We take three different values of $\fseed = 1$, $0.1$, and $0.01$, and explore its effect on shaping the QLF and BHMF.
 Since we find that the results in the cases of $\fseed = 1$ and $0.1$ are quantitatively similar,
@@
 and the derivative of ($\D \ln \lambda_\ast / \D  \Mbh )|_{\Delta t, M_{\bullet,0}}$ is also determined.
-For existing BHs formed before this checkpoint, we calculate the evolution of the mass distribution by setting $\Delta t = \tlife$.
+For existing BHs, we calculate the evolution of the mass distribution by setting $\Delta t = \tlife$.
 For a seed BH formed during this cycle (i.e., $T_0\leq t_k < T_0+\tlife$), 
@@
 For an accreting BH with a bolometric luminosity of $\Lbol=\lambda L_\mathrm{Edd}$, 
-its rest-frame ultraviolot (UV) absolute magnitude of $\Muv$ at 1450 $\mathrm{\AA}$ is estimated by
+its rest-frame ultraviolot (UV) absolute magnitude of $\Muv$ at 1450 $\mathrm{\AA}$ is estimated as
 %
@@
 We construct the QLF from the BHMF, combining this conversion factor and ERDF.
-However, we note that the shape and normalization of the {\it intrinsic} QLF is not necessary identical to the {\it observed} QLF
-because quasar surveys with optical and near-infrared telescopes are not sensitive to the obscured quasar population at high redshifts,
+However, we note that the shape and normalization of the {\it intrinsic} QLF is not necessarily identical to the {\it observed} QLF
+because quasar surveys with rest-frame UV-to-optical bands are not sensitive to the obscured quasar population,
 i.e., the observed number of fainter quasars is largely reduced by the obscuration effect
@@
 A widely-accepted mechanism causing quasar obscuration is extinction by dusty tori and dense gas clouds 
-in the circumnuclear region, hence tightly related with gas fueling and feedback processes from accreting BHs 
+in the circumnuclear region, hence tightly related to gas fueling and feedback processes from accreting BHs 
 \citep[see][for a review]{2018ARA&A..56..625H}.
@@
 %
-where $a=10.96$, $b = 11.93$, and $c = 17.79$ \citep[see Eq.~(2) in][]{2020A&A...636A..73D}. 
-In our analysis, we neglect the contribution from Compton-thick AGNs with $N_\mathrm{H}>10^{24}$ cm$^{-2}$, 
-which are obscured even in the hard X-ray band and show possible dependence on quasar properties.
-It is worth noting that the obscured fraction for high-$z$ quasar populations is still under investigation.
+where $a=10.96$, $b = 11.93$, and $c = 17.79$ \citep[see Eq.~2 in][]{2020A&A...636A..73D}. 
+% In our analysis, we neglect the contribution from Compton-thick AGNs with $N_\mathrm{H}>10^{24}$ cm$^{-2}$, 
+% which are obscured even in the hard X-ray band and show possible dependence on quasar properties.
+It is worth noting that the functional form of the obscuration fraction
+is calibrated with X-ray selected ANGs at $z\lesssim 5$,
+and the value for high-$z$ quasars is still under investigation.
 %and the uncertainties would affect our analyses for fainter quasars.
@@
 covering the same mass range as in their bootstrap resamples (see Figure 8 of \citetalias{2010AJ....140..546W}). 
-The observed QLF is taken from \citet{2018ApJ...869..150M} (hereafter \citetalias{2018ApJ...869..150M}) 
+The observed (unobscured) QLF is taken from \citet{2018ApJ...869..150M} (hereafter \citetalias{2018ApJ...869..150M}) 
 over a wide range of UV magnitude at $-30 < \Muv <-22$ mag (see their Table 4 and Figure 13). 
@@
 Adopting 10 mass bins and 12 magnitude bins, we treat the errors from comparison both in the BHMF and QLF
-with a nearly equal weight.
+with nearly equal weight.
 The posterior distribution of the MCMC fitting is stabilized around the minimum value of $\chi^2$ (highest likelihood), 
@@
 We discuss the MCMC fitting results and compare the BHMF and QLF with those observed distribution functions.
-In Fig.~\ref{fig:contour}, we visualize the fitting results for each parameter in two-dimensional 
+In Fig.~\ref{fig:contour}, we visualize the fitting results of the model parameters in two-dimensional 
 posterior distribution for the case of $\fseed= 0.1$ (left) and $0.01$ (right), respectively.
@@
 The best-fit values shown with the red lines are listed in Table~\ref{tab:best_fits},
-displaying consistency with the peaks in the one-dimensional distribution.
+and are consistent with the peak values in the one-dimensional distribution.
 %Note that the best-fit values may not overlap the 50\% quantile lines,
@@
 
-For the two cases, the best-fit solution consistently yields a small value of $\delta < 0.1$.
+For the two cases, the best-fit solution yields a small value of $\delta < 0.1$.
 This result favors the nearly exponential BH growth model (Eqs.~\ref{eq:mdot} and \ref{eq:f_M}).
-The typical duration of quasar activity is required to be $\tlife \simeq 20-30$ Myr for both the cases.
+The typical duration of quasar activity is required to be $\tlife \simeq 20-30$ Myr for both cases.
 This suggests that accreting seed BHs vary their growth speeds and their Eddington ratios 
-$\simeq 30-40$ times on average toward the cosmic time at $z\simeq 6$.
-The timescale of $\tlife$ is also related to the quasar lifetimes of $t_{\rm Q}\sim 1-10$ Myr, 
-which are estimated by the measurement of the physical extents of hydrogen Ly$\alpha$ proximity zones 
+$\simeq 30-40$ times toward the cosmic time at $z\simeq 6$.
+The timescale of $\tlife$ is also related to the quasar lifetime of $t_{\rm Q}\sim 1-10$ Myr, 
+which is estimated by the measurement of the physical extents of hydrogen Ly$\alpha$ proximity zones 
 observed in the rest-frame UV spectra \citep[e.g.,][]{2018ApJ...867...30E,2019ApJ...884L..19D}.
@@
 The power-law index of $\alpha$ in the ERDF increases as the seeding fraction decreases.
-Thus, a more significant fraction of BHs actively grow with $\lambda \gtrsim 1$ and contribute to developing of the QLF and BHMF.
+Thus, a more significant fraction of BHs actively grow with $\lambda \gtrsim 1$ and develop the QLF and BHMF.
 
@@
 
-The best-fit parameters for the two cases of $\fseed$ reproduce the bulk properties of the BHMF and QLF at $z\sim 6$,
+The best-fit parameters for the two cases reproduce the bulk properties of the BHMF and QLF at $z\sim 6$,
 despite the ten-fold difference in the seeding fraction.
@@
 In Fig.~\ref{fig:fitmf}, we show the BHMFs at $z=$ 6 reproduced by the best-fit parameters for 
-$\fseed = 0.1$ (left) and $0.01$ (right) as well as the statistical error, 
-which is defined as the $1\sigma$ standard deviation calculated from randomly selected parameters from the sampling.
+$\fseed = 0.1$ (left) and $0.01$ (right) as well as
+the $1\sigma$ standard deviation calculated from random parameter sampling in the Markov chain.
 For comparison, we present the BHMF inferred by \citetalias{2010AJ....140..546W} along with the statistical errors.
@@
 Overall, our best-fit BHMF model agrees with their constraints in this mass range.
-The power-law index of the BHMF ($\gamma{M_\bullet} \equiv \D \ln \Phi_{M_\bullet}/\D \ln M_\bullet$) is as steep as $\gamma_{M_\bullet}\lesssim -1$
+The power-law index of the BHMF ($\gamma_{M_\bullet} \equiv \D \ln \Phi_{M_\bullet}/\D \ln M_\bullet$) is as steep as $\gamma_{M_\bullet}\lesssim -1$
 at $M_\bullet \gtrsim 10^7~(3\times 10^7)~\Msun$ for $\fseed = 0.1 ~(0.01)$.
-The total mass budget of the entire BH population is dominated by BHs with the characteristic mass (see also Section~\ref{sec:cosm}). 
-The discrepancy between the model and observational data becomes larger at the high- and low-mass end,
+Thus, the total mass budget of the entire BH population is dominated by BHs with the characteristic mass (see also Section~\ref{sec:cosm}). 
+The discrepancy between the model and observational data enlarges at the high- and low-mass end,
 reflecting poor constraints on the BHMF from the current observations.
@@
 \caption{
-{\it Left}: The predicted BH mass functions at $z=6-10$ for the case with $\fseed=0.1$ (solid) and $0.01$ (dashed), including the seed population.
+{\it Left}: The predicted BH mass functions at $z=6$--$10$ for the case with $\fseed=0.1$ (solid) and $0.01$ (dashed), including the seed population.
 %including a fraction of $\fseed$ seeds evolving by our model assumption and the remaining ($1-\fseed$) fraction with no subsequent growth.
@@
 for $\fseed = 0.1$ (left) and $0.01$ (right).
-The solid and dashed curve is the unobscured and intrinsic QLF, respectively.
-The latter one includes both obscured and unobscured quasars.
+The solid and dashed curve are the unobscured and intrinsic QLF, respectively.
+The latter includes both obscured and unobscured quasars.
 For comparison, we overlay the observational data taken from \citetalias{2018ApJ...869..150M} in blue
@@
 but overproduces fainter quasars at $\Muv\gtrsim -24~{\rm mag}$.
-As seen in the BHMF, the difference between the model and observational data at the faint end becomes smaller with
+Simillar as the BHMF, the difference between the model and observational data at the faint end becomes smaller with
 the lower seeding fraction.
-Since the progenitors of those faint quasars were seed BHs located around the peak of the mass distribution,
-those BHs naturally produces a flatter slope of the QLF at the faint end.
+Since the progenitors of those faint quasars originate from lower mass seed BHs with $\fseed =0.01$ (see discussion above),
+the BH population on the peak of the mass distribution naturally produces a flatter slope of the QLF at the faint end.
 In addition, we show upper bounds of the faint quasar abundance at $\Muv\gtrsim -22~{\rm mag}$ \citep[green;][]{2022NatAs...6..850J}
@@
 Based on the X-ray selected faint quasars, \cite{2019ApJ...884...19G} reported a number density of 
-faint quasars at $\Muv \gtrsim -22$.
-Here we take their $z=5.55$ luminosity function correcting for redshift evolution 
-with a scale factor of $10^{-0.72\Delta z}$ \citep{2016ApJ...833..222J}, where $\Delta z=0.45$,
-shown in orange in Fig.~\ref{fig:fitlf}.
-These values are substantially higher than that expected from extrapolation of the rest-UV based QLF by 
+faint quasars at $\Muv \gtrsim -22$ mag.
+Here, we show their $z=5.55$ luminosity function in orange,
+for which the normalization is scaled to $z=6$ by a factor of
+$10^{-0.72\Delta z}$ \citep{2016ApJ...833..222J}, where $\Delta z=0.45$,
+These values are substantially higher than those expected from extrapolation of the rest-UV based QLF by 
 \citetalias{2018ApJ...869..150M} (dotted curve) down to the faint end.
@@
 (\citetalias{2018ApJ...869..150M}; \citealt{2020MNRAS.495.2135N,2020MNRAS.494.1771A,2021MNRAS.502.2757O,2021MNRAS.502..662B,2022arXiv220712282K}).
-However, at the faint end at $\Muv\gtrsim -24$ mag, extended sources such as the brightest galaxies at $z\sim 6$ 
+However, at the faint end of $\Muv\gtrsim -24$ mag, extended sources such as the brightest galaxies at $z\sim 6$ 
 dominate over quasars in number at the same UV magnitude \citep{2022ApJS..259...20H}.
@@
 
-In previous sections, we calibrated the models for early SMBH evolution based on the observational constraints of BHMF and QLF at $z\sim6$.
-Next, we apply our model to predict the statistical properties of SMBHs at higher redshifts ($z\gtrsim$ 6)
-and provide prediction for future explorations of high-$z$ quasars.
+In previous sections, we calibrate the model for early SMBH evolution based on the observational constraints of the BHMF and QLF at $z\sim6$.
+Next, we apply our model to predict the statistical properties of quasars at higher redshifts ($z\gtrsim$ 6)
+and provide prediction for future explorations.
 
@@
 
-In the left panel of Fig.~\ref{fig:BHMF_rhoz}, we show the predicted BHMFs at five different redshifts of $z=6-10$
+In the left panel of Fig.~\ref{fig:BHMF_rhoz}, we show the predicted BHMFs at five different redshifts of $z=6$--$10$
 for $\fseed=0.1$ (solid) and $0.01$ (dashed).
-As shown in Fig.~\ref{fig:seedmf}, the mass distribution of seed BHs develops up to $M_\bullet \lesssim 2\times10^5~\Msun$ by $z\gtrsim 17$.
-Thus, the high-mass tail of the BHMF is produced owing to subsequent growth of seed BHs with a fraction of $\fseed$.
-The information on the seeding process still remains in the low mass regime.
+As shown in Fig.~\ref{fig:seedmf}, the mass distribution of seed BHs establishes up to $M_\bullet \lesssim 2\times10^5~\Msun$ by $z\gtrsim 17$.
+Subsequently, the BHMF develops toward higher mass ranges by the growth of seeds with a fraction of $\fseed$.
+Thus, the information on the seeding process still remains in the low mass regime.
 In fact, the case with $\fseed=0.1$ yields the number density of those growing seeds ten times higher than that with $\fseed =0.01$,
@@
 Toward lower redshifts, heavier BHs with $\gtrsim 10^7~\Msun$ emerge owing to efficient growth
-and thus the number density of such massive BHs in the high-mass tail increases.
-Since our model is calibrated against the $z=6$ BHMF of \citetalias{2010AJ....140..546W},
+and thus BHMF in the high-mass tail increases.
+Since our model is calibrated against the $z\simeq 6$ BHMF of \citetalias{2010AJ....140..546W},
 the two cases with different seeding fractions yield similar shapes of mass distribution at $M_\bullet \simeq 10^8-3\times 10^9~\Msun$ (see Fig.~\ref{fig:fitmf}).
@@
 %
-This function shape is also used to characterize the BHMF at lower-$z$ quasar populations
+This function shape is also used to characterize the BHMF of lower-$z$ quasar populations
 \citep[e.g.,][]{2013ApJ...764...45K,2015MNRAS.447.2085S}.
@@
 and $\hat \alpha$ and $\hat \beta$ are the low and high-mass end slopes, respectively.
-In Table~\ref{tab:BHMF_fit}, we summarize those parameters of the parametric BHMF at $z=6-10$ for the best-fit model in the case of $\fseed=0.01$.
+In Table~\ref{tab:BHMF_fit}, we summarize those parameters at $z=6$--$10$ for the best-fit model in the case of $\fseed=0.01$.
 %while the difference in the two BHMF shapes is profound toward the low mass range of $M_\bullet \lesssim 10^7~\Msun$.
 %The BH abundance and shape of the mass distribution at $10^5 \lesssim M_\bullet/\Msun \lesssim 10^7$ depend on the seeding fraction,
-%while the distributions converge at $M_\bullet \gg 10^7~\Msun$ toward $z= 6$. 
+%while the distributions converge at $M_\bullet \gg 10^7~\Msun$ toward $z=6$. 
 %This result suggests that the information on the seeding process would still remain in the low mass regime of $M_\bullet \lesssim 10^7~\Msun$.
@@
 a double power-law function for the case with $\fseed=0.01$.
-The mass range we use for fitting is $10^6~\Msun \leq M_\bullet \leq 10^{10}~\Msun$.
+The mass range used for fitting is $10^6~\Msun \leq M_\bullet \leq 10^{10}~\Msun$.
 }
@@
 \caption{
-The predicted quasar luminosity functions at (a) $z\sim 7$, (b) $z\sim 8$, (c) $z\sim 9$, (d) $z\sim 10-13$.
+The predicted quasar luminosity functions at (a) $z\sim 7$, (b) $z\sim 8$, (c) $z\sim 9$, and (d) $z\sim 10-13$.
 The black solid and dashed curves are the unobscured and intrinsic QLF, respectively, and the shaded region presents the $1\sigma$ statistical error.
 The expected depths and volumes of future surveys with Wide Euclid (blue; $m_{1450}= 23$ mag) and Wide RST (red; $m_{1450}= 27$ mag) are overlaid in each panel (see Table~\ref{tab:N_detect}).
-For comparison, the galaxy UV luminosity functions are plotted with the data points (grey) and the fitting functions in purple with a Schechter (dotted) and double power-law (dash-dotted) shape.
+For comparison, the galaxy UV luminosity functions are plotted with the data points (grey) and the fitting functions in purple with a Schechter (solid) and double power-law (dashed) shape.
 The luminosity function data are taken from \citet{2013MNRAS.432.2696M}, \citet{2016ApJ...819..129O}, \citet{2018ApJ...867..150M},
@@
 \citet{2022ApJS..259...20H,Harikane_2022b,Harikane_2022c}, \citet{2022arXiv220712356D}, \citet{2022arXiv220709434N}.
-The fitting forms of the galaxy luminosity functions are given by \citet{2022ApJS..259...20H} at $z\simeq 7$, 
-\citet{2020MNRAS.493.2059B} and \citet{2013MNRAS.432.2696M} at $z\simeq 8$, and \citet{Harikane_2022c} at $9\lesssim z\lesssim 13$.}
+The fitting forms of the galaxy luminosity functions are given by \citet{2022ApJS..259...20H} at $z\sim 7$, 
+\citet{2020MNRAS.493.2059B} and \citet{2013MNRAS.432.2696M} at $z\sim 8$, and \citet{Harikane_2022c} at $9\lesssim z\lesssim 13$.}
 \label{fig:LFs}
@@
 
-In the right panel of Fig.~\ref{fig:BHMF_rhoz}, we present the cumulative mass density of BHs $\rho_\bullet(z)$ in a comoving volume
+In the right panel of Fig.~\ref{fig:BHMF_rhoz}, we present the cumulative BH mass density $\rho_\bullet(z)$ in a comoving volume
 for $\fseed=0.1$ (solid) and $0.01$ (dashed),
-which is equivalent to by the integration of the BHMF:
+which is equivalent to the integration of the BHMF:
 %
@@
 Overall, the mass density of the heaviest BHs quickly grows toward lower redshifts,
-while the mass density barely evolves for the lightest BHs.
-At $z\lesssim 7-8$, heavier BHs with $\gg 10^6~\Msun$ begin to dominate the total mass budget of the entire BH population,
+while for the lightest BHs the mass density barely evolves.
+At $z\lesssim 7-8$, heavier BHs with $\gg 10^6~\Msun$ begin to dominate the mass budget of the entire BH population,
 promoting the so-called downsizing or anti-hierarchical evolution of massive BHs 
@@
 Moreover, the seeding process affects the evolution of the mass density more substantially for less massive BHs,
-which keeps the information on their initial conditions at birth.
+which retain the information on their initial distributions.
 
@@
 owing to our model prescription that allows BH seed formation earlier on and (modest) super-Eddington episodes.
-Furthermore, the measured unresolved fraction of the cosmic X-ray background constrains
-the global accretion history of massive BHs at $z>5$ \citep{2012A&A...545L...6S,2013ApJ...778..130T}.
-Upper bounds on the accreted-mass density onto massive BHs (black arrows) prohibits overproduction of low mass BHs at cosmic dawn.
-The mass density of BHs formed in the biased, overdense region of the universe %(haboring DM halos with $\Mh\gtrsim 10^{11}~\Msun$) 
+Furthermore, the unresolved fraction of the cosmic X-ray background at $z\gtrsim 5$ constrains
+the global BH accretion history \citep{2012A&A...545L...6S,2013ApJ...778..130T}.
+Upper bounds on the accreted-mass density (black arrows) prohibit overproduction of low mass BHs at cosmic dawn.
+The mass density of BHs formed in the biased, overdense region of the universe %(haboring DM halos with $\Mh\gtrsim 10^{11}~\Msun$) The mass density of BHs formed in a biased, overdense region of the universe %(haboring DM halos with $\Mh\gtrsim 10^{11}~\Msun$)
 is consistent with the constraint, unlike models that require a large number of stellar-mass BH remnants \citep[see also][]{2009ApJ...696.1798T}.
@@
 %%%%%%%
-\begin{deluxetable*}{cccccccc}%[t!]
+\begin{deluxetable*}{cccccccccc}%[t!]
 \tablecolumns{1}
@@
 \tablehead{
-  \colhead{Survey} & \colhead{ Area} & \colhead{Selection} &  \colhead{$N(z\sim 6)$} & \colhead{$N(z\sim 7)$}& \colhead{$N(z\sim 8)$}&  \colhead{$N(z\sim 9)$}&  \colhead{$N(z\sim 10)$}\\
-  \colhead{} & \colhead{(\rm{deg}$^2$)} & \colhead{(mag)} & & & & & 
+\colhead{Survey} & \colhead{Reference}  & \colhead{ Area (\rm{deg}$^2$)} & \colhead{Selection} &  \colhead{$N(z\sim 6)$} & \colhead{$N(z\sim 7)$}& \colhead{$N(z\sim 8)$}&  \colhead{$N(z\sim 9)$}&  \colhead{$N(z\sim 10)$}
+% \colhead{}       & \colhead{(\rm{deg}$^2$)} & \colhead{(mag)} & & & & & 
 }
 \startdata
-Euclid      & 15000           & $m_{1450}\leq 24$   & $6654^{+95}_{-2282}$  &  $708^{+213}_{-237}$ &   $93^{+66}_{-56}$ & $14^{+32}_{-14}$ & --  \\
-Euclid      & 15000           & $m_{1450}\leq 23$   & $2480^{+188}_{-614}$  &  $207^{+144}_{-114}$ &   $23^{+27}_{-19}$ & $3^{+12}_{-3}$ & --  \\
-Euclid Collab. (2019) & 15000   & selection func.  & --                             &  $204 (117)$                &   $16 (6)$             & $7 (2)$ & --  \\
+Euclid      & This work             & 15000    & $m_{1450}\leq 24$   & $6654^{+95}_{-2282}$  &  $708^{+213}_{-237}$ &   $93^{+66}_{-56}$ & $14^{+32}_{-14}$ & --  \\
+            & This work             &          & $m_{1450}\leq 23$   & $2480^{+188}_{-614}$  &  $207^{+144}_{-114}$ &   $23^{+27}_{-19}$ & $3^{+12}_{-3}$ & --  \\
+            & Euclid Collab. (2019) &          & simulation  & --                             &  $204 (117)$                &   $16 (6)$             & $7 (2)$ & --  \\
 % Wide Euclid & 15000  & $\Muv=-26$  & $154^{+100}_{-38}$    &  $12^{+59}_{-50}$    &   $1^{+4}_{-3}$    & -- & --  \\
 \hline
-RST    &  2000  & $m_{1450}\leq 27$  & $6759_{-3185}^{+15} $ &  $1514_{-558}^{+169}$ &  $349_{-131}^{53}$ & $85_{-48}^{+23}$ & $25^{+12}_{-15}$  \\
+RST         & This work       &  2000  & $m_{1450}\leq 27$  & $6759_{-3185}^{+15} $ &  $1514_{-558}^{+169}$ &  $349_{-131}^{53}$ & $85_{-48}^{+23}$ & $25^{+12}_{-15}$  \\
 % Wide RST    &  2000  & $\Muv=-26$ & $21_{-5}^{+13} $      &  $2_{-7}^{+8}$        &  --  & -- & --  \\
@@
 \tablecomments{
-The detection number of high-$z$ quasars predicted by the BH growth model with $\fseed=0.01$ at each redshift with the Euclid ad RST wide-area surveys.
-The number density of quasars is shown from $z=6$ to $10$ with a step of 1.
-\blue{Selection completeness is assumed to be 100\% below the magnitude limits considered.
-The integration of the QLF is conducted for quasar populations brighter than the photometric depth $m_{1450}$,
-inferred from the 5$\sigma$ point source detection limits of the $YJH$ bands in each survey.
-To mimic realistic quasar identification capability, we show the detection numbers with $m_{1450}\leq 23$ mag in comparison with}
-\citet{2019Barnett}. The values are taken from the fourth column of their Table~3 for the three redshift range: $7.0<z<7.5$, $8.0<z<8.5$, and $8.5<z<9.0$.
-The values correspond to different extrapolation of the quasar number density at higher redshifts ($\propto 10^{k_{\rm L}z}$); $k_{\rm L}=-0.72$ and $-0.92$.
-\blue{We show the prediction of no detection or no prediction in the literature with the symbol ``--''.}
+Prediction of high-$z$ quasar numbers yielded by the Euclid and RST wide-area surveys from $z\sim 6$ to $10$ with $\Delta z=1$.
+% with the BH growth model of $\fseed=0.01$.
+The QLFs we utilize to estimate the detection numbers are from the BH growth model with $\fseed=0.01$.
+The integration of the QLF is conducted assuming 100\% selection completeness for quasar populations brighter than the photometric depths,
+which are adopted as the 5$\sigma$ point source detection limits of the $YJH$ bands in each survey.
+To mimic realistic quasar identification capability, we also show the detection numbers with $m_{1450}\leq 23$ mag in comparison with
+\citet{2019Barnett}.
+The latter prediction is migrated from the fourth column of their Table~3 for three redshift ranges: $7.0<z<7.5$, $8.0<z<8.5$, and $8.5<z<9.0$,
+with trials on different extrapolations of the quasar number density at higher redshifts ($\propto 10^{k_{\rm L}z}$); $k_{\rm L}=-0.72$ and $-0.92$.
+The prediction of no detection or no references in the literature are denoted by the symbol ``--''.
 }
@@
 
-Fig.~\ref{fig:LFs} presents our prediction of QLFs at $z>6$ taken from the BH growth model with $\fseed=0.01$.
-We show QLFs at different epochs; (a) $z\sim 7$, (b) $z\sim 8$, (c) $z\sim 9$, and (d) $z\sim 10-13$.
+Fig.~\ref{fig:LFs} presents our prediction of QLFs at $z\gtrsim 6$ taken from the BH growth model with $\fseed=0.01$.
+We show QLFs at different epochs; (a) $z\sim 7$, (b) $z\sim 8$, (c) $z\sim 9$, and (d) $z\sim 10$--$13$.
 The black solid and dashed curves of each panel show the QLF for the unobscured population 
-and entire population (including unobscured and obscured quasars), respectively.
+and intrinsic population (including unobscured and obscured quasars), respectively.
 % The obscured fraction based on X-ray samples \citep{2014ApJ...786..104U} is applied to faint objects, 
 % but the correction factor is highly uncertain at the faint end of $\Muv\gtrsim -20$ mag.
-The $z\sim 5$ obscured fraction derived in an X-ray study by \citet{2014ApJ...786..104U} is used to convert the intrinsic QLF to the unobscured one,
-while we note that their obscuration fraction is highly uncertain at $\Muv \gtrsim-20$ mag.
-Similar to the BHMF, for all the redshift range, the shape of the QLF is well approximated with a double power-law function,
+The obscured fraction derived in an X-ray quasar sample up to $z\sim 5$ by \citet{2014ApJ...786..104U} is applied to the conversion between the two populations,
+while we note that a large uncertainty exists at $\Muv \gtrsim-20$ mag.
+Similar to the BHMF, for all the redshift ranges, the shape of the QLF is well approximated with a double power-law function,
 %
@@
 $\Delta \Muv \equiv \Muv - \Muv^\ast$, and $\tilde \alpha$ and $\tilde \beta$ are the faint and bright-end slopes, respectively.
-In Table~\ref{tab:QLF_fit}, we summarize those parameters of the parametric QLFs at $z=6-10$ for the best-fit models.
-From higher to lower redshifts, the number density of luminous quasars increases and the bright-end slope gets flatter.
+In Table~\ref{tab:QLF_fit}, we summarize those parameters at $z=6$--$10$ for the best-fit models.
+From higher to lower redshifts, the QLF increases and the bright-end slope gets flatter.
 
@@
 Euclid (\citealt{2011arXiv1110.3193L}; \citealt{2019Barnett}) and RST \citep{2019arXiv190205569A}.
-We here consider only their wide-area survey layers because narrow-field deep surveys are not suitable for high-$z$ quasars \citep[but see][]{2022arXiv220907325O}.
-\blue{
-Table~\ref{tab:N_detect} summarizes the expected number of quasars from those surveys.
+We here consider only their wide-area survey layers because narrow-field deep surveys are not optimized for hunting high-$z$ quasars \citep[but see][]{2022arXiv220907325O}.
+Table~\ref{tab:N_detect} summarizes the expected number yields of quasars from those surveys.
 We first integrate the QLFs at the apparent magnitude $m_{1450}\leq$ 24 mag and 27 mag for Euclid and RST, respectively.
-These depths are the 5$\sigma$ point source detection limits in the $YJH$ bands of the two facilities.
-}
-Euclid will cover $\simeq 100-700$ quasars at $z\sim7-8$ down to the limiting magnitude, and can reach up to $z\sim 9$.
-The RST will explore fainter ($\Muv>-22$ mag) and more abundant quasar populations up to $z\sim 10$.
+These depths correspond to the 5$\sigma$ point source detection limits in the $YJH$ bands of the two facilities.
+Euclid will cover $\simeq 100$--$700$ quasars at $z\sim 7$--$8$ down to the limiting magnitude ($\Muv \sim -24$ mag),
+and can reach up to $z\sim 9$.
+The RST will explore fainter ($\Muv \gtrsim -24$ mag) and more abundant quasar populations up to $z\sim 10$.
 % and increase the detection number by a factor of $\sim 2-6$ depending on the redshift range.
@@
 % high-$z$ quasars from other astrophysical sources such as Galactic brown dwarfs and low-$z$ galaxy interlopers.
-However, the estimated values above give upper bounds of the number of detectable high-$z$ quasars,
-because selection completeness is not unity in the selection of high-$z$ quasars.
-\citet{2019Barnett} investigated the efficiency of quasar selection with Euclid images and
-\blue{found that combined with ground-based optical observations,
-$z\sim 7-9$ quasars can be identified down to $J \sim$ 23 mag}
+However, the estimated values above only give upper bounds of the number of detectable high-$z$ quasars,
+because selection completeness is not unity in identifying high-$z$ quasars.
+\citet{2019Barnett} investigated the efficiency of quasar selection with Euclid images
+and found that combined with ground-based optical observations,
+$z\sim 7$--$9$ quasars can be identified down to $J \sim$ 23 mag
 due to photometric noise and contaminants in the color selection such as Galactic brown dwarfs and low-$z$ early-type galaxies.
 Adopting $m_{1450}=23$ mag as the effective depth, %based on the quasar selection methods for Euclid \citep{2019Barnett},
-our predicted detection numbers are in good agreement with their results but shows a better match for the case
-where the QLFs are extrapolated with $10^{-0.72z}$ toward higher redshfits
-(see the fourth column in their Table~3).
-
-Luminous quasars with $\Muv \lesssim -26$ mag are expected to be marginally detected by the RST and Euclid up to $z\sim 7$ and 8, respectively,
-with $\sim 1$ detection number predicted by the integration over model QLFs.
-However, \citet{2019BAAS...51c.121F} proposed that quasar detection can reach $z\sim 9$ by the two surveys
-because a moderate decline of the quasar number density ($\propto 10^{-0.78z}$) is assumed.
-The differences in those predictions will be tested by upcoming high-$z$ quasar observations (see more discussion below).
+our predicted detection numbers are in good agreement with their results but show a better match for the case
+where their QLFs are extrapolated from $z\sim 6$ with $10^{-0.72z}$ toward higher redshfits
+(see the fourth column of Table~3 in \citealt{2019Barnett}).
+
+Luminous quasars with $\Muv \lesssim -26$ mag are expected to be marginally detected by Euclid and the RST up to $z\sim 7$ and 8, respectively,
+with $\sim 1$ detection number predicted by the integration over the model QLFs.
+However, \citet{2019BAAS...51c.121F} proposed that quasar detection can reach $z\sim 9$ by the two surveys,
+assuming a moderate decline of the quasar number density ($\propto 10^{-0.78z}$) in QLF extrapolations from $z\sim 6$
+(see more discussion in Fig.~\ref{fig:QLFmag_z}).
+The differences in those predictions will be tested by upcoming high-$z$ quasar observations.
 %Studies that take into account contamination from MLT dwarfs and compact early-type galaxies and quasar selction method
@@
 We also show the galaxy UV luminosity function in each panel of Fig.~\ref{fig:LFs}
-along with the fitting function in a Schechter (dotted) and double powe-law (dashed-dotted) shape extended to the brighter end
+along with the fitting function in a Schechter (solid) and double powe-law (dashed) shape extended to the bright end
 \citep{2013MNRAS.432.2696M, 2016ApJ...819..129O, 2018ApJ...867..150M, 2019ApJ...883...99S, 2020MNRAS.493.2059B,
@@
 2022ApJS..259...20H, Harikane_2022b, Harikane_2022c, 2022arXiv220709434N}.
-Galaxies at $\Muv\gtrsim -23$ mag dominate quasars in number at all the redshifts and make it 
-difficult to identify rare quasars among those faint objects.
+Galaxies at $\Muv\gtrsim -23$ mag dominate in number at all the redshifts and impede
+the identification of relatively rare quasars among those faint objects.
 Since the extrapolated galaxy luminosity function with a Schechter shape declines quickly with the luminosity increasing,
-the galaxy abundance becomes comparable to that of quasars at $\Muv \sim -23$ mag ($z=7-8$), $-24$ mag ($z=9$), and $-25$ mag ($z=10-13$).
-On the other hand, if the bright end of the galaxy luminosity function is extended, the critical UV magnitude shifts to
-$\Muv\sim-26$, $-25$, and $\ll -30$ mag for each redshift range.
-Future deep and wide surveys will unveil the relative contribution of the two populations and the relative roles in cosmic reionization
+the galaxy abundance becomes comparable to that of quasars at $\Muv \sim -23$ mag ($z\sim 7$--$8$), $-24$ mag ($z\sim 9$), and $-25$ mag ($z\sim 10$--$13$).
+On the other hand, if the bright end of the galaxy luminosity function is extended with the bright-end power-law slope,
+the critical UV magnitude shifts to $\Muv\sim-26$, $-25$, and $\ll -30$ mag for each redshift range.
+Future deep and wide surveys will unveil the relative contribution of the two populations and their roles in cosmic reionization
 (see also \citetalias{2018ApJ...869..150M}, \citealt{2022NatAs...6..850J}).
@@
 \caption{
-Redshift evolution of the quasar number density at different UV magnitudes.
-The theoretical prediction from $z=6$ to $10$ are shown for the cases of $\fseed=0.1$ (solid) and 0.01 (dashed), respectively.
-From the models at $z\geq 6$, the quasar number is characterized with $\propto 10^{k_{\rm L}z}$,
+Redshift evolution of the QLF value at different UV magnitudes from $\Muv= -27$ mag to $-23$ mag.
+The theoretical model prediction from $z=6$ to $10$ are shown for the cases of $\fseed=0.1$ (solid) and 0.01 (dashed), respectively.
+At $z\geq 6$, the quasar number is characterized with $\propto 10^{k_{\rm L}z}$,
 where the index is $k_\mathrm{L} \simeq -0.91$ 
-and $-0.62$ for quasars at $\Muv=-27$ and $-23$ mag, respectively.
-The observational data at lower redshifts $z\sim 0-6$ are from the Subaru HSC results \citep{2018PASJ...70S..34A,2018ApJ...869..150M,2020ApJ...904...89N},
+and $-0.62$ for quasars at $\Muv=-27$ mag and $-23$ mag, respectively.
+The observational data at lower redshifts $0\leq z \leq 6$ are compiled from the Subaru HSC results \citep{2018PASJ...70S..34A,2018ApJ...869..150M,2020ApJ...904...89N},
 SDSS \citep{2006AJ....131.2766R,2013ApJ...768..105M},
@@
 
-In Fig.~\ref{fig:QLFmag_z}, we present the quasar number density at different UV magnitudes from $\Muv=-27$ to $-23$ mag as a function of redshift.
-The solid curves show the cases for $\fseed = 0.1$ and the dashed curves show the cases for $\fseed = 0.01$ at each magnitude bin.
-Each curve corresponds to the value at a UV magnitude from $\Muv=-27$ mag to $-23$ mag.
-Our theoretical predictions are shown at $z\geq 6$ (thick curves),
+In Fig.~\ref{fig:QLFmag_z}, we present the quasar number density evolution as a function of redshift.
+The solid curves show the cases for $\fseed = 0.1$ and the dashed curves show the cases for $\fseed = 0.01$, respectively.
+Each curve corresponds to the QLF value at a UV magnitude from $\Muv=-27$ mag to $-23$ mag.
+Our theoretical predictions are shown at $z\gtrsim 6$ (thick curves),
 while observational results compiled in \cite{2020ApJ...904...89N} are shown at lower redshifts (thin curves).
-The evolutionary trend can be fitted as $\propto 10^{k_{\rm L}z}$,
-where $k_{\rm L}\simeq -0.91$ and $-0.62$ for the brightest and faintest population
+The evolutionary trend can be fitted as $\propto 10^{k_{\rm L}z}$ at high redshifts.
+The best-fit indexes are $k_{\rm L}\simeq -0.91$ and $-0.62$ for the brightest and faintest population
 at $z\gtrsim 6$, respectively.
-A rapid decay of the luminous quasar abundance at $\Muv<-26$ mag toward higher redshifts is found by 
+For the abundance of luminous quasars with $\Muv \lesssim -26$ mag, a rapid decay toward higher redshifts is suggested by
 observational studies \citep[e.g.,][]{2001AJ....122.2833F,2013ApJ...768..105M,2016ApJ...833..222J,2019ApJ...884...30W}.
 For instance, \citet{2019ApJ...884...30W} proposed a decay index of $k_{\rm L}=-0.78\pm{0.18}$ for those bright quasars at $6\lesssim z \lesssim 7$.
-The slopes in our model prediction of $\Muv <=-26$ are slightly steeper ($k_\mathrm{L} \simeq -0.84$ at $\Muv=-26$),
-but consistent with their result within the $1\sigma$ error range.
+The slopes in our model prediction of $\Muv\leq -26$ are slightly steeper ($k_\mathrm{L} \simeq -0.84$ at $\Muv=-26$),
+but consistent with their finding within the $1\sigma$ error range.
 
@@
 
-From the BH growth model described in Section~\ref{sec:MF}, we further explore individual BH evolutionary tracks starting from the BH seeding phases.
+From the BH growth model described in Section~\ref{sec:MF}, we further explore individual BH evolutionary tracks starting from their seeding phases.
 We generate a sample of 10$^6$ BHs, whose formation time and mass distribution at birth follow the model described in Section~\ref{sec:seed}. 
 Adopting the best-fit parameters in the case of $\fseed = 0.01$, in every time interval $\tlife=18.76$ Myr,
-we assign a constant Eddington ratio generated from the Schechter-type ERDF characterized by $\lambda_0=0.87$ and $\alpha=0.20$ 
+we assign a constant Eddington ratio generated from the Schechter-type ERDF characterized with $\lambda_0=0.87$ and $\alpha=0.20$ 
 (see Section~\ref{sec:fitting_result}).
-With those parameters, we grow the individual BHs until $z=6$ and study their statistical properties in producing massive BHs.
+With those parameters, we grow the individual BHs until $z=6$ and study their statistical properties.
 
@@
 % (i.e., $\Delta t_{\rm H} \times f_{\rm duty} \simeq 55$, 69, and 85 Myr), respectively.
-On the other hand, the average duty cycle for the entire BH population is calculated as $f_{\rm duty}= \langle 0.075\rangle $
-adopting this ERDF (see Section~\ref{sec:fitting_result}), and is significantly lower than those for massive BH sub-samples.
+On the other hand, the average duty cycle for the entire BH population is calculated as $\langle f_{\rm duty} \rangle =0.075$
+adopting this ERDF (see Section~\ref{sec:fitting_result}), and is significantly lower than those for the massive BH sub-samples.
 Therefore, we suggest that SMBHs observed in $z\sim 6$ quasars are a biased population
-that undergoes longer active accretion episodes along its growth.
+that undergoes longer active accretion episodes.
 
@@
 % \red{KI: still not sure what we discuss below... among the 7 BHs, is anyone consistent with Feige's BH?}
-\citet{2021ApJ...907L...1W} discovered the currently known most distant quasar at $z=7.642$ (red diamond in Fig.~\ref{fig:Mevol}).
+\citet{2021ApJ...907L...1W} discovered the currently known most distant quasar at $z=7.642$,
+with $M_{\bullet}\simeq 1.6\times 10^9~\Msun$ and $\lambda \simeq 0.67$ (red diamond in Fig.~\ref{fig:Mevol}).
 Assuming continuous Eddington accretion, the extrapolated BH is as massive as $10^{4-6}~\Msun$ at $z= 30$. 
@@
 %Therefore we raise a caveat that under these assumptions the seed mass achieved may be unreliable. 
-Our best-fit model naturally explains the existence of the most extreme BH,
-taking into account the episodical accretion nature of quasars,
-%(note extrapolation with the observed $\lambda$ requires an unrealistically high seed mass). 
-%including both bursts of accretion and quiescent phases.
-%Among the five supermassive BH growth tracks,
-%we find one matching this currently known most distant quasar, 
-and the consistent growth track among the sub-sample is indicated with the red solid curve 
-(with $M_\bullet \simeq 1.7\times 10^9~\Msun$ and $\lambda \simeq 0.6$ at $z=7.6$).
-The result demonstrates that the formation of the massive BHs is achieved by the combination of rare halo environments planting a seed BH 
+Our best-fit model naturally explains the existence of this most extreme BH,
+taking into account the episodical accretion nature of quasars (see the red solid curve;
+$M_\bullet \simeq 1.7\times 10^9~\Msun$ and $\lambda \simeq 0.6$ at $z=7.6$).
+The result demonstrates that
+one possible formation channel of the highest-$z$ quasar is through the combination of rare halo environments planting a seed BH 
 with $\sim 2\times 10^5~\Msun$ at $z\sim 30$ and several (modest) super-Eddington accretion bursts.
 
-The measurement of the ionization state of the intergalactic medium (IGM) surrounding a quasar is
+Multiple episodes of BH accretion naturally yield variable quasar light curves and leave ionized gas with a complex structure.
+The measurement of the ionization state of the intergalactic medium surrounding a quasar is
 a powerful tool to constrain the timescale of $t_{\rm Q}$ in a luminous quasar phase
@@
 However, we note that the line-of-sight proximity effect is only sensitive to the most recent activity of quasars.
-Alternatively, the transverse proximity effect is useful to probe a longer quasar activity comparable to the Salpeter timescale \citep{2004ApJ...612..706A,2008ApJ...674..660V,2019ApJ...882..165S}.
+Alternatively, the transverse proximity effect is useful to probe a longer quasar activity comparable to a Salpeter timescale \citep{2004ApJ...612..706A,2008ApJ...674..660V,2019ApJ...882..165S}.
 Recently, \citet{2022MNRAS.516..582K} proposed a new technique to photometrically map the quasar light echoes using Ly$\alpha$ forest tomography
@@
 
-In general, it is challenging to unveil the properties of the underlying quasar population
+Even with the current observational facilities, it is challenging to unveil the properties of the underlying quasar population
 because of the limitation of the photometric depths of quasar surveys.
@@
 applying the mass distribution function of seed BHs over $10^2~\Msun \lesssim M_\bullet \lesssim 10^5~\Msun$
-that originate from massive primordial stars formed in massive DM progenitor halos of quasar host galaxies.
-In our accretion model, those early BH populations are assumed to experience multiple accretion bursts with a time duration,
+that originate from massive primordial stars formed in quasar host galaxies.
+In our accretion model, those early BH populations are assumed to experience multiple accretion bursts,
 in each of which a constant Eddington ratio is assigned following a Schechter distribution function.
@@
 \item
-The best-fitted model requires the duration of accretion bursts to be $\tau \simeq 20-30$ Myr,
-which is a good fraction of the $e$-folding time for the exponential BH mass growth.
-The Schechter-like shape of the ERDF is constrained to produce the observed BHMF and QLF at $z\simeq 6$; namely,
+The best-fitted model requires the typical duration of accretion bursts to be $\tau \simeq 20-30$ Myr,
+which is a fraction of the Salpeter time ($t_{\rm S} \simeq 45$ Myr).
+The ERDF with a Schechter-like shape is constrained to produce the observed BHMF and QLF at $z\simeq 6$; namely,
 the characteristic Eddington ratio and power-law slope are $\lambda_0 \simeq 0.88$ and $\alpha \simeq 0.12-0.2$,
@@
 We find that the existence of SMBHs hosted in $z\gtrsim 6$ quasars can be explained by
-multiple accretion episodes, instead of assuming continuous Eddington-limited growth (see Fig.~\ref{fig:Mevol}).
+multiple accretion episodes with variable Eddington ratios, instead of assuming continuous Eddington-limited growth (see Fig.~\ref{fig:Mevol}).
 In fact, the average duty cycle of active accretion phases with $\lambda \geq 1$ is as high as $\simeq 15~\%$
 for massive BHs that reach $\gtrsim 10^8~\Msun$ by $z\simeq 6$.
-This indicates that those biased BH populations undergo longer active accretion episodes to be observed as quasars.
+This result indicates that those biased BH populations undergo longer active accretion episodes to be observed as quasars.
 We also find that the observed Eddington-ratio distribution function is skewed to a log-normal shape from the intrinsic Schechter function
@@
 
-\vspace{100mm}
 \bibliography{ref}{}

### 2022-10-06 ms.tex
version1006(submit); aas linenumbers on, arxiv off

@@
 \usepackage{mathrsfs}
+
+\usepackage[mathlines]{lineno}
+\linenumbers
 
@@
 
-\title{The Assembly of Black Hole Mass ad Luminosity Functions of High-redshift Quasars\\via Multiple Accretion Episodes}
+\title{The Assembly of Black Hole Mass and Luminosity Functions of High-redshift Quasars\\via Multiple Accretion Episodes}
 
@@
 and each of them lasts for $\tau \simeq 20-30$ Myr.
-The average duty cycle in super-Eddington phases is $\simeq 15\%$ for massive BHs that reach $\gtrsim 10^8~\Msun$ by $z\simeq 6$,
+The average duty cycle in super-Eddington phases is $\simeq 15\%$ for massive BHs that reach $\gtrsim 10^8~M_\odot$ by $z\simeq 6$,
 which is nearly twice that of the entire population.
-We also find that the observed Eddington-ratio distribution function is skewed to a log-normal shape 
+We find that the observed Eddington-ratio distribution function is skewed to a log-normal shape 
 owing to detection limits of quasar surveys.

### 2022-11-19 ms.tex
1119; typos corrected in bold

@@
 %
-The normalization is set so that the integrant of this function over $\lambda_\mathrm{min}(=0.01) \leq \lambda < \infty$ is unity.
+The normalization is set so that the \textbf{integral} of this function over $\lambda_\mathrm{min}(=0.01) \leq \lambda < \infty$ is unity.
 The minimum Eddington ratio $\lambda_\mathrm{min}$ is adopted from the simulated evolution of quasar luminosities 
@@
 
-We discuss the MCMC fitting results and compare the BHMF and QLF with those observed distribution functions.
+We discuss the MCMC fitting results and compare the BHMF and QLF with \textbf{the} observed distribution functions.
 In Fig.~\ref{fig:contour}, we visualize the fitting results of the model parameters in two-dimensional 
@@
 The power-law index of $\alpha$ in the ERDF increases as the seeding fraction decreases.
-Thus, a more significant fraction of BHs actively grow with $\lambda \gtrsim 1$ and develop the QLF and BHMF.
+Thus, a more significant fraction of BHs actively \textbf{grows} with $\lambda \gtrsim 1$ and \textbf{develops} the QLF and BHMF.
 
@@
 but overproduces fainter quasars at $\Muv\gtrsim -24~{\rm mag}$.
-Simillar as the BHMF, the difference between the model and observational data at the faint end becomes smaller with
+\textbf{Similarly to} the BHMF, the difference between the model and observational data at the faint end becomes smaller with
 the lower seeding fraction.
@@
 We also show the galaxy UV luminosity function in each panel of Fig.~\ref{fig:LFs}
-along with the fitting function in a Schechter (solid) and double powe-law (dashed) shape extended to the bright end
+along with the fitting function in a Schechter (solid) and double \textbf{power}-law (dashed) shape extended to the bright end
 \citep{2013MNRAS.432.2696M, 2016ApJ...819..129O, 2018ApJ...867..150M, 2019ApJ...883...99S, 2020MNRAS.493.2059B,

### 2022-12-25 response.txt
review1222; my revision: ms revised, ref added, answers in response.pages copied to response.txt, figs/f*_corner_logtau.pdf added

Dear Editor,
Thank you for forwarding us the reviewer's comments concerning our manuscript submitted to the Astrophysical Journal
Title: The Assembly of Black Hole Mass and Luminosity Functions of High-redshift Quasars via Multiple Accretion Episodes
Authors: Wenxiu Li, Kohei Inayoshi, Masafusa Onoue and Daisuke Toyouchi
Number: AAS42476
We are thankful for the reviewer's comments and have revised our manuscript accordingly.
We hope that the revised version is now acceptable for publication.
Sincerely,
The Authors

— to reviewer —
We thank the reviewer for the careful reading and thoughtful comments. We have revised the manuscript to address the reviewer’s comments, and the revised parts are indicated by red text throughout the manuscript. We reply to the specific comments point-by-point below.

1) Section 2, page 3, right column: In Li+21, the authors employ the Dijkstra+14 prescription to 
estimate the LW background, which assumes that haloes nearby formed all of the stars in a single burst. 
I was wondering whether the authors considered a more physically motivated case in which 
SF proceeds smoothly when galaxies become more massive (see, e.g. Lupi et al. 2021) 
and the impact it might have on the seed formation probability.

Thanks for the suggestion. In Li+21, we do not consider the smoothed SF process. In our semi-analytical model, the information of nearby halos is limited to their masses and emergence time from the Press-Schechter formalism and non-linear halo clustering. Therefore, we lack the information of stellar mass evolving in nearby halos. Moreover, our treatment of measuring the LW photons at a free-fall timescale after single star bursts underestimates the LW radiation by assuming all old stars instead of young stars emitting strong UV radiation.
Therefore, the influence of the LW background enhancing the seed mass is conservative. We add explanations to point out the simplification adopted in our model (page 3, right column, line 233-240).

2) Section 2.2, page 4, eq 6: Eq 6 defines an accretion rate, not a mass growth rate, as it neglects the (1-eta) factor (with eta being the radiative efficiency). 
Given the definition of lambda, the mass growth should account for the missing factor. 
Obviously, since eta=0.1 is small, the correction is not expected to significantly impact the results. Nonetheless, a comment on this missing factor should be included.

Thanks for pointing it out, we add a comment on the simplification of the (1-eta) factor (page 5, left column, line 343-347 ).

3) Section 2.3, page 7, Eq. 13: I am not sure Eq. 13 is correct. In particular, as it is written in the manuscript, the only way fobs can become smaller than 0.84 is for Lbol to be larger than 10^42 Lsol, which is not plausible. I personally rederived Eq. 13, and I could not obtain the one reported in the manuscript. On top of this, Eq. 13 is derived assuming the flat regime of the X-ray bolometric correction in Eq. 14. At low BH masses, which likely correspond to low luminosities, this assumption is perfectly reasonable.  However, at the high luminosities potentially reached when the BHs exceed 10^7 Msun, this relation is not valid anymore, 
and the slope change should be accounted for. If the authors do not want to include this additional term,  they should at least comment on the expected effect on the results.

Thanks for the reviewer’s careful reading. This equation was wrong in the expression of L_bol.
In the code the f_obs is calculated from L_Xray and we now replace this equation Eq.13 with the correct functional form f_obs(L_Xray) from Ueda et al. 2014 (https://ui.adsabs.harvard.edu/abs/2014ApJ...786..104U). (page 7, right column, line 511-516)

4) Section 2.5, MCMC fitting: More details on the MCMC procedure should be given. 
For example, there is no mention of the number of samples used in the MCMC. 
It is also not clear whether the MCMC has reached convergence (computing the autocorrelation or changing the number of samples).

We agree with the reviewer that the convergence of MCMC fitting is essential and always necessary to be ensured. We add descriptions regarding this (page 8, left column, line 539-544).

5) The corner plots in Fig. 3 show some curious results. First, it seems that a correlation exists between alpha and lambda0, which is not clear to me. Why does the MCMC not explore the high alpha/high lambda 0 region at all? 
Secondly, the value of tau seems to be completely skewed toward the lower boundary of the prior distribution, hence the best fit value might be biased by this choice. Have the authors tried to extend the range of tau to enclose values down to 1 or less Myr to see how the distribution changes?

As the reviewer mentioned, there is an anti-correlation between lambda0 and alpha. The reason is that fixing the other parameters, the higher characteristic Eddington ratio (lambda0) would lead to more rapid BH growth, then constrained by the z=6 data, the best-fit alpha would prefer the Eddington ratio distribution function being skewed to lower lambda values, i.e., lower alpha. The posterior distribution reached by MCMC stays with this (lambda0, alpha) anti-correlation, thus does not spread in the high alpha/high lambda 0 region. We add an explanation on this (page 9, right column line 638-642). We delete the statement on the anti-correlation between alpha and fseed, since it’s not strongly indicated by the results.

On the fitting for parameter tau, we set the uniform prior within (10-200) Myr, the lower bound is determined by the trade-off between the computing time and the reliability of the prior.
Low values of tau make the iteration times too much (~800 times of calculation of Eq.9 from z=20-6 with tau=1 Myr in one sample) and dramatically lower the efficiency of the fitting.
To ensure the best-fit tau in posterior is not biased by the choice of lower boundary, we carry out two tests: (i) a parameter survey with fixed tau=1-10 Myr with delta tau=1 Myr and grids of other parameters. The lowest chi^2 value (7.28) found by these parameter combinations are higher than the best-fit results found at tau~18.76 Myr (6.21).
(ii) we do the MCMC fitting for 3 parameters (log_delta, lambda0, alpha) in the fseed=0.01 case, with two fixed tau values: 5 and 10Myr. The fitting can converge within reasonable computing time, and the best fit chi2 = 8.44 and 7.16, for tau=5 and 10 Myr, respectively. Both are higher than chi2=6.21, found at tau~18.76 in our previous fitting. 
Therefore, we confirm that the chi^2 reaches a minimum value at the best-fit parameters we find. For illustration purpose, in Fig.3 we change the tau distribution to be in log scale: the height of the histogram is written as dP/dlog_tau, keeping the the area of bars as the fraction of samples in the tau ranges. In this way the tau distribution is more balanced and easy to read.
We find the definition of the chi^2 value was wrong. The MCMC fitting explores the parrameter space to minimize the value of the classical chi^2 + prior function, which is identical to 
-2*ln (P_data*P_prior). We correct the descriptions (see page 8, right column, line 585-598).

6) I understand that running the MCMC with 5 parameters instead of 4 would have been more expensive and also that the authors wanted to explore the impact of different fseed. 
Nonetheless, I wonder whether they considered this idea of running the MCMC including fseed, to find the most likely fseed (if any) that matched the BHMF and the QLF.

As the reviewer expected, initially we tried fitting with the 5 free parameters including fseed and found it hard to reach convergence.
So we decided to fix fseed and vary it with 3 values to demonstrate its influence on the fitting. We add an explanation on this on page 8, left column, in Section 2.5, line 540.

7) Apart from delta, the other best-fit parameters in Table 1 seem more similar between the fseed=0.1 and fseed=0.01 cases than between the 1 and 0.1 ones. How does this relate to the authors' comment about the 1 and 0.1 being quantitatively similar (also in the light of the chi-squared value which is a factor of 2 higher in the fseed=1 case than in the 0.1 one)? 
Moreover, is delta perfectly identical in the 1.0 and 0.1 cases? Or is it a matter of number of digits reported? In this second case, I would suggest the authors to report the value using exponential notation, to highlight how different they are.

Thanks for asking. We find the term "quantitatively similar" less objective than we intended. 
In the revised version, we choose to emphasize the fseed=1 case is omitted for its unreality (100% of BHs formed having subsequent growth, without considering any negative environmental effects). We re-arrange the statement on page 9, left column, line 601. We changed delta values to exponential notation in Table 1.

8) In Section 4.1 the authors comment on the fact that the information on the seeding process remains in the low mass regime. However, Fig. 6 shows that the 0.1 and 0.01 cases perfectly overlap at very low masses. Could the authors comment on it? Is it because typical PopIII remnants are so abundant that the difference is not significant, whereas the conditions for larger seed masses become less likely for low fseed? Or is there another reason?

Thanks for asking. In Fig.6, the BHMF consist of the mass distribution of both growing BHs and the remaining seeds, i.e., fseed of the whole BH population with subsequent growth + (1-fseed) of all BHs stay at their initial masses in the range of 10^2-10^5 solar mass.
The BHs remaining in this very low mass range are 90% and 99% of the seeds in the fseed=0.1 and 0.01 cases, respectively, so the difference between the solid and dashed lines is not significant plotted in log scale spanning a large range of the y axis. 
We realized that the term "the seeding process” is ambiguous, with which we refer to the different seeding fraction fseed, which results in different BHMF shapes in 10^5-10^7 solar mass range. We changed the phrasing that may cause confusion (page 11, left column, line 747).

9) Moreover, in this work the authors only consider haloes above 10^11 Msun at z=6 for their models, neglecting lower mass haloes. 
I am wondering what effect lower mass haloes in these overdense regions might have on the low-mass end of the BHMF/QLF. 
Obviously, given the available constraints, I do not expect the results to change in the high-mass end, but maybe the predictions at lower masses might vary.

Thanks for pointing it out. The BHs we consider are a biased population formed in halos above 10^11 solar mass. Namely, the BH seeds are more massive and early-formed than typical PopIII stars. We modify the statement and raise the caveat on page 12, right column, line 780.
Here we give a rough estimate on the contribution of low mass BHs formed in M=10^10 Msun halos. The halo abundance is ~0.03 Mpc^-3. BHs formed as typical PopIII remnants in such small halos reach mass ~10^3 Msun (Hirano+2015). Considering the shallow halo gravitational potential, such BHs can hardly grow their mass with sufficient cold gas accretion. Therefore, the mass density of these small BHs is ~ 30 Msun, which is comparable to our current value. In this sense, the underestimation is not severe problem.

Minor comments

- Introduction, page 2, second column: In Lupi et al. 2021, the author also mentioned the fact that the higher probability of mergers and irradiation is not the only condition affecting the formation of massive seeds, because of the stronger metal pollution resulting from star formation. I think a comment on this aspect is relevant.

Thanks for the reviewer’s suggestion. We add a discussion in the introduction.

- Introduction, page 2, second column: in addition to Lupi et al 2021 and Li et al. 2021, there is also a recent paper by Latif and collaborators that suggested massive clouds could form in qso progenitors (arxiv 2207.05093)

Thanks for the recommendation. We included the reference in the same paragraph, line 126, highlighting the influence of turbulence. Therefore, we choose to mention only the Lupi+ 2021 and Li+ 2021, which account for more comprehensive aspects in the seed formation.

- Section 2.1, page 4, line 288: The assumption of massive primordial stars collapsing into BHs assumes that stars are at most mildly rotating. However, when rotation is important, Stacey et al. (2016) showed that PopIII stars might produce strong winds, reducing their mass, and finally exploding as SNe similar to PopII/I stars. I am wondering whether the authors considered that very massive protostars as those likely to directly collapse into BHs could be characterised by large radii, and might therefore accrete gas with significant angular momentum, resulting in potentially fast rotation.

We do not trace angular momentum in the stellar evolution. We add some references and more explicitly describe the parameter eta depicting angular momentum in the BH seed formation (see page 4, left column).

- Section 2.5, line 525: What is the reason behind the exponential cutoff? What is the impact of this choice compared to a uniform prior over the entire considered range?

We impose an exponential cut-off on the prior for log_delta <-4, in order to suppress the probability of such low delta’s, which are similarly equivalent with delta=0 (exponential BH growth). This treatment helps with the fitting convergence at low log_delta values.

- Section 2.5, line 538: I checked Figure 21 in Schulze et al. 2015, but I could not find anything related to alpha. Maybe the authors wanted to refer to a different figure from the same article. If not, I suggest them to refer to the Table in Schulze+2015, which reports some values for alpha both positive and negative.

Thanks for the suggestion. In Schulze+ 2015, the authors use fitting formula including mass dependence in the characteristic lambda (see Eq. 15, 16). So the alpha parameter we adopt does not correspond to any parameters in their fitting function. We refer readers to the Figure 21, which shows a positive and negative slope at the low lambda end, for type 1 and type 2 AGNs, respectively. We believe the figure is adequate for indicating the slope of the Schechter lambda distribution.

- Section 3, Fig. 4: Maybe I misunderstood these results, but it seems that a significant fraction of the MBH population at high redshift might be characterised by low luminosities, in order not to overestimate the luminosity function. In this respect, I think it might help the reader to show (even in an appendix) a distribution of the average Eddington ratio/quasar lifetime as a function of BH mass.

We model the Eddington ratio distribution without including mass dependence, for simplicity in describing the BH growth. In Fig. 4, the low mass BHs may not be observable, e.g., 10^7 Msun BH with an Eddington ratio < 0.1. The massive BHs (M>10^8 Msun), however, are a statistically biased population with on average higher lambda realized in their growth history.

- Section 5, lines 917-921: The authors comment on the formation and evolution of highest-z quasars that results from their work. This conclusion is in line with results by dedicated cosmological simulations, as those by Di Matteo+17, Barai+18, and Lupi+19 (the latter also mentions that super-Eddington accretion phases occurred in the simulation, although the growth was forced to stay within the Eddington limit).

Thanks for the recommendation. We have added a comment on the consistency with these simulation results (page16, left column, line 975).

- The model presented in this work assumes that the Eddington ratio distribution follows a well-defined distribution which is the same independently of the redshift or the BH mass. Although consistent with observations of high-redshift quasars, cosmological simulations showed that MBHs in massive galaxies (Dubois+14, Di Matteo+17, Barai+18, Lupi+19) are characterised by three different growth phases, one of them being almost constant at the Eddington rate. I am perfectly aware that the model cannot easily take into account this behaviour, but I think a comment about it is in order.

Following the reviewer’s suggestion, we have added a comment about this Eddington ratio distribution assumption (page 6, right column, line 401-407).

Typos:

- Section 2.2, line 360: integrant->integral

- Section 3, line 567: with those observed -> with the observed

- Section 3, lines 594-595: grow->grows, develop->develops

- Section 3, line 639: Similar as -> Similarly to

Section 4.2, line 820: powe-law -> power-law

We have fixed the typos thanks to the reviewer’s correction.

Sincerely yours,
The Authors

### 2022-12-25 ms.tex
review1222; my revision: ms revised, ref added, answers in response.pages copied to response.txt, figs/f*_corner_logtau.pdf added

@@
 \citep{2021ApJ...917...60L, 2022arXiv220614459T}.
+\red{
+We note that metal enrichment of the pristine halos from internal and external star formation activities also regulates the IMF.
+Further studies accounting for this effect are essential to improve our work.
+}
 %As a result, \citet{2021ApJ...917...60L} predicted a top-heavy mass distribution of seed BHs ranging from $10^2-10^5~\Msun$.
@@
 The time evolution of the gas dynamics and thermal states is calculated in a self-consistent way with the halo assembly history.
+\red{
+We note that the H$_2$-photodissociating radiation is calculated following \citet{2014MNRAS.442.2036D},
+measuring the flux at a free-fall timescale after single star bursts in nearby halos. 
+This treatment underestimates the photodissociating flux, since the assumption of old stellar population provides less UV photons than smoothly-proceeding star formation
+\citep{2021MNRAS.503.5046L}.
+Therefore, our scenario is conservative in estimating the enhanced seed BH mass.
+}
 
@@
 
-At the vicinity of an accreting protostar, an accretion disk forms due to angular momentum of the inflowing material from large scales. 
+At the vicinity of an accreting protostar, an accretion disk forms due to angular momentum of the inflowing material from large scales
+\red{
+\citep{2010MNRAS.403...45S,2011Sci...331.1040C,2011ApJ...737...75G}.
+}
 The episodic nature of disk accretion decreases the time-averaged accretion rate onto the protostar as $\Mdot_{\star}=\eta \Mdot$, 
-where we adopt $\eta=0.3$ as the conversion efficiency \citep{2016MNRAS.459.1137S, 2022arXiv220614459T}. 
+where we adopt $\eta=0.3$ as the conversion efficiency \red{due to the centrifugal barrier} \citep{2016MNRAS.459.1137S, 2022arXiv220614459T}. 
 %\blue{
@@
 which is consistent with the value obtained from the Soltan-Paczy{\'n}ski argument \citep[e.g.,][]{2002MNRAS.335..965Y,2010ApJ...725..388C}.
+\red{
+Here we take the mass accretion rate as the net BH growth rate,
+omitting the subtraction of energy loss with radiation by a factor of $1-\eta_0=0.9$.
+This treatment simplifies the functional form without significantly impacting the results.
+}
 Based on studies on the mass dependence of the radiative efficiency for AGNs at $z\lesssim$ 3 
@@
 
-To characterize the % ERDF for a BH population at any time snapshot together with 
-episodic accretion patterns of individual BHs, 
+To characterize the episodic accretion patterns of individual BHs, 
 we introduce a time duration of $\tlife$, during which a single value of $\lambda$ is assigned to an accreting BH
@@
 long-lasting rapid growth phase of a BH.
-This phenomenological method also avoids numerous uncertainties in modeling of the galaxy assembly, 
-gas feeding, and BH feedback processes in the quasar progenitor halos.
-Instead of treating those ingredients implemented in previous semi-analytical models, we extract 
+This phenomenological method avoids numerous uncertainties in modeling of the galaxy assembly, 
+gas feeding, and BH feedback processes in the quasar progenitor halos,
+\red{
+which are implemented as sub-grid models in cosmological simulations \citep{2017MNRAS.467.4243D,2018MNRAS.473.4003B,2019MNRAS.488.4004L}.
+Interestingly, these studies found the growth of massive BH seeds toward SMBHs is characterized by patterns including quiescent stages and accretion bursts.
+Instead of treating these ingredients explicitly in our semi-analytical model,} we extract 
 an averaged but fundamental timescale that governs mutual correlation between the QLF and BHMF,
@@
 We take three different values of $\fseed = 1$, $0.1$, and $0.01$, and explore its effect on shaping the QLF and BHMF.
-Since we find that the results in the cases of $\fseed = 1$ and $0.1$ are quantitatively similar,
-we thus show only the cases with $\fseed=0.1$ and $0.01$ in the following discussion.
+% Since we find that the results in the cases of $\fseed = 1$ and $0.1$ are quantitatively similar,
+% we thus show only the cases with $\fseed=0.1$ and $0.01$ in the following discussion.
 Note that the seed mass function shown in Fig.~\ref{fig:seedmf} is given with $\fseed = 1$.
@@
 
-In this study, we adopt the obscuration fraction $\fobsc$ based on X-ray observations \citep{2014ApJ...786..104U}
-and rewrite it with bolometric luminosity as
+In this study, we adopt the obscuration fraction $\fobsc$ based on X-ray observations \citep{2014ApJ...786..104U}:
+\red{
+%
+\begin{eqnarray}
+\fobsc & = \text{min} & \left\{ \psi_{\rm max}, \right.  \\ \nonumber 
+&   & \left. \text{max}\left[ \psi_{43.75}  - \beta (\log L_{\rm X} -43.75), \psi_{\rm min}     \right]\right\},
+\end{eqnarray}
+%
+where the parameters are written as $\psi_{\rm max}=0.84$, $\psi_{\rm min}=0.2$, $\psi_{43.75}=0.73$, and $\beta=0.24$.
+% %
+% \begin{eqnarray}
+% \fobsc & = \text{min} & \left\{ 0.84, \right.  \\ \nonumber 
+% &   & \left. \text{max}\left[   0.73-0.24 \log \left(\frac{L_{\rm X}}{10^{43.75}L_\odot}\right),0.2      \right]\right\}
+% \end{eqnarray}
+% %
+%
+Here, we use the bolometric correction factor of the hard X-ray band:}
 %
 \begin{equation}
-\fobsc = \text{min}\left\{0.84 , 11.23-0.24 \log \left(\frac{\Lbol}{L_\odot}\right) \right \}.
-%  \fobsc = \text{min}\lbrace  0.84 , 0.73-0.24\times[ \log (\Lbol/L_\odot) -43.75] \rbrace,
-\end{equation}
-%
-Here, we use the bolometric correction factor from the hard X-ray band:
-%
-\begin{equation}
-  f^{\rm bol}_{\rm X} =
+  f^{\rm bol}_{\rm X} \equiv \frac{\Lbol}{L_{\rm X}}=
   a\left[1+\left(\frac{\log \left(\Lbol / L_\odot\right)}{b}\right)^{c}\right],
@@
 The best-fit values of the first four parameters are calculated by the MCMC method, while $\fseed$ is fixed to a single value.
+\red{
+We vary four parameters instead of five in the fitting to guarantee that the Marchov chain can be stabilized. 
+The fitting is carried out by sampling 100 walkers with 5000 steps.
+We verify the convergence of the posterior distribution results by doubling the chain length.
+}
 % In what follows, we describe the results for $\fseed = 0.1$ and $0.01$ (see Appendix for the case with $\fseed =1.0$).
@@
 In this analysis, we constrain those four parameters to be within certain physically acceptable ranges, 
-assuming a prior function for each quantity.
+assuming \red{a prior probability function $P^{\rm prior}_a$ for each quantity $a=\tlife$, $\delta$, $\lambda_0$, and $\alpha$}.
 We use a uniform prior on $\tlife$ with a limit of $10~{\rm Myr} \leq \tlife \leq 200~{\rm Myr}$,
@@
 % posterior
-Following the prior distribution functions, the four parameters are sampled to generate the synthetic 
-BHMF and QLF dataset, which are compared to the observational dataset. 
-The discrepancy between the model and observational data is evaluated with a $\chi^2$-value defined by
+\red{
+In the MCMC fitting, the four parameters are sampled to generate the synthetic BHMF and QLF dataset,
+which are compared to the observational dataset. 
+The probability is evaluated by a $\chi^2$-type value defined by
+% The discrepancy between the model and observational data is evaluated with a $\chi^2$-type value defined by
 %
@@
   \chi^2 = \sum_{x,i}
-  \frac{\left(\log{\Phi^{\rm mod}_{x,i}} - \log{\Phi^{\rm obs}_{x,i}}\right)^2}{(\log{\Phi^{\rm err}_{x,i}})^2},
+  \frac{\left(\log{\Phi^{\rm mod}_{x,i}} - \log{\Phi^{\rm obs}_{x,i}}\right)^2}{(\log{\Phi^{\rm err}_{x,i}})^2}
+  - 2 \sum_{a} \ln P^{\rm prior}_a.
 \end{align}
 %
+The first term on the right hand side is the classical $\chi^2$ value in statistics which measures the dispersion of the observational data from the model prediction,
 where $\Phi^{\rm mod}_{x,i}$ and $\Phi^{\rm obs}_{x,i}$ represent the modeled and observational value 
@@
 with nearly equal weight.
-The posterior distribution of the MCMC fitting is stabilized around the minimum value of $\chi^2$ (highest likelihood), 
+The second term denotes the deviation of the parameter set from the prior distribution.
+The posterior distribution of the MCMC fitting is stabilized around the minimum value of $\chi^2$ (highest probability), 
 with the models best reproducing the $z=$ 6 BHMF and QLF.
+}
+% Following the prior distribution functions, the four parameters are sampled to generate the synthetic 
+% BHMF and QLF dataset, which are compared to the observational dataset. 
+% The discrepancy between the model and observational data is evaluated with a $\chi^2$-value defined by
+% %
+% \begin{align}
+%   \chi^2 = \sum_{x,i}
+%   \frac{\left(\log{\Phi^{\rm mod}_{x,i}} - \log{\Phi^{\rm obs}_{x,i}}\right)^2}{(\log{\Phi^{\rm err}_{x,i}})^2},
+% \end{align}
+% %
+% where $\Phi^{\rm mod}_{x,i}$ and $\Phi^{\rm obs}_{x,i}$ represent the modeled and observational value 
+% on the \textit{i-}th bin of the BHMF ($x=\Mbh$) and QLF ($x=\Muv$), and $\Phi^{\rm err}_{x,i}$ is the corresponding error.
+% Adopting 10 mass bins and 12 magnitude bins, we treat the errors from comparison both in the BHMF and QLF
+% with nearly equal weight.
+% The posterior distribution of the MCMC fitting is stabilized around the minimum value of $\chi^2$ (highest likelihood), 
+% with the models best reproducing the $z=$ 6 BHMF and QLF.
 
@@
 \centering
-\includegraphics[width=85mm]{f1_corner.pdf}\hspace{3mm}
-\includegraphics[width=85mm]{f2_corner.pdf}
+\includegraphics[width=85mm]{f1_corner_logtau.pdf}\hspace{3mm}
+\includegraphics[width=85mm]{f2_corner_logtau.pdf}
 \caption{
@@
 
-We discuss the MCMC fitting results and compare the BHMF and QLF with \textbf{the} observed distribution functions.
+\red{
+In the following, we discuss the MCMC fitting results and compare the BHMF and QLF with \textbf{the} observed distribution functions.
+The best-fit parameters together with the $\chi^2$ values for the three $\fseed$ cases are tabulated in Table~\ref{tab:best_fits}.
+Since $\fseed=1$ is an idealized case neglecting any environmental effects impeding BHs from subsequent growth,
+and the deviation from the observational data denoted by $\chi^2$ is nearly a factor of 2 higher than those in the other two cases,
+hereafter we discuss only the results of $\fseed=0.1$ and $0.01$ in comparison with observations.
+}
 In Fig.~\ref{fig:contour}, we visualize the fitting results of the model parameters in two-dimensional 
@@
 
-For the two cases, the best-fit solution yields a small value of $\delta < 0.1$.
+The best-fit solutions yield a small value of $\delta < 0.1$.
 This result favors the nearly exponential BH growth model (Eqs.~\ref{eq:mdot} and \ref{eq:f_M}).
@@
 observed in the rest-frame UV spectra \citep[e.g.,][]{2018ApJ...867...30E,2019ApJ...884L..19D}.
-The characteristic Eddington ratio needs to be close to unity, otherwise the highest luminosity and BH mass
+The characteristic Eddington ratio $\lambda_0$ needs to be close to unity, otherwise the highest luminosity and BH mass
 in the model would differ from those in observations.
-The power-law index of $\alpha$ in the ERDF increases as the seeding fraction decreases.
+\red{
+\sout{The power-law index of $\alpha$ in the ERDF increases as the seeding fraction decreases.
 Thus, a more significant fraction of BHs actively \textbf{grows} with $\lambda \gtrsim 1$ and \textbf{develops} the QLF and BHMF.
+}
+As shown in Fig.~\ref{fig:contour}, the power-law index $\alpha$ in the ERDF shows an anti-correlation with the value of $\lambda_0$.
+With lower $\lambda_0$, higher values of $\alpha$ enhance the fraction of actively accreting BHs,
+and develop the QLF and BHMF consistent with the observations.
+}
 
@@
 \tablehead{
-  \colhead{$\fseed$}  && \colhead{$\tau$ (Myr)} & \colhead{$\delta$} &  \colhead{$\lambda_0$}  & \colhead{$\alpha$}  & \colhead{$\chi^2$}
+  \colhead{$\fseed$}  && \colhead{$\tau$ (Myr)} & \colhead{\red{$\log\delta$}} &  \colhead{$\lambda_0$}  & \colhead{$\alpha$}  & \colhead{$\chi^2$}
 }
 \startdata
-1.0    &&  23.13 &    0.001    &   0.96    &   -0.06    &    15.77   \\
-0.1    &&  20.07 &    0.001    &   0.89    &    0.12    &    8.27    \\
-0.01   &&  18.76 &    0.055    &   0.87    &    0.20    &    6.21    \\
+1.0    &&  23.13 &    -2.97    &   0.96    &   -0.06    &    15.77   \\
+0.1    &&  20.07 &    -2.98    &   0.89    &    0.12    &    8.27    \\
+0.01   &&  18.76 &    -1.26    &   0.87    &    0.20    &    6.21    \\
 \enddata
@@
 Subsequently, the BHMF develops toward higher mass ranges by the growth of seeds with a fraction of $\fseed$.
-Thus, the information on the seeding process still remains in the low mass regime.
+\red{\sout{
+Thus, the information on the seeding process still remains in the low mass regime.}}
 In fact, the case with $\fseed=0.1$ yields the number density of those growing seeds ten times higher than that with $\fseed =0.01$,
 making the difference in the BH abundance at $M_\bullet \sim 10^{5-6}~\Msun$.
+\red{
+Thus, the information on the seeding fraction still remains in this low mass regime.}
 Toward lower redshifts, heavier BHs with $\gtrsim 10^7~\Msun$ emerge owing to efficient growth
@@
 % $\fseed=0.1~(0.01)$.
-Moreover, the seeding process affects the evolution of the mass density more substantially for less massive BHs,
-which retain the information on their initial distributions.
+\red{
+We note that our model captures a biased BH population formed in the overdense region,
+and neglects the BH seeds from typical PopIII remnants in lower-mass halos ($\Mh<10^{11}~\Msun$).
+The latter population is typically less massive but more abundant and emerges later.
+Therefore, although the BHMFs in the high-mass end ($M_\bullet \gtrsim 10^7~\Msun$) sufficiently match the observations,
+we caution that in the low-mass range, the BH abundance can be underestimated.
+}
 
@@
 with $\sim 2\times 10^5~\Msun$ at $z\sim 30$ and several (modest) super-Eddington accretion bursts.
+\red{
+From a statistical perspective, our semi-analytical model predicts Eddington accretion phases in line with the results found by previous cosmological simulations
+\citep{2017MNRAS.467.4243D,2018MNRAS.473.4003B,2019MNRAS.488.4004L}.
+}
 

### 2022-12-27 ms.tex
review1225; k revised version

@@
 and frequency of halo mergers.
+\blue{In such massive halos, intense cold streams through cosmic webs and supersonic turbulent motion promote the formation
+of massive gas clouds that collapse into supermassive stars and seed BHs \citep{2009Natur.457..451D,2012MNRAS.422.2539I,2022Natur.607...48L}.}
 The mass distribution of seed BHs is expected to be substantially top-heavy, extending the upper mass to $\gtrsim 10^{4-5}~\Msun$
 \citep{2021ApJ...917...60L, 2022arXiv220614459T}.
-\red{
-We note that metal enrichment of the pristine halos from internal and external star formation activities also regulates the IMF.
-Further studies accounting for this effect are essential to improve our work.
+\blue{
+Metal enrichment of the progenitor halos due to internal and external star formation activity would regulate the formation of 
+seed BHs and alter the characteristic of the mass distribution function (see also a quantitative argument on the low efficiency of enrichment in 
+\citealt{2021ApJ...917...60L}).
+Further studies with hydrodynamic simulations are required to improve our understanding of the efficiency of metal enrichment in quasar progenitor halos
+\citep[e.g.,][]{2018MNRAS.475.4378C}.
 }
@@
 The time evolution of the gas dynamics and thermal states is calculated in a self-consistent way with the halo assembly history.
-\red{
-We note that the H$_2$-photodissociating radiation is calculated following \citet{2014MNRAS.442.2036D},
-measuring the flux at a free-fall timescale after single star bursts in nearby halos. 
-This treatment underestimates the photodissociating flux, since the assumption of old stellar population provides less UV photons than smoothly-proceeding star formation
-\citep{2021MNRAS.503.5046L}.
-Therefore, our scenario is conservative in estimating the enhanced seed BH mass.
+\blue{
+We calculate the time-dependent H$_2$-photodissociating and H$^-$ photo-detachment radiation flux (${\rm H}_2+\gamma \rightarrow 2~{\rm H}$; 
+${\rm H}^-+\gamma \rightarrow {\rm H}+{\rm e}^-$) from each star forming galaxy with a radiation temperature of $T_{\rm rad}=2\times 10^4~{\rm K}$ \citep{2014MNRAS.445..544S,2015MNRAS.450.4350I}.
+Following the treatment adopted in \citet{2014MNRAS.442.2036D}, the flux is measured at one free-fall timescale of the individual source halos after their single star bursts.
+This assumption underestimates the radiation flux because the radiation contribution from pre-existing old stellar populations is neglected
+(see also \citealt{2021MNRAS.503.5046L}, where the star formation activity is assumed to proceed in a smooth way rather than single burst episodes).
+Therefore, our model gives a conservative estimate of the formation efficiency of seed BHs.
 }
@@
 where $c_{\rm s}$ is the thermal sound speed, $v_{\rm tur}$ is the turbulent velocity of gas (i.e., the specific kinetic energy accumulated through halo mergers), and
-the coefficient is set to $\alpha_0=1$ \footnote[1]{The value of $\alpha_0=1.0$ is motivated by cosmological simulations of massive primordial stars
+the coefficient is set to $\alpha_0=1$ \footnote{The value of $\alpha_0=1.0$ is motivated by cosmological simulations of massive primordial stars
 under fast streaming velocities \citep{2017Sci...357.1375H,2019MNRAS.484.3510S}.
@@
 
+\blue{
 At the vicinity of an accreting protostar, an accretion disk forms due to angular momentum of the inflowing material from large scales
-\red{
-\citep{2010MNRAS.403...45S,2011Sci...331.1040C,2011ApJ...737...75G}.
-}
+\citep{2010MNRAS.403...45S,2011Sci...331.1040C,2011ApJ...737...75G}.}
 The episodic nature of disk accretion decreases the time-averaged accretion rate onto the protostar as $\Mdot_{\star}=\eta \Mdot$, 
-where we adopt $\eta=0.3$ as the conversion efficiency \red{due to the centrifugal barrier} \citep{2016MNRAS.459.1137S, 2022arXiv220614459T}. 
+where we adopt $\eta=0.3$ as the conversion efficiency \blue{owing to angular momentum of the accreting flow} \citep{2016MNRAS.459.1137S, 2022arXiv220614459T}. 
 %\blue{
@@
 The feedback-regulated mass can be approximated as
-\footnote[2]{A recent study by \citet{2022arXiv220614459T} provides a more sophisticated prescription of the feedback-regulated stellar mass based on their radiation hydrodynamical simulations.}
+\footnote{A recent study by \citet{2022arXiv220614459T} provides a more sophisticated prescription of the feedback-regulated stellar mass based on their radiation hydrodynamical simulations.}
 %
@@
 via stellar winds \citep{2003ApJ...591..288H,2015MNRAS.451.4086S}.
-Therefore, we assume that the mass of a remant BH is equal to that of its stellar progenitor.
+\blue{One important caveat is the effect of stellar rotation on the structure evolution.
+Namely, the mass loss rate of a rotating massive star via winds would be enhanced by the centrifugal force on the surface
+or suppressed by efficient mixing of the interior structure by meridional circulation \citep[see][references therein]{2008A&A...489..685E,2012A&A...542A.113Y}.
+Although those effects in the high mass regime are poorly understood yet, full general-relativistic simulations of the gravitational collapse of a rotating supermassive star 
+show that most of the stellar mass is eventually swallowed by the newly born BH, ejecting only $\sim 10\%$ of the mass \citep{2002ApJ...572L..39S,2016PhRvD..94b1501S}.}
+Therefore, we assume that the mass of a remnant BH is equal to that of its stellar progenitor.
+%\footnote{
+%\blue{Stellar rotation is expected to induce various effects on the structure evolution; namely, the mass loss rate via winds would be enhanced by the centrifugal force on the surface
+%or suppressed by efficient mixing of the interior structure by meridional circulation \citep[see][references therein]{2008A&A...489..685E,2012A&A...542A.113Y}.
+%Although those effects in the high mass regime are poorly understood yet, full general-relativistic simulations of the gravitational collapse of a rotating supermassive star 
+%found that most of the stellar mass is eventually swallowed by the newly born BH, ejecting only $\sim 10\%$ of the mass \citep{2002ApJ...572L..39S,2016PhRvD..94b1501S}.}}.
 
@@
 which is consistent with the value obtained from the Soltan-Paczy{\'n}ski argument \citep[e.g.,][]{2002MNRAS.335..965Y,2010ApJ...725..388C}.
-\red{
-Here we take the mass accretion rate as the net BH growth rate,
-omitting the subtraction of energy loss with radiation by a factor of $1-\eta_0=0.9$.
-This treatment simplifies the functional form without significantly impacting the results.
-}
 Based on studies on the mass dependence of the radiative efficiency for AGNs at $z\lesssim$ 3 
@@
 where $M_{\bullet,c}=10^8~\Msun$ is adopted
-\footnote[3]{
+\footnote{
 A series of radiation hydrodynamical simulations for BH accretion
@@
 With a positive value of $\delta$, the BH growth at the high mass end is suppressed,
-while the growth speed for less masssive BHs is accelerated.
+while the growth speed for less massive BHs is accelerated.
 In the limit of $\delta \ll 1$, where $f(\Mbh) \simeq 1$ is nearly independent of $M_{\bullet,c}$,
@@
 $t_{\rm S} =  \Mbh/\Mdot_{\mathrm{Edd}} \approx 45$ Myr (the so-called Salpeter timescale; \citealt{1964ApJ...140..796S}).
+\blue{
+Note that we do not explicitly consider the energy loss with radiation in Eq.~(\ref{eq:mdot}), neglecting a factor of $1-\eta_0=0.9$.
+This small deviation from unity can be absorbed by the uncertainty due to the functional form of $f(M_\bullet)$ and does not bring 
+a significant impact on the results discussed below.
+}
 
@@
 gas feeding, and BH feedback processes in the quasar progenitor halos,
-\red{
-which are implemented as sub-grid models in cosmological simulations \citep{2017MNRAS.467.4243D,2018MNRAS.473.4003B,2019MNRAS.488.4004L}.
-Interestingly, these studies found the growth of massive BH seeds toward SMBHs is characterized by patterns including quiescent stages and accretion bursts.
+\blue{
+which are implemented as sub-grid models in previous cosmological simulations \citep{2017MNRAS.467.4243D,2018MNRAS.473.4003B,2019MNRAS.488.4004L}.
+These studies found that the growth of massive BH seeds toward SMBHs is characterized by the intermittent patterns with quiescent and accretion phases.
 Instead of treating these ingredients explicitly in our semi-analytical model,} we extract 
@@
 For an accreting BH with a bolometric luminosity of $\Lbol=\lambda L_\mathrm{Edd}$, 
-its rest-frame ultraviolot (UV) absolute magnitude of $\Muv$ at 1450 $\mathrm{\AA}$ is estimated as
+its rest-frame ultraviolet (UV) absolute magnitude of $\Muv$ at 1450 $\mathrm{\AA}$ is estimated as
 %
@@
 In this study, we adopt the obscuration fraction $\fobsc$ based on X-ray observations \citep{2014ApJ...786..104U}:
-\red{
+\blue{
 %
 \begin{eqnarray}
-\fobsc & = \text{min} & \left\{ \psi_{\rm max}, \right.  \\ \nonumber 
-&   & \left. \text{max}\left[ \psi_{43.75}  - \beta (\log L_{\rm X} -43.75), \psi_{\rm min}     \right]\right\},
+%\fobsc & = \text{min} & \left\{ \psi_{\rm max}, \right.  \\ \nonumber 
+%&   & \left. \text{max}\left[ \psi_{43.75}  - \beta (\log L_{\rm X} -43.75), \psi_{\rm min}     \right]\right\},
+\fobsc && = \text{min}  \left[ \psi_{\rm max}, \psi \right], \\[5pt]
+\psi &&= \text{max}\left[\psi_0  - \beta \log (L_{\rm X}/L_{\rm X,0}), \psi_{\rm min}     \right],
 \end{eqnarray}
 %
-where the parameters are written as $\psi_{\rm max}=0.84$, $\psi_{\rm min}=0.2$, $\psi_{43.75}=0.73$, and $\beta=0.24$.
+where the parameters are written as $\psi_{\rm max}=0.84$, $\psi_{\rm min}=0.2$, $\psi_{0}=0.73$, $\beta=0.24$, and $L_{\rm X,0}=10^{43.75}~{\rm erg~s}^{-1}$.
 % %
@@
 The best-fit values of the first four parameters are calculated by the MCMC method, while $\fseed$ is fixed to a single value.
-\red{
+\blue{
 We vary four parameters instead of five in the fitting to guarantee that the Marchov chain can be stabilized. 
@@
 In this analysis, we constrain those four parameters to be within certain physically acceptable ranges, 
-assuming \red{a prior probability function $P^{\rm prior}_a$ for each quantity $a=\tlife$, $\delta$, $\lambda_0$, and $\alpha$}.
+assuming \blue{a prior probability function $P^{\rm prior}_a$ for each quantity $a=\tlife$, $\delta$, $\lambda_0$, and $\alpha$}.
 We use a uniform prior on $\tlife$ with a limit of $10~{\rm Myr} \leq \tlife \leq 200~{\rm Myr}$,
@@
 is constrained at $-4 \leq \log \delta \leq -0.3$
-\footnote[4]{ We first set a uniform prior at $0\leq \delta \leq 1$, 
+\footnote{ We first set a uniform prior at $0\leq \delta \leq 1$, 
 and find the posterior distribution assembles to $\delta \lesssim 0.1$.
@@
 Note that the value of $\alpha$ remains poorly constrained by the current high-$z$ quasar observations,
-but the low-$z$ quasar samples support $-0.3 \lesssim \alpha \lesssim 0.3$ \citep[e.g., see Figure 21 in][]{2015MNRAS.447.2085S}.
+but the low-$z$ quasar samples support $-0.3 \lesssim \alpha \lesssim 0.3$ 
+\blue{\citep[e.g., see the mass-integrated ERDF for comparison; the right panel of Figure 21 in][]{2015MNRAS.447.2085S}}.
 
@@
 % posterior
-\red{
+\blue{
 In the MCMC fitting, the four parameters are sampled to generate the synthetic BHMF and QLF dataset,
@@
 %
-The first term on the right hand side is the classical $\chi^2$ value in statistics which measures the dispersion of the observational data from the model prediction,
+The first term on the right hand side is the classical $\chi^2$ value that measures the dispersion of the observational data from the model prediction,
 where $\Phi^{\rm mod}_{x,i}$ and $\Phi^{\rm obs}_{x,i}$ represent the modeled and observational value 
@@
 with nearly equal weight.
-The second term denotes the deviation of the parameter set from the prior distribution.
+The second term denotes the deviation of the parameter set from the assumed prior distribution functions.
 The posterior distribution of the MCMC fitting is stabilized around the minimum value of $\chi^2$ (highest probability), 
@@
 
-\red{
-In the following, we discuss the MCMC fitting results and compare the BHMF and QLF with \textbf{the} observed distribution functions.
-The best-fit parameters together with the $\chi^2$ values for the three $\fseed$ cases are tabulated in Table~\ref{tab:best_fits}.
-Since $\fseed=1$ is an idealized case neglecting any environmental effects impeding BHs from subsequent growth,
-and the deviation from the observational data denoted by $\chi^2$ is nearly a factor of 2 higher than those in the other two cases,
-hereafter we discuss only the results of $\fseed=0.1$ and $0.01$ in comparison with observations.
+\blue{
+We discuss the MCMC fitting results and compare the BHMF and QLF with their observed distribution functions.
+The best-fit model parameters together with the $\chi^2$ values for the three cases with $\fseed$ are summarized in Table~\ref{tab:best_fits}.
+We note that the ideal case with $\fseed=1.0$, where environmental effects preventing BHs from growing is neglected, yields a $\chi^2$ value 
+nearly twice larger than those in the other two cases.
+Therefore, in the following, we focus only on the results with $\fseed=0.1$ and $0.01$ in comparison with observations.
 }
@@
 in the model would differ from those in observations.
-\red{
-\sout{The power-law index of $\alpha$ in the ERDF increases as the seeding fraction decreases.
-Thus, a more significant fraction of BHs actively \textbf{grows} with $\lambda \gtrsim 1$ and \textbf{develops} the QLF and BHMF.
-}
-As shown in Fig.~\ref{fig:contour}, the power-law index $\alpha$ in the ERDF shows an anti-correlation with the value of $\lambda_0$.
-With lower $\lambda_0$, higher values of $\alpha$ enhance the fraction of actively accreting BHs,
-and develop the QLF and BHMF consistent with the observations.
-}
-
-%%%%%%%
-%    Table. 1
-%%%%%%%
-\begin{deluxetable}{cccccccc}%[t!]
-\tablecolumns{1}
-\renewcommand\thetable{1} %! fix indexing
-\tablewidth{0pt}
-\tablecaption{Best-fit parameters for BH growth\label{tab:best_fits}} %!!!!
-\tablehead{
-  \colhead{$\fseed$}  && \colhead{$\tau$ (Myr)} & \colhead{\red{$\log\delta$}} &  \colhead{$\lambda_0$}  & \colhead{$\alpha$}  & \colhead{$\chi^2$}
-}
-\startdata
-1.0    &&  23.13 &    -2.97    &   0.96    &   -0.06    &    15.77   \\
-0.1    &&  20.07 &    -2.98    &   0.89    &    0.12    &    8.27    \\
-0.01   &&  18.76 &    -1.26    &   0.87    &    0.20    &    6.21    \\
-\enddata
-\tablecomments{
-The best-fit parameters optimized by MCMC sampling for the three different cases of $\fseed$.
-The fitting performance is quantified with the relative magnitudes of the $\chi^2$ value.}
-\end{deluxetable}
+\blue{
+%\sout{The power-law index of $\alpha$ in the ERDF increases as the seeding fraction decreases.
+%Thus, a more significant fraction of BHs actively \textbf{grows} with $\lambda \gtrsim 1$ and \textbf{develops} the QLF and BHMF.
+%}
+As shown in Fig.~\ref{fig:contour}, the power-law index $\alpha$ in the ERDF shows an anti-correlation with the characteristic Eddington ratio $\lambda_0$.
+With a higher $\lambda_0$ (i.e., faster BH growth), the ERDF needs to be skewed toward the lower $\lambda$ regime with a smaller value of $\alpha$ (i.e., a larger fraction of inactive BHs)
+to be consistent with the observed QLF and BHMF.
+}
 
@@
 and the ten-fold difference in $\fseed$ is nearly compensated.
-
-%%%%%%%
-%    Fig. 4
-%%%%%%%
-\begin{figure*}
-\centering
-%\includegraphics[width=170mm]{fits_MF.png}
-\includegraphics[width=85mm]{f1ndraw60MF_spread.pdf}\hspace{3mm}
-\includegraphics[width=85mm]{f2ndraw60MF_spread.pdf}
-\caption{
-The BH mass function at $z=6$ with the best-fit parameters (black curve) and the $1\sigma$ statistical error (grey shaded region) 
-for the cases with $\fseed=0.1$ (left) and $0.01$ (right). 
-For comparison, the BHMF constructed by \citetalias{2010AJ....140..546W} and their statistical errors (see text) are shown with the cyan curve and shaded region.
-}
-\label{fig:fitmf}
-\vspace{2mm}
-\end{figure*}
-
-%%%%%%%
-%    Fig. 5
-%%%%%%%
-\begin{figure*}
-\centering
-%\includegraphics[width=170mm]{fits_LF.png}
-\includegraphics[width=85mm]{f1ndraw60LF_spread.pdf}\hspace{3mm}
-\includegraphics[width=85mm]{f2ndraw60LF_spread.pdf}
-\caption{
-The quasar luminosity function at $z=6$ with the best-fit parameters (black curve) and the $1\sigma$ statistical error (grey shaded region) 
-for the cases with $\fseed=0.1$ (left) and $0.01$ (right).
-The solid and dashed curves are the unobscured and intrinsic QLF, respectively.
-We overlay the observational data for the unobscured QLF taken from \citetalias{2018ApJ...869..150M} in blue and their parametric function with a double power-law function (dotted curve).
-Upper bounds of the number density of faint quasars are given by \citet{2022NatAs...6..850J}, based on the Hubble Space Telescope imaging observations (green).
-The QLF data based on X-ray selected quasars at $z\sim 5.55$ are overlaid in orange \citep{2019ApJ...884...19G}, for which the normalization is scaled to $z=6$
-by a factor of $10^{-0.72\Delta z}$ \citep{2016ApJ...833..222J}, where $\Delta z=0.45$.
-}
-\label{fig:fitlf}
-\vspace{5mm}
-\end{figure*}
 
@@
 %%%%%%%
+%    Table. 1
+%%%%%%%
+\begin{deluxetable}{cccccccc}%[t!]
+\tablecolumns{1}
+\renewcommand\thetable{1} %! fix indexing
+\tablewidth{0pt}
+\tablecaption{Best-fit parameters for BH growth\label{tab:best_fits}} %!!!!
+\tablehead{
+  \colhead{$\fseed$}  && \colhead{$\tau$ (Myr)} & \colhead{\blue{$\log\delta$}} &  \colhead{$\lambda_0$}  & \colhead{$\alpha$}  & \colhead{$\chi^2$}
+}
+\startdata
+1.0    &&  23.13 &    -2.97    &   0.96    &   -0.06    &    15.77   \\
+0.1    &&  20.07 &    -2.98    &   0.89    &    0.12    &    8.27    \\
+0.01   &&  18.76 &    -1.26    &   0.87    &    0.20    &    6.21    \\
+\enddata
+\tablecomments{
+The best-fit parameters optimized by MCMC sampling for the three different cases of $\fseed$.
+The fitting performance is quantified with the relative magnitudes of the $\chi^2$ value.}
+\end{deluxetable}
+
+%%%%%%%
+%    Fig. 4
+%%%%%%%
+\begin{figure*}
+\centering
+%\includegraphics[width=170mm]{fits_MF.png}
+\includegraphics[width=85mm]{f1ndraw60MF_spread.pdf}\hspace{3mm}
+\includegraphics[width=85mm]{f2ndraw60MF_spread.pdf}
+\caption{
+The BH mass function at $z=6$ with the best-fit parameters (black curve) and the $1\sigma$ statistical error (grey shaded region) 
+for the cases with $\fseed=0.1$ (left) and $0.01$ (right). 
+For comparison, the BHMF constructed by \citetalias{2010AJ....140..546W} and their statistical errors (see text) are shown with the cyan curve and shaded region.
+}
+\label{fig:fitmf}
+\vspace{2mm}
+\end{figure*}
+
+%%%%%%%
+%    Fig. 5
+%%%%%%%
+\begin{figure*}
+\centering
+%\includegraphics[width=170mm]{fits_LF.png}
+\includegraphics[width=85mm]{f1ndraw60LF_spread.pdf}\hspace{3mm}
+\includegraphics[width=85mm]{f2ndraw60LF_spread.pdf}
+\caption{
+The quasar luminosity function at $z=6$ with the best-fit parameters (black curve) and the $1\sigma$ statistical error (grey shaded region) 
+for the cases with $\fseed=0.1$ (left) and $0.01$ (right).
+The solid and dashed curves are the unobscured and intrinsic QLF, respectively.
+We overlay the observational data for the unobscured QLF taken from \citetalias{2018ApJ...869..150M} in blue and their parametric function with a double power-law function (dotted curve).
+Upper bounds of the number density of faint quasars are given by \citet{2022NatAs...6..850J}, based on the Hubble Space Telescope imaging observations (green).
+The QLF data based on X-ray selected quasars at $z\sim 5.55$ are overlaid in orange \citep{2019ApJ...884...19G}, for which the normalization is scaled to $z=6$
+by a factor of $10^{-0.72\Delta z}$ \citep{2016ApJ...833..222J}, where $\Delta z=0.45$.
+}
+\label{fig:fitlf}
+\vspace{5mm}
+\end{figure*}
+
+%%%%%%%
 %    Fig. 6
@@
 Subsequently, the BHMF develops toward higher mass ranges by the growth of seeds with a fraction of $\fseed$.
-\red{\sout{
-Thus, the information on the seeding process still remains in the low mass regime.}}
+%\red{\sout{
+%Thus, the information on the seeding process still remains in the low mass regime.}}
 In fact, the case with $\fseed=0.1$ yields the number density of those growing seeds ten times higher than that with $\fseed =0.01$,
-making the difference in the BH abundance at $M_\bullet \sim 10^{5-6}~\Msun$.
-\red{
+\blue{making the difference in the BH abundance at $M_\bullet \sim 10^{5-7}~\Msun$.
 Thus, the information on the seeding fraction still remains in this low mass regime.}
@@
 % $\fseed=0.1~(0.01)$.
-\red{
-We note that our model captures a biased BH population formed in the overdense region,
-and neglects the BH seeds from typical PopIII remnants in lower-mass halos ($\Mh<10^{11}~\Msun$).
-The latter population is typically less massive but more abundant and emerges later.
-Therefore, although the BHMFs in the high-mass end ($M_\bullet \gtrsim 10^7~\Msun$) sufficiently match the observations,
-we caution that in the low-mass range, the BH abundance can be underestimated.
+\blue{
+We note that our model considers a BH population formed in the overdense region,
+and neglects the contribution of BH seeds from ordinary PopIII remnants in lower-mass halos ($\Mh<10^{11}~\Msun$).
+The latter population is typically less massive ($M_\star \lesssim 10^3~\Msun$) but more abundant \citep[e.g.,][]{2015MNRAS.448..568H,2022arXiv220614459T}.
+Therefore, the BHMF at the low-mass end in our model underestimate their contribution while
+the high-mass end at $M_\bullet \gtrsim 10^7~\Msun$ matches the observed distribution well.
 }
@@
 our predicted detection numbers are in good agreement with their results but show a better match for the case
-where their QLFs are extrapolated from $z\sim 6$ with $10^{-0.72z}$ toward higher redshfits
+where their QLFs are extrapolated from $z\sim 6$ with $10^{-0.72z}$ toward higher redshifts
 (see the fourth column of Table~3 in \citealt{2019Barnett}).
@@
 The differences in those predictions will be tested by upcoming high-$z$ quasar observations.
-%Studies that take into account contamination from MLT dwarfs and compact early-type galaxies and quasar selction method
+%Studies that take into account contamination from MLT dwarfs and compact early-type galaxies and quasar selection method
 %have confirmed the capability of these surveys in searching high-$z$ quasars \citep{2019A&A...631A..85E,2019BAAS...51c.121F}.
@@
 with $\sim 2\times 10^5~\Msun$ at $z\sim 30$ and several (modest) super-Eddington accretion bursts.
-\red{
-From a statistical perspective, our semi-analytical model predicts Eddington accretion phases in line with the results found by previous cosmological simulations
-\citep{2017MNRAS.467.4243D,2018MNRAS.473.4003B,2019MNRAS.488.4004L}.
+\blue{
+The mass range of the highest-$z$ SMBHs can be achieved by previous cosmological simulations with a certain type of
+sub-grid models for BH feeding and feedback \citep{2017MNRAS.467.4243D,2018MNRAS.473.4003B,2019MNRAS.488.4004L}.
 }

### 2022-12-28 ms.tex
review1228; publicated ref updated

@@
 \citep[e.g.][]{1971ApJ...170..223C,1992MNRAS.259..725S,2002MNRAS.335..965Y,2004MNRAS.351..169M,2008MNRAS.388.1011M,2004MNRAS.354.1020S,
-2009ApJ...690...20S,2014MNRAS.439.2736D,2014ApJ...786..104U,2017A&A...600A..64T,2022arXiv220607357S}.
+2009ApJ...690...20S,2014MNRAS.439.2736D,2014ApJ...786..104U,2017A&A...600A..64T,2022ApJ...934...66S}.
 
@@
 The second approach is more phenomenological, using extrapolation of the low-$z$ QLF evolution with 
-fitting function forms \citep[e.g.,][]{2019MNRAS.488.1035K,2020MNRAS.495.3252S,2022arXiv220702233F}.
+fitting function forms \citep[e.g.,][]{2019MNRAS.488.1035K,2020MNRAS.495.3252S,2022ApJ...938...25F}.
 This method also allows us to forecast the higher-$z$ QLF and bring insights for future surveys.
@@
 \citep{2006MNRAS.370..289B,2009MNRAS.396..343R,2009ApJ...696.1798T,2012MNRAS.422.2051N,2014ApJ...781...60H,
-2015MNRAS.448..568H,2018MNRAS.474.3825V,2021MNRAS.506..613S,2022arXiv220614459T,2022arXiv220505717B}.
+2015MNRAS.448..568H,2018MNRAS.474.3825V,2021MNRAS.506..613S,2023MNRAS.518.1601T,2022MNRAS.516..138B}.
 Massive star formation episodes in the early universe is substantially modulated by external environmental effects such as
@@
 and allow supermassive stars with $\sim 10^5~\Msun$ (presumably seed BHs) to form at the halo centers 
-\citep{2013ApJ...778..178H,2013A&A...558A..59S,2019PASA...36...27W,2022arXiv220614459T}.
+\citep{2013ApJ...778..178H,2013A&A...558A..59S,2019PASA...36...27W,2023MNRAS.518.1601T}.
 Although the conditions required for heavy seed formation are thought to be too stringent to be realized in the typical regions of the early universe
@@
 The mass distribution of seed BHs is expected to be substantially top-heavy, extending the upper mass to $\gtrsim 10^{4-5}~\Msun$
-\citep{2021ApJ...917...60L, 2022arXiv220614459T}.
+\citep{2021ApJ...917...60L, 2023MNRAS.518.1601T}.
 \blue{
@@
 where $c_{\rm s}$ is the thermal sound speed, $v_{\rm tur}$ is the turbulent velocity of gas (i.e., the specific kinetic energy accumulated through halo mergers), and
-the coefficient is set to $\alpha_0=1$ \footnote{The value of $\alpha_0=1.0$ is motivated by cosmological simulations of massive primordial stars
+the coefficient is set to $\alpha_0=1$ \footnote[1]{The value of $\alpha_0=1.0$ is motivated by cosmological simulations of massive primordial stars
 under fast streaming velocities \citep{2017Sci...357.1375H,2019MNRAS.484.3510S}.
@@
 The episodic nature of disk accretion decreases the time-averaged accretion rate onto the protostar as $\Mdot_{\star}=\eta \Mdot$, 
-where we adopt $\eta=0.3$ as the conversion efficiency \blue{owing to angular momentum of the accreting flow} \citep{2016MNRAS.459.1137S, 2022arXiv220614459T}. 
+where we adopt $\eta=0.3$ as the conversion efficiency \blue{owing to angular momentum of the accreting flow} \citep{2016MNRAS.459.1137S, 2023MNRAS.518.1601T}. 
 %\blue{
@@
 The feedback-regulated mass can be approximated as
-\footnote{A recent study by \citet{2022arXiv220614459T} provides a more sophisticated prescription of the feedback-regulated stellar mass based on their radiation hydrodynamical simulations.}
+\footnote[2]{A recent study by \citet{2023MNRAS.518.1601T} provides a more sophisticated prescription of the feedback-regulated stellar mass based on their radiation hydrodynamical simulations.}
 %
@@
 Therefore, we assume that the mass of a remnant BH is equal to that of its stellar progenitor.
-%\footnote{
-%\blue{Stellar rotation is expected to induce various effects on the structure evolution; namely, the mass loss rate via winds would be enhanced by the centrifugal force on the surface
-%or suppressed by efficient mixing of the interior structure by meridional circulation \citep[see][references therein]{2008A&A...489..685E,2012A&A...542A.113Y}.
-%Although those effects in the high mass regime are poorly understood yet, full general-relativistic simulations of the gravitational collapse of a rotating supermassive star 
-%found that most of the stellar mass is eventually swallowed by the newly born BH, ejecting only $\sim 10\%$ of the mass \citep{2002ApJ...572L..39S,2016PhRvD..94b1501S}.}}.
 
@@
 where $M_{\bullet,c}=10^8~\Msun$ is adopted
-\footnote{
+\footnote[3]{
 A series of radiation hydrodynamical simulations for BH accretion
@@
 higher redshifts \citep{2020MNRAS.495.2135N}.
-%and the obscured fraction is expected to increase with redshift \citep[]{2022arXiv220603508G}. 
+%and the obscured fraction is expected to increase with redshift \citep[]{2022A&A...666A..17G}. 
 %However, we adopt the prescription of the obscured fraction constrained from quasar observations at $z\lesssim 5$ 
@@
 Moreover, the obscured fraction is found to increase gradually toward higher redshifts and is saturated at $z\gtrsim 2-3$
-\citep{2008A&A...490..905H,2014ApJ...786..104U,2014MNRAS.437.3550M,2018MNRAS.473.2378V,2022arXiv220603508G}.
+\citep{2008A&A...490..905H,2014ApJ...786..104U,2014MNRAS.437.3550M,2018MNRAS.473.2378V,2022A&A...666A..17G}.
 
@@
 is constrained at $-4 \leq \log \delta \leq -0.3$
-\footnote{ We first set a uniform prior at $0\leq \delta \leq 1$, 
+\footnote[4]{ We first set a uniform prior at $0\leq \delta \leq 1$, 
 and find the posterior distribution assembles to $\delta \lesssim 0.1$.
@@
 only bright quasars outshining their host galaxies can be identified as point-like sources in the rest-UV quasar selection 
-(\citetalias{2018ApJ...869..150M}; \citealt{2020MNRAS.495.2135N,2020MNRAS.494.1771A,2021MNRAS.502.2757O,2021MNRAS.502..662B,2022arXiv220712282K}).
+(\citetalias{2018ApJ...869..150M}; \citealt{2020MNRAS.495.2135N,2020MNRAS.494.1771A,2021MNRAS.502.2757O,2021MNRAS.502..662B,2022AJ....164..114K}).
 However, at the faint end of $\Muv\gtrsim -24$ mag, extended sources such as the brightest galaxies at $z\sim 6$ 
@@
 \citet{2019ApJ...883...99S}, \citet{2020MNRAS.493.2059B}, \citet{2021AJ....162...47B},
-\citet{2022ApJS..259...20H,Harikane_2022b,Harikane_2022c}, \citet{2022arXiv220712356D}, \citet{2022arXiv220709434N}.
+\citet{2022ApJS..259...20H,Harikane_2022b,Harikane_2022c}, \citet{2023MNRAS.518.6011D}, \citet{2022ApJ...940L..14N}.
 The fitting forms of the galaxy luminosity functions are given by \citet{2022ApJS..259...20H} at $z\sim 7$, 
@@
 and neglects the contribution of BH seeds from ordinary PopIII remnants in lower-mass halos ($\Mh<10^{11}~\Msun$).
-The latter population is typically less massive ($M_\star \lesssim 10^3~\Msun$) but more abundant \citep[e.g.,][]{2015MNRAS.448..568H,2022arXiv220614459T}.
-Therefore, the BHMF at the low-mass end in our model underestimate their contribution while
+The latter population is typically less massive ($M_\star \lesssim 10^3~\Msun$) but more abundant \citep[e.g.,][]{2015MNRAS.448..568H,2023MNRAS.518.1601T}.
+Therefore, the BHMF at the low-mass end in our model underestimates the abundance while
 the high-mass end at $M_\bullet \gtrsim 10^7~\Msun$ matches the observed distribution well.
@@
 \citep{2013MNRAS.432.2696M, 2016ApJ...819..129O, 2018ApJ...867..150M, 2019ApJ...883...99S, 2020MNRAS.493.2059B,
-2021AJ....162...47B, 2022arXiv220712356D,
-2022ApJS..259...20H, Harikane_2022b, Harikane_2022c, 2022arXiv220709434N}.
+2021AJ....162...47B, 2023MNRAS.518.6011D,
+2022ApJS..259...20H, Harikane_2022b, Harikane_2022c, 2022ApJ...940L..14N}.
 Galaxies at $\Muv\gtrsim -23$ mag dominate in number at all the redshifts and impede
@@
 while the observed Eddington ratio is biased toward higher values and the distribution results in a log-normal shape,
-consistent with that of the brightest quasars at $z\sim 6$ \citep[e.g.,][]{2010AJ....140..546W,2019ApJ...873...35S,2021ApJ...923..262Y,2022arXiv220705113F}.
+consistent with that of the brightest quasars at $z\sim 6$ \citep[e.g.,][]{2010AJ....140..546W,2019ApJ...873...35S,2021ApJ...923..262Y,2022ApJ...941..106F}.
 The log-normal shape still holds with the lower luminosity cut, but a lower luminosity threshold allows us to unveil more hidden quasars with low Eddington ratios.
